### 2020-07-13 tex/Main Text/manuscript.tex
确认了转移进来的tex可以用

\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Water resource utilization regimes at a basin scale: transition framework and development traps}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
\author[a, b]{Bojie Fu}  % 傅老师
\author[c, d]{Xutong Wu}  % 武旭同

% 机构列表
\affil[a]{ % 北师大地表国重
	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
	Faculty of Geographical Science, 
	Beijing Normal University, 
	Beijing 100875, 
	P.R. China
}
\affil[b]{ % 北师大地理学部
	Institute of Land Surface System and Sustainability, 
	Faculty of Geographical Science, 
	Beijing Normal University, 
	Beijing 100875, 
	P.R. China
}
\affil[c]{ % 北大城环
	College of Urban and Environmental Sciences, 
	Peking University, 
	Beijing 100871, 
	P.R. China
}
\affil[d]{ % 中科院生态中心
	State Key Laboratory of Urban and Regional Ecology, 
	Research Center for Eco-Environmental Sciences, 
	Chinese Academy of Sciences, 
	Beijing 100085, 
	P.R. China 
}

% Please give the surname of the lead author for the running footer
% 领衔作者
\leadauthor{Song}

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{ % 作者的相应贡献
	Shuai Wang and Bojie Fu designed this research,
	Shuang Song performed the research and analysed data,
	Shuang Song, Xutong Wu wrote the paper.
}
\authordeclaration{ % 利益冲突陈述
	The authors declare no competing interests.
}

% 如果有共同一作的情况，则uncomment下面这行代码的注释
%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}

% 通讯作者信息
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: shuaiwang@bnu.edu.cn}

% 关键词，三到五个
% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{Water resource management  $|$ Human-water relationship $|$ Water scarcity $|$ Sustainable development}

%tag 摘要
\begin{abstract}
	% 水资源(water resources)对人类社会的重要性，人类对水资源的影响，
	The importance of water resources to human society, 
	the impact of humans on water resources, the relationship between humans and... 
	% 人类与水资源之间逐渐建立了复杂的{人水关系(human-water relationship)}，并形成了{"水资源利用体系 (water utilization regime)"}。
	A complex human-water relationship is gradually being established between water resources.
	And resulted in water utilization regime.
	%通过在流域尺度分析(analyse)水资源利用体系来刻画(depict)人水关系，有助于识别(distinguish)和理解(understand)流域发展过程中面对的困局(traps)，
	% 进而为流域{综合水资源管理 Integrated water resources management}和{协调发展(develop in a coordinated way}提供理论依据。
	This helps to identify and understand the traps in the development of river basins, 
	thus providing a theoretical basis for integrated water resources management and development in a coordinated way.

%这里，同时考虑了流域水资源利用的{“资源压力(stress)”}，{“倾向性(lopsidedness)”}和{“格局(pattern)”}，
% 我们提出了{流域协调发展指数 (Basin coordinated development index)}，用以归纳(summarise)流域水资源利用体系的发展变化情况。

% 以黄河(世界上人为干预最严重的大河之一)为例，流域协调发展系数的变化结果指示，流域的水资源利用体系自上世纪50年代起先后历经了三个不同的阶段。

% 其中1977年前后经历的第一次体系转变(regime shift)主要表现为水资源利用压力的迅速增加，
% 而1993年前后历经的第二次体系转变则主要由水资源利用的倾向性和格局来驱动。

% 这表明黄河流域发展过程中曾一度陷入资源困局，而后成功通过积极调整水资源利用体系摆脱了困局，但当前仍面临陷入结构困局的风险。
% 最后，结合相关理论，我们进一步总结了流域水资源利用体系的一般过渡框架(transition framework)，
% 该框架对理解水资源利用体系的变化及发展过程中面临的相关困局具有指导意义。
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, 
is not only essential for myriad Earth system processes,
but also a key resource supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
At the same time, however, human's modification has profoundly influenced water processes 
and related changes may lead to adverse transitions in functions of human-water systems,
along with various development traps. 
% 世界上诸多大河流域都是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展
Facing major challenges of the Anthropocene, many of the world's big river basins are also centres of economy and civilization 
and urgently in need for integrated water resources management toward sustainability. \cite{bestAnthropogenicStressesWorld2019}
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助
Therefore, understanding the complex relationship between human societies and water resources utilization 
provides underlying supports to development in a coordinated way, at a basin scale.

% tag 引言第二段
% Regime的定义。
Regime is a general term of system’s structure and function 
and one of the most explanatory perspectives when analysis interactions within a coupling system, 
like human and water.
% Regime的转变
Since widespread fluctuating disturbances in social development and natural water resources were out of consideration, 
water utilization regime only will be driven shifting when reorganizations occurred and the tipping points reached.
% Regime过渡性的存在。
As many large river basins had all experienced phases of accelerated water exploitation, over-exploitation of water resource,
and integrated water management, it is a reasonable assumption that existence of a transitional water utilization regime 
corresponds to development of societies. 
% 过渡性有助于理解流域存在的问题
Understanding the transitional nature of water resource regimes, therefore, can help to diagnosis and predict development traps, 
which is crucial for integrated management and coordinated development at a basin scale regard to sustainability.
% 对过渡性的研究还很少
% Despite pervasive and important, there is lacking of formal framework to interpret the water utilization regimes, 
% with much fewer attempts in developing effective methods to detect them and their transitions as well. 
Despite pervasive and important as it is, there is lacking of effective method to detect the water utilization regimes and their shifts, 
with much fewer attempts to develop formal models of its transitions as well.

% Tag 引言第三段
% 作为是古老而常青的现象，前人已经从不同视角刻画了人水关系.
The key to analysis water utilization regimes is to understand the interactions between human societies and water resources, 
which have been depicted from different dimensions, as an ancient but evergreen topic.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, the most widespread concern is the rising stresses on human societies with regard to water resources.
% 人类取水量增加，不灵活部分增长，尽管社会通过不断发展拥有更强大的调蓄能力，但世界上绝大多数流域都面临着更大的水资源压力。
Even though the stocks of water in increasing artificial reservoirs are helpful to water resources availability, 
highly stressed basins still characterized by high water consumption intensities and a major constraint to socio-economic development,
driven by a significant increase in water extractions and a larger share of inflexible water utilization during the last century.
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the need of industrial and ecological developments, tendentiousness of water utilization changed with.
% 尽管主要的用水方式还是农业灌溉，但工业的经济和用水都正在增长，且存在潜在的冲突。
Despite a major water utilization of agricultural irrigation dominating most of the river basins,
there are significant growths and preferential tendentiousness in the economy profits and water consumption regarding industry, 
leading a high potential for conflict between the industrial and agricultural sectors.
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since water availability and utilization are inherently regional concerns, patterns of also play an important role.
% 全球总的取水量很少，但缺水地区很多
Although only 10\% of available water is withdrawn on global average, about 30\% of population live in highly water-stressed areas,
where dominated sections regarding water utilization are various. 
\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}
% 此外，人类活动还在改变这一格局
In addition, human activities are still changing this pattern, 
since positive impacts caused by human interventions mostly occur in upper regions 
whereas aggravated water resources downstream, in many basins around the world.
\cite{veldkampWaterScarcityHotspots2017}
% 将三种视角结合，就是“水资源利用体系”。
Although existing researches have evaluated the aspects of water resource utilization from these different dimensions, 
we still cannot obtain a coherent understanding of regime regard to social development and water utilization, without integrating them.

% tag 讨论最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned dimensions of water utilization, 
we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale
to give a sketch of relationships between human societies and their water utilization.
% 使用案例研究
Then, by applying this index to the Yellow River Basin, China,
we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, 
with change points detection and contribution decomposition methods following.
% 指出发展困局
In addition, combining model and data analysis, 
we further identify resource and development traps that have been exposed by regimes' shifting.
% 最后总结出一般性框架
Finally, refer to the existing theories, we summarized a general transition framework of water utilization regimes, 
which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.

%tag 结果
\section*{Results}
\subsection*{Division of Water Utilization Regimes}
% 这一节主要展示BCDI的变化趋势和WUR的划分
Figure \ref{fig:wcci} shows the change trend of the index.

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:wcci}
\end{figure}

\subsection*{Drivers of the First Regime Shift}

\subsection*{Drivers of the Second Regime Shift}

\subsection*{Language-Editing Services}
Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at www.pnas.org/page/authors/language-editing). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.

\subsection*{Digital Figures}

EPS, high-resolution PDF, and PowerPoint are preferred formats for figures that will be used in the main manuscript. Authors may submit PRC or U3D files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format. Colour images must be in RGB (red, green, blue) mode. Include the font files for any text.

Images must be provided at final size, preferably 1 column width (8.7 cm). Figures wider than 1 column should be sized to 11.4 cm or 17.8 cm wide. Numbers, letters, and symbols should be no smaller than 6 points (2 mm) and no larger than 12 points (6 mm) after reduction and must be consistent.

Figures and tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

\subsection*{Tables}
Tables should be included in the main manuscript file and should not be uploaded separately.

\begin{table}%[htbp]
	\centering
	\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
	\begin{tabular}{lrrr}
		Species & CBS & CV & G3 \\
		\midrule
		1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
		2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
		3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
		\bottomrule
	\end{tabular}

	\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

% tag 讨论
\section*{Discussion}

\subsection*{Transition Framework}
Tables should be included in the main manuscript file and should not be uploaded separately.

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:wcci}
\end{figure}

\subsection*{Development Traps}

%tag 研究方法
\matmethods{Please describe your materials and methods here. This can be more than one paragraph, and may contain subsections and equations as required. Authors should include a statement in the methods section describing how readers will be able to access the data in the paper.

	\subsection*{Water utilization regime index}
	Example text for subsection.
	\subsubsection*{Stresses}
% 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
	Various metrics, therefore, proposed for water stress 
	(e.g. water scarcity, water stresses index, scarcity-flexibility-variability index), 
	where the dimensions of human impact are increasingly valued.
	% 其中SFV指数比较有用
	Among of them, by taking changes of water flexibility and variability into account, 
	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective,
	which considered a valid indicator of temporal changes in water stresses.
	\subsubsection*{Lopsidedness}
	% xxx等人通过考虑消费品中的水消耗提出了虚拟水理论
	% 但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。
	% 如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类在“消耗水”向“利用水”和的倾斜。

	\subsubsection*{Patterns}

	\subsection*{Change points detection}

	\subsection*{Contribution decomposition}
}

\showmatmethods{} % Display the Materials and Methods section

\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}

\showacknow{} % Display the acknowledgments section

% Bibliography
\bibliography{my-papers}

\end{document}

### 2020-07-13 schemes/rep.r
测试可以使用R脚本

@@ -1,0 +1,639 @@
+## Replication Code for
+# A. Abadie, A. Diamond, and J. Hainmueller. 2014.
+# Comparative Politics and the Synthetic Control Method
+# American Journal of Political Science.
+
+rm(list=ls())
+library(foreign)
+library(Synth)
+library(xtable)
+
+# Load Data 
+d <- read.dta("data/repgermany.dta")
+## Table 1 & 2, Figure 1, 2, & 3
+
+## pick v by cross-validation
+# data setup for training model
+dataprep.out <-
+  dataprep(
+           foo = d,
+           predictors    = c("gdp","trade","infrate"),
+           dependent     = "gdp",
+           unit.variable = 1,
+           time.variable = 3,
+           special.predictors = list(
+            list("industry", 1971:1980, c("mean")),
+            list("schooling",c(1970,1975), c("mean")),
+            list("invest70" ,1980, c("mean"))
+           ),
+           treatment.identifier = 7,
+           controls.identifier = unique(d$index)[-7],
+           time.predictors.prior = 1971:1980,
+           time.optimize.ssr = 1981:1990,
+           unit.names.variable = 2,
+           time.plot = 1960:2003
+         )
+
+# fit training model
+synth.out <- 
+  synth(
+        data.prep.obj=dataprep.out,
+        Margin.ipop=.005,Sigf.ipop=7,Bound.ipop=6
+        )
+
+# data prep for main model
+dataprep.out <-
+ dataprep(
+  foo = d,
+  predictors    = c("gdp","trade","infrate"),
+  dependent     = "gdp",
+  unit.variable = 1,
+  time.variable = 3,
+  special.predictors = list(
+    list("industry" ,1981:1990, c("mean")),
+    list("schooling",c(1980,1985), c("mean")),
+    list("invest80" ,1980, c("mean"))
+  ),
+  treatment.identifier = 7,
+  controls.identifier = unique(d$index)[-7],
+  time.predictors.prior = 1981:1990,
+  time.optimize.ssr = 1960:1989,
+  unit.names.variable = 2,
+  time.plot = 1960:2003
+)
+
+# fit main model with v from training model
+synth.out <- synth(
+  data.prep.obj=dataprep.out,
+  custom.v=as.numeric(synth.out$solution.v)
[…]

### 2020-07-13 tools/processing.py

@@ -1,0 +1,47 @@
+# !/usr/bin/env python
+# - * - coding: utf-8 - * -
+# author: Shuang Song time: 2020/1/14
+# Email: SongshGeo@Gmail.com
+# project: 
+
+import os
+import pandas as pd
+import numpy as np
+from matplotlib import pyplot as plt
+from constants import UP, MIDDLE, DOWN
+import csv
+
+
+def judge_region(data):
+    up_df = pd.DataFrame(columns=data.columns)
+    mid_df = pd.DataFrame(columns=data.columns)
+    down_df = pd.DataFrame(columns=data.columns)
+    for region, group in data.groupby('分区'):
+        if region in UP:
+            up_df = up_df.append(group)
+        elif region in MIDDLE:
+            mid_df = mid_df.append(group)
+        elif region in DOWN:
+            down_df = down_df.append(group)
+        else:
+            pass
+    return [up_df, mid_df, down_df]
+
+
+
+# 将dbf文件读取入pandas.DataFrame
+def pd_read_dbf(io, usecols=False):
+    """从文件系统中读取dbf文件并写入DataFrame
+    io: 文件路径，
+    usecols: 使用的列"""
+    from dbfread import DBF  # 加载dbfreead包才能读取文件
+    if io.endswith('.dbf'):
+        table = DBF(io)
+    else:
+        raise Exception("{} is not a dbf file.".format(io.split("/")[-1]))
+    df = pd.DataFrame(table)
+    if usecols:
+        for col in df:
+            if col not in usecols:
+                df.drop(col, axis=1, inplace=True)
+    return df

### 2020-07-13 tools/statistic.py

@@ -1,0 +1,256 @@
+# !/usr/bin/env python
+# - * - coding: utf-8 - * -
+# author: Shuang Song time: 2020/1/14
+# Email: SongshGeo@Gmail.com
+# project: 
+
+import os
+import pandas as pd
+import numpy as np
+from matplotlib import pyplot as plt
+import math
+
+
+def line_fit(x, y):
+    N = float(len(x))
+    sx, sy, sxx, syy, sxy = 0, 0, 0, 0, 0
+    for i in range(0, int(N)):
+        sx += x[i]
+        sy += y[i]
+        sxx += x[i] * x[i]
+        syy += y[i] * y[i]
+        sxy += x[i] * y[i]
+    a = (sy * sx / N - sxy) / (sx * sx / N - sxx)
+    b = (sy - a * sx) / N
+    r = abs(sy * sx / N - sxy) / math.sqrt((sxx - sx * sx / N) * (syy - sy * sy / N))
+    formula = r"$k = %10.2f; R^2 =%10.2f$" % (a, r)
+    return formula
+
+
+def compile_cols(data, col1, col2):
+    # 需要对比的值为value_x和value_y
+    # 新家的列名为value_final
+    # 1.设置一个flag,值为value_y-value_x,为正代表y较大，负代表x较大
+    data['value_flag'] = data[col1] - data[col2]
+    # 2.分别取得y较大的部分和x较大的部分
+    df_test_bigger = data[data['value_flag'] >= 0].copy()
+    df_test_litter = data[data['value_flag'] < 0].copy()
+    # 3.分别对final进行赋值
+    df_test_bigger['Value_Final'] = df_test_bigger[col1]
+    df_test_litter['Value_Final'] = df_test_litter[col2]
+    # 4.使用concat函数将其聚合
+    df_result = pd.concat([df_test_bigger, df_test_litter])
+    return df_result
+
+
+def normalization(data):
+    _range = np.max(data) - np.min(data)
+    return (data - np.min(data)) / _range
+
+
+def huanbi_rate(data, use_col, new_col):
+    data = data.reset_index()
+    result = []
+    for i in range(0, len(data)):
+        if i == 0:
+            rate = np.nan
+            result.append(rate)
+        else:
+            rate = format((data[use_col][i] - data[use_col][i - 1]) / data[use_col][i - 1], '.2%')
+            result.append(rate)
+    data[new_col] = result
+
+
+def difference(data, use_col, new_col):
+    data = data.reset_index()
+    result = []
[…]

### 2020-07-13 tools/processing.py
选择python解析器并修改读取地理文件

@@ -8,24 +8,7 @@ import os
 import pandas as pd
 import numpy as np
 from matplotlib import pyplot as plt
-from constants import UP, MIDDLE, DOWN
 import csv
-
-
-def judge_region(data):
-    up_df = pd.DataFrame(columns=data.columns)
-    mid_df = pd.DataFrame(columns=data.columns)
-    down_df = pd.DataFrame(columns=data.columns)
-    for region, group in data.groupby('分区'):
-        if region in UP:
-            up_df = up_df.append(group)
-        elif region in MIDDLE:
-            mid_df = mid_df.append(group)
-        elif region in DOWN:
-            down_df = down_df.append(group)
-        else:
-            pass
-    return [up_df, mid_df, down_df]
 
 
 

### 2020-07-14 tools/processing.py
读取流域数据

@@ -28,3 +28,14 @@ def pd_read_dbf(io, usecols=False):
             if col not in usecols:
                 df.drop(col, axis=1, inplace=True)
     return df
+
+
+def dbf_data_list(folder_path):
+    """使用保存dbf文件的路径返回所有dbf文件列表
+    folder_path: 装有dbf文件的文件夹"""
+    dbf_files = []
+    full_list = os.listdir(folder_path)
+    for file in full_list:
+        if file.endswith(".dbf"):
+            dbf_files.append(file)
+    return dbf_files

### 2020-07-15 scripts/formula_script.R
可以调用synth方法进行分析的版本

@@ -1,0 +1,41 @@
+
+
+# Load package
+library(Synth)
+
+# Load Data 
+myd <- read.csv("../data/perfectures/basins/all_basins.csv")
+myd$Basin <- as.character(myd$Basin)
+
+## pick v by cross-validation
+# data setup for training model
+dataprep.out <-
+  dataprep(
+           foo = myd,
+           predictors    = c("Total.water.use", "Irrigated.area..Total", "Irrigated.area..Rice", "Irrigated.area..Wheat", "Irrigated.area..Maize", "Irrigated.area..Vegetables.and.fruits", "Irrigated.area..Others", "Industrial.gross.value.added..GVA...Total", "Industrial.gross.value.added..GVA...Textile", "Industrial.gross.value.added..GVA...Papermaking", "Industrial.gross.value.added..GVA...Petrochemicals", "Industrial.gross.value.added..GVA...Metallurgy", "Industrial.gross.value.added..GVA...Mining", "Industrial.gross.value.added..GVA...Food", "Industrial.gross.value.added..GVA...Cements", "Industrial.gross.value.added..GVA...Machinery", "Industrial.gross.value.added..GVA...Electronics", "Industrial.gross.value.added..GVA...Thermal.electrivity", "Industrial.gross.value.added..GVA...Others", "Urban.population", "Service.GVA", "Rural.population", "Livestock.population"),
+           dependent     = "Total.water.use",
+           unit.variable = "Index",
+           time.variable = "Year",
+           treatment.identifier = 3,
+           controls.identifier = c(0, 1, 2, 4, 5, 6, 7, 8),
+           time.predictors.prior = 1965:1987,
+           time.optimize.ssr = 1988:2013,
+           unit.names.variable = "Basin",
+           time.plot = 1965:2013
+         )
+
+# fit training model
+synth.out <- 
+  synth(
+        data.prep.obj=dataprep.out,
+        Margin.ipop=.005,Sigf.ipop=7,Bound.ipop=6
+        )
+
+
+actual_data <- dataprep.out$Y1plot
+synth_data <- dataprep.out$Y0plot %*% synth.out$solution.w 
+
+out_list <- list(
+  y1 = actual_data,
+  y0 = synth_data
+)

### 2020-07-15 schemes/rep.r
把测试数据删去了

@@ -1,639 +1,0 @@
-## Replication Code for
-# A. Abadie, A. Diamond, and J. Hainmueller. 2014.
-# Comparative Politics and the Synthetic Control Method
-# American Journal of Political Science.
-
-rm(list=ls())
-library(foreign)
-library(Synth)
-library(xtable)
-
-# Load Data 
-d <- read.dta("data/repgermany.dta")
-## Table 1 & 2, Figure 1, 2, & 3
-
-## pick v by cross-validation
-# data setup for training model
-dataprep.out <-
-  dataprep(
-           foo = d,
-           predictors    = c("gdp","trade","infrate"),
-           dependent     = "gdp",
-           unit.variable = 1,
-           time.variable = 3,
-           special.predictors = list(
-            list("industry", 1971:1980, c("mean")),
-            list("schooling",c(1970,1975), c("mean")),
-            list("invest70" ,1980, c("mean"))
-           ),
-           treatment.identifier = 7,
-           controls.identifier = unique(d$index)[-7],
-           time.predictors.prior = 1971:1980,
-           time.optimize.ssr = 1981:1990,
-           unit.names.variable = 2,
-           time.plot = 1960:2003
-         )
-
-# fit training model
-synth.out <- 
-  synth(
-        data.prep.obj=dataprep.out,
-        Margin.ipop=.005,Sigf.ipop=7,Bound.ipop=6
-        )
-
-# data prep for main model
-dataprep.out <-
- dataprep(
-  foo = d,
-  predictors    = c("gdp","trade","infrate"),
-  dependent     = "gdp",
-  unit.variable = 1,
-  time.variable = 3,
-  special.predictors = list(
-    list("industry" ,1981:1990, c("mean")),
-    list("schooling",c(1980,1985), c("mean")),
-    list("invest80" ,1980, c("mean"))
-  ),
-  treatment.identifier = 7,
-  controls.identifier = unique(d$index)[-7],
-  time.predictors.prior = 1981:1990,
-  time.optimize.ssr = 1960:1989,
-  unit.names.variable = 2,
-  time.plot = 1960:2003
-)
-
-# fit main model with v from training model
-synth.out <- synth(
-  data.prep.obj=dataprep.out,
-  custom.v=as.numeric(synth.out$solution.v)
-  )
[…]

### 2020-07-15 scripts/formula_script.R

@@ -12,14 +12,14 @@ myd$Basin <- as.character(myd$Basin)
 dataprep.out <-
   dataprep(
            foo = myd,
-           predictors    = c("Total.water.use", "Irrigated.area..Total", "Irrigated.area..Rice", "Irrigated.area..Wheat", "Irrigated.area..Maize", "Irrigated.area..Vegetables.and.fruits", "Irrigated.area..Others", "Industrial.gross.value.added..GVA...Total", "Industrial.gross.value.added..GVA...Textile", "Industrial.gross.value.added..GVA...Papermaking", "Industrial.gross.value.added..GVA...Petrochemicals", "Industrial.gross.value.added..GVA...Metallurgy", "Industrial.gross.value.added..GVA...Mining", "Industrial.gross.value.added..GVA...Food", "Industrial.gross.value.added..GVA...Cements", "Industrial.gross.value.added..GVA...Machinery", "Industrial.gross.value.added..GVA...Electronics", "Industrial.gross.value.added..GVA...Thermal.electrivity", "Industrial.gross.value.added..GVA...Others", "Urban.population", "Service.GVA", "Rural.population", "Livestock.population"),
+           predictors    = c("Irrigated.area..Total", "Industrial.gross.value.added..GVA...Total", "Urban.population", "Service.GVA", "Rural.population", "Livestock.population"),
            dependent     = "Total.water.use",
            unit.variable = "Index",
            time.variable = "Year",
            treatment.identifier = 3,
            controls.identifier = c(0, 1, 2, 4, 5, 6, 7, 8),
-           time.predictors.prior = 1965:1987,
-           time.optimize.ssr = 1988:2013,
+           time.predictors.prior = 1965:1994,
+           time.optimize.ssr = 1995:2013,
            unit.names.variable = "Basin",
            time.plot = 1965:2013
          )

### 2020-07-15 scripts/formula_script.R
做完了利用陷阱的实验

@@ -12,23 +12,22 @@ myd$Basin <- as.character(myd$Basin)
 dataprep.out <-
   dataprep(
            foo = myd,
-           predictors    = c("Irrigated.area..Total", "Industrial.gross.value.added..GVA...Total", "Urban.population", "Service.GVA", "Rural.population", "Livestock.population"),
+           predictors    = c("Irrigated.area..Total", "Irrigated.area..Rice", "Irrigated.area..Wheat", "Irrigated.area..Maize", "Irrigated.area..Vegetables.and.fruits", "Irrigated.area..Others", "Industrial.gross.value.added..GVA...Total", "Industrial.gross.value.added..GVA...Textile", "Industrial.gross.value.added..GVA...Papermaking", "Industrial.gross.value.added..GVA...Petrochemicals", "Industrial.gross.value.added..GVA...Metallurgy", "Industrial.gross.value.added..GVA...Mining", "Industrial.gross.value.added..GVA...Food", "Industrial.gross.value.added..GVA...Cements", "Industrial.gross.value.added..GVA...Machinery", "Industrial.gross.value.added..GVA...Electronics", "Industrial.gross.value.added..GVA...Thermal.electrivity", "Industrial.gross.value.added..GVA...Others", "Urban.population", "Service.GVA", "Rural.population", "Livestock.population"),
            dependent     = "Total.water.use",
            unit.variable = "Index",
            time.variable = "Year",
            treatment.identifier = 3,
            controls.identifier = c(0, 1, 2, 4, 5, 6, 7, 8),
-           time.predictors.prior = 1965:1994,
+           time.predictors.prior = 1978:1994,
            time.optimize.ssr = 1995:2013,
            unit.names.variable = "Basin",
-           time.plot = 1965:2013
+           time.plot = 1978:2013
          )
 
 # fit training model
 synth.out <- 
   synth(
-        data.prep.obj=dataprep.out,
-        Margin.ipop=.005,Sigf.ipop=7,Bound.ipop=6
+        data.prep.obj=dataprep.out
         )
 
 

### 2020-07-16 tex/Main Text/manuscript.tex
可以调用synth方法进行分析的版本
结果第一段写完

@@
 
-%tag 结果
 \section*{Results}
-\subsection*{Division of Water Utilization Regimes}
+%tag 结果1: 指数划分结构
+\subsection*{Water utilization regimes}
 % 这一节主要展示BCDI的变化趋势和WUR的划分
-Figure \ref{fig:wcci} shows the change trend of the index.
+By the two significantly detected change points,
+the changes of IWRU index are split into three periods, 
+whose slopes are various and mainly contributed by different factors \ref{fig:IWRU}.
+\begin{figure}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main_text/index}
+	\caption{Changes of the IWRU index. 
+	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
+	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
+	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
+	}
+	\label{fig:IWRU}
+\end{figure}
+% 接下来分句介绍每个阶段的特征
+% 第一阶段
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
+and the lightening of water stresses made the most striking contribution (xx\%), 
+while tendentiousness and pattern of the water utilization had slight negative contribution.
+% 第二阶段
+In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
+despite positive contributions of tendentiousness and pattern of water utilization,
+because of increasing stresses on water resource playing a larger negative role (xx\%). 
+% 第三阶段
+However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
+and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+% 总的来说，用水三个维度的组合呈现出阶段特征明显，但缓慢过渡的变化趋势
+Taken together, combining the three dimensions of water resources utilization, 
+whose regimes have clear phase-characteristics with gradual transitions between different phases}.
+
+%tag 结果2
+\subsection*{Changes between different regimes}
 
@@
 	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
-	\label{fig:wcci}
+	\label{fig:changes}
 \end{figure}
 
-\subsection*{Drivers of the First Regime Shift}
-
-\subsection*{Drivers of the Second Regime Shift}
+\subsection*{Main drivers of the regime shifts}
 
@@
 	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
-	\label{fig:wcci}
+	\label{fig:framework}
 \end{figure}

### 2020-07-16 tex/Main Text/manuscript.tex
制作了结果一分阶段的图

@@
 Taken together, combining the three dimensions of water resources utilization, 
-whose regimes have clear phase-characteristics with gradual transitions between different phases}.
+whose regimes have clear phase-characteristics with gradual transitions between different phases.
 

### 2020-07-16 tex/Main Text/manuscript.tex
修改了图2阶段划分

@@
 the changes of IWRU index are split into three periods, 
-whose slopes are various and mainly contributed by different factors \ref{fig:IWRU}.
+whose slopes are various and mainly contributed by different factors (Figure~\ref{fig:IWRU}).
 \begin{figure}%[htbp]
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/index}
+	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
 	\caption{Changes of the IWRU index. 
@@
 In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
-and the lightening of water stresses made the most striking contribution (xx\%), 
+and the lightening of water stresses made the most striking contribution (124\%), 
 while tendentiousness and pattern of the water utilization had slight negative contribution.
@@
 despite positive contributions of tendentiousness and pattern of water utilization,
-because of increasing stresses on water resource playing a larger negative role (xx\%). 
+because of increasing stresses on water resource playing a larger negative role (-146\%). 
 % 第三阶段
@@
 Taken together, combining the three dimensions of water resources utilization, 
-whose regimes have clear phase-characteristics with gradual transitions between different phases.
+whose regimes have clear phase-characteristics with gradual transitions between different phases (Figure~\ref{fig:phases}).
+
+\begin{figure}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main_text/phases.pdf}
+	\caption{Combination of three dimensions of water utilization regimes in three different periods. 
+	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.}
+	\label{fig:phases}
+\end{figure}
 

### 2020-07-17 tex/Main Text/manuscript.tex
写完引言第二段

@@
 and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
-% 总的来说，用水三个维度的组合呈现出阶段特征明显，但缓慢过渡的变化趋势
-Taken together, combining the three dimensions of water resources utilization, 
-whose regimes have clear phase-characteristics with gradual transitions between different phases (Figure~\ref{fig:phases}).
+% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
+As a result, each period is various in the most striking positive contributors to IWRU, 
+corresponding to different dimensions of water utilization.
 
+% 用水三个维度的组合呈现出阶段特征明显
+Combining the three dimensions of water resources utilization, further more, 
+sub-index regard to different water utilization dimensions were aggregative distinguishably in each same period, 
+whose regimes show clear phase-characteristics (Figure~\ref{fig:phases}).
 \begin{figure}%[htbp]
@@
 	\includegraphics[width=\linewidth]{../../figures/main_text/phases.pdf}
-	\caption{Combination of three dimensions of water utilization regimes in three different periods. 
-	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.}
+	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
+	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
+	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).
+	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
 	\label{fig:phases}
 \end{figure}
+% 第一阶段到第二阶段
+At the very beginning of research period (1965), high water stress domain the regime, 
+while it experienced a large shift after entering P2 since 1978, 
+with a change in the proportion of contributions between tendentiousness and pattern, too.
+% 第三阶段集中
+In contrast, the three dimensions' contribution were similar from 1994 into P3 to 2013, 
+making the points highly concentrated at the centre of the ternary diagram for that period.
+% 总之，出现制度
+Taken all together, the three phases delineate distinct water resource utilization regimes, 
+corresponding each period of.
 
@@
 \subsection*{Changes between different regimes}
+% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
+A comparison of the phases under different dimensions reveals notable differences between each water use regime 
+(Figure~\ref{fig:dimensions}).
+\begin{figure*}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
+	\caption{
+		Changes in different dimensions of water resources utilization regime.
+		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
+		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
+		\textbf{C,} changes of water utilization pattern index.
+		}
+		\label{fig:dimensions}
+	\end{figure*}
+% 从阶段一到阶段二，水资源压力的变化最为明显
+Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water stresses (Figure~\ref{fig:dimensions}A).
+% 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
+The P1, when water resources were the most abundant period, also had the least water consumption, 
+while most of which were flexible water utilization.
+Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, 
+which increased storage capacities in each water-demand region to relief water resource stresses (SI).
+However, entering P2, although water consumptions continued to increase, 
+the number of new reservoirs was significantly reduced and the total storage capacity of each region was hardly increasing any more. 
+Coupled with declining natural water resources, the water stress index of the basin was rapidly increasing.
+% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
+On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
+tendentiousness and patterns of water utilization were still enlarging their impacts (Figure~\ref{fig:dimensions}B and C). 
+% 首先是用水比例的变化
+Representing tendentiousness of water utilization, 
+increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
+while the influence of both is waning.
+% 再讨论用水格局的变化
+However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
+were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
+% 最后，每个阶段起
+In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
+are reflected in the changes in the corresponding indicators of the three dimensions.
 
-\begin{figure}%[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/index}
-	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
-	\label{fig:changes}
-\end{figure}
-
-\subsection*{Main drivers of the regime shifts}
-
-\subsection*{Language-Editing Services}
-Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at www.pnas.org/page/authors/language-editing).
-PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.
-
-\subsection*{Digital Figures}
-
-EPS, high-resolution PDF, and PowerPoint are preferred formats for figures that will be used in the main manuscript.
-Authors may submit PRC or U3D files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format.
-Colour images must be in RGB (red, green, blue) mode.
-Include the font files for any text.
-
-Images must be provided at final size, preferably 1 column width (8.7 cm).
-Figures wider than 1 column should be sized to 11.4 cm or 17.8 cm wide.
-Numbers, letters, and symbols should be no smaller than 6 points (2 mm) and no larger than 12 points (6 mm) after reduction and must be consistent.
-
-Figures and tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.
-
-\subsection*{Tables}
-Tables should be included in the main manuscript file and should not be uploaded separately.
-
-\begin{table}%[htbp]
-	\centering
-	\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
-	\begin{tabular}{lrrr}
-		Species & CBS & CV & G3 \\
-		\midrule
-		1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
-		2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
-		3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
-		\bottomrule
-	\end{tabular}
-
-	\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
-\end{table}
+\subsection*{Drivers of regime shifts}
+Two regime shifts had distinct main drivers.
+% 第一个 regime shift 包含着
 
@@
 
-\begin{figure}%[htbp]
+\begin{figure*}%[htbp]
 	\centering
@@
 	\label{fig:framework}
-\end{figure}
+\end{figure*}
 

### 2020-07-17 tools/statistic.py

@@ -113,7 +113,7 @@ def Pettitt_change_points(inputdata, p_shr=0.001):
     return change_points
 
 
-def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None, colors=None):
+def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None, colors=None, legend=True, **kargs):
     from scipy import optimize
     def linear(x, k, b):
         return k * x + b
@@ -135,13 +135,14 @@ def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None,
         
         # 绘图
         if colors: 
-            ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), color=colors[i-1])  # 源数据散点图
+            ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), color=colors[i-1], **kargs)  # 源数据散点图
             ax.plot(xi, y_simu, '--', color=colors[i-1])  # 拟合直线图
         else: 
-            ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1])) 
+            ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), **kargs) 
             ax.plot(xi, y_simu, '--')
     
-    ax.legend()
+    if legend:
+        ax.legend()
     y_position = ax.get_ylim()[1]
     for cp in change_points:
         ax.axvline(x=cp, ls=":", c="gray", lw=2)

### 2020-07-26 tex/Main Text/manuscript.tex
7月26给老师看

@@
 \subsection*{Drivers of regime shifts}
-Two regime shifts had distinct main drivers.
-% 第一个 regime shift 包含着
+Based on our model, two regime shifts had distinct main drivers.
+% 第一个 regime shift 主要是经济总量提升导致资源耗竭的加速。
+%经济总量对用水量预测的能力，经济总量对水资源压力的预测能力。
+%经济总量+水库修建对水量、水资源压力的预测
+% 第二次 regime shift 发生了用水关系的变化
 
@@
 	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
-	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
+	\caption{Transition framework of the water utilization regime.}
 	\label{fig:framework}

### 2020-08-03 tex/Main Text/manuscript.tex
写完结果第三段

@@
 \section*{Results}
-%tag 结果1: 指数划分结构
-\subsection*{Water utilization regimes}
-% 这一节主要展示BCDI的变化趋势和WUR的划分
+\subsection*{Division of Water utilization regimes}
+% 这一节主要展示IWRU的变化趋势和WUR的划分
 By the two significantly detected change points,
@@
 %tag 结果2
-\subsection*{Changes between different regimes}
+\subsection*{Changes of water utilization between regimes}
 % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
-A comparison of the phases under different dimensions reveals notable differences between each water use regime 
-(Figure~\ref{fig:dimensions}).
+A comparison of the phases under different dimensions reveals notable differences regarding water utilization
+between each water use regime (Figure~\ref{fig:dimensions}).
 \begin{figure*}%[htbp]
@@
 
-\subsection*{Drivers of regime shifts}
-Based on our model, two regime shifts had distinct main drivers.
-% 第一个 regime shift 主要是经济总量提升导致资源耗竭的加速。
-%经济总量对用水量预测的能力，经济总量对水资源压力的预测能力。
-%经济总量+水库修建对水量、水资源压力的预测
-% 第二次 regime shift 发生了用水关系的变化
+\subsection*{Causes of water utilization regime changes}
+Some main drivers caused the changes of water utilization regime.
+% 经济总量提升导致资源耗竭的加速。
+(1) The expansion of irrigated area and the economic growth of industry and services are key to the
+changes in the tendentiousness of water utilization in P1 and P2.
+During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
+and agriculture was the dominant water use (xx \% of the total).
+After entering P2 to P3, however, while the expansion of irrigated area stalled, 
+industry and services gradually took off, which took up more water resources.
+% 用水关系的变化
+(2) Efficiency of water use sparkly changed during the P3.
+Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
+both their output per unit and water consumption per unit area experienced significant declines.
+% 不断变化的管理模式。
+(3) Changing water management practice contributed between different periods.
+In P1, most of the reservoirs are built in regions where water use is growing, 
+and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
+In P2, on the other hand, the number of additional reservoirs decreases significantly. 
+In P3, the number of reservoirs increases significantly again, 
+but the growth of storage capacity does not match the growth of water demand.
 

### 2020-08-11 tex/Main Text/manuscript.tex
初步写完结果和讨论

@@
 and agriculture was the dominant water use (xx \% of the total).
-After entering P2 to P3, however, while the expansion of irrigated area stalled, 
+After entering P2, however, while the expansion of irrigated area stalled, 
 industry and services gradually took off, which took up more water resources.
@@
 both their output per unit and water consumption per unit area experienced significant declines.
+As a result, after the P3, the proportions of the different water-using sectors tend to average out 
+while the total water consumption remains stable.
 % 不断变化的管理模式。
@@
 In P2, on the other hand, the number of additional reservoirs decreases significantly. 
-In P3, the number of reservoirs increases significantly again, 
+Within P3, the number of reservoirs increases significantly again, 
 but the growth of storage capacity does not match the growth of water demand.
@@
 \subsection*{Transition Framework}
-Tables should be included in the main manuscript file and should not be uploaded separately.
+% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
+Widespread regime shift of coupled systems can be caused by gradual or abrupt changes, 
+where anthropogenic stresses are among the most important drivers of. 
+% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
+With the accumulation of human interventions, 
+a natural-social binary structure of the water cycle has emerged, 
+dominating the current feedbacks of the human-water systems.
+% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
+According to our results, 
+regime shifts as transitional phases of water utilization regimes, 
+similar to evolution of social-ecological system, 
+is one of the most important characteristics towards natural-social binary structure.
+% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
+As such, we summarized a transition framework of the water utilization regimes, 
+which conceptualizes a general trajectory towards a natural-social binary water cycle (figure \ref{fig:framework}).
 
@@
 
+% 在水循环向二元系统过渡过程中，存在几个明显的特征。
+Towards natural-social binary cycle, there are two obvious features between different transition phases.
+% 阶段1
+From the first phase (natural cycle) (Figure~\ref{fig:framework}a), 
+water is a kind of direct provisioning resources, mainly supporting to crop, livestocks or human-beings, 
+as basic ecological services.
+% 阶段2
+However, to the second phase (local binary cycle) (Figure~\ref{fig:framework}b), 
+as local socio-economic systems developing, 
+industry and services (secondary and tertiary-industry) calling for further water consumptions.
+However, since their services can only be generated through the circulation of socio-economic systems, 
+water resources play a non-provisioning role in this cycle. 
+What's more, better organized socio-economic system and developed technology 
+gives humans the will and ability to better manage water resources and change, 
+with intensive intervention in the natural water cycle. 
+% 阶段3
+Entering the third phase (basin binary cycle) (Figure~\ref{fig:framework}c), 
+with further growth in more economically efficient industries and services, 
+trade-off between whose water demands with provisioning demands 
+should be based on the needs of regional socio-economic systems.
+What's more, Water withdrawals are no longer simply determined by local economic development, 
+but more so by the socio-economic development needs of the entire basin, 
+while water resource management are also more often considered on a basin-wide basis, correspondingly.
+
+% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
+Throughout the above transition phases towards binary water cycle, 
+three dimensions of water utilization regime are various, following three laws of evolution respectively.
+Firstly, although stresses on water resources increases by economic expansion boosting water demands, 
+socio-economic progress responding to resource scarcity because of better management and increased water use efficiency. 
+For Example...
+Secondly, the non-provisioning part of water demands further growths and 
+tendentiousness of water utilization continually changes, 
+as humans are more dependent on benefits from non-provisioning part of water supply.
+Thirdly, With closer socio-economic ties between regions and between regions and river basins, 
+the geographic scope of resource supply and demand allocation is expanding, 
+leading to changing patterns of water utilization.
+By combining the three dimensions, water utilization regimes have a tendency of transitional evolution.
+
+% 综上所述，社会对水资源的利用模式作为一个人-水互馈系统，存在阶段性过渡特征。
+For the Yellow River Basin, 
+In addition to the Yellow River Basin, which is the focus of this study, 
+human-water relations in major river basins around the world 
+can be explained by the phases of the transitional framework.
+For examples, \dots \dots.
+In summary, our proposed transitional framework for the nature-society binary water cycle is general in nature.
+
 \subsection*{Development Traps}
+% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
+Since each basin at different transition phase, 
+they are facing different development traps regarding water utilization, 
+leading an unsustainable trajectory. 
+Like social-ecological systems and other complex systems, 
+coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, 
+or collapse emerged because of structural mismatches.
+A number of studies have identified transformation as an important way out of unsustainable trajectory, 
+and different types of transformation are required according to dominating phases and traps of systems.
+Thus, it is crucial to distinguish major development traps 
+based on the transition framework of water utilization regimes.
+
+% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
+According to case studies from watersheds around the world, 
+big river basins often face a resource trap at the beginning of their development, 
+while highly developed ones often face a structural trap.
+% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
+For the Yellow River Basin, 
+after the successive expansion of agriculture and industrial services during the P1 and P2 phases, 
+the utilization rate of surface water resources has reached 80\% of the natural runoff, 
+far exceeding the internationally recognized threshold of 40\%.
+Although water management measures in P1 (construction of numerous reservoirs) 
+mitigated the pressure on water resources due to accelerated development, 
+the pressure on water resources rebounded rapidly during P2, 
+when the number of new reservoirs declined significantly.
+These have led to increasingly severe outages and groundwater depletion of the Yellow River from P2 onwards, 
+and the Yellow River basin had been in a notable resource trap.
+% 资源困局可能普遍存在
+In any case, the xxx and xxx basins have a development history similar to that of the Yellow River, 
+suggesting that resource distress may be widespread in the early stages of the transition.
+
+% 后来摆脱了资源陷阱（表现形式 xxx）。
+Faced with a clear resource trap, a clear transformation path towards integrated basin management was proposed
+that has contributed to the gradual escape of the Yellow River from the resource trap.
+.....
+In short, these integrated management practices made the utilization of water resources into a regime of unified scheduling, 
+in the Yellow River Basin 
+to escape from the “resource trap” of economic expansion and accelerated resource depletion.
+Similarly, 
+many of the world's major river basins have eventually moved towards a system of integrated management and integrated dispatch, 
+especially the XXX and XXX basins, 
+where water resources are extremely scarce.
+
+% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
+However, Despite achieving integrated management and escaping through increased water efficiency, 
+basins still face new structural traps and require further transformation.
+Firstly, in line with paradox of irrigation efficiency \ref{graftonParadoxIrrigationEfficiency2018}, 
+significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 
+has been accompanied by a resurgence in irrigated area, 
+resulting in an unabated and weak upward trend in water stress.
+% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
+As integrated basin allocation dominates water allocation, 
+the propensity to allocate water between non-supply industries, such as industrial services, 
+and agriculture is becoming fixed.
+At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. 
+Typically, similar to other cases, these may lead to a reduction in watershed resilience 
+and leave highly coupled human-water systems facing greater vulnerability to collapse 
+-- a typically structural trap.
+% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
+% 总结：整个流域需进一步转型与适应，以实现高质量发展。
+Therefore, based on the identification of the current basin transition stage and development dilemma, 
+further transitional governance is still needed to achieve high-quality sustainable development of the basin.
 

### 2020-08-15 tex/Main Text/manuscript.tex
做好图3

@@
 \subsection*{Causes of water utilization regime changes}
-Some main drivers caused the changes of water utilization regime.
+
+\begin{figure}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
+	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
+	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
+	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).
+	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
+	\label{fig:Causes}
+\end{figure}
+
+Some main drivers caused the changes of water utilization regime (Figure\ref{fig:Causes}).
 % 经济总量提升导致资源耗竭的加速。

### 2020-08-16 tex/Supplementary Information/PNAS-template-main.tex
一个可以编译补充材料的版本

\documentclass[9pt,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnassupportinginfo}

\title{Water resource utilization regimes at a basin scale: transition framework and development traps}
\author{Shuang Song, Shuai Wang, Bojie Fu, Xutong Wu (complete author list)}
\correspondingauthor{Shuai Wang.\\E-mail: shuaiwang@bnu.edu.cn}

\begin{document}

%% Comment out or remove this line before generating final copy for submission; this will also remove the warning re: "Consecutive odd pages found".
% \instructionspage

\maketitle

%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
\SItext test

% \subsection*{Brief description of Supplementary Information contents: }
% Type or paste text here. This should be additional explanatory text such as an extended technical description of results, full details of mathematical models, etc.

% \section*{Supplementary Information Methods}
\section*{Methods S1. Definition of study area}
% 黄河经历了水资源开发利用和制度改革
The study area is the Yellow River Basin (YRB), 
which has experienced the most intense water exploitation 
and the most dramatic reform of management regimes.

\subsection*{Introduction of Yellow River Basin}
\subsection*{Subarea of Yellow River Basin}
\subsection*{General situation of water use in the YRB}

\section*{Methods S2. Detailed information on dataset and processing}
Add a materials' subsection if you need to.

\section*{Methods S3. Water Utilization Regime Index}
Add a methods subsection if you need to.

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_measured_runoff.pdf}
\caption{Natural measured runoff of Yellow River within different periods.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_wu_sections_stackplot.jpg}
\caption{Second figure}
\end{figure}

\begin{table}\centering
\caption{This is a table}

% 表格
\begin{tabular}{lrrr}
Species & CBS & CV & G3 \\
\midrule
1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
\bottomrule
\end{tabular}
\end{table}

%%% Add this line AFTER all your figures and tables
\FloatBarrier

\dataset{dataset_one.txt}{Type or paste legend here.}

\dataset{dataset_two.txt}{Type or paste legend here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}

\bibliography{pnas-sample}

\end{document}

### 2020-08-19 tex/Supplementary Information/PNAS-template-main.tex
补充说明第一节文字部分

@@
 % 黄河经历了水资源开发利用和制度改革
-The study area is the Yellow River Basin (YRB), 
-which has experienced the most intense water exploitation 
-and the most dramatic reform of management regimes.
+The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime (Supplementary Fig.
+1).
+According to ecological zoning, landscapes types, water resource zoning et al., the Yellow River Basin can be divided into four different regions (supplementary Fig.
+2), which has been widely recognized (ref.).
+Using this division, there are also some differences of nature between different regions regarding water utilization regimes (supplementary Fig.
+3):
+\begin{itemize}
+    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region.
+The most ecology function here is water conservation, as sparsely populated and less economically developed.
+    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region.
+However, because of backward production methods, efficiency of irrigation are used to be very low.
+    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk.
+To reverse this situation, the grain for green project changed the water utilization here strikingly.
+    \item \textbf{Lower Region (LR):} With dense population and the traditional agricultural trajectory, lower region used to be the largest water use region.
+However, as the industrial transformation going, proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
+\end{itemize}
 
@@
 \section*{Methods S2. Detailed information on dataset and processing}
+Since the Yellow River Basin consists of ten provincial areas, the above division can also maintain broad consistency with administrative divisions.
 Add a materials' subsection if you need to.
@@
 %%% Each figure should be on its own page
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
+    \caption{Yellow River Basin}
+\end{figure}
+
 \begin{figure}

### 2020-08-19 tex/Main Text/manuscript.tex
补充结果部分图3的说明文字

@@
 
+% tag 结果3
 \subsection*{Causes of water utilization regime changes}
@@
 	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
-	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
-	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
-	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).
-	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
+	\caption{
+		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
+		\textbf{A.} Total irrigated area and water consumption per unit of irrigated area.
+		\textbf{B.} Gross values added of industry and services, and their water use density (WUI) respectively.
+		\textbf{C.} Number of management practices in different periods, including policy and reservoirs.
+		\textbf{D.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time.
+Red ones denote hub reservoirs in the basin, which plays a role in integrated water management.
+Size of the points indicates their magnitude of water storage capacities.
+Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Three Gorge Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
+(2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage.
+Therefore, these marked reservoirs are significant for the entire basin, far crucial than regional development.
+	}
 	\label{fig:Causes}
@@
 	\caption{Transition framework of the water utilization regime.}
+	tet
 	\label{fig:framework}

### 2020-08-19 tex/Main Text/manuscript.tex
更新过渡阶段的图注释

@@
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes, 
-which conceptualizes a general trajectory towards a natural-social binary water cycle (figure \ref{fig:framework}).
+As such, we summarized a transition framework of the water utilization regimes, which conceptualizes a general trajectory towards a natural-social binary water cycle.
 
@@
 	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
-	\caption{Transition framework of the water utilization regime.}
-	tet
+	\caption{
+		Transition framework of the water utilization regime towards natural-social binary cycle.
+		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
+		\textbf{B. Local binary cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role.
+What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle.
+		\textbf{C.
+Basin binary cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
+Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
+	}
 	\label{fig:framework}
@@
 % 在水循环向二元系统过渡过程中，存在几个明显的特征。
-Towards natural-social binary cycle, there are two obvious features between different transition phases.
-% 阶段1
-From the first phase (natural cycle) (Figure~\ref{fig:framework}a), 
-water is a kind of direct provisioning resources, mainly supporting to crop, livestocks or human-beings, 
-as basic ecological services.
-% 阶段2
-However, to the second phase (local binary cycle) (Figure~\ref{fig:framework}b), 
-as local socio-economic systems developing, 
-industry and services (secondary and tertiary-industry) calling for further water consumptions.
-However, since their services can only be generated through the circulation of socio-economic systems, 
-water resources play a non-provisioning role in this cycle. 
-What's more, better organized socio-economic system and developed technology 
-gives humans the will and ability to better manage water resources and change, 
-with intensive intervention in the natural water cycle. 
-% 阶段3
-Entering the third phase (basin binary cycle) (Figure~\ref{fig:framework}c), 
-with further growth in more economically efficient industries and services, 
-trade-off between whose water demands with provisioning demands 
-should be based on the needs of regional socio-economic systems.
-What's more, Water withdrawals are no longer simply determined by local economic development, 
-but more so by the socio-economic development needs of the entire basin, 
-while water resource management are also more often considered on a basin-wide basis, correspondingly.
-
+Towards natural-social binary cycle, there are two obvious features between different transition phases  (figure \ref{fig:framework}).
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。

### 2020-08-19 tex/main/manuscript.tex
更改tex文件夹的命名

--- 2020-08-19 tex/Main Text/manuscript.tex
@@
 % {pnasinvited} %= Template for a PNAS invited submission
+% \usepackage{cite}
 
@@
 \ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
 % If your first paragraph (i.e.
@@
 % tag 引言第一段
-% 水资源在人类世的重要性，是支持人类社会发展的基础
-\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, 
-is not only essential for myriad Earth system processes,
-but also a key resource supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
-% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-At the same time, however, human's modification has profoundly influenced water processes 
-and related changes may lead to adverse transitions in functions of human-water systems,
-along with various development traps. 
-% 世界上诸多大河流域都是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展
-Facing major challenges of the Anthropocene, many of the world's big river basins are also centres of economy and civilization 
-and urgently in need for integrated water resources management toward sustainability. \cite{bestAnthropogenicStressesWorld2019}
-% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助
-Therefore, understanding the complex relationship between human societies and water resources utilization 
-provides underlying supports to development in a coordinated way, at a basin scale.
+% 水资源在人类世的重要性，是支持人类社会发展的基础。但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。世界上诸多大河流域都是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
+
+\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also a key resource supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
+At the same time, however, human's modification has profoundly influenced water processes and related changes may lead to adverse transitions in functions of human-water systems, along with various development traps \cite{cummingLinkingEconomicGrowth2018}.
+Facing major challenges of the Anthropocene, many of the world's big river basins are also centres of economy and civilization and urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}.
+Therefore, understanding the complex relationship between human societies and water resources utilization provides underlying supports to development in a coordinated way, at a basin scale\cite{HuangHeFangZongZongHeShiCeShiShiDiaoDuGuGanShuiKu}.
 

### 2020-08-20 tex/main/manuscript.tex
测试了可以编译新的参考文献
过了一遍引言的文字

--- 2020-08-19 tex/Main Text/manuscript.tex
@@
+%!BIB program = bibtex
 \documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
@@
 % tag 引言第一段
-% 水资源在人类世的重要性，是支持人类社会发展的基础
-\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, 
-is not only essential for myriad Earth system processes,
-but also a key resource supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
+% 水资源在人类世的重要性，是支持人类社会发展的基础。
+\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
 % 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-At the same time, however, human's modification has profoundly influenced water processes 
-and related changes may lead to adverse transitions in functions of human-water systems,
-along with various development traps. 
-% 世界上诸多大河流域都是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展
-Facing major challenges of the Anthropocene, many of the world's big river basins are also centres of economy and civilization 
-and urgently in need for integrated water resources management toward sustainability. \cite{bestAnthropogenicStressesWorld2019}
-% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助
-Therefore, understanding the complex relationship between human societies and water resources utilization 
-provides underlying supports to development in a coordinated way, at a basin scale.
+At the same time, however, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development traps \cite{cummingLinkingEconomicGrowth2018}.
+% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
+Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}.
+% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
+Therefore, understanding the complex relationship between human societies and water resources utilization, and its evolution provides underlying supports to development in a coordinated way, at a basin scale.
 
 % tag 引言第二段
-% Regime的定义。
-Regime is a general term of system’s structure and function 
-and one of the most explanatory perspectives when analysis interactions within a coupling system, 
-like human and water.
-% Regime的转变
-Since widespread fluctuating disturbances in social development and natural water resources were out of consideration, 
-water utilization regime only will be driven shifting when reorganizations occurred and the tipping points reached.
-% Regime过渡性的存在。
-As many large river basins had all experienced phases of accelerated water exploitation, over-exploitation of water resource,
-and integrated water management, it is a reasonable assumption that existence of a transitional water utilization regime 
-corresponds to development of societies. 
+% Regime 和 Regime shift 的定义。
+Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018a}.
+% 人水系统中的水资源功能
+Within human-water systems, water have several key functions, the most important of which is supplying for human societies in sustainable development based on a complex structure of water utilization.
+% 水资源利用 regime shift
+However, inter-connected human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced regime shifts in water utilization
+\cite{falkenmarkUnderstandingWaterResilience2019}.
+% 稳态转换随着社会发展增加
+These regime shifts, triggered by gradual or abrupt drivers, are likely to occur more often as societies' development increasing their pressure or stuck in traps at a basin scale.
+% Regime 过渡性的存在
+As a result, many large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated governance, as such it is a reasonable assumption that there is a transition pattern within regime shifts.
 % 过渡性有助于理解流域存在的问题
-Understanding the transitional nature of water resource regimes, therefore, can help to diagnosis and predict development traps, 
-which is crucial for integrated management and coordinated development at a basin scale regard to sustainability.
+Sketching the transition of water utilization regimes, therefore, can help to understand and predict development traps, which is crucial for integrated management and coordinated development towards sustainability at a basin scale.
 % 对过渡性的研究还很少
-% Despite pervasive and important, there is lacking of formal framework to interpret the water utilization regimes, 
-% with much fewer attempts in developing effective methods to detect them and their transitions as well. 
-Despite pervasive and important as it is, there is lacking of effective method to detect the water utilization regimes and their shifts, 
-with much fewer attempts to develop formal models of its transitions as well.
+Despite pervasive and important, there is still lacking of effective method to define the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transition phases as well.
 
 % Tag 引言第三段
-% 作为是古老而常青的现象，前人已经从不同视角刻画了人水关系.
-The key to analysis water utilization regimes is to understand the interactions between human societies and water resources, 
-which have been depicted from different dimensions, as an ancient but evergreen topic.
+% 前人已经从不同维度刻画了人水关系.
+Development of societies by using water resources has been going on for at least thousands of years.
+Although its regime shifts and transition phases are not fully understood yet, water utilization has been depicted and studied from different dimensions.
 % 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
-Firstly, the most widespread concern is the rising stresses on human societies with regard to water resources.
-% 人类取水量增加，不灵活部分增长，尽管社会通过不断发展拥有更强大的调蓄能力，但世界上绝大多数流域都面临着更大的水资源压力。
-Even though the stocks of water in increasing artificial reservoirs are helpful to water resources availability, 
-highly stressed basins still characterized by high water consumption intensities and a major constraint to socio-economic development,
-driven by a significant increase in water extractions and a larger share of inflexible water utilization during the last century.
+Firstly, since water resources are scarce, the most widespread concern is the rising stresses on human societies to use water resources.
+Even though the stocks of water in artificial reservoirs are helpful to water resources availability, greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water utilization during the last century.
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}
@@
 Secondly, as the need of industrial and ecological developments, tendentiousness of water utilization changed with. 
-% 尽管主要的用水方式还是农业灌溉，但工业的经济和用水都正在增长，且存在潜在的冲突。
-Despite a major water utilization of agricultural irrigation dominating most of the river basins,
-there are significant growths and preferential tendentiousness in the economy profits and water consumption regarding industry, 
-leading a high potential for conflict between the industrial and agricultural sectors.
+Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential tendentiousness in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors.
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}
 % 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
-Thirdly, since water availability and utilization are inherently regional concerns, patterns of also play an important role.
+Thirdly, since water distribution and utilization are inherently basinal concerns, patterns of also play an important role.
 % 全球总的取水量很少，但缺水地区很多
 Although only 10\% of available water is withdrawn on global average, about 30\% of population live in highly water-stressed areas,
-where dominated sections regarding water utilization are various. 
+where dominated sectors of water utilization are various as well. 
 \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}
 % 此外，人类活动还在改变这一格局
-In addition, human activities are still changing this pattern, 
-since positive impacts caused by human interventions mostly occur in upper regions 
-whereas aggravated water resources downstream, in many basins around the world.
+In addition, human activities are still changing this pattern, since positive impacts caused by human interventions mostly occur in upper regions whereas aggravated water resources downstream, in many basins around the world.
 \cite{veldkampWaterScarcityHotspots2017}
 % 将三种视角结合，就是“水资源利用体系”。
-Although existing researches have evaluated the aspects of water resource utilization from these different dimensions, 
-we still cannot obtain a coherent understanding of regime regard to social development and water utilization, without integrating them.
+Although existing researches have evaluated the aspects of water resource utilization from these different dimensions, we still cannot obtain a coherent understanding of regime shifts regard to social development and water utilization, without integrating them.
 
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, by integrating three above mentioned dimensions of water utilization, 
-we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale
-to give a sketch of relationships between human societies and their water utilization.
+Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization.
 % 使用案例研究
-Then, by applying this index to the Yellow River Basin, China,
-we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, 
-with change points detection and contribution decomposition methods following.
+Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, with change points detection and contribution decomposition methods following.
 % 指出发展困局
-In addition, combining model and data analysis, 
-we further identify resource and development traps that have been exposed by regimes' shifting.
+In addition, combining data analysis, we identify causes of the regime shifts. 
 % 最后总结出一般性框架
-Finally, refer to the existing theories, we summarized a general transition framework of water utilization regimes, 
-which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.
+Finally, refer to the existing theories, we summarized a general transition framework of water utilization regimes, which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.
 

### 2020-08-20 tex/main/manuscript.tex
过一遍结果第一部分

@@
 
-% tag 讨论最后一段
+% tag 引言最后一段
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
@@
 \section*{Results}
-\subsection*{Division of Water utilization regimes}
+\subsection*{Detection of Water utilization regimes}
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-By the two significantly detected change points,
-the changes of IWRU index are split into three periods, 
-whose slopes are various and mainly contributed by different factors (Figure~\ref{fig:IWRU}).
+With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, tendentiousness or pattern of water utilization) (Figure~\ref{fig:IWRU}).
 \begin{figure}%[htbp]
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
-and the lightening of water stresses made the most striking contribution (124\%), 
-while tendentiousness and pattern of the water utilization had slight negative contribution.
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722), while tendentiousness and pattern of the water utilization had slight negative contribution (-0.048 and -0.09 respectively).
 % 第二阶段
-In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
-despite positive contributions of tendentiousness and pattern of water utilization,
-because of increasing stresses on water resource playing a larger negative role (-146\%). 
+In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of tendentiousness and pattern of water utilization (+0.352 and +0.279 respectively), because of increasing stresses on water resource playing a larger negative role (-0.636).
 % 第三阶段
-However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
-and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+However, as the further increasing of positive contributions of water utilization tendentiousness (+0.485) and pattern (+0.515), and decelerations of water stresses (-0.344, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-As a result, each period is various in the most striking positive contributors to IWRU, 
-corresponding to different dimensions of water utilization.
+As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is tendentiousness; and P3 is pattern.
 
 % 用水三个维度的组合呈现出阶段特征明显
-Combining the three dimensions of water resources utilization, further more, 
-sub-index regard to different water utilization dimensions were aggregative distinguishably in each same period, 
-whose regimes show clear phase-characteristics (Figure~\ref{fig:phases}).
+Combining these three dimensions' net contribution to IWRU further, ratios of the contributions of the three dimensions clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
 \begin{figure}%[htbp]
@@
 % 第一阶段到第二阶段
-At the very beginning of research period (1965), high water stress domain the regime, 
-while it experienced a large shift after entering P2 since 1978, 
-with a change in the proportion of contributions between tendentiousness and pattern, too.
+At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stress.
+After then, it experienced a shift to low stress since 1978, with a change in the proportion of contributions between tendentiousness and pattern, too.
 % 第三阶段集中
-In contrast, the three dimensions' contribution were similar from 1994 into P3 to 2013, 
-making the points highly concentrated at the centre of the ternary diagram for that period.
-% 总之，出现制度
-Taken all together, the three phases delineate distinct water resource utilization regimes, 
-corresponding each period of.
+Finally, the three dimensions' contribution were much similar in P3, making the points highly concentrated at the centre of the ternary diagram for that period.
 

### 2020-08-21 tex/main/manuscript.tex
修改结果2的图

@@
 %tag 结果2
-\subsection*{Changes of water utilization between regimes}
+\subsection*{Differences between water utilization regimes}
 % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
-A comparison of the phases under different dimensions reveals notable differences regarding water utilization
-between each water use regime (Figure~\ref{fig:dimensions}).
+The differences between the water utilization regimes are reflected in changes of all three dimensions.
 \begin{figure*}%[htbp]
@@
 % 从阶段一到阶段二，水资源压力的变化最为明显
-Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water stresses (Figure~\ref{fig:dimensions}A).
+Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress (Figure~\ref{fig:dimensions}A).
 % 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
@@
 while most of which were flexible water utilization.
-Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, 
-which increased storage capacities in each water-demand region to relief water resource stresses (SI).
+Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, which increased storage capacities in each water-demand region to relief water resource stresses (SI).
 However, entering P2, although water consumptions continued to increase, 

### 2020-08-21 tools/processing.py

@@ -39,3 +39,11 @@ def dbf_data_list(folder_path):
         if file.endswith(".dbf"):
             dbf_files.append(file)
     return dbf_files
+
+
+def get_position_by_ratio(ax, x_ratio, y_ratio):
+     x_min, x_max = ax.get_xlim()
+     y_min, y_max = ax.get_ylim()
+     x = (x_max-x_min) * x_ratio + x_min
+     y = (y_max-y_min) * y_ratio + y_min
+     return x, y

### 2020-08-21 tools/statistic.py

@@ -217,7 +217,7 @@ def ratio_contribution(numerator, denominator, breakpoints=[1978, 1993]):
 
 
     
-def plot_ratio_contribution(contribution_df, ax=None, bar_width=0.4, denominator_label='Denominator', colors=None, denominator_color=None):
+def plot_ratio_contribution(contribution_df, ax=None, bar_width=0.4, denominator_label='Denominator', colors=None, denominator_color=None, legend_loc=1):
     if colors is None:
         colors = ["#0077b6", "#e07a5f", "#f2cc8f","#81b29a"]
     if denominator_color is None:
@@ -234,7 +234,8 @@ def plot_ratio_contribution(contribution_df, ax=None, bar_width=0.4, denominator
                    height=contribution_df.loc['Numerator', period], 
                    label=denominator_label, 
                    width=bar_width, 
-                   color=colors[0])
+                   color=colors[0],
+                   edgecolor='lightgray')
             
         else:  # 分子有多个需要分别计算贡献
             bottom = 0
@@ -246,12 +247,13 @@ def plot_ratio_contribution(contribution_df, ax=None, bar_width=0.4, denominator
                              bottom=bottom, 
                              label=contribution_df.index[j], 
                              width=bar_width, 
-                             color=colors[color_index])
+                             color=colors[color_index], 
+                             edgecolor='lightgray')
                 bottom += height
                 color_index += 1
-        ax.bar(x=denominator_position, height=contribution_df.loc['Denominator', period], width=bar_width, color=denominator_color, label=denominator_label)
+        ax.bar(x=denominator_position, height=contribution_df.loc['Denominator', period], width=bar_width, color=denominator_color, label=denominator_label, edgecolor='lightgray')
         
         if i == 0:
-            ax.legend()
+            ax.legend(loc=legend_loc)
     ax.set_xticks(np.arange(0, len(contribution_df.columns), 1))
     ax.set_xticklabels(contribution_df.columns.tolist())

### 2020-08-21 tools/statistic.py
修改结果图的细节

@@ -158,10 +158,10 @@ def plot_slopes(slopes, ax=None, colors=None):
     if colors:
         color_list = colors.copy()
         color_list.reverse()
-        slopes.plot.barh(color=color_list, ax=ax)
+        slopes.plot.barh(color=color_list, ax=ax, edgecolor='lightgray')
     else:
-        slopes.plot.barh(color='gray', ax=ax)
-    ax.axvline(x=0, c='gray', lw=2)
+        slopes.plot.barh(color='gray', ax=ax, edgecolor='lightgray')
+    ax.axvline(x=0, c='gray', lw=2, ls="--")
 
     
     

### 2020-08-21 tex/main/manuscript.tex
结果第二部分第一段，及相应的补充材料，图

@@
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, tendentiousness or pattern of water utilization) (Figure~\ref{fig:IWRU}).
+With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, tendentiousness or pattern of water utilization, see Methods) (Figure~\ref{fig:IWRU}).
 \begin{figure}%[htbp]
@@
 % 从阶段一到阶段二，水资源压力的变化最为明显
-Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress (Figure~\ref{fig:dimensions}A).
-% 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
-The P1, when water resources were the most abundant period, also had the least water consumption, 
-while most of which were flexible water utilization.
-Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, which increased storage capacities in each water-demand region to relief water resource stresses (SI).
-However, entering P2, although water consumptions continued to increase, 
-the number of new reservoirs was significantly reduced and the total storage capacity of each region was hardly increasing any more. 
-Coupled with declining natural water resources, the water stress index of the basin was rapidly increasing.
+Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress, which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}A and Figure~\ref{fig:dimensions}D).
+% 1. 水资源丰富，耗水量少且灵活用水
+In the P1, natural surface water resources were rather abundant with lesser water consumptions (supplementary Fig.
+S1 and S3) and most of which were flexible water utilization (supplementary Fig.
+S4).
+During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce.
+Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but most of which built in P1 (supplementary Fig.
+S5 and supplementary Table S1).
+As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.
+
 % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
 On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
-tendentiousness and patterns of water utilization were still enlarging their impacts (Figure~\ref{fig:dimensions}B and C). 
+tendentiousness (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}E) and patterns (Figure~\ref{fig:dimensions}C and Figure~\ref{fig:dimensions}F) of water utilization were enlarging their impacts.
 % 首先是用水比例的变化

### 2020-08-21 tex/sup/PNAS-template-main.tex
结果第二部分第一段，及相应的补充材料，图

--- 2020-08-19 tex/Supplementary Information/PNAS-template-main.tex
@@
 The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime (Supplementary Fig.
-1).
+1A).
 According to ecological zoning, landscapes types, water resource zoning et al., the Yellow River Basin can be divided into four different regions (supplementary Fig.
-2), which has been widely recognized (ref.).
+1B), which has been widely recognized (ref.).
 Using this division, there are also some differences of nature between different regions regarding water utilization regimes (supplementary Fig.
-3):
+2):
 \begin{itemize}
@@
 %%% Each figure should be on its own page
+% 补充图片1：研究区示意图
 \begin{figure}
@@
 
+% 补充图片2：研究区分区特征
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
+    \caption{Different regions}
+\end{figure}
+
+% 补充图片3：天然水资源量
 \begin{figure}
@@
 
+% 补充图片4：水资源灵活性
 \begin{figure}
     \centering
-\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_wu_sections_stackplot.jpg}
-\caption{Second figure}
+    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/inflexible_wu.pdf}
+    \caption{Flexibility}
 \end{figure}
 
+% 补充图片5：水库数量和累积库容
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/reservoirs.pdf}
+    \caption{Reservoirs and accumulated storage}
+\end{figure}
+
+%% 表格
 \begin{table}\centering

### 2020-08-21 tex/main/manuscript.tex
结果第二段改完

@@
 % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
-tendentiousness (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}E) and patterns (Figure~\ref{fig:dimensions}C and Figure~\ref{fig:dimensions}F) of water utilization were enlarging their impacts.
+On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, tendentiousness and patterns of water utilization were keeping to enlarge their impacts (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}C).
 % 首先是用水比例的变化
-Representing tendentiousness of water utilization, 
-increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
-while the influence of both is waning.
+Representing tendentiousness of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while the influence of both are weakening (Figure~\ref{fig:dimensions}E).
 % 再讨论用水格局的变化
-However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
-were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
-% 最后，每个阶段起
-In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
-are reflected in the changes in the corresponding indicators of the three dimensions.
+However, patterns of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing disparities in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
 

### 2020-08-21 tex/main/manuscript.tex
订正了所有正文的图

@@
 		\textbf{B.} Gross values added of industry and services, and their water use density (WUI) respectively.
-		\textbf{C.} Number of management practices in different periods, including policy and reservoirs.
-		\textbf{D.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time.
+		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time.
 Red ones denote hub reservoirs in the basin, which plays a role in integrated water management.
 Size of the points indicates their magnitude of water storage capacities.
-Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Three Gorge Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
+Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
 (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage.

### 2020-08-21 tools/statistic.py

@@ -113,7 +113,7 @@ def Pettitt_change_points(inputdata, p_shr=0.001):
     return change_points
 
 
-def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None, colors=None, legend=True, **kargs):
+def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None, colors=None, returns='slopes', legend=True, **kargs):
     from scipy import optimize
     def linear(x, k, b):
         return k * x + b
@@ -127,6 +127,7 @@ def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None,
     if ax is None:
         fig, ax = plt.subplots()
     i = 0
+    legend = []
     for xi, yi in zip(x_arr, y_arr):
         i += 1
         k, b = optimize.curve_fit(linear, xi, yi)[0]  # 最小二乘拟合直线
@@ -135,19 +136,22 @@ def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None,
         
         # 绘图
         if colors: 
-            ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), color=colors[i-1], **kargs)  # 源数据散点图
+            a = ax.scatter(xi, yi, label='P{}'.format(i), color=colors[i-1], **kargs)  # 源数据散点图
             ax.plot(xi, y_simu, '--', color=colors[i-1])  # 拟合直线图
         else: 
-            ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), **kargs) 
+            a = ax.scatter(xi, yi, label='P{}'.format(i), **kargs) 
             ax.plot(xi, y_simu, '--')
-    
+        legend.append(a)
     if legend:
         ax.legend()
     y_position = ax.get_ylim()[1]
     for cp in change_points:
         ax.axvline(x=cp, ls=":", c="gray", lw=2)
         # ax.text(cp, y_position, "{}".format(cp), va='top', ha='center')  注释年份
-    return slopes
+    if returns == 'slopes':
+        return slopes
+    elif returns == 'legend':
+        return legend
         
         
 def plot_slopes(slopes, ax=None, colors=None):    

### 2020-08-21 tex/main/manuscript.tex
梳理完结果部分

@@
 
-Some main drivers caused the changes of water utilization regime (Figure\ref{fig:Causes}).
+Some main drivers caused the above changes of water utilization regime.
 % 经济总量提升导致资源耗竭的加速。
-(1) The expansion of irrigated area and the economic growth of industry and services are key to the
-changes in the tendentiousness of water utilization in P1 and P2.
-During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
-and agriculture was the dominant water use (xx \% of the total).
-After entering P2, however, while the expansion of irrigated area stalled, 
-industry and services gradually took off, which took up more water resources.
+(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the tendentiousness of water utilization between P1 and P2 (Figure\ref{fig:Causes} A).
+During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6/year$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978).
+Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water.
+
 % 用水关系的变化
-(2) Efficiency of water use sparkly changed during the P3.
-Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
-both their output per unit and water consumption per unit area experienced significant declines.
-As a result, after the P3, the proportions of the different water-using sectors tend to average out 
-while the total water consumption remains stable.
+(2) During the P3, irrigation, whose water consumptions were still dominating, have noticeable changes in its efficiency, however.
+Although irrigated agricultural area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes} A and B).
+It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (supplementary Fig.
+S6).
+As a result, the proportions of water use between the different sectors tend to average out while the total water consumption remains stable, after the P3 (supplementary Fig.
+S7).
+
 % 不断变化的管理模式。
-(3) Changing water management practice contributed between different periods.
-In P1, most of the reservoirs are built in regions where water use is growing, 
-and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
-In P2, on the other hand, the number of additional reservoirs decreases significantly. 
-Within P3, the number of reservoirs increases significantly again, 
-but the growth of storage capacity does not match the growth of water demand.
+(3) Changing water management practice contributed throughout all three periods.
+In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C).
+In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (supplementary Fig.
+S5).
+Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and supplementary Fig.
+S5).
 

### 2020-08-21 tex/sup/PNAS-template-main.tex
订正了所有正文的图
梳理完结果部分

@@
 
+% 补充图片6：节水措施
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{../../figures/placeholder_l.jpg}
+    \caption{technological solutions and water conservation practices}
+\end{figure}
+
+% 补充图片7：用水比例
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{../../figures/supplementary_information/sf_wu_sections_stackplot.jpg}
+    \caption{Proportions of water use between the different sectors}
+\end{figure}
+
+% 补充图片X：管理政策
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/managements.pdf}
+    \caption{Number of management practices in different periods, including policy and reservoirs.}
+\end{figure}
+
 %% 表格

### 2020-08-21 tools/statistic.py

@@ -127,7 +127,7 @@ def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None,
     if ax is None:
         fig, ax = plt.subplots()
     i = 0
-    legend = []
+    legends = []
     for xi, yi in zip(x_arr, y_arr):
         i += 1
         k, b = optimize.curve_fit(linear, xi, yi)[0]  # 最小二乘拟合直线
@@ -136,12 +136,12 @@ def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None,
         
         # 绘图
         if colors: 
-            a = ax.scatter(xi, yi, label='P{}'.format(i), color=colors[i-1], **kargs)  # 源数据散点图
+            a = ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), color=colors[i-1], **kargs)  # 源数据散点图
             ax.plot(xi, y_simu, '--', color=colors[i-1])  # 拟合直线图
         else: 
-            a = ax.scatter(xi, yi, label='P{}'.format(i), **kargs) 
+            a = ax.scatter(xi, yi, label='P{}: {}-{}'.format(i, xi[0], xi[-1]), **kargs) 
             ax.plot(xi, y_simu, '--')
-        legend.append(a)
+        legends.append(a)
     if legend:
         ax.legend()
     y_position = ax.get_ylim()[1]
@@ -151,7 +151,7 @@ def plot_pittitt_change_points(series, ax=None, p_shr=0.001, change_points=None,
     if returns == 'slopes':
         return slopes
     elif returns == 'legend':
-        return legend
+        return legends
         
         
 def plot_slopes(slopes, ax=None, colors=None):    

### 2020-08-22 tex/main/manuscript.tex
整理讨论第一段

@@
 % 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
-Widespread regime shift of coupled systems can be caused by gradual or abrupt changes, 
-where anthropogenic stresses are among the most important drivers of. 
+Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}.
 % 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
-With the accumulation of human interventions, 
-a natural-social binary structure of the water cycle has emerged, 
-dominating the current feedbacks of the human-water systems.
+At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
+% 与社会-自然二元水循环理论
+This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
+\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
 % 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
-According to our results, 
-regime shifts as transitional phases of water utilization regimes, 
-similar to evolution of social-ecological system, 
-is one of the most important characteristics towards natural-social binary structure.
+According to our results, regime shifts as transitional phases of water utilization regimes, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure
+\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes, which conceptualizes a general trajectory towards a natural-social binary water cycle.
+As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).g
 
@@
 		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B. Local binary cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+		\textbf{B. Regional cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
 		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role.
@@
 		\textbf{C.
-Basin binary cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
+Basinal cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
 Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
@@
 % 综上所述，社会对水资源的利用模式作为一个人-水互馈系统，存在阶段性过渡特征。
-For the Yellow River Basin, 
-In addition to the Yellow River Basin, which is the focus of this study, 
-human-water relations in major river basins around the world 
-can be explained by the phases of the transitional framework.
-For examples, \dots \dots.
-In summary, our proposed transitional framework for the nature-society binary water cycle is general in nature.
+For the Yellow River Basin, In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the phases of the transitional framework.
+For examples, \dots \dots. In summary, our proposed transitional framework for the nature-society binary water cycle is general in nature.
 

### 2020-08-22 tex/main/manuscript.tex
修改讨论第一段

@@
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).g
+As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).
 

### 2020-08-22 tex/main/manuscript.tex
过完讨论第一节

@@
 % 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
-According to our results, regime shifts as transitional phases of water utilization regimes, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure
+According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure
 \cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
@@
 
-% 在水循环向二元系统过渡过程中，存在几个明显的特征。
-Towards natural-social binary cycle, there are two obvious features between different transition phases  (figure \ref{fig:framework}).
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
-Throughout the above transition phases towards binary water cycle, 
-three dimensions of water utilization regime are various, following three laws of evolution respectively.
-Firstly, although stresses on water resources increases by economic expansion boosting water demands, 
-socio-economic progress responding to resource scarcity because of better management and increased water use efficiency. 
-For Example...
-Secondly, the non-provisioning part of water demands further growths and 
-tendentiousness of water utilization continually changes, 
-as humans are more dependent on benefits from non-provisioning part of water supply.
-Thirdly, With closer socio-economic ties between regions and between regions and river basins, 
-the geographic scope of resource supply and demand allocation is expanding, 
-leading to changing patterns of water utilization.
-By combining the three dimensions, water utilization regimes have a tendency of transitional evolution.
+Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution, corresponding to typical changes within the Yellow River Basins as an example (Figure~\ref{fig:dimensions}).
+% 水资源压力
+(1) Firstly, although stresses on water resources increases by economic expansion boosting water demands, socio-economic progress responding to resource scarcity by better management and efficiency.
+Water resources were becoming more scarce in the Yellow River Basin from P1 to P3, but the expansion of farmland, the construction of reservoirs, and the increase in water use efficiency became responses to different water utilization stresses in aspects (Figure~\ref{fig:Causes}).
+Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
+% 水资源倾向性
+(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading tendentiousness of water utilization continually tilted to the socio-economic part.
+As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}.
+As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}.
+Anyhow, this changes of tendentiousness reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
+% 水资源格局
+(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing patterns of water utilization.
+In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
+However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}.
+The changes in water utilization patterns along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.
 
-% 综上所述，社会对水资源的利用模式作为一个人-水互馈系统，存在阶段性过渡特征。
-For the Yellow River Basin, In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the phases of the transitional framework.
-For examples, \dots \dots. In summary, our proposed transitional framework for the nature-society binary water cycle is general in nature.
+% 综上所述
+By combining the above three dimensions, water utilization regimes reflect a tendency of transitional evolution thoroughly.
+In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework.
+For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural phases, rapid developments and integrated management regimes.
+\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
+In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal, for identify regime shifts of water utilization.
 
@@
 basins still face new structural traps and require further transformation.
-Firstly, in line with paradox of irrigation efficiency \ref{graftonParadoxIrrigationEfficiency2018}, 
+Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, 
 significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 

### 2020-08-23 tex/main/manuscript.tex
修改讨论第二节第一段，以及做新图

@@
 % 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
-Since each basin at different transition phase, 
-they are facing different development traps regarding water utilization, 
-leading an unsustainable trajectory. 
-Like social-ecological systems and other complex systems, 
-coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, 
-or collapse emerged because of structural mismatches.
-A number of studies have identified transformation as an important way out of unsustainable trajectory, 
-and different types of transformation are required according to dominating phases and traps of systems.
-Thus, it is crucial to distinguish major development traps 
-based on the transition framework of water utilization regimes.
+At different transition phases, basins may face to various development traps in water utilization, leading an unsustainable trajectory (Figure~\ref{fig:traps}).
+Like social-ecological systems and other complex systems, coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, or collapse emerged because of structural mismatches.
+A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems.
+Thus, it is crucial to distinguish major development traps based on the transition framework of water utilization regimes.
+
+\begin{figure}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main_text/traps.jpg}
+	\caption{
+		\textbf{Transition phases of water resources utilization regime and development traps.}
+		Green arrows indicate the trajectory without falling into any development trap, IWRU roughly follows a non-linear upward trend at the same time.
+However, overexploitation of water resources will leave the system in a local resource trap, without moving to regional coordinated cycle.
+And even if one enters a regional cycle, it can still fall into a structural trap when water utilization fails to adapt to the complex changes within human-water systems.
+	}
+	\label{fig:traps}
+\end{figure}
 
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
-According to case studies from watersheds around the world, 
-big river basins often face a resource trap at the beginning of their development, 
-while highly developed ones often face a structural trap.
+According to case studies from watersheds around the world, big river basins often face a resource trap at the beginning of their development, while highly developed ones often face a structural trap.
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-For the Yellow River Basin, 
-after the successive expansion of agriculture and industrial services during the P1 and P2 phases, 
-the utilization rate of surface water resources has reached 80\% of the natural runoff, 
-far exceeding the internationally recognized threshold of 40\%.
-Although water management measures in P1 (construction of numerous reservoirs) 
-mitigated the pressure on water resources due to accelerated development, 
-the pressure on water resources rebounded rapidly during P2, 
-when the number of new reservoirs declined significantly.
-These have led to increasingly severe outages and groundwater depletion of the Yellow River from P2 onwards, 
-and the Yellow River basin had been in a notable resource trap.
+For the Yellow River Basin, after the successive expansion of agriculture and industrial services during the P1 and P2 phases, the utilization rate of surface water resources has reached 80\% of the natural runoff, far exceeding the internationally recognized threshold of 40\%.
+Although water management measures in P1 (construction of numerous reservoirs) mitigated the pressure on water resources due to accelerated development, the pressure on water resources rebounded rapidly during P2, when the number of new reservoirs declined significantly.
+These have led to increasingly severe outages and groundwater depletion of the Yellow River from P2 onwards, and the Yellow River basin had been in a notable resource trap.
 % 资源困局可能普遍存在

### 2020-08-23 tex/main/manuscript.tex
过一遍引言第二节的第二段

@@
 At different transition phases, basins may face to various development traps in water utilization, leading an unsustainable trajectory (Figure~\ref{fig:traps}). 
-Like social-ecological systems and other complex systems, coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, or collapse emerged because of structural mismatches.
-A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems.
-Thus, it is crucial to distinguish major development traps based on the transition framework of water utilization regimes.
+% 资源陷阱和失配，导致崩溃
+Like social-ecological systems and other complex systems, coupled human-water system may collapse under the gradual pressure on resources or because of structural mismatches 
+\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
+% 转型应对陷阱
+A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
+% 我们的框架有助于理解和识别
+Thus, our transition framework can identify regime shifts of water utilization, which can help to predict possible development traps.
 
@@
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
-According to case studies from watersheds around the world, big river basins often face a resource trap at the beginning of their development, while highly developed ones often face a structural trap.
+According to case studies around the world, big river basins often face resource traps at the beginning of their developments, while highly developed ones often face structural traps.
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-For the Yellow River Basin, after the successive expansion of agriculture and industrial services during the P1 and P2 phases, the utilization rate of surface water resources has reached 80\% of the natural runoff, far exceeding the internationally recognized threshold of 40\%.
-Although water management measures in P1 (construction of numerous reservoirs) mitigated the pressure on water resources due to accelerated development, the pressure on water resources rebounded rapidly during P2, when the number of new reservoirs declined significantly.
-These have led to increasingly severe outages and groundwater depletion of the Yellow River from P2 onwards, and the Yellow River basin had been in a notable resource trap.
+During P1 and P2 (refers from natural cycle to the local cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
+Although water management practices in P1 (construction of numerous reservoirs) mitigated the stress on water resources from accelerated development, it became scarce rapidly throughout and water utilization stresses rebounded in the P2 along with a regime shift.
+The resource trap is revealed at this point, with severe runoff outages and groundwater depletion of the Yellow River from P2 onwards (supplementary Fig.
+S8).
 % 资源困局可能普遍存在
-In any case, the xxx and xxx basins have a development history similar to that of the Yellow River, 
-suggesting that resource distress may be widespread in the early stages of the transition.
+Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to local cycle
+\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
 

### 2020-08-23 tex/main/manuscript.tex
讨论第二节第三段

@@
 		Green arrows indicate the trajectory without falling into any development trap, IWRU roughly follows a non-linear upward trend at the same time.
-However, overexploitation of water resources will leave the system in a local resource trap, without moving to regional coordinated cycle.
+However, overexploitation of water resources will leave the system in a resource trap, without moving to regional coordinated cycle.
 And even if one enters a regional cycle, it can still fall into a structural trap when water utilization fails to adapt to the complex changes within human-water systems.
@@
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-During P1 and P2 (refers from natural cycle to the local cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
+During P1 and P2 (refers from natural cycle to the regional cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
 Although water management practices in P1 (construction of numerous reservoirs) mitigated the stress on water resources from accelerated development, it became scarce rapidly throughout and water utilization stresses rebounded in the P2 along with a regime shift.
@@
 % 资源困局可能普遍存在
-Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to local cycle
+Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to regional cycle
 \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
@@
 % 后来摆脱了资源陷阱（表现形式 xxx）。
-Faced with a clear resource trap, a clear transformation path towards integrated basin management was proposed
-that has contributed to the gradual escape of the Yellow River from the resource trap.
-.....
-In short, these integrated management practices made the utilization of water resources into a regime of unified scheduling, 
-in the Yellow River Basin 
-to escape from the “resource trap” of economic expansion and accelerated resource depletion.
-Similarly, 
-many of the world's major river basins have eventually moved towards a system of integrated management and integrated dispatch, 
-especially the XXX and XXX basins, 
-where water resources are extremely scarce.
+To get rid of the resource trap, a clear transformation towards integrated basin management was proposed, with several management practices (supplementary Methods S4 and Fig.
+S9).
+The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}.
+Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}.
+These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the “resource trap”.
+Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g.
+Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017a}.
 
 % 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
-However, Despite achieving integrated management and escaping through increased water efficiency, 
-basins still face new structural traps and require further transformation.
-Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, 
-significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 
-has been accompanied by a resurgence in irrigated area, 
+However, in the regional cycle regime of water utilization, basins still face new structural traps and require further transformation.
+Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, significant improvement in agricultural irrigation efficiency (or decline in water use intensity) has been accompanied by a resurgence in irrigated area,
 resulting in an unabated and weak upward trend in water stress.
 % 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
-As integrated basin allocation dominates water allocation, 
-the propensity to allocate water between non-supply industries, such as industrial services, 
-and agriculture is becoming fixed.
+As integrated basin allocation dominates water allocation, the propensity to allocate water between non-supply industries, such as industrial services, and agriculture is becoming fixed.
 At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly.
-Typically, similar to other cases, these may lead to a reduction in watershed resilience 
-and leave highly coupled human-water systems facing greater vulnerability to collapse 
--- a typically structural trap.
+Typically, similar to other cases, these may lead to a reduction in watershed resilience and leave highly coupled human-water systems facing greater vulnerability to collapse --a typically structural trap.
 % 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。

### 2020-08-23 tex/main/manuscript.tex
整理完全部讨论

@@
 
-% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
-However, in the regional cycle regime of water utilization, basins still face new structural traps and require further transformation.
-Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, significant improvement in agricultural irrigation efficiency (or decline in water use intensity) has been accompanied by a resurgence in irrigated area,
-resulting in an unabated and weak upward trend in water stress.
+% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
+However, in the regional cycle regime of water utilization, the Yellow River Basins still faces structural traps and require further transformation according to changes within the human-water system. 
+Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency (i.e.
+decline in water use intensity) has been accompanied by a resurgence in irrigated area, resulting in an unabated and weak upward trend in water stress \cite{graftonParadoxIrrigationEfficiency2018}.
 % 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
-As integrated basin allocation dominates water allocation, the propensity to allocate water between non-supply industries, such as industrial services, and agriculture is becoming fixed.
-At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly.
-Typically, similar to other cases, these may lead to a reduction in watershed resilience and leave highly coupled human-water systems facing greater vulnerability to collapse --a typically structural trap.
+Secondly, the changing tendentiousness between non-provisioning (i.e.
+industry and urban services) and provisioning (i.e.
+domestic and irrigation water use) is stagnating (see Figure~\ref{fig:dimensions}E) because of rigidify in the industrial structure.
+At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly (supplementary Fig. S4). 
 % 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
 % 总结：整个流域需进一步转型与适应，以实现高质量发展。
-Therefore, based on the identification of the current basin transition stage and development dilemma, 
-further transitional governance is still needed to achieve high-quality sustainable development of the basin.
+Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural trap \cite{cummingResilienceBigRiver2011}.
+Therefore, based on the identification of current phases and development traps by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin \cite{scoonesTransformationsSustainabilityCombining2020a}.
 

### 2020-08-23 tex/main/manuscript.tex
写完摘要和significance

@@
 % PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
-\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
+\significancestatement{
+	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
 The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership.
-The significance statement appears in the paper itself and is required for all research papers.}
+The significance statement appears in the paper itself and is required for all research papers.
+	Water, a key resource to support the sustainable development of human societies, whose natural cycle has been modified by growing socio-economic processes.
+We propose a new method with an integrated indicator to detect water utilization regimes and applying them on the Yellow River Basin, a typical overexploited basin in China.
+After sketching changes of relationships between development and water utilization within the Yellow River Basin, we summarized a general transition framework.
+By predicting widespread development traps, it can be a useful guideline for basins all around the world in their sustainable developing trajectories.
+}
 
@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Water resource management  $|$ Human-water relationship $|$ Water scarcity $|$ Sustainable development}
+\keywords{Regime shifts $|$ Human-water relationship $|$ Water resource management $|$ Water utilization $|$ Sustainable development}
 
@@
 \begin{abstract}
-	% 水资源(water resources)对人类社会的重要性，人类对水资源的影响，
-	The importance of water resources to human society, 
-	the impact of humans on water resources, the relationship between humans and... 
-	% 人类与水资源之间逐渐建立了复杂的{人水关系(human-water relationship)}，并形成了{"水资源利用体系 (water utilization regime)"}。
-	A complex human-water relationship is gradually being established between water resources.
-	And resulted in water utilization regime.
-	%通过在流域尺度分析(analyse)水资源利用体系来刻画(depict)人水关系，有助于识别(distinguish)和理解(understand)流域发展过程中面对的困局(traps)，
-	% 进而为流域{综合水资源管理 Integrated water resources management}和{协调发展(develop in a coordinated way}提供理论依据。
-	This helps to identify and understand the traps in the development of river basins, 
-	thus providing a theoretical basis for integrated water resources management and development in a coordinated way.
-
-%这里，同时考虑了流域水资源利用的{“资源压力(stress)”}，{“倾向性(lopsidedness)”}和{“格局(pattern)”}，
-% 我们提出了{流域协调发展指数 (Basin coordinated development index)}，用以归纳(summarise)流域水资源利用体系的发展变化情况。
-
-% 以黄河(世界上人为干预最严重的大河之一)为例，流域协调发展系数的变化结果指示，流域的水资源利用体系自上世纪50年代起先后历经了三个不同的阶段。
-
-% 其中1977年前后经历的第一次体系转变(regime shift)主要表现为水资源利用压力的迅速增加，
-% 而1993年前后历经的第二次体系转变则主要由水资源利用的倾向性和格局来驱动。
-
-% 这表明黄河流域发展过程中曾一度陷入资源困局，而后成功通过积极调整水资源利用体系摆脱了困局，但当前仍面临陷入结构困局的风险。
-% 最后，结合相关理论，我们进一步总结了流域水资源利用体系的一般过渡框架(transition framework)，
-% 该框架对理解水资源利用体系的变化及发展过程中面临的相关困局具有指导意义。
+	In the context of regime shifts, understanding the complex relationship between human societies and water resources utilization provides underlying supports to development in a coordinated way at a basin scale.
+However, there is still lacking of effective method to detect regime shifts of water utilization, with much fewer attempts to develop theoretical models to explain their transition phases as well.
+Here, by integrating three different dimensions of water utilization (stress, tendentiousness and pattern), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to detect regime shifts.
+By applying this index to the Yellow River Basin, China, we summarized a general transition framework of regimes, which gives a sketch of relationships between human societies and their water utilization.
+Based on the framework, transition phases within the three regimes and accompanying development traps can be well understood, as a useful guideline for the Yellow River to develop in a coordinated way.
 \end{abstract}

### 2020-08-23 tex/main/manuscript.tex
修正图的位置和图例

@@
 	\caption{
-		Changes in different dimensions of water resources utilization regime.
-		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
-		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
-		\textbf{C,} changes of water utilization pattern index.
+		Changes in different dimensions of water resources utilization regimes and their main contributors.
+		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index).
+		\textbf{B,} changes of water utilization tendentiousness, indicated by non-provisioning water shares.
+		\textbf{C,} changes of water utilization pattern, indicated by unstandardized distribution information entropy index (see supplementary: Methods. S3 for details).
+		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their contributions to changes of unstandardized SFV-index.
+		\textbf{E,} Main impact water uses to water utilization tendentiousnesses, and their contributions to changes of non-provisioning water shares.
+		\textbf{F,} Main impact factors to water utilization patterns, and their contributions to changes of related unstandardized distribution information entropy index (see supplementary: Methods.
+S3 for details).
 		}
@@
 		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
-		\textbf{A.} Total irrigated area and water consumption per unit of irrigated area.
-		\textbf{B.} Gross values added of industry and services, and their water use density (WUI) respectively.
+		\textbf{A.} Changes of total irrigated area and water consumption per unit of irrigated area.
+		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (see supplementary: Methods. S2 for details).
 		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time.
@@
 \subsection*{Transition Framework}
-% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
-Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}.
-% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
-At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
-% 与社会-自然二元水循环理论
-This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
-\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
-% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
-According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure
-\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
-% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).
 
-\begin{figure*}%[htbp]
+\begin{figure*}[thbp]
 	\centering
@@
 \end{figure*}
+
+% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
+Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}.
+% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
+At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
+% 与社会-自然二元水循环理论
+This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
+\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
+% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
+According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure
+\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
+% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
+As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).
 

### 2020-08-23 tex/main/manuscript.tex
写完断点检测和贡献分解的方法

@@
 	which considered a valid indicator of temporal changes in water stresses.
-	\subsubsection*{Lopsidedness}
+	\subsubsection*{Tendentiousness}
 	% xxx等人通过考虑消费品中的水消耗提出了虚拟水理论
@@
 	\subsection*{Change points detection}
+		The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
+		The approach after Pettitt (1979) is commonly applied to detect a single change-point in hydrological series or climate series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
+It tests the $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
+The non-parametric statistic is defined as:
 
+		$$ K_t = max|U_{t, T}|$$
+		where:
+		$$ U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j) $$
+
+		The change-point of the series is located at $K_T$, provided that the statistic is significant.
+We use 0.001 as the threshold of p-value, which means the probability of a statistically significant change-point judgment being valid is more than $99.9\%$.
+Since this method only can return one significant change point, we repeat it Until all significant change points were detected.
+
+	% 计算贡献度
 	\subsection*{Contribution decomposition}
+		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
+Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress (S), tendentiousness (T) and pattern (P) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
+S3):
+		$$ IWRU = T * P * S ^ {-1} $$
+		Take the logarithm of both sides then, we get:
+		$$ ln(IWRU) = ln(S) + ln(T) - ln(P) $$
+		Since the changes of IWRU $\Delta IWRU$ can be expressed as $\Delta IWRU = ln(IWRU_2) - ln(IWRU_1)$, where $IWRU_2$ and $IWRU_1$ are ending and beginning values of IWRU in a certain time period, combining the above equations we can get:
+		$$ \Delta IWRU = ln(\frac{S_1}{S_2}) + ln(\frac{T_2}{T_1}) + ln(\frac{P_2}{P_1}) = -\Delta S + \Delta T + \Delta P $$
+		Then, we can calculate contributions $C_F$ of a certain factor $F$ in a certain period by:
+		$$ C_{F} = \frac{|\Delta C_{F}|}{\Delta IWRU}$$
 }

### 2020-08-23 tex/main/manuscript.tex
写完方法IWUR的整体部分

@@
 %tag 研究方法
-\matmethods{Please describe your materials and methods here.
-This can be more than one paragraph, and may contain subsections and equations as required.
-Authors should include a statement in the methods section describing how readers will be able to access the data in the paper.
+\matmethods{
+Here, we constructed the Integrated Water Resources Utilization (IWRU) Index which consists of three dimensions and identified the regime in the changes of the index over time by change points detection.
+Finally, the contribution to changes of IWRU index along with each main indicators were calculated separately for each regime (i.e.
+period).
 
-	\subsection*{Water utilization regime index}
-	Example text for subsection.
-	\subsubsection*{Stresses}
+	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
+	The Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (stresses, tendentiousnesses and patterns, denoted by sub-indicators correspondingly).
+Assuming they have equal weights, we log-transformed and standardized the three sub-indicators for elimination of differences between indicators.
+It means for each indicator $I_{sub}$, we performed:
+	$$ I' = log(I_{sub}) $$
+	$$ I = (I' - I'_{min}) / (I'_{max}-I'_{min})$$
+	where $I$ is standardized series for $I_{sub}$.
+	Then, since we assumed different relationships between development and sub-indicators, we added them together in equal weights:
+	$$ IWRU = \sum_{i}^3 I'_i $$
+	where $i$ is stress, tendentiousness or pattern, and $I'_i$ is standardized sub-indicator of them.
+A brief description of the sub-indicators used to measure each dimension follows (see SI Methods.
+S3 for more details).
+
+	\subsubsection*{Sub-indicator of Stresses}
 % 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
-	Various metrics, therefore, proposed for water stress 
-	(e.g. water scarcity, water stresses index, scarcity-flexibility-variability index), 
-	where the dimensions of human impact are increasingly valued.
+	Various metrics, therefore, proposed for water stress (e.g.
+water scarcity, water stresses index, scarcity-flexibility-variability index), where the dimensions of human impact are increasingly valued.
 	% 其中SFV指数比较有用
-	Among of them, by taking changes of water flexibility and variability into account, 
-	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective,
-	which considered a valid indicator of temporal changes in water stresses.
-	\subsubsection*{Tendentiousness}
+	Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid indicator of temporal changes in water stresses.
+	\subsubsection*{Sub-indicator of Tendentiousness}
 	% xxx等人通过考虑消费品中的水消耗提出了虚拟水理论
@@
 
-	\subsubsection*{Patterns}
+	\subsubsection*{Sub-indicator of Patterns}
 
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress (S), tendentiousness (T) and pattern (P) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
+Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($S$), tendentiousness ($T$) and pattern ($P$) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
 S3):

### 2020-08-23 tex/main/manuscript.tex
初稿

@@
 	\subsubsection*{Sub-indicator of Stresses}
-% 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
-	Various metrics, therefore, proposed for water stress (e.g.
-water scarcity, water stresses index, scarcity-flexibility-variability index), where the dimensions of human impact are increasingly valued.
-	% 其中SFV指数比较有用
-	Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid indicator of temporal changes in water stresses.
+	Humans use technology to continuously manage water resources, so a simple physical water scarcity index cannot reasonably assess water scarcity in the evolution and transition of socio-water systems.
+Therefore, we refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water scarcity in the basin.
+The index takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity \cite{qinFlexibilityIntensityGlobal2019}.
+
+	To apply this method, we need to combine three metrics following:
+
+	First for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume, in year $j$ and region $i$:
+	$$ A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}} $$
+	Second for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.
+for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
+	$$ B_{i, j} = \frac{WU_{inflexible}}{R_{i, avg}} $$
+	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
+	$$ C_i = C1_i * (1 - C2_i) $$
+	$$ C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} $$
+	$$ C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} $$
+	$$ C2_{i} = 1, \ if RC >= R_{i, avg} $$
+	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+
+	Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate $SFV$ index after normalizing them:
+	$$ V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3} $$
+	$$ a = \frac{1}{V_{max} - V_{min}}; $$
+	$$ b = \frac{1}{V_{min} - V_{max}} * V_{min} $$
+	$$ SFV = a * V + b $$
+
 	\subsubsection*{Sub-indicator of Tendentiousness}
-	% xxx等人通过考虑消费品中的水消耗提出了虚拟水理论
-	% 但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。
-	% 如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类在“消耗水”向“利用水”和的倾斜。
+	To tendentiousness, we use non-provisioning shares of water use as an indicator.
+While provisional water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning water use ($WU_{non-pro}$) includes industrial and urban services water uses.
+Then, we can calculate the non-provisioning shares by:
+	$$ NPS_{ij} = \frac{WU_{indirect, i, j}}{WU_{direct, i, j} + WU_{undirect, i, j}} $$
 
 	\subsubsection*{Sub-indicator of Patterns}
+	To description of patterns between regions or sections, we designed an indicator by imitation of information entropy.
+Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy).
+The ratio between the actual water allocation entropy and this maximum entropy is the allocation entropy index.
+	$$ ratio = \frac{Entropy}{Entropy_{max}} $$
+	where $Entropy$ and $Entropy_{max}$ are entropy and maximum entropy of water distributions, respectively. They can be calculated by:
+	$$ Entropy = \sum_{i=1}^n \sum_{j=1}^m -log(p_{ij}) * p_{ij} $$
+	$$ Entropy_{max} = n * \sum_{j=1}^m -\frac{p_j}{n} * log(\frac{p_j}{n}) $$ 
+	where $p_j$ and $p_ij$ are proportions of water use in sector $j$ and region $i$:
+	$$ p_j = \frac{\sum_{i=1}^n WU_j}{\sum_{i=1}^n WU} $$
+	$$ p_{ij} = \frac{WU_{ij}} {\sum_{i=1}^n \sum_{j=1}^m WU_{ij}} $$
+	where $n$ is the total number of regions ($n=4$ here, see supplementary Methods. S1) and $m$ is the total number of sectors ($m=4$ here, see supplementary Methods. S2).
 

### 2020-08-23 tex/sup/PNAS-template-main.tex
过一遍引言第二节的第二段
讨论第二节第三段
初稿

@@
 
+\subsection*{Stress: SFV-index}
+	% 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
+	Various metrics, therefore, proposed for water stress (e.g.
+water scarcity, water stresses index, scarcity-flexibility-variability index), where the dimensions of human impact are increasingly valued.
+	% 其中SFV指数比较有用
+    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid indicator of temporal changes in water stresses.
+
+\subsection*{Tendentiousness: Non-provisioning share}
+	% xxx等人通过考虑消费品中的水消耗提出了虚拟水理论
+	% 但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。
+	% 如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类在“消耗水”向“利用水”和的倾斜。
+
+\section{Methods S4. Water Management Practices}
+
 %%% Each figure should be on its own page
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
+    \includegraphics[width=\textwidth]{../../figures/supplementary_information/YRB.jpg}
     \caption{Yellow River Basin}
@@
 
-% 补充图片X：管理政策
+% 补充图片8：黄河断流
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/outages.jpg}
+    \caption{Severe runoff outages and groundwater depletion}
+\end{figure}
+
+% 补充图片9：管理政策
 \begin{figure}

### 2020-09-10 tex/sup/supplementary_information.tex
修改补充材料的名字
更改好了机房电脑的Latex和Python配置

--- 2020-08-23 tex/sup/PNAS-template-main.tex
@@
 %% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
-\SItext test
+\SItext{This supplementary document consists of three sections and 10 figures.
+Firstly, we introduced our study area, the Yellow River Basin, in the section Methods S1.
+Definition of study area.
+Then, we give a detailed description of used datasets and analysis their uncertainties in the section Methods S2.
+Detailed information on dataset and processing.
+Finally, the index along with corresponding indicators are introduced in the section Methods S3.
+Water Utility Regime Index.}
 
@@
 
-\section*{Methods S3. Water Utilization Regime Index}
+\section*{Methods S3. Water Utility Regime Index}
 Add a methods subsection if you need to.
@@
 
-%% 表格
-\begin{table}\centering
-\caption{This is a table}
+% %% 表格
+% \begin{table}\centering
+% \caption{This is a table}
 
-% 表格
-\begin{tabular}{lrrr}
-Species & CBS & CV & G3 \\
-\midrule
-1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
-2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
-3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
-\bottomrule
-\end{tabular}
-\end{table}
+% % 表格
+% \begin{tabular}{lrrr}
+% Species & CBS & CV & G3 \\
+% \midrule
+% 1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
+% 2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
+% 3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
+% \bottomrule
+% \end{tabular}
+% \end{table}
 
@@
 
-\dataset{dataset_one.txt}{Type or paste legend here.}
+% \dataset{dataset_one.txt}{Type or paste legend here.}
 
-\dataset{dataset_two.txt}{Type or paste legend here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}
+% \dataset{dataset_two.txt}{Type or paste legend here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}
 

### 2020-09-11 tex/sup/supplementary_information.tex
写完补充材料研究区第一部分：分区

@@
 \section*{Methods S1. Definition of study area}
-% 黄河经历了水资源开发利用和制度改革
-The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime (Supplementary Fig.
-1A).
-According to ecological zoning, landscapes types, water resource zoning et al., the Yellow River Basin can be divided into four different regions (supplementary Fig.
-1B), which has been widely recognized (ref.).
-Using this division, there are also some differences of nature between different regions regarding water utilization regimes (supplementary Fig.
-2):
+
+\subsection*{Region divisions of Yellow River Basin}
+
+The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime in China.
+According to the Yellow River Conservancy Commission, an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by characteristic of river.
+However, there is another scheme suggesting that the upstream only refers to river source areas with little human disturbance and high water retention capacity.
+Anyhow, since the socio-economic and natural conditions were considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
+S1).
+Previous studies have also shown that such a division is valid when both social water use and the natural conditions of the basin are considered, as the regions exhibit strong heterogeneity among themselves (see Fig.
+S2):
+
 \begin{itemize}
@@
 
-\subsection*{Introduction of Yellow River Basin}
-\subsection*{Subarea of Yellow River Basin}
-\subsection*{General situation of water use in the YRB}
+In general, there are inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin.
+On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin.
+Thus, as a case study for analysing the evolution of the human-water relationship, it possesses typicality.
+
+\subsection*{Importance of water resource to society within the YRB}
+Water resources make an irreplaceable contribution to the development of society in the watersheds constituted by the four heterogeneous regions mentioned above.
+
+Historic and recent river basin management practices have strong impacts on water utilization.
+
+\subsection*{Changes brought from human activities on the YRB}
+Humans are constantly modifying the water cycle processes in the watersheds as society develops.
 

### 2020-09-14 tex/sup/supplementary_information.tex
改完了补充材料第一节

@@
 
-The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime in China.
+The study area is the Yellow River Basin (YRB, see Fig.
+S1-A), which has experienced the most intense water exploitation and the most dramatic shifts of management regime in China.
 According to the Yellow River Conservancy Commission, an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by characteristic of river.
@@
 Anyhow, since the socio-economic and natural conditions were considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
-S1).
+S1-B).
 Previous studies have also shown that such a division is valid when both social water use and the natural conditions of the basin are considered, as the regions exhibit strong heterogeneity among themselves (see Fig.
-S2):
+S1-C):
 
@@
 
-In general, there are inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin.
+In general, there are inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (see Fig.
+S2).
 On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin.
@@
 \subsection*{Importance of water resource to society within the YRB}
-Water resources make an irreplaceable contribution to the development of society in the watersheds constituted by the four heterogeneous regions mentioned above.
+Water resources make an irreplaceable contribution to the development of society in the YRB.
+Firstly, each aspect of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig.
+S3-A).
+Secondly, their relationships have noticeably changed over the study period.
+In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig.
+S3-B).
 
-Historic and recent river basin management practices have strong impacts on water utilization.
+% 举农业案例作为说明
+%For an example, the agriculture, which occupied over 60\% of water consumptions, whose relationship with regional economic development has weakened, and there have been significant changes in water consumption per unit and total water consumption (see Fig.
+S).
 
@@
 Humans are constantly modifying the water cycle processes in the watersheds as society develops.
+\begin{itemize}
+    \item Firstly, the YRB has been subject to strong intervention by human activities since ancient times, while the last 60 years have seen the most dramatic changes.
+Under human influence, the Yellow River's surface runoff, sediment transport, and human water consumption patterns have all undergone multiple regime shifts in the last 60 years (see Fig.
+S4).
+    \item Secondly, landscapes in the YRB have significantly altered by human activities, which can both change the natural and the social water cycle (see Fig.
+S5).
+For an example, “grain for green” project has produced a significant change of landscapes in the middle region (MR) of YRB.
+With the addition of xxx hectares of forest in an erosion-prone area, water use patterns in the area and surface runoff patterns in the middle and lower reaches have been radically altered.
+    \item Thirdly, a series of management practices have promoted in order to govern the YRB (see Fig.
+S6).
+Since the establishment of the Yellow River Water Conservancy Commission in XX, the agency has continued to reform and expand, eventually forming a basin management agency with unified coordination, scheduling and regulatory functions.
+Since the promulgation of the Water Law in xxx, the Ministry of Water Resources, the Yellow River Conservancy Commission and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws.
+\end{itemize}
+Historic and recent river basin management practices have strong impacts on water utilization.
 

### 2020-09-19 tools/processing.py
完成了补充图2

@@ -10,6 +10,53 @@ import numpy as np
 from matplotlib import pyplot as plt
 import csv
 
+# 所有黄河流域的省份
+PROVINCES = [
+    '青海', '青海省', 'Qinghai',
+    '四川', '四川省', 'Sichuan',
+    '甘肃', '甘肃省', 'Gansu',
+    '宁夏', '宁夏回族自治区', 'Ningxia',
+    '内蒙', '内蒙古', '内蒙古自治区', 'Neimeng',
+    '陕西', '陕西省', 'Shanxi', 
+    '山西', '山西省', 'Shaanxi',
+    '河南', '河南省', 'Henan',
+    '山东', '山东省', 'Shandong'
+    '河北', '河北省', 'Hebei'
+]
+
+
+period_colors = ['#0889A6', '#F1801F', '#006C43']
+region_colors = ["#0077b6", "#e07a5f", "#f2cc8f","#81b29a"]
+index_colors = ['#CFA7D1', '#79D6F0', '#E25A53']
+import matplotlib
+index_colormap = matplotlib.colors.ListedColormap(index_colors, 'indexed')
+total_water_use_color = '#D1495B'
+
+
+# 划分子图
+def add_subplot_by_order(gs=(2, 2), order=1):
+    a, b = gs
+    x = (order - 1) // b  # 第几排
+    y = order % b - 1
+    return x, y
+
+
+# 根据省份判断所在区域
+def get_region_by_province_name(name):
+    """使用省份名称获取该省属于哪个区域（SR, UR, MR or DR）
+    name: 一个中国黄河流域的省份
+    return: 区域（源区上中下游，或返回空值）
+    """
+    if name in PROVINCES[:6]:
+        return 'SR'
+    elif name in PROVINCES[6:16]:
+        return 'UR'
+    elif name in PROVINCES[16:22]:
+        return 'MR'
+    elif name in PROVINCES[22:]:
+        return 'DR'
+    else:
+        return None
 
 
 # 将dbf文件读取入pandas.DataFrame
@@ -41,6 +88,7 @@ def dbf_data_list(folder_path):
     return dbf_files
 
 
+# 使用图片的比例来定位
 def get_position_by_ratio(ax, x_ratio, y_ratio):
      x_min, x_max = ax.get_xlim()
      y_min, y_max = ax.get_ylim()

### 2020-09-21 tex/main/manuscript.tex
更改好了机房电脑的Latex和Python配置
制作新的框架图

@@
 
+\begin{figure}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main_text/framework1.jpg}
+	\caption{
+		A framework for understanding the changing relationship between watershed development and water resources.
+	}
+	\label{fig:framework1}
+\end{figure}
+
 \section*{Results}
@@
 	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
-	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
+	Size of the points denoting average of absolute value of each indicator: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
 	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).

### 2020-09-21 tex/main/manuscript.tex
摘要更新

@@
 \begin{abstract}
-	In the context of regime shifts, understanding the complex relationship between human societies and water resources utilization provides underlying supports to development in a coordinated way at a basin scale.
-However, there is still lacking of effective method to detect regime shifts of water utilization, with much fewer attempts to develop theoretical models to explain their transition phases as well.
+	From agrarian to industrial societies, humans have harnessed ecosystems over rivers basins around the world, while using water resources as blood that sustains social developments. 
+	However, there is still lacking of effective method to detect regime shifts of water utilization linking to social changes, with much fewer attempts to develop theoretical models to explain their transition phases as well.
 	Here, by integrating three different dimensions of water utilization (stress, tendentiousness and pattern), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to detect regime shifts.

### 2020-09-21 tex/sup/supplementary_information.tex
数据介绍大纲

@@
 \section*{Methods S2. Detailed information on dataset and processing}
-Since the Yellow River Basin consists of ten provincial areas, the above division can also maintain broad consistency with administrative divisions.
-Add a materials' subsection if you need to.
+
+Multiple datasets were used in this study. 
+\subsection*{Statistical datasets}
+The 2nd National Water Resources Assessment Program.
+
+\subsection*{Hydrological datasets}
+
+\subsection*{Political datasets}
+
+\section{Methods S4.  Detailed information on data processing}
 

### 2020-09-22 tex/sup/supplementary_information.tex
编译测试

@@
 
-Multiple datasets were used in this study. 
+Multiple types of dataset were used in this study. 
 \subsection*{Statistical datasets}
-The 2nd National Water Resources Assessment Program.
+For statistics, we used GDP data, statistical yearbook data, and data extracted from the 2nd National Water Resources Assessment Program
+\cite{zhouDecelerationChinaHuman2020}.
 

### 2020-09-22 tex/sup/supplementary_information.tex
数据集介绍1-2段

--- 2020-09-21 tex/sup/supplementary_information.tex
@@
 
-% \section*{Supplementary Information Methods}
+% tag 研究区定义
 \section*{Methods S1. Definition of study area}
@@
 S1-A), which has experienced the most intense water exploitation and the most dramatic shifts of management regime in China.
-According to the Yellow River Conservancy Commission, an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by characteristic of river.
+According to the Yellow River Conservancy Commission (YRCC), an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by characteristic of river.
 However, there is another scheme suggesting that the upstream only refers to river source areas with little human disturbance and high water retention capacity.
@@
 Since the establishment of the Yellow River Water Conservancy Commission in XX, the agency has continued to reform and expand, eventually forming a basin management agency with unified coordination, scheduling and regulatory functions.
-Since the promulgation of the Water Law in xxx, the Ministry of Water Resources, the Yellow River Conservancy Commission and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws.
+Since the promulgation of the Water Law in xxx, the Ministry of Water Resources, the YRCC and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws.
 \end{itemize}
@@
 
-\section*{Methods S2. Detailed information on dataset and processing}
+% tag 数据集介绍
+\section*{Methods S2. Detailed information on datasets}
 
-Multiple datasets were used in this study. 
+Multiple types of dataset were used in this study (see Table S1). 
 \subsection*{Statistical datasets}
-The 2nd National Water Resources Assessment Program.
+% 使用了GDP数据，年鉴数据，还有从第二次水资源调查提取的数据
+For statistics, we used GDP data, water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhouDecelerationChinaHuman2020} and statistical yearbook data of YRB.
+GDP data from the China Macro data in the Wind database, which firstly aggregated from annual reports of the provinces. 
+Water resources uses dataset was published by Zhou et al.
+\cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in perfects level.
+This dataset was mainly extracted by 2nd National Water Resources Assessment Program launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details).
+Since then, the statistics from the survey using the same criteria have been supplemented and harmonized to the 2013 administrative divisions.
+%TODO xx 
+The data covers a total of subcategories of water use under four broad categories: agriculture, industry, urban and rural, but does not distinguish between surface water and groundwater.
+There is uncertainty at the county scale for each disaggregated water use sector, but because the data are corrected for statistical information using the water balance method, the data are adequate for the regional scale and the four broad water use categories used in this study.
+Finally, in order to make a simple distinction between the proportion of surface water and groundwater extraction where needed, we use basin-scale water resources annual reporting data.
+Yearbook data of YRB documenting surface water resources and groundwater resource extraction in each watershed and province.
 
 \subsection*{Hydrological datasets}
+For hydrological datasets, reservoirs data and a measured runoff data were used in this study.
+The reservoir dataset were collected by Wang et al.
+\cite{wangYellowRiverWater2019}, which introduced includes the major new reservoirs built in the Yellow River Basin since 1949.
+Of these, we consider the reservoirs marked as pivot projects by the YRCC to be more important, as they are directly involved in water resources management in the basin (\url{http://www.yrcc.gov.cn/hhyl/sngc/}).
+Annual runoff data derived from hydrological station measurements.
 
@@
 
-\section{Methods S4.  Detailed information on data processing}
+% tag 数据处理
+\section*{Methods S3. Harmonization of datasets}
 
-\section*{Methods S3. Water Utility Regime Index}
-Add a methods subsection if you need to.
+% 指数介绍
+\section*{Methods S4. Water Utility Regime Index}
 
@@
 
+% tag 附录图
+
 %%% Each figure should be on its own page
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/supplementary_information/YRB.jpg}
+    \includegraphics[width=\textwidth]{../../figures/supplementary_information/s1_study_area.jpg}
     \caption{Yellow River Basin}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
+    \includegraphics[width=\textwidth]{../../figures/supplementary_information/region_differences.jpg}
     \caption{Different regions}
@@
 % % 表格
-% \begin{tabular}{lrrr}
+% \begin{tabular}{lrrrr}
 % Species & CBS & CV & G3 \\
@@
 % \end{table}
+
+%% 表格
+\begin{table}\centering
+    \caption{Used datasets and their sources.}
+
+    % 表格
+    \begin{tabular}{lrrrr}
+    Dataset & Type & Spatial scale & Time limit & Source \\
+    \midrule
+    1. Water use & Statistical & Perfects & 1965-2013 & 2nd National Water Resources Assessment Program \\
+    2. GDP & Statistical & Province & 1949-2019 & Wind database \\
+    3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
+    \bottomrule
+    \end{tabular}
+\end{table}
 

### 2020-09-22 tex/sup/supplementary_information.tex
补充参考文献
数据集介绍大纲

@@
 Since then, the statistics from the survey using the same criteria have been supplemented and harmonized to the 2013 administrative divisions.
-%TODO xx 
+%TODO xx 这里把每个数据的子类介绍清楚
 The data covers a total of subcategories of water use under four broad categories: agriculture, industry, urban and rural, but does not distinguish between surface water and groundwater.
@@
 \subsection*{Political datasets}
+%对于政策数据集，我们选取了《黄河流域综合规划》中流域级部门（如黄河水利委员会）级以上（如国家部委）颁布施行的与黄河流域有关的法律政策。此外，我们还从《黄河水利委员会组织沿革》一书中获取的黄河水利委员会作为黄河流域级管理单位的组织沿革情况，以反映流域级管理举措的实施情况。
+For the policy data set, we select the laws and policies related to the Yellow River basin promulgated and implemented by departments at and above the river Basin level (such as Yellow River Conservancy Commission) in the Comprehensive Planning for the Yellow River Basin (such as national ministries and commissions) \cite{yellowriverconservancycommissionYellowRiverBasin2013}.
+In addition, we also obtain the organizational evolution of the Yellow River Water Conservancy Commission as a watershed management unit from the book Organizational Evolution of the Yellow River Water Conservancy Commission to reflect the implementation of watershed management measures \cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
 
@@
     3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
+    % TODO 这里应该把所有表格补充完整
     \bottomrule
     \end{tabular}
+\end{table}
+
+%% 表格
+\begin{table}\centering
+    \caption{Policies and regulations above YRB level.}
+
+    % 表格
+    \begin{tabular}{lrr}
+    Name & Year & Agency \\
+    \midrule
+    1. Water Law of PRC & 1988 & NPC $^a$ \\
+    2. Water Law of PRC -revised 1 & 2009 & NPC \\
+    3. Water Law of PRC -revised 2 & 2016 & NPC \\
+    % TODO 这里应该把所有表格补充完整
+    \bottomrule
+    \end{tabular}
+
+    \footnotesize{$^a$ National People's Congress of PRC}
 \end{table}

### 2020-09-23 tex/sup/supplementary_information.tex
写完S3数据统一

@@
 % tag 研究区定义
+\newpage
 \section*{Methods S1. Definition of study area}
@@
 % tag 数据集介绍
+\newpage
 \section*{Methods S2. Detailed information on datasets}
@@
 % tag 数据处理
+\newpage
 \section*{Methods S3. Harmonization of datasets}
+% 由于我们的数据集来源广泛，且具有不同的空间尺度，我们需要在区域尺度（SR，UR，MR和DR）上对数据进行调和，根据数据的空间尺度有不同的处理方式。
+Due to the wide sources of our data set and the different spatial scales, we need to reconcile the data on the regional scale (SR, UR, MR and DR), and have different processing methods according to the spatial scale of the data.
+\begin{itemize}
+    \item 1. Watersheds:
+    % 由于流域的分区由水文分区决定，所以水文年报数据和实测径流量数据都能直接根据其对应的水文站直接划分。
+        Due to the fact that the subdivision of a basin is determined by hydrological subdivision, hydrological annual data and measured runoff data can be directly divided according to their corresponding hydrological stations.
+    \item 2. Perfects:
+    % 在市县尺度下，我们分别计算了市县在不同流域分区中所占的面积，选取其中最大的区域，如果该面积占该县面积的95%以上，则认为该市属于该区域，即：
+        At the scale of cities and counties, we respectively calculate the area occupied by cities and counties in different watershed districts, and select the largest region.
+If this area accounts for more than 95\% of the area of the county, the city is considered to belong to this region, that is:
+        $$ S_{ij} = MAX(S_ij / S_i)$$
+        where $i$ refers a certain perfect and $j$ refers a region within YRB, i.e.
+SR, UR, MR, or DR.
+$S_i$ refers the area of perfect $i$, and $S_{ij}$ refers intersecting area between perfect $i$ and region $j$.
+        We define perfect $i$ belongs to region $j$ if their intersecting area over 95\% of $S_i$, i.e.:
+        $$ MAX(S_{ij}) > 0.95 * S_i $$
+    \item 3. Province:
+    % 在省域尺度的数据（即不同行业的GDP数据）更多用以定性描述，且不与县域尺度数据进行横向比例，因此数据的精度不再重要。我们采用了粗略的处理。即，根据不同区域包含的主要省份，判断该省的数据被融合进哪个区域。参考传统划分惯例，我们进行的划分是：
+    Data at the provincial scale (i.e., GDP data of different industries) are more used for qualitative description, and do not carry out horizontal proportion with data at the county scale, so the accuracy of the data is no longer important.
+We have adopted a rough treatment.
+That is, according to the major provinces contained in different regions, determine which region the data of that province is merged into.
+Referring to the traditional division practice, we made the following division:
+    \begin{itemize}
+        \item SR: Qinghai Gansu and Sichuan,
+        \item UR: Ningxia and Neimeng,
+        \item MR: Shanxi and Shaanxi,
+        \item DR: Shandong, Hebei and Henan
+    \end{itemize}
+\end{itemize}
 
+% 最后，当我们处理位置点数据（如水库修建位置数据时），根据其所在位置判断其所属省份，再按照省尺度的区域归类方式进行处理。经过上述处理，所有的数据都能很好的在区域尺度得到协调。
+Finally, when we process the location data (such as the location data of reservoir construction), we judge the province it belongs to according to its location, and then process it according to the regional classification method on the provincial scale.
+After the above processing, all the data can be well coordinated at the regional scale.
+
+\newpage
 % 指数介绍
@@
 
-\section{Methods S4. Water Management Practices}
+\section{Methods S5. Water Management Practices}
 

### 2020-09-23 tex/main/manuscript.tex
补充参考文献
Methods S4 index

@@
 Despite pervasive and important, there is still lacking of effective method to define the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transition phases as well.
+s
 
@@
 	\subsubsection*{Sub-indicator of Patterns}
-	To description of patterns between regions or sections, we designed an indicator by imitation of information entropy.
+	To description of patterns between regions or sections, we designed an indicator by imitation of information entropy (Allocational Entropy Metric, see supplementary document: Methods S4).
 Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy).

### 2020-09-23 tex/sup/supplementary_information.tex
Methods S4 index

@@
 \section*{Methods S4. Water Utility Regime Index}
+% 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
+The steady-state index of water resources utilization considers the three most important dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of "how much water", "how to use" and "for whom, for where" respectively.
+%? TODO 这里需要增加参考文献，证明这三个维度是最重要的。
+% 无论如何，为了让这些维度能够被量化，我们寻找或发明了共计三个度量指标来对应指示其变化趋势：
+In order for these dimensions to be quantified, we found or invented a total of three metrics corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocational Entropy Metric.
 
 \subsection*{Stress: SFV-index}
-	% 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
+	%* 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
+	There is how much water can be used in a certain basin?
+How much stresses has societies put on the water resources of the basin?
 Various metrics, therefore, proposed for water stress (e.g.
 water scarcity, water stresses index, scarcity-flexibility-variability index), where the dimensions of human impact are increasingly valued.
-	% 其中SFV指数比较有用
-    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid indicator of temporal changes in water stresses.
+	%* 其中SFV指数比较有用
+    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses.
+    % TODO 这里也要插入 Qin et al., 的参考文献
+    %* 该指标从人类开发利用水资源的角度，考虑了影响人类感知水资源压力的三个方面：水资源的总量、水资源变异性、人类利用水资源的灵活性。
 
 \subsection*{Tendentiousness: Non-provisioning share}
-	% xxx等人通过考虑消费品中的水消耗提出了虚拟水理论
-	% 但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。
-	% 如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类在“消耗水”向“利用水”和的倾斜。
+    %* 从消耗水 到 利用水
+    % xxx等人通过考虑消费品中的水消耗提出了虚拟水理论，发现水资源作为粮食与消耗产品的供给是水资源的主要用途，且能够随着贸易发生流动。但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类社会发生着从“消耗水”向“利用水”的倾斜。
+    How to use water resources?
+XXX et al.
+put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption products is the main use of water resources, and can flow with trade.
+However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related products and services.
+Today, the world's non-product form of water supply to human beings has reached XX\%, including XXXXXX and other ways, the human society is occurring from "consumption of water" to "use of water" tilt.
+    % TODO 这里要补充一些材料
+    % *这里我们使用非用于供给性的水资源量所占的比例作为指标，即:
+    Here, we use Non-Provisioning Shares (NPS) of used water resources as an metric to indicate tendentiousness of water utility:
+    $$ NPS_{ij} = \frac{WU_{indirect, i, j}}{WU_{direct, i, j} + WU_{undirect, i, j}} $$
+    where $i$ refers a certain year and $j$ refers a certain region.
+Thus, $WU_{i,j}$ means the water use in $i$ year and region $j$, where $direct$ part and $undirect$ part indicate provisioning sectors and non-provisioning sectors respectively.
+    %* 直接用水和非直接用水
+    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 Tendentiousness 的变化。
+    % TODO 这里要补充一些材料 Li 2020，虚拟水贸易，水粮食能源的联结
+    In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as supply water.
+Correspondingly, non-supply water is often industrial water, mainly energy water.
+Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which supply water is often the key to support the production of agricultural products, while non-supply water is more involved in industrial and other social processes.
+For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade.
+But if industrial consumption is taken into account, China is exporting virtual water.
+However, as a river basin with high degree of water resource scarcity, the tradeoff between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of tendentientitreating with water.
+
+\subsection*{Pattern: Allocational Entropy Metric}
+    %* 哪里利用水资源？  
+    Where to use water resources? 
+    % * 设计了一个熵指标
+    % 水资源的分配一直是难题，需要在上下游之间、不同用水部门之间进行权衡，但目前还缺少相关的指标进行量化。这里我们设计了一个“分配熵指标”，能够把水资源分配的格局（倾向于平均分配还是更加侧重某一区域）简单直接的表达出来。我们模仿了物理学中信息熵的思想，当信息（这里是水资源）的分配越趋于平均时，其熵在增加，当分配更倾向于某一区域时，该区域获得发展的确定性在增加，导致总体的熵减少。
+    %! 这里的表述需要好好思考一下
+    The allocation of water resources has always been a difficult problem, requiring tradeoffs between upstream and downstream and between different water sectors, but there is still a lack of relevant indicators to quantify.
+Here we have designed a "distribution entropy index", which can simply and directly express the pattern of water allocation (which tends to be more evenly distributed or more focused on a certain region).
+We imitate the idea of information entropy in physics.
+When the distribution of information (here is water resource) is more equal, its entropy increases; when the distribution is more inclined to a certain region, the certainty of development in that region increases, resulting in the overall entropy decrease.
+    %* 这里需不需要一张图表示？
+    % 该指标将不同区域（SR, UR, MR, DR）和不同部门（农业、工业、服务业、人居）消耗的水资源 Water Use (WU) 视做观察的结果，计算完全平均分配水资源时候的水资源分配熵作为最大值，再计算实际水资源分配最大熵与实际熵的比值，以表示水资源分配的格局多大程度上偏离平均分配。
+    The indicators will be different areas (SR, UR, MR, DR) and different departments (agriculture, industry, service industry, human settlements) of Water consumption of Water Use (WU) as observations, calculation completely when the average allocation of Water resources allocation of Water resources as the maximum entropy, and the actual Water distribution of the ratio of the maximum entropy and the actual entropy, to show the pattern of Water resources allocation how much deviation from the average allocation, i.e.:
+
+    $$ ratio = \frac{Entropy}{Entropy_{max}} $$
+	where $Entropy$ and $Entropy_{max}$ are entropy and maximum entropy of water distributions, respectively. They can be calculated by:
+	$$ Entropy = \sum_{i=1}^n \sum_{j=1}^m -log(p_{ij}) * p_{ij} $$
+	$$ Entropy_{max} = n * \sum_{j=1}^m -\frac{p_j}{n} * log(\frac{p_j}{n}) $$ 
+    where $p_j$ and $p_ij$ are proportions of water use in sector $j$ and region $i$:
+	$$ p_j = \frac{\sum_{i=1}^n WU_j}{\sum_{i=1}^n WU} $$
+	$$ p_{ij} = \frac{WU_{ij}} {\sum_{i=1}^n \sum_{j=1}^m WU_{ij}} $$
+	where $n$ is the total number of regions ($n=4$ here, see supplementary Methods. S1) and $m$ is the total number of sectors ($m=4$ here, see supplementary Methods. S2).
+
+    % 上述指标同时考虑了地区之间的分配和行业之间的分配，但随着流域发展，两者的趋势是有差异的。对于位于同一个国家内的流域，区域之间通过开采水资源获取发展的机会是相等的，实际的水资源使用更多取决于自身的经济实力，因此考虑不受实际经济制约的理想情况，四个区域之间的水资源应该被公平（平均）分配的（熵增）。但同时，由于地理差异和部门分工的广泛存在，不同的区域有其比较优势，是制约其理论上将水资源分配于哪个用水行业的关键因素，因此其特定区域的部门之间水资源分配在理想情况下将总体呈现差异增加（熵减）的趋势。同时，部门分工也将随着比较优势出现，让不同区域都相较于流域的平均水平有其各自的优势部门（相较于平均熵）。
+    % TODO 这里一定要想一下，怎么能给人讲的更明白
+    The above indicators take into account the distribution between regions and between industries, but with the development of the basin, the trend of the two is different.
+For river basin is located in the same country, from the exploitation of water resources for development between regional opportunities are equal, the actual use of water resources depends more on their own economic strength, so consider don't ideal is conditioned by the actual economic situation, between the four areas of water resources should be fair (on average) distribution (entropy).
+But at the same time, due to the wide existence of geographical differences and division of labor, different regions have their comparative advantages, which is the key factor restricting which water resources are allocated to in the water industry theoretically.
+Therefore, the distribution of water resources among departments in a specific region will show an overall trend of increasing differences (entropy reduction) in an ideal situation.
+At the same time, the division of labor will emerge along with the comparative advantage, so that different regions have their own advantageous departments (compared with the average level of the river basin).
+
+% 最后，我们将三个维度各自的指标在标准化后等权重考虑，组成了 Water Utility Regime Index。
+Finally, we consider the indexes of the three dimensions in the same weight after standardization to form the Water Utility Regime Index.
 

### 2020-09-24 tex/sup/supplementary_information.tex
delete Methods S5
a simple version of figure S8
make sure sup.tex run normally

@@
 
-\section{Methods S5. Water Management Practices}
-
 % tag 附录图
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/supplementary_information/s1_study_area.jpg}
+    \includegraphics[width=\textwidth]{../../figures/sup/s1_study_area.jpg}
     \caption{Yellow River Basin}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/supplementary_information/region_differences.jpg}
+    \includegraphics[width=\textwidth]{../../figures/sup/region_differences.jpg}
     \caption{Different regions}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_measured_runoff.pdf}
+    \includegraphics[width=\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
     \caption{Natural measured runoff of Yellow River within different periods.}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/inflexible_wu.pdf}
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
     \caption{Flexibility}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/reservoirs.pdf}
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/reservoirs.pdf}
     \caption{Reservoirs and accumulated storage}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/placeholder_l.jpg}
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/saving_water.jpg}
     \caption{technological solutions and water conservation practices}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/supplementary_information/sf_wu_sections_stackplot.jpg}
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
     \caption{Proportions of water use between the different sectors}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/outages.jpg}
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/outages.jpg}
     \caption{Severe runoff outages and groundwater depletion}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/managements.pdf}
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/managements.pdf}
     \caption{Number of management practices in different periods, including policy and reservoirs.}

### 2020-09-24 scripts/formula_script.R
move out synth control methods related files

@@ -1,40 +1,0 @@
-
-
-# Load package
-library(Synth)
-
-# Load Data 
-myd <- read.csv("../data/perfectures/basins/all_basins.csv")
-myd$Basin <- as.character(myd$Basin)
-
-## pick v by cross-validation
-# data setup for training model
-dataprep.out <-
-  dataprep(
-           foo = myd,
-           predictors    = c("Irrigated.area..Total", "Irrigated.area..Rice", "Irrigated.area..Wheat", "Irrigated.area..Maize", "Irrigated.area..Vegetables.and.fruits", "Irrigated.area..Others", "Industrial.gross.value.added..GVA...Total", "Industrial.gross.value.added..GVA...Textile", "Industrial.gross.value.added..GVA...Papermaking", "Industrial.gross.value.added..GVA...Petrochemicals", "Industrial.gross.value.added..GVA...Metallurgy", "Industrial.gross.value.added..GVA...Mining", "Industrial.gross.value.added..GVA...Food", "Industrial.gross.value.added..GVA...Cements", "Industrial.gross.value.added..GVA...Machinery", "Industrial.gross.value.added..GVA...Electronics", "Industrial.gross.value.added..GVA...Thermal.electrivity", "Industrial.gross.value.added..GVA...Others", "Urban.population", "Service.GVA", "Rural.population", "Livestock.population"),
-           dependent     = "Total.water.use",
-           unit.variable = "Index",
-           time.variable = "Year",
-           treatment.identifier = 3,
-           controls.identifier = c(0, 1, 2, 4, 5, 6, 7, 8),
-           time.predictors.prior = 1978:1994,
-           time.optimize.ssr = 1995:2013,
-           unit.names.variable = "Basin",
-           time.plot = 1978:2013
-         )
-
-# fit training model
-synth.out <- 
-  synth(
-        data.prep.obj=dataprep.out
-        )
-
-
-actual_data <- dataprep.out$Y1plot
-synth_data <- dataprep.out$Y0plot %*% synth.out$solution.w 
-
-out_list <- list(
-  y1 = actual_data,
-  y0 = synth_data
-)

### 2020-09-24 tools/gdp_processing.py
rename and sort notebooks files

@@ -1,0 +1,98 @@
+#!/usr/bin/env python 3.83
+# -*-coding:utf-8 -*-
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+import numpy as np
+import pandas as pd
+
+
+# 清洗列名
+def from_col_name_extract_province_and_industry(name):
+    elements = name.split(':')  # 分割列名
+    province = elements[0].strip()  # 地名
+    industry = elements[-1].strip()  # 产业
+    return province, industry
+
+
+
+# 根据年份，提取数据
+def extract_data_by_yr(data, start_yr, end_yr):
+    # 当需要提取的年份在起点年份之前，采用时间序列中最早的一年
+    if start_yr not in data.index:
+        start_yr = data.index[0]
+    # 同理，如果终点年份超出索引，采用最晚的一年
+    if end_yr not in data.index:
+        end_yr = data.index[-1]
+
+    # 当两者相等时，无标准差
+    if start_yr == end_yr:
+        return data.loc[end_yr], False
+    else:
+        use_data = data.loc[start_yr: end_yr]
+        return np.mean(use_data), np.std(use_data)
+
+
+
+def plot_bar_by_category(ax, data, categories, colors, position, start_yr, end_yr, **kargs):
+    """ 绘制一个分类柱状图，将不同类别画在同一个位置上
+    ax: 绘图区域
+    data: 数据，DataFrame，index 是时间（年份），列与 categories 相关
+    categories: 分类列表，其中的类应该是 data 中出现的列名
+    colors: 每个类使用的颜色
+    position: 这个分类柱状图的柱子位置
+    start_yr: 截取数据的起始年
+    end_yr: 截取数据的末位年
+    **kargs: 与绘图相关的参数
+    ---------------------------------------------
+    return: 返回图例
+    """
+    bottom = 0  # 初始的柱状图底
+    legends = []  # 图例
+    for i, category in enumerate(categories):  # 对每个分类
+        use_data = data[category]  # 数据是其中的类
+        height, std = extract_data_by_yr(use_data, start_yr, end_yr)
+        if std:  # 如果有标准差，就绘制误差线
+            bar = ax.bar(
+                x=position,
+                bottom=bottom,
+                height=height, 
+                yerr=std,
+                color=colors[i],
+                **kargs
+            )
+        else:
+            bar = ax.bar(
[…]

### 2020-09-24 tools/get_water_resource.py

@@ -1,0 +1,88 @@
+#!/usr/bin/env python 3.83
+# -*-coding:utf-8 -*-
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+from values import REGIONS
+import pandas as pd
+
+# 加载实测径流量
+def get_measured_runoff(region):
+    use_cols = {
+        '年份': 'Year',
+        '唐乃亥': 'SR',  # 唐乃亥控制源区
+        '头道拐': 'UR',  # 头道拐控制上游
+        '花园口': 'MR',  # 花园口控制中游
+        '利津': 'DR'     # 利津控制下游
+    }
+    measured_runoff = pd.read_csv(r'../data/hydrology/1956-2016_runoff.csv')
+    measured_runoff = measured_runoff.loc[:, use_cols.keys()]
+    measured_runoff.rename(use_cols, axis=1, inplace=True)
+    measured_runoff.set_index('Year', inplace=True)
+    return measured_runoff[region]
+
+
+# 获取天然径流量的差值
+def get_runoff_difference(region):
+    index = REGIONS.index(region)
+    if index == 0:
+        runoff_in = 0
+    else:
+        runoff_in = get_measured_runoff(REGIONS[index-1])
+    runoff_out = get_measured_runoff(region)
+    return runoff_out - runoff_in
+
+
+# 加载消耗量
+def get_consumptions(region):
+    """计算从此区域及其上游区域，合计的【水资源】消耗量，单位是立方千米"""
+    city_yr = pd.read_csv(r'../data/perfectures/yr/perfectures_in_YR_with_threshold_0.05.csv')
+    water_use = city_yr[['Year', 'Region', 'Total water use']]
+    consumption = water_use.groupby(['Region', 'Year']).sum().loc[region]['Total water use']
+    flag = 0
+    index = REGIONS.index(region)
+    while flag < index:
+        consumption += water_use.groupby(['Region', 'Year']).sum().loc[REGIONS[flag]]['Total water use']
+        flag += 1
+    return consumption * 10  # 单位由 10^8 变成 10^9
+
+
+# 计算每个区域的地表/地下水修正系数
+def get_surface_groundwater_coefficient(region):
+    watersheds = pd.read_csv(r"../data/watershed_merged.csv")
+
[…]

### 2020-09-24 tools/processing.py

@@ -10,32 +10,10 @@ import numpy as np
 from matplotlib import pyplot as plt
 import csv
 
-# 所有黄河流域的省份
-PROVINCES = [
-    '青海', '青海省', 'Qinghai',
-    '四川', '四川省', 'Sichuan',
-    '甘肃', '甘肃省', 'Gansu',
-    '宁夏', '宁夏回族自治区', 'Ningxia',
-    '内蒙', '内蒙古', '内蒙古自治区', 'Neimeng',
-    '陕西', '陕西省', 'Shanxi', 
-    '山西', '山西省', 'Shaanxi',
-    '河南', '河南省', 'Henan',
-    '山东', '山东省', 'Shandong'
-    '河北', '河北省', 'Hebei'
-]
-
-
-period_colors = ['#0889A6', '#F1801F', '#006C43']
-region_colors = ["#0077b6", "#e07a5f", "#f2cc8f","#81b29a"]
-index_colors = ['#CFA7D1', '#79D6F0', '#E25A53']
-import matplotlib
-index_colormap = matplotlib.colors.ListedColormap(index_colors, 'indexed')
-total_water_use_color = '#D1495B'
-
 
 # 划分子图
 def add_subplot_by_order(gs=(2, 2), order=1):
-    a, b = gs
+    b = gs[1]
     x = (order - 1) // b  # 第几排
     y = order % b - 1
     return x, y
@@ -43,6 +21,7 @@ def add_subplot_by_order(gs=(2, 2), order=1):
 
 # 根据省份判断所在区域
 def get_region_by_province_name(name):
+    from values import PROVINCES
     """使用省份名称获取该省属于哪个区域（SR, UR, MR or DR）
     name: 一个中国黄河流域的省份
     return: 区域（源区上中下游，或返回空值）

### 2020-09-24 tools/values.py

@@ -1,0 +1,38 @@
+#!/usr/bin/env python 3.83
+# -*-coding:utf-8 -*-
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+
+# 所有黄河流域的省份
+PROVINCES = [
+    '青海', '青海省', 'Qinghai',
+    '四川', '四川省', 'Sichuan',
+    '甘肃', '甘肃省', 'Gansu',
+    '宁夏', '宁夏回族自治区', 'Ningxia',
+    '内蒙', '内蒙古', '内蒙古自治区', 'Neimeng',
+    '陕西', '陕西省', 'Shanxi', 
+    '山西', '山西省', 'Shaanxi',
+    '河南', '河南省', 'Henan',
+    '山东', '山东省', 'Shandong'
+    '河北', '河北省', 'Hebei'
+]
+
+REGIONS = ['SR', 'UR', 'MR', 'DR']  # 设置区域
+
+
+# 所有GDP相关常量
+INDUSTRIES = ['第一', '第二', '第三']  # 三个产业
+INDUSTRIES_eng = ['Agriculture', 'Industry', 'Services']  # 三个产业对应的英文
+
+
+period_colors = ['#0889A6', '#F1801F', '#006C43']
+region_colors = ["#0077b6", "#e07a5f", "#f2cc8f","#81b29a"]
+index_colors = ['#CFA7D1', '#79D6F0', '#E25A53']
+
+
+import matplotlib
+index_colormap = matplotlib.colors.ListedColormap(index_colors, 'indexed')
+total_water_use_color = '#D1495B'

### 2020-09-24 tools/gdp_processing.py
make sure notebooks works well

@@ -7,7 +7,11 @@
 
 import numpy as np
 import pandas as pd
+from matplotlib import pyplot as plt
 
+REGIONS = ['SR', 'UR', 'MR', 'DR']
+INDUSTRIES = ['第一', '第二', '第三']  # 三个产业
+INDUSTRIES_eng = ['Agriculture', 'Industry', 'Services']  # 三个产业对应的英文
 
 # 清洗列名
 def from_col_name_extract_province_and_industry(name):
@@ -94,5 +98,67 @@ def extract_gdp_by_industry(data, industry):
     return df.sum(axis=1)
 
 
+# 加载经济数据
+def clean_gdp_data():
+
+    gdp = (pd.read_excel(r'../data/GDP.xlsx')  # 读取数据
+            .drop(0)  # 删除单位行
+            .astype(float)  # 转为浮点
+            .rename({'指标名称': 'Year'}, axis=1)  # 将年份列改名
+            .astype({'Year': int})  # 将年份从浮点改为整形
+            .set_index('Year')  # 并设置为索引
+            .replace(0., np.nan)  # 空值是没数据，不可能为 0
+            .drop(list(np.arange(1949, 1965)), axis=0)  # 删除不考虑的时间范围
+            )
+
+    region_dict = {region: pd.DataFrame() for region in REGIONS}  # 用来储存每个区域的GDP数据
+    for col in gdp:
+        province = from_col_name_extract_province_and_industry(col)[0]  # 清洗列名
+        region = get_region_by_province_name(province)  # 属于哪个区域
+        if region: region_dict[region][col] = gdp[col]  # 如果是黄河流域的省份，存进对应的字典
+        else:  gdp.drop(col, axis=1, inplace=True)  # 不是黄河流域的省份，就丢掉
+
+    return region_dict
+
+
+
+# GDP 制图
+def plot_gdp(ax, colors, start_yr, end_yr, **kargs):
+    region_dict = clean_gdp_data()
+    # 对每个区域进行处理
+    for i, region in enumerate(REGIONS):
+        use_data = region_dict[region]  # 某个区域的数据
+        mean = []  # 用来储存该区域的 一、二、三 产业的总平均 gdp
+        # std = []  # 用来储存该区域的 一、二、三 产业的gdp方差
+
+        gdp_region_data = {}
+        # 对每个产业进行处理
+        for industry in INDUSTRIES:
+            # 该区域、该产业的gdp序列，以产业为键存入字典，以供函数调用
[…]

### 2020-09-24 tools/processing.py

@@ -10,6 +10,19 @@ import numpy as np
 from matplotlib import pyplot as plt
 import csv
 
+PROVINCES = [
+    '青海', '青海省', 'Qinghai',
+    '四川', '四川省', 'Sichuan',
+    '甘肃', '甘肃省', 'Gansu',
+    '宁夏', '宁夏回族自治区', 'Ningxia',
+    '内蒙', '内蒙古', '内蒙古自治区', 'Neimeng',
+    '陕西', '陕西省', 'Shanxi', 
+    '山西', '山西省', 'Shaanxi',
+    '河南', '河南省', 'Henan',
+    '山东', '山东省', 'Shandong'
+    '河北', '河北省', 'Hebei'
+]
+
 
 # 划分子图
 def add_subplot_by_order(gs=(2, 2), order=1):
@@ -21,7 +34,6 @@ def add_subplot_by_order(gs=(2, 2), order=1):
 
 # 根据省份判断所在区域
 def get_region_by_province_name(name):
-    from values import PROVINCES
     """使用省份名称获取该省属于哪个区域（SR, UR, MR or DR）
     name: 一个中国黄河流域的省份
     return: 区域（源区上中下游，或返回空值）

### 2020-09-24 script/region_differences.py
a error version of appendix

@@ -5,13 +5,15 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
-import numpy as np
+
 import pandas as pd
+import numpy as np
 from matplotlib import pyplot as plt
 
-REGIONS = ['SR', 'UR', 'MR', 'DR']
-INDUSTRIES = ['第一', '第二', '第三']  # 三个产业
-INDUSTRIES_eng = ['Agriculture', 'Industry', 'Services']  # 三个产业对应的英文
+import sys
+sys.path.append(r"..")
+from tools.values import REGIONS, PROVINCE, INDUSTRIES, INDUSTRIES_eng
+from tools.processing import get_region_by_province_name
 
 # 清洗列名
 def from_col_name_extract_province_and_industry(name):
@@ -156,9 +158,124 @@ def plot_gdp(ax, colors, start_yr, end_yr, **kargs):
     return mean
 
 
-if __name__ == "__main__":
-    fig, ax = plt.subplots()
-    start_yr, end_yr = 1980, 2000
-    gdp_colors = index_colors
-    plot_gdp(ax, gdp_colors, start_yr, end_yr)
-    pass
+
+# 加载实测径流量
+def get_measured_runoff(region):
+    use_cols = {
+        '年份': 'Year',
+        '唐乃亥': 'SR',  # 唐乃亥控制源区
+        '头道拐': 'UR',  # 头道拐控制上游
+        '花园口': 'MR',  # 花园口控制中游
+        '利津': 'DR'     # 利津控制下游
+    }
+    measured_runoff = pd.read_csv(r'../data/hydrology/1956-2016_runoff.csv')
+    measured_runoff = measured_runoff.loc[:, use_cols.keys()]
+    measured_runoff.rename(use_cols, axis=1, inplace=True)
+    measured_runoff.set_index('Year', inplace=True)
+    return measured_runoff[region]
+
+
+# 获取天然径流量的差值
+def get_runoff_difference(region):
+    index = REGIONS.index(region)
+    if index == 0:
+        runoff_in = 0
+    else:
+        runoff_in = get_measured_runoff(REGIONS[index-1])
+    runoff_out = get_measured_runoff(region)
+    return runoff_out - runoff_in
+
+
+# 加载消耗量
+def get_consumptions(region):
+    """计算从此区域及其上游区域，合计的【水资源】消耗量，单位是立方千米"""
[…]

### 2020-09-24 tools/get_water_resource.py

@@ -1,88 +1,0 @@
-#!/usr/bin/env python 3.83
-# -*-coding:utf-8 -*-
-# @Author  : Shuang Song
-# @Contact   : SongshGeo@gmail.com
-# GitHub   : https://github.com/SongshGeo
-# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
-
-from values import REGIONS
-import pandas as pd
-
-# 加载实测径流量
-def get_measured_runoff(region):
-    use_cols = {
-        '年份': 'Year',
-        '唐乃亥': 'SR',  # 唐乃亥控制源区
-        '头道拐': 'UR',  # 头道拐控制上游
-        '花园口': 'MR',  # 花园口控制中游
-        '利津': 'DR'     # 利津控制下游
-    }
-    measured_runoff = pd.read_csv(r'../data/hydrology/1956-2016_runoff.csv')
-    measured_runoff = measured_runoff.loc[:, use_cols.keys()]
-    measured_runoff.rename(use_cols, axis=1, inplace=True)
-    measured_runoff.set_index('Year', inplace=True)
-    return measured_runoff[region]
-
-
-# 获取天然径流量的差值
-def get_runoff_difference(region):
-    index = REGIONS.index(region)
-    if index == 0:
-        runoff_in = 0
-    else:
-        runoff_in = get_measured_runoff(REGIONS[index-1])
-    runoff_out = get_measured_runoff(region)
-    return runoff_out - runoff_in
-
-
-# 加载消耗量
-def get_consumptions(region):
-    """计算从此区域及其上游区域，合计的【水资源】消耗量，单位是立方千米"""
-    city_yr = pd.read_csv(r'../data/perfectures/yr/perfectures_in_YR_with_threshold_0.05.csv')
-    water_use = city_yr[['Year', 'Region', 'Total water use']]
-    consumption = water_use.groupby(['Region', 'Year']).sum().loc[region]['Total water use']
-    flag = 0
-    index = REGIONS.index(region)
-    while flag < index:
-        consumption += water_use.groupby(['Region', 'Year']).sum().loc[REGIONS[flag]]['Total water use']
-        flag += 1
-    return consumption * 10  # 单位由 10^8 变成 10^9
-
-
-# 计算每个区域的地表/地下水修正系数
-def get_surface_groundwater_coefficient(region):
-    watersheds = pd.read_csv(r"../data/watershed_merged.csv")
-
[…]

### 2020-09-24 script/region_differences.py
move region differences into script

@@ -12,15 +12,40 @@ from matplotlib import pyplot as plt
 
 import sys
 sys.path.append(r"..")
-from tools.values import REGIONS, PROVINCE, INDUSTRIES, INDUSTRIES_eng
 from tools.processing import get_region_by_province_name
+from tools.values import PROVINCES, INDUSTRIES_eng, INDUSTRIES, REGIONS
 
-# 清洗列名
-def from_col_name_extract_province_and_industry(name):
-    elements = name.split(':')  # 分割列名
-    province = elements[0].strip()  # 地名
-    industry = elements[-1].strip()  # 产业
-    return province, industry
+
+
+def get_yr_gdp_data(how='gdp'):
+    # 清洗列名
+    def clean_col_names(name):
+        elements = name.split(':')  # 分割列名
+        province = elements[0].strip()  # 地名
+        industry = elements[-1].strip()  # 产业
+        return province, industry
+        
+    # 加载经济数据
+    gdp = (pd.read_excel('../data/GDP.xlsx')  # 读取数据
+            .drop(0)  # 删除单位行
+            .astype(float)  # 转为浮点
+            .rename({'指标名称': 'Year'}, axis=1)  # 将年份列改名
+            .astype({'Year': int})  # 将年份从浮点改为整形
+            .set_index('Year')  # 并设置为索引
+            .replace(0., np.nan)  # 空值是没数据，不可能为 0
+            .drop(list(np.arange(1949, 1965)), axis=0)  # 删除不考虑的时间范围
+            )
+    region_dict = {region: pd.DataFrame() for region in REGIONS}  # 用来储存每个区域的GDP数据
+    for col in gdp:
+        province = clean_col_names(col)[0]  # 清洗列名
+        region = get_region_by_province_name(province)  # 属于哪个区域
+        if region: region_dict[region][col] = gdp[col]  # 如果是黄河流域的省份，存进对应的字典
+        else:  gdp.drop(col, axis=1, inplace=True)  # 不是黄河流域的省份，就丢掉
+
+    if how == 'gdp':
+        return gdp
+    else:
+        return region_dict
 
 
 
@@ -39,7 +64,6 @@ def extract_data_by_yr(data, start_yr, end_yr):
     else:
         use_data = data.loc[start_yr: end_yr]
         return np.mean(use_data), np.std(use_data)
-
 
 
[…]

### 2020-09-24 tex/main/manuscript.tex
rewrite figures to makesure everything works well

@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/framework1.jpg}
+	\includegraphics[width=\linewidth]{../../figures/main/framework.jpg}
 	\caption{
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
+	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
 	\caption{Changes of the IWRU index. 
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/phases.pdf}
+	\includegraphics[width=\linewidth]{../../figures/main/phases.pdf}
 	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
+	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
 	\caption{
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
+	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
 	\caption{
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
+	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
 	\caption{
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main_text/traps.jpg}
+	\includegraphics[width=\linewidth]{../../figures/main/traps.jpg}
 	\caption{

### 2020-09-26 tex/main/manuscript.tex
update abstract

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Water resource utilization regimes at a basin scale: transition framework and development traps}
+\title{Universal regime transition for water resources utilization in developing river basins}
 
@@
 	From agrarian to industrial societies, humans have harnessed ecosystems over rivers basins around the world, while using water resources as blood that sustains social developments. 
-	However, there is still lacking of effective method to detect regime shifts of water utilization linking to social changes, with much fewer attempts to develop theoretical models to explain their transition phases as well.
-	Here, by integrating three different dimensions of water utilization (stress, tendentiousness and pattern), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to detect regime shifts.
-	By applying this index to the Yellow River Basin, China, we summarized a general transition framework of regimes, which gives a sketch of relationships between human societies and their water utilization.
-	Based on the framework, transition phases within the three regimes and accompanying development traps can be well understood, as a useful guideline for the Yellow River to develop in a coordinated way.
+	Although relations between societies and water resources keep changing throughout, there is still lacking effective methods to detect related regimes of water utilization, with much fewer attempts to develop theoretical framework to explain their transitions as well.
+	Here, by integrating three equally important but differentiated dimensions of water utilization (stress, priority and lopsidedness), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
+	By applying this index to the Yellow River Basin, China, results suggest three water utilization regimes in developing over half a century, whose shifts led by various but pervasive causes.
+	Based on that, we summarized a general transition framework which gives a sketch of relationships between human societies and their water utilization, as a useful guideline for big river basins to develop in a coordinated way.
 \end{abstract}
@@
 % 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
-Secondly, as the need of industrial and ecological developments, tendentiousness of water utilization changed with. 
-Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential tendentiousness in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors.
+Secondly, as the need of industrial and ecological developments, priority of water utilization changed with. 
+Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential priority in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors.
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}
@@
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, tendentiousness or pattern of water utilization, see Methods) (Figure~\ref{fig:IWRU}).
+With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, priority or lopsidedness of water utilization, see Methods) (Figure~\ref{fig:IWRU}).
 \begin{figure}%[htbp]
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722), while tendentiousness and pattern of the water utilization had slight negative contribution (-0.048 and -0.09 respectively).
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722), while priority and lopsidedness of the water utilization had slight negative contribution (-0.048 and -0.09 respectively).
 % 第二阶段
-In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of tendentiousness and pattern of water utilization (+0.352 and +0.279 respectively), because of increasing stresses on water resource playing a larger negative role (-0.636).
+In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and lopsidedness of water utilization (+0.352 and +0.279 respectively), because of increasing stresses on water resource playing a larger negative role (-0.636).
 % 第三阶段
-However, as the further increasing of positive contributions of water utilization tendentiousness (+0.485) and pattern (+0.515), and decelerations of water stresses (-0.344, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+However, as the further increasing of positive contributions of water utilization priority (+0.485) and lopsidedness (+0.515), and decelerations of water stresses (-0.344, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is tendentiousness; and P3 is pattern.
+As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is priority; and P3 is lopsidedness.
 
@@
 	\includegraphics[width=\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
+	\caption{Combination of three dimensions (S: stresses; T: priority; P: lopsidedness) in different periods. 
 	Size of the points denoting average of absolute value of each indicator: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
-	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).
+	The red indicator line in this ternary plot denotes 1:1 contributions between priority (T) and patterns (P).
 	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
@@
 At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stress.
-After then, it experienced a shift to low stress since 1978, with a change in the proportion of contributions between tendentiousness and pattern, too.
+After then, it experienced a shift to low stress since 1978, with a change in the proportion of contributions between priority and lopsidedness, too.
 % 第三阶段集中
@@
 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index).
-		\textbf{B,} changes of water utilization tendentiousness, indicated by non-provisioning water shares.
-		\textbf{C,} changes of water utilization pattern, indicated by unstandardized distribution information entropy index (see supplementary: Methods. S3 for details).
+		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares.
+		\textbf{C,} changes of water utilization lopsidedness, indicated by unstandardized distribution information entropy index (see supplementary: Methods. S3 for details).
 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their contributions to changes of unstandardized SFV-index.
@@
 % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, tendentiousness and patterns of water utilization were keeping to enlarge their impacts (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}C).
+On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority and patterns of water utilization were keeping to enlarge their impacts (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}C).
 % 首先是用水比例的变化
-Representing tendentiousness of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while the influence of both are weakening (Figure~\ref{fig:dimensions}E).
+Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while the influence of both are weakening (Figure~\ref{fig:dimensions}E).
 % 再讨论用水格局的变化
@@
 % 经济总量提升导致资源耗竭的加速。
-(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the tendentiousness of water utilization between P1 and P2 (Figure\ref{fig:Causes} A).
+(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes} A).
 During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6/year$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978).
@@
 % 水资源倾向性
-(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading tendentiousness of water utilization continually tilted to the socio-economic part.
+(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part.
 As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}.
 As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}.
-Anyhow, this changes of tendentiousness reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
+Anyhow, this changes of priority reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
 % 水资源格局
@@
 % 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
-Secondly, the changing tendentiousness between non-provisioning (i.e.
+Secondly, the changing priority between non-provisioning (i.e.
 industry and urban services) and provisioning (i.e.
@@
 	$$ IWRU = \sum_{i}^3 I'_i $$
-	where $i$ is stress, tendentiousness or pattern, and $I'_i$ is standardized sub-indicator of them.
+	where $i$ is stress, priority or lopsidedness, and $I'_i$ is standardized sub-indicator of them.
 A brief description of the sub-indicators used to measure each dimension follows (see SI Methods.
@@
 
-	\subsubsection*{Sub-indicator of Tendentiousness}
-	To tendentiousness, we use non-provisioning shares of water use as an indicator.
+	\subsubsection*{Sub-indicator of priority}
+	To priority, we use non-provisioning shares of water use as an indicator.
 While provisional water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning water use ($WU_{non-pro}$) includes industrial and urban services water uses.
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($S$), tendentiousness ($T$) and pattern ($P$) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
+Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($S$), priority ($T$) and lopsidedness ($P$) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
 S3):

### 2020-09-27 tex/main/manuscript.tex
Revised introduction and abstract, with a new diagram of theory framework

@@
 % 水资源在人类世的重要性，是支持人类社会发展的基础。
-\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
+\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects.
+% TODO 这里增加三篇“大文章”参引
 % 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-At the same time, however, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development traps \cite{cummingLinkingEconomicGrowth2018}.
+At the same time, however, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
+% TODO 这里增加参考文献，人类对水循环的改造 
 % 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
@@
 % 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
-Therefore, understanding the complex relationship between human societies and water resources utilization, and its evolution provides underlying supports to development in a coordinated way, at a basin scale.
+Therefore, understanding the complex relationship between human societies, water resources utilization and their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.
 
@@
 % Regime 和 Regime shift 的定义。
-Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018a}.
+Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018a, schefferCatastrophicRegimeShifts2003a, schefferCatastrophicShiftsEcosystems2001}.
 % 人水系统中的水资源功能
-Within human-water systems, water have several key functions, the most important of which is supplying for human societies in sustainable development based on a complex structure of water utilization.
+Within human-water systems, water have several key functions, the most important of which is supplying for human societies in developments based on a complex structure of water utilization. 
 % 水资源利用 regime shift
@@
 % 稳态转换随着社会发展增加
-These regime shifts, triggered by gradual or abrupt drivers, are likely to occur more often as societies' development increasing their pressure or stuck in traps at a basin scale.
+These regime shifts, triggered by gradual or abrupt drivers, are likely to occur more often as societies' development increasing their stresses on water resources and deepening dependences on them.
+% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
 % Regime 过渡性的存在
-As a result, many large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated governance, as such it is a reasonable assumption that there is a transition pattern within regime shifts.
+As a result, most large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated governance, for which it is a reasonable assumption that there is a general transition pattern.
+% TODO 这里需要安排参考文献，大河流域的发展历程
 % 过渡性有助于理解流域存在的问题
-Sketching the transition of water utilization regimes, therefore, can help to understand and predict development traps, which is crucial for integrated management and coordinated development towards sustainability at a basin scale.
+Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
 % 对过渡性的研究还很少
-Despite pervasive and important, there is still lacking of effective method to define the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transition phases as well.
-s
+Despite pervasiveness, there is still lacking of effective method to define the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.
 
@@
 Development of societies by using water resources has been going on for at least thousands of years.
-Although its regime shifts and transition phases are not fully understood yet, water utilization has been depicted and studied from different dimensions.
+Although its regime shifts and transition phases are not fully understood yet, features of water utilization has been depicted and studied from different perspectives.
 % 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
-Firstly, since water resources are scarce, the most widespread concern is the rising stresses on human societies to use water resources.
-Even though the stocks of water in artificial reservoirs are helpful to water resources availability, greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water utilization during the last century.
-\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}
+Firstly, water stresses if of increasing importance and widespread concerns because of scarcity.
+Even though the stocks of water in reservoirs are helpful to water resources availability, greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water utilization during the last century
+\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}.
 % 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
-Secondly, as the need of industrial and ecological developments, priority of water utilization changed with. 
-Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential priority in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors.
-\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}
+Secondly, as the need of industry, services and ecology developments, priority of water utilization changed with. 
+Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential priority in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors
+\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
 % 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
-Thirdly, since water distribution and utilization are inherently basinal concerns, patterns of also play an important role.
+Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by competitive sectors, lopsidedness also plays as an important aspect.
 % 全球总的取水量很少，但缺水地区很多
-Although only 10\% of available water is withdrawn on global average, about 30\% of population live in highly water-stressed areas,
-where dominated sectors of water utilization are various as well. 
-\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}
+While only 10\% of available water is withdrawn on global average, about 30\% of population settles in highly water-stressed regions with vary dominated water demands
+\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
 % 此外，人类活动还在改变这一格局
-In addition, human activities are still changing this pattern, since positive impacts caused by human interventions mostly occur in upper regions whereas aggravated water resources downstream, in many basins around the world.
-\cite{veldkampWaterScarcityHotspots2017}
+Human activities further affect this lopsidedness, as positive impacts mostly occur in upper regions whereas aggravated downstream, though most governments are trying to control this situation. 
+\cite{veldkampWaterScarcityHotspots2017}. 
+% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
+Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: “How much water resources?”, “How to use them?” and “Used for whom or in where?”.
 % 将三种视角结合，就是“水资源利用体系”。
-Although existing researches have evaluated the aspects of water resource utilization from these different dimensions, we still cannot obtain a coherent understanding of regime shifts regard to social development and water utilization, without integrating them.
+However, as these dimensions haven't been well integrated by quantitative methods, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.
 
@@
 % 最后总结出一般性框架
-Finally, refer to the existing theories, we summarized a general transition framework of water utilization regimes, which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.
+Finally, refer to the existing theories, we summarized a universal transition framework of water utilization regimes, which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.
 
-\begin{figure}%[htbp]
+\begin{figure*}%[htbp]
 	\centering
@@
 		A framework for understanding the changing relationship between watershed development and water resources.
+		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
+		\textbf{A,} three dimensions (stress, priority and lopsidedness) of water resources utilization.
+Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis.
+(1) Stress of water use shifts between low and high, which means there is no shortage of water supply or there is.
+(2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies.
+(3) Lopsidedness can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
+We presume that water utilization regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development.
+		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
+		\textbf{B,} the changes after combining the three dimensions.
+Because the above three dimensions are changing with the development of society, their combined water resource utilization status is also different.
+When abrupt transitions occur during this process, they may indicate a regime shift in water utilization, so we need an indicator to monitor this change.
 	}
 	\label{fig:framework1}
-\end{figure}
+\end{figure*}
 

### 2020-09-29 tex/main/manuscript.tex
change contribution / net contribution, update phases figs

@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization.
+Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization Figure~\ref{fig:framework}.
 % 使用案例研究
@@
 	}
-	\label{fig:framework1}
+	\label{fig:framework}
 \end{figure*}
@@
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, priority or lopsidedness of water utilization, see Methods) (Figure~\ref{fig:IWRU}).
+With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or lopsidedness of water utilization, see Methods.) (Figure~\ref{fig:IWRU}).
 \begin{figure}%[htbp]
@@
 	\caption{Changes of the IWRU index. 
-	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
+	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
 	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722), while priority and lopsidedness of the water utilization had slight negative contribution (-0.048 and -0.09 respectively).
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and lopsidedness of the water utilization had slight negative contribution (-0.048, 5.6\% and -0.09, 10.7\% respectively).
 % 第二阶段
-In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and lopsidedness of water utilization (+0.352 and +0.279 respectively), because of increasing stresses on water resource playing a larger negative role (-0.636).
+In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and lopsidedness of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636, 50.2\%).
 % 第三阶段
-However, as the further increasing of positive contributions of water utilization priority (+0.485) and lopsidedness (+0.515), and decelerations of water stresses (-0.344, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+However, as the further increasing of positive contributions of water utilization priority (+0.485 change contribution and 36.1\% net contribution) and lopsidedness (+0.515 and 38.3\%, corresponding), and decelerations of water stresses (-0.344 change contribution, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
@@
 % 用水三个维度的组合呈现出阶段特征明显
-Combining these three dimensions' net contribution to IWRU further, ratios of the contributions of the three dimensions clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
+Combining these three dimensions' net contribution (differ from change contributions, see Method) to IWRU further, ratios of the contributions of the three dimensions clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
 \begin{figure}%[htbp]
@@
 	\includegraphics[width=\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of three dimensions (S: stresses; T: priority; P: lopsidedness) in different periods. 
-	Size of the points denoting average of absolute value of each indicator: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
-	The red indicator line in this ternary plot denotes 1:1 contributions between priority (T) and patterns (P).
-	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
+	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; L: lopsidedness).
+The closer a point to an angle, greater the proportion of the net contribution of this dimension.
+	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and lopsidedness (L).
+When the points are bellow this line, the net contribution ratio of lopsidedness is lower than that of priority, and vice versa.}
+	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
 	\label{fig:phases}
@@
 At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stress.
-After then, it experienced a shift to low stress since 1978, with a change in the proportion of contributions between priority and lopsidedness, too.
+After then, it experienced a shift to low stress since 1978, with a change in the proportion of net contributions between priority and lopsidedness, too.
 % 第三阶段集中
-Finally, the three dimensions' contribution were much similar in P3, making the points highly concentrated at the centre of the ternary diagram for that period.
+Finally, the net contribution of three dimensions were much similar in P3, making the points highly concentrated at the centre of the ternary diagram in that period.
 
@@
 	}
-	\label{fig:framework}
+	\label{fig:summary}
 \end{figure*}
@@
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).
+As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:summary}).
 
@@
 	\subsection*{Contribution decomposition}
+	\subsubsection*{Change contributions}
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
@@
 		$$ C_{F} = \frac{|\Delta C_{F}|}{\Delta IWRU}$$
+
+	\subsubsection*{Net contributions}
+		% TODO 这里补充 ”net contribution“ 的方法介绍
 		}

### 2020-09-29 tools/statistic.py
*.ipynb

@@ -261,3 +261,17 @@ def plot_ratio_contribution(contribution_df, ax=None, bar_width=0.4, denominator
             ax.legend(loc=legend_loc)
     ax.set_xticks(np.arange(0, len(contribution_df.columns), 1))
     ax.set_xticklabels(contribution_df.columns.tolist())
+
+
+def judge_one_way_f_test(group1, group2):
+    from scipy import stats
+    F, p = stats.f_oneway(group1, group2)
+    F_test = stats.f.ppf((1-0.05), 4, 15)
+    print('F值是{:.2f}，p值是{:.5f}'.format(F,p))
+    print('F_test的值是{:.2f}'.format(F_test))
+    if F>=F_test:
+        print('拒绝原假设，两组均值不相等, 显著性是{:.5f}'.format(p))
+        return False
+    else:
+        print('接受原假设，两组均值可认为是相等，显著性是{:.5f}'.format(p))
+        return True

### 2020-09-29 tex/main/manuscript.tex
update results and refs. to SI figures

@@
 	Although relations between societies and water resources keep changing throughout, there is still lacking effective methods to detect related regimes of water utilization, with much fewer attempts to develop theoretical framework to explain their transitions as well.
-	Here, by integrating three equally important but differentiated dimensions of water utilization (stress, priority and lopsidedness), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
+	Here, by integrating three equally important but differentiated dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
 	By applying this index to the Yellow River Basin, China, results suggest three water utilization regimes in developing over half a century, whose shifts led by various but pervasive causes.
@@
 % 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
-Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by competitive sectors, lopsidedness also plays as an important aspect.
+Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by competitive sectors, configuration also plays as an important aspect.
 % 全球总的取水量很少，但缺水地区很多
@@
 % 此外，人类活动还在改变这一格局
-Human activities further affect this lopsidedness, as positive impacts mostly occur in upper regions whereas aggravated downstream, though most governments are trying to control this situation. 
+Human activities further affect this configuration, as positive impacts mostly occur in upper regions whereas aggravated downstream, though most governments are trying to control this situation. 
 \cite{veldkampWaterScarcityHotspots2017}. 
@@
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three dimensions (stress, priority and lopsidedness) of water resources utilization.
+		\textbf{A,} three dimensions (stress, priority and configuration) of water resources utilization.
 Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis.
@@
 (2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies.
-(3) Lopsidedness can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
+(3) configuration can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
 We presume that water utilization regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development.
@@
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or lopsidedness of water utilization, see Methods.) (Figure~\ref{fig:IWRU}).
+With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
 \begin{figure}%[htbp]
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and lopsidedness of the water utilization had slight negative contribution (-0.048, 5.6\% and -0.09, 10.7\% respectively).
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and configuration of the water utilization had slight negative contribution (-0.048, 5.6\% and -0.09, 10.7\% respectively).
 % 第二阶段
-In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and lopsidedness of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636, 50.2\%).
+In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and configuration of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636, 50.2\%).
 % 第三阶段
-However, as the further increasing of positive contributions of water utilization priority (+0.485 change contribution and 36.1\% net contribution) and lopsidedness (+0.515 and 38.3\%, corresponding), and decelerations of water stresses (-0.344 change contribution, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+However, as the further increasing of positive contributions of water utilization priority (+0.485 change contribution and 36.1\% net contribution) and configuration (+0.515 and 38.3\%, corresponding), and decelerations of water stresses (-0.344 change contribution, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is priority; and P3 is lopsidedness.
+As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is priority; and P3 is configuration.
 
@@
 	\includegraphics[width=\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; L: lopsidedness).
+	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; L: configuration).
 The closer a point to an angle, greater the proportion of the net contribution of this dimension.
-	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and lopsidedness (L).
-When the points are bellow this line, the net contribution ratio of lopsidedness is lower than that of priority, and vice versa.}
+	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (L).
+When the points are bellow this line, the net contribution ratio of configuration is lower than that of priority, and vice versa.}
 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
@@
 At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stress.
-After then, it experienced a shift to low stress since 1978, with a change in the proportion of net contributions between priority and lopsidedness, too.
+After then, it experienced a shift to low stress since 1978, with a change in the proportion of net contributions between priority and configuration, too.
 % 第三阶段集中
@@
 		Changes in different dimensions of water resources utilization regimes and their main contributors.
-		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index).
-		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares.
-		\textbf{C,} changes of water utilization lopsidedness, indicated by unstandardized distribution information entropy index (see supplementary: Methods. S3 for details).
-		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their contributions to changes of unstandardized SFV-index.
-		\textbf{E,} Main impact water uses to water utilization tendentiousnesses, and their contributions to changes of non-provisioning water shares.
-		\textbf{F,} Main impact factors to water utilization patterns, and their contributions to changes of related unstandardized distribution information entropy index (see supplementary: Methods.
-S3 for details).
+		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
+		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see Methods S4).
+		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
+		\textbf{E,} Main impact water uses to water utilization tendentiousnesses, and their change contributions to non-provisioning water shares.
+		\textbf{F,} Main impact factors to water utilization patterns, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
 		}
@@
 % 从阶段一到阶段二，水资源压力的变化最为明显
-Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress, which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}A and Figure~\ref{fig:dimensions}D).
+Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D).
 % 1. 水资源丰富，耗水量少且灵活用水
-In the P1, natural surface water resources were rather abundant with lesser water consumptions (supplementary Fig.
-S1 and S3) and most of which were flexible water utilization (supplementary Fig.
+In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig.
+S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig.
 S4).
 During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce.
-Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but most of which built in P1 (supplementary Fig.
-S5 and supplementary Table S1).
+Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix S5}).
 As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.
@@
 % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority and patterns of water utilization were keeping to enlarge their impacts (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}C).
+On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts.
 % 首先是用水比例的变化
-Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while the influence of both are weakening (Figure~\ref{fig:dimensions}E).
+Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
 % 再讨论用水格局的变化
-However, patterns of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing disparities in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
+However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing disparities in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
 
 % tag 结果3
-\subsection*{Causes of water utilization regime changes}
+\subsection*{Drivers of water utilization regime shifts}
 
@@
 	\caption{
-		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
-		\textbf{A.} Changes of total irrigated area and water consumption per unit of irrigated area.
-		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (see supplementary: Methods. S2 for details).
+		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
+		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
+		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Method} S2).
 		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time.
-Red ones denote hub reservoirs in the basin, which plays a role in integrated water management.
+Red ones denote hub reservoirs in the basin, which plays a role in bainsal integrated water management.
 Size of the points indicates their magnitude of water storage capacities.
-Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
+Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
 (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage.
-Therefore, these marked reservoirs are significant for the entire basin, far crucial than regional development.
+These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
 	}
@@
 (1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes} A).
-During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6/year$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978).
-Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water.
+During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6/year$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix}).
+Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix}).
 
 % 用水关系的变化
-(2) During the P3, irrigation, whose water consumptions were still dominating, have noticeable changes in its efficiency, however.
+(2) During the P3, irrigation had noticeable changes in its efficiency, whose water consumptions were reduced but still dominant.
 Although irrigated agricultural area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes} A and B).
-It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (supplementary Fig.
+It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
+S7).
+As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig.
 S6).
-As a result, the proportions of water use between the different sectors tend to average out while the total water consumption remains stable, after the P3 (supplementary Fig.
-S7).
 
@@
 (3) Changing water management practice contributed throughout all three periods.
-In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C).
-In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (supplementary Fig.
+In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
+In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig.
 S5).
-Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and supplementary Fig.
+Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
 S5).
@@
 	$$ IWRU = \sum_{i}^3 I'_i $$
-	where $i$ is stress, priority or lopsidedness, and $I'_i$ is standardized sub-indicator of them.
+	where $i$ is stress, priority or configuration, and $I'_i$ is standardized sub-indicator of them.
 A brief description of the sub-indicators used to measure each dimension follows (see SI Methods.
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($S$), priority ($T$) and lopsidedness ($P$) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
+Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($S$), priority ($T$) and configuration ($P$) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
 S3):

### 2020-09-29 tex/sup/supplementary_information.tex
update results and refs. to SI figures

@@
     \includegraphics[width=\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
-    \caption{Natural measured runoff of Yellow River within different periods.}
+    \caption{Water resources in different regions. 
+        \textbf{A,} changing trend of measured runoff, \textbf{B, C and D} average measured runoff and water consumptions within different periods.
+    % TODO 这里增加一个耗水量的图
+    }
 \end{figure}
@@
     \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
-    \caption{Flexibility}
+    \caption{
+        Flexibility and its change contributions of water utilization.
+        \textbf{A,} Proportion of inflexible water uses.
+        \textbf{B,} Change contributions of inflexible water uses.
+    }
 \end{figure}
@@
     \includegraphics[width=0.95\textwidth]{../../figures/sup/reservoirs.pdf}
-    \caption{Reservoirs and accumulated storage}
+    \caption{
+        Reservoirs and their storage.
+        \textbf{A,} number of new reservoirs in different periods.
+        \textbf{B,} total storage capacities in different regions. 
+    }
 \end{figure}
 
-% 补充图片6：节水措施
+% 补充图片6：用水比例
+% TODO 这里只保留堆积图即可，做的更好看点
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
+    \caption{Proportions of total water use between the different sectors}
+\end{figure}
+
+% 补充图片7：节水措施
+% TODO 这里增加更丰富的节水措施图
 \begin{figure}
@@
     \includegraphics[width=0.95\textwidth]{../../figures/sup/saving_water.jpg}
-    \caption{technological solutions and water conservation practices}
-\end{figure}
-
-% 补充图片7：用水比例
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
-    \caption{Proportions of water use between the different sectors}
+    \caption{
+        technological solutions and water conservation practices
+    }
 \end{figure}

### 2020-09-29 script/region_differences.py
Add a small function to calculate wu proportions for supporting tex

@@ -197,7 +197,7 @@ def plot_wu(ax, colors, start_yr, end_yr, **kargs):
         mean, std = extract_data_by_yr(use_data, start_yr, end_yr)     
         bar = ax.bar(
                 x=i,
-                height=mean,
+                height=mean * 10,  # 这里换算单位成为 10^8 m^3
                 yerr=std,
                 color=colors[i],
                 **kargs
@@ -309,3 +309,18 @@ def plot_water(ax, start_yr, end_yr, colors):
     ax.set_xticklabels(REGIONS)
     ax.set_xlabel('Regions')
     ax.set_ylabel('Natural yield')
+
+
+def get_consumptions_ratio(yr, revise=False):
+    measured = get_measured_runoff('DR')
+    water_use_all_regions = pd.DataFrame()
+    for region in REGIONS:
+        if revise:
+            c = get_surface_groundwater_coefficient(region)
+            data = get_consumptions(region) * c
+        else:
+            data = get_consumptions(region)
+        water_use_all_regions[region] = data
+    wu = water_use_all_regions.sum(axis=1)
+    ratio = wu / (measured + wu)
+    return ratio.loc[yr]

### 2020-09-29 tex/main/manuscript.tex
add a paragraph in discussion to give a interpret

@@
 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
-		\textbf{E,} Main impact water uses to water utilization tendentiousnesses, and their change contributions to non-provisioning water shares.
-		\textbf{F,} Main impact factors to water utilization patterns, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
+		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
 		}
@@
 
+\subsection*{Interpret of regime shifts within YRB}
+% 我们发明的指数能将三个维度的变化捕捉到。
+The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
+% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
+Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
+% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
+Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
+S8).
+% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
+Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
+% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
+At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
+% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
+As a result, this regime is characterized by a rapid expansion of irrigation water to support agricultural development.
+
+% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
+% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
+The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
+In 1972, the Yellow River was cut off for the first time with a length of 310 km for 19 days, and continued to be cut off for many years since then (\textit{SI Appendix} Fig.
+S9).
+% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
+Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
+% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
+Since then, the expansion trend of agriculture has been contained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market.
+In addition, most laws and regulations have been gradually implemented (\textit{SI Appendix} Table 3 and Fig.
+S10).
+For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.
+
+% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
+The next regime shift was not occurred by a significant increase in water use efficiency in about 1993. 
+% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
+After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.S8).
+% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
+A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture.
+As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig.
+S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).
+
+In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement, have driven the YRB to change regimes twice between 1965 and 2013, which had been along with social development in different aspects and can be interpreted by a transition process.
+
 \subsection*{Transition Framework}
@@
 % 水资源格局
-(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing patterns of water utilization.
+(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
 In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
 However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}.
-The changes in water utilization patterns along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.
+The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.
 
@@
 	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
-	The Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (stresses, tendentiousnesses and patterns, denoted by sub-indicators correspondingly).
+	The Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (stresses, priority and configurations, denoted by sub-indicators correspondingly).
 Assuming they have equal weights, we log-transformed and standardized the three sub-indicators for elimination of differences between indicators.
@@
 
-	\subsubsection*{Sub-indicator of Patterns}
-	To description of patterns between regions or sections, we designed an indicator by imitation of information entropy (Allocational Entropy Metric, see supplementary document: Methods S4).
+	\subsubsection*{Sub-indicator of configurations}
+	To description of configurations between regions or sections, we designed an indicator by imitation of information entropy (Allocational Entropy Metric, see supplementary document: Methods S4).
 Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy).

### 2020-09-30 tex/main/manuscript.tex
update discussion2: transition framework

@@
 
-\subsection*{Transition Framework}
+\subsection*{Transition Framework of water utilization}
 
@@
 		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B. Regional cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+		\textbf{B. Local cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
 		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role.
@@
 		\textbf{C.
-Basinal cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
+Regional cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
 Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
@@
 % 与社会-自然二元水循环理论
-This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
+This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle hypothesis
 \cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
 % 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
-According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure
+According to our results, regime shifts of water utilization, as transition phases in three related dimensions induced by social development, are of the most important characteristics towards natural-social dualistic cycle
 \cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:summary}).
+As such, we summarized a universal transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:summary}).
 
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
-Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution, corresponding to typical changes within the Yellow River Basins as an example (Figure~\ref{fig:dimensions}).
+Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution. 
 % 水资源压力
@@
 As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}.
-Anyhow, this changes of priority reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
+Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
 % 水资源格局
-(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
+(3) Last, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
 In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
@@
 % 综上所述
-By combining the above three dimensions, water utilization regimes reflect a tendency of transitional evolution thoroughly.
+By combining the above three dimensions, these changes gradually transformed water utilization regimes in a “natural cycle” (Figure~\ref{fig:summary}A) to one in local or regional cycle (Figure~\ref{fig:summary} B and C), towards dualistic water cycle.
 In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework.
@@
 
-\subsection*{Development Traps}
+\subsection*{Dilemmas and future directions}
 % 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。

### 2020-10-01 tex/main/manuscript.tex
update discussion-3 and add a new fig

@@
 % \usepackage{cite}
-
+\usepackage{url}	
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
@@
 After sketching changes of relationships between development and water utilization within the Yellow River Basin, we summarized a general transition framework.
-By predicting widespread development traps, it can be a useful guideline for basins all around the world in their sustainable developing trajectories.
+By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories.
 }
@@
 % Regime 和 Regime shift 的定义。
-Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018a, schefferCatastrophicRegimeShifts2003a, schefferCatastrophicShiftsEcosystems2001}.
+Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018, schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
 % 人水系统中的水资源功能
@@
 Even though the stocks of water in reservoirs are helpful to water resources availability, greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water utilization during the last century
-\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}.
+\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
 % 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
@@
 % 最后总结出一般性框架
-Finally, refer to the existing theories, we summarized a universal transition framework of water utilization regimes, which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.
+Finally, refer to the existing theories, we summarized a universal transition framework of water utilization regimes, which can be a useful guideline for basins to predict development dilemmas and to develop in a coordinated way.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/framework.jpg}
+	\includegraphics[width=0.9\linewidth]{../../figures/main/framework.jpg}
 	\caption{
@@
 	\caption{Changes of the IWRU index. 
-	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
+	\textbf{A,} two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
 	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
@@
 	\includegraphics[width=\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; L: configuration).
+	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration).
 The closer a point to an angle, greater the proportion of the net contribution of this dimension.
-	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (L).
+	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C).
 When the points are bellow this line, the net contribution ratio of configuration is lower than that of priority, and vice versa.}
@@
 		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Method} S2).
-		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time.
+		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
 Red ones denote hub reservoirs in the basin, which plays a role in bainsal integrated water management.
@@
 Since then, the expansion trend of agriculture has been contained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market.
-In addition, most laws and regulations have been gradually implemented (\textit{SI Appendix} Table 3 and Fig.
-S10).
+In addition, most laws and regulations have been gradually implemented (\textit{SI Appendix} Table 3).
 For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.
@@
 
-\subsection*{Transition Framework of water utilization}
+\subsection*{Transition framework of water utilization}
 
@@
 % 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
-Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}.
+Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018,falkenmarkUnderstandingWaterResilience2019}.
 % 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
@@
 \subsection*{Dilemmas and future directions}
+% 对于可持续科学，认识这种稳态的变化很重要
+For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
 % 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
-At different transition phases, basins may face to various development traps in water utilization, leading an unsustainable trajectory (Figure~\ref{fig:traps}). 
+At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
 % 资源陷阱和失配，导致崩溃
-Like social-ecological systems and other complex systems, coupled human-water system may collapse under the gradual pressure on resources or because of structural mismatches 
+Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
 \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
 % 转型应对陷阱
-A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
+A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
 % 我们的框架有助于理解和识别
-Thus, our transition framework can identify regime shifts of water utilization, which can help to predict possible development traps.
+Since our transition framework can identify regime shifts of water utilization, it may help to predict possible dilemmas in development.
 
+% TODO 这里把图改成全球大河流域的资源问题类型图
 \begin{figure}%[htbp]
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/traps.jpg}
+	\includegraphics[width=\linewidth]{../../figures/main/big_rivers.pdf}
 	\caption{
-		\textbf{Transition phases of water resources utilization regime and development traps.}
-		Green arrows indicate the trajectory without falling into any development trap, IWRU roughly follows a non-linear upward trend at the same time.
-However, overexploitation of water resources will leave the system in a resource trap, without moving to regional coordinated cycle.
-And even if one enters a regional cycle, it can still fall into a structural trap when water utilization fails to adapt to the complex changes within human-water systems.
+		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
+		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure.
+Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
 	}
@@
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
-According to case studies around the world, big river basins often face resource traps at the beginning of their developments, while highly developed ones often face structural traps.
+According to case studies around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-During P1 and P2 (refers from natural cycle to the regional cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
-Although water management practices in P1 (construction of numerous reservoirs) mitigated the stress on water resources from accelerated development, it became scarce rapidly throughout and water utilization stresses rebounded in the P2 along with a regime shift.
-The resource trap is revealed at this point, with severe runoff outages and groundwater depletion of the Yellow River from P2 onwards (supplementary Fig.
+In the Yellow River Basin, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
+The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig.
 S8).
-% 资源困局可能普遍存在
-Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to regional cycle
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
+% 后来摆脱了资源陷阱（表现形式 xxx）。
+To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices (\textit{SI Appendix} Methods S5).
+These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the “resource dilemma”.
 
-% 后来摆脱了资源陷阱（表现形式 xxx）。
-To get rid of the resource trap, a clear transformation towards integrated basin management was proposed, with several management practices (supplementary Methods S4 and Fig.
-S9).
+% 一段有关87分水方案的介绍
 The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}.
 Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}.
-These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the “resource trap”.
+
+% 资源困局可能普遍存在
+Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle
+\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
+% 结构困局可能普遍存在
 Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g.
-Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017a}.
+Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017}.
 
 % 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
-However, in the regional cycle regime of water utilization, the Yellow River Basins still faces structural traps and require further transformation according to changes within the human-water system. 
+However, basins still face structural dilemmas and require further transformation according to changes within the regional cycle of water utilization. 
 Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency (i.e.
@@
 % 总结：整个流域需进一步转型与适应，以实现高质量发展。
-Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural trap \cite{cummingResilienceBigRiver2011}.
-Therefore, based on the identification of current phases and development traps by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin \cite{scoonesTransformationsSustainabilityCombining2020a}.
+Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.
+Therefore, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin \cite{scoonesTransformationsSustainabilityCombining2020a}.
 

### 2020-10-01 tex/sup/supplementary_information.tex
add a paragraph in discussion to give a interpret
update discussion-3 and add a new fig

@@
 \section*{Methods S3. Harmonization of datasets}
+% TODO 这里要强调省级数据和县级数据在不确定性上的差异
 % 由于我们的数据集来源广泛，且具有不同的空间尺度，我们需要在区域尺度（SR，UR，MR和DR）上对数据进行调和，根据数据的空间尺度有不同的处理方式。
@@
 
+% TODO 这里补充 SI Appendix Methods S5：简要介绍黄河的管理措施变化
+
 % tag 附录图
@@
     \caption{
-        technological solutions and water conservation practices
+        technological solutions and water conservation practices in 2013
     }
@@
 
-% 补充图片8：黄河断流
+% 补充图片8：
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/ternary.pdf}
+    \caption{Net contribution of agriculture, industry and services to GDP in different years.}
+\end{figure}
+
+% 补充图片9：黄河断流
 \begin{figure}
@@
 
-% 补充图片9：管理政策
-\begin{figure}
-    \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/managements.pdf}
-    \caption{Number of management practices in different periods, including policy and reservoirs.}
-\end{figure}
+% % 补充图片10：管理政策
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.95\textwidth]{../../figures/sup/managements.pdf}
+%     \caption{Number of management practices in different periods, including policy and reservoirs.}
+% \end{figure}
+
+% 补充图片10：地下水
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.95\textwidth]{../../figures/sup/outages.jpg}
+%     \caption{Severe runoff outages and groundwater depletion}
+% \end{figure}
+% TODO 这里处理一下地下水的图片，看看地下水是否需要提及
 
@@
 
+% TODO 这里要加一个黄委会沿革的简表
+
 %% 表格

### 2020-10-02 tex/main/manuscript.tex
update some details after the first reading

@@
 	Water, a key resource to support the sustainable development of human societies, whose natural cycle has been modified by growing socio-economic processes.
-We propose a new method with an integrated indicator to detect water utilization regimes and applying them on the Yellow River Basin, a typical overexploited basin in China.
-After sketching changes of relationships between development and water utilization within the Yellow River Basin, we summarized a general transition framework.
+We propose a new method with an integrated index to detect water utilization regimes and applying it to the Yellow River Basin, a typical overexploited basin in China.
+After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a universal transition framework.
 By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories.
@@
 	From agrarian to industrial societies, humans have harnessed ecosystems over rivers basins around the world, while using water resources as blood that sustains social developments. 
-	Although relations between societies and water resources keep changing throughout, there is still lacking effective methods to detect related regimes of water utilization, with much fewer attempts to develop theoretical framework to explain their transitions as well.
-	Here, by integrating three equally important but differentiated dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
-	By applying this index to the Yellow River Basin, China, results suggest three water utilization regimes in developing over half a century, whose shifts led by various but pervasive causes.
-	Based on that, we summarized a general transition framework which gives a sketch of relationships between human societies and their water utilization, as a useful guideline for big river basins to develop in a coordinated way.
+	Although relations between societies and water resources keep changing throughout, there is still lacking effective methods to detect related regimes of water resources utilization, with much fewer attempts to develop theoretical framework to explain their transitions as well.
+	Here, by integrating three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
+	By applying this index to the Yellow River Basin, China, our results suggest three water utilization regimes in developing over half a century, whose shifts led by various but pervasive causes.
+	Based on that, we summarized a universal transition framework which gives a sketch of relationships between human societies and their water utilization, as a useful guideline for big river basins to develop in a coordinated way.
 \end{abstract}
@@
 % 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-At the same time, however, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
+However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
 % TODO 这里增加参考文献，人类对水循环的改造 
@@
 % 人水系统中的水资源功能
-Within human-water systems, water have several key functions, the most important of which is supplying for human societies in developments based on a complex structure of water utilization. 
+Water have several key functions within a human-water system, the most important of which is supplying for human societies in further developments based on water utilization. 
 % 水资源利用 regime shift
-However, inter-connected human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced regime shifts in water utilization
+However, interplayed human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
 \cite{falkenmarkUnderstandingWaterResilience2019}.
 % 稳态转换随着社会发展增加
-These regime shifts, triggered by gradual or abrupt drivers, are likely to occur more often as societies' development increasing their stresses on water resources and deepening dependences on them.
+These gradual or abrupt drivers triggered regime shifts as societies' development strengthen their interlinks to water utilization and deepening dependences on them.
 % TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
 % Regime 过渡性的存在
-As a result, most large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated governance, for which it is a reasonable assumption that there is a general transition pattern.
+As a result, most large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern.
 % TODO 这里需要安排参考文献，大河流域的发展历程
@@
 % 对过渡性的研究还很少
-Despite pervasiveness, there is still lacking of effective method to define the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.
+Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.
 
@@
 % 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
-Firstly, water stresses if of increasing importance and widespread concerns because of scarcity.
-Even though the stocks of water in reservoirs are helpful to water resources availability, greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water utilization during the last century
+Firstly, water stresses are of increasing importance and concerns because of scarcity.
+Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use during the last century, while store of water resource in reservoirs are helpful to relief of
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
@@
 Secondly, as the need of industry, services and ecology developments, priority of water utilization changed with. 
-Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential priority in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors
+Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths in economy profits of industry or services and their priority in water consumption, leading potential conflicts between different sectors
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
 % 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
-Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by competitive sectors, configuration also plays as an important aspect.
+Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by economically competitive sectors, configuration also plays as an important aspect.
 % 全球总的取水量很少，但缺水地区很多
@@
 % 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
-Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: “How much water resources?”, “How to use them?” and “Used for whom or in where?”.
+Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
 % 将三种视角结合，就是“水资源利用体系”。
-However, as these dimensions haven't been well integrated by quantitative methods, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.
+As these dimensions haven't been well integrated by quantitative methods, however, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.
 
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization Figure~\ref{fig:framework}.
+Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization (Figure~\ref{fig:framework}).
 % 使用案例研究
@@
 % 指出发展困局
-In addition, combining data analysis, we identify causes of the regime shifts. 
+In addition, combining data analysis, we identify drivers of the regime shifts. 
 % 最后总结出一般性框架
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{../../figures/main/framework.jpg}
+	\includegraphics[width=0.85\linewidth]{../../figures/main/framework.jpg}
 	\caption{
@@
 Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis.
-(1) Stress of water use shifts between low and high, which means there is no shortage of water supply or there is.
+(1) Stress of water utilization shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
 (2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies.
@@
 \section*{Results}
-\subsection*{Detection of Water utilization regimes}
+\subsection*{Water utilization regimes}
 % 这一节主要展示IWRU的变化趋势和WUR的划分
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and configuration of the water utilization had slight negative contribution (-0.048, 5.6\% and -0.09, 10.7\% respectively).
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and configuration of the water utilization had slight negative contribution (-0.048 and -0.09 in change contributions, 5.6\% and 10.7\% in net contributions, respectively).
 % 第二阶段
-In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and configuration of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636, 50.2\%).
+In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and configuration of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636 change contribution and 50.2\% net contribution).
 % 第三阶段
@@
 % 用水三个维度的组合呈现出阶段特征明显
-Combining these three dimensions' net contribution (differ from change contributions, see Method) to IWRU further, ratios of the contributions of the three dimensions clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
+Combining these three dimensions' net contribution (differ from change contributions, see \textit{Methods}) to IWRU further, ratios of the contributions of the three dimensions clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
 \begin{figure}%[htbp]
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/phases.pdf}
+	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
 	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration).
-The closer a point to an angle, greater the proportion of the net contribution of this dimension.
+The closer a point to an angle of the triangle, greater the proportion of the net contribution of this dimension.
 	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C).
@@
 % 第一阶段到第二阶段
-At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stress.
-After then, it experienced a shift to low stress since 1978, with a change in the proportion of net contributions between priority and configuration, too.
+At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses.
+After then, it experienced a shift to low stresses since 1978, with a change in the proportion of net contributions between priority and configuration, too.
 % 第三阶段集中
-Finally, the net contribution of three dimensions were much similar in P3, making the points highly concentrated at the centre of the ternary diagram in that period.
+Finally, the net contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
 
@@
 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
-		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see Methods S4).
+		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
@@
 % 从阶段一到阶段二，水资源压力的变化最为明显
-Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D).
+Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).
 % 1. 水资源丰富，耗水量少且灵活用水
@@
 During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce.
-Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix S5}).
+Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig.
+S5).
 As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.
@@
 % 再讨论用水格局的变化
-However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing disparities in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
+However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
 
@@
 		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
-		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Method} S2).
+		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
 		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
@@
 % 经济总量提升导致资源耗竭的加速。
-(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes} A).
-During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6/year$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix}).
+(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A).
+During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
+S6).
 Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix}).
@@
 (2) During the P3, irrigation had noticeable changes in its efficiency, whose water consumptions were reduced but still dominant.
-Although irrigated agricultural area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes} A and B).
-It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
-S7).
+Although irrigated area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices.
 As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig.
@@
 % 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
-As a result, this regime is characterized by a rapid expansion of irrigation water to support agricultural development.
+As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.
 
@@
 % 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
-Since then, the expansion trend of agriculture has been contained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market.
-In addition, most laws and regulations have been gradually implemented (\textit{SI Appendix} Table 3).
+Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market.
+In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 3).
 For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.
@@
 	\caption{
-		Transition framework of the water utilization regime towards natural-social binary cycle.
-		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
+		Transition framework of the water utilization regime towards nature-society dualistic water cycle.
+		\textbf{A. Natural cycle:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
 		\textbf{B. Local cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
-		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role.
-What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle.
+		However, as their ecological services generated through the socio-economic cycle, water resource plays a non-provisioning role.
+What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
 		\textbf{C.
-Regional cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
+Regional cycle:} Entering this phase, with further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
 Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
@@
 % 与社会-自然二元水循环理论
-This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle hypothesis
+This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
 \cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.

### 2020-10-03 tex/main/manuscript.tex
update discussion 2

@@
 	\centering
-	\includegraphics[width=0.85\linewidth]{../../figures/main/framework.jpg}
+	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
 	\caption{
@@
 \subsection*{Water utilization regimes}
-% 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
-\begin{figure}%[htbp]
+
+\begin{figure}[h!]
 	\centering
@@
 	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
-	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
+	\textbf{C,} changes of the IWRU within three periods, which have different main contributors.
 	}
@@
 \end{figure}
+
+% 这一节主要展示IWRU的变化趋势和WUR的划分
+With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
 % 接下来分句介绍每个阶段的特征
@@
 
+% 上述过渡过程与稳态转换的关联可能是普遍的
+The association between the above transition process and the regime shifts may be pervasive.
 % 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
@@
 % 与社会-自然二元水循环理论
-This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
+This social water cycle has linked to the natural water cycle through water utilization, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
 \cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
 % 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
-According to our results, regime shifts of water utilization, as transition phases in three related dimensions induced by social development, are of the most important characteristics towards natural-social dualistic cycle
+According to our results, regime shifts of water utilization, with changing in three related dimensions induced by social development, are of the most important characteristics towards natural-social dualistic cycle
 \cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
@@
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
-Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution. 
+Throughout the transition towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of changes. 
 % 水资源压力
-(1) Firstly, although stresses on water resources increases by economic expansion boosting water demands, socio-economic progress responding to resource scarcity by better management and efficiency.
-Water resources were becoming more scarce in the Yellow River Basin from P1 to P3, but the expansion of farmland, the construction of reservoirs, and the increase in water use efficiency became responses to different water utilization stresses in aspects (Figure~\ref{fig:Causes}).
+(1) Firstly, although stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency.
+Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig.
+S3).
+However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles in different aspects (Figure~\ref{fig:Causes}).
 Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
@@
 % 水资源格局
-(3) Last, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
+(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
 In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
-However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}.
+However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}.
 The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.
@@
 % 综上所述
-By combining the above three dimensions, these changes gradually transformed water utilization regimes in a “natural cycle” (Figure~\ref{fig:summary}A) to one in local or regional cycle (Figure~\ref{fig:summary} B and C), towards dualistic water cycle.
+By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural cycle'' (Figure~\ref{fig:summary}A) to one in local or regional cycle (Figure~\ref{fig:summary} B and C), towards a natural-society dualistic water cycle.
 In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework.
-For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural phases, rapid developments and integrated management regimes.
+For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes.
 \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
-In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal, for identify regime shifts of water utilization.
+In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal in interpreting regime shifts of water utilization.
 
-\subsection*{Dilemmas and future directions}
+\section*{Dilemmas and future directions}
 % 对于可持续科学，认识这种稳态的变化很重要

### 2020-10-03 tex/main/manuscript.tex
update dilemmas and future directions

@@
 % 转型应对陷阱
-A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
+A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
 % 我们的框架有助于理解和识别
-Since our transition framework can identify regime shifts of water utilization, it may help to predict possible dilemmas in development.
+Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/big_rivers.pdf}
+	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
 	\caption{
@@
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
-According to case studies around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
+According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-In the Yellow River Basin, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
+In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
 The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig.
@@
 % 后来摆脱了资源陷阱（表现形式 xxx）。
-To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices (\textit{SI Appendix} Methods S5).
-These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the “resource dilemma”.
-
+To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices. 
 % 一段有关87分水方案的介绍
@@
 Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}.
-
+These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
 % 资源困局可能普遍存在
@@
 \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
-% 结构困局可能普遍存在
+% 通过协同治理来摆脱困局也普遍存在
 Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g.
-Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017}.
+Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017,unep-dhiTransboundaryRiverBasins2016}.
 
+% 此外，即使发展极大提升了用水效率，黄河流域的困境也并没能完全解决。
+In addition, further dilemmas of the YRB has not been completely solved though water use efficiency greatly improved by development.
 % 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
-However, basins still face structural dilemmas and require further transformation according to changes within the regional cycle of water utilization. 
-Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency (i.e.
-decline in water use intensity) has been accompanied by a resurgence in irrigated area, resulting in an unabated and weak upward trend in water stress \cite{graftonParadoxIrrigationEfficiency2018}.
+% Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
+Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency has been accompanied by re-growths in irrigated area, still resulting in an unabated and weak upward trend in water resources stress \cite{graftonParadoxIrrigationEfficiency2018}.
 % 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
 Secondly, the changing priority between non-provisioning (i.e.
-industry and urban services) and provisioning (i.e.
-domestic and irrigation water use) is stagnating (see Figure~\ref{fig:dimensions}E) because of rigidify in the industrial structure.
-At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly (supplementary Fig. S4). 
+industry or services) and provisioning (i.e.
+domestic and irrigation water use) may rigidify the flexibility of water use, since domestic water use and thermal water use growth rapidly (supplementary Fig.
+S4).
 % 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
@@
 Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.
-Therefore, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin \cite{scoonesTransformationsSustainabilityCombining2020a}.
+Therefore, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin, because development is not a panacea for the dilemmas \cite{scoonesTransformationsSustainabilityCombining2020a}.
 

### 2020-10-03 tex/main/manuscript.tex
fix some minor language errors

@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
 	\centering
@@
 		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
-Red ones denote hub reservoirs in the basin, which plays a role in bainsal integrated water management.
+Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management.
 Size of the points indicates their magnitude of water storage capacities.
@@
 % 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
-After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.S8).
+After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.
+S8).
 % 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
@@
 	\subsubsection*{Sub-indicator of configurations}
-	To description of configurations between regions or sections, we designed an indicator by imitation of information entropy (Allocational Entropy Metric, see supplementary document: Methods S4).
+	To description of configurations between regions or sections, we designed an indicator by imitation of information entropy (Allocation Entropy Metric, see supplementary document: Methods S4).
 Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy).

### 2020-10-03 tex/main/manuscript.tex
add net contributions in methods

@@
 		% TODO 这里补充 ”net contribution“ 的方法介绍
+		% 不同于变化贡献，净贡献不考虑变化方向，旨在表达不同因子对指标的影响力，与变化贡献的计算方式也略有不同：
+		Different from the change contribution, the net contribution does not consider the direction of changes and is intended to express the influence of different factors on the indicator.
+The calculation method is also slightly different from the change contribution:
+
+		$$ Cn_{F} = \frac{|\Delta C_{F}|}{\sum_{i=1}^n |C_{Fi}|} $$
+
+		where $Cn_{F}$ denotes the net contribution of factor $F$, $|\Delta C_{Fi}|$ refers net change of the factor $F$, and $|C_{Fi}|$ refers net change of the factor $F_i$.
+The factor $F_i$ to $F_n$ are $n$ elements in the same level involved in changes of the index.
 }

### 2020-10-03 tex/sup/supplementary_information.tex
update figs in sup

@@
 
-The study area is the Yellow River Basin (YRB, see Fig.
-S1-A), which has experienced the most intense water exploitation and the most dramatic shifts of management regime in China.
-According to the Yellow River Conservancy Commission (YRCC), an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by characteristic of river.
+The study area is the Yellow River Basin (YRB, see Fig. S1-A), which had experienced the most intense water exploitation and the most dramatic shifts of management regime in China. 
+According to the Yellow River Conservancy Commission (YRCC), an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by the characteristic of river.
 However, there is another scheme suggesting that the upstream only refers to river source areas with little human disturbance and high water retention capacity.
-Anyhow, since the socio-economic and natural conditions were considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
+% TODO 这里补充参考文献，黄河上游的划分争议 
+Anyhow, since the socio-economic and natural conditions were both considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
 S1-B).
 Previous studies have also shown that such a division is valid when both social water use and the natural conditions of the basin are considered, as the regions exhibit strong heterogeneity among themselves (see Fig.
-S1-C):
+S1-C) \cite{wangYellowRiverWater2019}:
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/sup/s1_study_area.jpg}
-    \caption{Yellow River Basin}
+    \includegraphics[width=0.8\textwidth]{../../figures/sup/s1_study_area.jpg}
+    % 黄河流域示意图
+    % A. 黄河流域示意图及研究区子区域的划分
+    % B. 黄河主河道的剖面图
+    % C. 典型景观
+    \caption{
+        The study area.
+        \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR: Source Region, UR: Upper Region, MR: Middle Region, DR: Downstream region).
+        \textbf{B.} Profile of main channel of the Yellow River.
+        \textbf{C.} Typical landscapes in different regions in the YRB.
+    }
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/sup/region_differences.jpg}
-    \caption{Different regions}
+    \includegraphics[width=0.8\textwidth]{../../figures/sup/region_differences.jpg}
+    % 黄河流域各区域的基本社会-经济状况和水资源条件差异。
+    \caption{
+        Basic socio-economic status and water resource conditions of different regions in the YRB, the average from 1980 to 2000 shown.
+        \textbf{A.} Proportion of GDP in different industries (primary, secondary or tertiary industry) in different regions.
+        \textbf{B.} Population of urban or rural area in different regions.
+        \textbf{C.} Natural water yield in different regions.
+        \textbf{D.} Total water use in different regions.
+    }
 \end{figure}
@@
     \caption{Water resources in different regions. 
-        \textbf{A,} changing trend of measured runoff, \textbf{B, C and D} average measured runoff and water consumptions within different periods.
-    % TODO 这里增加一个耗水量的图
+        \textbf{A,} changing trend of measured runoff, 
+        \textbf{B, C and D} average measured runoff within different periods.
+        \textbf{E, F and G} average total water consumptions within different periods. 
     }
@@
 % 补充图片6：用水比例
-% TODO 这里只保留堆积图即可，做的更好看点
 \begin{figure}
@@
 % 补充图片7：节水措施
-% TODO 这里增加更丰富的节水措施图
 \begin{figure}
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/saving_water.jpg}
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/saving_water.jpg}
     \caption{
-        technological solutions and water conservation practices in 2013
+        Saving water irrigated area ratio in 2013.
     }
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/ternary.pdf}
+    \includegraphics[width=0.5\textwidth]{../../figures/sup/ternary.pdf}
     \caption{Net contribution of agriculture, industry and services to GDP in different years.}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/outages.jpg}
-    \caption{Severe runoff outages and groundwater depletion}
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/outages.pdf}
+    \caption{Runoff outages records, size of points indicates length of drying up river segments.}
 \end{figure}
@@
 % \end{figure}
-% TODO 这里处理一下地下水的图片，看看地下水是否需要提及
 

### 2020-10-03 tex/sup/supplementary_information.tex
update tables in sup

@@
     3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
-    % TODO 这里应该把所有表格补充完整
+    4. Reservoirs & Hydrological & Points & 1949-2015 & Wang et al. \cite{wangYellowRiverWater2019} \\
+    5. Measured runoff & Hydrological & Points & 1949-2019 & Measured data from YRCC \\
+    6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommissionYellowRiverBasin2013} \\
+    7. History of YRCC & Political & Documents & 1949-2002 & YRCC \cite{ yellowriverarchivesOrganizationalHistoryYellow2004} \\
     \bottomrule
@@
 \begin{table}\centering
-    \caption{Policies and regulations above YRB level.}
+    \caption{Policies and regulations above YRB level which affected the whole basin in water utilization $^a$}
 
@@
     \midrule
-    1. Water Law of PRC & 1988 & NPC $^a$ \\
-    2. Water Law of PRC -revised 1 & 2009 & NPC \\
-    3. Water Law of PRC -revised 2 & 2016 & NPC \\
-    % TODO 这里应该把所有表格补充完整
+    1. Water Law of PRC & 1988 & National People's Congress of the PRC \\
+    2. Water Law of PRC -revised 1 & 2009 & National People's Congress of the PRC \\
+    3. Water Law of PRC -revised 2 & 2016 & National People's Congress of the PRC \\
+    4. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
+    5. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees -revised 1 & 2017 & State Council of the PRC \\
+    6. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
+    7. Yellow River water supply distribution scheme & 1987 & State Council of the PRC \\
+    8. Measures for the Administration of Water Drawing Permits & 2008 & Ministry of Water Resources of the PRC \\
+    9. Measures for the Administration of Water Drawing Permits -revised 1 & 2015 & Ministry of Water Resources of the PRC \\
+    10. Measures for the Administration of Water Drawing Permits -revised 2 & 2017 & Ministry of Water Resources of the PRC \\
+    11. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
+    12. Annual distribution of available water supply of the Yellow River and main stream water dispatching scheme & 1998 & Ministry of Water Resources of the PRC \\
+    13. The Yellow River water dispatching management measures & 1998 & Ministry of Water Resources \\
+    14. Measures for the Implementation of the Yellow River Water Rights Conversion Management & 2004 & Ministry of Water Resources \\
+    15. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
+    16. Measures for the implementation of the water drawing Permit system & 1993 \\ State Council of the PRC \\
+    17. Measures for the demonstration and management of water resources in construction projects & 2002 & Ministry of Water Resources of the PRC \\
+    18. Implementation Opinions on the Reform of Water Conservancy Project Management System & 2006 & State Council of the PRC \\
+
     \bottomrule
@@
 
-    \footnotesize{$^a$ National People's Congress of PRC}
+    \footnotesize{$^a$ If a policy was proposed by multiple legacies, we only choose the highest one to show.}
 \end{table}

### 2020-10-03 tex/sup/supplementary_information.tex
update introduction of sup text

@@
 %% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
-\SItext{This supplementary document consists of three sections and 10 figures.
-Firstly, we introduced our study area, the Yellow River Basin, in the section Methods S1.
-Definition of study area.
+\SItext{This supplementary document consists of four \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables.
+Firstly, we introduced our study area, the Yellow River Basin, and its subdivisions in the section Methods S1.
 Then, we give a detailed description of used datasets and analysis their uncertainties in the section Methods S2.
-Detailed information on dataset and processing.
-Finally, the index along with corresponding indicators are introduced in the section Methods S3.
-Water Utility Regime Index.}
+Further, we introduced how to harmonized different datasets with various spatial and temporal scales in Methods S3.
+Finally, the index along with corresponding indicators are introduced in the section Methods S4.}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
+    \includegraphics[width=0.8\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
     \caption{Water resources in different regions. 

### 2020-10-03 tex/sup/supplementary_information.tex
revised some details in language

@@
 
-\subsection*{Importance of water resource to society within the YRB}
+% \subsection*{Importance of water resource to society within the YRB}
 Water resources make an irreplaceable contribution to the development of society in the YRB.
 Firstly, each aspect of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig.
-S3-A).
-Secondly, their relationships have noticeably changed over the study period.
-In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig.
-S3-B).
+S2-A, B and D).
+% Secondly, their relationships have noticeably changed over the study period. In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig. S3-B).
 
@@
     \item Firstly, the YRB has been subject to strong intervention by human activities since ancient times, while the last 60 years have seen the most dramatic changes.
-Under human influence, the Yellow River's surface runoff, sediment transport, and human water consumption patterns have all undergone multiple regime shifts in the last 60 years (see Fig.
-S4).
-    \item Secondly, landscapes in the YRB have significantly altered by human activities, which can both change the natural and the social water cycle (see Fig.
-S5).
+Under human influence, the Yellow River's surface runoff, sediment transport, and human water consumption patterns have all undergone multiple regime shifts in the last 60 years
+    % \cite{}.
+    % TODO 这里增加参考文献，黄河近六十年的变化 
+    \item Secondly, landscapes in the YRB have significantly altered by human activities, which can both change the natural and the social water cycle.
 For an example, “grain for green” project has produced a significant change of landscapes in the middle region (MR) of YRB.
-With the addition of xxx hectares of forest in an erosion-prone area, water use patterns in the area and surface runoff patterns in the middle and lower reaches have been radically altered.
-    \item Thirdly, a series of management practices have promoted in order to govern the YRB (see Fig.
-S6).
+With the addition forest in an erosion-prone area, water use patterns in the area and surface runoff patterns in the middle and lower reaches have been radically altered.
+    % TODO 这里增加参考文献  景观的变化 \cite{}
+    \item Thirdly, a series of management practices have promoted in order to govern the YRB.
 Since the establishment of the Yellow River Water Conservancy Commission in XX, the agency has continued to reform and expand, eventually forming a basin management agency with unified coordination, scheduling and regulatory functions.
-Since the promulgation of the Water Law in xxx, the Ministry of Water Resources, the YRCC and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws.
+Since the promulgation of the Water Law in xxx, the Ministry of Water Resources, the YRCC and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws (see \textit{SI Appendix} Table S2).
 \end{itemize}
@@
 GDP data from the China Macro data in the Wind database, which firstly aggregated from annual reports of the provinces.
-Water resources uses dataset was published by Zhou et al.
+Water resources use dataset was published by Zhou et al.
 \cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in perfects level.
@@
         \item MR: Shanxi and Shaanxi,
-        \item DR: Shandong, Hebei and Henan
+        \item DR: Shandong, Hebei and Henan.
     \end{itemize}
@@
 % 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
-The steady-state index of water resources utilization considers the three most important dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of "how much water", "how to use" and "for whom, for where" respectively.
-%? TODO 这里需要增加参考文献，证明这三个维度是最重要的。
+The steady-state index of water resources utilization considers the three most important dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively.
+% TODO 这里需要增加参考文献，证明这三个维度是最重要的。
 % 无论如何，为了让这些维度能够被量化，我们寻找或发明了共计三个度量指标来对应指示其变化趋势：
-In order for these dimensions to be quantified, we found or invented a total of three metrics corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocational Entropy Metric.
+In order for these dimensions to be quantified, we found or invented a total of three metrics corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.
 
@@
 	There is how much water can be used in a certain basin?
-How much stresses has societies put on the water resources of the basin?
+How many stresses has societies put on the water resources of the basin?
 Various metrics, therefore, proposed for water stress (e.g.
@@
 	%* 其中SFV指数比较有用
-    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses.
-    % TODO 这里也要插入 Qin et al., 的参考文献
+    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses \cite{qinFlexibilityIntensityGlobal2019}.
     %* 该指标从人类开发利用水资源的角度，考虑了影响人类感知水资源压力的三个方面：水资源的总量、水资源变异性、人类利用水资源的灵活性。
 
-\subsection*{Tendentiousness: Non-provisioning share}
+\subsection*{Priority: Non-provisioning share}
     %* 从消耗水 到 利用水
@@
     How to use water resources?
-XXX et al.
-put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption products is the main use of water resources, and can flow with trade.
-However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related products and services.
-Today, the world's non-product form of water supply to human beings has reached XX\%, including XXXXXX and other ways, the human society is occurring from "consumption of water" to "use of water" tilt.
+There has been put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption provisions is the main use of water resources, and can flow with trade.
+However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related provisions and services.
+Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is occurring from ``consumption of water'' to ``use of water'' tilt.
     % TODO 这里要补充一些材料
     % *这里我们使用非用于供给性的水资源量所占的比例作为指标，即:
-    Here, we use Non-Provisioning Shares (NPS) of used water resources as an metric to indicate tendentiousness of water utility:
+    Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate priority of water utility:
     $$ NPS_{ij} = \frac{WU_{indirect, i, j}}{WU_{direct, i, j} + WU_{undirect, i, j}} $$
@@
     %* 直接用水和非直接用水
-    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 Tendentiousness 的变化。
+    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 priority 的变化。
     % TODO 这里要补充一些材料 Li 2020，虚拟水贸易，水粮食能源的联结
-    In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as supply water.
-Correspondingly, non-supply water is often industrial water, mainly energy water.
-Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which supply water is often the key to support the production of agricultural products, while non-supply water is more involved in industrial and other social processes.
+    In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as provisioning water.
+Correspondingly, non-provisioning water is often industrial water, mainly energy water.
+Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which provisioning water is often the key to support the production of agricultural products, while non-provisioning water is more involved in industrial and other social processes.
 For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade.
 But if industrial consumption is taken into account, China is exporting virtual water.
-However, as a river basin with high degree of water resource scarcity, the tradeoff between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of tendentientitreating with water.
+However, as a river basin with high degree of water resource scarcity, the trade-off between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of priority with water.
 
-\subsection*{Pattern: Allocational Entropy Metric}
+\subsection*{Configuration: Allocation Entropy Metric}
     %* 哪里利用水资源？  
@@
     %! 这里的表述需要好好思考一下
-    The allocation of water resources has always been a difficult problem, requiring tradeoffs between upstream and downstream and between different water sectors, but there is still a lack of relevant indicators to quantify.
-Here we have designed a "distribution entropy index", which can simply and directly express the pattern of water allocation (which tends to be more evenly distributed or more focused on a certain region).
+    The allocation of water resources has always been a difficult problem, requiring trade-offs between upstream and downstream and between different water sectors, but there is still a lack of relevant indicators to quantify.
+Here we have designed a ``distribution entropy index'', which can simply and directly express the configuration of water allocation (which tends to be more evenly distributed or more focused on a certain region).
 We imitate the idea of information entropy in physics.
@@
     % 该指标将不同区域（SR, UR, MR, DR）和不同部门（农业、工业、服务业、人居）消耗的水资源 Water Use (WU) 视做观察的结果，计算完全平均分配水资源时候的水资源分配熵作为最大值，再计算实际水资源分配最大熵与实际熵的比值，以表示水资源分配的格局多大程度上偏离平均分配。
-    The indicators will be different areas (SR, UR, MR, DR) and different departments (agriculture, industry, service industry, human settlements) of Water consumption of Water Use (WU) as observations, calculation completely when the average allocation of Water resources allocation of Water resources as the maximum entropy, and the actual Water distribution of the ratio of the maximum entropy and the actual entropy, to show the pattern of Water resources allocation how much deviation from the average allocation, i.e.:
+    The indicators will be different areas (SR, UR, MR, DR) and different departments (agriculture, industry, service industry, human settlements) of Water consumption of Water Use (WU) as observations, calculation completely when the average allocation of Water resources allocation of Water resources as the maximum entropy, and the actual Water distribution of the ratio of the maximum entropy and the actual entropy, to show the configuration of Water resources allocation how much deviation from the average allocation, i.e.:
 
@@
 For river basin is located in the same country, from the exploitation of water resources for development between regional opportunities are equal, the actual use of water resources depends more on their own economic strength, so consider don't ideal is conditioned by the actual economic situation, between the four areas of water resources should be fair (on average) distribution (entropy).
-But at the same time, due to the wide existence of geographical differences and division of labor, different regions have their comparative advantages, which is the key factor restricting which water resources are allocated to in the water industry theoretically.
+But at the same time, due to the wide existence of geographical differences and division of labour, different regions have their comparative advantages, which is the key factor restricting which water resources are allocated to in the water industry theoretically.
 Therefore, the distribution of water resources among departments in a specific region will show an overall trend of increasing differences (entropy reduction) in an ideal situation.
-At the same time, the division of labor will emerge along with the comparative advantage, so that different regions have their own advantageous departments (compared with the average level of the river basin).
+At the same time, the division of labour will emerge along with the comparative advantage, so that different regions have their own advantageous departments (compared with the average level of the river basin).
 
@@
     3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
-    4. Reservoirs & Hydrological & Points & 1949-2015 & Wang et al. \cite{wangYellowRiverWater2019} \\
-    5. Measured runoff & Hydrological & Points & 1949-2019 & Measured data from YRCC \\
+    4. Reservoirs & Hydrological & Location & 1949-2015 & Wang et al. \cite{wangYellowRiverWater2019} \\
+    5. Measured runoff & Hydrological & Location & 1949-2019 & Measured data from YRCC \\
     6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommissionYellowRiverBasin2013} \\

### 2020-10-09 tex/main/manuscript.tex
update tables in sup
change abstract and title

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Universal regime transition for water resources utilization in developing river basins}
+\title{Regime transition identification for water utilization in river basin developments}
 
@@
 We propose a new method with an integrated index to detect water utilization regimes and applying it to the Yellow River Basin, a typical overexploited basin in China.
-After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a universal transition framework.
+After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a general transition framework.
 By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories.
@@
 \begin{abstract}
-	From agrarian to industrial societies, humans have harnessed ecosystems over rivers basins around the world, while using water resources as blood that sustains social developments. 
-	Although relations between societies and water resources keep changing throughout, there is still lacking effective methods to detect related regimes of water resources utilization, with much fewer attempts to develop theoretical framework to explain their transitions as well.
-	Here, by integrating three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
-	By applying this index to the Yellow River Basin, China, our results suggest three water utilization regimes in developing over half a century, whose shifts led by various but pervasive causes.
-	Based on that, we summarized a universal transition framework which gives a sketch of relationships between human societies and their water utilization, as a useful guideline for big river basins to develop in a coordinated way.
+	For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
+	Here, considering three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
+	By applying this index to the Yellow River Basin, China, our results suggest there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
+	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework of relationships associated regime shifts with developments.
+	By predicting widespread development dilemmas in transition regimes of water utilization, it can be a useful guideline for big river basins to develop in a coordinated way.
 \end{abstract}
@@
 % 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
+However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
 % TODO 这里增加参考文献，人类对水循环的改造 
@@
 
-%tag 结果2
-\subsection*{Differences between water utilization regimes}
-% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
-The differences between the water utilization regimes are reflected in changes of all three dimensions.
-\begin{figure*}%[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
-	\caption{
-		Changes in different dimensions of water resources utilization regimes and their main contributors.
-		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
-		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
-		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
-		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
-		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
-		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
-		}
-	\label{fig:dimensions}
-\end{figure*}
-% 从阶段一到阶段二，水资源压力的变化最为明显
-Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).
-% 1. 水资源丰富，耗水量少且灵活用水
-In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig.
+% %tag 结果2
+% \subsection*{Differences between water utilization regimes}
+% % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
+% The differences between the water utilization regimes are reflected in changes of all three dimensions.
+
+% % 从阶段一到阶段二，水资源压力的变化最为明显
+% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).
+% % 1. 水资源丰富，耗水量少且灵活用水
+% In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig.
 S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig.
@@
 
-% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts.
-% 首先是用水比例的变化
-Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
-% 再讨论用水格局的变化
-However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
+% % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
+% On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts.
+% % 首先是用水比例的变化
+% Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
+% % 再讨论用水格局的变化
+% However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
 
@@
 
-\begin{figure}%[htbp]
+\begin{figure}[th!]
 	\centering
@@
 
-\subsection*{Interpret of regime shifts within YRB}
+\subsection*{Shifted regimes with development}
 % 我们发明的指数能将三个维度的变化捕捉到。
@@
 Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market.
-In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 3).
+In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2).
 For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.
@@
 
-\subsection*{Transition framework of water utilization}
+\subsection*{Regime transition framework}
 
-\begin{figure*}[thbp]
+\begin{figure*}[th!]
 	\centering
@@
 Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
-
-% TODO 这里把图改成全球大河流域的资源问题类型图
-\begin{figure}%[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
-	\caption{
-		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
-		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure.
-Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
-	}
-	\label{fig:traps}
-\end{figure}
-
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。

### 2020-10-09 tex/sup/supplementary_information.tex
change abstract and title

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
+	\caption{
+		Changes in different dimensions of water resources utilization regimes and their main contributors.
+		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
+		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
+		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
+		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
+		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+		}
+	\label{fig:dimensions}
+\end{figure}
+
 % 补充图片4：水资源灵活性
@@
 
-% %% 表格
-% \begin{table}\centering
-% \caption{This is a table}
-
-% % 表格
-% \begin{tabular}{lrrrr}
-% Species & CBS & CV & G3 \\
-% \midrule
-% 1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
-% 2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
-% 3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
+\begin{figure}%[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
+	\caption{
+		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
+		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure.
+Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
+	}
+	\label{fig:traps}
+\end{figure}
 

### 2020-10-09 tex/main/manuscript.tex
refine the introduction section

@@
 % Regime 和 Regime shift 的定义。
-Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018, schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
+Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
 % 人水系统中的水资源功能
@@
 % Regime 过渡性的存在
-As a result, most large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern.
+As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization.
 % TODO 这里需要安排参考文献，大河流域的发展历程
-% 过渡性有助于理解流域存在的问题
-Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
-% 对过渡性的研究还很少
-Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.
+% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
+Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
+
+% 这里删掉的部分
+% % 过渡性有助于理解流域存在的问题
+% Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
+% % 对过渡性的研究还很少
+% Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.
 
@@
 % 前人已经从不同维度刻画了人水关系.
-Development of societies by using water resources has been going on for at least thousands of years.
-Although its regime shifts and transition phases are not fully understood yet, features of water utilization has been depicted and studied from different perspectives.
+Features of water utilization has been depicted and studied from various intertwined perspectives so far.
 % 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
 Firstly, water stresses are of increasing importance and concerns because of scarcity.
-Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use during the last century, while store of water resource in reservoirs are helpful to relief of
+Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
 % 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
-Secondly, as the need of industry, services and ecology developments, priority of water utilization changed with. 
-Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths in economy profits of industry or services and their priority in water consumption, leading potential conflicts between different sectors
+Secondly, as the need of developments, priority of water utilization changed with and there are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
 % 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
-Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by economically competitive sectors, configuration also plays as an important aspect.
+Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
 % 全球总的取水量很少，但缺水地区很多
-While only 10\% of available water is withdrawn on global average, about 30\% of population settles in highly water-stressed regions with vary dominated water demands
+As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
 \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
-% 此外，人类活动还在改变这一格局
-Human activities further affect this configuration, as positive impacts mostly occur in upper regions whereas aggravated downstream, though most governments are trying to control this situation. 
-\cite{veldkampWaterScarcityHotspots2017}. 
 % 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
@@
 % 使用案例研究
-Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, with change points detection and contribution decomposition methods following.
-% 指出发展困局
-In addition, combining data analysis, we identify drivers of the regime shifts. 
+Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes shifts and their drivers in this typical basin of anthropogenic impacts.
 % 最后总结出一般性框架
-Finally, refer to the existing theories, we summarized a universal transition framework of water utilization regimes, which can be a useful guideline for basins to predict development dilemmas and to develop in a coordinated way.
+Finally, we proposed a transition phases framework of development echoing to the regime shifts, which can be a useful guideline for basins to predict dilemmas in water utilization and to develop in a coordinated way.
 

### 2020-10-09 tex/main/manuscript.tex
refine the methods section

@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and configuration of the water utilization had slight negative contribution (-0.048 and -0.09 in change contributions, 5.6\% and 10.7\% in net contributions, respectively).
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (83.7\%), while priority and configuration of the water utilization had slight negative contribution (5.6\% and 10.7\%).
 % 第二阶段
-In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and configuration of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636 change contribution and 50.2\% net contribution).
+In the second period (P2, 1979-1994), though increased positive contributions of priority and configuration (27.8\% and 22.0\% respectively), the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (50.2\% contribution but in negative).
 % 第三阶段
-However, as the further increasing of positive contributions of water utilization priority (+0.485 change contribution and 36.1\% net contribution) and configuration (+0.515 and 38.3\%, corresponding), and decelerations of water stresses (-0.344 change contribution, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+However, as the further increasing of positive contributions of priority (36.1\%) and configuration (38.3\%), and decreases of water stresses in negative contribution (25.6\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is priority; and P3 is configuration.
+As a result, each period has a different most striking positive contributor to IWRU: P1 is stress (83.7\%); P2 is priority (27.8\%); and P3 is configuration (38.3\%).
 
-% 用水三个维度的组合呈现出阶段特征明显
-Combining these three dimensions' net contribution (differ from change contributions, see \textit{Methods}) to IWRU further, ratios of the contributions of the three dimensions clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
+% 三个维度（压力、优先性、配置）的在每年也有各自的变化趋势，将三者结合后，呈现出阶段特征明显
+While the above three dimensions (stress, priority and configuration) also have own variation (see \textit{SI Appendix} Methods S4 and Fig.
+SX), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
 \begin{figure}%[htbp]
@@
 	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of net contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration).
-The closer a point to an angle of the triangle, greater the proportion of the net contribution of this dimension.
+	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration).
+The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
 	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C).
-When the points are bellow this line, the net contribution ratio of configuration is lower than that of priority, and vice versa.}
+When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
@@
 At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses.
-After then, it experienced a shift to low stresses since 1978, with a change in the proportion of net contributions between priority and configuration, too.
+After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
 % 第三阶段集中
-Finally, the net contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
+Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
 
@@
 S6).
-Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix}).
+Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).
 
@@
 
-\subsection*{Shifted regimes with development}
+\subsection*{Shifted water utilization regimes with development}
 % 我们发明的指数能将三个维度的变化捕捉到。
@@
 
-In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement, have driven the YRB to change regimes twice between 1965 and 2013, which had been along with social development in different aspects and can be interpreted by a transition process.
+In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement, have driven the YRB to change regimes twice between 1965 and 2013, which had been along with social development in different aspects and can be interpreted as a transition process towards comprehensive water utilization.
 
-\subsection*{Regime transition framework}
+\subsection*{Transition framework towards comprehensive water utilization}
 
@@
 	\caption{
-		Transition framework of the water utilization regime towards nature-society dualistic water cycle.
-		\textbf{A. Natural cycle:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B. Local cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
-		However, as their ecological services generated through the socio-economic cycle, water resource plays a non-provisioning role.
+		Transition framework towards a comprehensive water utilization, where water undertakes more socio-economic functions and needs to be considered holistically.
+Blue paths dominated by a natural water loop while red ones dominated by socio-economic loops.
+		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
+		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+		However, as their ecological services generated through the socio-economic path, water resource are non-provisioning.
 What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
 		\textbf{C.
-Regional cycle:} Entering this phase, with further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
+Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
 Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
@@
 % 上述过渡过程与稳态转换的关联可能是普遍的
-The association between the above transition process and the regime shifts may be pervasive.
-% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
-Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018,falkenmarkUnderstandingWaterResilience2019}.
-% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
-At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
-% 与社会-自然二元水循环理论
-This social water cycle has linked to the natural water cycle through water utilization, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
-\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
-% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
-According to our results, regime shifts of water utilization, with changing in three related dimensions induced by social development, are of the most important characteristics towards natural-social dualistic cycle
-\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
+The association between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic loops are gradually dominating human-water systems in most river basins.
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a universal transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:summary}).
+As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a comprehensive water utilization (Figure~\ref{fig:summary}).
+% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
 
-% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
-Throughout the transition towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of changes. 
+Throughout the transition, three dimensions of water utilization are various in discipline of changes. 
 % 水资源压力
-(1) Firstly, although stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency.
+(1) Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency.
 Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig.
@@
 % 综上所述
-By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural cycle'' (Figure~\ref{fig:summary}A) to one in local or regional cycle (Figure~\ref{fig:summary} B and C), towards a natural-society dualistic water cycle.
+By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary} B and C), towards a comprehensive.
 In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework.
@@
 % 对于可持续科学，认识这种稳态的变化很重要
-For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
+% For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
 % 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
-At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
-% 资源陷阱和失配，导致崩溃
-Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
-\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
-% 转型应对陷阱
-A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
-% 我们的框架有助于理解和识别
+% At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
+% % 资源陷阱和失配，导致崩溃
+% Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
+% \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
+% % 转型应对陷阱
+% A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
+% % 我们的框架有助于理解和识别
 Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
-According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
+According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig.
+S11).
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
 In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
-The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig.
+The resource dilemma revealed after the regime shift, with severe runoff outages(\textit{SI Appendix} Fig.
 S8).
@@
 Here, we constructed the Integrated Water Resources Utilization (IWRU) Index which consists of three dimensions and identified the regime in the changes of the index over time by change points detection.
-Finally, the contribution to changes of IWRU index along with each main indicators were calculated separately for each regime (i.e.
-period).
+Each dimension is reflected by an indicator after normalization.
+Finally, the contribution to changes of IWRU index along with each main indicators were calculated separately for each regime (i.e. period).
 
 	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
-	The Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (stresses, priority and configurations, denoted by sub-indicators correspondingly).
-Assuming they have equal weights, we log-transformed and standardized the three sub-indicators for elimination of differences between indicators.
-It means for each indicator $I_{sub}$, we performed:
-	$$ I' = log(I_{sub}) $$
-	$$ I = (I' - I'_{min}) / (I'_{max}-I'_{min})$$
-	where $I$ is standardized series for $I_{sub}$.
-	Then, since we assumed different relationships between development and sub-indicators, we added them together in equal weights:
-	$$ IWRU = \sum_{i}^3 I'_i $$
-	where $i$ is stress, priority or configuration, and $I'_i$ is standardized sub-indicator of them.
-A brief description of the sub-indicators used to measure each dimension follows (see SI Methods.
-S3 for more details).
+	Assuming they have equal weights, the Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (S: stresses, P: priority and C: configurations, denoted by sub-indicators correspondingly):
+
+	$$ IWRU = I'_T + I'_P - I'_S $$
+
+	% 其中 I 是代表每个维度的每个子指标
+	Where $I'$ is normalized indicator of a certain dimension (P: Priority, C: Configuration, S: Stress).
+The direction of stress is different from the other two dimensions because the expected change of this indicator with social development is different (see \textit{SI Appendix} Methods S4).
+
+	\subsubsection*{Normalization}
+	We log-transformed and standardized the three sub-indicators for elimination of differences between indicators. It means for actual values of each indicator $I_{indicator}$, we performed:
+
+	$$ I' = (I - I_{min}) / (I_{max} - I_{min}) $$
+
+	Where $I$ is log-transformed series of actual values for $I_{F}$ and $F$ can be P: Priority, C: Configuration or S: Stress.
 
 	\subsubsection*{Sub-indicator of Stresses}
-	Humans use technology to continuously manage water resources, so a simple physical water scarcity index cannot reasonably assess water scarcity in the evolution and transition of socio-water systems.
-Therefore, we refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water scarcity in the basin.
-The index takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity \cite{qinFlexibilityIntensityGlobal2019}.
+	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water scarcity in a certain region $SFV_i$ as indicator \cite{qinFlexibilityIntensityGlobal2019}.
+The index takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity:
 
-	To apply this method, we need to combine three metrics following:
+	$$ SFV_i = a * V_i + b $$
+	$$ V_i = \frac{A_i + B_i + C_i}{3} $$
+	$$ a = \frac{1}{V_{i, max} - V_{i, min}}; $$
+	$$ b = \frac{1}{V_{i, min} - V_{i, max}} * V_{i, min} $$
 
-	First for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume, in year $j$ and region $i$:
-	$$ A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}} $$
-	Second for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.
-for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
-	$$ B_{i, j} = \frac{WU_{inflexible}}{R_{i, avg}} $$
-	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
-	$$ C_i = C1_i * (1 - C2_i) $$
-	$$ C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} $$
-	$$ C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} $$
-	$$ C2_{i} = 1, \ if RC >= R_{i, avg} $$
-	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+	where $A_i$, $B_i$, and $C_i$ are sub-indicators of scarcity, flexibility and variability of water in a certain region $i$(see \textit{SI Appendix} Methods S4).
+For the whole basin, we use the average NPS as indicator of stress $I_S$:
 
-	Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate $SFV$ index after normalizing them:
-	$$ V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3} $$
-	$$ a = \frac{1}{V_{max} - V_{min}}; $$
-	$$ b = \frac{1}{V_{min} - V_{max}} * V_{min} $$
-	$$ SFV = a * V + b $$
+	$$ I_S = \frac{1}{n} * \sum_{i=1}^n SFV_{i} $$.
 
 	\subsubsection*{Sub-indicator of priority}
-	To priority, we use non-provisioning shares of water use as an indicator.
+	To priority $I_P$, we use Non-Provisioning Shares (NPS) of water use as an indicator.
 While provisional water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning water use ($WU_{non-pro}$) includes industrial and urban services water uses.
 Then, we can calculate the non-provisioning shares by:
-	$$ NPS_{ij} = \frac{WU_{indirect, i, j}}{WU_{direct, i, j} + WU_{undirect, i, j}} $$
+
+	$$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
+
+	Where $i$ refers a certain region, or the whole basin (i.e. $I_P$ = $NPS_{basin}$).
 
 	\subsubsection*{Sub-indicator of configurations}
-	To description of configurations between regions or sections, we designed an indicator by imitation of information entropy (Allocation Entropy Metric, see supplementary document: Methods S4).
-Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy).
-The ratio between the actual water allocation entropy and this maximum entropy is the allocation entropy index.
-	$$ ratio = \frac{Entropy}{Entropy_{max}} $$
-	where $Entropy$ and $Entropy_{max}$ are entropy and maximum entropy of water distributions, respectively. They can be calculated by:
-	$$ Entropy = \sum_{i=1}^n \sum_{j=1}^m -log(p_{ij}) * p_{ij} $$
-	$$ Entropy_{max} = n * \sum_{j=1}^m -\frac{p_j}{n} * log(\frac{p_j}{n}) $$ 
-	where $p_j$ and $p_ij$ are proportions of water use in sector $j$ and region $i$:
-	$$ p_j = \frac{\sum_{i=1}^n WU_j}{\sum_{i=1}^n WU} $$
-	$$ p_{ij} = \frac{WU_{ij}} {\sum_{i=1}^n \sum_{j=1}^m WU_{ij}} $$
-	where $n$ is the total number of regions ($n=4$ here, see supplementary Methods. S1) and $m$ is the total number of sectors ($m=4$ here, see supplementary Methods. S2).
+	To description of configurations $I_C$, we designed an indicator by imitation of information entropy, called Configuration Entropy Metric (CEL).
+CEL is a metric to measure the degree of evenness of water configuration (see \textit{SI Appendix} Methods S4), basin development is often accompanied by the reduction of regional differences and sectors' differences in the whole basin, but there is a complement of sectors between regions, i.e.:
+
+	$$ I_C = \frac{CEL_{r} * CEL_{s}}{CEL_{rs}} $$
+
+	where $CEL_{r}$ and $CEL_{s}$ are Configuration Entropy Metric in different regions and different sectors.
+$CEL_{rs}$ is differences between sectors in a certain region to the whole basin (see \textit{SI Appendix} Methods S4).
 
@@
 	\subsection*{Contribution decomposition}
-	\subsubsection*{Change contributions}
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($S$), priority ($T$) and configuration ($P$) (indicated by their own index respectively, see Water utilization regime index and supplementary Methods.
-S3):
-		$$ IWRU = T * P * S ^ {-1} $$
-		Take the logarithm of both sides then, we get:
-		$$ ln(IWRU) = ln(S) + ln(T) - ln(P) $$
-		Since the changes of IWRU $\Delta IWRU$ can be expressed as $\Delta IWRU = ln(IWRU_2) - ln(IWRU_1)$, where $IWRU_2$ and $IWRU_1$ are ending and beginning values of IWRU in a certain time period, combining the above equations we can get:
-		$$ \Delta IWRU = ln(\frac{S_1}{S_2}) + ln(\frac{T_2}{T_1}) + ln(\frac{P_2}{P_1}) = -\Delta S + \Delta T + \Delta P $$
-		Then, we can calculate contributions $C_F$ of a certain factor $F$ in a certain period by:
-		$$ C_{F} = \frac{|\Delta C_{F}|}{\Delta IWRU}$$
+Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($I_S$), priority ($I_P$) and configuration ($I_C$) (indicated by their own index respectively.
+Since $I_{F}$ refers log-transformed of indicator $F$ ($F$ can be one of P: Priority, C: Configuration or S: Stress), we calculate log-transformed IWRU index $ln(IWRU)$ by:
 
-	\subsubsection*{Net contributions}
-		% TODO 这里补充 ”net contribution“ 的方法介绍
-		% 不同于变化贡献，净贡献不考虑变化方向，旨在表达不同因子对指标的影响力，与变化贡献的计算方式也略有不同：
-		Different from the change contribution, the net contribution does not consider the direction of changes and is intended to express the influence of different factors on the indicator.
-The calculation method is also slightly different from the change contribution:
+		$$ ln(IWRU) = I_{P} + I_{C} - I_{S} $$
+
+		Since the changes of IWRU $\Delta IWRU$ can be expressed as $\Delta IWRU = ln(IWRU_2) - ln(IWRU_1)$, while $IWRU_2$ and $IWRU_1$ are ending and beginning values of IWRU in a certain time period, combining the above equations we can get:
+
+		$$ \Delta IWRU = ln(\frac{S_1}{S_2}) + ln(\frac{T_2}{T_1}) + ln(\frac{P_2}{P_1}) = -\Delta I_P + \Delta I_C + \Delta I_S $$
+
+		Then, we can calculate contributions of a certain factor $F$ in a certain period by:
 
@@
 The factor $F_i$ to $F_n$ are $n$ elements in the same level involved in changes of the index.
+
+	\subsection*{Dataset for calculating indicators}
+	% 为了计算 IWRU ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
+	In order to calculate IWRU, we need to calculate multiple indicators and sub-indicators.
+All the datasets used are listed in the \textit{SI Appendix} table S1.
+A detailed description of the data can be seen in the supplementary materials \textit{SI Appendix} Methods S2.
 }

### 2020-10-09 tex/sup/supplementary_information.tex
refine the methods section

@@
     %* 该指标从人类开发利用水资源的角度，考虑了影响人类感知水资源压力的三个方面：水资源的总量、水资源变异性、人类利用水资源的灵活性。
+
+	To apply this method, we need to combine three metrics following:
+
+	First for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume, in year $j$ and region $i$:
+	$$ A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}} $$
+	Second for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.
+for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
+	$$ B_{i, j} = \frac{WU_{inflexible}}{R_{i, avg}} $$
+	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
+	$$ C_i = C1_i * (1 - C2_i) $$
+	$$ C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} $$
+	$$ C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} $$
+	$$ C2_{i} = 1, \ if RC >= R_{i, avg} $$
+	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+
+	Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate $SFV$ index after normalizing them:
+	$$ V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3} $$
+	$$ a = \frac{1}{V_{max} - V_{min}}; $$
+	$$ b = \frac{1}{V_{min} - V_{max}} * V_{min} $$
+	$$ SFV = a * V + b $$
 

### 2020-10-09 tex/main/manuscript.tex
fixed main issues in main manuscript

@@
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
+With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods} and \textit{SI Appendix} Methods S4) (Figure~\ref{fig:IWRU}).
 % 接下来分句介绍每个阶段的特征
@@
 While the above three dimensions (stress, priority and configuration) also have own variation (see \textit{SI Appendix} Methods S4 and Fig.
-SX), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
+S4), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
 \begin{figure}%[htbp]
@@
 During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
-S6).
+S7).
 Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).
@@
 Although irrigated area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices.
+It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
+S8).
 As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig.
-S6).
+S7).
 
@@
 In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig.
-S5).
+S6).
 Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
-S5).
+S6).
 
@@
 Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
-S8).
+S9).
 % 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
@@
 The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
-In 1972, the Yellow River was cut off for the first time with a length of 310 km for 19 days, and continued to be cut off for many years since then (\textit{SI Appendix} Fig.
-S9).
+In 1972, the Yellow River was dried up for the first time with a length of 310 km for 19 days, and continued to be dried up for many years since then (\textit{SI Appendix} Fig.
+S10).
 % 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
@@
 After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.
-S8).
+S9).
 % 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
@@
 
-In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement, have driven the YRB to change regimes twice between 1965 and 2013, which had been along with social development in different aspects and can be interpreted as a transition process towards comprehensive water utilization.
+In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system.
+Since they have driven the YRB to change regimes twice between 1965 and 2013 along with social development, it can be interpreted as a transition process towards comprehensive water utilization.
 
-\subsection*{Transition framework towards comprehensive water utilization}
+\subsection*{Transition framework in water utilization}
 
@@
 		Transition framework towards a comprehensive water utilization, where water undertakes more socio-economic functions and needs to be considered holistically.
-Blue paths dominated by a natural water loop while red ones dominated by socio-economic loops.
+Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
 		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
@@
 % 上述过渡过程与稳态转换的关联可能是普遍的
-The association between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic loops are gradually dominating human-water systems in most river basins.
+The association between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic pathways are gradually dominating human-water systems in most river basins.
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a comprehensive water utilization (Figure~\ref{fig:summary}).
+As such, we summarized a transition framework, which conceptualizes a general trajectory towards a comprehensive water utilization where regional socio-economic pathways dominating stage by stage (Figure~\ref{fig:summary}).
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
 
-Throughout the transition, three dimensions of water utilization are various in discipline of changes. 
+Throughout the transition phases, three dimensions of water utilization are various in discipline of changes. 
 % 水资源压力
@@
 S3).
-However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles in different aspects (Figure~\ref{fig:Causes}).
+However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles (Figure~\ref{fig:Causes}).
 Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
@@
 (3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
-In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
-However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}.
-The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.
+In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
+However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories\cite{wangThirtyYearsYellow2018}.
+The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.
 
@@
 By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary} B and C), towards a comprehensive.
-In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework.
+In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework.
 For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes.
 \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
-In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal in interpreting regime shifts of water utilization.
+In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.
 
@@
 % 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$.
-The resource dilemma revealed after the regime shift, with severe runoff outages(\textit{SI Appendix} Fig.
-S8).
+After the successive exploitation of agriculture, industry and services (refers from natural phase to a local phase in the framework, Figure~\ref{fig:summary}), it is easy for basins to get into a resource dilemma.
 % 后来摆脱了资源陷阱（表现形式 xxx）。
-To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices. 
+As an example, the YRB proposed a clear transformation towards integrated basin management to get rid of the severe resource dilemma, with several management practices. 
 % 一段有关87分水方案的介绍
@@
 % 资源困局可能普遍存在
-Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
+Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well
+\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
 % 通过协同治理来摆脱困局也普遍存在
-Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g.
-Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017,unep-dhiTransboundaryRiverBasins2016}.
 
 % 此外，即使发展极大提升了用水效率，黄河流域的困境也并没能完全解决。
-In addition, further dilemmas of the YRB has not been completely solved though water use efficiency greatly improved by development.
+In addition, further dilemmas has not been completely solved as basins developments tighter interlinked to the ecosystems after integrated management and move to a regional phase (refers from a local phase to a regional phase in the framework, Figure~\ref{fig:summary}).
 % 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
 % Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
-Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency has been accompanied by re-growths in irrigated area, still resulting in an unabated and weak upward trend in water resources stress \cite{graftonParadoxIrrigationEfficiency2018}.
-% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
+Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency has been accompanied by re-growths in irrigated area, resulting in a usually unabated trend of water resources stress \cite{graftonParadoxIrrigationEfficiency2018}.
 Secondly, the changing priority between non-provisioning (i.e.
 industry or services) and provisioning (i.e.
-domestic and irrigation water use) may rigidify the flexibility of water use, since domestic water use and thermal water use growth rapidly (supplementary Fig.
+domestic and irrigation water use) may rigidify the inflexibility of water use \cite{qinFlexibilityIntensityGlobal2019}.
+Take the YRB as an example again, after getting rid of the resource dilemma, the stresses on water resources were still growing, while inflexible water use (domestic and thermal uses) growth most strikingly (supplementary Fig.
 S4).
+% 这可能对全球的流域都是一个警示，因为
+It can be a warning to river basins around the world in comprehensive developments, since these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.
+
 % 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
 % 总结：整个流域需进一步转型与适应，以实现高质量发展。
-Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.
-Therefore, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin, because development is not a panacea for the dilemmas \cite{scoonesTransformationsSustainabilityCombining2020a}.
+Taken together, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin, because development is not a panacea for every dilemma \cite{scoonesTransformationsSustainabilityCombining2020a}.
 

### 2020-10-15 tex/main/manuscript.tex
update methods -- IWRU section

@@
 \matmethods{
-Here, we constructed the Integrated Water Resources Utilization (IWRU) Index which consists of three dimensions and identified the regime in the changes of the index over time by change points detection.
-Each dimension is reflected by an indicator after normalization.
-Finally, the contribution to changes of IWRU index along with each main indicators were calculated separately for each regime (i.e. period).
+Here, we constructed the Integrated Water Resources Utilization (IWRU) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
+Each dimension is reflected by an independent indicator after normalization, and water utilization regime were characterized by combination of impacts of each dimension in periods.
+In addition, the contribution to changes of IWRU index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).
 
 	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
-	Assuming they have equal weights, the Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (S: stresses, P: priority and C: configurations, denoted by sub-indicators correspondingly):
+	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
+	We believe that water resources utilization system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):
+
+	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
+	\begin{itemize}
+		\item Social development is usually accompanied by a change of priority in water use towards social and economic systems because of higher returns:
+		$$ Dev. \propto P $$
+		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
+		\item Social development usually lead to more complex structure in configuration of water resources, which is a result of division and cooperation between regions and sectors for developing:
+		$$ Dev \propto C $$ 
+		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
+		\item Further social development can only be achieved by effectively alleviating the water resource stresses generated in the process of development through technological means:
+		$$ Dev \propto S^{-1} $$
+	\end{itemize}
+
+	% 将三者合一起，即：
+	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with social development: 
+	$$ Dev. \propto P*C*S^{-1} $$
+
+	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWRU)，使 IWRU 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
+	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension after which, the above equation is transformed into a natural logarithm to facilitate calculation:
+
+	$$ Dev. \propto ln(I_P) + ln(I_C) - ln(I_S) $$
+
+	Assuming they have equal weights, the Integrated Water Resources Utilization (IWRU) Index:
 
@@
 
-	% 其中 I 是代表每个维度的每个子指标
-	Where $I'$ is normalized indicator of a certain dimension (P: Priority, C: Configuration, S: Stress).
-The direction of stress is different from the other two dimensions because the expected change of this indicator with social development is different (see \textit{SI Appendix} Methods S4).
+	where $I'_x$ is a normalization of log-transformed indicator $I_x$ for a certain dimension:
+
+	$$ I'_x = normalize(ln(I_x)) $$
 
@@
 	\subsubsection*{Sub-indicator of configurations}
-	To description of configurations $I_C$, we designed an indicator by imitation of information entropy, called Configuration Entropy Metric (CEL).
-CEL is a metric to measure the degree of evenness of water configuration (see \textit{SI Appendix} Methods S4), basin development is often accompanied by the reduction of regional differences and sectors' differences in the whole basin, but there is a complement of sectors between regions, i.e.:
+	To description of configurations $I_C$, we designed an indicator by imitation of information entropy, called Configuration Entropy Metric (CEM).
+CEM is a metric to measure the degree of evenness of water configuration (see \textit{SI Appendix} Methods S4), basin development is often accompanied by the reduction of regional differences and sectors' differences in the whole basin, but there is a complement of sectors between regions, i.e.:
 
-	$$ I_C = \frac{CEL_{r} * CEL_{s}}{CEL_{rs}} $$
+	$$ I_C = \frac{CEN_{r} * CEN_{s}}{CEN_{rs}} $$
 
-	where $CEL_{r}$ and $CEL_{s}$ are Configuration Entropy Metric in different regions and different sectors.
-$CEL_{rs}$ is differences between sectors in a certain region to the whole basin (see \textit{SI Appendix} Methods S4).
+	where $CEN_{r}$ and $CEN_{s}$ are Configuration Entropy Metric in different regions and different sectors.
+$CEN_{rs}$ is differences between sectors in a certain region to the whole basin (see \textit{SI Appendix} Methods S4).
 

### 2020-10-15 tex/main/manuscript.tex
go over the main text methods

@@
 	\subsubsection*{Normalization}
-	We log-transformed and standardized the three sub-indicators for elimination of differences between indicators. It means for actual values of each indicator $I_{indicator}$, we performed:
+	In fact, we have tested different normalization methods and it makes no difference in change points detection (see \textit{SI Appendix} Methods S5.
+Sensitivity analysis).
+In this study, finally, we performed min-max normalization as the formulation below:
 
-	$$ I' = (I - I_{min}) / (I_{max} - I_{min}) $$
+	$$ normalize(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
 
-	Where $I$ is log-transformed series of actual values for $I_{F}$ and $F$ can be P: Priority, C: Configuration or S: Stress.
+	\subsubsection*{Indicator of Stress}
+	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityIntensityGlobal2019}.
+This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
+For the whole YRB, indicator of stress $I_S$ is the average stress of all regions' SFV-index:
 
-	\subsubsection*{Sub-indicator of Stresses}
-	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water scarcity in a certain region $SFV_i$ as indicator \cite{qinFlexibilityIntensityGlobal2019}.
-The index takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity:
+	$$ I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i} $$
 
-	$$ SFV_i = a * V_i + b $$
-	$$ V_i = \frac{A_i + B_i + C_i}{3} $$
-	$$ a = \frac{1}{V_{i, max} - V_{i, min}}; $$
-	$$ b = \frac{1}{V_{i, min} - V_{i, max}} * V_{i, min} $$
+	Where $SFV_i$ is the SFV-index for region $i$, and $i=1$ to $4$ refers SR, UR, MR, and DR (see \textit{SI Appendix} Methods S1 Definition of study area).
 
-	where $A_i$, $B_i$, and $C_i$ are sub-indicators of scarcity, flexibility and variability of water in a certain region $i$(see \textit{SI Appendix} Methods S4).
-For the whole basin, we use the average NPS as indicator of stress $I_S$:
-
-	$$ I_S = \frac{1}{n} * \sum_{i=1}^n SFV_{i} $$.
-
-	\subsubsection*{Sub-indicator of priority}
+	\subsubsection*{Indicator of priority}
 	To priority $I_P$, we use Non-Provisioning Shares (NPS) of water use as an indicator.
@@
 
-	Where $i$ refers a certain region, or the whole basin (i.e. $I_P$ = $NPS_{basin}$).
+	Where $i$ refers a certain region, or the whole basin, i.e:
 
-	\subsubsection*{Sub-indicator of configurations}
-	To description of configurations $I_C$, we designed an indicator by imitation of information entropy, called Configuration Entropy Metric (CEM).
-CEM is a metric to measure the degree of evenness of water configuration (see \textit{SI Appendix} Methods S4), basin development is often accompanied by the reduction of regional differences and sectors' differences in the whole basin, but there is a complement of sectors between regions, i.e.:
+	$I_P$ = $NPS_{basin}$
 
-	$$ I_C = \frac{CEN_{r} * CEN_{s}}{CEN_{rs}} $$
+	\subsubsection*{Indicator of configurations}
+	%$CEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
+	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
+	To description of configurations $I_C$, we designed an indicator by imitation of information entropy, called Configuration Entropy Metric (CEM), a metric to measure the degree of evenness of water configuration (see \textit{SI Appendix} Methods S4).
+	While our indicator $I_C$ should reflect that with the development of society, water resources configuration is more balanced among regions and generally meets the needs of different sectors (means smaller gaps, too), but different regions have a trend of division of labour among various sectors (with larger gaps):
+
+	$$ I_C = \frac{CEM_{r}*CEM_{s}}{CEM_{rs}}$$
 
@@
 		$$ K_t = max|U_{t, T}|$$
-		where:
+
+		Where:
+
 		$$ U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j) $$
@@
 		The change-point of the series is located at $K_T$, provided that the statistic is significant.
-We use 0.001 as the threshold of p-value, which means the probability of a statistically significant change-point judgment being valid is more than $99.9\%$.
+We use 0.001 as the threshold  of p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), which means the probability of a statistically significant change-point judgment being valid is more than $99.9\%$.
 		Since this method only can return one significant change point, we repeat it Until all significant change points were detected.
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions: stress ($I_S$), priority ($I_P$) and configuration ($I_C$) (indicated by their own index respectively.
-Since $I_{F}$ refers log-transformed of indicator $F$ ($F$ can be one of P: Priority, C: Configuration or S: Stress), we calculate log-transformed IWRU index $ln(IWRU)$ by:
+Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), priority ($I'_P$) and configuration ($I'_C$).
+We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
 
-		$$ ln(IWRU) = I_{P} + I_{C} - I_{S} $$
+		\begin{align*}
+			\Delta IWRU &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
+			&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
+			&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
+		\end{align*}
+		Then, the contribution of dimension $x$ to IWRU's changes can be referred as:
 
-		Since the changes of IWRU $\Delta IWRU$ can be expressed as $\Delta IWRU = ln(IWRU_2) - ln(IWRU_1)$, while $IWRU_2$ and $IWRU_1$ are ending and beginning values of IWRU in a certain time period, combining the above equations we can get:
+		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWRU|} $$
 
-		$$ \Delta IWRU = ln(\frac{S_1}{S_2}) + ln(\frac{T_2}{T_1}) + ln(\frac{P_2}{P_1}) = -\Delta I_P + \Delta I_C + \Delta I_S $$
+		Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
+		$$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
 
-		Then, we can calculate contributions of a certain factor $F$ in a certain period by:
+		or just for contributions (in proportion) within a certain year $j$ to the regime:
+		$$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
 
-		$$ Cn_{F} = \frac{|\Delta C_{F}|}{\sum_{i=1}^n |C_{Fi}|} $$
-
-		where $Cn_{F}$ denotes the net contribution of factor $F$, $|\Delta C_{Fi}|$ refers net change of the factor $F$, and $|C_{Fi}|$ refers net change of the factor $F_i$.
-The factor $F_i$ to $F_n$ are $n$ elements in the same level involved in changes of the index.
-
-	\subsection*{Dataset for calculating indicators}
+	\subsection*{Datasets}
 	% 为了计算 IWRU ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。

### 2020-10-15 tex/sup/supplementary_information.tex
add a sensitivity analysis section

@@
 
+\section*{Sensitive analysis}
+% 一个对断点检测方法普遍的批评是可以通过调整方法的使用来操纵结果，因此我们对断点识别的过程进行了敏感性分析，以证明我们的结果是鲁棒性的。
+A common criticism of breakpoint detection methods is that the results can be manipulated by adjusting the use of the methods, so we conducted a sensitivity analysis of the breakpoint recognition process to demonstrate that our results are robust.
+
+Firstly, we performed three different normalization methods in construction of IWRU for breakpoint detection:
+
+\begin{itemize}
+    \item Min-max normalization:
+        $$ normalized(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
+    \item Mean-max normalization:
+        $$ normalized(X) = (X - X_{mean}) / (X_{max} - X_{min}) $$
+    \item Z-score normalization:
+        $$ normalized(X) = \frac{X-X_{mean}}{X_{std}} $$ 
+\end{itemize}
+
+Where $X$ is a time series and $X_{mean}$, $X_{std}$, $X_{min}$, $X_{max}$ are mean, standard deviation, minimum, maximum of it.
+% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWRU，我们对IWRU的断点检测结果都相同。
+No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWRU breakpoints are the same.
+
+Another place where there is room for manipulation is the choice of significance threshold (i.e.
+threshold of the p-value) in the Pettitt Change points detection method.
+Here, we test 1000 possible p-values between $10^{-6}$ and $0.01$, and most of the results give the same detection in breakpoints.
+It has not given another breakpoint before the threshold is near to $10^{-2}$ (see \textit{SI Appendix} Fig. S12: A). 
+% 不仅如此，当三个断点被检测出时，之前的两个断点仍然存在，且新增加的断点带来阶段划分的趋势差异并不明显
+Not only that, when three breakpoints are detected, the previous two breakpoints still exist (1978 and 1994), and the trend difference of the new breakpoints is not obvious (see \textit{SI Appendix} Fig.
+S12: B and C).
+
+Taken together, the results of three periods in this study with the two breakpoints detected (1978 and 1994) are robust.
+
 % tag 附录图
@@
 
+% 补充图片 11 全球案例
 \begin{figure}%[htbp]
@@
 	\label{fig:traps}
+\end{figure}
+
+补充图片10：地下水
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{../../figures/sup/sensitivity.pdf}
+    \caption{
+        Sensitivity analysis of the threshold of p-values. 
+        \textbf{A.} number of breakpoints in different p-values.
+        \textbf{B.} A typical result of two breakpoints.
+        \textbf{C.} A typical result of three breakpoints.
+    }
 \end{figure}

### 2020-10-15 tex/sup/supplementary_information.tex
add methods in the sup and refined it

@@
 
-\title{Water resource utilization regimes at a basin scale: transition framework and development traps}
+\title{Regime transition identification for water utilization in river basin developments}
 \author{Shuang Song, Shuai Wang, Bojie Fu, Xutong Wu (complete author list)}
@@
 %% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
-\SItext{This supplementary document consists of four \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables.
+\SItext{This supplementary document consists of 5 \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables.
 Firstly, we introduced our study area, the Yellow River Basin, and its subdivisions in the section Methods S1.
@@
 Further, we introduced how to harmonized different datasets with various spatial and temporal scales in Methods S3.
-Finally, the index along with corresponding indicators are introduced in the section Methods S4.}
+Then, the indicators corresponding to the IWRU are introduced in the section Methods S4.
+Finally, we proposed a sensitivity analysis in the section Methods S5, to test the robustness of our results.}
 
@@
 % 指数介绍
-\section*{Methods S4. Water Utility Regime Index}
+\section*{Methods S4. Indicators of IWRU}
 % 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
-The steady-state index of water resources utilization considers the three most important dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively.
+The Integrated Water Resources Utilization (IWRU) index of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively.
 % TODO 这里需要增加参考文献，证明这三个维度是最重要的。
 % 无论如何，为了让这些维度能够被量化，我们寻找或发明了共计三个度量指标来对应指示其变化趋势：
-In order for these dimensions to be quantified, we found or invented a total of three metrics corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.
+In order for these dimensions to be quantified, we found or invented a total of three metrics corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Configuration Entropy Metric.
 
@@
 How many stresses has societies put on the water resources of the basin?
+Answering these questions are crucial for water utilization.
 Various metrics, therefore, proposed for water stress (e.g.
-water scarcity, water stresses index, scarcity-flexibility-variability index), where the dimensions of human impact are increasingly valued.
+water scarcity, water stresses index, scarcity-flexibility-variability index), where the aspect of human impact are increasingly valued.
 	%* 其中SFV指数比较有用
@@
     How to use water resources?
-There has been put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption provisions is the main use of water resources, and can flow with trade.
+    % 这里是一段关于虚拟水的介绍 
+    % There has been put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption provisions is the main use of water resources, and can flow with trade.
 However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related provisions and services.
-Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is occurring from ``consumption of water'' to ``use of water'' tilt.
+    Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
     % TODO 这里要补充一些材料
@@
     Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate priority of water utility:
-    $$ NPS_{ij} = \frac{WU_{indirect, i, j}}{WU_{direct, i, j} + WU_{undirect, i, j}} $$
-    where $i$ refers a certain year and $j$ refers a certain region.
-Thus, $WU_{i,j}$ means the water use in $i$ year and region $j$, where $direct$ part and $undirect$ part indicate provisioning sectors and non-provisioning sectors respectively.
+    $$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
+    Where $i$ refers a certain region, or the whole basin, i.e:
+	$I_P$ = $NPS_{basin}$
     %* 直接用水和非直接用水
@@
 
-\subsection*{Configuration: Allocation Entropy Metric}
+\subsection*{Configuration: Configuration Entropy Metric}
     %* 哪里利用水资源？  
@@
     % * 设计了一个熵指标
-    % 水资源的分配一直是难题，需要在上下游之间、不同用水部门之间进行权衡，但目前还缺少相关的指标进行量化。这里我们设计了一个“分配熵指标”，能够把水资源分配的格局（倾向于平均分配还是更加侧重某一区域）简单直接的表达出来。我们模仿了物理学中信息熵的思想，当信息（这里是水资源）的分配越趋于平均时，其熵在增加，当分配更倾向于某一区域时，该区域获得发展的确定性在增加，导致总体的熵减少。
-    %! 这里的表述需要好好思考一下
-    The allocation of water resources has always been a difficult problem, requiring trade-offs between upstream and downstream and between different water sectors, but there is still a lack of relevant indicators to quantify.
-Here we have designed a ``distribution entropy index'', which can simply and directly express the configuration of water allocation (which tends to be more evenly distributed or more focused on a certain region).
-We imitate the idea of information entropy in physics.
-When the distribution of information (here is water resource) is more equal, its entropy increases; when the distribution is more inclined to a certain region, the certainty of development in that region increases, resulting in the overall entropy decrease.
+    % 水资源的分配一直是难题，需要在上下游之间、不同用水部门之间进行权衡，但目前还缺少相关的指标进行量化。
+    The configuration of water resources has always been a difficult problem, requiring trade-offs between upstream and downstream and even different water sectors.
+However, there is still a lack of comprehensive indicators to quantify.
+    % 这里我们设计了一个“分配熵指标”，能够把水资源分配的格局（倾向于平均分配还是更加侧重某一区域）简单直接的表达出来。
+    Here we designed a ``Configuration Entropy Metric (CEM)'', which can simply and directly express the configuration of water allocation (which tends to be more evenly distributed or more focused on a certain region and sector).
+    % 我们模仿了物理学中信息熵的思想，当信息（这里是水资源）的分配越趋于平均时，其熵在增加，当分配更倾向于某一区域时，该区域获得发展的确定性在增加，导致总体的熵减少。
+    We imitate the idea of information entropy in physics --When the distribution of information (here is water resource) is more equal, its entropy increases.
     %* 这里需不需要一张图表示？
     % 该指标将不同区域（SR, UR, MR, DR）和不同部门（农业、工业、服务业、人居）消耗的水资源 Water Use (WU) 视做观察的结果，计算完全平均分配水资源时候的水资源分配熵作为最大值，再计算实际水资源分配最大熵与实际熵的比值，以表示水资源分配的格局多大程度上偏离平均分配。
-    The indicators will be different areas (SR, UR, MR, DR) and different departments (agriculture, industry, service industry, human settlements) of Water consumption of Water Use (WU) as observations, calculation completely when the average allocation of Water resources allocation of Water resources as the maximum entropy, and the actual Water distribution of the ratio of the maximum entropy and the actual entropy, to show the configuration of Water resources allocation how much deviation from the average allocation, i.e.:
+    The CEM is a metrics for different regions (SR, UR, MR, DR) and different sectors (agriculture, industry, domestic and services) in configurations of Water Use (WU), calculated by:
 
-    $$ ratio = \frac{Entropy}{Entropy_{max}} $$
-	where $Entropy$ and $Entropy_{max}$ are entropy and maximum entropy of water distributions, respectively. They can be calculated by:
-	$$ Entropy = \sum_{i=1}^n \sum_{j=1}^m -log(p_{ij}) * p_{ij} $$
-	$$ Entropy_{max} = n * \sum_{j=1}^m -\frac{p_j}{n} * log(\frac{p_j}{n}) $$ 
-    where $p_j$ and $p_ij$ are proportions of water use in sector $j$ and region $i$:
-	$$ p_j = \frac{\sum_{i=1}^n WU_j}{\sum_{i=1}^n WU} $$
-	$$ p_{ij} = \frac{WU_{ij}} {\sum_{i=1}^n \sum_{j=1}^m WU_{ij}} $$
-	where $n$ is the total number of regions ($n=4$ here, see supplementary Methods. S1) and $m$ is the total number of sectors ($m=4$ here, see supplementary Methods. S2).
+    $$ CEM = \sum_{i=1}^n -log(p_{i}) * p_{i} $$
+
+    Where $i$ represents the unit (a region or a sector) in configuration of water utilization, $p_i$ represents the proportion of water used by the units.
+    For different regions, when water resources are completely evenly used, (i.e. for any region $i$, $p_i = 1/n $), the maximum value of CEM is:
+
+    $$ CEM_{max} = \sum_{i=1}^n -log(p_{i}) * p_{i} = - log(\frac{1}{n}) $$
+
+    $I_C$, an indicator to measure the configuration dimensions of water resources utilization, is composed of three parts:
+
+    $$ I_C = \frac{CEM_{r}*CEM_{s}}{CEM_{rs}}$$
+
+    \begin{itemize}
+        \item Configuration between regions $CEM_r$:
+            $$ CEM_r = \sum_{i=1}^4 -log(p_{i}) * p_{i} $$
+            where $p_i$ is the proportion of region $i$ in water resource usage ($WU_i$), in the total water resource consumption in all regions ($i=1$ to $4$ represents SR, UR, MR, or, DR respectively), i.e.:
+            $$ p_i = \frac{WU_i}{\sum_{i=1}^4 WU_i} $$
+        \item Configuration between sectors $CEM_s$:
+            $$ CEM_s = \sum_{j=1}^3 -log(p_{j}) * p_{j} $$ 
+            where $p_j$ is the proportion of sector $j$ in water resources usage ($WU_j$), in the total water consumption in all sectors ($j=1$ to $3$ represents agriculture, industry and domestic \& services respectively), i.e.:
+            $$ p_j = \frac{WU_j}{\sum_{j=1}^3 WU_j} $$
+        \item Division of sectors' function between regions $CEM_{rs}$
+            $$ CEM_{rs} = \frac{1}{3} * \sum_{j=1}^3 \sum_{i=1}^4 -log(p_{ij} * p_{ij})$$
+            where $p_{ij}$ refers water use proportion of region $i$ in the sector $j$, in the total water consumptions of all regions in this sector, i.e.: 
+            $$ p_{ij} = \frac{WU_ij}{\sum_{i=1}^4 WU_ij} $$
+    \end{itemize}
 
@@
     % TODO 这里一定要想一下，怎么能给人讲的更明白
-    The above indicators take into account the distribution between regions and between industries, but with the development of the basin, the trend of the two is different.
-For river basin is located in the same country, from the exploitation of water resources for development between regional opportunities are equal, the actual use of water resources depends more on their own economic strength, so consider don't ideal is conditioned by the actual economic situation, between the four areas of water resources should be fair (on average) distribution (entropy).
-But at the same time, due to the wide existence of geographical differences and division of labour, different regions have their comparative advantages, which is the key factor restricting which water resources are allocated to in the water industry theoretically.
-Therefore, the distribution of water resources among departments in a specific region will show an overall trend of increasing differences (entropy reduction) in an ideal situation.
-At the same time, the division of labour will emerge along with the comparative advantage, so that different regions have their own advantageous departments (compared with the average level of the river basin).
+    The indicator $I_C$ (Configuration of water utilization), therefore, not only take into account the distribution between different regions and industries, but also considers the complicated professional division with the development of society.
 
-% 最后，我们将三个维度各自的指标在标准化后等权重考虑，组成了 Water Utility Regime Index。
-Finally, we consider the indexes of the three dimensions in the same weight after standardization to form the Water Utility Regime Index.
-
-% TODO 这里补充 SI Appendix Methods S5：简要介绍黄河的管理措施变化
-
+\newpage
 \section*{Sensitive analysis}
@@
     \item Min-max normalization:
-        $$ normalized(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
+        $$ normalized(X) = \frac{X - X_{min}}{X_{max} - X_{min}} $$
     \item Mean-max normalization:
-        $$ normalized(X) = (X - X_{mean}) / (X_{max} - X_{min}) $$
+        $$ normalized(X) = \frac{X - X_{mean}}{X_{max} - X_{min}} $$
     \item Z-score normalization:
@@
 
-补充图片10：地下水
 \begin{figure}

### 2020-10-15 tex/main/manuscript.tex
comment some not important references

@@
 (3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
-In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}.
-However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories\cite{wangThirtyYearsYellow2018}.
+In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation
+% \cite{wangThirtyYearsYellow2018}. 
+However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories 
+%\cite{wangThirtyYearsYellow2018}. 
 The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.
@@
 % 综上所述
-By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary} B and C), towards a comprehensive.
+By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary}B and Figure~\ref{fig:summary}C), towards a comprehensive.
 In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework.
 For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. 
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
+%\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
 In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.
@@
 % 一段有关87分水方案的介绍
-The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}.
-Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}.
+The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors 
+%\cite{wangThirtyYearsYellow2018}. 
+Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account 
+% \cite{wangThirtyYearsYellow2018}. 
 These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 

### 2020-10-24 tex/main/manuscript.tex
fixed by wu's suggestions

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Regime transition identification for water utilization in river basin developments}
+\title{Regime transition identification for water utilization of river basin}
 
@@
 \author[a, b, 1]{Shuai Wang}  % 王老师，通讯
+\author[c, d]{Xutong Wu}  % 武旭同
 \author[a, b]{Bojie Fu}  % 傅老师
-\author[c, d]{Xutong Wu}  % 武旭同
 
@@
 \begin{abstract}
-	For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
-	Here, considering three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
-	By applying this index to the Yellow River Basin, China, our results suggest there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
-	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework of relationships associated regime shifts with developments.
-	By predicting widespread development dilemmas in transition regimes of water utilization, it can be a useful guideline for big river basins to develop in a coordinated way.
+	\label{abstract}
+	% For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
+	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
+	Detecting these abrupt reorganizations of structure and function is crucial for understanding changes of human-water system. 
+	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
+	By applying this index to the Yellow River Basin, China, it suggests that there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
+	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework in interpreting associated changes.
+	By identifying and predicting widespread dilemmas in transition of water utilization, this framework can be a useful guideline for big river basins to develop in a coordinated way.
 \end{abstract}
@@
 
+\label{introduction}
 % tag 引言第一段
@@
 % 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
+However, human's modification has profoundly influenced the water cycle, which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
 % TODO 这里增加参考文献，人类对水循环的改造 
 % 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
-Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}.
+Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, urgently need integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}.
 % 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
-Therefore, understanding the complex relationship between human societies, water resources utilization and their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.
+Since it requires deep understanding of the complex relationships between human societies and water resources utilization, sketching their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.
 
@@
 % 人水系统中的水资源功能
-Water have several key functions within a human-water system, the most important of which is supplying for human societies in further developments based on water utilization. 
+Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization. 
 % 水资源利用 regime shift
-However, interplayed human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
+However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
 \cite{falkenmarkUnderstandingWaterResilience2019}.
 % 稳态转换随着社会发展增加
-These gradual or abrupt drivers triggered regime shifts as societies' development strengthen their interlinks to water utilization and deepening dependences on them.
+These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
 % TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
@@
 % 前人已经从不同维度刻画了人水关系.
-Features of water utilization has been depicted and studied from various intertwined perspectives so far.
+Features of water utilization has been depicted and studied from various intertwined perspectives.
 % 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
-Firstly, water stresses are of increasing importance and concerns because of scarcity.
+Firstly, water stresses are of increasing importance and concerns.
 Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
@@
 % 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
-Secondly, as the need of developments, priority of water utilization changed with and there are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
+Secondly, as the priority of water utilization changed with the need of development. 
+There are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
@@
 % 全球总的取水量很少，但缺水地区很多
-As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
-\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
+% As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
+% \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
 % 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
@@
 % 将三种视角结合，就是“水资源利用体系”。
-As these dimensions haven't been well integrated by quantitative methods, however, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.
+However, these dimensions haven't been well integrated by quantitative methods, and a coherent interpret of regime shifts regard to social development and water utilization is needed.
 
@@
 	\caption{Changes of the IWRU index. 
-	\textbf{A,} two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
-	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
-	\textbf{C,} changes of the IWRU within three periods, which have different main contributors.
+	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWRU have three periods in changing trend.
+	\textbf{B,} Changing slopes of each period.
+	\textbf{C,} Contributions of each dimension to the changes of IWRU within three periods. Stress, priority and configuration are the main positive contributor of P1, P2 and P3, respectively.
 	}
@@
 % 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods} and \textit{SI Appendix} Methods S4) (Figure~\ref{fig:IWRU}).
-% 接下来分句介绍每个阶段的特征
+With two significant points, the changing trend of IWRU index are detected into three periods (Figure~\ref{fig:IWRU}A). 
+Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWRU}B and Figure~\ref{fig:IWRU}C).
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (83.7\%), while priority and configuration of the water utilization had slight negative contribution (5.6\% and 10.7\%).
+In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
 % 第二阶段
-In the second period (P2, 1979-1994), though increased positive contributions of priority and configuration (27.8\% and 22.0\% respectively), the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (50.2\% contribution but in negative).
+In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
 % 第三阶段
-However, as the further increasing of positive contributions of priority (36.1\%) and configuration (38.3\%), and decreases of water stresses in negative contribution (25.6\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
-% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-As a result, each period has a different most striking positive contributor to IWRU: P1 is stress (83.7\%); P2 is priority (27.8\%); and P3 is configuration (38.3\%).
+However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
 
-% 三个维度（压力、优先性、配置）的在每年也有各自的变化趋势，将三者结合后，呈现出阶段特征明显
-While the above three dimensions (stress, priority and configuration) also have own variation (see \textit{SI Appendix} Methods S4 and Fig.
-S4), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
-\begin{figure}%[htbp]
+\begin{figure}[!htbp]
 	\centering
@@
 \end{figure}
+
+% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
+Taken together, each period has the unique most striking positive contributor to IWRU, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
 % 第一阶段到第二阶段
@@
 		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
-		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
+		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
 Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management.
@@
 
-Some main drivers caused the above changes of water utilization regime.
+Various main drivers caused the above changes of water utilization regime.
 % 经济总量提升导致资源耗竭的加速。
-(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A).
+Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A).
 During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
@@
 % 用水关系的变化
-(2) During the P3, irrigation had noticeable changes in its efficiency, whose water consumptions were reduced but still dominant.
-Although irrigated area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+Secondly, efficiency of water utilization changed from the P2 to the P3.
+While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B).
+However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
 It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
@@
 % 不断变化的管理模式。
-(3) Changing water management practice contributed throughout all three periods.
-In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
-In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig.
-S6).
-Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
+Finally, changing water management practice contributed throughout all three periods. 
+According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
+In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
+In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
+Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
 S6).
@@
 
-\subsection*{Shifted water utilization regimes with development}
+\subsection*{Shifted water utilization regimes with the development of society}
 % 我们发明的指数能将三个维度的变化捕捉到。
-The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
+The IWRU index captures the complex human-water feedbacks that links social development and water resources utilization from three dimensions (stress, priority and configuration). 
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
@@
 % 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
-Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
+At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
 S9).
 % 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
-Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
+Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
 % 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
-At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
+At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
 % 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
@@
 % 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
-The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
-In 1972, the Yellow River was dried up for the first time with a length of 310 km for 19 days, and continued to be dried up for many years since then (\textit{SI Appendix} Fig.
+The regime nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
+As the most obvious performance, the Yellow River was dried up for several times since 1972 (\textit{SI Appendix} Fig.
 S10).
 % 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
-Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
+During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
 % 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
-Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market.
+Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy.
 In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2).
@@
 % 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
-The next regime shift was not occurred by a significant increase in water use efficiency in about 1993. 
+The next regime shift was not occurred until a significant increase in water use efficiency since about 1993. 
 % 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
@@
 
-In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system.
-Since they have driven the YRB to change regimes twice between 1965 and 2013 along with social development, it can be interpreted as a transition process towards comprehensive water utilization.
+In short, agricultural expansion, industries and services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system.
+They have driven the YRB to change regimes twice between 1965 and 2013, which can be interpreted as a transition process along with social development.
 
@@
 	\caption{
-		Transition framework towards a comprehensive water utilization, where water undertakes more socio-economic functions and needs to be considered holistically.
-Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
+		\textbf{Transition framework of water utilization.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
 		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
@@
 % 上述过渡过程与稳态转换的关联可能是普遍的
-The association between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic pathways are gradually dominating human-water systems in most river basins.
+The links between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic processes are gradually dominating human-water systems in most river basins.
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework, which conceptualizes a general trajectory towards a comprehensive water utilization where regional socio-economic pathways dominating stage by stage (Figure~\ref{fig:summary}).
+As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage (Figure~\ref{fig:summary}).
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
 
-Throughout the transition phases, three dimensions of water utilization are various in discipline of changes. 
+Three dimensions of water utilization are various throughout the transition. 
 % 水资源压力
-(1) Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency.
+Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can respond to resource scarcity by better management or efficiency.
 Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig.
 S3).
-However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles (Figure~\ref{fig:Causes}).
+However, water utilization stresses changes a lot rather than always increasing, because constructions of reservoir and the increased water use efficiency were all played roles (Figure~\ref{fig:Causes}).
 Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
 % 水资源倾向性
-(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part.
-As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}.
+Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part.
+As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but converted to an energy industry zone now \cite{WillEnergyBases}.
 As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}.
@@
 % 水资源格局
-(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
-In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation
+Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
+In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed configuration.
 % \cite{wangThirtyYearsYellow2018}. 
-However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories 
+% However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories 
 %\cite{wangThirtyYearsYellow2018}. 
-The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.
+% The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.
 
 % 综上所述
-By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary}B and Figure~\ref{fig:summary}C), towards a comprehensive.
+By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary}B and Figure~\ref{fig:summary}C), with socio-economic processes dominated step by step.
 In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework.
 For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. 
-%\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
+\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
 In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.
@@
 % % 我们的框架有助于理解和识别
-Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
+Not only the index helps to identify regime shifts of water utilization, our transition framework also helps in predicting possible dilemmas with the development of society.
 % 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
@@
 % 一段有关87分水方案的介绍
-The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors 
+The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors. 
 %\cite{wangThirtyYearsYellow2018}. 
-Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account 
+Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually formed. 
 % \cite{wangThirtyYearsYellow2018}. 
@@
 % 此外，即使发展极大提升了用水效率，黄河流域的困境也并没能完全解决。
-In addition, further dilemmas has not been completely solved as basins developments tighter interlinked to the ecosystems after integrated management and move to a regional phase (refers from a local phase to a regional phase in the framework, Figure~\ref{fig:summary}).
+In addition, further dilemmas occurred as basins developments tighter interlinked to the ecosystems after integrated management and move to a regional phase (refers from a local phase to a regional phase in the framework, Figure~\ref{fig:summary}).
 % 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
 % Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
-Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency has been accompanied by re-growths in irrigated area, resulting in a usually unabated trend of water resources stress \cite{graftonParadoxIrrigationEfficiency2018}.
+Firstly, significant improvement in agricultural irrigation efficiency has been accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency \cite{graftonParadoxIrrigationEfficiency2018}.
 Secondly, the changing priority between non-provisioning (i.e.
 industry or services) and provisioning (i.e.
-domestic and irrigation water use) may rigidify the inflexibility of water use \cite{qinFlexibilityIntensityGlobal2019}.
+domestic and irrigation water use) may lead the water utilization more inflexible and damage to resilience of the basin \cite{qinFlexibilityIntensityGlobal2019}.
 Take the YRB as an example again, after getting rid of the resource dilemma, the stresses on water resources were still growing, while inflexible water use (domestic and thermal uses) growth most strikingly (supplementary Fig.
@@
 	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	We believe that water resources utilization system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):
+	Water resources utilization system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):
 
@@
 	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWRU)，使 IWRU 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension after which, the above equation is transformed into a natural logarithm to facilitate calculation:
+	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension.
+Then, the above equation is transformed into a natural logarithm to facilitate calculation:
 
@@
 	\subsection*{Change points detection}
-		The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
-		The approach after Pettitt (1979) is commonly applied to detect a single change-point in hydrological series or climate series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
+		% The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
+
+		With no assumptions about the distribution of the data, the Pettitt (1979) approach of changing points detection is commonly applied to detect a single change-point in hydrological series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
 		It tests the $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
@@
 
-		Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
-		$$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
+		% Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
+		% $$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
 
-		or just for contributions (in proportion) within a certain year $j$ to the regime:
-		$$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
+		% or just for contributions (in proportion) within a certain year $j$ to the regime:
+		% $$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
 

### 2020-10-24 tex/main/manuscript.tex
first v. converted to word

@@
 \dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects.
-% TODO 这里增加三篇“大文章”参引
-% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
 However, human's modification has profoundly influenced the water cycle, which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
-% TODO 这里增加参考文献，人类对水循环的改造 
-% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
 Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, urgently need integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}.
-% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
 Since it requires deep understanding of the complex relationships between human societies and water resources utilization, sketching their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.
@@
 Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
-% 人水系统中的水资源功能
 Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization.
-% 水资源利用 regime shift
-However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
-\cite{falkenmarkUnderstandingWaterResilience2019}.
-% 稳态转换随着社会发展增加
+However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use \cite{falkenmarkUnderstandingWaterResilience2019}.
 These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
-% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
-% Regime 过渡性的存在
 As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization.
-% TODO 这里需要安排参考文献，大河流域的发展历程
-% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
 Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
@@
 % 前人已经从不同维度刻画了人水关系.
-Features of water utilization has been depicted and studied from various intertwined perspectives.
-% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
-Firstly, water stresses are of increasing importance and concerns.
-Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
-\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
-% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
+Features of water utilization has been depicted and studied from various intertwined perspectives. Firstly, water stresses are of increasing importance and concerns.
+Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
 Secondly, as the priority of water utilization changed with the need of development.
-There are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
-\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
-% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
+There are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
 Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
-% 全球总的取水量很少，但缺水地区很多
-% As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
-% \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
-% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
 Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
-% 将三种视角结合，就是“水资源利用体系”。
 However, these dimensions haven't been well integrated by quantitative methods, and a coherent interpret of regime shifts regard to social development and water utilization is needed.
@@
 % tag 引言最后一段
-% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
 Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization (Figure~\ref{fig:framework}).
-% 使用案例研究
 Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes shifts and their drivers in this typical basin of anthropogenic impacts.
-% 最后总结出一般性框架
 Finally, we proposed a transition phases framework of development echoing to the regime shifts, which can be a useful guideline for basins to predict dilemmas in water utilization and to develop in a coordinated way.
@@
 	\caption{
-		A framework for understanding the changing relationship between watershed development and water resources.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three dimensions (stress, priority and configuration) of water resources utilization.
+		\textbf{A,} Three dimensions (stress, priority and configuration) of water resources utilization.
 Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis.
@@
 		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B,} the changes after combining the three dimensions.
+		\textbf{B,} The changes after combining the three dimensions.
 Because the above three dimensions are changing with the development of society, their combined water resource utilization status is also different.
@@
 With two significant points, the changing trend of IWRU index are detected into three periods (Figure~\ref{fig:IWRU}A).
-Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWRU}B and Figure~\ref{fig:IWRU}C).
-% 第一阶段
+Not only the slope of changes is various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWRU}B and Figure~\ref{fig:IWRU}C).
 In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
-% 第二阶段
 In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
-% 第三阶段
 However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
@@
 Taken together, each period has the unique most striking positive contributor to IWRU, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
-% 第一阶段到第二阶段
 At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses.
 After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
-% 第三阶段集中
 Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
@@
 Various main drivers caused the above changes of water utilization regime.
-% 经济总量提升导致资源耗竭的加速。
 Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A).
@@
 In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
-In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
+In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig.
+S6).
 Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
@@
 The IWRU index captures the complex human-water feedbacks that links social development and water resources utilization from three dimensions (stress, priority and configuration).
-% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
 Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
-% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
 At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
 S9).
-% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
 Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
-% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
 At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
-% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
 As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.
@@
 S10).
-% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
 During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
-% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
 Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy.
@@
 The next regime shift was not occurred until a significant increase in water use efficiency since about 1993.
-% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
 After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.
 S9).
-% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
 A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture.
@@
 The links between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic processes are gradually dominating human-water systems in most river basins.
-% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
 As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage (Figure~\ref{fig:summary}).
-% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
 
 Three dimensions of water utilization are various throughout the transition.
-% 水资源压力
 Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can respond to resource scarcity by better management or efficiency.
@@
 Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
-% 水资源倾向性
+
 Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part.
@@
 Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
-% 水资源格局
+
 Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
@@
 In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework.
-For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. 
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
+For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
 In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.
@@
 Not only the index helps to identify regime shifts of water utilization, our transition framework also helps in predicting possible dilemmas with the development of society.
-% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
 According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig.
 S11).
-% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
 After the successive exploitation of agriculture, industry and services (refers from natural phase to a local phase in the framework, Figure~\ref{fig:summary}), it is easy for basins to get into a resource dilemma.
-% 后来摆脱了资源陷阱（表现形式 xxx）。
 As an example, the YRB proposed a clear transformation towards integrated basin management to get rid of the severe resource dilemma, with several management practices.
-% 一段有关87分水方案的介绍
-The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors. 
-%\cite{wangThirtyYearsYellow2018}. 
-Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually formed. 
-% \cite{wangThirtyYearsYellow2018}. 
+The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}.
+Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually formed \cite{wangThirtyYearsYellow2018}.
 These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma.
-% 资源困局可能普遍存在
-Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
+Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
 % 通过协同治理来摆脱困局也普遍存在
@@
 In addition, further dilemmas occurred as basins developments tighter interlinked to the ecosystems after integrated management and move to a regional phase (refers from a local phase to a regional phase in the framework, Figure~\ref{fig:summary}).
-% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
-% Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
 Firstly, significant improvement in agricultural irrigation efficiency has been accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency \cite{graftonParadoxIrrigationEfficiency2018}.
@@
 S4).
-% 这可能对全球的流域都是一个警示，因为
 It can be a warning to river basins around the world in comprehensive developments, since these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.
@@
 Each dimension is reflected by an independent indicator after normalization, and water utilization regime were characterized by combination of impacts of each dimension in periods.
-In addition, the contribution to changes of IWRU index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).
+In addition, the contribution to changes of IWRU index along with each main indicators were decomposed and calculated separately for each regime (i.e.
+period).
 

### 2020-10-25 tex/main/manuscript.tex
polished by wu's suggestion v2

--- 2020-10-24 tex/main/manuscript.tex
@@
 	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
-	Detecting these abrupt reorganizations of structure and function is crucial for understanding changes of human-water system. 
+	Detecting these abrupt reorganizations of structure and function is critical to successful future river basin management. 
 	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
@@
 		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
-		However, as their ecological services generated through the socio-economic path, water resource are non-provisioning.
+		\textbf{B.
+Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
 What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
@@
 % 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage (Figure~\ref{fig:summary}).
+As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage.
 % 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
+In the framework, provisioning water utilization (agriculture, domestic or livestock) are dominated at the primal phase and social processes take over dominating with growths of industry and services in the followed phases, with coordinated considerations of water utilization over the whole basin (Figure~\ref{fig:summary}).
 

### 2020-10-25 tex/main/manuscript.tex
update by ShuaiWang suggestions

@@
 	\caption{
-		A framework for understanding the changing relationship between watershed development and water resources.
+		A schematic diagram for understanding the changing relationship between social development and water utilization.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
@@
 
-Various main drivers caused the above changes of water utilization regime.
 % 经济总量提升导致资源耗竭的加速。

### 2020-10-29 tex/main/manuscript.tex
change configuration to allocation, priority to provision

@@
 		\item Social development usually lead to more complex structure in configuration of water resources, which is a result of division and cooperation between regions and sectors for developing:
-		$$ Dev \propto C $$ 
+		$$ Dev \propto A $$ 
 		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
@@
 	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with social development: 
-	$$ Dev. \propto P*C*S^{-1} $$
+	$$ Dev. \propto P*A*S^{-1} $$
 
@@
 
-	$$ Dev. \propto ln(I_P) + ln(I_C) - ln(I_S) $$
+	$$ Dev. \propto ln(I_P) + ln(I_A) - ln(I_S) $$
 
@@
 
-	$$ IWRU = I'_T + I'_P - I'_S $$
+	$$ IWRU = I'_A + I'_P - I'_S $$
 

### 2020-11-04 tex/main/manuscript.tex
reset figure5

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Regime transition identification for water utilization of river basin}
-
+\title{Regime transition identification for water governance of river basin}
+\label{title}
 % Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
@@
 \author[a, b]{Bojie Fu}  % 傅老师
+\author[e]{Yongping Wei} % 尉老师
 
@@
 	P.R. China 
+}
+\affil[e]{ % 昆士兰大学
+	School of Earth and Environmental Sciences, 
+	The University of Queensland, 
+	Brisbane 4067, 
+	Australia
 }
@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Human-water relationship $|$ Water resource management $|$ Water utilization $|$ Sustainable development}
+\keywords{Regime shifts $|$ Sustainability $|$ Instructional fit $|$ Water governance challenges $|$ River basins}
 
@@
 \section*{Discussion}
+\label{Discussion}
+% Water governance challenges along transition regimes
 
+% Implications and future directions
 \subsection*{Shifted water utilization regimes with the development of society}

### 2020-11-09 tex/main/manuscript.tex
change the title
update abstract in gov.

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Regime transition identification for water governance of river basin}
+\title{Regime transition identification for basin's governance challenges of water use}
 \label{title}
@@
 %tag 摘要
+% 为了
 \begin{abstract}
 	\label{abstract}
-	% For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
-	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
-	Detecting these abrupt reorganizations of structure and function is critical to successful future river basin management. 
-	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts.
-	By applying this index to the Yellow River Basin, China, it suggests that there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
-	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework in interpreting associated changes.
-	By identifying and predicting widespread dilemmas in transition of water utilization, this framework can be a useful guideline for big river basins to develop in a coordinated way.
+	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
+	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
+	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
+	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding effective and sustainable water uses.
+	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
+	Here, considering three main dimensions of water governance (stress, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
+	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
+	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by changes of environment, economy and policy.
+	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
+	Based on the results, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
+	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
+	Since resource challenges and structural challenges mainly bother water governance within different regimes, this schema can be a useful guideline for governing big river basins in a coordinated way.
 \end{abstract}

### 2020-11-09 tex/main/manuscript.tex
update significance

@@
 \significancestatement{
+\label{significance}
 	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
@@
 The significance statement appears in the paper itself and is required for all research papers.
-	Water, a key resource to support the sustainable development of human societies, whose natural cycle has been modified by growing socio-economic processes.
-We propose a new method with an integrated index to detect water utilization regimes and applying it to the Yellow River Basin, a typical overexploited basin in China.
-After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a general transition framework.
-By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories.
+	It is a well-known fact that water use plays a key role in development of human societies.
+	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
+	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
+	Since our index integrates various considerations of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
+	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
 }
@@
 	Shuang Song, Xutong Wu wrote the paper.
+	Yongping Wei reviewed the manuscript and proposed major useful advices.
 }

### 2020-11-09 tex/main/manuscript.tex
update keywords -gov.
update introduction-section-1 gov.

@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Sustainability $|$ Instructional fit $|$ Water governance challenges $|$ River basins}
+\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Governance challenges $|$ River basins}
 
@@
 	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
-	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding effective and sustainable water uses.
+	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding efficient and sustainable water uses.
 	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
@@
 
-\label{introduction}
-% tag 引言第一段
+\label{introduction-section-1}
 % 水资源在人类世的重要性，是支持人类社会发展的基础。
 \dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects.
-% TODO 这里增加三篇“大文章”参引
-% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
-However, human's modification has profoundly influenced the water cycle, which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
-% TODO 这里增加参考文献，人类对水循环的改造 
-% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
-Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, urgently need integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}.
-% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
-Since it requires deep understanding of the complex relationships between human societies and water resources utilization, sketching their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.
+%* add references
+% 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
+Because of needs for water use, human's modification has profoundly influenced the natural water cycle and led the trajectory toward hydro-social cycle stage by stage
+\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
+% 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
+Facing this major transformation in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for sustainable water use
+\cite{bestAnthropogenicStressesWorld2019}. 
+% 由于水的治理需要对人类社会和水的使用之间的复杂关系有深刻的理解，因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
+Since water governance requires deep understanding of the complex relationships between human societies and water use, it is crucial to identify its changes induced by the transformation towards hydro-social water cycle, at a basin scales.
 
-% tag 引言第二段
+\label{introduction-section-2}
 % Regime 和 Regime shift 的定义。
-Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
+Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts
+\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
 % 人水系统中的水资源功能

### 2020-11-10 tex/main/manuscript.tex
update introduction gov.

@@
 \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
-% 人水系统中的水资源功能
-Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization. 
-% 水资源利用 regime shift
-However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
-\cite{falkenmarkUnderstandingWaterResilience2019}.
-% 稳态转换随着社会发展增加
-These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
-% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
-% Regime 过渡性的存在
-As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization.
-% TODO 这里需要安排参考文献，大河流域的发展历程
-% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
-Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
+% 因此，识别水治理的制度变迁对于快速变化的流域具有重要意义，可以作为水利用的系统转变的信号，并给可持续发展带来新的挑战。
+Therefore, identifying regime shifts of water governance is important for fast-changing river basins, since it can be a signal of substantive change in water use and lead to new challenges in sustainability at a basin scale.
+% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
+According to United Nations Development Programme (UNDP), three key aspects of water use are decided by water governance: ``How to meet scarcity of water use?
+(stress of water use)'', ``How to balances different water use services?
+(provision of water use)'' and ``How to allocate water equally and efficiently?
+(allocation of water use)''.
+% 这三个问题的答案取决于不同水治理制度下的环境、经济、社会和政治形势。
+Answers of the three questions depend on environmental, economic, social and political situation within different water governance regimes. 
+% 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
+Firstly, effected by environment deteriorate and water uses for economic development, water scarcity can increase stress on society, but management policies such as construction of reservoirs are helpful to relief the stresses.
+\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
+% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
+Secondly, there is trade-off between provisioning water use (such as domestic use and food production uses) and non-provisioning water (such as uses for industrial production or energy), which in need of considerations through water governance
+\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
+% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
+Thirdly, since allocation is basins' concerns, it not only influenced by regional environmental foundations, but also changed by regions' economic comparative advantages, which may effected by social development and policies.
+% 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
+In general, water governance determines the ``stresses'', ``provision'' and ``allocation'' of water use, which all change constantly in the transformation towards the hydro-social water cycle because of changes environmental, economic, social and political situation Figure~\ref{fig:framework}.
+% 因此，通过识别这种变化的稳态转化对理解是很有帮助的。
+Therefore, identification of regime shifts for water governance is critical to understand the complex changes of relationships between human societies and water use.
 
-% 这里删掉的部分
-% % 过渡性有助于理解流域存在的问题
-% Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
-% % 对过渡性的研究还很少
-% Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.
-
-% Tag 引言第三段
-% 前人已经从不同维度刻画了人水关系.
-Features of water utilization has been depicted and studied from various intertwined perspectives.
-% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
-Firstly, water stresses are of increasing importance and concerns.
-Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
-\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
-% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
-Secondly, as the priority of water utilization changed with the need of development. 
-There are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
-\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
-% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
-Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
-% 全球总的取水量很少，但缺水地区很多
-% As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
-% \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
-% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
-Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
-% 将三种视角结合，就是“水资源利用体系”。
-However, these dimensions haven't been well integrated by quantitative methods, and a coherent interpret of regime shifts regard to social development and water utilization is needed.
+% 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
+The Yellow River Basin (YRB, see \textit{Appendix} Methods S1) had experienced the most intense water exploitation and the most dramatic shifts of management regime in China. 
+% 从古至今，黄河一直为水治理带来了异乎寻常的挑战
+Since ancient times, YRB had brought extraordinary challenges to water governance.
+% 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
+Before 1960, the huge sediment loads of the Yellow River in China not only brought flood disasters, but also brought great difficulties to water use of YRB. 
+% 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
+With the implementation of governance measures such as conservation policies, regulation reservoirs, and levees constructions, these issues were effectively contained.
+% 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
+However, more and more serious drying up of the Yellow River brings new challenges to governance and promoted a range of related policies to deal with.
+% 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
+Today, the Yellow River basin still faces serious governance challenges, as regional water demands are still difficult to be fully met and various trade-offs must be involved.
+% 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
+All in all, the transformation of the Yellow River basin has been the most rapid in the world in response to the endless governance challenges brought by the increasing human influence.
+% 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
+Therefore, identifying the regime shifts of water governance for YRB can provide key insights for the sustainable water use governance in the world's great river basins.
 
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization (Figure~\ref{fig:framework}).
+Here, by integrating three above mentioned key questions in water governance, we develop an Integrated Water Governance Index (IWGI) at a basin scale to indicate changes of basin's water governance (Figure~\ref{fig:framework}).
 % 使用案例研究
-Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes shifts and their drivers in this typical basin of anthropogenic impacts.
+Then, by applying this index to the YRB, we analysed the regimes shifts of water governance and their main causes, in this typical basin of rapidly transforming.
 % 最后总结出一般性框架
-Finally, we proposed a transition phases framework of development echoing to the regime shifts, which can be a useful guideline for basins to predict dilemmas in water utilization and to develop in a coordinated way.
+Finally, we summarized a general regime transition schema, echoing to the different challenges in water governance, which can be a useful guideline for basins to develop in a coordinated way.
 

### 2020-11-15 tex/main/manuscript.tex
update discussion section-1

@@
 	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
-	\caption{Changes of the IWRU index. 
-	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWRU have three periods in changing trend.
+	\caption{Changes of the IWGI index. 
+	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
 	\textbf{B,} Changing slopes of each period.
-	\textbf{C,} Contributions of each dimension to the changes of IWRU within three periods. Stress, priority and configuration are the main positive contributor of P1, P2 and P3, respectively.
+	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, priority and configuration are the main positive contributor of P1, P2 and P3, respectively.
 	}
-	\label{fig:IWRU}
+	\label{fig:IWGI}
 \end{figure}
 
-% 这一节主要展示IWRU的变化趋势和WUR的划分
-With two significant points, the changing trend of IWRU index are detected into three periods (Figure~\ref{fig:IWRU}A). 
-Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWRU}B and Figure~\ref{fig:IWRU}C).
+% 这一节主要展示IWGI的变化趋势和WUR的划分
+With two significant points, the changing trend of IWGI index are detected into three periods (Figure~\ref{fig:IWGI}A). 
+Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWGI}B and Figure~\ref{fig:IWGI}C).
 % 第一阶段
-In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
 % 第二阶段
-In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
+In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
 % 第三阶段
-However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
+However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
 
@@
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-Taken together, each period has the unique most striking positive contributor to IWRU, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
+Taken together, each period has the unique most striking positive contributor to IWGI, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
 % 第一阶段到第二阶段
@@
 % % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-% On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts.
+% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts.
 % % 首先是用水比例的变化
@@
 % % 再讨论用水格局的变化
-% However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
+% However, configuration of water utilization, whose contributions to the IWGI are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
 
 % tag 结果3
-\subsection*{Drivers of water utilization regime shifts}
+\subsection*{Causes of water utilization regime shifts}
 
@@
 \label{Discussion}
-% Water governance challenges along transition regimes
 
-% Implications and future directions
-\subsection*{Shifted water utilization regimes with the development of society}
-% 我们发明的指数能将三个维度的变化捕捉到。
-The IWRU index captures the complex human-water feedbacks that links social development and water resources utilization from three dimensions (stress, priority and configuration). 
-% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
-Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
-% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
-At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
+\subsection*{Water governance challenges along transition regimes}
+% 我们发明的指数能同时关注水资源治理的三个关键方面。
+The IWGI index we developed captures three key dimensions of water governance simultaneously: (water use stress, provision of water use and allocation for water use). 
+% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
+Based on that, our results show that three distinct but sequential governance regimes within YRB, whose shifts have been caused by different environmental, economic, social or political aspects.
+% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
+It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
+
+% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
+At the first regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant in this period, governance of water use tended to provide more resources for agriculture (construction of reservoirs and channels for examples).
+% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
+Due to the limited socio-economic influences on the natural water cycle, the governance system with few protective policies encouraged unlimited water withdrawals and storage in the regions requiring water supply, with little consideration of the social equity over the basin.
+% 近80%的地表水用于供应(家庭用水、牲畜用水或粮食生产)，黄河的干涸发生在政权末期，留下了巨大的环境危机。
+With nearly 80\% of surface water used for provisioning (domestic, livestocks' use or food production), drying up of the Yellow River occurred at the end of the regime and left a huge crisis of environment.
+
+% 第二个政权与中国的经济改革相吻合，新兴的工业和服务业打破了农业的主导地位，在新的治理体制下争夺用水。
+The second regime coincided with Chinese economic reform, when the emerging industry and services broke the dominance of agriculture and competed for water use under the new governance regime. 
+% 与此同时，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
+At the same time, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
+% 该制度稳态不仅遏止了用水效率低下的农业的扩张，更出台了一系列政策法规应对水资源压力，并调节用水分配。
+As results, the regime not only stopped the expansion of inefficient agriculture, but also introduced a range of policies and regulations to deal with the stresses of water use and regulate the allocation of water.
+
+% 第三次稳态转换直到1993年左右才由用水效率的显著提升而带来，因为社会经济发展后先进技术的广泛应用。
+The next regime shift was not brought until a significant increase in water use efficiency around 1993, due to the widespread applying of advanced technologies after socio-economic developments. 
+% 而区域社会经济的权衡成为了用水分配的关键，如此时期普及开的水权转换项目就是把节约的农业用水用于工业发展。
+The regional socio-economic trade-off had become the key to water governance in this period, and for an example, the water rights conversion project popularized in this regime is to use the saved agricultural water for industrial developments.
+% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
+However, the water allocating policy (i.g.
+``87 Water Diversion Scheme''), which had helped the YRB get rid of the environmental crisis in the last regime, became the shackle of equity and coordination during this period.
+% 这是因为用水分配方案高度路径依赖，用水方式也更加不灵活，这些成为新的社会经济形势下的治理难题。
+This is because the water allocation scheme is highly path dependent and the way of water use is also more inflexible, both of which have become challenges for governance under the new regime.
+
+% 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
+In general, shifts of the three governance regimes occurred sequentially with the transformation towards the hydro-social cycle, with an obvious transition.
+% 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
+This transition is considered to be pervasive in socio-ecological systems, such as ecosystem services and national economic-social developments, as increasing anthropogenic pressures gradually dominate the world at large.
+% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
+With the typical transition towards a hydro-social water cycle, we find that the regime shifts of water governance echoes the two major challenges globally.
+% 根据前人广泛的总结，目前全球一部分流域正面临着经济发展和资源困境（如缺水和用水困难），而另一些则迫切需要社会政策层面的协调与合作以实现可持续（如跨境河流的用水分配与协作治理）。
+According to the summary of previous studies, some river basins are facing economic development and resource dilemma (such as water shortage and water supplying difficulties), while others are in urgent need of coordination and cooperation at the social policy (such as water disputes and lack of cooperative governance, especially for cross-border rivers).
+% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
+It is very representative that these two kinds of major challenges have occurred successively in the transition of the YRB, accompanied by the transformation of governance regime.
+% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
+Our analysis indicates that the early stage of transition often brings environmental and economic governance challenges, while the later stage of transition is dominated by social and policy challenges.
+% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
+Again, our schema have outlined echoes the four dimensions (economic, environmental, social and political) summarized by UNDP, and two types of global challenges, regarding water governance.
+
+% % 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
+% At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
 S9).
-% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
-Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
-% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
-At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
-% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
-As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.
+% % 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
+% Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
+% % 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
+% At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
+% % 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
+% As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.
 
-% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
-% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
-The regime nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
+% % 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
+% % 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
+% The regime nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
 As the most obvious performance, the Yellow River was dried up for several times since 1972 (\textit{SI Appendix} Fig.
 S10).
-% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
-During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
-% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
-Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy.
+% % 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
+% During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
+% % 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
+% Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy.
 In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2).
@@
 
-% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
-The next regime shift was not occurred until a significant increase in water use efficiency since about 1993. 
-% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
-After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.
+% % 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
+% The next regime shift was not occurred until a significant increase in water use efficiency since about 1993. 
+% % 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
+% After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.
 S9).
-% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
-A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture.
+% % 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
+% A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture.
 As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig.
@@
 
-In short, agricultural expansion, industries and services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system.
+% In short, agricultural expansion, industries and services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system.
 They have driven the YRB to change regimes twice between 1965 and 2013, which can be interpreted as a transition process along with social development.
 
-\subsection*{Transition framework in water utilization}
+\subsection*{Implications and future directions}
 
@@
 \matmethods{
-Here, we constructed the Integrated Water Resources Utilization (IWRU) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
+Here, we constructed the Integrated Water Resources Utilization (IWGI) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
 Each dimension is reflected by an independent indicator after normalization, and water utilization regime were characterized by combination of impacts of each dimension in periods.
-In addition, the contribution to changes of IWRU index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).
+In addition, the contribution to changes of IWGI index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).
 
-	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
+	\subsection*{Integrated Water Resources Utilization (IWGI) Index}
 	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
@@
 
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWRU)，使 IWRU 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
+	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
 	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension.
@@
 
-	Assuming they have equal weights, the Integrated Water Resources Utilization (IWRU) Index:
+	Assuming they have equal weights, the Integrated Water Resources Utilization (IWGI) Index:
 
-	$$ IWRU = I'_A + I'_P - I'_S $$
+	$$ IWGI = I'_A + I'_P - I'_S $$
 
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWRU) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), priority ($I'_P$) and configuration ($I'_C$).
+Use Integrated Water Resources Utilization (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), priority ($I'_P$) and configuration ($I'_C$).
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
@@
 		\begin{align*}
-			\Delta IWRU &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
+			\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
 			&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
@@
 		\end{align*}
-		Then, the contribution of dimension $x$ to IWRU's changes can be referred as:
+		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
 
-		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWRU|} $$
+		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|} $$
 
@@
 	\subsection*{Datasets}
-	% 为了计算 IWRU ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWRU, we need to calculate multiple indicators and sub-indicators.
+	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
+	In order to calculate IWGI, we need to calculate multiple indicators and sub-indicators.
 All the datasets used are listed in the \textit{SI Appendix} table S1.

### 2020-11-17 tex/main/manuscript.tex
changed into governance context  on the whole

@@
 	\caption{
-		A schematic diagram for understanding the changing relationship between social development and water utilization.
+		A schematic diagram for understanding the changing relationship between social development and water governance.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three dimensions (stress, priority and configuration) of water resources utilization.
-Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis.
-(1) Stress of water utilization shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
-(2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies.
-(3) configuration can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
-We presume that water utilization regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development.
+		\textbf{A,} three dimensions (stress, provision and allocation) of water resources governance.
+Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources governance changes along that axis.
+(1) Stress of water governance shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
+(2) provision of water governance can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies.
+(3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
+We presume that water governance regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development.
 		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
 		\textbf{B,} the changes after combining the three dimensions.
-Because the above three dimensions are changing with the development of society, their combined water resource utilization status is also different.
-When abrupt transitions occur during this process, they may indicate a regime shift in water utilization, so we need an indicator to monitor this change.
+Because the above three dimensions are changing with the development of society, their combined water resource governance status is also different.
+When abrupt transitions occur during this process, they may indicate a regime shift in water governance, so we need an indicator to monitor this change.
 	}
@@
 \section*{Results}
-\subsection*{Water utilization regimes}
+\subsection*{Water governance regimes}
 
@@
 	\textbf{B,} Changing slopes of each period.
-	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, priority and configuration are the main positive contributor of P1, P2 and P3, respectively.
+	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
 	}
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while provision and allocation of the water governance had slight negative contribution (-11\% and -20\%).
 % 第二阶段
-In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
+In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
 % 第三阶段
-However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
+However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
 
@@
 	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration).
+	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: provision; C: allocation).
 The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
-	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C).
-When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
+	The red indicator line in this ternary plot denotes 1:1 contributions between provision (P) and allocation (C).
+When the points are bellow this line, the contribution ratio of allocation is lower than that of provision, and vice versa.}
 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
@@
 % 第一阶段到第二阶段
-At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses.
-After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
+At the very beginning (1965) and throughout the whole P1, water governance regime dominated by lower stresses.
+After then, it experienced a shift to high stresses since 1978, with a change in the proportion of contributions between provision and allocation, too.
 % 第三阶段集中
-Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
+Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
 
 % %tag 结果2
-% \subsection*{Differences between water utilization regimes}
+% \subsection*{Differences between water governance regimes}
 % % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
-% The differences between the water utilization regimes are reflected in changes of all three dimensions.
+% The differences between the water governance regimes are reflected in changes of all three dimensions.
 
 % % 从阶段一到阶段二，水资源压力的变化最为明显
-% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).
+% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water governance stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).
 % % 1. 水资源丰富，耗水量少且灵活用水
 % In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig.
-S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig.
+S3) and most of which were flexible water governance (\textit{SI Appendix} Fig.
 S4).
@@
 S5).
-As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.
+As a result, water governance stress decreases during P1, but begins to rise rapidly in P2.
 
 % % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts.
+% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, provision (Figure~\ref{fig:dimensions}B) and allocation (Figure~\ref{fig:dimensions}C) of water governance were keeping to enlarge their impacts.
 % % 首先是用水比例的变化
-% Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
+% Representing provision of water governance, increasing non-provisioning share of water governance were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
 % % 再讨论用水格局的变化
-% However, configuration of water utilization, whose contributions to the IWGI are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
+% However, allocation of water governance, whose contributions to the IWGI are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
 
 % tag 结果3
-\subsection*{Causes of water utilization regime shifts}
+\subsection*{Causes of water governance regime shifts}
 
@@
 	\caption{
-		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
+		Drivers of water governance regime shifts: economy growths, efficiency changes, and management practices.
 		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
@@
 % 经济总量提升导致资源耗竭的加速。
-Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A).
-During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
+Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision of water use between P1 and P2 (Figure\ref{fig:Causes}A).
+During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant governance way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
 S7).
@@
 % 用水关系的变化
-Secondly, efficiency of water utilization changed from the P2 to the P3.
+Secondly, efficiency of water use changed from the P2 to the P3.
 While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B).
 However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
+It means, water governance ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
 S8).
@@
 % 不断变化的管理模式。
-Finally, changing water management practice contributed throughout all three periods. 
+Finally, water policies and management practices contributed throughout all three periods. 
 According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
@@
 \subsection*{Water governance challenges along transition regimes}
+
+\begin{figure*}[htbp!]
+	\centering
+	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
+	\caption{
+		\textbf{Transition framework of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
+		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
+		\textbf{B.
+Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
+		\textbf{C.
+Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
+Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
+	}
+	\label{fig:summary}
+\end{figure*}
+
 % 我们发明的指数能同时关注水资源治理的三个关键方面。
@@
 
-% % 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
-% At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig.
-S9).
-% % 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
-% Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
-% % 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
-% At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C).
-% % 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
-% As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.
+\subsection*{Implications and future directions}
+\label{Outlook}
 
-% % 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
-% % 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
-% The regime nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff.
-As the most obvious performance, the Yellow River was dried up for several times since 1972 (\textit{SI Appendix} Fig.
-S10).
-% % 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
-% During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
-% % 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
-% Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy.
-In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2).
-For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.
-
-% % 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
-% The next regime shift was not occurred until a significant increase in water use efficiency since about 1993. 
-% % 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
-% After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.
-S9).
-% % 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
-% A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture.
-As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig.
-S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).
-
-% In short, agricultural expansion, industries and services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system.
-They have driven the YRB to change regimes twice between 1965 and 2013, which can be interpreted as a transition process along with social development.
-
-\subsection*{Implications and future directions}
-
-\begin{figure*}[th!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
-	\caption{
-		\textbf{Transition framework of water utilization.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
-		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B.
-Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
-What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
-		\textbf{C.
-Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
-Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
-	}
-	\label{fig:summary}
-\end{figure*}
-
-% 上述过渡过程与稳态转换的关联可能是普遍的
-The links between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic processes are gradually dominating human-water systems in most river basins.
-% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
-As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage.
-% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
-In the framework, provisioning water utilization (agriculture, domestic or livestock) are dominated at the primal phase and social processes take over dominating with growths of industry and services in the followed phases, with coordinated considerations of water utilization over the whole basin (Figure~\ref{fig:summary}).
-
-Three dimensions of water utilization are various throughout the transition. 
-% 水资源压力
-Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can respond to resource scarcity by better management or efficiency.
-Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig.
-S3).
-However, water utilization stresses changes a lot rather than always increasing, because constructions of reservoir and the increased water use efficiency were all played roles (Figure~\ref{fig:Causes}).
-Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
-% 水资源倾向性
-Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part.
-As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but converted to an energy industry zone now \cite{WillEnergyBases}.
-As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}.
-Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
-% 水资源格局
-Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization.
-In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed configuration.
-% \cite{wangThirtyYearsYellow2018}. 
-% However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories 
-%\cite{wangThirtyYearsYellow2018}. 
-% The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.
-
-% 综上所述
-By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary}B and Figure~\ref{fig:summary}C), with socio-economic processes dominated step by step.
-In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework.
-For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. 
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
-In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.
-
-\section*{Dilemmas and future directions}
-% 对于可持续科学，认识这种稳态的变化很重要
-% For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
-% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
-% At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
-% % 资源陷阱和失配，导致崩溃
-% Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
-% \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
-% % 转型应对陷阱
-% A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}.
-% % 我们的框架有助于理解和识别
-Not only the index helps to identify regime shifts of water utilization, our transition framework also helps in predicting possible dilemmas with the development of society.
-% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
-According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig.
-S11).
-% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
-After the successive exploitation of agriculture, industry and services (refers from natural phase to a local phase in the framework, Figure~\ref{fig:summary}), it is easy for basins to get into a resource dilemma.
-% 后来摆脱了资源陷阱（表现形式 xxx）。
-As an example, the YRB proposed a clear transformation towards integrated basin management to get rid of the severe resource dilemma, with several management practices. 
-% 一段有关87分水方案的介绍
-The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors. 
-%\cite{wangThirtyYearsYellow2018}. 
-Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually formed. 
-% \cite{wangThirtyYearsYellow2018}. 
-These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
-% 资源困局可能普遍存在
-Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well
-\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
-% 通过协同治理来摆脱困局也普遍存在
-
-% 此外，即使发展极大提升了用水效率，黄河流域的困境也并没能完全解决。
-In addition, further dilemmas occurred as basins developments tighter interlinked to the ecosystems after integrated management and move to a regional phase (refers from a local phase to a regional phase in the framework, Figure~\ref{fig:summary}).
-% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
-% Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
-Firstly, significant improvement in agricultural irrigation efficiency has been accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency \cite{graftonParadoxIrrigationEfficiency2018}.
-Secondly, the changing priority between non-provisioning (i.e.
-industry or services) and provisioning (i.e.
-domestic and irrigation water use) may lead the water utilization more inflexible and damage to resilience of the basin \cite{qinFlexibilityIntensityGlobal2019}.
-Take the YRB as an example again, after getting rid of the resource dilemma, the stresses on water resources were still growing, while inflexible water use (domestic and thermal uses) growth most strikingly (supplementary Fig.
-S4).
-% 这可能对全球的流域都是一个警示，因为
-It can be a warning to river basins around the world in comprehensive developments, since these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.
-
-% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
-% 总结：整个流域需进一步转型与适应，以实现高质量发展。
-Taken together, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin, because development is not a panacea for every dilemma \cite{scoonesTransformationsSustainabilityCombining2020a}.
+% 我们发展的指数捕捉了水治理的过渡制度，以一种相对全面但简单的方式
+The index we developed (IWGI), captures the transition regimes of water governance with different challenges, in a relatively simple but comprehensive way.
+% 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
+It is important for scientists and decision makers to recognize the changing challenges for water governance, because development is not a panacea for all basin issues regarding sustainability.
+% 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
+For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development provision strategies are still the main guideline to meet them.
+% 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
+Although most large river basins improved water management and efficiency along with development, most studies still pessimistically point out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
+% 总的来说，这可能有两点主要原因。
+Overall, there are probably two main reasons.
+% 首先，效率悖论
+Firstly, significant improvement in agricultural irrigation efficiency is usually accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency
+\cite{graftonParadoxIrrigationEfficiency2018}. 
+% 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
+Secondly, complicated structure of water allocation or provision under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
+\cite{qinFlexibilityIntensityGlobal2019}.
+% 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
+At this point, we need corresponding comprehensive strategies to address the governance challenges, because the heart factors of are beyond the control of any related actor. 
+% 基于对治理稳态的认识，我们可以为应对挑战创造有利条件，让利益相关者实现对社会和环境状况的预期，从而维持流域社会-生态系统的弹性。
+Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and enabling stakeholders to realize their expectations of social and environmental changes, thus maintaining the resilience of the basin's socio-ecosystem.
+% 总的来说，这些都有助于指导流域迈向可持续性。
+Taken together, these have helped guide the basin towards sustainability.
 
@@
 \matmethods{
-Here, we constructed the Integrated Water Resources Utilization (IWGI) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
-Each dimension is reflected by an independent indicator after normalization, and water utilization regime were characterized by combination of impacts of each dimension in periods.
+Here, we constructed the Integrated Water Resources governance (IWGI) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
+Each dimension is reflected by an independent indicator after normalization, and water governance regime were characterized by combination of impacts of each dimension in periods.
 In addition, the contribution to changes of IWGI index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).
 
-	\subsection*{Integrated Water Resources Utilization (IWGI) Index}
+	\subsection*{Integrated Water Resources governance (IWGI) Index}
 	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources utilization system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):
+	Water resources governance system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):
 
@@
 	\begin{itemize}
-		\item Social development is usually accompanied by a change of priority in water use towards social and economic systems because of higher returns:
+		\item Social development is usually accompanied by a change of provision in water use towards social and economic systems because of higher returns:
 		$$ Dev. \propto P $$
 		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item Social development usually lead to more complex structure in configuration of water resources, which is a result of division and cooperation between regions and sectors for developing:
+		\item Social development usually lead to more complex structure in allocation of water resources, which is a result of division and cooperation between regions and sectors for developing:
 		$$ Dev \propto A $$ 
@@
 
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension.
+	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
+	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to provision, allocation and Stress respectively) for each dimension.
 Then, the above equation is transformed into a natural logarithm to facilitate calculation:
@@
 
-	Assuming they have equal weights, the Integrated Water Resources Utilization (IWGI) Index:
+	Assuming they have equal weights, the Integrated Water Resources governance (IWGI) Index:
 
@@
 
-	\subsubsection*{Indicator of priority}
-	To priority $I_P$, we use Non-Provisioning Shares (NPS) of water use as an indicator.
+	\subsubsection*{Indicator of provision}
+	To provision $I_P$, we use Non-Provisioning Shares (NPS) of water use as an indicator.
 While provisional water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning water use ($WU_{non-pro}$) includes industrial and urban services water uses.
@@
 
-	\subsubsection*{Indicator of configurations}
+	\subsubsection*{Indicator of allocations}
 	%$CEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
 	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To description of configurations $I_C$, we designed an indicator by imitation of information entropy, called Configuration Entropy Metric (CEM), a metric to measure the degree of evenness of water configuration (see \textit{SI Appendix} Methods S4).
-	While our indicator $I_C$ should reflect that with the development of society, water resources configuration is more balanced among regions and generally meets the needs of different sectors (means smaller gaps, too), but different regions have a trend of division of labour among various sectors (with larger gaps):
+	To description of allocations $I_C$, we designed an indicator by imitation of information entropy, called allocation Entropy Metric (CEM), a metric to measure the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
+	While our indicator $I_C$ should reflect that with the development of society, water resources allocation is more balanced among regions and generally meets the needs of different sectors (means smaller gaps, too), but different regions have a trend of division of labour among various sectors (with larger gaps):
 
@@
 
-	where $CEN_{r}$ and $CEN_{s}$ are Configuration Entropy Metric in different regions and different sectors.
+	where $CEN_{r}$ and $CEN_{s}$ are allocation Entropy Metric in different regions and different sectors.
 $CEN_{rs}$ is differences between sectors in a certain region to the whole basin (see \textit{SI Appendix} Methods S4).
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources Utilization (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), priority ($I'_P$) and configuration ($I'_C$).
+Use Integrated Water Resources governance (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), provision ($I'_P$) and allocation ($I'_C$).
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:

### 2020-11-18 tex/main/manuscript.tex
update polish introduction

@@
 \author[c, d]{Xutong Wu}  % 武旭同
+\author[e]{Yongping Wei} % 尉老师
 \author[a, b]{Bojie Fu}  % 傅老师
-\author[e]{Yongping Wei} % 尉老师
 
@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Governance challenges $|$ River basins}
+\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Socio-hydrology $|$ Sustainability}
 
@@
 	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
-	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding efficient and sustainable water uses.
+	Since water governance regime decides who gets what water, when and how much, identification for its changes is critical to guiding efficient and sustainable water uses.
 	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
-	Here, considering three main dimensions of water governance (stress, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
+	Here, considering three main dimensions of water governance (storage, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
 	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
-	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by changes of environment, economy and policy.
+	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by environmental, economic social and political changes.
 	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
-	Based on the results, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
+	Based on these, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
 	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
-	Since resource challenges and structural challenges mainly bother water governance within different regimes, this schema can be a useful guideline for governing big river basins in a coordinated way.
+	Since resources and structural challenges of water governance mainly occurred at different stages of transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
 \end{abstract}
@@
 % 水资源在人类世的重要性，是支持人类社会发展的基础。
-\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects.
+\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for Earth system processes, but also supporting development of human societies. 
 %* add references
 % 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
-Because of needs for water use, human's modification has profoundly influenced the natural water cycle and led the trajectory toward hydro-social cycle stage by stage
+Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle, stage by stage
 \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
@@
 \cite{bestAnthropogenicStressesWorld2019}. 
-% 由于水的治理需要对人类社会和水的使用之间的复杂关系有深刻的理解，因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
-Since water governance requires deep understanding of the complex relationships between human societies and water use, it is crucial to identify its changes induced by the transformation towards hydro-social water cycle, at a basin scales.
+% 作为地球系统治理框架的一个组成部分，水治理需要对人类社会和水资源利用之间的复杂关系有深刻的理解。
+As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human societies and water use.
+% Biermann et al., 2012.
+% 因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
+Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scales.
 
 \label{introduction-section-2}
+% 缺乏治理就是缺乏可持续性
+On the trajectory of development, missing governance means missing sustainability.
+% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
+According to United Nations Development Programme (UNDP), three key dimensions of water use are decided by a water governance regime directly: ``How much water can be used?
+(storage)'', ``How to balances different water use services?
+(provision)'' and ``How to allocate water equally and efficiently?
+(allocation)''.
 % Regime 和 Regime shift 的定义。
@@
 \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
-% 因此，识别水治理的制度变迁对于快速变化的流域具有重要意义，可以作为水利用的系统转变的信号，并给可持续发展带来新的挑战。
-Therefore, identifying regime shifts of water governance is important for fast-changing river basins, since it can be a signal of substantive change in water use and lead to new challenges in sustainability at a basin scale.
-% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to United Nations Development Programme (UNDP), three key aspects of water use are decided by water governance: ``How to meet scarcity of water use?
-(stress of water use)'', ``How to balances different water use services?
-(provision of water use)'' and ``How to allocate water equally and efficiently?
-(allocation of water use)''.
-% 这三个问题的答案取决于不同水治理制度下的环境、经济、社会和政治形势。
-Answers of the three questions depend on environmental, economic, social and political situation within different water governance regimes. 
+% 因此，确定关于水治理的制度变化是重要的，它标志着水资源利用的实质性变化，并导致可持续性方面的新的治理挑战。
+Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new governance challenges in sustainability.
+% 随着环境、经济、社会和政策情况。
+Changed with environmental, economic, social and political situation, the three dimensions may compose various water governance regimes. 
 % 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
-Firstly, effected by environment deteriorate and water uses for economic development, water scarcity can increase stress on society, but management policies such as construction of reservoirs are helpful to relief the stresses.
+Firstly, effected by environment deteriorate and demands of further economic development, maintaining storage for societies can face stress because of water scarcity, but governance policies (such as construction of reservoirs for storage) are helpful to relief
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
@@
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Thirdly, since allocation is basins' concerns, it not only influenced by regional environmental foundations, but also changed by regions' economic comparative advantages, which may effected by social development and policies.
+Thirdly, since allocation is a concern of the whole basin, it not only influenced by regional environmental foundations, but also changed by regions' economic comparative advantages, which is easily changed by social development and policies.
 % 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
-In general, water governance determines the ``stresses'', ``provision'' and ``allocation'' of water use, which all change constantly in the transformation towards the hydro-social water cycle because of changes environmental, economic, social and political situation Figure~\ref{fig:framework}.
-% 因此，通过识别这种变化的稳态转化对理解是很有帮助的。
-Therefore, identification of regime shifts for water governance is critical to understand the complex changes of relationships between human societies and water use.
+Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes determined by three changing dimensions (storage, provision and allocation), and it is crucial to identify their shifts in a simple but comprehensive way for basins' sustainability (Figure~\ref{fig:framework}).
 
+\label{introduction-section-3}
 % 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
-The Yellow River Basin (YRB, see \textit{Appendix} Methods S1) had experienced the most intense water exploitation and the most dramatic shifts of management regime in China. 
-% 从古至今，黄河一直为水治理带来了异乎寻常的挑战
-Since ancient times, YRB had brought extraordinary challenges to water governance.
+The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since ancient times.
 % 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
-Before 1960, the huge sediment loads of the Yellow River in China not only brought flood disasters, but also brought great difficulties to water use of YRB. 
+Half century ago, the huge sediment loads of the Yellow River in China not only brought disasters, but also made it difficult for water use. 
 % 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
-With the implementation of governance measures such as conservation policies, regulation reservoirs, and levees constructions, these issues were effectively contained.
+Since 1960s, with implementations of conservation policies, regulation reservoirs, and levees constructions, these issues were effectively contained.
 % 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
-However, more and more serious drying up of the Yellow River brings new challenges to governance and promoted a range of related policies to deal with.
+However, serious drying up of the Yellow River led new challenges to governance and promoted a range of related policies to deal with.
 % 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
-Today, the Yellow River basin still faces serious governance challenges, as regional water demands are still difficult to be fully met and various trade-offs must be involved.
+Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
 % 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
-All in all, the transformation of the Yellow River basin has been the most rapid in the world in response to the endless governance challenges brought by the increasing human influence.
+All in all, the transformation of the YRB has been the most rapid in the world in responses to the endless governance challenges induced by environmental, economic, social or political factors.
 % 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
-Therefore, identifying the regime shifts of water governance for YRB can provide key insights for the sustainable water use governance in the world's great river basins.
+Therefore, identifying the regime shifts with challenges regarding water governance for YRB can provide insights for the world's fast-changing big river basins in their sustainable development.
 
+\label{introduction-section-3}
 % tag 引言最后一段
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, by integrating three above mentioned key questions in water governance, we develop an Integrated Water Governance Index (IWGI) at a basin scale to indicate changes of basin's water governance (Figure~\ref{fig:framework}).
+Here, by integrating three above mentioned key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) at a basin scale to indicate changes of basin's water governance (Figure~\ref{fig:framework}).
 % 使用案例研究
-Then, by applying this index to the YRB, we analysed the regimes shifts of water governance and their main causes, in this typical basin of rapidly transforming.
+Then, by applying this index to the YRB, we analysed the regimes shifts of water governance and their main causes, in this typical basin of rapidly changes.
 % 最后总结出一般性框架

### 2020-11-18 tex/main/manuscript.tex
update polish

@@
 	\caption{
-		A schematic diagram for understanding the changing relationship between social development and water governance.
+		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three dimensions (stress, provision and allocation) of water resources governance.
-Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources governance changes along that axis.
-(1) Stress of water governance shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
-(2) provision of water governance can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies.
+		\textbf{A,} three dimensions (storage, provision and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details).
+Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis.
+(1) Storage shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
+(2) provision of water can move between provisioning services or non-provisioning services, indicating how much water were used in food supporting.
 (3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
@@
 		\textbf{B,} the changes after combining the three dimensions.
-Because the above three dimensions are changing with the development of society, their combined water resource governance status is also different.
-When abrupt transitions occur during this process, they may indicate a regime shift in water governance, so we need an indicator to monitor this change.
+Because the above three dimensions are changing with the trajectory towards hydro-social water cycle, their combined water governance status is also different.
+When abrupt change occur during this process, they may indicate a regime shift in water governance, and we propose an indicator to monitor this change.
 	}
@@
 	\textbf{B,} Changing slopes of each period.
-	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
+	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Storage, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
 	}
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while provision and allocation of the water governance had slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the storage made the most striking positive contribution (131\%), while provision and allocation had slight negative contribution (-11\% and -20\%).
 % 第二阶段
-In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1).
+In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because declining storage plays a larger negative role (-188\% dropped than P1).
 % 第三阶段
-However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
+However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water storage in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
 
@@
 	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: provision; C: allocation).
+	\caption{Combination of contributions regards three dimensions in different periods (S: storage; P: provision; C: allocation).
 The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
@@
 % 第一阶段到第二阶段
-At the very beginning (1965) and throughout the whole P1, water governance regime dominated by lower stresses.
-After then, it experienced a shift to high stresses since 1978, with a change in the proportion of contributions between provision and allocation, too.
+At the very beginning (1965) and throughout the whole P1, water governance regime dominated by increasing storage.
+After then, it experienced a shift to slow down in increasing storage since 1978, with a change in the proportion of contributions between provision and allocation, too.
 % 第三阶段集中
-Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
+Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and storage respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
 
@@
 	\caption{
-		Drivers of water governance regime shifts: economy growths, efficiency changes, and management practices.
+		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
 		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
@@
 % 经济总量提升导致资源耗竭的加速。
-Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision of water use between P1 and P2 (Figure\ref{fig:Causes}A).
-During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant governance way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
+Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision between P1 and P2 (Figure\ref{fig:Causes}A).
+During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
 S7).
@@
 Secondly, efficiency of water use changed from the P2 to the P3.
-While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B).
+While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes} A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B).
 However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-It means, water governance ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
+It means, water governance have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
 S8).
@@
 % 不断变化的管理模式。
-Finally, water policies and management practices contributed throughout all three periods. 
+Finally, environmental context, social transformation and water governance policies played roles throughout all three periods. 
 According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
-In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
+In the P1 when natural water resource is relatively abundant (see \textit{SI Appendix} Figure S3), most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
 In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6).  
@@
 S6).
+% After the major environmental regulation, myriad new water policies proposed during this period.
 
@@
 	\caption{
-		\textbf{Transition framework of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
+		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
+There is a transformation towards the hydro-social water cycle where red loop increases.
 		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
@@
 Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
+		Water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
 	}
@@
 % 我们发明的指数能同时关注水资源治理的三个关键方面。
-The IWGI index we developed captures three key dimensions of water governance simultaneously: (water use stress, provision of water use and allocation for water use). 
+The IWGI index we developed captures three key dimensions of water governance simultaneously: (storage, provision and allocation). 
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
@@
 % 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
+It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).
 
@@
 However, the water allocating policy (i.g.
-``87 Water Diversion Scheme''), which had helped the YRB get rid of the environmental crisis in the last regime, became the shackle of equity and coordination during this period.
+``87 Water Diversion Scheme''), which had helped the YRB get rid of the environmental crisis at the last regime, became the shackle of equity and coordination during this period.
 % 这是因为用水分配方案高度路径依赖，用水方式也更加不灵活，这些成为新的社会经济形势下的治理难题。
@@
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-With the typical transition towards a hydro-social water cycle, we find that the regime shifts of water governance echoes the two major challenges globally.
+With the typical transition towards a hydro-social water cycle, we find that the regime transition of water governance echoes the two kinds of major challenges globally.
 % 根据前人广泛的总结，目前全球一部分流域正面临着经济发展和资源困境（如缺水和用水困难），而另一些则迫切需要社会政策层面的协调与合作以实现可持续（如跨境河流的用水分配与协作治理）。
@@
 % 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-Again, our schema have outlined echoes the four dimensions (economic, environmental, social and political) summarized by UNDP, and two types of global challenges, regarding water governance.
+Again, this schema outlines the key dimensions proposed by UNDP and two types of global challenges, regarding water governance.
 
@@
 At this point, we need corresponding comprehensive strategies to address the governance challenges, because the heart factors of are beyond the control of any related actor. 
-% 基于对治理稳态的认识，我们可以为应对挑战创造有利条件，让利益相关者实现对社会和环境状况的预期，从而维持流域社会-生态系统的弹性。
-Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and enabling stakeholders to realize their expectations of social and environmental changes, thus maintaining the resilience of the basin's socio-ecosystem.
+% 基于对治理体制转型对理解，我们可以创造有利条件以应对挑战，并保持流域社会-生态系统对弹性，以实现可持续发展。
+Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and maintaining the resilience of the basin's socio-ecosystem, towards sustainability.
 % 总的来说，这些都有助于指导流域迈向可持续性。
-Taken together, these have helped guide the basin towards sustainability.
+% Taken together, these have helped guide the basin towards sustainability.
 

### 2020-11-18 tex/main/manuscript.tex
update some slight amends in abstract

@@
 The significance statement appears in the paper itself and is required for all research papers.
-	It is a well-known fact that water use plays a key role in development of human societies.
+	It is a well-known fact that development of human societies backs on water use.
 	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
@@
 	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
-	Since resources and structural challenges of water governance mainly occurred at different stages of transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
+	Since different governance challenges mainly occurred at different stages in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
 \end{abstract}

### 2020-11-20 tex/main/manuscript.tex
change fig.4 and related descriptions

@@
 These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
+		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2).
+Four transformations are ``ethos of overcome nature since 1958'', ``reform and opening-up since 1978'', ``the 87 Water Diversion Scheme since 1987'', ``environmental regulation since 2003'' in order.
 	}
@@
 
-% 不断变化的管理模式。
+% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
 Finally, environmental context, social transformation and water governance policies played roles throughout all three periods. 
-According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
-In the P1 when natural water resource is relatively abundant (see \textit{SI Appendix} Figure S3), most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
-In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6).  
-Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
+% 根据水库的位置，计算了各水库的区域用水量与盆地用水量之比。
+According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for storage rather than regulating (see \textit{SI Appendix} Figure S3).
+% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
+Under the guide of ``ethos of overcome nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant, as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
+% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
+In the P2, the number of new reservoirs decreases significantly and allocation of water were rigorously controlled by ``the 87 Water Diversion Scheme'', with little increment of total storage capacities (\textit{SI Appendix} Fig.
 S6).
-% After the major environmental regulation, myriad new water policies proposed during this period.
+% 而进入P3期后，新增水库数量远高于P1期，且多数建在区域用水量比较低的区域(图~\ref{fig: Causes}C和\textit{SI  Appendix}图S6)。
+Entering the P3, myriad national-level water governance policies proposed under the guide of ``environmental regulation'', and the number of new reservoirs are even higher for facilitating regulation, most of which were built in regions with lower R/B ratio (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
+S6).
 

### 2020-11-20 tex/main/manuscript.tex
polish the introduction

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Regime transition identification for basin's governance challenges of water use}
+\title{Regime transition identification for water governance at a basin scale}
 \label{title}
@@
 \author[a, b]{Shuang Song}  % 宋爽，一作
-\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
+\author[a, b]{Shuai Wang}  % 王老师，通讯
 \author[c, d]{Xutong Wu}  % 武旭同
 \author[e]{Yongping Wei} % 尉老师
-\author[a, b]{Bojie Fu}  % 傅老师
+\author[a, b, 1]{Bojie Fu}  % 傅老师
 
@@
 	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
-	Since our index integrates various considerations of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
-	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
+	Since our index integrates various dimensions of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
+	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainability. 
 }
@@
 	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
-	Here, considering three main dimensions of water governance (storage, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
+	Here, combining three main dimensions of water governance (storage, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
 	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
-	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by environmental, economic social and political changes.
+	By applying this index to a typical fast-changing basin -the Yellow River Basin, China, it paints shifts between three water governance regimes throughout half a century, which were caused by environmental, economic social and political changes.
 	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
-	Based on these, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
+	Based on these, we summarized a widespread transition schema of water governance regime, paralleled with the transformative trajectory towards hydro-social water cycle.
 	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
@@
 % 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
-Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle, stage by stage
+Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
 \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
 % 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
-Facing this major transformation in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for sustainable water use
+Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for Sustainability
 \cite{bestAnthropogenicStressesWorld2019}. 
 % 作为地球系统治理框架的一个组成部分，水治理需要对人类社会和水资源利用之间的复杂关系有深刻的理解。
-As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human societies and water use.
+As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
 % Biermann et al., 2012.
 % 因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
-Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scales.
+Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.
 
@@
 % 缺乏治理就是缺乏可持续性
-On the trajectory of development, missing governance means missing sustainability.
+Missing governance means missing sustainability.
 % 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to United Nations Development Programme (UNDP), three key dimensions of water use are decided by a water governance regime directly: ``How much water can be used?
+According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used?
 (storage)'', ``How to balances different water use services?
@@
 % 因此，确定关于水治理的制度变化是重要的，它标志着水资源利用的实质性变化，并导致可持续性方面的新的治理挑战。
-Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new governance challenges in sustainability.
+Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new challenges to sustainability.
 % 随着环境、经济、社会和政策情况。
-Changed with environmental, economic, social and political situation, the three dimensions may compose various water governance regimes. 
+Along with environmental, economic, social and political changes, the three dimensions may compose various water governance regimes. 
 % 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
-Firstly, effected by environment deteriorate and demands of further economic development, maintaining storage for societies can face stress because of water scarcity, but governance policies (such as construction of reservoirs for storage) are helpful to relief
+Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water storage for societies can face stress because of scarcity, but governance policies (such as construction of reservoirs) can be helpful
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
@@
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Thirdly, since allocation is a concern of the whole basin, it not only influenced by regional environmental foundations, but also changed by regions' economic comparative advantages, which is easily changed by social development and policies.
+Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
 % 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
-Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes determined by three changing dimensions (storage, provision and allocation), and it is crucial to identify their shifts in a simple but comprehensive way for basins' sustainability (Figure~\ref{fig:framework}).
+Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (storage, provision and allocation), and the lack of simple but comprehensive ways to identify regime shifts leaves crucial gaps towards successful governance (Figure~\ref{fig:framework}).
 
@@
 % 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
-The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since ancient times.
+The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since the ancient time.
 % 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
-Half century ago, the huge sediment loads of the Yellow River in China not only brought disasters, but also made it difficult for water use. 
+Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
 % 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
-Since 1960s, with implementations of conservation policies, regulation reservoirs, and levees constructions, these issues were effectively contained.
+Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
 % 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
-However, serious drying up of the Yellow River led new challenges to governance and promoted a range of related policies to deal with.
+However, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies to deal with.
 % 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
@@
 % 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
-All in all, the transformation of the YRB has been the most rapid in the world in responses to the endless governance challenges induced by environmental, economic, social or political factors.
+All in all, the YRB has been the most rapid-changing basins in the world with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
 % 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
-Therefore, identifying the regime shifts with challenges regarding water governance for YRB can provide insights for the world's fast-changing big river basins in their sustainable development.
+Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.
 
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, by integrating three above mentioned key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) at a basin scale to indicate changes of basin's water governance (Figure~\ref{fig:framework}).
+Here, based on three key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) to indicate changes of water governance at a basin scale (Figure~\ref{fig:framework}).
 % 使用案例研究
-Then, by applying this index to the YRB, we analysed the regimes shifts of water governance and their main causes, in this typical basin of rapidly changes.
+Then, by applying it to the YRB, we analysed regimes shifts of water governance and their main causes.
 % 最后总结出一般性框架
-Finally, we summarized a general regime transition schema, echoing to the different challenges in water governance, which can be a useful guideline for basins to develop in a coordinated way.
+Finally, we summarized a general regime transition schema which can be a useful guideline for basins to develop in a coordinated way, with echoes to the different kinds of challenges regarding water governance.
 

### 2020-11-22 tex/main/manuscript.tex
changed into supply and purpose context

@@
 	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
-	Here, combining three main dimensions of water governance (storage, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
+	Here, combining three main dimensions of water governance (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
 	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
@@
 According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used?
-(storage)'', ``How to balances different water use services?
-(provision)'' and ``How to allocate water equally and efficiently?
+(supply)'', ``How to balances different water use services?
+(purpose)'' and ``How to allocate water equally and efficiently?
 (allocation)''.
@@
 % 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
-Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water storage for societies can face stress because of scarcity, but governance policies (such as construction of reservoirs) can be helpful
+Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but governance policies (such as construction of reservoirs) can be helpful
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Secondly, there is trade-off between provisioning water use (such as domestic use and food production uses) and non-provisioning water (such as uses for industrial production or energy), which in need of considerations through water governance
+Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of considerations through water governance
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
@@
 % 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
-Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (storage, provision and allocation), and the lack of simple but comprehensive ways to identify regime shifts leaves crucial gaps towards successful governance (Figure~\ref{fig:framework}).
+Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation), and the lack of simple but comprehensive ways to identify regime shifts leaves crucial gaps towards successful governance (Figure~\ref{fig:framework}).
 
@@
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three dimensions (storage, provision and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details).
+		\textbf{A,} three dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details).
 Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis.
-(1) Storage shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
-(2) provision of water can move between provisioning services or non-provisioning services, indicating how much water were used in food supporting.
+(1) supply shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
+(2) purpose of water can move between provisioning services or non-provisioning services, indicating how much water were used in food supporting.
 (3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
@@
 	\textbf{B,} Changing slopes of each period.
-	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Storage, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
+	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation are the main positive contributor of P1, P2 and P3, respectively.
 	}
@@
 % 这一节主要展示IWGI的变化趋势和WUR的划分
-With two significant points, the changing trend of IWGI index are detected into three periods (Figure~\ref{fig:IWGI}A). 
-Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWGI}B and Figure~\ref{fig:IWGI}C).
+With two significant points, the changes of IWGI are detected into three periods (Figure~\ref{fig:IWGI}A). 
+Not only the slope of trends are various within each period (Figure~\ref{fig:IWGI}B), changes are also mainly contributed by different water governance dimensions (Figure~\ref{fig:IWGI}C).
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the storage made the most striking positive contribution (131\%), while provision and allocation had slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI had a rapidly increasing and the supply made the most striking positive contribution (131\%), while purpose and allocation had slight negative contribution (-11\% and -20\%).
 % 第二阶段
-In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because declining storage plays a larger negative role (-188\% dropped than P1).
+In the second period (P2, 1979-1994), though contributions of purpose and allocation turned into positive, the IWGI index experienced a drop because declining supply plays a larger negative role (-188\% dropped than P1).
 % 第三阶段
-However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water storage in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
+However, as the further increasing of positive contributions of purpose (75\%) and allocation (84\%), and decreases of water supply in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
 
@@
 	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions regards three dimensions in different periods (S: storage; P: provision; C: allocation).
+	\caption{Combination of contributions regards three dimensions in different periods (S: supply; P: purpose; C: allocation).
 The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
-	The red indicator line in this ternary plot denotes 1:1 contributions between provision (P) and allocation (C).
-When the points are bellow this line, the contribution ratio of allocation is lower than that of provision, and vice versa.}
+	The red indicator line in this ternary plot denotes 1:1 contributions between purpose (P) and allocation (C).
+When the points are bellow this line, the contribution ratio of allocation is lower than that of function, and vice versa.}
 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
@@
 % 第一阶段到第二阶段
-At the very beginning (1965) and throughout the whole P1, water governance regime dominated by increasing storage.
-After then, it experienced a shift to slow down in increasing storage since 1978, with a change in the proportion of contributions between provision and allocation, too.
+At the very beginning (1965) and throughout the whole P1, water governance regime dominated by increasing supply.
+After then, it experienced a shift to slow down in increasing supply since 1978, with a change in the proportion of contributions between purpose and allocation, too.
 % 第三阶段集中
-Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and storage respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
+Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
 
@@
 During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce.
-Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig.
+Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting supply capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig.
 S5).
@@
 % % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, provision (Figure~\ref{fig:dimensions}B) and allocation (Figure~\ref{fig:dimensions}C) of water governance were keeping to enlarge their impacts.
+% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, purpose (Figure~\ref{fig:dimensions}B) and allocation (Figure~\ref{fig:dimensions}C) of water governance were keeping to enlarge their impacts.
 % % 首先是用水比例的变化
-% Representing provision of water governance, increasing non-provisioning share of water governance were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
+% Representing purpose of water governance, increasing non-purposeing share of water governance were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
 % % 再讨论用水格局的变化
@@
 Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
-(2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage.
+(2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply.
 These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
@@
 % 经济总量提升导致资源耗竭的加速。
-Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision between P1 and P2 (Figure\ref{fig:Causes}A).
+Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the purpose between P1 and P2 (Figure\ref{fig:Causes}A).
 During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
@@
 % 根据水库的位置，计算了各水库的区域用水量与盆地用水量之比。
-According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for storage rather than regulating (see \textit{SI Appendix} Figure S3).
+According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for supply rather than regulating (see \textit{SI Appendix} Figure S3).
 % 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
@@
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In the P2, the number of new reservoirs decreases significantly and allocation of water were rigorously controlled by ``the 87 Water Diversion Scheme'', with little increment of total storage capacities (\textit{SI Appendix} Fig.
+In the P2, the number of new reservoirs decreases significantly and allocation of water were rigorously controlled by ``the 87 Water Diversion Scheme'', with little increment of total water storage capacities (\textit{SI Appendix} Fig.
 S6).
@@
 There is a transformation towards the hydro-social water cycle where red loop increases.
-		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
+		\textbf{A.
+Natural phase:} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
 		\textbf{B.
@@
 		\textbf{C.
-Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent.
-Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore.
+Regional phase:} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent.
+Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore.
 		Water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
@@
 % 我们发明的指数能同时关注水资源治理的三个关键方面。
-The IWGI index we developed captures three key dimensions of water governance simultaneously: (storage, provision and allocation). 
+The IWGI index we developed captures three key dimensions of water governance simultaneously: (supply, purpose and allocation). 
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
@@
 % 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited socio-economic influences on the natural water cycle, the governance system with few protective policies encouraged unlimited water withdrawals and storage in the regions requiring water supply, with little consideration of the social equity over the basin.
+Due to the limited socio-economic influences on the natural water cycle, the governance system with few protective policies encouraged unlimited water withdrawals and supply in the regions requiring water supply, with little consideration of the social equity over the basin.
 % 近80%的地表水用于供应(家庭用水、牲畜用水或粮食生产)，黄河的干涸发生在政权末期，留下了巨大的环境危机。
-With nearly 80\% of surface water used for provisioning (domestic, livestocks' use or food production), drying up of the Yellow River occurred at the end of the regime and left a huge crisis of environment.
+With nearly 80\% of surface water used for provisioning-purpose (domestic, livestocks' use or food production), drying up of the Yellow River occurred at the end of the regime and left a huge crisis of environment.
 
@@
 % 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
-For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development provision strategies are still the main guideline to meet them.
+For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development purpose strategies are still the main guideline to meet them.
 % 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
@@
 % 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
-Secondly, complicated structure of water allocation or provision under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
+Secondly, complicated structure of water allocation or purpose under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
 \cite{qinFlexibilityIntensityGlobal2019}.
@@
 	\begin{itemize}
-		\item Social development is usually accompanied by a change of provision in water use towards social and economic systems because of higher returns:
+		\item Social development is usually accompanied by a change of purpose in water use towards social and economic systems because of higher returns:
 		$$ Dev. \propto P $$
@@
 	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with social development:
-	$$ Dev. \propto P*A*S^{-1} $$
+
+	$$ Dev. \propto P*A*S^{-1}$$
 
 	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to provision, allocation and Stress respectively) for each dimension.
+	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to purpose, allocation and Stress respectively) for each dimension.
 Then, the above equation is transformed into a natural logarithm to facilitate calculation:
@@
 
-	\subsubsection*{Indicator of provision}
-	To provision $I_P$, we use Non-Provisioning Shares (NPS) of water use as an indicator.
-While provisional water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-Then, we can calculate the non-provisioning shares by:
+	\subsubsection*{Indicator of purpose}
+	To purpose $I_P$, we use Non-provisioning purpose Shares (NPS) of water use as an indicator.
+While provisioning-purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
+Then, we can calculate the NPS by:
 
@@
 		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources governance (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), provision ($I'_P$) and allocation ($I'_C$).
+Use Integrated Water Resources governance (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:

### 2020-11-22 tex/main/manuscript.tex
polish throughtout

@@
 % 第二阶段
-In the second period (P2, 1979-1994), though contributions of purpose and allocation turned into positive, the IWGI index experienced a drop because declining supply plays a larger negative role (-188\% dropped than P1).
+In the second period (P2, 1979-1994), though contributions of purpose and allocation turned into positive, the IWGI experienced a drop because huge-declined supply capacity plays a larger negative role (-188\% dropped than P1).
 % 第三阶段
@@
 	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions regards three dimensions in different periods (S: supply; P: purpose; C: allocation).
+	\caption{Combination of contributions regards three dimensions in different periods (S: supply; P: purpose; A: allocation).
 The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
-	The red indicator line in this ternary plot denotes 1:1 contributions between purpose (P) and allocation (C).
+	The red indicator line in this ternary plot denotes 1:1 contributions between purpose (P) and allocation (A).
 When the points are bellow this line, the contribution ratio of allocation is lower than that of function, and vice versa.}
@@
 % 第一阶段到第二阶段
-At the very beginning (1965) and throughout the whole P1, water governance regime dominated by increasing supply.
-After then, it experienced a shift to slow down in increasing supply since 1978, with a change in the proportion of contributions between purpose and allocation, too.
+Throughout the whole P1, water governance regime dominated by increasing supply capacities.
+After then, it experienced a shift to slow down in increasing supply since 1978, with a reverse in the contributed proportion between purpose and allocation, too.
 % 第三阶段集中
 Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
+% 总结来说，三个稳态
+All in all, there were three water governance regimes corresponding three different periods: massive supply regime (1965-1978), purpose turned regime (1979-1993), all-sided governance regime (1994-2013).
 
-% %tag 结果2
-% \subsection*{Differences between water governance regimes}
-% % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
-% The differences between the water governance regimes are reflected in changes of all three dimensions.
-
-% % 从阶段一到阶段二，水资源压力的变化最为明显
-% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water governance stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).
-% % 1. 水资源丰富，耗水量少且灵活用水
-% In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig.
-S3) and most of which were flexible water governance (\textit{SI Appendix} Fig.
-S4).
-During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce.
-Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting supply capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig.
-S5).
-As a result, water governance stress decreases during P1, but begins to rise rapidly in P2.
-
-% % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
-% On the other hand, as the most positive contributors to the IWGI index in P2 and P3 separately, purpose (Figure~\ref{fig:dimensions}B) and allocation (Figure~\ref{fig:dimensions}C) of water governance were keeping to enlarge their impacts.
-% % 首先是用水比例的变化
-% Representing purpose of water governance, increasing non-purposeing share of water governance were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
-% % 再讨论用水格局的变化
-% However, allocation of water governance, whose contributions to the IWGI are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
-
-% tag 结果3
+% tag 结果2
 \subsection*{Causes of water governance regime shifts}
+\label{result2}
 
@@
 		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2).
-Four transformations are ``ethos of overcome nature since 1958'', ``reform and opening-up since 1978'', ``the 87 Water Diversion Scheme since 1987'', ``environmental regulation since 2003'' in order.
+Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order.
 	}
@@
 % 经济总量提升导致资源耗竭的加速。
-Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the purpose between P1 and P2 (Figure\ref{fig:Causes}A).
+Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the turn of purpose between P1 and P2 (Figure\ref{fig:Causes}A).
 During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
 S7).
-Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).
+Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off with more water demands (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water use (\textit{SI Appendix} S7).
 
@@
 Secondly, efficiency of water use changed from the P2 to the P3.
-While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes} A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B).
-However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-It means, water governance have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig.
-S8).
-As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig.
-S7).
+While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes} A), both industry, urban services were boosting their economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+However, because of the improved water use efficiency by technology and water conservation practices (\textit{SI Appendix} Fig.
+S8), both of them experienced significant declines in water use intensity for unit production (WUI) (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).
 
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and water governance policies played roles throughout all three periods. 
+Finally, environmental context, social transformation and water governance policies played roles throughout all three regimes. 
 % 根据水库的位置，计算了各水库的区域用水量与盆地用水量之比。
@@
 % 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guide of ``ethos of overcome nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant, as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
+Under the guide of ``ethos of conquer nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant, as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
@@
 S6).
-% 而进入P3期后，新增水库数量远高于P1期，且多数建在区域用水量比较低的区域(图~\ref{fig: Causes}C和\textit{SI  Appendix}图S6)。
+% 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
 Entering the P3, myriad national-level water governance policies proposed under the guide of ``environmental regulation'', and the number of new reservoirs are even higher for facilitating regulation, most of which were built in regions with lower R/B ratio (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
@@
 
-% 我们发明的指数能同时关注水资源治理的三个关键方面。
-The IWGI index we developed captures three key dimensions of water governance simultaneously: (supply, purpose and allocation). 
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Based on that, our results show that three distinct but sequential governance regimes within YRB, whose shifts have been caused by different environmental, economic, social or political aspects.
+Our results show that three distinct but sequential governance regimes within YRB (massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013)), whose shifts caused by different environmental, economic, social or political aspects.
 % 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).
+It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social water cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).
 
 % 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-At the first regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant in this period, governance of water use tended to provide more resources for agriculture (construction of reservoirs and channels for examples).
+At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant, water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples).
 % 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited socio-economic influences on the natural water cycle, the governance system with few protective policies encouraged unlimited water withdrawals and supply in the regions requiring water supply, with little consideration of the social equity over the basin.
-% 近80%的地表水用于供应(家庭用水、牲畜用水或粮食生产)，黄河的干涸发生在政权末期，留下了巨大的环境危机。
-With nearly 80\% of surface water used for provisioning-purpose (domestic, livestocks' use or food production), drying up of the Yellow River occurred at the end of the regime and left a huge crisis of environment.
+Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin.
+% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
+With nearly 80\% of surface water used mainly for provisioning-purpose, the Yellow River dried up at the second half of the regime. 
+% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
+Ecological issues such as shrink of wetlands, declines of biodiversity emerged as the drying up became more and more serious, leading a huge crisis in environment which challenges water governance rigorously.
 
-% 第二个政权与中国的经济改革相吻合，新兴的工业和服务业打破了农业的主导地位，在新的治理体制下争夺用水。
-The second regime coincided with Chinese economic reform, when the emerging industry and services broke the dominance of agriculture and competed for water use under the new governance regime. 
-% 与此同时，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-At the same time, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
+% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
+The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use.
+% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
+Facing legacy environmental challenges and new economic challenges, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB.
 % 该制度稳态不仅遏止了用水效率低下的农业的扩张，更出台了一系列政策法规应对水资源压力，并调节用水分配。
-As results, the regime not only stopped the expansion of inefficient agriculture, but also introduced a range of policies and regulations to deal with the stresses of water use and regulate the allocation of water.
+As results, the YRB introduced new policies and regulations ahead of the whole country (for an example, ``the 87 Water Diversion Scheme'') to allocate water and successfully stopped the expansion of irrigated water consumption.
 
-% 第三次稳态转换直到1993年左右才由用水效率的显著提升而带来，因为社会经济发展后先进技术的广泛应用。
-The next regime shift was not brought until a significant increase in water use efficiency around 1993, due to the widespread applying of advanced technologies after socio-economic developments. 
-% 而区域社会经济的权衡成为了用水分配的关键，如此时期普及开的水权转换项目就是把节约的农业用水用于工业发展。
-The regional socio-economic trade-off had become the key to water governance in this period, and for an example, the water rights conversion project popularized in this regime is to use the saved agricultural water for industrial developments.
+% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
+The next regime shift to all-sided governance was not brought until a significant increase in water use efficiency since about 1993, due to the widely applying of advanced technologies after socio-economic developments.
+% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
+Since socio-economic trade-offs between regions and sectors in water demands played a key role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply.
+% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
+For an example, the water rights conversion project popularized since this period may save regional agricultural water for industrial developments even in another region.
 % 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-However, the water allocating policy (i.g.
-``87 Water Diversion Scheme''), which had helped the YRB get rid of the environmental crisis at the last regime, became the shackle of equity and coordination during this period.
-% 这是因为用水分配方案高度路径依赖，用水方式也更加不灵活，这些成为新的社会经济形势下的治理难题。
-This is because the water allocation scheme is highly path dependent and the way of water use is also more inflexible, both of which have become challenges for governance under the new regime.
+On the other hand, however, the old water policy (i.g.
+``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence.
+% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
+Anyhow, myriad national-level water policies were proposed or adjusted under this regime, as the absence of such policies gaps and social injustice regarding water use are becoming new structural challenges for governance
 
 % 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
-In general, shifts of the three governance regimes occurred sequentially with the transformation towards the hydro-social cycle, with an obvious transition.
+In general, shifts of the three governance regimes occurred sequentially along with a transformation towards the hydro-social cycle.
 % 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
-This transition is considered to be pervasive in socio-ecological systems, such as ecosystem services and national economic-social developments, as increasing anthropogenic pressures gradually dominate the world at large.
+This kind of transition may be widespread in socio-ecological systems, such as transition of ecosystem services and transition of economic-social developments, as increasing anthropogenic impacts gradually change the world at large.
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-With the typical transition towards a hydro-social water cycle, we find that the regime transition of water governance echoes the two kinds of major challenges globally.
-% 根据前人广泛的总结，目前全球一部分流域正面临着经济发展和资源困境（如缺水和用水困难），而另一些则迫切需要社会政策层面的协调与合作以实现可持续（如跨境河流的用水分配与协作治理）。
-According to the summary of previous studies, some river basins are facing economic development and resource dilemma (such as water shortage and water supplying difficulties), while others are in urgent need of coordination and cooperation at the social policy (such as water disputes and lack of cooperative governance, especially for cross-border rivers).
+Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges).
+% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
+Resource challenges represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and highly related to economic and environmental changes. 
+% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
+Other side, highly-controlled and developed basins (especially for cross-border rivers) are mainly facing structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects.
 % 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
-It is very representative that these two kinds of major challenges have occurred successively in the transition of the YRB, accompanied by the transformation of governance regime.
+It is very representative that resource challenges and structural challenges have occurred successively along the transition of water governance within the YRB, because of rapid-changing regimes.
 % 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Our analysis indicates that the early stage of transition often brings environmental and economic governance challenges, while the later stage of transition is dominated by social and policy challenges.
+Based on that, our analysis suggests that the early stage of transition often leads resource challenges by economic and environmental changes, while the later stage is dominated by structural challenges regarding social and political aspects.
 % 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-Again, this schema outlines the key dimensions proposed by UNDP and two types of global challenges, regarding water governance.
+Aligned with the core dimensions emphasized by UNDP regarding water governance, this schema paints a co-evolution between the governance challenges and basins' transformation towards a hydro-social water cycle, again.
 
@@
 % 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
-It is important for scientists and decision makers to recognize the changing challenges for water governance, because development is not a panacea for all basin issues regarding sustainability.
+It is important for scientists and decision makers to recognize the changing governance challenges because development is not a panacea for all basin issues regarding sustainability.
 % 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
-For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development purpose strategies are still the main guideline to meet them.
+For today's world, water-related challenges remains one of the major gaps towards sustainability, while development-first strategies are still the main guideline to conquer them rather than optimizing governance.
 % 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
-Although most large river basins improved water management and efficiency along with development, most studies still pessimistically point out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
+Although most large river basins improved water management technologies and water use efficiency along with development, most studies still pessimistically carried out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
 % 总的来说，这可能有两点主要原因。
@@
 % 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
-Secondly, complicated structure of water allocation or purpose under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
+Secondly, without successful governance, complicated structure dominated by hydro-social water cycle may lead a more inflexible water use and undermined to resilience of social-ecological systems at a basin scale
 \cite{qinFlexibilityIntensityGlobal2019}.
 % 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
-At this point, we need corresponding comprehensive strategies to address the governance challenges, because the heart factors of are beyond the control of any related actor. 
+From these perspectives, we need comprehensive strategies to address the governance challenges correspondingly, because the heart factors of are beyond the control of any related aspect alone. 
 % 基于对治理体制转型对理解，我们可以创造有利条件以应对挑战，并保持流域社会-生态系统对弹性，以实现可持续发展。
-Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and maintaining the resilience of the basin's socio-ecosystem, towards sustainability.
+Based on a deeper understanding of governance regime transition, we can create favourable status of or maintain the resilience of the basin's socio-ecological system, for meeting the challenges towards sustainability.
 % 总的来说，这些都有助于指导流域迈向可持续性。

### 2020-11-23 tex/main/manuscript.tex
polish througtout by Wei's comments

@@
 	It is a well-known fact that development of human societies backs on water use.
-	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
-	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
-	Since our index integrates various dimensions of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
-	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainability. 
+	Therefore, as natural water cycle has been dominated by growing socio-economic processes towards a hydro-social water cycle, big river basins are roundly governed stage by stage for further water use.
+	We propose an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
+	Three water governance regimes are identified (massive supply regime, purpose turned regime, all-sided governance regime) and a widespread regime-transition schema can be summarized after then. 
+	By linking the transition with major water governance challenges, the schema can be a useful guideline for big river basins all around the world in their sustainability. 
 }
@@
 	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
-	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
+	For water uses in sustaining socio-economic development, human have governed large rivers and led a transformation towards a hydro-social water cycle within basins all around the world. 
 	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
@@
 	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
-	Here, combining three main dimensions of water governance (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
-	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
-	By applying this index to a typical fast-changing basin -the Yellow River Basin, China, it paints shifts between three water governance regimes throughout half a century, which were caused by environmental, economic social and political changes.
+	Here, combining three main dimensions (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts of water governance.
+	% 将该指数应用于典型的快速变化的流域——中国黄河流域，描绘了由环境、经济、社会和政治变化引起的长达半个世纪的三种水治理制度(大规模供应制度、目的性转向制度、全方位治理制度)之间的变迁。
+	By applying the index to a typical rapid-changing basin -the Yellow River Basin, China, shifts between three water governance regimes (massive supply regime, purpose turned regime, all-sided governance regime) throughout half a century are well painted, which were caused by environmental, economic social and political changes.
 	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
-	Based on these, we summarized a widespread transition schema of water governance regime, paralleled with the transformative trajectory towards hydro-social water cycle.
+	Based on that, we summarize a widespread transition schema of water governance regime, paralleled with a transformative trajectory towards hydro-social water cycle in the Anthropocene.
 	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
@@
 \label{introduction-section-1}
-% 水资源在人类世的重要性，是支持人类社会发展的基础。
-\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for Earth system processes, but also supporting development of human societies. 
+% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
+\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for earth system processes, but also supporting development of human societies. 
 %* add references
-% 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
+% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
 Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
 \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
-% 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
-Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for Sustainability
+% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
+Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful water governance for sustainability
 \cite{bestAnthropogenicStressesWorld2019}. 
-% 作为地球系统治理框架的一个组成部分，水治理需要对人类社会和水资源利用之间的复杂关系有深刻的理解。
-As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
+% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
+As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
 % Biermann et al., 2012.
-% 因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
+% 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
 Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.
@@
 (allocation)''.
-% Regime 和 Regime shift 的定义。
+% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
 Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts
 \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
-% 因此，确定关于水治理的制度变化是重要的，它标志着水资源利用的实质性变化，并导致可持续性方面的新的治理挑战。
-Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new challenges to sustainability.
-% 随着环境、经济、社会和政策情况。
-Along with environmental, economic, social and political changes, the three dimensions may compose various water governance regimes. 
-% 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
-Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but governance policies (such as construction of reservoirs) can be helpful
+% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
+Regime shifts, therefore, is a signal of substantive change of water governance and may lead to new challenges to sustainability.
+% 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
+Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation).
+% 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
+Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
 \cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of considerations through water governance
+Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of weights through water governance
 \cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
@@
 Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
-% 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
-Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation), and the lack of simple but comprehensive ways to identify regime shifts leaves crucial gaps towards successful governance (Figure~\ref{fig:framework}).
+% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
+Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation).
+However, the lack of simple but comprehensive method to identify changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).
 
 \label{introduction-section-3}
-% 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
-The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since the ancient time.
-% 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
+% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
+The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
+% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
 Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
-% 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
+% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
 Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
-% 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
-However, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies to deal with.
-% 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
+% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
+However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with.
+% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
 Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
-% 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
-All in all, the YRB has been the most rapid-changing basins in the world with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
-% 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
+% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
+All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
+% 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
 Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, based on three key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) to indicate changes of water governance at a basin scale (Figure~\ref{fig:framework}).
+Here, based on three key dimensions (supply, purpose and allocation) of water governance, we develop an Integrated Water Governance Index (IWGI) to detect changes of water governance at a basin scale (Figure~\ref{fig:framework}).
 % 使用案例研究
-Then, by applying it to the YRB, we analysed regimes shifts of water governance and their main causes.
+By applying the index to a typical rapid-changing big river basin (the YRB), we analysed the complicated regimes shifts of water governance and their main causes in a comprehensive but simple way.
 % 最后总结出一般性框架
-Finally, we summarized a general regime transition schema which can be a useful guideline for basins to develop in a coordinated way, with echoes to the different kinds of challenges regarding water governance.
+Finally, a general regime transition schema is summarized, which can be a practicable guideline for big river basins to governance in a coordinated way towards sustainability since it reveals widespread challenges regarding water governance.
 
@@
 	\caption{
-		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes.
+		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes, with a main goal in detecting regime shifts by a simple and comprehensive index.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details).
-Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis.
-(1) supply shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not.
-(2) purpose of water can move between provisioning services or non-provisioning services, indicating how much water were used in food supporting.
-(3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed.
-We presume that water governance regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development.
+		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details).
+Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
+(2) ``purpose'' weighted between provisioning services or non-provisioning services.
+(3) ``allocation'' changes between balanced or lopsided.
+We presume that water governance regimes equally weighted by these basic dimensions.
 		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B,} the changes after combining the three dimensions.
-Because the above three dimensions are changing with the trajectory towards hydro-social water cycle, their combined water governance status is also different.
-When abrupt change occur during this process, they may indicate a regime shift in water governance, and we propose an indicator to monitor this change.
+		\textbf{B,} the governance changes combined the three dimensions.
+Because the above three dimensions change along with the trajectory towards hydro-social water cycle, combined water governance status is also various with that.
+When abrupt change occurs during this process, it may indicate a regime shift in water governance.
 	}
@@
 		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
-		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
+		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Method S2).
 		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
@@
 (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply.
-These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
+These marked reservoirs, therefore are more significant for the entire basin, rather than regional development.
 		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2).
@@
 Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore.
-		Water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
+		\textbf{D.
+Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
 	}

### 2020-11-24 tex/main/manuscript.tex
update references

@@
 Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
-\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
+\cite{gleeson2020,sivapalan2012,qin2014,abbott2019,levia2020}.
 % 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
 Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful water governance for sustainability
-\cite{bestAnthropogenicStressesWorld2019}. 
+\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarre2019}. 
 % 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
-As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
-% Biermann et al., 2012.
+As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water
+\cite{biermann2012,steffen2020,dibaldassarre2019}
 % 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
@@
 % 缺乏治理就是缺乏可持续性
-Missing governance means missing sustainability.
+For water, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
 % 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used?
+According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly: ``How much water can be used?
 (supply)'', ``How to balances different water use services?
 (purpose)'' and ``How to allocate water equally and efficiently?
-(allocation)''.
+(allocation)''
+\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
 % 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
 Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts
-\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
+\cite{rocha2018,gregr2020}.
 % 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Regime shifts, therefore, is a signal of substantive change of water governance and may lead to new challenges to sustainability.
+Regime shifts, therefore, can be a signal of substantive change of water governance and may lead to new challenges to sustainability 
+\cite{steffen2020}.
 % 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
-Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation).
+Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation)
+\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
 % 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
 Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
-\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
+\cite{greveGlobalAssessmentWater2018, wada2017, qin2019}.
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
 Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of weights through water governance
-\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
+\cite{liu2017, florke2018}.
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
+Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes
+\cite{roobavannan2017,speed2013}.
 % 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
@@
 % 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
-The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
+The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
 % 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
+Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use 
+\cite{song2020,li2020}. 
 % 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
-Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
+Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained 
+\cite{wang2016,wu2020}.
 % 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
-However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with.
+However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with
+\cite{xia2012}.
 % 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
-Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
+Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance 
+\cite{wang2019, wohlfart2016}.
 % 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
+All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors 
+\cite{bestAnthropogenicStressesWorld2019}.
 % 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
@@
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details).
+		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
 Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
@@
 Because the above three dimensions change along with the trajectory towards hydro-social water cycle, combined water governance status is also various with that.
-When abrupt change occurs during this process, it may indicate a regime shift in water governance.
+When abrupt change occurs during this process, it may indicate a regime shift in water governance
+		\cite{steffen2018,abbott2019,levia2020}.
 	}
@@
 		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
-		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
-		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Method S2).
+		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Appendix} Methods S2).
+		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Methods S2).
 		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
@@
 		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2).
-Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order.
+Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{Appendix SI} Table S3).
 	}
@@
 There is a transformation towards the hydro-social water cycle where red loop increases.
-		\textbf{A.
-Natural phase:} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B.
-Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+		\textbf{A.} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
+		\textbf{B.} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
 What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
-		\textbf{C.
-Regional phase:} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent.
+		\textbf{C.} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent.
 Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore.
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that three distinct but sequential governance regimes within YRB (massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013)), whose shifts caused by different environmental, economic, social or political aspects.
+Our results show that three distinct but sequential governance regimes within YRB: massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013), whose shifts caused by different environmental, economic, social or political aspects.
 % 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
@@
 % 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant, water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples).
+At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S3), water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples).
 % 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin.
+Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin
+\cite{zhou2020}. 
 % 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-With nearly 80\% of surface water used mainly for provisioning-purpose, the Yellow River dried up at the second half of the regime. 
+With nearly 80\% of surface water used mainly for provisioning-purpose, the Yellow River dried up at the second half of the regime (\textit{SI Appendix} Figure S10). 
 % 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
@@
 % “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use.
+The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use (Figure~\ref{fig:Causes}).
 % 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-Facing legacy environmental challenges and new economic challenges, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB.
-% 该制度稳态不仅遏止了用水效率低下的农业的扩张，更出台了一系列政策法规应对水资源压力，并调节用水分配。
-As results, the YRB introduced new policies and regulations ahead of the whole country (for an example, ``the 87 Water Diversion Scheme'') to allocate water and successfully stopped the expansion of irrigated water consumption.
+Facing legacy environmental challenges and new economic challenges, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB
+\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
+% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
+As results, the YRB introduced new policies and regulations ahead of the whole country (for an example, ``the 87 Water Diversion Scheme'') to allocate water and successfully stopped the expansion of irrigated water consumption
+\cite{wang2018}.
 
@@
 % 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between regions and sectors in water demands played a key role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply.
+Since socio-economic trade-offs between regions and sectors in water demands played a key role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply
+\cite{dalin2015a}.
 % 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For an example, the water rights conversion project popularized since this period may save regional agricultural water for industrial developments even in another region.
+For an example, the water rights conversion project popularized since this period may save regional agricultural water for industrial developments even in another region, while the water transfer is also another huge project to meet water needs within the YRB
+\cite{barnett2015,yunpeng2010}.
 % 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
 On the other hand, however, the old water policy (i.g.
-``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence.
+``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence
+\cite{wang2018}.
 % 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
 Anyhow, myriad national-level water policies were proposed or adjusted under this regime, as the absence of such policies gaps and social injustice regarding water use are becoming new structural challenges for governance
+\cite{konar2019}
 
@@
 % 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
-This kind of transition may be widespread in socio-ecological systems, such as transition of ecosystem services and transition of economic-social developments, as increasing anthropogenic impacts gradually change the world at large.
+This kind of transition may be widespread in socio-ecological systems, such as transition of ecosystem services and transition of economic-social developments, as increasing anthropogenic impacts gradually change the world at large
+\cite{best2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges).
+Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges)
+\cite{singh2019,porcher2019}.
 % 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
-Resource challenges represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and highly related to economic and environmental changes. 
+Resource challenges represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and highly related to economic and environmental changes
+\cite{allan2019,florke2018,liu2012}. 
 % 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Other side, highly-controlled and developed basins (especially for cross-border rivers) are mainly facing structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects.
+Other side, highly-controlled and developed basins (especially for transboundary rivers) are mainly facing structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects
+\cite{kitroeff2020,roobavannan2017,unep-dhi2016}.
 % 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
@@
 % 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
-It is important for scientists and decision makers to recognize the changing governance challenges because development is not a panacea for all basin issues regarding sustainability.
+It is important for scientists and decision makers to recognize the changing governance challenges because development is not a panacea for all basin issues regarding sustainability 
+\cite{cummingLinkingEconomicGrowth2018,reyers2018}.
 % 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
-For today's world, water-related challenges remains one of the major gaps towards sustainability, while development-first strategies are still the main guideline to conquer them rather than optimizing governance.
+For today's world, water-related challenges remains one of the major gaps towards sustainability, while development-first strategies are still the main guideline to conquer them rather than optimizing governance
+\cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
 % 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
-Although most large river basins improved water management technologies and water use efficiency along with development, most studies still pessimistically carried out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
+Although most large river basins improved water management technologies and water use efficiency along with development, most studies still pessimistically carried out that freshwater use is reaching planetary boundaries where human-water systems may collapse
+\cite{li2020a,degraaf2019,huggins2020}.
 % 总的来说，这可能有两点主要原因。
@@
 Firstly, significant improvement in agricultural irrigation efficiency is usually accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency
-\cite{graftonParadoxIrrigationEfficiency2018}. 
+\cite{grafton2018}. 
 % 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
 Secondly, without successful governance, complicated structure dominated by hydro-social water cycle may lead a more inflexible water use and undermined to resilience of social-ecological systems at a basin scale
-\cite{qinFlexibilityIntensityGlobal2019}.
+\cite{qin2019,levia2020,grill2019}.
 % 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
-From these perspectives, we need comprehensive strategies to address the governance challenges correspondingly, because the heart factors of are beyond the control of any related aspect alone. 
+From these perspectives, we need comprehensive strategies to address the governance challenges correspondingly, because the heart factors of are beyond the control of any related aspect alone
+\cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
 % 基于对治理体制转型对理解，我们可以创造有利条件以应对挑战，并保持流域社会-生态系统对弹性，以实现可持续发展。
 Based on a deeper understanding of governance regime transition, we can create favourable status of or maintain the resilience of the basin's socio-ecological system, for meeting the challenges towards sustainability.
-% 总的来说，这些都有助于指导流域迈向可持续性。
-% Taken together, these have helped guide the basin towards sustainability.
 
@@
 	\subsubsection*{Indicator of Stress}
-	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityIntensityGlobal2019}.
+	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a certain region $i$ \cite{qin2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).

### 2020-11-24 tex/main/manuscript.tex
update all figures and Appendix SI

@@
 	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
-	\textbf{B,} Changing slopes of each period.
-	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation are the main positive contributor of P1, P2 and P3, respectively.
+	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation are the main positive contributor of P1, P2 and P3, respectively.
 	}
@@
 \matmethods{
-Here, we constructed the Integrated Water Resources governance (IWGI) Index which consists of three dimensions and identified the changes periods of the index over time by change points detection. 
+Here, we constructed the Integrated Water Governance Index (IWGI) which consists of three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
 Each dimension is reflected by an independent indicator after normalization, and water governance regime were characterized by combination of impacts of each dimension in periods.
-In addition, the contribution to changes of IWGI index along with each main indicators were decomposed and calculated separately for each regime (i.e. period).
+In addition, the contribution to changes of IWGI index along with each main indicators were decomposed and calculated separately for each regime period.
 
-	\subsection*{Integrated Water Resources governance (IWGI) Index}
+	\subsection*{Integrated Water Governance (IWGI)}
 	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):
+	Water resources governance system is closely related to the transformation towards hydro-social water cycle in three dimensions below (see \textit{SI Appendix} Methods S4 for details)
+	\cite{steffen2018,abbott2019,levia2020}:
 
@@
 	\begin{itemize}
-		\item Social development is usually accompanied by a change of purpose in water use towards social and economic systems because of higher returns:
+		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
+		\item The socio-economic dominance may lead to further demands of water supply (S) because of increasing water withdrawals.
+However, an effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development along with the transformative trajectory, means:
+		$$ Dev \propto S^{-1} $$
+		\item The transformation is usually accompanied by a tilt of purpose in water governance towards socio-economic services (usually non-provisioning purposes), because of higher returns:
 		$$ Dev. \propto P $$
 		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item Social development usually lead to more complex structure in allocation of water resources, which is a result of division and cooperation between regions and sectors for developing:
+		\item The transformation usually lead to more complicated structure in water allocation, which is mainly a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
 		$$ Dev \propto A $$ 
-		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item Further social development can only be achieved by effectively alleviating the water resource stresses generated in the process of development through technological means:
-		$$ Dev \propto S^{-1} $$
 	\end{itemize}
@@
 	% 将三者合一起，即：
-	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with social development:
+	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with the transformation towards hydro-social water cycle:
 
@@
 	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to purpose, allocation and Stress respectively) for each dimension.
+	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
 Then, the above equation is transformed into a natural logarithm to facilitate calculation:
 
-	$$ Dev. \propto ln(I_P) + ln(I_A) - ln(I_S) $$
+	$$ Dev. \propto ln(I_S) + ln(I_P) - ln(I_A) $$
 
-	Assuming they have equal weights, the Integrated Water Resources governance (IWGI) Index:
+	Assuming they have equal weights, the Integrated Water Governance Index (IWGI):
 
-	$$ IWGI = I'_A + I'_P - I'_S $$
+	$$ IWGI = I'_S + I'_P - I'_A $$
 
@@
 	\subsubsection*{Indicator of Stress}
-	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a certain region $i$ \cite{qin2019}.
+	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qin2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
-For the whole YRB, indicator of stress $I_S$ is the average stress of all regions' SFV-index:
+For the whole YRB, indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
 
@@
 	To purpose $I_P$, we use Non-provisioning purpose Shares (NPS) of water use as an indicator.
-While provisioning-purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
+While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
 Then, we can calculate the NPS by:

### 2020-11-24 tex/sup/supplementary_information.tex
update references
update all figures and Appendix SI

@@
 Historic and recent river basin management practices have strong impacts on water utilization.
+
+\subsection*{Historical Social transformations within the YRB}
+
+We list four main water-governance-related social transformations in table S3, here are explainations:
+
+\begin{itemize}
+    \item \textbf{The Ethos of Conquering Nature (since 1958)} Conquering the natural movement, although the Yellow River basin was poor and backward at that time, a collective spirit of 'man can conquer nature' was formed.
+In addition to the construction of large-scale water conservancy projects represented by the Yellow River 'The Hongqi Channel', dramatic changes such as the' Great Leap Forward' movement and ``Large-scale production'' movement were also formed in this transformation.
+    \item \textbf{The Reform and Opening-up (since 1978).} Before the reform and opening up, the allocation of resources and production activities throughout China, including the Yellow River Basin, were led by the state.
+At this time, the market gradually began to dominate.
+    \item \textbf{The 87 Water Diversion Scheme (since 1987).} Before the water diversion Scheme, all local sectors had unlimited access to water resources.
+However, after the water diversion scheme was proposed, the Yellow River Basin formed social rules to control water use indicators from top to bottom, from the province to the urban area to all departments.
+    \item \textbf{Environmental Regulation (since 2003).} Environmental issues, including water governance, have become a key KPI for local officials in China since a new leader took office in 2003 with an emphasis on environmental issues.
+\end{itemize}
 

### 2020-11-24 tex/main/manuscript.tex
amend figure captions

@@
 With two significant points, the changes of IWGI are detected into three periods (Figure~\ref{fig:IWGI}A). 
-Not only the slope of trends are various within each period (Figure~\ref{fig:IWGI}B), changes are also mainly contributed by different water governance dimensions (Figure~\ref{fig:IWGI}C).
+Not only the slope of trends are various within each period, changes are also mainly contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
 % 第一阶段

### 2020-11-24 tex/main/manuscript.tex
update fig5 with only two stages

@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
+	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.jpg}
 	\caption{
-		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
+		Transition schema of water governance (A to B) along with the transformation towards hydro-social water cycle (C).
+Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
 There is a transformation towards the hydro-social water cycle where red loop increases.
-		\textbf{A.} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
-		\textbf{B.} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
-What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
-		\textbf{C.} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent.
+		\textbf{A.
+Prophase} With socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
+What's more, better organized socio-economic system and better technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
+		\textbf{B.
+Anaphase} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes highly prominent.
 Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore.
+		\textbf{C.
+Transformation from a natural water cycle towards the hydro-social water cycle.} The above transition paralleled with the transformation towards hydro-social water cycle and generally distinguished when a water use limit reached.
+The three water governance regimes in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose turned regime, Regime 3: all-sided governance regime).
 		\textbf{D.

### 2020-11-25 tex/main/manuscript.tex
polished throughout along with the SI

@@
 	It is a well-known fact that development of human societies backs on water use.
-	Therefore, as natural water cycle has been dominated by growing socio-economic processes towards a hydro-social water cycle, big river basins are roundly governed stage by stage for further water use.
+	Therefore, as natural water cycle has been dominated by growing socio-economic processes towards a hydro-social water cycle, big river basins are roundly governed phase by phase for further water use.
 	We propose an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
-	Three water governance regimes are identified (massive supply regime, purpose turned regime, all-sided governance regime) and a widespread regime-transition schema can be summarized after then. 
+	Three water governance regimes are identified (massive supply, purpose turned, and all-sided governance), and a widespread regime-transition schema can be summarized after then. 
 	By linking the transition with major water governance challenges, the schema can be a useful guideline for big river basins all around the world in their sustainability. 
@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Socio-hydrology $|$ Sustainability}
+\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Transformation $|$ Sustainability}
 
@@
 	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
-	Here, combining three main dimensions (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts of water governance.
+	Here, combining three main dimensions (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) to detect regime shifts of water governance at a basin scale.
 	% 将该指数应用于典型的快速变化的流域——中国黄河流域，描绘了由环境、经济、社会和政治变化引起的长达半个世纪的三种水治理制度(大规模供应制度、目的性转向制度、全方位治理制度)之间的变迁。
@@
 	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
-	Based on that, we summarize a widespread transition schema of water governance regime, paralleled with a transformative trajectory towards hydro-social water cycle in the Anthropocene.
+	Based on that, we summarize a widespread transition schema of water governance regimes, paralleled with a transformative trajectory towards hydro-social water cycle in the Anthropocene.
 	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
-	Since different governance challenges mainly occurred at different stages in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
+	Since different governance challenges mainly occurred at different phases in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
 \end{abstract}
@@
 % 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
-Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
+Because of relying on water use, human activities have profoundly modified the natural water cycle and led a trajectory towards a hydro-social water cycle phase by phase
 \cite{gleeson2020,sivapalan2012,qin2014,abbott2019,levia2020}.
@@
 % 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
-Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.
+Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, especially at a basin scale.
 
@@
 % 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts
+Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to huge impacts on the outcomes of system with widespread cascading effects 
 \cite{rocha2018,gregr2020}.
 % 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Regime shifts, therefore, can be a signal of substantive change of water governance and may lead to new challenges to sustainability 
+Defined as regime shifts, therefore, it is a signal of substantive changes in water governance and may lead to new challenges to sustainability 
 \cite{steffen2020}.
 % 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
-Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation)
+Along with environmental, economic, social and political changes, however, regime shifts of water governance can be triggered from each of the above key dimensions (supply, purpose, and allocation)
 \cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
 % 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
-Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
+Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can be stressful because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
 \cite{greveGlobalAssessmentWater2018, wada2017, qin2019}.
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of weights through water governance
+Secondly, there is trade-off between provisioning-purpose water services (such as domestic use and food production uses) and non-provisioning-purpose services (such as uses for industrial production or energy), which in need of weights through water governance
 \cite{liu2017, florke2018}.
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes
+Thirdly, since governance concerns water allocation at the whole basin, it is not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by changing social and political
 \cite{roobavannan2017,speed2013}.
@@
 Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation).
-However, the lack of simple but comprehensive method to identify changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).
+However, the lack of simple but comprehensive method in identifying changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).
 
@@
 % 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
-The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
+The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
 % 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
@@
 % 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
-Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained 
+Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these high-sediment-caused issues were effectively contained 
 \cite{wang2016,wu2020}.
@@
 % 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors 
-\cite{bestAnthropogenicStressesWorld2019}.
+All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
 % 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
-Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.
+Therefore, identifying the regime shifts for water governance within YRB can provide crucial insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.
 
@@
 	\caption{
-		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes, with a main goal in detecting regime shifts by a simple and comprehensive index.
+		A framework for understanding the relationship between transformation towards hydro-social cycle and transitional water governance regimes, with our main goal in detecting regime shifts by a simple and comprehensive index.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
@@
 (3) ``allocation'' changes between balanced or lopsided.
-We presume that water governance regimes equally weighted by these basic dimensions.
 		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
@@
 	\caption{Changes of the IWGI index. 
-	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation are the main positive contributor of P1, P2 and P3, respectively.
+	\textbf{A,} Change points detection. With sigificant change points in 1978 and 1994, the IWGI have three different periods in changing trend.
+	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation have made the main positive contributor of P1, P2 and P3, respectively.
 	}
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI had a rapidly increasing and the supply made the most striking positive contribution (131\%), while purpose and allocation had slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI was rapidly increasing and the supply made the most striking positive contribution (131\%), while purpose and allocation had slight negative contribution (-11\% and -20\%).
 % 第二阶段
@@
 Throughout the whole P1, water governance regime dominated by increasing supply capacities.
-After then, it experienced a shift to slow down in increasing supply since 1978, with a reverse in the contributed proportion between purpose and allocation, too.
+After then, it experienced a shift to slow down in increasing supply during the P2, with a reverse in the contributed proportion between purpose and allocation, too.
 % 第三阶段集中
-Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points highly concentrated at the centre of the ternary diagram in that period.
+Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points highly concentrated at the centre of the ternary diagram.
 % 总结来说，三个稳态
-All in all, there were three water governance regimes corresponding three different periods: massive supply regime (1965-1978), purpose turned regime (1979-1993), all-sided governance regime (1994-2013).
+All in all, there were three water governance regimes corresponding three different periods: massive supply regime (P1: 1965-1978), purpose turned regime (P2: 1979-1993), all-sided governance regime (P3: 1994-2013).
 
@@
 These marked reservoirs, therefore are more significant for the entire basin, rather than regional development.
-		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2).
-Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{Appendix SI} Table S3).
+		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
+Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
 	}
@@
 % 经济总量提升导致资源耗竭的加速。
-Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the turn of purpose between P1 and P2 (Figure\ref{fig:Causes}A).
-During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig.
-S7).
-Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off with more water demands (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water use (\textit{SI Appendix} S7).
+Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the turn of purpose between P1 and P2.
+During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, \textit{SI Appendix} Fig.
+S3).
+Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off with more water demands (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water use (\textit{SI Appendix} S3).
 
@@
 Secondly, efficiency of water use changed from the P2 to the P3.
-While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes} A), both industry, urban services were boosting their economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+While irrigated area resumed expansion again in the P3 (Figure\ref{fig:Causes}A), both industry, urban services were boosting their economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
 However, because of the improved water use efficiency by technology and water conservation practices (\textit{SI Appendix} Fig.
-S8), both of them experienced significant declines in water use intensity for unit production (WUI) (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).
+S4), both of them experienced significant declines in water use intensity (WUI) for unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+As a result, the differences between sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S3).
 
@@
 % 根据水库的位置，计算了各水库的区域用水量与盆地用水量之比。
-According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for supply rather than regulating (see \textit{SI Appendix} Figure S3).
+According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for supply rather than regulating (Figure~\ref{fig:Causes}C).
 % 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guide of ``ethos of conquer nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant, as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
+Under the guide of ``ethos of conquer nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant (\textit{SI Appendix} Fig.
+S5), as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
@@
 % 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering the P3, myriad national-level water governance policies proposed under the guide of ``environmental regulation'', and the number of new reservoirs are even higher for facilitating regulation, most of which were built in regions with lower R/B ratio (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
+Entering the P3, myriad national-level water governance policies proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs are even higher for facilitating regulating, most of which were built in regions with lower R/B ratio (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
 S6).
@@
 	\caption{
-		Transition schema of water governance (A to B) along with the transformation towards hydro-social water cycle (C).
+		Transition schema of water governance along with the transformation towards hydro-social water cycle.
 Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
@@
 		\textbf{C.
-Transformation from a natural water cycle towards the hydro-social water cycle.} The above transition paralleled with the transformation towards hydro-social water cycle and generally distinguished when a water use limit reached.
+Transformation from a natural water cycle towards the hydro-social water cycle.} The above transition paralleled with the transformation towards hydro-social water cycle and generally distinguished when water resource limits reached.
 The three water governance regimes in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose turned regime, Regime 3: all-sided governance regime).
 		\textbf{D.
-Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
+Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the prophase while social and policy challenges in the anaphase.
 	}
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that three distinct but sequential governance regimes within YRB: massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013), whose shifts caused by different environmental, economic, social or political aspects.
+Our results show that three distinct but sequential governance regimes within YRB (Figure~\ref{fig:phases}): massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013).
+Their shifts caused by different environmental, economic, social or political aspects (Figure~\ref{fig:Causes}).
 % 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social water cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).
+It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social water cycle, facing primarily economic and environmental challenges in the prophase while social and policy challenges in the anaphase (Figure~\ref{fig:summary}).
 
 % 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S3), water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples).
+At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5), water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples).
 % 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin
+Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin, too
 \cite{zhou2020}. 
 % 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-With nearly 80\% of surface water used mainly for provisioning-purpose, the Yellow River dried up at the second half of the regime (\textit{SI Appendix} Figure S10). 
+Since nearly 80\% of surface water used (mainly for provisioning-purpose), the Yellow River dried up at the second half of the regime (\textit{SI Appendix} Figure S7). 
 % 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
-Ecological issues such as shrink of wetlands, declines of biodiversity emerged as the drying up became more and more serious, leading a huge crisis in environment which challenges water governance rigorously.
+Ecological issues such as shrink of wetlands, declines of biodiversity emerged as the drying up became more and more serious, leading a huge crisis in environment which challenges water governance rigorously
+\cite{wohlfart2016}.
 
 % “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use (Figure~\ref{fig:Causes}).
+The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
+S8).
 % 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-Facing legacy environmental challenges and new economic challenges, the Yellow River Conservancy Commission undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB
+Facing endless environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB
 \cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
@@
 % 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next regime shift to all-sided governance was not brought until a significant increase in water use efficiency since about 1993, due to the widely applying of advanced technologies after socio-economic developments.
+The next shift to all-sided governance regime was not brought until a significant increase in water use efficiency since about 1993, for overcoming resources limits  
+\cite{liuWaterconservancyprojects2013}. 
 % 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between regions and sectors in water demands played a key role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply
+Since socio-economic trade-offs between regions and sectors in water demands played a more important role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply
 \cite{dalin2015a}.
 % 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For an example, the water rights conversion project popularized since this period may save regional agricultural water for industrial developments even in another region, while the water transfer is also another huge project to meet water needs within the YRB
+For an example, the water rights conversion project popularized since this regime may save regional agricultural water for industrial developments even in another region, while the water transfer is also another huge project to meet water demands within the YRB
 \cite{barnett2015,yunpeng2010}.
 % 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, however, the old water policy (i.g.
-``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence
+On the other hand, the old water policy (i.g.
+``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, however, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence
 \cite{wang2018}.
@@
 Anyhow, myriad national-level water policies were proposed or adjusted under this regime, as the absence of such policies gaps and social injustice regarding water use are becoming new structural challenges for governance
-\cite{konar2019}
+\cite{konar2019}.
 
@@
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges)
+Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
+S9)
 \cite{singh2019,porcher2019}.
@@
 % 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Other side, highly-controlled and developed basins (especially for transboundary rivers) are mainly facing structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects
+Other side, highly-controlled and developed basins (especially for transboundary rivers) are mainly bothered by structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects
 \cite{kitroeff2020,roobavannan2017,unep-dhi2016}.
@@
 % 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Based on that, our analysis suggests that the early stage of transition often leads resource challenges by economic and environmental changes, while the later stage is dominated by structural challenges regarding social and political aspects.
+Based on that, our analysis suggests that the prophase of transition often leads resource challenges by economic and environmental changes, while the anaphase is dominated by structural challenges regarding social and political aspects.
 % 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-Aligned with the core dimensions emphasized by UNDP regarding water governance, this schema paints a co-evolution between the governance challenges and basins' transformation towards a hydro-social water cycle, again.
+Aligned with the core dimensions emphasized by UNDP regarding water governance, this schema paints resonances between the governance challenges and basins' transformation towards a hydro-social water cycle, again.
 
@@
 % 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
-It is important for scientists and decision makers to recognize the changing governance challenges because development is not a panacea for all basin issues regarding sustainability 
+It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
 \cite{cummingLinkingEconomicGrowth2018,reyers2018}.
@@
 However, an effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development along with the transformative trajectory, means:
-		$$ Dev \propto S^{-1} $$
+		$$ Transformation \propto S^{-1} $$
 		\item The transformation is usually accompanied by a tilt of purpose in water governance towards socio-economic services (usually non-provisioning purposes), because of higher returns:
-		$$ Dev. \propto P $$
+		$$ Transformation. \propto P $$
 		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
 		\item The transformation usually lead to more complicated structure in water allocation, which is mainly a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
-		$$ Dev \propto A $$ 
+		$$ Transformation \propto A $$ 
 	\end{itemize}
@@
 
-	$$ Dev. \propto P*A*S^{-1}$$
+	$$ Transformation \propto P*A*S^{-1}$$
 
@@
 
-	$$ Dev. \propto ln(I_S) + ln(I_P) - ln(I_A) $$
+	$$ Transformation \propto ln(I_S) + ln(I_P) - ln(I_A) $$
 
@@
 	\subsection*{Contribution decomposition}
-		We have decomposed the amount of variation in each index at different stages in order to observe the contribution of each influencing factor to them.
+		We have decomposed the amount of variation in each index at different periods in order to observe the contribution of each influencing factor to them.
 Use Integrated Water Resources governance (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).

### 2020-11-25 tex/sup/supplementary_information.tex
polished throughout along with the SI

@@
 \title{Regime transition identification for water utilization in river basin developments}
-\author{Shuang Song, Shuai Wang, Bojie Fu, Xutong Wu (complete author list)}
+\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Bojie Fu (complete author list)}
 \correspondingauthor{Shuai Wang.\\E-mail: shuaiwang@bnu.edu.cn}
@@
 On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin.
+Specially, Water resources make an irreplaceable contribution to the development of society in the YRB.
+Each sector of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig.
+S3).
 Thus, as a case study for analysing the evolution of the human-water relationship, it possesses typicality.
 
-% \subsection*{Importance of water resource to society within the YRB}
-Water resources make an irreplaceable contribution to the development of society in the YRB.
-Firstly, each aspect of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig.
-S2-A, B and D).
 % Secondly, their relationships have noticeably changed over the study period. In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig. S3-B).
@@
 
-We list four main water-governance-related social transformations in table S3, here are explainations:
+We list four main water-governance-related social transformations in Fig 5D of the main text, here are explanations:
 
@@
 
-% 补充图片3：天然水资源量
+% 补充图片3：用水比例
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
+    \caption{Proportions of total water use between the different sectors}
+\end{figure}
+
+% 补充图片7：节水措施
+\begin{figure}
+    % TODO 这里还要增加一个过去的比例做对比
+    \centering
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/saving_water.jpg}
+    \caption{
+        Saving water irrigated area ratio in 2013.
+    }
+\end{figure}
+
+% 补充图片4：天然水资源量
 \begin{figure}
@@
         \textbf{E, F and G} average total water consumptions within different periods. 
-    }
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
-	\caption{
-		Changes in different dimensions of water resources utilization regimes and their main contributors.
-		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
-		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
-		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
-		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
-		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
-		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
-		}
-	\label{fig:dimensions}
-\end{figure}
-
-% 补充图片4：水资源灵活性
-\begin{figure}
-    \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
-    \caption{
-        Flexibility and its change contributions of water utilization.
-        \textbf{A,} Proportion of inflexible water uses.
-        \textbf{B,} Change contributions of inflexible water uses.
     }
@@
 
-% 补充图片6：用水比例
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
+% 	\caption{
+% 		Changes in different dimensions of water resources utilization regimes and their main contributors.
+% 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
+% 		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
+% 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+% 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
+% 		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
+% 		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+% 		}
+% 	\label{fig:dimensions}
+% \end{figure}
+
+% 补充图片9：黄河断流
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
-    \caption{Proportions of total water use between the different sectors}
-\end{figure}
-
-% 补充图片7：节水措施
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/saving_water.jpg}
-    \caption{
-        Saving water irrigated area ratio in 2013.
-    }
+    \includegraphics[width=0.6\textwidth]{../../figures/sup/outages.pdf}
+    \caption{Runoff outages records, size of points indicates length of drying up river segments.}
 \end{figure}
@@
 
-% 补充图片9：黄河断流
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/outages.pdf}
-    \caption{Runoff outages records, size of points indicates length of drying up river segments.}
-\end{figure}
-
 % % 补充图片10：管理政策
@@
 %     \caption{Number of management practices in different periods, including policy and reservoirs.}
-% \end{figure}
-
-% 补充图片10：地下水
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\textwidth]{../../figures/sup/outages.jpg}
-%     \caption{Severe runoff outages and groundwater depletion}
 % \end{figure}
@@
 \end{figure}
+
+% % 补充图片4：水资源灵活性
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
+%     \caption{
+%         Flexibility and its change contributions of water utilization.
+%         \textbf{A,} Proportion of inflexible water uses.
+%         \textbf{B,} Change contributions of inflexible water uses.
+%     }
+% \end{figure}
 

### 2020-11-25 tex/main/manuscript.tex
rectify a spelling mistake
sync in windows

@@
 	\caption{Changes of the IWGI index. 
-	\textbf{A,} Change points detection. With sigificant change points in 1978 and 1994, the IWGI have three different periods in changing trend.
+	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI have three different periods in changing trend.
 	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation have made the main positive contributor of P1, P2 and P3, respectively.
@@
 		\item The transformation is usually accompanied by a tilt of purpose in water governance towards socio-economic services (usually non-provisioning purposes), because of higher returns:
-		$$ Transformation. \propto P $$
+		$$ Transformation \propto P $$
 		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：

### 2021-02-27 tex/main/manuscript.tex
last rectify before polished by Cumming
polish full text by Cumming

@@
 % 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Regime transition identification for water governance at a basin scale}
+\title{Identifying regime transitions for water governance at a basin scale}
 \label{title}
@@
 \author[e]{Yongping Wei} % 尉老师
+\author{Graeme S. Cumming} % Cumming
 \author[a, b, 1]{Bojie Fu}  % 傅老师
@@
 The significance statement appears in the paper itself and is required for all research papers.
-	It is a well-known fact that development of human societies backs on water use.
-	Therefore, as natural water cycle has been dominated by growing socio-economic processes towards a hydro-social water cycle, big river basins are roundly governed phase by phase for further water use.
-	We propose an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
-	Three water governance regimes are identified (massive supply, purpose turned, and all-sided governance), and a widespread regime-transition schema can be summarized after then. 
-	By linking the transition with major water governance challenges, the schema can be a useful guideline for big river basins all around the world in their sustainability. 
+	% 人类社会的发展和维持依赖于水。由于自然水循环被加速的社会经济过程推向水社会水循环，大的河流流域往往被控制阶段进一步用水。
+	Development and maintenance of human societies depends on water.
+As natural water cycles are pushed by accelerating socio-economic processes towards a hydrosocial water cycle, big river basins are often governed phase by phase for further water use.
+	% 我们提出了一种综合指标来检测水治理机制，并将其应用于快速变化的黄河流域。
+	We propose an integrated index to detect water governance regimes and apply it to the Yellow River Basin, a fast-changing basin.
+	% 确定了三种水治理机制(大规模供应、目的转变和全面治理)。
+	Three water governance regimes are identified (massive supply, purpose turned, and all-sided governance).
+	% 他们为大型河流流域提出了一般的政权过渡方案。
+	They suggest a general regime-transition schema for large river basins.
+	% 通过将河流治理转型与主要的水治理挑战联系起来，我们的方法可以为世界各地的大河流域提供有用的可持续发展指导方针。
+	By linking river basin governance transitions with major water governance challenges, our approach can offer useful sustainability guidelines for big river basins all around the world.
 }
@@
 	\label{abstract}
-	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
-	For water uses in sustaining socio-economic development, human have governed large rivers and led a transformation towards a hydro-social water cycle within basins all around the world. 
-	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
-	Since water governance regime decides who gets what water, when and how much, identification for its changes is critical to guiding efficient and sustainable water uses.
-	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
-	Here, combining three main dimensions (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) to detect regime shifts of water governance at a basin scale.
-	% 将该指数应用于典型的快速变化的流域——中国黄河流域，描绘了由环境、经济、社会和政治变化引起的长达半个世纪的三种水治理制度(大规模供应制度、目的性转向制度、全方位治理制度)之间的变迁。
-	By applying the index to a typical rapid-changing basin -the Yellow River Basin, China, shifts between three water governance regimes (massive supply regime, purpose turned regime, all-sided governance regime) throughout half a century are well painted, which were caused by environmental, economic social and political changes.
-	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
-	Based on that, we summarize a widespread transition schema of water governance regimes, paralleled with a transformative trajectory towards hydro-social water cycle in the Anthropocene.
-	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
-	Since different governance challenges mainly occurred at different phases in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
+	% 在许多大型河流流域，利用和管理河流以促进社会经济发展已经导致全球从自然水系向社会-生态水系或“水-社会”水系转变。
+	In many large river basins, the use and governance of rivers for socio-economic development has led to a global transformation from natural to social-ecological or ‘hydrosocial’ water regimes.
+	% 水治理决定谁、什么时候、得到多少水。因此，确定水管理体制如何以及何时改变，对于理解社会-生态水动力学和指导有效和可持续地使用水至关重要。
+	Water governance decides who gets water, when, and how much.
+Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
+	% 我们结合水治理的三个主要维度(供应、目的和配置)，开发了一个定量的综合水治理指数(IWGI)，可以检测流域尺度上的水治理机制变化。
+	We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
+	% 将该指标应用于一个快速变化的大流域(黄河流域)，结果表明，该指标能够描述三种水治理体制(大规模供水体制;purpose-turned政权;并提供了一种方法，将这些变化与环境、经济、社会和政治变化联系起来。
+	Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-turned regime; and all-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
+	% 我们对IWGI的应用提出了一个广泛的水治理机制转型模式和一个普遍的转型轨迹，作为理解人类世水文社会水循环的假设。
+	Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydro-social water cycles in the Anthropocene.
+	% 黄河转型的不同阶段所面临的不同治理挑战，也为大流域的协调治理提供了潜在的指导方针。
+	The different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines for the coordinated governance of big river basins in general.
 \end{abstract}
@@
 % 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
-\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for earth system processes, but also supporting development of human societies. 
-%* add references
+\dropcap{W}ater has been described as being “at the centre of the planetary drama of the Anthropocene” \cite{gleeson2020}.
 % 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
-Because of relying on water use, human activities have profoundly modified the natural water cycle and led a trajectory towards a hydro-social water cycle phase by phase
-\cite{gleeson2020,sivapalan2012,qin2014,abbott2019,levia2020}.
+It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle
+\cite{gleeson2020,sivapalan2012,qin2014,abbott2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
 % 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
-Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful water governance for sustainability
+Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
 \cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarre2019}. 
 % 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
-As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water
-\cite{biermann2012,steffen2020,dibaldassarre2019}
-% 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
-Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, especially at a basin scale.
+As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
+\cite{biermann2012,steffen2020,dibaldassarre2019}.
 
@@
 % 缺乏治理就是缺乏可持续性
-For water, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
+For water resources in populated areas, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
+% 确定向社会水循环过渡的第一个重要步骤是确定发生过渡的不同制度。
+A first important step in identifying transitions towards a hydrosocial water cycle is to identify the different regimes under which it occurs.
 % 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly: ``How much water can be used?
-(supply)'', ``How to balances different water use services?
-(purpose)'' and ``How to allocate water equally and efficiently?
-(allocation)''
+According to the United Nations Development Programme (UNDP), three key dimensions of water use are decided by the water governance regime directly: ``How much water can be used?'' (supply), ``How can different services provided by water be balanced?'' (purpose), and ``How can water be allocated equally and efficiently?'' (allocation)
 \cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
 % 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to huge impacts on the outcomes of system with widespread cascading effects 
+A regime is defined as a locally stable state of a system’s structure, function, and dominant controls. 
+Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
 \cite{rocha2018,gregr2020}.
 % 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Defined as regime shifts, therefore, it is a signal of substantive changes in water governance and may lead to new challenges to sustainability 
+Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability
 \cite{steffen2020}.
+
 % 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
-Along with environmental, economic, social and political changes, however, regime shifts of water governance can be triggered from each of the above key dimensions (supply, purpose, and allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
+In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation;
+\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}).
 % 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
-Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can be stressful because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
+First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
 \cite{greveGlobalAssessmentWater2018, wada2017, qin2019}.
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Secondly, there is trade-off between provisioning-purpose water services (such as domestic use and food production uses) and non-provisioning-purpose services (such as uses for industrial production or energy), which in need of weights through water governance
+Second, the purposes for which water is used are balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or fisheries); water may also provide a range of different non-consumptive regulating and cultural services, such as waste disposal or scenic values
 \cite{liu2017, florke2018}.
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Thirdly, since governance concerns water allocation at the whole basin, it is not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by changing social and political
+Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
+Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socioeconomic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
 \cite{roobavannan2017,speed2013}.
 % 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
-Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation).
-However, the lack of simple but comprehensive method in identifying changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).
+Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive method for identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
 
@@
 % 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
-The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
+As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details). 
+The YRB has experienced some of the most intense water use and dramatic regime shifts of any large river basin in China, giving rise to long-standing challenges for its governance.
 % 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use 
+From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
 \cite{song2020,li2020}. 
 % 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
-Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these high-sediment-caused issues were effectively contained 
+Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
 \cite{wang2016,wu2020}.
 % 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
-However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with
+However, water over-use has led to drying up of the Yellow River, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
 \cite{xia2012}.
 % 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
-Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance 
+Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
 \cite{wang2019, wohlfart2016}.
 % 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
-% 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
-Therefore, identifying the regime shifts for water governance within YRB can provide crucial insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.
+All in all, therefore, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
+% 因此，确定长江流域水资源管理制度的变化可以为了解世界上快速变化的大流域以及治理如何应对其可持续性挑战提供重要的见解。
+Identifying regime shifts in water governance within the YRB can thus provide crucial insights into the world’s rapidly-changing big river basins and the ways in which governance may respond to meeting challenges to their sustainability.
 
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, based on three key dimensions (supply, purpose and allocation) of water governance, we develop an Integrated Water Governance Index (IWGI) to detect changes of water governance at a basin scale (Figure~\ref{fig:framework}).
+We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (Figure~\ref{fig:framework}).
 % 使用案例研究
-By applying the index to a typical rapid-changing big river basin (the YRB), we analysed the complicated regimes shifts of water governance and their main causes in a comprehensive but simple way.
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
 % 最后总结出一般性框架
-Finally, a general regime transition schema is summarized, which can be a practicable guideline for big river basins to governance in a coordinated way towards sustainability since it reveals widespread challenges regarding water governance.
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
 
@@
 % 这一节主要展示IWGI的变化趋势和WUR的划分
-With two significant points, the changes of IWGI are detected into three periods (Figure~\ref{fig:IWGI}A). 
-Not only the slope of trends are various within each period, changes are also mainly contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
+With two significant breakpoints, the changes in the IWGI are divided into three periods (Figure~\ref{fig:IWGI}A) with different slopes. 
+The changes are contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI was rapidly increasing and the supply made the most striking positive contribution (131\%), while purpose and allocation had slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI increased rapidly. 
+Water supply made the most striking positive contribution (131\%), while purpose and allocation had a slight negative contribution (-11\% and -20\%).
 % 第二阶段
-In the second period (P2, 1979-1994), though contributions of purpose and allocation turned into positive, the IWGI experienced a drop because huge-declined supply capacity plays a larger negative role (-188\% dropped than P1).
+In the second period (P2, 1979-1994), the contributions of purpose and allocation became positive and the IWGI experienced a drop because steeply declining supply capacity played a larger negative role (dropping to -188\% lower than P1).
 % 第三阶段
-However, as the further increasing of positive contributions of purpose (75\%) and allocation (84\%), and decreases of water supply in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
+In the third period (P3, 1995-2013), as positive contributions from purpose (75\%) and allocation (84\%) increased further and the negative contribution of water supply lessened (-59\%), positive growth of the IWGI returned.
 
@@
 % 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
-Taken together, each period has the unique most striking positive contributor to IWGI, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
+Each period has a unique most striking positive contributor to IWGI. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
 % 第一阶段到第二阶段
-Throughout the whole P1, water governance regime dominated by increasing supply capacities.
-After then, it experienced a shift to slow down in increasing supply during the P2, with a reverse in the contributed proportion between purpose and allocation, too.
+Throughout P1, the water governance regime was dominated by increasing supply capacities. 
 % 第三阶段集中
-Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points highly concentrated at the centre of the ternary diagram.
+It then experienced a shift, slowing down in increasing supply during P2, with an accompanying reverse in the contributed proportion between purpose and allocation.
+Finally, the contribution of all three dimensions was similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points cluster at the centre of the diagram.
 % 总结来说，三个稳态
-All in all, there were three water governance regimes corresponding three different periods: massive supply regime (P1: 1965-1978), purpose turned regime (P2: 1979-1993), all-sided governance regime (P3: 1994-2013).
+The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-turned regime (P2: 1979-1993), and an all-sided governance regime (P3: 1994-2013).
 
@@
 % 经济总量提升导致资源耗竭的加速。
-Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the turn of purpose between P1 and P2.
-During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, \textit{SI Appendix} Fig.
+Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated area and the economic growth of industry and services were key to the change in purpose between P1 and P2.
+During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
 S3).
-Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off with more water demands (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water use (\textit{SI Appendix} S3).
+Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
 
 % 用水关系的变化
-Secondly, efficiency of water use changed from the P2 to the P3.
-While irrigated area resumed expansion again in the P3 (Figure\ref{fig:Causes}A), both industry, urban services were boosting their economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-However, because of the improved water use efficiency by technology and water conservation practices (\textit{SI Appendix} Fig.
-S4), both of them experienced significant declines in water use intensity (WUI) for unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S3).
+The efficiency of water use changed from P2 to P3.
+While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
+S4), However, because of more efficient technology and better water conservation practices (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
 
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and water governance policies played roles throughout all three regimes. 
-% 根据水库的位置，计算了各水库的区域用水量与盆地用水量之比。
-According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for supply rather than regulating (Figure~\ref{fig:Causes}C).
+Finally, environmental context, social transformation and water governance policies played roles in all three regimes.
+We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio), with a higher ratio representing a potential role for supply rather than regulation (Figure~\ref{fig:Causes}C).
 % 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guide of ``ethos of conquer nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant (\textit{SI Appendix} Fig.
-S5), as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
+Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1, when natural water resources were relatively abundant (\textit{SI Appendix} Fig.
+S5), and R/B ratios were significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In the P2, the number of new reservoirs decreases significantly and allocation of water were rigorously controlled by ``the 87 Water Diversion Scheme'', with little increment of total water storage capacities (\textit{SI Appendix} Fig.
+In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Diversion Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
 S6).
 % 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering the P3, myriad national-level water governance policies proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs are even higher for facilitating regulating, most of which were built in regions with lower R/B ratio (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
+Entering P3, myriad national-level water governance policies were proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs was even higher for facilitating and regulating objectives.
+Most of these were built in regions with lower R/B ratios (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
 S6).
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that three distinct but sequential governance regimes within YRB (Figure~\ref{fig:phases}): massive supply regime (1965-1978), purpose turned regime (1979-1993) and all-sided governance regime (1994-2013).
-Their shifts caused by different environmental, economic, social or political aspects (Figure~\ref{fig:Causes}).
+Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-turned regime (1979-1993) and an all-sided governance regime (1994-2013).
+Shifts between these regimes were caused by different environmental, economic, social or political drivers (Figure~\ref{fig:Causes}).
 % 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social water cycle, facing primarily economic and environmental challenges in the prophase while social and policy challenges in the anaphase (Figure~\ref{fig:summary}).
+It is important to note that each regime occurred gradually, with multifaceted causes, as the basin moves towards a hydrosocial water cycle.
+The challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
 
 % 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-At the massive supply regime (1965-1978), since the basin economy was mainly dependent on agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5), water governance tended to supply more resources for agriculture (by construction of reservoirs and channels for examples).
+During the massive supply regime (1965-1978), the basin economy was mainly dependent on the agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5); water governance thus tended to supply more resources for agriculture (e.g.
+by construction of reservoirs and channels).
 % 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects from socio-economic loops at this regime, water governance with few protective policies encouraged unlimited water supply for the required regions, with little consideration of the social equity and environmental impact over the basin, too
+Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
 \cite{zhou2020}. 
 % 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-Since nearly 80\% of surface water used (mainly for provisioning-purpose), the Yellow River dried up at the second half of the regime (\textit{SI Appendix} Figure S7). 
+Since nearly 80\% of surface water was used (mainly for provisioning purposes), the Yellow River dried up during the second half of the regime (\textit{SI Appendix} Figure S7). 
 % 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
-Ecological issues such as shrink of wetlands, declines of biodiversity emerged as the drying up became more and more serious, leading a huge crisis in environment which challenges water governance rigorously
+Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
 \cite{wohlfart2016}.
@@
 % “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of ``the purpose turned regime'' (1978) coincided with Chinese ``reform and opening-up'', the huge social transformation led the emerging industry and services broke the dominance of agriculture and competed for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
+The start of the purpose-turned regime (1978) coincided with Chinese ``reform and opening-up''.
+This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
 S8).
 % 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-Facing endless environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work regarding hydrology and basin management in YRB
+In the face of ongoing environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) underwent a reorganization and received instructions from the Ministry of Water Resources (then called the Ministry of Water Resources and Electric Power) to resume and strengthen work on hydrology and basin management in the YRB
 \cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
 % 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
-As results, the YRB introduced new policies and regulations ahead of the whole country (for an example, ``the 87 Water Diversion Scheme'') to allocate water and successfully stopped the expansion of irrigated water consumption
+As a result, new policies and regulations (e.g., ``the 87 Water Diversion Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water and successfully stop the expansion of irrigated water consumption
 \cite{wang2018}.
@@
 % 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next shift to all-sided governance regime was not brought until a significant increase in water use efficiency since about 1993, for overcoming resources limits  
+The next shift, to the all-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits  
 \cite{liuWaterconservancyprojects2013}. 
 % 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between regions and sectors in water demands played a more important role at this regime, water governance needs to meet efficient water allocating and balances between different purposes, under limited water supply
+Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
 \cite{dalin2015a}.
 % 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For an example, the water rights conversion project popularized since this regime may save regional agricultural water for industrial developments even in another region, while the water transfer is also another huge project to meet water demands within the YRB
+For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
 \cite{barnett2015,yunpeng2010}.
 % 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, the old water policy (i.g.
-``The 87 Water Diversion Scheme'') which once helped the YRB get rid of the environmental crisis, however, had become the shackle of social equity and coordinated allocation under the new regime because of path dependence
+On the other hand, the old water policy (e.g., ``The 87 Water Diversion Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
 \cite{wang2018}.
 % 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
-Anyhow, myriad national-level water policies were proposed or adjusted under this regime, as the absence of such policies gaps and social injustice regarding water use are becoming new structural challenges for governance
+Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
 \cite{konar2019}.
@@
 % 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
-In general, shifts of the three governance regimes occurred sequentially along with a transformation towards the hydro-social cycle.
+In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
 % 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
-This kind of transition may be widespread in socio-ecological systems, such as transition of ecosystem services and transition of economic-social developments, as increasing anthropogenic impacts gradually change the world at large
+Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
 \cite{best2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
+Some of the implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
+% *TODO 增加一个参考文献 MA 2000 
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-Regards to water governance we mainly concern, we find that the transition regimes echoes the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
+The transition regimes identified here echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
 S9)
@@
 % 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
-Resource challenges represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and highly related to economic and environmental changes
+Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
 \cite{allan2019,florke2018,liu2012}. 
 % 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Other side, highly-controlled and developed basins (especially for transboundary rivers) are mainly bothered by structural challenges such as water disputes or lack of equity, and in urgent need of flexible and efficient governance structure for social and political aspects
+Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
 \cite{kitroeff2020,roobavannan2017,unep-dhi2016}.
 % 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
-It is very representative that resource challenges and structural challenges have occurred successively along the transition of water governance within the YRB, because of rapid-changing regimes.
+It is typical that resource challenges and structural challenges have occurred sequentially during the transition of water governance within the YRB. 
 % 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Based on that, our analysis suggests that the prophase of transition often leads resource challenges by economic and environmental changes, while the anaphase is dominated by structural challenges regarding social and political aspects.
+Our analysis thus suggests that the initial phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
 % 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-Aligned with the core dimensions emphasized by UNDP regarding water governance, this schema paints resonances between the governance challenges and basins' transformation towards a hydro-social water cycle, again.
+From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
+
+Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes.
+Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
+Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects.
+(example from the YRB – e.g., tradeoffs between income for local farmers vs national growth needs supported by water-dependent industries?)
 
@@
 % 我们发展的指数捕捉了水治理的过渡制度，以一种相对全面但简单的方式
-The index we developed (IWGI), captures the transition regimes of water governance with different challenges, in a relatively simple but comprehensive way.
+The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
 % 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
@@
 \cite{cummingLinkingEconomicGrowth2018,reyers2018}.
+% 在一种制度下开发的模型和方法在另一种制度下不一定有用。
+Models and approaches developed under one regime are not necessarily useful under a different regime.
 % 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
-For today's world, water-related challenges remains one of the major gaps towards sustainability, while development-first strategies are still the main guideline to conquer them rather than optimizing governance
+For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
 \cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
 % 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
-Although most large river basins improved water management technologies and water use efficiency along with development, most studies still pessimistically carried out that freshwater use is reaching planetary boundaries where human-water systems may collapse
+Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
 \cite{li2020a,degraaf2019,huggins2020}.
 % 总的来说，这可能有两点主要原因。
-Overall, there are probably two main reasons.
+Overall, there are probably two main reasons for this apparent failure of governance.
 % 首先，效率悖论
-Firstly, significant improvement in agricultural irrigation efficiency is usually accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency
+First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
 \cite{grafton2018}. 
 % 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
-Secondly, without successful governance, complicated structure dominated by hydro-social water cycle may lead a more inflexible water use and undermined to resilience of social-ecological systems at a basin scale
+Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
 \cite{qin2019,levia2020,grill2019}.
 % 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
-From these perspectives, we need comprehensive strategies to address the governance challenges correspondingly, because the heart factors of are beyond the control of any related aspect alone
+From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage 
 \cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
 % 基于对治理体制转型对理解，我们可以创造有利条件以应对挑战，并保持流域社会-生态系统对弹性，以实现可持续发展。
-Based on a deeper understanding of governance regime transition, we can create favourable status of or maintain the resilience of the basin's socio-ecological system, for meeting the challenges towards sustainability.
+A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
 
@@
 \matmethods{
-Here, we constructed the Integrated Water Governance Index (IWGI) which consists of three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
-Each dimension is reflected by an independent indicator after normalization, and water governance regime were characterized by combination of impacts of each dimension in periods.
-In addition, the contribution to changes of IWGI index along with each main indicators were decomposed and calculated separately for each regime period.
+We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
+Each dimension is reflected by an independent indicator after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different time periods.
+The contribution to changes of IWGI index along with each main indicator were also decomposed and calculated separately for each regime period.
 
@@
 	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to the transformation towards hydro-social water cycle in three dimensions below (see \textit{SI Appendix} Methods S4 for details)
+	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see \textit{SI Appendix} Methods S4 for details)
 	\cite{steffen2018,abbott2019,levia2020}:
@@
 		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item The socio-economic dominance may lead to further demands of water supply (S) because of increasing water withdrawals.
-However, an effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development along with the transformative trajectory, means:
+		\item Socio-economic dominance may lead to further demands on the water supply (S) because of increasing water withdrawals.
+However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
 		$$ Transformation \propto S^{-1} $$
-		\item The transformation is usually accompanied by a tilt of purpose in water governance towards socio-economic services (usually non-provisioning purposes), because of higher returns:
+		\item Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
 		$$ Transformation \propto P $$
 		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item The transformation usually lead to more complicated structure in water allocation, which is mainly a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
+		\item Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
 		$$ Transformation \propto A $$ 
@@
 	% 将三者合一起，即：
-	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with the transformation towards hydro-social water cycle:
+	We combined these three dimensions into a single integrated index, keeping their positive or negative relationship with the transformation towards a hydrosocial water cycle:
 
@@
 	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
-Then, the above equation is transformed into a natural logarithm to facilitate calculation:
+	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
+Then, the above equation was transformed into a natural logarithm to facilitate calculation:
 
@@
 
-	Assuming they have equal weights, the Integrated Water Governance Index (IWGI):
+	Assuming they have equal weights, the Integrated Water Governance Index (IWGI) is:
 
@@
 	\subsubsection*{Normalization}
-	In fact, we have tested different normalization methods and it makes no difference in change points detection (see \textit{SI Appendix} Methods S5.
+	We tested different normalization methods, and they made no difference in change points detection (see \textit{SI Appendix} Methods S5.
 Sensitivity analysis).
-In this study, finally, we performed min-max normalization as the formulation below:
+We performed min-max normalization using the formulation below:
 
@@
 	\subsubsection*{Indicator of Stress}
-	We refer to the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qin2019}.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qin2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
-For the whole YRB, indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
+For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
 
@@
 	\subsubsection*{Indicator of purpose}
-	To purpose $I_P$, we use Non-provisioning purpose Shares (NPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, the non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-Then, we can calculate the NPS by:
+	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
+While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
+We calculated the NPS as:
 
@@
 	\subsubsection*{Indicator of allocations}
-	%$CEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
+	%$AEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
 	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To description of allocations $I_C$, we designed an indicator by imitation of information entropy, called allocation Entropy Metric (CEM), a metric to measure the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
-	While our indicator $I_C$ should reflect that with the development of society, water resources allocation is more balanced among regions and generally meets the needs of different sectors (means smaller gaps, too), but different regions have a trend of division of labour among various sectors (with larger gaps):
+	To describe allocations $I_C$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
+	Our indicator $I_C$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
 
-	$$ I_C = \frac{CEM_{r}*CEM_{s}}{CEM_{rs}}$$
+	$$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
 
-	where $CEN_{r}$ and $CEN_{s}$ are allocation Entropy Metric in different regions and different sectors.
-$CEN_{rs}$ is differences between sectors in a certain region to the whole basin (see \textit{SI Appendix} Methods S4).
+	where $AEM_{r}$ and $AEM_{s}$ are Allocation Entropy Metric in different regions and different sectors.
+$AEM_{rs}$ describes differences between sectors in a certain region relative to the whole basin (see \textit{SI Appendix} Methods S4).
 
@@
 
-		With no assumptions about the distribution of the data, the Pettitt (1979) approach of changing points detection is commonly applied to detect a single change-point in hydrological series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
-		It tests the $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
+		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
+		It tests $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
 The non-parametric statistic is defined as:
@@
 		The change-point of the series is located at $K_T$, provided that the statistic is significant.
-We use 0.001 as the threshold  of p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), which means the probability of a statistically significant change-point judgment being valid is more than $99.9\%$.
-		Since this method only can return one significant change point, we repeat it Until all significant change points were detected.
+We used 0.001 as the threshold p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
+		Since this method can only return one significant change point, we repeated it until all significant change points were detected.
 
@@
 	\subsection*{Contribution decomposition}
-		We have decomposed the amount of variation in each index at different periods in order to observe the contribution of each influencing factor to them.
-Use Integrated Water Resources governance (IWGI) Index as an example, which influenced by three dimensions' normalized indicator: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
+		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index.
+Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
@@
 All the datasets used are listed in the \textit{SI Appendix} table S1.
-A detailed description of the data can be seen in the supplementary materials \textit{SI Appendix} Methods S2.
+A detailed description of the data is provided in the supplementary materials \textit{SI Appendix} Methods S2.
 }

### 2021-02-27 tex/main/manuscript.tex
polish figure captions according to Cummig

@@
 	% 确定了三种水治理机制(大规模供应、目的转变和全面治理)。
-	Three water governance regimes are identified (massive supply, purpose turned, and all-sided governance).
+	Three water governance regimes are identified (massive supply, purpose turned, and many-sided governance).
 	% 他们为大型河流流域提出了一般的政权过渡方案。
@@
 	% 将该指标应用于一个快速变化的大流域(黄河流域)，结果表明，该指标能够描述三种水治理体制(大规模供水体制;purpose-turned政权;并提供了一种方法，将这些变化与环境、经济、社会和政治变化联系起来。
-	Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-turned regime; and all-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
+	Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-focused regime; and many-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
 	% 我们对IWGI的应用提出了一个广泛的水治理机制转型模式和一个普遍的转型轨迹，作为理解人类世水文社会水循环的假设。
@@
 	\caption{
-		A framework for understanding the relationship between transformation towards hydro-social cycle and transitional water governance regimes, with our main goal in detecting regime shifts by a simple and comprehensive index.
+		A framework for understanding the relationship between transitional water governance regimes and eventual transformation to a hydrosocial cycle.
+A key missing element in current knowledge is an ability to detect regime shifts using a simple and comprehensive index.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
+		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
 Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
-(2) ``purpose'' weighted between provisioning services or non-provisioning services.
+(2) ``purpose'' is weighted between consumptive services or non-consumptive uses.
 (3) ``allocation'' changes between balanced or lopsided.
 		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B,} the governance changes combined the three dimensions.
-Because the above three dimensions change along with the trajectory towards hydro-social water cycle, combined water governance status is also various with that.
-When abrupt change occurs during this process, it may indicate a regime shift in water governance
+		\textbf{B:} governance changes are an emergent outcome of trends across the three dimensions.
+Water governance status changes along a trajectory towards a hydrosocial water cycle.
+When abrupt change occurs, it may indicate a regime shift in water governance
 		\cite{steffen2018,abbott2019,levia2020}.
@@
 	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
-	\caption{Changes of the IWGI index. 
-	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI have three different periods in changing trend.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation have made the main positive contributor of P1, P2 and P3, respectively.
+	\caption{Changes in the IWGI index. 
+	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
+	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were respectively the main positive contributors to P1, P2 and P3.
 	}
@@
 	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions regards three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
-	The red indicator line in this ternary plot denotes 1:1 contributions between purpose (P) and allocation (A).
-When the points are bellow this line, the contribution ratio of allocation is lower than that of function, and vice versa.}
+	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
+The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
+	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
+When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
@@
 % 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-turned regime (P2: 1979-1993), and an all-sided governance regime (P3: 1994-2013).
+The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-focused regime (P2: 1979-1993), and a many-sided governance regime (P3: 1994-2013).
 
@@
 	\caption{
-		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
-		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Methods S2).
-		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time.
-Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management.
-Size of the points indicates their magnitude of water storage capacities.
-Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River.
-(2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply.
-These marked reservoirs, therefore are more significant for the entire basin, rather than regional development.
-		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
-Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
+		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
+		\textbf{A.} Changes in total irrigated area (orange line), and water consumptions per unit of area (green dot line, see \textit{SI Appendix} Methods S2).
+		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use intensity for unit production (WUI, red dot line) respectively (\textit{SI Appendix} Methods S2).
+		\textbf{C.} Completed time of each new reservoir and their surrounding region's water use percentages as a proportion of the basin's total water use (WU) at that time.
+Red circles denote hub reservoirs in the basin, which play a role in integrated basin water management.
+		The size of each circle indicates the magnitude of its water storage capacity.
+Some important reservoirs include: (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing flood water discharge and water supply.
+The named reservoirs are significant for the entire basin, not only for regional development.
+		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
+In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
 	}
@@
 	\caption{
-		Transition schema of water governance along with the transformation towards hydro-social water cycle.
-Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops.
-There is a transformation towards the hydro-social water cycle where red loop increases.
+		Transition schema of water governance during transformation towards a hydrosocial water cycle.
+Blue pathways are dominated by natural water cycle while red pathways are dominated by socio-economic feedbacks.
+There is a transformation towards the hydrosocial water cycle where red loop increases.
 		\textbf{A.
-Prophase} With socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
-What's more, better organized socio-economic system and better technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle.
+Early phase.} As socio-economic systems develop, industry and services gradually demand increasing amounts of water; at the same time, increasing social organization and technological capacity allow people to manage water resources more intensively, including intensive intervention in the natural water cycle.
 		\textbf{B.
-Anaphase} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes highly prominent.
-Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore.
-		\textbf{C.
-Transformation from a natural water cycle towards the hydro-social water cycle.} The above transition paralleled with the transformation towards hydro-social water cycle and generally distinguished when water resource limits reached.
-The three water governance regimes in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose turned regime, Regime 3: all-sided governance regime).
+Late phase} With further developed and economically efficient industries and services, trade-offs between provisioning-purpose and non-provisioning water use become prominent.
+Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
+		Thus, \textbf{C.
+Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle.
+This is generally distinguished when water resource limits are reached.
+The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
 		\textbf{D.
-Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the prophase while social and policy challenges in the anaphase.
+Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
 	}
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-turned regime (1979-1993) and an all-sided governance regime (1994-2013).
+Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-focused regime (1979-1993) and a many-sided governance regime (1994-2013).
 Shifts between these regimes were caused by different environmental, economic, social or political drivers (Figure~\ref{fig:Causes}).
@@
 % “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of the purpose-turned regime (1978) coincided with Chinese ``reform and opening-up''.
+The start of the purpose-focused regime (1978) coincided with Chinese ``reform and opening-up''.
 This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
@@
 % 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next shift, to the all-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits  
+The next shift, to the many-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits  
 \cite{liuWaterconservancyprojects2013}. 

### 2021-02-28 tex/main/manuscript.tex
Rectified according to Cumming's comments

@@
 Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle
-\cite{gleeson2020,sivapalan2012,qin2014,abbott2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
+\cite{gleeson2020,sivapalanSociohydrologynewscience2012,qin2014,abbottwatercycleAnthropocene2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
 % 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
 Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
-\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarre2019}. 
+\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarreSociohydrologyScientificChallenges2019}. 
 % 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
 As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
-\cite{biermann2012,steffen2020,dibaldassarre2019}.
+\cite{biermann2012,steffen2020,dibaldassarreSociohydrologyScientificChallenges2019}.
 
@@
 % 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-A regime is defined as a locally stable state of a system’s structure, function, and dominant controls. 
+A regime is defined as a locally stable state of a system’s structure, function, and dominant controls \cite{carpenterEarlyWarningsRegime2011}. 
 Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
@@
 First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{greveGlobalAssessmentWater2018, wada2017, qin2019}.
+\cite{greveGlobalAssessmentWater2018, wada2017,qinFlexibilityintensityglobal2019}.
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
 Second, the purposes for which water is used are balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or fisheries); water may also provide a range of different non-consumptive regulating and cultural services, such as waste disposal or scenic values
-\cite{liu2017, florke2018}.
+\cite{liu2017, florke2018,kleemannQuantifyinginterregionalflows2020}.
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
 Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
-Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socioeconomic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
+Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
 \cite{roobavannan2017,speed2013}.
@@
 From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
-\cite{song2020,li2020}. 
+\cite{songSedimenttransportincreasing2020a,li2020}. 
 % 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
 Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
-\cite{wang2016,wu2020}.
+\cite{wangReducedsedimenttransport2016,wu2020}.
 % 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
@@
 Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
-\cite{wang2019, wohlfart2016}.
+\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallenges2016}.
 % 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
@@
 When abrupt change occurs, it may indicate a regime shift in water governance
-		\cite{steffen2018,abbott2019,levia2020}.
+		\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}.
 	}
@@
 		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in total irrigated area (orange line), and water consumptions per unit of area (green dot line, see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use intensity for unit production (WUI, red dot line) respectively (\textit{SI Appendix} Methods S2).
+		\textbf{A.} Changes in total irrigated area (orange line), and water uses in per unit of area (WU/A, green dot line, see \textit{SI Appendix} Methods S2).
+		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use for unit production (WU/GVA, red dot line) respectively (\textit{SI Appendix} Methods S2).
 		\textbf{C.} Completed time of each new reservoir and their surrounding region's water use percentages as a proportion of the basin's total water use (WU) at that time.
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.jpg}
+	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.png}
 	\caption{
@@
 Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
-\cite{zhou2020}. 
+\cite{zhouDecelerationChinahuman2020}. 
 % 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
@@
 Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
-\cite{wohlfart2016}.
+\cite{wohlfartSocialecologicalchallenges2016}.
 
@@
 Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
-\cite{dalin2015a}.
+\cite{dalinBalancingwaterresource2015}.
 % 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
@@
 Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
-\cite{konar2019}.
+\cite{konarExpandingScopeFoundation2019}.
 
@@
 Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
-\cite{best2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
-Some of the implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
-% *TODO 增加一个参考文献 MA 2000 
+\cite{bestPaceHumanInducedChange2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
+Some of the implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario \cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
@@
 Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
-\cite{allan2019,florke2018,liu2012}. 
+\cite{allan2019,florke2018,liuWaterSustainabilityChina2012}. 
 % 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
 Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
-\cite{kitroeff2020,roobavannan2017,unep-dhi2016}.
+\cite{kitroeff2020,roobavannan2017,unep-dhiTransboundaryRiverBasins2016}.
 % 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
@@
 Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
+% 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
+For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi reservoir of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time.
+% 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
 Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects.
-(example from the YRB – e.g., tradeoffs between income for local farmers vs national growth needs supported by water-dependent industries?)
 
@@
 It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
-\cite{cummingLinkingEconomicGrowth2018,reyers2018}.
+\cite{cummingLinkingEconomicGrowth2018,reyersSocialEcologicalSystemsInsights2018}.
 % 在一种制度下开发的模型和方法在另一种制度下不一定有用。
@@
 Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
-\cite{li2020a,degraaf2019,huggins2020}.
+\cite{li2020a,degraafEnvironmentalflowlimits2019,huggins2020}.
 % 总的来说，这可能有两点主要原因。
@@
 Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
-\cite{qin2019,levia2020,grill2019}.
+\cite{qinFlexibilityintensityglobal2019,levia2020,grill2019}.
 % 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
@@
 	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see \textit{SI Appendix} Methods S4 for details)
-	\cite{steffen2018,abbott2019,levia2020}:
+	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure~\ref{fig:framework} and \textit{SI Appendix} Methods S4 for details)
+	\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}:
 
@@
 		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item Socio-economic dominance may lead to further demands on the water supply (S) because of increasing water withdrawals.
+		\item \textbf{Supply($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
 However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
 		$$ Transformation \propto S^{-1} $$
-		\item Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
+
+		\item \textbf{Priority($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
 		$$ Transformation \propto P $$
+
 		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
+		\item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
 		$$ Transformation \propto A $$
+
 	\end{itemize}
@@
 
-	\subsubsection*{Indicator of Stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qin2019}.
+	\subsubsection*{Indicator of supply}
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityintensityglobal2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).

### 2021-03-04 tex/main/manuscript.tex
Rectified by Cumming's comments.

@@
 \author[e]{Yongping Wei} % 尉老师
-\author{Graeme S. Cumming} % Cumming
+\author[f]{Graeme S. Cumming} % Cumming
 \author[a, b, 1]{Bojie Fu}  % 傅老师
@@
 	Australia
+}
+\affil[f]{
+	ARC Centre of Excellence for Coral Reef Studies, 
+	James Cook University, 
+	Townsville 4811, 
+	QLD, Australia
 }
@@
 However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), However, because of more efficient technology and better water conservation practices (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+S4), both experienced significant declines in water use for unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
 As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
@@
 
-\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}
+\acknow{Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).}
 

### 2021-03-04 tex/main/manuscript.tex
update everything after Cumming's comments

@@
 % 通讯作者信息
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: shuaiwang@bnu.edu.cn}
+\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: fubj@bnu.edu.cn}
 
@@
 	% 我们对IWGI的应用提出了一个广泛的水治理机制转型模式和一个普遍的转型轨迹，作为理解人类世水文社会水循环的假设。
-	Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydro-social water cycles in the Anthropocene.
+	Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydrosocial water cycles in the Anthropocene.
 	% 黄河转型的不同阶段所面临的不同治理挑战，也为大流域的协调治理提供了潜在的指导方针。
@@
 % 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability
-\cite{steffen2020}.
+Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability.
 
-% 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
-In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation;
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}).
-% 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
+% 除了由关键的环境、经济、社会和政治变量的变化引起外，水治理的制度变迁也可以通过治理的三个关键维度(供应、目的和分配)
+In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation)
+\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
+% 首先，水的供应不仅取决于天气(许多地区的长期趋势令人担忧，如冰川的消失)，还取决于诸如灌溉和工业等经济活动的需求;蓄水可以解决部分问题，但不能解决所有问题
 First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
@@
 % 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Second, the purposes for which water is used are balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or fisheries); water may also provide a range of different non-consumptive regulating and cultural services, such as waste disposal or scenic values
+Second, the purposes for which water is used are in need of balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or urban services)
 \cite{liu2017, florke2018,kleemannQuantifyinginterregionalflows2020}.
+% 水治理可以看作是为每一个不同的目的分配权重并执行结果规则的过程。
+Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
 % 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
 Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (Figure~\ref{fig:framework}).
+We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (see Figure~\ref{fig:framework} and methods).
 % 使用案例研究
@@
 % 最后总结出一般性框架
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
+Finally, we propose a general regime transition scheme as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
 
@@
 
-% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
+% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
 Each period has a unique most striking positive contributor to IWGI. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
@@
 		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
-In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
+In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Allocation Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
 	}
@@
 
-% 经济总量提升导致资源耗竭的加速。
+% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
 Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated area and the economic growth of industry and services were key to the change in purpose between P1 and P2.
+% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
 During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
 S3).
-Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
+% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
+Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
 
-% 用水关系的变化
+% 水分利用效率由P2变化到P3。
 The efficiency of water use changed from P2 to P3. 
@@
 However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), both experienced significant declines in water use for unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+S4), both experienced significant declines in water use for unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
 As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
@@
 Finally, environmental context, social transformation and water governance policies played roles in all three regimes. 
+% 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio), with a higher ratio representing a potential role for supply rather than regulation (Figure~\ref{fig:Causes}C).
@@
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Diversion Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
+In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Allocation Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
 S6).
@@
 % 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
-As a result, new policies and regulations (e.g., ``the 87 Water Diversion Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water and successfully stop the expansion of irrigated water consumption
+As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
 \cite{wang2018}.
@@
 % 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, the old water policy (e.g., ``The 87 Water Diversion Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
+On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
 \cite{wang2018}.
@@
 
-% 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
+% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
 In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
-% 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
+% 随着越来越多的人为影响逐渐改变世界，对生态系统动力学从生物物理控制向社会和政治控制的转变可能在社会-生态系统中变得越来越普遍
 Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
 \cite{bestPaceHumanInducedChange2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
-Some of the implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario \cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
+Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
+\cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
@@
 
+% 随着河流流域在不同制度之间的过渡而发生的升级过程也带来了额外的挑战。在经济力量的影响下，水资源利用逐渐从一个地方性的问题转变为国家或国际的问题，大型河流流域成为生态系统服务、经济发展和人类福祉的重要来源。
 Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes.
@@
 % 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
-For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi reservoir of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time.
+For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi Dam of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time
+\cite{kongEnvironmentalimpactassessments2017}.
 % 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
-Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects.
+Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
+\cite{cummingQuantifyingSocialEcologicalScale2020}.
 
@@
 
-% 我们发展的指数捕捉了水治理的过渡制度，以一种相对全面但简单的方式
+% IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
 The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
-% 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
+% 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
 It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
@@
 Models and approaches developed under one regime are not necessarily useful under a different regime.
-% 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
+% 就当今世界而言，与水有关的挑战仍是我们在实现可持续性方面取得进展的主要差距之一，而发展优先战略在许多地方仍是主导方针，可能不利于改善治理
 For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
 \cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
-% 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
+% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
 Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
 \cite{li2020a,degraafEnvironmentalflowlimits2019,huggins2020}.
-% 总的来说，这可能有两点主要原因。
+% 总的来说，这种明显的治理失败可能有两个主要原因。
 Overall, there are probably two main reasons for this apparent failure of governance.
-% 首先，效率悖论
+% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
 First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
 \cite{grafton2018}. 
-% 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
+% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
 Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
 \cite{qinFlexibilityintensityglobal2019,levia2020,grill2019}.
-% 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
+% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
 From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage 
 \cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
-% 基于对治理体制转型对理解，我们可以创造有利条件以应对挑战，并保持流域社会-生态系统对弹性，以实现可持续发展。
+% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
 A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.

### 2021-03-04 tex/sup/supplementary_information.tex
Rectified according to Cumming's comments
update everything after Cumming's comments

@@
 
-\title{Regime transition identification for water utilization in river basin developments}
-\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Bojie Fu (complete author list)}
-\correspondingauthor{Shuai Wang.\\E-mail: shuaiwang@bnu.edu.cn}
+\title{Identifying regime transitions for water governance at a basin scale}
+\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Graeme S. Cumming, Bojie Fu (complete author list)}
+\correspondingauthor{Bojie Fu.\\E-mail: fubj@bnu.edu.cn}
 
@@
 \SItext{This supplementary document consists of 5 \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables. 
-Firstly, we introduced our study area, the Yellow River Basin, and its subdivisions in the section Methods S1.
-Then, we give a detailed description of used datasets and analysis their uncertainties in the section Methods S2.
-Further, we introduced how to harmonized different datasets with various spatial and temporal scales in Methods S3.
+% 在方法S1部分，我们介绍了我们的研究区域——黄河流域及其区域划分。
+In the section Methods S1, we introduced our study area, the Yellow River Basin, and its subdivisions of regions. 
+% 在Methods S2部分，我们给出了使用的数据集的详细描述和分析它们的不确定性。
+In the section Methods S2, we give a detailed description of used datasets and analysis their uncertainties. 
+For the section Methods S3, we introduced how to harmonize different datasets with various spatial and temporal scales. 
 Then, the indicators corresponding to the IWRU are introduced in the section Methods S4. 
-Finally, we proposed a sensitivity analysis in the section Methods S5, to test the robustness of our results.}
+Finally, we proposed sensitivity analysis in the section Methods S5, to test the robustness of our results.}
 
@@
 \subsection*{Region divisions of Yellow River Basin}
-
+% 研究区为黄河流域(YRB，图S1-A)，是中国水资源开发最强烈、管理体制变化最剧烈的区域。
 The study area is the Yellow River Basin (YRB, see Fig. S1-A), which had experienced the most intense water exploitation and the most dramatic shifts of management regime in China. 
-According to the Yellow River Conservancy Commission (YRCC), an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by the characteristic of river.
+% 根据黄河水利委员会(水利部下属的流域一级行政政府)的研究，黄河的上、中、下游可由河流特征来区分。
+According to the Yellow River Conservancy Commission (YRCC), an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by the physics characteristic of river.
+% 但也有一种方案认为上游仅指人为干扰少、蓄水量大的河源区。
 However, there is another scheme suggesting that the upstream only refers to river source areas with little human disturbance and high water retention capacity.
-% TODO 这里补充参考文献，黄河上游的划分争议 
-Anyhow, since the socio-economic and natural conditions were both considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
+% 无论如何，由于本研究同时考虑了社会经济条件和自然条件，我们将上述两种方案结合起来，将黄河流域划分为四个区域，并以三个重要的水文控制站加以区分(见图S1-B)。
+Since the socio-economic and natural conditions were both considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
 S1-B).
+% 之前的研究也表明，当考虑流域的社会用水和自然条件时，这样的划分是有效的，因为区域之间具有很强的异质性(见图S1-C)。
 Previous studies have also shown that such a division is valid when both social water use and the natural conditions of the basin are considered, as the regions exhibit strong heterogeneity among themselves (see Fig.
@@
 \begin{itemize}
-    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region.
-The most ecology function here is water conservation, as sparsely populated and less economically developed.
+    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region. The most ecology function here is water yield, as sparsely populated and less economically developed.
     \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region.
@@
 
-In general, there are inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (see Fig.
+% 总体来看，黄河流域在经济布局、水资源分布、用水量分布、人口分布等方面存在明显的区域差异(图S2)。
+In general, there are obvious inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (see Fig.
 S2).
+% 在这些根本差异的基础上，社会发展和流域管理继续影响和重塑它们的变化，使黄河流域成为世界上联系最密切、变化最剧烈的大流域。
 On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin.
+% 特别是水资源对长江流域的社会发展做出了不可替代的贡献。
 Specially, Water resources make an irreplaceable contribution to the development of society in the YRB. 
-Each sector of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig.
-S3).
-Thus, as a case study for analysing the evolution of the human-water relationship, it possesses typicality.
+% 因此，作为分析人水关系演变的个案研究，具有典型性。
+Thus, as a case study for analysing the evolution of the human-water relationship, the YRB possesses typicality.
 
@@
 \begin{itemize}
+    % 首先，长江三角洲自古以来就受到人类活动的强烈干预，近60年来变化最为剧烈。近60年来，在人类活动的影响下，黄河地表径流、输沙和人类用水格局均经历了多次变迁
     \item Firstly, the YRB has been subject to strong intervention by human activities since ancient times, while the last 60 years have seen the most dramatic changes.
 Under human influence, the Yellow River's surface runoff, sediment transport, and human water consumption patterns have all undergone multiple regime shifts in the last 60 years
-    % \cite{}.
-    % TODO 这里增加参考文献，黄河近六十年的变化 
+    \cite{wu2020,wangReducedsedimenttransport2016}.
+    % 第二，人类活动对长江流域的景观产生了重大影响，这不仅改变了自然水循环，也改变了社会水循环。例如，“退耕还林”工程使长江铁路中部地区的景观发生了重大变化。随着易受侵蚀地区森林的增加，该地区的水利用模式和中下游的地表径流模式已发生根本改变。
     \item Secondly, landscapes in the YRB have significantly altered by human activities, which can both change the natural and the social water cycle.
-For an example, “grain for green” project has produced a significant change of landscapes in the middle region (MR) of YRB.
-With the addition forest in an erosion-prone area, water use patterns in the area and surface runoff patterns in the middle and lower reaches have been radically altered.
-    % TODO 这里增加参考文献  景观的变化 \cite{}
-    \item Thirdly, a series of management practices have promoted in order to govern the YRB.
-Since the establishment of the Yellow River Water Conservancy Commission in XX, the agency has continued to reform and expand, eventually forming a basin management agency with unified coordination, scheduling and regulatory functions.
-Since the promulgation of the Water Law in xxx, the Ministry of Water Resources, the YRCC and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws (see \textit{SI Appendix} Table S2).
+For an example, ``grain for green'' project has produced a significant change of landscapes in the Middle Region (MR) of the YRB.
+With the addition forest in an erosion-prone area, water use patterns in the area and surface runoff patterns in the middle and lower reaches have been radically altered
+    \cite{wu2020}.
+    \item Thirdly, a series of management practices have promoted in order to manage the YRB.
+Since the establishment of the Yellow River Water Conservancy Commission, the agency has continued to reform and expand, eventually forming a basin management agency with unified coordination, scheduling and regulatory functions \cite{yellowriverconservancycommissionYellowRiverBasin2013}.
+    As results, the Ministry of Water Resources, the YRCC and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws (see \textit{SI Appendix} Table S2).
 \end{itemize}
-Historic and recent river basin management practices have strong impacts on water utilization.
+% Historic and recent river basin management practices have strong impacts on water utilization.
 
@@
 \begin{itemize}
-    \item \textbf{The Ethos of Conquering Nature (since 1958)} Conquering the natural movement, although the Yellow River basin was poor and backward at that time, a collective spirit of 'man can conquer nature' was formed.
-In addition to the construction of large-scale water conservancy projects represented by the Yellow River 'The Hongqi Channel', dramatic changes such as the' Great Leap Forward' movement and ``Large-scale production'' movement were also formed in this transformation.
+    \item \textbf{The Ethos of Conquering Nature (since 1958)} Conquering the natural movement, although the Yellow River basin was poor and backward at that time, a collective spirit of ``man can conquer nature'' was formed.
+In addition to the construction of large-scale water conservancy projects represented by the Yellow River ``The Hong Qi Channel'', dramatic changes such as the ``Great Leap Forward'' movement and ``Large-scale production'' movement were also formed in this transformation.
     \item \textbf{The Reform and Opening-up (since 1978).} Before the reform and opening up, the allocation of resources and production activities throughout China, including the Yellow River Basin, were led by the state.
@@
 However, after the water diversion scheme was proposed, the Yellow River Basin formed social rules to control water use indicators from top to bottom, from the province to the urban area to all departments.
-    \item \textbf{Environmental Regulation (since 2003).} Environmental issues, including water governance, have become a key KPI for local officials in China since a new leader took office in 2003 with an emphasis on environmental issues.
+    % 自2003年新一届领导人上任以来，包括水治理在内的环境问题已成为中国地方官员的关键考核指标。
+    \item \textbf{Environmental Regulation (since 2003).} Environmental issues, including water governance, have become key indicators for local officials in China since a new leader took office in 2003 with an emphasis on environmental issues
+    \cite{heWateringEnvironmentalRegulation2020}. 
 \end{itemize}
@@
 % 使用了GDP数据，年鉴数据，还有从第二次水资源调查提取的数据
-For statistics, we used GDP data, water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhouDecelerationChinaHuman2020} and statistical yearbook data of YRB.
+For statistics, we used GDP data, water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhouDecelerationChinaHuman2020} and statistical yearbook data of YRB \url{http://www.yrcc.gov.cn/other/hhgb/}.
 GDP data from the China Macro data in the Wind database, which firstly aggregated from annual reports of the provinces.
@@
 Since then, the statistics from the survey using the same criteria have been supplemented and harmonized to the 2013 administrative divisions.
-%TODO xx 这里把每个数据的子类介绍清楚
-The data covers a total of subcategories of water use under four broad categories: agriculture, industry, urban and rural, but does not distinguish between surface water and groundwater.
-There is uncertainty at the county scale for each disaggregated water use sector, but because the data are corrected for statistical information using the water balance method, the data are adequate for the regional scale and the four broad water use categories used in this study.
-Finally, in order to make a simple distinction between the proportion of surface water and groundwater extraction where needed, we use basin-scale water resources annual reporting data.
-Yearbook data of YRB documenting surface water resources and groundwater resource extraction in each watershed and province.
+
+The data covers a total of subcategories of water use under four broad categories: agriculture (IRR), industry (IND), urban (URB) and rural (RUR) water uses (see Zhou et al., for details \cite{zhouDecelerationChinahuman2020}).
+There is uncertainty at the county scale for each disaggregated water use sector, but because the data are corrected for statistical information using the water balance method, the data are adequate for the regional scale used in this study.
+
+Finally, in order to make a simple distinction the proportion of surface water and groundwater uses, we calculate a basin-scale ratio between the two types of water use, by yearbook data.
 
 \subsection*{Hydrological datasets}
-For hydrological datasets, reservoirs data and a measured runoff data were used in this study.
-The reservoir dataset were collected by Wang et al.
-\cite{wangYellowRiverWater2019}, which introduced includes the major new reservoirs built in the Yellow River Basin since 1949.
-Of these, we consider the reservoirs marked as pivot projects by the YRCC to be more important, as they are directly involved in water resources management in the basin (\url{http://www.yrcc.gov.cn/hhyl/sngc/}).
+Reservoirs data and a measured runoff data were used in this study.
+% 水库数据集由Wang et al. 收集，其中介绍了1949年以来黄河流域新建的主要水库。
+The reservoir dataset were collected by Wang et al. \cite{wangYellowRiverWater2019}, which introduced includes the major new reservoirs built in the Yellow River Basin since 1949. 
+% 其中，我们认为枢纽水库更为重要，因为它们直接参与流域水资源管理(由YRCC定义，见\url{http://www.yrcc.gov.cn/hhyl/sngc/})。
+Of these, we consider the hub-reservoirs to be more important, as they are directly involved in water resources management in the basin (defined by YRCC, see \url{http://www.yrcc.gov.cn/hhyl/sngc/}). 
+% 年径流数据来源于水文站的测量。
 Annual runoff data derived from hydrological station measurements.
@@
 %对于政策数据集，我们选取了《黄河流域综合规划》中流域级部门（如黄河水利委员会）级以上（如国家部委）颁布施行的与黄河流域有关的法律政策。此外，我们还从《黄河水利委员会组织沿革》一书中获取的黄河水利委员会作为黄河流域级管理单位的组织沿革情况，以反映流域级管理举措的实施情况。
-For the policy data set, we select the laws and policies related to the Yellow River basin promulgated and implemented by departments at and above the river Basin level (such as Yellow River Conservancy Commission) in the Comprehensive Planning for the Yellow River Basin (such as national ministries and commissions) \cite{yellowriverconservancycommissionYellowRiverBasin2013}.
-In addition, we also obtain the organizational evolution of the Yellow River Water Conservancy Commission as a watershed management unit from the book Organizational Evolution of the Yellow River Water Conservancy Commission to reflect the implementation of watershed management measures \cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
+For the policy data set, we list the laws and policies related to the Yellow River basin promulgated and implemented by departments at (such as YRCC) and above (such as national institutions) the Basin's level  \cite{yellowriverconservancycommissionYellowRiverBasin2013}.
+% In addition, we also obtain the organizational evolution of the Yellow River Water Conservancy Commission as a watershed management unit from the book Organizational Evolution of the Yellow River Water Conservancy Commission to reflect the implementation of watershed management measures \cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
 
@@
 \section*{Methods S3. Harmonization of datasets}
-% TODO 这里要强调省级数据和县级数据在不确定性上的差异
 % 由于我们的数据集来源广泛，且具有不同的空间尺度，我们需要在区域尺度（SR，UR，MR和DR）上对数据进行调和，根据数据的空间尺度有不同的处理方式。
-Due to the wide sources of our data set and the different spatial scales, we need to reconcile the data on the regional scale (SR, UR, MR and DR), and have different processing methods according to the spatial scale of the data.
+Due to the wide sources of our data set and the different spatial scales, we need to reconcile the datasets into the regional scale (SR, UR, MR and DR).
 \begin{itemize}
-    \item 1. Watersheds:
+    \item 1. Datasets at watersheds scales:
     % 由于流域的分区由水文分区决定，所以水文年报数据和实测径流量数据都能直接根据其对应的水文站直接划分。
-        Due to the fact that the subdivision of a basin is determined by hydrological subdivision, hydrological annual data and measured runoff data can be directly divided according to their corresponding hydrological stations.
-    \item 2. Perfects:
+        Due to the fact that the subdivision of a basin is determined by hydrological subdivision, hydrological annual data and measured runoff data can be directly divided according to their corresponding hydrological stations (see Figure S1 A and B).
+    \item 2. Perfecture:
     % 在市县尺度下，我们分别计算了市县在不同流域分区中所占的面积，选取其中最大的区域，如果该面积占该县面积的95%以上，则认为该市属于该区域，即：
-        At the scale of cities and counties, we respectively calculate the area occupied by cities and counties in different watershed districts, and select the largest region.
+        At the scale of perfecture, we calculate the area of each perfecture belongs to different regions respectively and select the largest one.
 If this area accounts for more than 95\% of the area of the county, the city is considered to belong to this region, that is:
         $$ S_{ij} = MAX(S_ij / S_i)$$
-        where $i$ refers a certain perfect and $j$ refers a region within YRB, i.e.
+        where $i$ refers a certain perfecture and $j$ refers a region within YRB, i.e.
 SR, UR, MR, or DR.
 $S_i$ refers the area of perfect $i$, and $S_{ij}$ refers intersecting area between perfect $i$ and region $j$.
-        We define perfect $i$ belongs to region $j$ if their intersecting area over 95\% of $S_i$, i.e.:
+        We define perfecture $i$ belongs to region $j$ if their intersecting area $S_{ij}$ over 95\% of $S_i$, i.e.:
         $$ MAX(S_{ij}) > 0.95 * S_i $$
@@
     % 在省域尺度的数据（即不同行业的GDP数据）更多用以定性描述，且不与县域尺度数据进行横向比例，因此数据的精度不再重要。我们采用了粗略的处理。即，根据不同区域包含的主要省份，判断该省的数据被融合进哪个区域。参考传统划分惯例，我们进行的划分是：
-    Data at the provincial scale (i.e., GDP data of different industries) are more used for qualitative description, and do not carry out horizontal proportion with data at the county scale, so the accuracy of the data is no longer important.
-We have adopted a rough treatment.
-That is, according to the major provinces contained in different regions, determine which region the data of that province is merged into.
-Referring to the traditional division practice, we made the following division:
+    Data at the provincial scale (i.e., GDP data of different industries) are more used for qualitative description, so it is not important and necessary for down-scaling.
+Thus, according to the major provinces contained in different regions, we determine which region the data of that province is merged into by referring to the traditional division practice:
     \begin{itemize}
@@
 % 最后，当我们处理位置点数据（如水库修建位置数据时），根据其所在位置判断其所属省份，再按照省尺度的区域归类方式进行处理。经过上述处理，所有的数据都能很好的在区域尺度得到协调。
-Finally, when we process the location data (such as the location data of reservoir construction), we judge the province it belongs to according to its location, and then process it according to the regional classification method on the provincial scale.
+Finally, when we process the location data (i.e., the location data of reservoir), we judge the province it belongs to according to its location, and then process it as provincial scale.
+
 After the above processing, all the data can be well coordinated at the regional scale.
@@
 % 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
-The Integrated Water Resources Utilization (IWRU) index of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively.
-% TODO 这里需要增加参考文献，证明这三个维度是最重要的。
-% 无论如何，为了让这些维度能够被量化，我们寻找或发明了共计三个度量指标来对应指示其变化趋势：
-In order for these dimensions to be quantified, we found or invented a total of three metrics corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Configuration Entropy Metric.
+The Integrated Water Resources Utilization (IWRU) index of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
+% 为了对这些维度进行量化，我们发现或发明了三个与指示其变化趋势相对应的指标:SFV指数、非供应共享和配置熵指标。
+In order for these dimensions to be quantified, we used a total of three sub-indicators corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.
 
-\subsection*{Stress: SFV-index}
+\subsection*{Indicator of supply: SFV-index}
 	%* 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
-	There is how much water can be used in a certain basin?
-How many stresses has societies put on the water resources of the basin?
-Answering these questions are crucial for water utilization.
-Various metrics, therefore, proposed for water stress (e.g.
-water scarcity, water stresses index, scarcity-flexibility-variability index), where the aspect of human impact are increasingly valued.
-	%* 其中SFV指数比较有用
-    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses \cite{qinFlexibilityIntensityGlobal2019}.
-    %* 该指标从人类开发利用水资源的角度，考虑了影响人类感知水资源压力的三个方面：水资源的总量、水资源变异性、人类利用水资源的灵活性。
+	How much water can be supplied in a basin? 
+    Various metrics, therefore, proposed for description of stresses on water supply (e.g. water scarcity, water stresses index, scarcity-flexibility-variability index) 
+    \cite{qinFlexibilityintensityglobal2019,bestAnthropogenicstressesworld2019,florke2018}.
+    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses \cite{qinFlexibilityintensityglobal2019}.
 
@@
 However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related provisions and services.
-    Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
-    % TODO 这里要补充一些材料
-    % *这里我们使用非用于供给性的水资源量所占的比例作为指标，即:
+    % Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
     Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate priority of water utility:
@@
     % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 priority 的变化。
-    % TODO 这里要补充一些材料 Li 2020，虚拟水贸易，水粮食能源的联结
     In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as provisioning water.
@@
 Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which provisioning water is often the key to support the production of agricultural products, while non-provisioning water is more involved in industrial and other social processes.
-For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade.
+    % For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade.
 But if industrial consumption is taken into account, China is exporting virtual water.
@@
 
-\subsection*{Configuration: Configuration Entropy Metric}
+\subsection*{Allocation: Allocation Entropy Metric}
     %* 哪里利用水资源？  
     Where to use water resources? 
-    % * 设计了一个熵指标
     % 水资源的分配一直是难题，需要在上下游之间、不同用水部门之间进行权衡，但目前还缺少相关的指标进行量化。
-    The configuration of water resources has always been a difficult problem, requiring trade-offs between upstream and downstream and even different water sectors.
+    % The allocation of water resources has always been a difficult problem, requiring trade-offs between upstream and downstream and even different water sectors.
 However, there is still a lack of comprehensive indicators to quantify.
     % 这里我们设计了一个“分配熵指标”，能够把水资源分配的格局（倾向于平均分配还是更加侧重某一区域）简单直接的表达出来。
-    Here we designed a ``Configuration Entropy Metric (CEM)'', which can simply and directly express the configuration of water allocation (which tends to be more evenly distributed or more focused on a certain region and sector).
+    Here we designed a ``Allocation Entropy Metric (AEM)'', which can simply and directly express the configuration of water allocation (which tends to be more evenly distributed or more focused on a certain region and sector).
     % 我们模仿了物理学中信息熵的思想，当信息（这里是水资源）的分配越趋于平均时，其熵在增加，当分配更倾向于某一区域时，该区域获得发展的确定性在增加，导致总体的熵减少。
     We imitate the idea of information entropy in physics --When the distribution of information (here is water resource) is more equal, its entropy increases.
-    %* 这里需不需要一张图表示？
     % 该指标将不同区域（SR, UR, MR, DR）和不同部门（农业、工业、服务业、人居）消耗的水资源 Water Use (WU) 视做观察的结果，计算完全平均分配水资源时候的水资源分配熵作为最大值，再计算实际水资源分配最大熵与实际熵的比值，以表示水资源分配的格局多大程度上偏离平均分配。
-    The CEM is a metrics for different regions (SR, UR, MR, DR) and different sectors (agriculture, industry, domestic and services) in configurations of Water Use (WU), calculated by:
+    The AEM is a metrics for different regions (SR, UR, MR, DR) or different sectors (agriculture, industry, domestic and services) in allocation of Water Use (WU), calculated by:
 
-    $$ CEM = \sum_{i=1}^n -log(p_{i}) * p_{i} $$
+    $$ AEM = \sum_{i=1}^n -log(p_{i}) * p_{i} $$
 
     Where $i$ represents the unit (a region or a sector) in configuration of water utilization, $p_i$ represents the proportion of water used by the units.
-    For different regions, when water resources are completely evenly used, (i.e. for any region $i$, $p_i = 1/n $), the maximum value of CEM is:
+    For different regions, when water resources are completely evenly used, (i.e. for any region $i$, $p_i = 1/n $), the maximum value of AEM is:
 
-    $$ CEM_{max} = \sum_{i=1}^n -log(p_{i}) * p_{i} = - log(\frac{1}{n}) $$
+    $$ AEM_{max} = \sum_{i=1}^n -log(p_{i}) * p_{i} = - log(\frac{1}{n}) $$
 
@@
 
-    $$ I_C = \frac{CEM_{r}*CEM_{s}}{CEM_{rs}}$$
+    $$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
 
     \begin{itemize}
-        \item Configuration between regions $CEM_r$:
-            $$ CEM_r = \sum_{i=1}^4 -log(p_{i}) * p_{i} $$
+        \item Allocation between regions $AEM_r$:
+            $$ AEM_r = \sum_{i=1}^4 -log(p_{i}) * p_{i} $$
             where $p_i$ is the proportion of region $i$ in water resource usage ($WU_i$), in the total water resource consumption in all regions ($i=1$ to $4$ represents SR, UR, MR, or, DR respectively), i.e.:
             $$ p_i = \frac{WU_i}{\sum_{i=1}^4 WU_i} $$
-        \item Configuration between sectors $CEM_s$:
-            $$ CEM_s = \sum_{j=1}^3 -log(p_{j}) * p_{j} $$ 
+        \item Allocation between sectors $AEM_s$:
+            $$ AEM_s = \sum_{j=1}^3 -log(p_{j}) * p_{j} $$ 
             where $p_j$ is the proportion of sector $j$ in water resources usage ($WU_j$), in the total water consumption in all sectors ($j=1$ to $3$ represents agriculture, industry and domestic \& services respectively), i.e.:
             $$ p_j = \frac{WU_j}{\sum_{j=1}^3 WU_j} $$
-        \item Division of sectors' function between regions $CEM_{rs}$
-            $$ CEM_{rs} = \frac{1}{3} * \sum_{j=1}^3 \sum_{i=1}^4 -log(p_{ij} * p_{ij})$$
+        \item Division of sectors' function between regions $AEM_{rs}$
+            $$ AEM_{rs} = \frac{1}{3} * \sum_{j=1}^3 \sum_{i=1}^4 -log(p_{ij} * p_{ij})$$
             where $p_{ij}$ refers water use proportion of region $i$ in the sector $j$, in the total water consumptions of all regions in this sector, i.e.: 
@@
     % TODO 这里一定要想一下，怎么能给人讲的更明白
-    The indicator $I_C$ (Configuration of water utilization), therefore, not only take into account the distribution between different regions and industries, but also considers the complicated professional division with the development of society.
+    The indicator $I_C$ (Allocation of water utilization), therefore, not only take into account the distribution between different regions and industries, but also considers the complicated professional division with the development of society.
 
@@
         \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR: Source Region, UR: Upper Region, MR: Middle Region, DR: Downstream region).
-        \textbf{B.} Profile of main channel of the Yellow River.
+        \textbf{B.} Profile of main channel of the Yellow River. SR, UR, MR and DR are divided by main hydrological stations.
         \textbf{C.} Typical landscapes in different regions in the YRB.
@@
     \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
-    \caption{Proportions of total water use between the different sectors}
+    \caption{
+        Total water use of different sectors.
+        IND: Industrial water use;
+        IRR: Irrigation water use;
+        URB: Urban water use;
+        RUR: Rural water use;
+    }
 \end{figure}
@@
     \caption{
-        Saving water irrigated area ratio in 2013.
+        Saving water irrigated area ratio in 2013 for each region. There were no saving water irrigated area in  the YRB in 1960s.
     }
@@
     \includegraphics[width=0.6\textwidth]{../../figures/sup/outages.pdf}
-    \caption{Runoff outages records, size of points indicates length of drying up river segments.}
+    \caption{Runoff drying-up records. Size of the circles indicates length of drying up river segments.}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{../../figures/sup/ternary.pdf}
-    \caption{Net contribution of agriculture, industry and services to GDP in different years.}
+    \caption{Net contribution of agriculture, industry and services to GDP of the whole YRB in different years.}
 \end{figure}
@@
         Sensitivity analysis of the threshold of p-values. 
-        \textbf{A.} number of breakpoints in different p-values.
+        \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
         \textbf{B.} A typical result of two breakpoints.

### 2021-03-05 tex/main/manuscript.tex
cover letter

@@
 	% 确定了三种水治理机制(大规模供应、目的转变和全面治理)。
-	Three water governance regimes are identified (massive supply, purpose turned, and many-sided governance).
+	Three water governance regimes are identified (massive supply, purpose-focused, and many-sided governance).
 	% 他们为大型河流流域提出了一般的政权过渡方案。
@@
 % 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, therefore, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
+All in all, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
 % 因此，确定长江流域水资源管理制度的变化可以为了解世界上快速变化的大流域以及治理如何应对其可持续性挑战提供重要的见解。
@@
 % 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-Each period has a unique most striking positive contributor to IWGI. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
+Each period has a unique most striking contributor to IWGI in positive. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
 % 第一阶段到第二阶段

### 2021-04-28 tex/main/manuscript.tex
submit to pnas version

@@
 As natural water cycles are pushed by accelerating socio-economic processes towards a hydrosocial water cycle, big river basins are often governed phase by phase for further water use.
-	% 我们提出了一种综合指标来检测水治理机制，并将其应用于快速变化的黄河流域。
 We propose an integrated index to detect water governance regimes and apply it to the Yellow River Basin, a fast-changing basin.
-	% 确定了三种水治理机制(大规模供应、目的转变和全面治理)。
 Three water governance regimes are identified (massive supply, purpose-focused, and many-sided governance).
-	% 他们为大型河流流域提出了一般的政权过渡方案。
 They suggest a general regime-transition schema for large river basins.
-	% 通过将河流治理转型与主要的水治理挑战联系起来，我们的方法可以为世界各地的大河流域提供有用的可持续发展指导方针。
 By linking river basin governance transitions with major water governance challenges, our approach can offer useful sustainability guidelines for big river basins all around the world.
@@
 	Shuang Song, Xutong Wu wrote the paper.
-	Yongping Wei reviewed the manuscript and proposed major useful advices.
+	Yongping Wei and Graeme S. Cumming reviewed the manuscript and proposed major useful advices.
 }
@@
 % 通讯作者信息
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: fubj@bnu.edu.cn}
+\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: bfu@rcees.ac.cn}
 
@@
 	\label{abstract}
-	% 在许多大型河流流域，利用和管理河流以促进社会经济发展已经导致全球从自然水系向社会-生态水系或“水-社会”水系转变。
 	In many large river basins, the use and governance of rivers for socio-economic development has led to a global transformation from natural to social-ecological or ‘hydrosocial’ water regimes.
-	% 水治理决定谁、什么时候、得到多少水。因此，确定水管理体制如何以及何时改变，对于理解社会-生态水动力学和指导有效和可持续地使用水至关重要。
 Water governance decides who gets water, when, and how much.
 Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
-	% 我们结合水治理的三个主要维度(供应、目的和配置)，开发了一个定量的综合水治理指数(IWGI)，可以检测流域尺度上的水治理机制变化。
 We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
-	% 将该指标应用于一个快速变化的大流域(黄河流域)，结果表明，该指标能够描述三种水治理体制(大规模供水体制;purpose-turned政权;并提供了一种方法，将这些变化与环境、经济、社会和政治变化联系起来。
 Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-focused regime; and many-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
-	% 我们对IWGI的应用提出了一个广泛的水治理机制转型模式和一个普遍的转型轨迹，作为理解人类世水文社会水循环的假设。
 Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydrosocial water cycles in the Anthropocene.
-	% 黄河转型的不同阶段所面临的不同治理挑战，也为大流域的协调治理提供了潜在的指导方针。
 The different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines for the coordinated governance of big river basins in general.

### 2022-04-21 paper/main/01_introduction.tex
initialize standard to NW

--- 2021-04-28 tex/main/manuscript.tex
@@
-%!BIB program = bibtex
-\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
+\label{Intro.}
+Water has been described as being ``at the centre of the planetary drama of the Anthropocene'' 
+\cite{gleesonIlluminatingwatercycle2020}. 
+It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle in which social and power relations dominate the nature of hydrological cycles
+\cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}. 
+Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
+\cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}. 
+As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
+\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.
 
-% PNAS研究论文模板
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
-% \usepackage{cite}
-\usepackage{url}	
-% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Identifying regime transitions for water governance at a basin scale}
-\label{title}
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-% 作者列表
-\author[a, b]{Shuang Song}  % 宋爽，一作
-\author[a, b]{Shuai Wang}  % 王老师，通讯
-\author[c, d]{Xutong Wu}  % 武旭同
-\author[e]{Yongping Wei} % 尉老师
-\author[f]{Graeme S. Cumming} % Cumming
-\author[a, b, 1]{Bojie Fu}  % 傅老师
-
-% 机构列表
-\affil[a]{ % 北师大地表国重
-	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[b]{ % 北师大地理学部
-	Institute of Land Surface System and Sustainability, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[c]{ % 北大城环
-	College of Urban and Environmental Sciences, 
-	Peking University, 
-	Beijing 100871, 
-	P.R. China
-}
-\affil[d]{ % 中科院生态中心
-	State Key Laboratory of Urban and Regional Ecology, 
-	Research Center for Eco-Environmental Sciences, 
-	Chinese Academy of Sciences, 
-	Beijing 100085, 
-	P.R. China 
-}
-\affil[e]{ % 昆士兰大学
-	School of Earth and Environmental Sciences, 
-	The University of Queensland, 
-	Brisbane 4067, 
-	Australia
-}
-\affil[f]{
-	ARC Centre of Excellence for Coral Reef Studies, 
-	James Cook University, 
-	Townsville 4811, 
-	QLD, Australia
-}
-
-% Please give the surname of the lead author for the running footer
-% 领衔作者
-\leadauthor{Song}
-
-% Please add a significance statement to explain the relevance of your work
-% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
-\significancestatement{
-\label{significance}
-	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership.
-The significance statement appears in the paper itself and is required for all research papers.
-	% 人类社会的发展和维持依赖于水。由于自然水循环被加速的社会经济过程推向水社会水循环，大的河流流域往往被控制阶段进一步用水。
-	Development and maintenance of human societies depends on water.
-As natural water cycles are pushed by accelerating socio-economic processes towards a hydrosocial water cycle, big river basins are often governed phase by phase for further water use.
-We propose an integrated index to detect water governance regimes and apply it to the Yellow River Basin, a fast-changing basin.
-Three water governance regimes are identified (massive supply, purpose-focused, and many-sided governance).
-They suggest a general regime-transition schema for large river basins.
-By linking river basin governance transitions with major water governance challenges, our approach can offer useful sustainability guidelines for big river basins all around the world.
-}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{ % 作者的相应贡献
-	Shuai Wang and Bojie Fu designed this research,
-	Shuang Song performed the research and analysed data,
-	Shuang Song, Xutong Wu wrote the paper.
-	Yongping Wei and Graeme S. Cumming reviewed the manuscript and proposed major useful advices.
-}
-\authordeclaration{ % 利益冲突陈述
-	The authors declare no competing interests.
-}
-
-% 如果有共同一作的情况，则uncomment下面这行代码的注释
-%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
-
-% 通讯作者信息
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: bfu@rcees.ac.cn}
-
-% 关键词，三到五个
-% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Transformation $|$ Sustainability}
-
-%tag 摘要
-% 为了
-\begin{abstract}
-	\label{abstract}
-	In many large river basins, the use and governance of rivers for socio-economic development has led to a global transformation from natural to social-ecological or ‘hydrosocial’ water regimes.
-Water governance decides who gets water, when, and how much.
-Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
-We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
-Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-focused regime; and many-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
-Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydrosocial water cycles in the Anthropocene.
-The different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines for the coordinated governance of big river basins in general.
-\end{abstract}
-
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\label{introduction-section-1}
-% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
-\dropcap{W}ater has been described as being “at the centre of the planetary drama of the Anthropocene” \cite{gleeson2020}.
-% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
-It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle
-\cite{gleeson2020,sivapalanSociohydrologynewscience2012,qin2014,abbottwatercycleAnthropocene2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
-% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
-Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
-\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarreSociohydrologyScientificChallenges2019}. 
-% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
-As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
-\cite{biermann2012,steffen2020,dibaldassarreSociohydrologyScientificChallenges2019}.
-
-\label{introduction-section-2}
-% 缺乏治理就是缺乏可持续性
-For water resources in populated areas, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
-% 确定向社会水循环过渡的第一个重要步骤是确定发生过渡的不同制度。
+For water resources in populated areas, missing governance means missing sustainability 
+\cite{undpwatergovernancefacilityWaterGovernanceIssue}. 
 A first important step in identifying transitions towards a hydrosocial water cycle is to identify the different regimes under which it occurs. 
-% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
 According to the United Nations Development Programme (UNDP), three key dimensions of water use are decided by the water governance regime directly: ``How much water can be used?'' (supply), ``How can different services provided by water be balanced?'' (purpose), and ``How can water be allocated equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-A regime is defined as a locally stable state of a system’s structure, function, and dominant controls \cite{carpenterEarlyWarningsRegime2011}. 
+\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. 
+A regime is defined as a locally stable state of a system’s structure, function, and dominant controls 
+\cite{carpenterEarlyWarningsRegime2011}. 
 Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects 
-\cite{rocha2018,gregr2020}.
-% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
+\cite{rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}. 
 Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability.
 
-% 除了由关键的环境、经济、社会和政治变量的变化引起外，水治理的制度变迁也可以通过治理的三个关键维度(供应、目的和分配)
 In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 首先，水的供应不仅取决于天气(许多地区的长期趋势令人担忧，如冰川的消失)，还取决于诸如灌溉和工业等经济活动的需求;蓄水可以解决部分问题，但不能解决所有问题
+\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. 
 First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{greveGlobalAssessmentWater2018, wada2017,qinFlexibilityintensityglobal2019}.
-% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
+\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}. 
 Second, the purposes for which water is used are in need of balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or urban services) 
-\cite{liu2017, florke2018,kleemannQuantifyinginterregionalflows2020}.
-% 水治理可以看作是为每一个不同的目的分配权重并执行结果规则的过程。
+\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}. 
 Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules. 
-% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
 Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
-\cite{roobavannan2017,speed2013}.
-% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
-Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive method for identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
+\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}. 
+Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive approach to identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability Figure~\ref{fig:framework}.
 
-\label{introduction-section-3}
-% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
 As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details). 
@@
 From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
-\cite{songSedimenttransportincreasing2020a,li2020}. 
-% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
+\cite{wangReducedsedimenttransport2016,liDecadalwaterstorage2020}. 
 Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads 
-\cite{wangReducedsedimenttransport2016,wu2020}.
-% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
+\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}. 
 However, water over-use has led to drying up of the Yellow River, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
-\cite{xia2012}.
-% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
+\cite{xiaDevelopmentWaterAllocation2012}. 
 Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
-\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallenges2016}.
-% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
-% 因此，确定长江流域水资源管理制度的变化可以为了解世界上快速变化的大流域以及治理如何应对其可持续性挑战提供重要的见解。
+\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}. 
+The YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into the world’s rapidly-changing big river basins and the ways in which governance may respond to meeting challenges to their sustainability.
 
-\label{introduction-section-3}
-% tag 引言最后一段
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
+	\includegraphics[width=0.9\textwidth]{main/framework.jpg}
 	\caption{
@@
 When abrupt change occurs, it may indicate a regime shift in water governance
-		\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}.
+		\cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
 	}
@@
 \end{figure*}
-
-\section*{Results}
-\subsection*{Water governance regimes}
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
-	\caption{Changes in the IWGI index. 
-	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were respectively the main positive contributors to P1, P2 and P3.
-	}
-	\label{fig:IWGI}
-\end{figure}
-
-% 这一节主要展示IWGI的变化趋势和WUR的划分
-With two significant breakpoints, the changes in the IWGI are divided into three periods (Figure~\ref{fig:IWGI}A) with different slopes. 
-The changes are contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
-% 第一阶段
-In the first period (P1, 1965-1978), the IWGI increased rapidly. 
-Water supply made the most striking positive contribution (131\%), while purpose and allocation had a slight negative contribution (-11\% and -20\%).
-% 第二阶段
-In the second period (P2, 1979-1994), the contributions of purpose and allocation became positive and the IWGI experienced a drop because steeply declining supply capacity played a larger negative role (dropping to -188\% lower than P1).
-% 第三阶段
-In the third period (P3, 1995-2013), as positive contributions from purpose (75\%) and allocation (84\%) increased further and the negative contribution of water supply lessened (-59\%), positive growth of the IWGI returned.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
-When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
-	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
-	\label{fig:phases}
-\end{figure}
-
-% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-Each period has a unique most striking contributor to IWGI in positive. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
-% 第一阶段到第二阶段
-Throughout P1, the water governance regime was dominated by increasing supply capacities. 
-% 第三阶段集中
-It then experienced a shift, slowing down in increasing supply during P2, with an accompanying reverse in the contributed proportion between purpose and allocation.
-Finally, the contribution of all three dimensions was similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points cluster at the centre of the diagram.
-% 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-focused regime (P2: 1979-1993), and a many-sided governance regime (P3: 1994-2013).
-
-% tag 结果2
-\subsection*{Causes of water governance regime shifts}
-\label{result2}
-
-\begin{figure}[th!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
-	\caption{
-		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in total irrigated area (orange line), and water uses in per unit of area (WU/A, green dot line, see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use for unit production (WU/GVA, red dot line) respectively (\textit{SI Appendix} Methods S2).
-		\textbf{C.} Completed time of each new reservoir and their surrounding region's water use percentages as a proportion of the basin's total water use (WU) at that time.
-Red circles denote hub reservoirs in the basin, which play a role in integrated basin water management.
-		The size of each circle indicates the magnitude of its water storage capacity.
-Some important reservoirs include: (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing flood water discharge and water supply.
-The named reservoirs are significant for the entire basin, not only for regional development.
-		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
-In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Allocation Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
-	}
-	\label{fig:Causes}
-\end{figure}
-
-% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
-Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated area and the economic growth of industry and services were key to the change in purpose between P1 and P2.
-% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
-S3).
-% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
-
-% 水分利用效率由P2变化到P3。
-The efficiency of water use changed from P2 to P3. 
-While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), both experienced significant declines in water use for unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
-
-% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and water governance policies played roles in all three regimes. 
-% 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
-We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio), with a higher ratio representing a potential role for supply rather than regulation (Figure~\ref{fig:Causes}C).
-% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1, when natural water resources were relatively abundant (\textit{SI Appendix} Fig.
-S5), and R/B ratios were significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
-% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Allocation Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
-S6).
-% 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering P3, myriad national-level water governance policies were proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs was even higher for facilitating and regulating objectives.
-Most of these were built in regions with lower R/B ratios (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
-S6).
-
-% tag 讨论
-\section*{Discussion}
-\label{Discussion}
-
-\subsection*{Water governance challenges along transition regimes}
-
-\begin{figure*}[htbp!]
-	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.png}
-	\caption{
-		Transition schema of water governance during transformation towards a hydrosocial water cycle.
-Blue pathways are dominated by natural water cycle while red pathways are dominated by socio-economic feedbacks.
-There is a transformation towards the hydrosocial water cycle where red loop increases.
-		\textbf{A.
-Early phase.} As socio-economic systems develop, industry and services gradually demand increasing amounts of water; at the same time, increasing social organization and technological capacity allow people to manage water resources more intensively, including intensive intervention in the natural water cycle.
-		\textbf{B.
-Late phase} With further developed and economically efficient industries and services, trade-offs between provisioning-purpose and non-provisioning water use become prominent.
-Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
-		Thus, \textbf{C.
-Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle.
-This is generally distinguished when water resource limits are reached.
-The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
-		\textbf{D.
-Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
-	}
-	\label{fig:summary}
-\end{figure*}
-
-% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-focused regime (1979-1993) and a many-sided governance regime (1994-2013).
-Shifts between these regimes were caused by different environmental, economic, social or political drivers (Figure~\ref{fig:Causes}).
-% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that each regime occurred gradually, with multifaceted causes, as the basin moves towards a hydrosocial water cycle.
-The challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
-
-% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-During the massive supply regime (1965-1978), the basin economy was mainly dependent on the agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5); water governance thus tended to supply more resources for agriculture (e.g.
-by construction of reservoirs and channels).
-% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
-\cite{zhouDecelerationChinahuman2020}. 
-% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-Since nearly 80\% of surface water was used (mainly for provisioning purposes), the Yellow River dried up during the second half of the regime (\textit{SI Appendix} Figure S7). 
-% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
-Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
-\cite{wohlfartSocialecologicalchallenges2016}.
-
-% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of the purpose-focused regime (1978) coincided with Chinese ``reform and opening-up''.
-This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
-S8).
-% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-In the face of ongoing environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) underwent a reorganization and received instructions from the Ministry of Water Resources (then called the Ministry of Water Resources and Electric Power) to resume and strengthen work on hydrology and basin management in the YRB
-\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
-% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
-As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
-\cite{wang2018}.
-
-% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next shift, to the many-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits  
-\cite{liuWaterconservancyprojects2013}. 
-% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
-\cite{dalinBalancingwaterresource2015}.
-% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
-\cite{barnett2015,yunpeng2010}.
-% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
-\cite{wang2018}.
-% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
-Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
-\cite{konarExpandingScopeFoundation2019}.
-
-% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
-In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
-% 随着越来越多的人为影响逐渐改变世界，对生态系统动力学从生物物理控制向社会和政治控制的转变可能在社会-生态系统中变得越来越普遍
-Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
-\cite{bestPaceHumanInducedChange2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
-Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
-\cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
-% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-The transition regimes identified here echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
-S9)
-\cite{singh2019,porcher2019}.
-% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
-Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
-\cite{allan2019,florke2018,liuWaterSustainabilityChina2012}. 
-% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
-\cite{kitroeff2020,roobavannan2017,unep-dhiTransboundaryRiverBasins2016}.
-% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
-It is typical that resource challenges and structural challenges have occurred sequentially during the transition of water governance within the YRB. 
-% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Our analysis thus suggests that the initial phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
-% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
-
-% 随着河流流域在不同制度之间的过渡而发生的升级过程也带来了额外的挑战。在经济力量的影响下，水资源利用逐渐从一个地方性的问题转变为国家或国际的问题，大型河流流域成为生态系统服务、经济发展和人类福祉的重要来源。
-Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes.
-Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
-% 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
-For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi Dam of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time
-\cite{kongEnvironmentalimpactassessments2017}.
-% 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
-Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
-\cite{cummingQuantifyingSocialEcologicalScale2020}.
-
-\subsection*{Implications and future directions}
-\label{Outlook}
-
-% IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
-The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
-% 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
-It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
-\cite{cummingLinkingEconomicGrowth2018,reyersSocialEcologicalSystemsInsights2018}.
-% 在一种制度下开发的模型和方法在另一种制度下不一定有用。
-Models and approaches developed under one regime are not necessarily useful under a different regime.
-% 就当今世界而言，与水有关的挑战仍是我们在实现可持续性方面取得进展的主要差距之一，而发展优先战略在许多地方仍是主导方针，可能不利于改善治理
-For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
-\cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
-% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
-Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
-\cite{li2020a,degraafEnvironmentalflowlimits2019,huggins2020}.
-% 总的来说，这种明显的治理失败可能有两个主要原因。
-Overall, there are probably two main reasons for this apparent failure of governance.
-% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
-First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
-\cite{grafton2018}. 
-% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
-Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
-\cite{qinFlexibilityintensityglobal2019,levia2020,grill2019}.
-% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
-From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage 
-\cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
-% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
-A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
-
-%tag 研究方法
-\matmethods{
-We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
-Each dimension is reflected by an independent indicator after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different time periods.
-The contribution to changes of IWGI index along with each main indicator were also decomposed and calculated separately for each regime period.
-
-	\subsection*{Integrated Water Governance (IWGI)}
-	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure~\ref{fig:framework} and \textit{SI Appendix} Methods S4 for details)
-	\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}:
-
-	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
-	\begin{itemize}
-		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item \textbf{Supply($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
-However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
-		$$ Transformation \propto S^{-1} $$
-
-		\item \textbf{Priority($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
-		$$ Transformation \propto P $$
-
-		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
-		$$ Transformation \propto A $$
-
-	\end{itemize}
-
-	% 将三者合一起，即：
-	We combined these three dimensions into a single integrated index, keeping their positive or negative relationship with the transformation towards a hydrosocial water cycle:
-
-	$$ Transformation \propto P*A*S^{-1}$$
-
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
-Then, the above equation was transformed into a natural logarithm to facilitate calculation:
-
-	$$ Transformation \propto ln(I_S) + ln(I_P) - ln(I_A) $$
-
-	Assuming they have equal weights, the Integrated Water Governance Index (IWGI) is:
-
-	$$ IWGI = I'_S + I'_P - I'_A $$
-
-	where $I'_x$ is a normalization of log-transformed indicator $I_x$ for a certain dimension:
-
-	$$ I'_x = normalize(ln(I_x)) $$
-
-	\subsubsection*{Normalization}
-	We tested different normalization methods, and they made no difference in change points detection (see \textit{SI Appendix} Methods S5.
-Sensitivity analysis).
-We performed min-max normalization using the formulation below:
-
-	$$ normalize(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
-
-	\subsubsection*{Indicator of supply}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityintensityglobal2019}.
-This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
-For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
-
-	$$ I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i} $$
-
-	Where $SFV_i$ is the SFV-index for region $i$, and $i=1$ to $4$ refers SR, UR, MR, and DR (see \textit{SI Appendix} Methods S1 Definition of study area).
-
-	\subsubsection*{Indicator of purpose}
-	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the NPS as:
-
-	$$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
-
-	Where $i$ refers a certain region, or the whole basin, i.e:
-
-	$I_P$ = $NPS_{basin}$
-
-	\subsubsection*{Indicator of allocations}
-	%$AEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
-	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To describe allocations $I_C$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
-	Our indicator $I_C$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
-
-	$$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
-
-	where $AEM_{r}$ and $AEM_{s}$ are Allocation Entropy Metric in different regions and different sectors.
-$AEM_{rs}$ describes differences between sectors in a certain region relative to the whole basin (see \textit{SI Appendix} Methods S4).
-
-	\subsection*{Change points detection}
-		% The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
-
-		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
-		It tests $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
-The non-parametric statistic is defined as:
-
-		$$ K_t = max|U_{t, T}|$$
-
-		Where:
-
-		$$ U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j) $$
-
-		The change-point of the series is located at $K_T$, provided that the statistic is significant.
-We used 0.001 as the threshold p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
-		Since this method can only return one significant change point, we repeated it until all significant change points were detected.
-
-	% 计算贡献度
-	\subsection*{Contribution decomposition}
-		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index.
-Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
-We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
-
-		\begin{align*}
-			\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
-			&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
-			&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
-		\end{align*}
-		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
-
-		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|} $$
-
-		% Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
-		% $$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
-
-		% or just for contributions (in proportion) within a certain year $j$ to the regime:
-		% $$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
-
-	\subsection*{Datasets}
-	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI, we need to calculate multiple indicators and sub-indicators.
-All the datasets used are listed in the \textit{SI Appendix} table S1.
-A detailed description of the data is provided in the supplementary materials \textit{SI Appendix} Methods S2.
-}
-
-\showmatmethods{} % Display the Materials and Methods section
-
-\acknow{Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).}
-
-\showacknow{} % Display the acknowledgments section
-
-% Bibliography
-\bibliography{my-papers}
-
-\end{document}

### 2022-04-21 paper/main/02_methods.tex
initialize standard to NW

--- 2021-04-28 tex/main/manuscript.tex
@@
-%!BIB program = bibtex
-\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
-
-% PNAS研究论文模板
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
-% \usepackage{cite}
-\usepackage{url}	
-% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Identifying regime transitions for water governance at a basin scale}
-\label{title}
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-% 作者列表
-\author[a, b]{Shuang Song}  % 宋爽，一作
-\author[a, b]{Shuai Wang}  % 王老师，通讯
-\author[c, d]{Xutong Wu}  % 武旭同
-\author[e]{Yongping Wei} % 尉老师
-\author[f]{Graeme S. Cumming} % Cumming
-\author[a, b, 1]{Bojie Fu}  % 傅老师
-
-% 机构列表
-\affil[a]{ % 北师大地表国重
-	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[b]{ % 北师大地理学部
-	Institute of Land Surface System and Sustainability, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[c]{ % 北大城环
-	College of Urban and Environmental Sciences, 
-	Peking University, 
-	Beijing 100871, 
-	P.R. China
-}
-\affil[d]{ % 中科院生态中心
-	State Key Laboratory of Urban and Regional Ecology, 
-	Research Center for Eco-Environmental Sciences, 
-	Chinese Academy of Sciences, 
-	Beijing 100085, 
-	P.R. China 
-}
-\affil[e]{ % 昆士兰大学
-	School of Earth and Environmental Sciences, 
-	The University of Queensland, 
-	Brisbane 4067, 
-	Australia
-}
-\affil[f]{
-	ARC Centre of Excellence for Coral Reef Studies, 
-	James Cook University, 
-	Townsville 4811, 
-	QLD, Australia
-}
-
-% Please give the surname of the lead author for the running footer
-% 领衔作者
-\leadauthor{Song}
-
-% Please add a significance statement to explain the relevance of your work
-% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
-\significancestatement{
-\label{significance}
-	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership.
-The significance statement appears in the paper itself and is required for all research papers.
-	% 人类社会的发展和维持依赖于水。由于自然水循环被加速的社会经济过程推向水社会水循环，大的河流流域往往被控制阶段进一步用水。
-	Development and maintenance of human societies depends on water.
-As natural water cycles are pushed by accelerating socio-economic processes towards a hydrosocial water cycle, big river basins are often governed phase by phase for further water use.
-We propose an integrated index to detect water governance regimes and apply it to the Yellow River Basin, a fast-changing basin.
-Three water governance regimes are identified (massive supply, purpose-focused, and many-sided governance).
-They suggest a general regime-transition schema for large river basins.
-By linking river basin governance transitions with major water governance challenges, our approach can offer useful sustainability guidelines for big river basins all around the world.
-}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{ % 作者的相应贡献
-	Shuai Wang and Bojie Fu designed this research,
-	Shuang Song performed the research and analysed data,
-	Shuang Song, Xutong Wu wrote the paper.
-	Yongping Wei and Graeme S. Cumming reviewed the manuscript and proposed major useful advices.
-}
-\authordeclaration{ % 利益冲突陈述
-	The authors declare no competing interests.
-}
-
-% 如果有共同一作的情况，则uncomment下面这行代码的注释
-%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
-
-% 通讯作者信息
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: bfu@rcees.ac.cn}
-
-% 关键词，三到五个
-% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Transformation $|$ Sustainability}
-
-%tag 摘要
-% 为了
-\begin{abstract}
-	\label{abstract}
-	In many large river basins, the use and governance of rivers for socio-economic development has led to a global transformation from natural to social-ecological or ‘hydrosocial’ water regimes.
-Water governance decides who gets water, when, and how much.
-Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
-We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
-Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-focused regime; and many-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
-Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydrosocial water cycles in the Anthropocene.
-The different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines for the coordinated governance of big river basins in general.
-\end{abstract}
-
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\label{introduction-section-1}
-% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
-\dropcap{W}ater has been described as being “at the centre of the planetary drama of the Anthropocene” \cite{gleeson2020}.
-% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
-It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle
-\cite{gleeson2020,sivapalanSociohydrologynewscience2012,qin2014,abbottwatercycleAnthropocene2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
-% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
-Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
-\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarreSociohydrologyScientificChallenges2019}. 
-% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
-As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
-\cite{biermann2012,steffen2020,dibaldassarreSociohydrologyScientificChallenges2019}.
-
-\label{introduction-section-2}
-% 缺乏治理就是缺乏可持续性
-For water resources in populated areas, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
-% 确定向社会水循环过渡的第一个重要步骤是确定发生过渡的不同制度。
-A first important step in identifying transitions towards a hydrosocial water cycle is to identify the different regimes under which it occurs.
-% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to the United Nations Development Programme (UNDP), three key dimensions of water use are decided by the water governance regime directly: ``How much water can be used?'' (supply), ``How can different services provided by water be balanced?'' (purpose), and ``How can water be allocated equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-A regime is defined as a locally stable state of a system’s structure, function, and dominant controls \cite{carpenterEarlyWarningsRegime2011}. 
-Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
-\cite{rocha2018,gregr2020}.
-% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability.
-
-% 除了由关键的环境、经济、社会和政治变量的变化引起外，水治理的制度变迁也可以通过治理的三个关键维度(供应、目的和分配)
-In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 首先，水的供应不仅取决于天气(许多地区的长期趋势令人担忧，如冰川的消失)，还取决于诸如灌溉和工业等经济活动的需求;蓄水可以解决部分问题，但不能解决所有问题
-First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{greveGlobalAssessmentWater2018, wada2017,qinFlexibilityintensityglobal2019}.
-% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Second, the purposes for which water is used are in need of balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or urban services)
-\cite{liu2017, florke2018,kleemannQuantifyinginterregionalflows2020}.
-% 水治理可以看作是为每一个不同的目的分配权重并执行结果规则的过程。
-Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
-% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
-\cite{roobavannan2017,speed2013}.
-% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
-Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive method for identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
-
-\label{introduction-section-3}
-% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
-As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details). 
-The YRB has experienced some of the most intense water use and dramatic regime shifts of any large river basin in China, giving rise to long-standing challenges for its governance.
-% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
-\cite{songSedimenttransportincreasing2020a,li2020}. 
-% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
-Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
-\cite{wangReducedsedimenttransport2016,wu2020}.
-% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
-However, water over-use has led to drying up of the Yellow River, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
-\cite{xia2012}.
-% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
-Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
-\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallenges2016}.
-% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
-% 因此，确定长江流域水资源管理制度的变化可以为了解世界上快速变化的大流域以及治理如何应对其可持续性挑战提供重要的见解。
-Identifying regime shifts in water governance within the YRB can thus provide crucial insights into the world’s rapidly-changing big river basins and the ways in which governance may respond to meeting challenges to their sustainability.
-
-\label{introduction-section-3}
-% tag 引言最后一段
-% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (see Figure~\ref{fig:framework} and methods).
-% 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
-% 最后总结出一般性框架
-Finally, we propose a general regime transition scheme as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
-
-\begin{figure*}%[htbp]
-	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
-	\caption{
-		A framework for understanding the relationship between transitional water governance regimes and eventual transformation to a hydrosocial cycle.
-A key missing element in current knowledge is an ability to detect regime shifts using a simple and comprehensive index.
-		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
-Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
-(2) ``purpose'' is weighted between consumptive services or non-consumptive uses.
-(3) ``allocation'' changes between balanced or lopsided.
-		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B:} governance changes are an emergent outcome of trends across the three dimensions.
-Water governance status changes along a trajectory towards a hydrosocial water cycle.
-When abrupt change occurs, it may indicate a regime shift in water governance
-		\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}.
-	}
-	\label{fig:framework}
-\end{figure*}
-
-\section*{Results}
-\subsection*{Water governance regimes}
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
-	\caption{Changes in the IWGI index. 
-	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were respectively the main positive contributors to P1, P2 and P3.
-	}
-	\label{fig:IWGI}
-\end{figure}
-
-% 这一节主要展示IWGI的变化趋势和WUR的划分
-With two significant breakpoints, the changes in the IWGI are divided into three periods (Figure~\ref{fig:IWGI}A) with different slopes. 
-The changes are contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
-% 第一阶段
-In the first period (P1, 1965-1978), the IWGI increased rapidly. 
-Water supply made the most striking positive contribution (131\%), while purpose and allocation had a slight negative contribution (-11\% and -20\%).
-% 第二阶段
-In the second period (P2, 1979-1994), the contributions of purpose and allocation became positive and the IWGI experienced a drop because steeply declining supply capacity played a larger negative role (dropping to -188\% lower than P1).
-% 第三阶段
-In the third period (P3, 1995-2013), as positive contributions from purpose (75\%) and allocation (84\%) increased further and the negative contribution of water supply lessened (-59\%), positive growth of the IWGI returned.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
-When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
-	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
-	\label{fig:phases}
-\end{figure}
-
-% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-Each period has a unique most striking contributor to IWGI in positive. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
-% 第一阶段到第二阶段
-Throughout P1, the water governance regime was dominated by increasing supply capacities. 
-% 第三阶段集中
-It then experienced a shift, slowing down in increasing supply during P2, with an accompanying reverse in the contributed proportion between purpose and allocation.
-Finally, the contribution of all three dimensions was similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points cluster at the centre of the diagram.
-% 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-focused regime (P2: 1979-1993), and a many-sided governance regime (P3: 1994-2013).
-
-% tag 结果2
-\subsection*{Causes of water governance regime shifts}
-\label{result2}
-
-\begin{figure}[th!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
-	\caption{
-		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in total irrigated area (orange line), and water uses in per unit of area (WU/A, green dot line, see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use for unit production (WU/GVA, red dot line) respectively (\textit{SI Appendix} Methods S2).
-		\textbf{C.} Completed time of each new reservoir and their surrounding region's water use percentages as a proportion of the basin's total water use (WU) at that time.
-Red circles denote hub reservoirs in the basin, which play a role in integrated basin water management.
-		The size of each circle indicates the magnitude of its water storage capacity.
-Some important reservoirs include: (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing flood water discharge and water supply.
-The named reservoirs are significant for the entire basin, not only for regional development.
-		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
-In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Allocation Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
-	}
-	\label{fig:Causes}
-\end{figure}
-
-% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
-Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated area and the economic growth of industry and services were key to the change in purpose between P1 and P2.
-% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
-S3).
-% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
-
-% 水分利用效率由P2变化到P3。
-The efficiency of water use changed from P2 to P3. 
-While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), both experienced significant declines in water use for unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
-
-% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and water governance policies played roles in all three regimes. 
-% 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
-We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio), with a higher ratio representing a potential role for supply rather than regulation (Figure~\ref{fig:Causes}C).
-% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1, when natural water resources were relatively abundant (\textit{SI Appendix} Fig.
-S5), and R/B ratios were significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
-% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Allocation Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
-S6).
-% 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering P3, myriad national-level water governance policies were proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs was even higher for facilitating and regulating objectives.
-Most of these were built in regions with lower R/B ratios (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
-S6).
-
-% tag 讨论
-\section*{Discussion}
-\label{Discussion}
-
-\subsection*{Water governance challenges along transition regimes}
-
-\begin{figure*}[htbp!]
-	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.png}
-	\caption{
-		Transition schema of water governance during transformation towards a hydrosocial water cycle.
-Blue pathways are dominated by natural water cycle while red pathways are dominated by socio-economic feedbacks.
-There is a transformation towards the hydrosocial water cycle where red loop increases.
-		\textbf{A.
-Early phase.} As socio-economic systems develop, industry and services gradually demand increasing amounts of water; at the same time, increasing social organization and technological capacity allow people to manage water resources more intensively, including intensive intervention in the natural water cycle.
-		\textbf{B.
-Late phase} With further developed and economically efficient industries and services, trade-offs between provisioning-purpose and non-provisioning water use become prominent.
-Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
-		Thus, \textbf{C.
-Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle.
-This is generally distinguished when water resource limits are reached.
-The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
-		\textbf{D.
-Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
-	}
-	\label{fig:summary}
-\end{figure*}
-
-% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-focused regime (1979-1993) and a many-sided governance regime (1994-2013).
-Shifts between these regimes were caused by different environmental, economic, social or political drivers (Figure~\ref{fig:Causes}).
-% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that each regime occurred gradually, with multifaceted causes, as the basin moves towards a hydrosocial water cycle.
-The challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
-
-% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-During the massive supply regime (1965-1978), the basin economy was mainly dependent on the agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5); water governance thus tended to supply more resources for agriculture (e.g.
-by construction of reservoirs and channels).
-% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
-\cite{zhouDecelerationChinahuman2020}. 
-% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-Since nearly 80\% of surface water was used (mainly for provisioning purposes), the Yellow River dried up during the second half of the regime (\textit{SI Appendix} Figure S7). 
-% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
-Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
-\cite{wohlfartSocialecologicalchallenges2016}.
-
-% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of the purpose-focused regime (1978) coincided with Chinese ``reform and opening-up''.
-This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
-S8).
-% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-In the face of ongoing environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) underwent a reorganization and received instructions from the Ministry of Water Resources (then called the Ministry of Water Resources and Electric Power) to resume and strengthen work on hydrology and basin management in the YRB
-\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
-% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
-As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
-\cite{wang2018}.
-
-% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next shift, to the many-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits  
-\cite{liuWaterconservancyprojects2013}. 
-% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
-\cite{dalinBalancingwaterresource2015}.
-% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
-\cite{barnett2015,yunpeng2010}.
-% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
-\cite{wang2018}.
-% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
-Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
-\cite{konarExpandingScopeFoundation2019}.
-
-% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
-In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
-% 随着越来越多的人为影响逐渐改变世界，对生态系统动力学从生物物理控制向社会和政治控制的转变可能在社会-生态系统中变得越来越普遍
-Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
-\cite{bestPaceHumanInducedChange2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
-Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
-\cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
-% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-The transition regimes identified here echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
-S9)
-\cite{singh2019,porcher2019}.
-% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
-Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
-\cite{allan2019,florke2018,liuWaterSustainabilityChina2012}. 
-% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
-\cite{kitroeff2020,roobavannan2017,unep-dhiTransboundaryRiverBasins2016}.
-% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
-It is typical that resource challenges and structural challenges have occurred sequentially during the transition of water governance within the YRB. 
-% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Our analysis thus suggests that the initial phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
-% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
-
-% 随着河流流域在不同制度之间的过渡而发生的升级过程也带来了额外的挑战。在经济力量的影响下，水资源利用逐渐从一个地方性的问题转变为国家或国际的问题，大型河流流域成为生态系统服务、经济发展和人类福祉的重要来源。
-Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes.
-Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
-% 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
-For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi Dam of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time
-\cite{kongEnvironmentalimpactassessments2017}.
-% 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
-Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
-\cite{cummingQuantifyingSocialEcologicalScale2020}.
-
-\subsection*{Implications and future directions}
-\label{Outlook}
-
-% IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
-The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
-% 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
-It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
-\cite{cummingLinkingEconomicGrowth2018,reyersSocialEcologicalSystemsInsights2018}.
-% 在一种制度下开发的模型和方法在另一种制度下不一定有用。
-Models and approaches developed under one regime are not necessarily useful under a different regime.
-% 就当今世界而言，与水有关的挑战仍是我们在实现可持续性方面取得进展的主要差距之一，而发展优先战略在许多地方仍是主导方针，可能不利于改善治理
-For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
-\cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
-% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
-Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
-\cite{li2020a,degraafEnvironmentalflowlimits2019,huggins2020}.
-% 总的来说，这种明显的治理失败可能有两个主要原因。
-Overall, there are probably two main reasons for this apparent failure of governance.
-% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
-First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
-\cite{grafton2018}. 
-% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
-Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
-\cite{qinFlexibilityintensityglobal2019,levia2020,grill2019}.
-% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
-From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage 
-\cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
-% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
-A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
-
-%tag 研究方法
-\matmethods{
-We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
+The aim of this analysis was to develop a transparent and easily replicable approach to identifying water governance regimes and regime shifts; thus, it is not intended to provide a comprehensive model of social-ecological water dynamics.
+We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure 1) selected a priori and identified the changes in periods of the index over time using change point detection.
 Each dimension is reflected by an independent indicator after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different time periods.
@@
 
-	\subsection*{Integrated Water Governance (IWGI)}
-	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure~\ref{fig:framework} and \textit{SI Appendix} Methods S4 for details)
-	\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}:
+\subsection{Integrated Water Governance Index (IWGI)}
+
+Our Integrated Water Governance Index offers an accessible and operational way of measuring regime changes based on the transparent underlying assumptions that water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure 1 and SI 322 Appendix Methods S4 for details)
+\cite{abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020,steffenTrajectoriesEarthSystem2018}.
 
@@
 However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
-		$$ Transformation \propto S^{-1} $$
+		\begin{equation}
+			Transformation \propto S^{-1}
+		\end{equation}
 
 		\item \textbf{Priority($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
-		$$ Transformation \propto P $$
+		\begin{equation}
+			Transformation \propto P
+		\end{equation}
 
@@
 		\item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
-		$$ Transformation \propto A $$
+		\begin{equation}
+			Transformation \propto A 
+		\end{equation}
 
@@
 	We combined these three dimensions into a single integrated index, keeping their positive or negative relationship with the transformation towards a hydrosocial water cycle: 
-
-	$$ Transformation \propto P*A*S^{-1}$$
+	\begin{equation}
+		Transformation \propto P*A*S^{-1}
+	\end{equation}
 
@@
 Then, the above equation was transformed into a natural logarithm to facilitate calculation:
-
-	$$ Transformation \propto ln(I_S) + ln(I_P) - ln(I_A) $$
+	\begin{equation}
+		Transformation \propto ln(I_S) + ln(I_P) - ln(I_A)
+	\end{equation}
 
 	Assuming they have equal weights, the Integrated Water Governance Index (IWGI) is:
-
-	$$ IWGI = I'_S + I'_P - I'_A $$
+	\begin{equation}
+		IWGI = I'_S + I'_P - I'_A
+	\end{equation}
 
 	where $I'_x$ is a normalization of log-transformed indicator $I_x$ for a certain dimension:
-
-	$$ I'_x = normalize(ln(I_x)) $$
+	\begin{equation}
+		I'_x = normalize(ln(I_x))
+	\end{equation}
 
@@
 We performed min-max normalization using the formulation below:
-
-	$$ normalize(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
+	\begin{equation}
+		normalize(X) = (X - X_{min}) / (X_{max} - X_{min})
+	\end{equation}
 
@@
 For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
-
-	$$ I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i} $$
+	\begin{equation}
+		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
+	\end{equation}
 
@@
 We calculated the NPS as:
-
-	$$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
+	\begin{equation}
+		NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}}
+	\end{equation}
 
 	Where $i$ refers a certain region, or the whole basin, i.e:
-
-	$I_P$ = $NPS_{basin}$
+	\begin{equation}
+		I_P = NPS_{basin}
+	\end{equation}
 
@@
 	Our indicator $I_C$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
-
-	$$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
+	\begin{equation}
+		I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}
+	\end{equation}
 
@@
 
-	\subsection*{Change points detection}
+	\subsection{Change points detection}
 		% The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
 
-		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
+		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data
+        \cite{pettittNonParametricApproachChangePoint1979}. 
 		It tests $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
 The non-parametric statistic is defined as:
-
-		$$ K_t = max|U_{t, T}|$$
+		\begin{equation}
+			K_t = max|U_{t, T}|
+		\end{equation}
 
 		Where:
-
-		$$ U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j) $$
+		\begin{equation}
+			U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j)
+		\end{equation}
 
@@
 	% 计算贡献度
-	\subsection*{Contribution decomposition}
+	\subsection{Contribution decomposition}
 		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index.
@@
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
-
-		\begin{align*}
+		\begin{align}
 		\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
@@
 		&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
-		\end{align*}
+		\end{align}
 		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
-
-		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|} $$
+		\begin{equation}
+			Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|}
+		\end{equation}
 
@@
 
-	\subsection*{Datasets}
+	\subsection{Datasets}
 	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
@@
 A detailed description of the data is provided in the supplementary materials \textit{SI Appendix} Methods S2.
-}
-
-\showmatmethods{} % Display the Materials and Methods section
-
-\acknow{Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).}
-
-\showacknow{} % Display the acknowledgments section
-
-% Bibliography
-\bibliography{my-papers}
-
-\end{document}

### 2022-04-21 paper/main/03_results.tex
initialize standard to NW

--- 2021-04-28 tex/main/manuscript.tex
@@
-%!BIB program = bibtex
-\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
-
-% PNAS研究论文模板
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
-% \usepackage{cite}
-\usepackage{url}	
-% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Identifying regime transitions for water governance at a basin scale}
-\label{title}
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-% 作者列表
-\author[a, b]{Shuang Song}  % 宋爽，一作
-\author[a, b]{Shuai Wang}  % 王老师，通讯
-\author[c, d]{Xutong Wu}  % 武旭同
-\author[e]{Yongping Wei} % 尉老师
-\author[f]{Graeme S. Cumming} % Cumming
-\author[a, b, 1]{Bojie Fu}  % 傅老师
-
-% 机构列表
-\affil[a]{ % 北师大地表国重
-	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[b]{ % 北师大地理学部
-	Institute of Land Surface System and Sustainability, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[c]{ % 北大城环
-	College of Urban and Environmental Sciences, 
-	Peking University, 
-	Beijing 100871, 
-	P.R. China
-}
-\affil[d]{ % 中科院生态中心
-	State Key Laboratory of Urban and Regional Ecology, 
-	Research Center for Eco-Environmental Sciences, 
-	Chinese Academy of Sciences, 
-	Beijing 100085, 
-	P.R. China 
-}
-\affil[e]{ % 昆士兰大学
-	School of Earth and Environmental Sciences, 
-	The University of Queensland, 
-	Brisbane 4067, 
-	Australia
-}
-\affil[f]{
-	ARC Centre of Excellence for Coral Reef Studies, 
-	James Cook University, 
-	Townsville 4811, 
-	QLD, Australia
-}
-
-% Please give the surname of the lead author for the running footer
-% 领衔作者
-\leadauthor{Song}
-
-% Please add a significance statement to explain the relevance of your work
-% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
-\significancestatement{
-\label{significance}
-	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership.
-The significance statement appears in the paper itself and is required for all research papers.
-	% 人类社会的发展和维持依赖于水。由于自然水循环被加速的社会经济过程推向水社会水循环，大的河流流域往往被控制阶段进一步用水。
-	Development and maintenance of human societies depends on water.
-As natural water cycles are pushed by accelerating socio-economic processes towards a hydrosocial water cycle, big river basins are often governed phase by phase for further water use.
-We propose an integrated index to detect water governance regimes and apply it to the Yellow River Basin, a fast-changing basin.
-Three water governance regimes are identified (massive supply, purpose-focused, and many-sided governance).
-They suggest a general regime-transition schema for large river basins.
-By linking river basin governance transitions with major water governance challenges, our approach can offer useful sustainability guidelines for big river basins all around the world.
-}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{ % 作者的相应贡献
-	Shuai Wang and Bojie Fu designed this research,
-	Shuang Song performed the research and analysed data,
-	Shuang Song, Xutong Wu wrote the paper.
-	Yongping Wei and Graeme S. Cumming reviewed the manuscript and proposed major useful advices.
-}
-\authordeclaration{ % 利益冲突陈述
-	The authors declare no competing interests.
-}
-
-% 如果有共同一作的情况，则uncomment下面这行代码的注释
-%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
-
-% 通讯作者信息
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: bfu@rcees.ac.cn}
-
-% 关键词，三到五个
-% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Transformation $|$ Sustainability}
-
-%tag 摘要
-% 为了
-\begin{abstract}
-	\label{abstract}
-	In many large river basins, the use and governance of rivers for socio-economic development has led to a global transformation from natural to social-ecological or ‘hydrosocial’ water regimes.
-Water governance decides who gets water, when, and how much.
-Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
-We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
-Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-focused regime; and many-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
-Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydrosocial water cycles in the Anthropocene.
-The different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines for the coordinated governance of big river basins in general.
-\end{abstract}
-
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\label{introduction-section-1}
-% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
-\dropcap{W}ater has been described as being “at the centre of the planetary drama of the Anthropocene” \cite{gleeson2020}.
-% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
-It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle
-\cite{gleeson2020,sivapalanSociohydrologynewscience2012,qin2014,abbottwatercycleAnthropocene2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
-% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
-Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
-\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarreSociohydrologyScientificChallenges2019}. 
-% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
-As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
-\cite{biermann2012,steffen2020,dibaldassarreSociohydrologyScientificChallenges2019}.
-
-\label{introduction-section-2}
-% 缺乏治理就是缺乏可持续性
-For water resources in populated areas, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
-% 确定向社会水循环过渡的第一个重要步骤是确定发生过渡的不同制度。
-A first important step in identifying transitions towards a hydrosocial water cycle is to identify the different regimes under which it occurs.
-% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to the United Nations Development Programme (UNDP), three key dimensions of water use are decided by the water governance regime directly: ``How much water can be used?'' (supply), ``How can different services provided by water be balanced?'' (purpose), and ``How can water be allocated equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-A regime is defined as a locally stable state of a system’s structure, function, and dominant controls \cite{carpenterEarlyWarningsRegime2011}. 
-Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
-\cite{rocha2018,gregr2020}.
-% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability.
-
-% 除了由关键的环境、经济、社会和政治变量的变化引起外，水治理的制度变迁也可以通过治理的三个关键维度(供应、目的和分配)
-In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 首先，水的供应不仅取决于天气(许多地区的长期趋势令人担忧，如冰川的消失)，还取决于诸如灌溉和工业等经济活动的需求;蓄水可以解决部分问题，但不能解决所有问题
-First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{greveGlobalAssessmentWater2018, wada2017,qinFlexibilityintensityglobal2019}.
-% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Second, the purposes for which water is used are in need of balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or urban services)
-\cite{liu2017, florke2018,kleemannQuantifyinginterregionalflows2020}.
-% 水治理可以看作是为每一个不同的目的分配权重并执行结果规则的过程。
-Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
-% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
-\cite{roobavannan2017,speed2013}.
-% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
-Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive method for identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
-
-\label{introduction-section-3}
-% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
-As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details). 
-The YRB has experienced some of the most intense water use and dramatic regime shifts of any large river basin in China, giving rise to long-standing challenges for its governance.
-% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
-\cite{songSedimenttransportincreasing2020a,li2020}. 
-% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
-Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
-\cite{wangReducedsedimenttransport2016,wu2020}.
-% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
-However, water over-use has led to drying up of the Yellow River, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
-\cite{xia2012}.
-% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
-Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
-\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallenges2016}.
-% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
-% 因此，确定长江流域水资源管理制度的变化可以为了解世界上快速变化的大流域以及治理如何应对其可持续性挑战提供重要的见解。
-Identifying regime shifts in water governance within the YRB can thus provide crucial insights into the world’s rapidly-changing big river basins and the ways in which governance may respond to meeting challenges to their sustainability.
-
-\label{introduction-section-3}
-% tag 引言最后一段
-% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (see Figure~\ref{fig:framework} and methods).
-% 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
-% 最后总结出一般性框架
-Finally, we propose a general regime transition scheme as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
-
-\begin{figure*}%[htbp]
-	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
-	\caption{
-		A framework for understanding the relationship between transitional water governance regimes and eventual transformation to a hydrosocial cycle.
-A key missing element in current knowledge is an ability to detect regime shifts using a simple and comprehensive index.
-		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
-Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
-(2) ``purpose'' is weighted between consumptive services or non-consumptive uses.
-(3) ``allocation'' changes between balanced or lopsided.
-		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B:} governance changes are an emergent outcome of trends across the three dimensions.
-Water governance status changes along a trajectory towards a hydrosocial water cycle.
-When abrupt change occurs, it may indicate a regime shift in water governance
-		\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}.
-	}
-	\label{fig:framework}
-\end{figure*}
-
-\section*{Results}
-\subsection*{Water governance regimes}
+\subsection{Water governance regimes}
+\label{Res.1}
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
+	\includegraphics[width=0.9\linewidth]{main/index.jpg}
 	\caption{Changes in the IWGI index. 
@@
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
-When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
-	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
-	\label{fig:phases}
-\end{figure}
-
 % 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
@@
 
-% tag 结果2
-\subsection*{Causes of water governance regime shifts}
-\label{result2}
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{main/phases.jpg}
+	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
+The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
+	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
+When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
+	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
+	\label{fig:phases}
+\end{figure}
+
+\subsection{Causes of water governance regime shifts}
+\label{Res.2}
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
+	\includegraphics[width=0.9\linewidth]{main/causes.jpg}
 	\caption{
@@
 S6).
-
-% tag 讨论
-\section*{Discussion}
-\label{Discussion}
-
-\subsection*{Water governance challenges along transition regimes}
-
-\begin{figure*}[htbp!]
-	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.png}
-	\caption{
-		Transition schema of water governance during transformation towards a hydrosocial water cycle.
-Blue pathways are dominated by natural water cycle while red pathways are dominated by socio-economic feedbacks.
-There is a transformation towards the hydrosocial water cycle where red loop increases.
-		\textbf{A.
-Early phase.} As socio-economic systems develop, industry and services gradually demand increasing amounts of water; at the same time, increasing social organization and technological capacity allow people to manage water resources more intensively, including intensive intervention in the natural water cycle.
-		\textbf{B.
-Late phase} With further developed and economically efficient industries and services, trade-offs between provisioning-purpose and non-provisioning water use become prominent.
-Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
-		Thus, \textbf{C.
-Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle.
-This is generally distinguished when water resource limits are reached.
-The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
-		\textbf{D.
-Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
-	}
-	\label{fig:summary}
-\end{figure*}
-
-% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-focused regime (1979-1993) and a many-sided governance regime (1994-2013).
-Shifts between these regimes were caused by different environmental, economic, social or political drivers (Figure~\ref{fig:Causes}).
-% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that each regime occurred gradually, with multifaceted causes, as the basin moves towards a hydrosocial water cycle.
-The challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
-
-% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-During the massive supply regime (1965-1978), the basin economy was mainly dependent on the agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5); water governance thus tended to supply more resources for agriculture (e.g.
-by construction of reservoirs and channels).
-% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
-\cite{zhouDecelerationChinahuman2020}. 
-% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-Since nearly 80\% of surface water was used (mainly for provisioning purposes), the Yellow River dried up during the second half of the regime (\textit{SI Appendix} Figure S7). 
-% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
-Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
-\cite{wohlfartSocialecologicalchallenges2016}.
-
-% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of the purpose-focused regime (1978) coincided with Chinese ``reform and opening-up''.
-This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
-S8).
-% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-In the face of ongoing environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) underwent a reorganization and received instructions from the Ministry of Water Resources (then called the Ministry of Water Resources and Electric Power) to resume and strengthen work on hydrology and basin management in the YRB
-\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
-% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
-As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
-\cite{wang2018}.
-
-% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next shift, to the many-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits  
-\cite{liuWaterconservancyprojects2013}. 
-% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
-\cite{dalinBalancingwaterresource2015}.
-% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
-\cite{barnett2015,yunpeng2010}.
-% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
-\cite{wang2018}.
-% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
-Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
-\cite{konarExpandingScopeFoundation2019}.
-
-% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
-In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
-% 随着越来越多的人为影响逐渐改变世界，对生态系统动力学从生物物理控制向社会和政治控制的转变可能在社会-生态系统中变得越来越普遍
-Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
-\cite{bestPaceHumanInducedChange2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
-Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
-\cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
-% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-The transition regimes identified here echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
-S9)
-\cite{singh2019,porcher2019}.
-% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
-Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
-\cite{allan2019,florke2018,liuWaterSustainabilityChina2012}. 
-% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
-\cite{kitroeff2020,roobavannan2017,unep-dhiTransboundaryRiverBasins2016}.
-% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
-It is typical that resource challenges and structural challenges have occurred sequentially during the transition of water governance within the YRB. 
-% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Our analysis thus suggests that the initial phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
-% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
-
-% 随着河流流域在不同制度之间的过渡而发生的升级过程也带来了额外的挑战。在经济力量的影响下，水资源利用逐渐从一个地方性的问题转变为国家或国际的问题，大型河流流域成为生态系统服务、经济发展和人类福祉的重要来源。
-Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes.
-Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
-% 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
-For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi Dam of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time
-\cite{kongEnvironmentalimpactassessments2017}.
-% 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
-Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
-\cite{cummingQuantifyingSocialEcologicalScale2020}.
-
-\subsection*{Implications and future directions}
-\label{Outlook}
-
-% IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
-The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
-% 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
-It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
-\cite{cummingLinkingEconomicGrowth2018,reyersSocialEcologicalSystemsInsights2018}.
-% 在一种制度下开发的模型和方法在另一种制度下不一定有用。
-Models and approaches developed under one regime are not necessarily useful under a different regime.
-% 就当今世界而言，与水有关的挑战仍是我们在实现可持续性方面取得进展的主要差距之一，而发展优先战略在许多地方仍是主导方针，可能不利于改善治理
-For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
-\cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
-% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
-Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
-\cite{li2020a,degraafEnvironmentalflowlimits2019,huggins2020}.
-% 总的来说，这种明显的治理失败可能有两个主要原因。
-Overall, there are probably two main reasons for this apparent failure of governance.
-% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
-First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
-\cite{grafton2018}. 
-% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
-Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
-\cite{qinFlexibilityintensityglobal2019,levia2020,grill2019}.
-% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
-From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage 
-\cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
-% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
-A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
-
-%tag 研究方法
-\matmethods{
-We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
-Each dimension is reflected by an independent indicator after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different time periods.
-The contribution to changes of IWGI index along with each main indicator were also decomposed and calculated separately for each regime period.
-
-	\subsection*{Integrated Water Governance (IWGI)}
-	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure~\ref{fig:framework} and \textit{SI Appendix} Methods S4 for details)
-	\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}:
-
-	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
-	\begin{itemize}
-		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item \textbf{Supply($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
-However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
-		$$ Transformation \propto S^{-1} $$
-
-		\item \textbf{Priority($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
-		$$ Transformation \propto P $$
-
-		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
-		$$ Transformation \propto A $$
-
-	\end{itemize}
-
-	% 将三者合一起，即：
-	We combined these three dimensions into a single integrated index, keeping their positive or negative relationship with the transformation towards a hydrosocial water cycle:
-
-	$$ Transformation \propto P*A*S^{-1}$$
-
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
-Then, the above equation was transformed into a natural logarithm to facilitate calculation:
-
-	$$ Transformation \propto ln(I_S) + ln(I_P) - ln(I_A) $$
-
-	Assuming they have equal weights, the Integrated Water Governance Index (IWGI) is:
-
-	$$ IWGI = I'_S + I'_P - I'_A $$
-
-	where $I'_x$ is a normalization of log-transformed indicator $I_x$ for a certain dimension:
-
-	$$ I'_x = normalize(ln(I_x)) $$
-
-	\subsubsection*{Normalization}
-	We tested different normalization methods, and they made no difference in change points detection (see \textit{SI Appendix} Methods S5.
-Sensitivity analysis).
-We performed min-max normalization using the formulation below:
-
-	$$ normalize(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
-
-	\subsubsection*{Indicator of supply}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityintensityglobal2019}.
-This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
-For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
-
-	$$ I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i} $$
-
-	Where $SFV_i$ is the SFV-index for region $i$, and $i=1$ to $4$ refers SR, UR, MR, and DR (see \textit{SI Appendix} Methods S1 Definition of study area).
-
-	\subsubsection*{Indicator of purpose}
-	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the NPS as:
-
-	$$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
-
-	Where $i$ refers a certain region, or the whole basin, i.e:
-
-	$I_P$ = $NPS_{basin}$
-
-	\subsubsection*{Indicator of allocations}
-	%$AEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
-	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To describe allocations $I_C$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
-	Our indicator $I_C$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
-
-	$$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
-
-	where $AEM_{r}$ and $AEM_{s}$ are Allocation Entropy Metric in different regions and different sectors.
-$AEM_{rs}$ describes differences between sectors in a certain region relative to the whole basin (see \textit{SI Appendix} Methods S4).
-
-	\subsection*{Change points detection}
-		% The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
-
-		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
-		It tests $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
-The non-parametric statistic is defined as:
-
-		$$ K_t = max|U_{t, T}|$$
-
-		Where:
-
-		$$ U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j) $$
-
-		The change-point of the series is located at $K_T$, provided that the statistic is significant.
-We used 0.001 as the threshold p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
-		Since this method can only return one significant change point, we repeated it until all significant change points were detected.
-
-	% 计算贡献度
-	\subsection*{Contribution decomposition}
-		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index.
-Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
-We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
-
-		\begin{align*}
-			\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
-			&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
-			&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
-		\end{align*}
-		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
-
-		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|} $$
-
-		% Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
-		% $$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
-
-		% or just for contributions (in proportion) within a certain year $j$ to the regime:
-		% $$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
-
-	\subsection*{Datasets}
-	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI, we need to calculate multiple indicators and sub-indicators.
-All the datasets used are listed in the \textit{SI Appendix} table S1.
-A detailed description of the data is provided in the supplementary materials \textit{SI Appendix} Methods S2.
-}
-
-\showmatmethods{} % Display the Materials and Methods section
-
-\acknow{Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).}
-
-\showacknow{} % Display the acknowledgments section
-
-% Bibliography
-\bibliography{my-papers}
-
-\end{document}

### 2022-04-21 paper/main/04_discussion.tex
initialize standard to NW

--- 2021-04-28 tex/main/manuscript.tex
@@
-%!BIB program = bibtex
-\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
-
-% PNAS研究论文模板
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
-% \usepackage{cite}
-\usepackage{url}	
-% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
-\title{Identifying regime transitions for water governance at a basin scale}
-\label{title}
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-% 作者列表
-\author[a, b]{Shuang Song}  % 宋爽，一作
-\author[a, b]{Shuai Wang}  % 王老师，通讯
-\author[c, d]{Xutong Wu}  % 武旭同
-\author[e]{Yongping Wei} % 尉老师
-\author[f]{Graeme S. Cumming} % Cumming
-\author[a, b, 1]{Bojie Fu}  % 傅老师
-
-% 机构列表
-\affil[a]{ % 北师大地表国重
-	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[b]{ % 北师大地理学部
-	Institute of Land Surface System and Sustainability, 
-	Faculty of Geographical Science, 
-	Beijing Normal University, 
-	Beijing 100875, 
-	P.R. China
-}
-\affil[c]{ % 北大城环
-	College of Urban and Environmental Sciences, 
-	Peking University, 
-	Beijing 100871, 
-	P.R. China
-}
-\affil[d]{ % 中科院生态中心
-	State Key Laboratory of Urban and Regional Ecology, 
-	Research Center for Eco-Environmental Sciences, 
-	Chinese Academy of Sciences, 
-	Beijing 100085, 
-	P.R. China 
-}
-\affil[e]{ % 昆士兰大学
-	School of Earth and Environmental Sciences, 
-	The University of Queensland, 
-	Brisbane 4067, 
-	Australia
-}
-\affil[f]{
-	ARC Centre of Excellence for Coral Reef Studies, 
-	James Cook University, 
-	Townsville 4811, 
-	QLD, Australia
-}
-
-% Please give the surname of the lead author for the running footer
-% 领衔作者
-\leadauthor{Song}
-
-% Please add a significance statement to explain the relevance of your work
-% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
-\significancestatement{
-\label{significance}
-	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership.
-The significance statement appears in the paper itself and is required for all research papers.
-	% 人类社会的发展和维持依赖于水。由于自然水循环被加速的社会经济过程推向水社会水循环，大的河流流域往往被控制阶段进一步用水。
-	Development and maintenance of human societies depends on water.
-As natural water cycles are pushed by accelerating socio-economic processes towards a hydrosocial water cycle, big river basins are often governed phase by phase for further water use.
-We propose an integrated index to detect water governance regimes and apply it to the Yellow River Basin, a fast-changing basin.
-Three water governance regimes are identified (massive supply, purpose-focused, and many-sided governance).
-They suggest a general regime-transition schema for large river basins.
-By linking river basin governance transitions with major water governance challenges, our approach can offer useful sustainability guidelines for big river basins all around the world.
-}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{ % 作者的相应贡献
-	Shuai Wang and Bojie Fu designed this research,
-	Shuang Song performed the research and analysed data,
-	Shuang Song, Xutong Wu wrote the paper.
-	Yongping Wei and Graeme S. Cumming reviewed the manuscript and proposed major useful advices.
-}
-\authordeclaration{ % 利益冲突陈述
-	The authors declare no competing interests.
-}
-
-% 如果有共同一作的情况，则uncomment下面这行代码的注释
-%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
-
-% 通讯作者信息
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: bfu@rcees.ac.cn}
-
-% 关键词，三到五个
-% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Transformation $|$ Sustainability}
-
-%tag 摘要
-% 为了
-\begin{abstract}
-	\label{abstract}
-	In many large river basins, the use and governance of rivers for socio-economic development has led to a global transformation from natural to social-ecological or ‘hydrosocial’ water regimes.
-Water governance decides who gets water, when, and how much.
-Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
-We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
-Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) shows that it can describe shifts between three water governance regimes (respectively, massive supply regime; purpose-focused regime; and many-sided governance regime) over half a century, and offer a way to relate these shifts to environmental, economic social and political changes.
-Our application of the IWGI suggests a widespread transition schema for water governance regimes and a general transformative trajectory as a hypothesis for understanding hydrosocial water cycles in the Anthropocene.
-The different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines for the coordinated governance of big river basins in general.
-\end{abstract}
-
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\label{introduction-section-1}
-% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
-\dropcap{W}ater has been described as being “at the centre of the planetary drama of the Anthropocene” \cite{gleeson2020}.
-% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
-It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle
-\cite{gleeson2020,sivapalanSociohydrologynewscience2012,qin2014,abbottwatercycleAnthropocene2019,levia2020}, in which social and power relations dominate the nature of hydrological cycles.
-% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
-Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
-\cite{bestAnthropogenicStressesWorld2019,falkenmark2019,dibaldassarreSociohydrologyScientificChallenges2019}. 
-% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
-As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
-\cite{biermann2012,steffen2020,dibaldassarreSociohydrologyScientificChallenges2019}.
-
-\label{introduction-section-2}
-% 缺乏治理就是缺乏可持续性
-For water resources in populated areas, missing governance means missing sustainability \cite{undpwatergovernancefacility2015}.
-% 确定向社会水循环过渡的第一个重要步骤是确定发生过渡的不同制度。
-A first important step in identifying transitions towards a hydrosocial water cycle is to identify the different regimes under which it occurs.
-% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
-According to the United Nations Development Programme (UNDP), three key dimensions of water use are decided by the water governance regime directly: ``How much water can be used?'' (supply), ``How can different services provided by water be balanced?'' (purpose), and ``How can water be allocated equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
-A regime is defined as a locally stable state of a system’s structure, function, and dominant controls \cite{carpenterEarlyWarningsRegime2011}. 
-Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
-\cite{rocha2018,gregr2020}.
-% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
-Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability.
-
-% 除了由关键的环境、经济、社会和政治变量的变化引起外，水治理的制度变迁也可以通过治理的三个关键维度(供应、目的和分配)
-In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation)
-\cite{undpwatergovernancefacility2013,undpwatergovernancefacility2015,undpwatergovernancefacility2016}.
-% 首先，水的供应不仅取决于天气(许多地区的长期趋势令人担忧，如冰川的消失)，还取决于诸如灌溉和工业等经济活动的需求;蓄水可以解决部分问题，但不能解决所有问题
-First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{greveGlobalAssessmentWater2018, wada2017,qinFlexibilityintensityglobal2019}.
-% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
-Second, the purposes for which water is used are in need of balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or urban services)
-\cite{liu2017, florke2018,kleemannQuantifyinginterregionalflows2020}.
-% 水治理可以看作是为每一个不同的目的分配权重并执行结果规则的过程。
-Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
-% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
-Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
-\cite{roobavannan2017,speed2013}.
-% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
-Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive method for identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
-
-\label{introduction-section-3}
-% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
-As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details). 
-The YRB has experienced some of the most intense water use and dramatic regime shifts of any large river basin in China, giving rise to long-standing challenges for its governance.
-% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
-\cite{songSedimenttransportincreasing2020a,li2020}. 
-% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
-Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
-\cite{wangReducedsedimenttransport2016,wu2020}.
-% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
-However, water over-use has led to drying up of the Yellow River, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
-\cite{xia2012}.
-% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
-Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
-\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallenges2016}.
-% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
-All in all, the YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
-% 因此，确定长江流域水资源管理制度的变化可以为了解世界上快速变化的大流域以及治理如何应对其可持续性挑战提供重要的见解。
-Identifying regime shifts in water governance within the YRB can thus provide crucial insights into the world’s rapidly-changing big river basins and the ways in which governance may respond to meeting challenges to their sustainability.
-
-\label{introduction-section-3}
-% tag 引言最后一段
-% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (see Figure~\ref{fig:framework} and methods).
-% 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
-% 最后总结出一般性框架
-Finally, we propose a general regime transition scheme as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
-
-\begin{figure*}%[htbp]
-	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
-	\caption{
-		A framework for understanding the relationship between transitional water governance regimes and eventual transformation to a hydrosocial cycle.
-A key missing element in current knowledge is an ability to detect regime shifts using a simple and comprehensive index.
-		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
-Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
-(2) ``purpose'' is weighted between consumptive services or non-consumptive uses.
-(3) ``allocation'' changes between balanced or lopsided.
-		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B:} governance changes are an emergent outcome of trends across the three dimensions.
-Water governance status changes along a trajectory towards a hydrosocial water cycle.
-When abrupt change occurs, it may indicate a regime shift in water governance
-		\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}.
-	}
-	\label{fig:framework}
-\end{figure*}
-
-\section*{Results}
-\subsection*{Water governance regimes}
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
-	\caption{Changes in the IWGI index. 
-	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were respectively the main positive contributors to P1, P2 and P3.
-	}
-	\label{fig:IWGI}
-\end{figure}
-
-% 这一节主要展示IWGI的变化趋势和WUR的划分
-With two significant breakpoints, the changes in the IWGI are divided into three periods (Figure~\ref{fig:IWGI}A) with different slopes. 
-The changes are contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
-% 第一阶段
-In the first period (P1, 1965-1978), the IWGI increased rapidly. 
-Water supply made the most striking positive contribution (131\%), while purpose and allocation had a slight negative contribution (-11\% and -20\%).
-% 第二阶段
-In the second period (P2, 1979-1994), the contributions of purpose and allocation became positive and the IWGI experienced a drop because steeply declining supply capacity played a larger negative role (dropping to -188\% lower than P1).
-% 第三阶段
-In the third period (P3, 1995-2013), as positive contributions from purpose (75\%) and allocation (84\%) increased further and the negative contribution of water supply lessened (-59\%), positive growth of the IWGI returned.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
-	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
-When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
-	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
-	\label{fig:phases}
-\end{figure}
-
-% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-Each period has a unique most striking contributor to IWGI in positive. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
-% 第一阶段到第二阶段
-Throughout P1, the water governance regime was dominated by increasing supply capacities. 
-% 第三阶段集中
-It then experienced a shift, slowing down in increasing supply during P2, with an accompanying reverse in the contributed proportion between purpose and allocation.
-Finally, the contribution of all three dimensions was similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points cluster at the centre of the diagram.
-% 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-focused regime (P2: 1979-1993), and a many-sided governance regime (P3: 1994-2013).
-
-% tag 结果2
-\subsection*{Causes of water governance regime shifts}
-\label{result2}
-
-\begin{figure}[th!]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
-	\caption{
-		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in total irrigated area (orange line), and water uses in per unit of area (WU/A, green dot line, see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use for unit production (WU/GVA, red dot line) respectively (\textit{SI Appendix} Methods S2).
-		\textbf{C.} Completed time of each new reservoir and their surrounding region's water use percentages as a proportion of the basin's total water use (WU) at that time.
-Red circles denote hub reservoirs in the basin, which play a role in integrated basin water management.
-		The size of each circle indicates the magnitude of its water storage capacity.
-Some important reservoirs include: (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing flood water discharge and water supply.
-The named reservoirs are significant for the entire basin, not only for regional development.
-		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
-In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Allocation Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
-	}
-	\label{fig:Causes}
-\end{figure}
-
-% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
-Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated area and the economic growth of industry and services were key to the change in purpose between P1 and P2.
-% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
-S3).
-% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
-
-% 水分利用效率由P2变化到P3。
-The efficiency of water use changed from P2 to P3. 
-While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), both experienced significant declines in water use for unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
-
-% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and water governance policies played roles in all three regimes. 
-% 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
-We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio), with a higher ratio representing a potential role for supply rather than regulation (Figure~\ref{fig:Causes}C).
-% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1, when natural water resources were relatively abundant (\textit{SI Appendix} Fig.
-S5), and R/B ratios were significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
-% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Allocation Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
-S6).
-% 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering P3, myriad national-level water governance policies were proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs was even higher for facilitating and regulating objectives.
-Most of these were built in regions with lower R/B ratios (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
-S6).
-
-% tag 讨论
-\section*{Discussion}
-\label{Discussion}
-
-\subsection*{Water governance challenges along transition regimes}
+\subsection{Water governance challenges along transition regimes}
 
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{../../figures/main/transition.png}
+	\includegraphics[width=0.9\linewidth]{main/transition.png}
 	\caption{
@@
 Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
-\cite{wohlfartSocialecologicalchallenges2016}.
+\cite{wohlfartRiverBasinCourse2016}.
 
@@
 As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
-\cite{wang2018}.
+\cite{wangThirtyYearsYellow2018}.
 
@@
 For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
-\cite{barnett2015,yunpeng2010}.
+\cite{barnettSustainabilityTransferproject2015,yunpengWaterRightTransfer2010}. 
 % 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
 On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
-\cite{wang2018}.
+\cite{wangThirtyYearsYellow2018}.
 % 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
@@
 Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
-\cite{bestPaceHumanInducedChange2020,cummingLinkingEconomicGrowth2018,cummingImplicationsAgriculturalTransitions2014}.
+\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}. 
 Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario 
-\cite{millenniumecosystemassessmentprogramEcosystemshumanwellbeing2005}.
+\cite{millenniumecosystemassessmentEcosystemshumanwellbeing2005}. 
 % 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
@@
 S9)
-\cite{singh2019,porcher2019}.
+\cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}. 
 % 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
 Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
-\cite{allan2019,florke2018,liuWaterSustainabilityChina2012}. 
+\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}. 
 % 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
 Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
-\cite{kitroeff2020,roobavannan2017,unep-dhiTransboundaryRiverBasins2016}.
+\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}. 
 % 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
@@
 Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
-\cite{cummingQuantifyingSocialEcologicalScale2020}.
+\cite{cummingScalemismatchessocialecological2006}.
 
-\subsection*{Implications and future directions}
+\subsection{Implications and future directions}
 \label{Outlook}
@@
 For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
-\cite{xu2020,liu2017,greveGlobalAssessmentWater2018}. 
+\cite{xuAssessingprogresssustainable2020,liuAerosolweakenedsummermonsoons2017,greveGlobalassessmentwater2018}. 
 % 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
 Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
-\cite{li2020a,degraafEnvironmentalflowlimits2019,huggins2020}.
+\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
 % 总的来说，这种明显的治理失败可能有两个主要原因。
@@
 First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
-\cite{grafton2018}. 
+\cite{graftonparadoxirrigationefficiency2018}. 
 % 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
 Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
-\cite{qinFlexibilityintensityglobal2019,levia2020,grill2019}.
+\cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
 % 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
 From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage 
-\cite{steffen2020,muneepeerakul2020,bodinCollaborativeEnvironmentalGovernance2017,biermann2012}. 
+\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}. 
 % 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
 A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
-
-%tag 研究方法
-\matmethods{
-We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure~\ref{fig:framework}) and identified the changes periods of the index over time by change points detection.
-Each dimension is reflected by an independent indicator after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different time periods.
-The contribution to changes of IWGI index along with each main indicator were also decomposed and calculated separately for each regime period.
-
-	\subsection*{Integrated Water Governance (IWGI)}
-	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
-	Water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure~\ref{fig:framework} and \textit{SI Appendix} Methods S4 for details)
-	\cite{steffen2018,abbottwatercycleAnthropocene2019,levia2020}:
-
-	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
-	\begin{itemize}
-		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item \textbf{Supply($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
-However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
-		$$ Transformation \propto S^{-1} $$
-
-		\item \textbf{Priority($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
-		$$ Transformation \propto P $$
-
-		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
-		$$ Transformation \propto A $$
-
-	\end{itemize}
-
-	% 将三者合一起，即：
-	We combined these three dimensions into a single integrated index, keeping their positive or negative relationship with the transformation towards a hydrosocial water cycle:
-
-	$$ Transformation \propto P*A*S^{-1}$$
-
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
-Then, the above equation was transformed into a natural logarithm to facilitate calculation:
-
-	$$ Transformation \propto ln(I_S) + ln(I_P) - ln(I_A) $$
-
-	Assuming they have equal weights, the Integrated Water Governance Index (IWGI) is:
-
-	$$ IWGI = I'_S + I'_P - I'_A $$
-
-	where $I'_x$ is a normalization of log-transformed indicator $I_x$ for a certain dimension:
-
-	$$ I'_x = normalize(ln(I_x)) $$
-
-	\subsubsection*{Normalization}
-	We tested different normalization methods, and they made no difference in change points detection (see \textit{SI Appendix} Methods S5.
-Sensitivity analysis).
-We performed min-max normalization using the formulation below:
-
-	$$ normalize(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
-
-	\subsubsection*{Indicator of supply}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityintensityglobal2019}.
-This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
-For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
-
-	$$ I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i} $$
-
-	Where $SFV_i$ is the SFV-index for region $i$, and $i=1$ to $4$ refers SR, UR, MR, and DR (see \textit{SI Appendix} Methods S1 Definition of study area).
-
-	\subsubsection*{Indicator of purpose}
-	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the NPS as:
-
-	$$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
-
-	Where $i$ refers a certain region, or the whole basin, i.e:
-
-	$I_P$ = $NPS_{basin}$
-
-	\subsubsection*{Indicator of allocations}
-	%$AEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
-	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To describe allocations $I_C$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
-	Our indicator $I_C$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
-
-	$$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
-
-	where $AEM_{r}$ and $AEM_{s}$ are Allocation Entropy Metric in different regions and different sectors.
-$AEM_{rs}$ describes differences between sectors in a certain region relative to the whole basin (see \textit{SI Appendix} Methods S4).
-
-	\subsection*{Change points detection}
-		% The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
-
-		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data \cite{pettittNonParametricApproachChangePoint1979}.
-		It tests $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
-The non-parametric statistic is defined as:
-
-		$$ K_t = max|U_{t, T}|$$
-
-		Where:
-
-		$$ U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j) $$
-
-		The change-point of the series is located at $K_T$, provided that the statistic is significant.
-We used 0.001 as the threshold p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
-		Since this method can only return one significant change point, we repeated it until all significant change points were detected.
-
-	% 计算贡献度
-	\subsection*{Contribution decomposition}
-		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index.
-Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
-We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
-
-		\begin{align*}
-			\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
-			&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
-			&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
-		\end{align*}
-		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
-
-		$$ Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|} $$
-
-		% Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
-		% $$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
-
-		% or just for contributions (in proportion) within a certain year $j$ to the regime:
-		% $$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
-
-	\subsection*{Datasets}
-	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI, we need to calculate multiple indicators and sub-indicators.
-All the datasets used are listed in the \textit{SI Appendix} table S1.
-A detailed description of the data is provided in the supplementary materials \textit{SI Appendix} Methods S2.
-}
-
-\showmatmethods{} % Display the Materials and Methods section
-
-\acknow{Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).}
-
-\showacknow{} % Display the acknowledgments section
-
-% Bibliography
-\bibliography{my-papers}
-
-\end{document}

### 2022-04-21 paper/main/manuscript.tex
initialize standard to NW

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing

%%=======================================================%%
%% to print line numbers in the margin use lineno option %%
%%=======================================================%%

%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%======================================================%%
%% to compile with pdflatex/xelatex use pdflatex option %%
%%======================================================%%

%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
% \documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
% \documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
% \documentclass[default]{sn-jnl}% Default
\documentclass[default,iicol]{sn-jnl}% Default with double column layout

%%%% Standard Packages
%%<additional latex packages if required can be included here>
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published 
%%%%  by Springer Nature. The guidance has been prepared in partnership with 
%%%%  production teams to conform to Springer Nature technical requirements. 
%%%%  Editorial and presentation requirements differ among journal portfolios and 
%%%%  research disciplines. You may find sections in this template are irrelevant 
%%%%  to your work and are empowered to omit any such section if allowed by the 
%%%%  journal you intend to submit to. The submission guidelines and policies 
%%%%  of the journal take precedence. A detailed User Manual is available in the 
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

\jyear{2021}%

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads
%! path of figs

\graphicspath{{/Users/songshgeo/Documents/VScode/water_governance_challenges/figures/}}
\begin{document}

\title[Article Title]{Article Title}

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}

\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}

\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}

\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}

%%==================================%%
%% sample for unstructured abstract %%
%%==================================%%

\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}

\keywords{keyword1, Keyword2, Keyword3, Keyword4}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

\maketitle

\section{Introduction}\label{sec1}
\input{01_introduction}

\section{Results}\label{sec2}
\input{03_results}

%! \section{Equations}\label{sec4}

% Equations in \LaTeX\ can either be inline or on-a-line by itself (``display equations''). For
% inline equations use the \verb+$...$+ commands. E.g.: The equation
% $H\psi = E \psi$ is written via the command \verb+$H \psi = E \psi$+.

% For display equations (with auto generated equation numbers)
% one can use the equation or align environments:
% \begin{equation}
% \|\tilde{X}(k)\|^2 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.\label{eq1}
% \end{equation}
% where,
% \begin{align}
% D_\mu &=  \partial_\mu - ig \frac{\lambda^a}{2} A^a_\mu \nonumber \\
% F^a_{\mu\nu} &= \partial_\mu A^a_\nu - \partial_\nu A^a_\mu + g f^{abc} A^b_\mu A^a_\nu \label{eq2}
% \end{align}
% Notice the use of \verb+\nonumber+ in the align environment at the end
% of each line, except the last, so as not to produce equation numbers on
% lines where no equation numbers are required. The \verb+\label{}+ command
% should only be used at the last line of an align environment where
% \verb+\nonumber+ is not used.
% \begin{equation}
% Y_\infty = \left( \frac{m}{\textrm{GeV}} \right)^{-3}
%     \left[ 1 + \frac{3 \ln(m/\textrm{GeV})}{15}
%     + \frac{\ln(c_2/5)}{15} \right]
% \end{equation}
% The class file also supports the use of \verb+\mathbb{}+, \verb+\mathscr{}+ and
% \verb+\mathcal{}+ commands. As such \verb+\mathbb{R}+, \verb+\mathscr{R}+
% and \verb+\mathcal{R}+ produces $\mathbb{R}$, $\mathscr{R}$ and $\mathcal{R}$
% respectively (refer Subsubsection~\ref{subsubsec2}).

% \section{Tables}\label{sec5}

% Tables can be inserted via the normal table and tabular environment. To put
% footnotes inside tables you should use \verb+\footnotetext[]{...}+ tag.
% The footnote appears just below the table itself (refer Tables~\ref{tab1} and \ref{tab2}). 
% For the corresponding footnotemark use \verb+\footnotemark[...]+

% % \begin{table}[h]
% % \begin{center}
% % \begin{minipage}{174pt}
% % \caption{Caption text}\label{tab1}%
% % \begin{tabular}{@{}llll@{}}
% % \toprule
% % Column 1 & Column 2  & Column 3 & Column 4\\
% % \midrule
% % row 1    & data 1   & data 2  & data 3  \\
% % row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
% % row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
% % \botrule
% % \end{tabular}
% % \footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
% % \footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
% % \footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
% % \end{minipage}
% % \end{center}
% % \end{table}

% % \noindent
% % The input format for the above table is as follows:

% % %%=============================================%%
% % %% For presentation purpose, we have included  %%
% % %% \bigskip command. please ignore this.       %%
% % %%=============================================%%
% % \bigskip
% % \begin{verbatim}
% % \begin{table}[<placement-specifier>]
% % \begin{center}
% % \begin{minipage}{<preferred-table-width>}
% % \caption{<table-caption>}\label{<table-label>}%
% % \begin{tabular}{@{}llll@{}}
% % \toprule
% % Column 1 & Column 2 & Column 3 & Column 4\\
% % \midrule
% % row 1 & data 1 & data 2	 & data 3 \\
% % row 2 & data 4 & data 5\footnotemark[1] & data 6 \\
% % row 3 & data 7 & data 8	 & data 9\footnotemark[2]\\
% % \botrule
% % \end{tabular}
% % \footnotetext{Source: This is an example of table footnote. 
% % This is an example of table footnote.}
% % \footnotetext[1]{Example for a first table footnote.
% % This is an example of table footnote.}
% % \footnotetext[2]{Example for a second table footnote. 
% % This is an example of table footnote.}
% % \end{minipage}
% % \end{center}
% % \end{table}
% % \end{verbatim}
% % \bigskip
%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%

% \begin{table}[h]
% \begin{center}
% \begin{minipage}{\textwidth}
% \caption{Example of a lengthy table which is set to full textwidth}\label{tab2}
% \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
% \toprule%
% & \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Element 2\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
% Project & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
% \midrule
% Element 3  & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$\\
% Element 4  & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$\\
% \botrule
% \end{tabular*}
% \footnotetext{Note: This is an example of table footnote. This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
% \footnotetext[1]{Example for a first table footnote.}
% \footnotetext[2]{Example for a second table footnote.}
% \end{minipage}
% \end{center}
% \end{table}

% In case of double column layout, tables which do not fit in single column width should be set to full text width. For this, you need to use \verb+\begin{table*}+ \verb+...+ \verb+\end{table*}+ instead of \verb+\begin{table}+ \verb+...+ \verb+\end{table}+ environment. Lengthy tables which do not fit in textwidth should be set as rotated table. For this, you need to use \verb+\begin{sidewaystable}+ \verb+...+ \verb+\end{sidewaystable}+ instead of \verb+\begin{table*}+ \verb+...+ \verb+\end{table*}+ environment. This environment puts tables rotated to single column width. For tables rotated to double column width, use \verb+\begin{sidewaystable*}+ \verb+...+ \verb+\end{sidewaystable*}+.

% \begin{sidewaystable}
% \sidewaystablefn%
% \begin{center}
% \begin{minipage}{\textheight}
% \caption{Tables which are too long to fit, should be written using the ``sidewaystable'' environment as shown here}\label{tab3}
% \begin{tabular*}{\textheight}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
% \toprule%
% & \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]}& \multicolumn{3}{@{}c@{}}{Element\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
% Projectile & Energy	& $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
% \midrule
% Element 3 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
% Element 4 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
% Element 5 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
% Element 6 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
% \botrule
% \end{tabular*}
% \footnotetext{Note: This is an example of table footnote this is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
% \footnotetext[1]{This is an example of table footnote.}
% \end{minipage}
% \end{center}
% \end{sidewaystable}

% \section{Figures}\label{sec6}

% As per the \LaTeX\ standards you need to use eps images for \LaTeX\ compilation and \verb+pdf/jpg/png+ images for \verb+PDFLaTeX+ compilation. This is one of the major difference between \LaTeX\ and \verb+PDFLaTeX+. Each image should be from a single input .eps/vector image file. Avoid using subfigures. The command for inserting images for \LaTeX\ and \verb+PDFLaTeX+ can be generalized. The package used to insert images in \verb+LaTeX/PDFLaTeX+ is the graphicx package. Figures can be inserted via the normal figure environment as shown in the below example:

%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%
% \bigskip
% \begin{verbatim}
% \begin{figure}[<placement-specifier>]
% \centering
% \includegraphics{<eps-file>}
% \caption{<figure-caption>}\label{<figure-label>}
% \end{figure}
% \end{verbatim}
% \bigskip
%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%

% \begin{figure}[h]%
% \centering
% \includegraphics[width=0.9\textwidth]{fig.eps}
% \caption{This is a widefig. This is an example of long caption this is an example of long caption  this is an example of long caption this is an example of long caption}\label{fig1}
% \end{figure}

% In case of double column layout, the above format puts figure captions/images to single column width. To get spanned images, we need to provide \verb+\begin{figure*}+ \verb+...+ \verb+\end{figure*}+.

% For sample purpose, we have included the width of images in the optional argument of \verb+\includegraphics+ tag. Please ignore this.

% \section{Algorithms, Program codes and Listings}\label{sec7}

% Packages \verb+algorithm+, \verb+algorithmicx+ and \verb+algpseudocode+ are used for setting algorithms in \LaTeX\ using the format:

% %%=============================================%%
% %% For presentation purpose, we have included  %%
% %% \bigskip command. please ignore this.       %%
% %%=============================================%%
% \bigskip
% \begin{verbatim}
% \begin{algorithm}
% \caption{<alg-caption>}\label{<alg-label>}
% \begin{algorithmic}[1]
% . . .
% \end{algorithmic}
% \end{algorithm}
% \end{verbatim}
% \bigskip
%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%

% You may refer above listed package documentations for more details before setting \verb+algorithm+ environment. For program codes, the ``program'' package is required and the command to be used is \verb+\begin{program}+ \verb+...+ \verb+\end{program}+. A fast exponentiation procedure:

% \begin{program}
% \BEGIN \\ %
%   \FOR i:=1 \TO 10 \STEP 1 \DO
%      |expt|(2,i); \\ |newline|() \OD %
% \rcomment{Comments will be set flush to the right margin}
% \WHERE
% \PROC |expt|(x,n) \BODY
%           z:=1;
%           \DO \IF n=0 \THEN \EXIT \FI;
%              \DO \IF |odd|(n) \THEN \EXIT \FI;
% \COMMENT{This is a comment statement};
%                 n:=n/2; x:=x*x \OD;
%              \{ n>0 \};
%              n:=n-1; z:=z*x \OD;
%           |print|(z) \ENDPROC
% \END
% \end{program}

% \begin{algorithm}
% \caption{Calculate $y = x^n$}\label{algo1}
% \begin{algorithmic}[1]
% \Require $n \geq 0 \vee x \neq 0$
% \Ensure $y = x^n$ 
% \State $y \Leftarrow 1$
% \If{$n < 0$}\label{algln2}
%         \State $X \Leftarrow 1 / x$
%         \State $N \Leftarrow -n$
% \Else
%         \State $X \Leftarrow x$
%         \State $N \Leftarrow n$
% \EndIf
% \While{$N \neq 0$}
%         \If{$N$ is even}
%             \State $X \Leftarrow X \times X$
%             \State $N \Leftarrow N / 2$
%         \Else[$N$ is odd]
%             \State $y \Leftarrow y \times X$
%             \State $N \Leftarrow N - 1$
%         \EndIf
% \EndWhile
% \end{algorithmic}
% \end{algorithm}
% \bigskip
%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%

% Similarly, for \verb+listings+, use the \verb+listings+ package. \verb+\begin{lstlisting}+ \verb+...+ \verb+\end{lstlisting}+ is used to set environments similar to \verb+verbatim+ environment. Refer to the \verb+lstlisting+ package documentation for more details.

% %%=============================================%%
% %% For presentation purpose, we have included  %%
% %% \bigskip command. please ignore this.       %%
% %%=============================================%%
% \bigskip
% \begin{minipage}{\hsize}%
% \lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}% Set your language (you can change the language for each code-block optionally)
% %%% Start your code-block
% \begin{lstlisting}
% for i:=maxint to 0 do
% begin
% { do nothing }
% end;
% Write('Case insensitive ');
% Write('Pascal keywords.');
% \end{lstlisting}
% \end{minipage}

% \section{Cross referencing}\label{sec8}

% Environments such as figure, table, equation and align can have a label
% declared via the \verb+\label{#label}+ command. For figures and table
% environments use the \verb+\label{}+ command inside or just
% below the \verb+\caption{}+ command. You can then use the
% \verb+\ref{#label}+ command to cross-reference them. As an example, consider
% the label declared for Figure~\ref{fig1} which is
% \verb+\label{fig1}+. To cross-reference it, use the command 
% \verb+Figure \ref{fig1}+, for which it comes up as
% ``Figure~\ref{fig1}''.

% To reference line numbers in an algorithm, consider the label declared for the line number 2 of Algorithm~\ref{algo1} is \verb+\label{algln2}+. To cross-reference it, use the command \verb+\ref{algln2}+ for which it comes up as line~\ref{algln2} of Algorithm~\ref{algo1}.

% \subsection{Details on reference citations}\label{subsec7}

% Standard \LaTeX\ permits only numerical citations. To support both numerical and author-year citations this template uses \verb+natbib+ \LaTeX\ package. For style guidance please refer to the template user manual.

% Here is an example for \verb+\cite{...}+: \cite{bib1}. Another example for \verb+\citep{...}+: \citep{bib2}. For author-year citation mode, \verb+\cite{...}+ prints Jones et al. (1990) and \verb+\citep{...}+ prints (Jones et al., 1990).

% All cited bib entries are printed at the end of this article: \cite{bib3}, \cite{bib4}, \cite{bib5}, \cite{bib6}, \cite{bib7}, \cite{bib8}, \cite{bib9}, \cite{bib10}, \cite{bib11} and \cite{bib12}.

% \section{Examples for theorem like environments}\label{sec10}

% For theorem like environments, we require \verb+amsthm+ package. There are three types of predefined theorem styles exists---\verb+thmstyleone+, \verb+thmstyletwo+ and \verb+thmstylethree+

%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%
% \bigskip
% \begin{tabular}{|l|p{19pc}|}
% \hline
% \verb+thmstyleone+ & Numbered, theorem head in bold font and theorem text in italic style \\\hline
% \verb+thmstyletwo+ & Numbered, theorem head in roman font and theorem text in italic style \\\hline
% \verb+thmstylethree+ & Numbered, theorem head in bold font and theorem text in roman style \\\hline
% \end{tabular}
% \bigskip
%%=============================================%%
%% For presentation purpose, we have included  %%
%% \bigskip command. please ignore this.       %%
%%=============================================%%

% For mathematics journals, theorem styles can be included as shown in the following examples:

% \begin{theorem}[Theorem subhead]\label{thm1}
% Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. 
% Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. 
% Example theorem text. 
% \end{theorem}

% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.

% \begin{proposition}
% Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. 
% Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. 
% \end{proposition}

% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.

% \begin{example}
% Phasellus adipiscing semper elit. Proin fermentum massa
% ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
% at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. 
% \end{example}

% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.

% \begin{remark}
% Phasellus adipiscing semper elit. Proin fermentum massa
% ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
% at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. 
% \end{remark}

% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.

% \begin{definition}[Definition sub head]
% Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. 
% \end{definition}

% Additionally a predefined ``proof'' environment is available: \verb+\begin{proof}+ \verb+...+ \verb+\end{proof}+. This prints a ``Proof'' head in italic font style and the ``body text'' in roman font style with an open square at the end of each proof environment.

% \begin{proof}
% Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. 
% \end{proof}

% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.

% \begin{proof}[Proof of Theorem~{\upshape\ref{thm1}}]
% Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. 
% \end{proof}

% \noindent
% For a quote environment, use \verb+\begin{quote}...\end{quote}+
% \begin{quote}
% Quoted text example. Aliquam porttitor quam a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
% convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
% \end{quote}

% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text (refer Figure~\ref{fig1}). Sample body text. Sample body text. Sample body text (refer Table~\ref{tab3}).

% Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work. Authors are encouraged to include RIIDs where appropriate.

% \textbf{Ethical approval declarations} (only required where applicable) Any article reporting experiment/s carried out on (i)~live vertebrate (or higher invertebrates), (ii)~humans or (iii)~human samples must include an unambiguous statement within the methods section that meets the following requirements:

% \begin{enumerate}[1.]
% \item Approval: a statement which confirms that all experimental protocols were approved by a named institutional and/or licensing committee. Please identify the approving body in the methods section

% \item Accordance: a statement explicitly saying that the methods were carried out in accordance with the relevant guidelines and regulations

% \item Informed consent (for experiments involving humans or human tissue samples): include a statement confirming that informed consent was obtained from all participants and/or their legal guardian/s
% \end{enumerate}

% If your manuscript includes potentially identifying patient/participant information, or if it describes human transplantation research, or if it reports results of a clinical trial then  additional information will be required. Please visit (\url{https://www.nature.com/nature-research/editorial-policies}) for Nature Portfolio journals, (\url{https://www.springer.com/gp/authors-editors/journal-author/journal-author-helpdesk/publishing-ethics/14214}) for Springer Nature journals, or (\url{https://www.biomedcentral.com/getpublished/editorial-policies\#ethics+and+consent}) for BMC.

\section{Discussion}\label{sec12}
\input{04_discussion}

\section{Conclusion}\label{sec13}
% \input{05_conclusion}

\section{Methods}\label{sec11}
\input{02_methods}

\backmatter

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so here.

Authors reporting data from electrophoretic gels and blots should supply the full unprocessed scans for key as part of their Supplementary information. This may be requested by the editorial team/s if it is missing.

Please refer to Journal-level guidance for any specific requirements.

\bmhead{Acknowledgments}

Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.

Please refer to Journal-level guidance for any specific requirements.

\section*{Declarations}

% Some journals require declarations to be submitted in a standardised format. Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section. If yes, your manuscript must contain the following sections under the heading `Declarations':

\begin{itemize}
\item Funding
\item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
\item Ethics approval 
\item Consent to participate
\item Consent for publication
\item Availability of data and materials
\item Code availability 
\item Authors' contributions
\end{itemize}

\noindent
If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.

%%===================================================%%
%% For presentation purpose, we have included        %%
%% \bigskip command. please ignore this.             %%
%%===================================================%%
\bigskip
\begin{flushleft}%
Editorial Policies for:

\bigskip\noindent
Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}

\bigskip\noindent
Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}

\bigskip\noindent
\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}

\bigskip\noindent
BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
\end{flushleft}

\begin{appendices}

\section{Section title of first appendix}\label{secA1}

%%=============================================%%
%% For submissions to Nature Portfolio Journals %%
%% please use the heading ``Extended Data''.   %%
%%=============================================%%

%%=============================================================%%
%% Sample for another appendix section			       %%
%%=============================================================%%

%% \section{Example of another appendix section}\label{secA2}%
%% Appendices may be used for helpful, supporting or essential material that would otherwise 
%% clutter, break up or be distracting to the text. Appendices can consist of sections, figures, 
%% tables and equations etc.

\end{appendices}

%%===========================================================================================%%
%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
%% system, please include the references within the manuscript file itself. You may do this  %%
%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
%% file, and delete the associated \verb+\bibliography+ commands.                            %%
%%===========================================================================================%%

\bibliographystyle{sn-basic}
\bibliography{mybib}% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl

%% Default %%
%%\input sn-sample-bib.tex%

\end{document}

### 2022-04-21 paper/main/04_discussion.tex
style(refractor-project-by-updated-workflow): refactor the project by updated workflow
BREAKING CHANGE:

@@
 % 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
-It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability 
-\cite{cummingLinkingEconomicGrowth2018,reyersSocialEcologicalSystemsInsights2018}.
+It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability.
+%\cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
 % 在一种制度下开发的模型和方法在另一种制度下不一定有用。

### 2022-04-21 config.py

@@ -1,0 +1,82 @@
+#!/usr/bin/env python
+# -*-coding:utf-8 -*-
+# Created date: 2022/2/22
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+import logging
+import os
+
+ROOT = "/Users/songshgeo/Documents/Pycharm/YRB_NLP"
+REPORTS = os.path.join(ROOT, "analysis/reports")
+
+PROJECT_NAME = "NLProcessing_YRB_2021"
+
+# BASIC logging settings.
+LOG_FORMAT = "%(asctime)s %(levelname)s %(filename)s %(message)s "
+DATE_FORMAT = "%Y-%m-%d  %H:%M:%S %a "
+FILE_LEVEL = "debug"
+CMD_LEVEL = "warn"
+
+
+def set_logger(
+    name,
+    path=None,
+    reset=False,
+    log_format=None,
+    file_level="debug",
+    cmd_level="info",
+):
+    """
+    Setup a log file for my project.
+    :param name: logger's name
+    :param path: sub-folder path of the log file
+    :param reset: remove the old log file and refresh new one?
+    :param log_format: format of file message.
+    :param file_level: message save level in file.
+    :param cmd_level: message level print in CMD
+    :return: a logger.
+    """
+    log = logging.getLogger(name)
+    log.setLevel(logging.DEBUG)
+
+    file_level = getattr(logging, file_level.upper())
+    cmd_level = getattr(logging, cmd_level.upper())
+
+    if path:
+        file_path = os.path.join(ROOT, path, f"{name}.log")
+    else:
+        file_path = os.path.join(ROOT, f"{name}.log")
+    if not log_format:
+        log_format = LOG_FORMAT
+    if reset:
+        if not os.path.exists(file_path):
+            raise FileNotFoundError(
+                f"Logging file not found in {file_path}, no need of reset."
+            )
+        else:
+            os.remove(file_path)
+
+    # 建立一个 FileHandler 来把日志记录在文件里
+    file_handler = logging.FileHandler(file_path)
+    file_handler.setLevel(file_level)
+    file_handler.setFormatter(logging.Formatter(log_format))
+
+    # 建立一个 StreamHandler 来把日志打在CMD窗口上
[…]

### 2022-04-21 tools/region_differences.py
refactor(data): delete data

@@ -6,47 +6,46 @@
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
 
-import pandas as pd
 import numpy as np
-from matplotlib import pyplot as plt
-
-import sys
-sys.path.append(r"..")
-from tools.processing import get_region_by_province_name
-from tools.values import PROVINCES, INDUSTRIES_eng, INDUSTRIES, REGIONS
+import pandas as pd
+from processing import get_region_by_province_name
+from values import INDUSTRIES, REGIONS, INDUSTRIES_eng
 
 
-
-def get_yr_gdp_data(how='gdp'):
+def get_yr_gdp_data(how="gdp"):
     # 清洗列名
     def clean_col_names(name):
-        elements = name.split(':')  # 分割列名
+        elements = name.split(":")  # 分割列名
         province = elements[0].strip()  # 地名
         industry = elements[-1].strip()  # 产业
         return province, industry
-        
+
     # 加载经济数据
-    gdp = (pd.read_excel('../data/GDP.xlsx')  # 读取数据
-            .drop(0)  # 删除单位行
-            .astype(float)  # 转为浮点
-            .rename({'指标名称': 'Year'}, axis=1)  # 将年份列改名
-            .astype({'Year': int})  # 将年份从浮点改为整形
-            .set_index('Year')  # 并设置为索引
-            .replace(0., np.nan)  # 空值是没数据，不可能为 0
-            .drop(list(np.arange(1949, 1965)), axis=0)  # 删除不考虑的时间范围
-            )
-    region_dict = {region: pd.DataFrame() for region in REGIONS}  # 用来储存每个区域的GDP数据
+    gdp = (
+        pd.read_excel("../data/GDP.xlsx")  # 读取数据
+        .drop(0)  # 删除单位行
+        .astype(float)  # 转为浮点
+        .rename({"指标名称": "Year"}, axis=1)  # 将年份列改名
+        .astype({"Year": int})  # 将年份从浮点改为整形
+        .set_index("Year")  # 并设置为索引
+        .replace(0.0, np.nan)  # 空值是没数据，不可能为 0
+        .drop(list(np.arange(1949, 1965)), axis=0)  # 删除不考虑的时间范围
+    )
+    region_dict = {
+        region: pd.DataFrame() for region in REGIONS
+    }  # 用来储存每个区域的GDP数据
     for col in gdp:
         province = clean_col_names(col)[0]  # 清洗列名
[…]

### 2022-04-22 paper/main/02_methods.tex
style(refractor-project-by-updated-workflow): refactor the project by updated workflow
BREAKING CHANGE:
refactor(config.py-processing.py-values.py-statistic.py): refactor in formats

@@
 	\subsection{Contribution decomposition}
-		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index.
+		We decomposed the amount of variation in each index at different periods to quantify each influence's contribution to the index.
 Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
@@
 		\end{align}
-		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
+		Then, the contribution of dimension $x$ to IWGI's changes can be referred to as:
 		\begin{equation}
-			Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|}
+			Contribution_x = \frac{\Delta I'_x}{\lvert \Delta IWGI \rvert}
 		\end{equation}

### 2022-04-22 config.py

@@ -9,10 +9,10 @@
 import logging
 import os
 
-ROOT = "/Users/songshgeo/Documents/Pycharm/YRB_NLP"
+ROOT = "/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020"
 REPORTS = os.path.join(ROOT, "analysis/reports")
 
-PROJECT_NAME = "NLProcessing_YRB_2021"
+PROJECT_NAME = "WGRegimes_YRB_2020"
 
 # BASIC logging settings.
 LOG_FORMAT = "%(asctime)s %(levelname)s %(filename)s %(message)s "
@@ -71,12 +71,13 @@ def set_logger(
 
     log.addHandler(file_handler)
     log.addHandler(cmd_handler)
-    log.info(f"{name} starts logging.")
     return log
 
 
 log = set_logger(PROJECT_NAME, file_level=FILE_LEVEL, cmd_level=CMD_LEVEL)
 
-# if __name__ == '__main__':
-#     logger = set_logger(PROJECT_NAME, reset=True, file_level="info", cmd_level="warn")
-#     log.info("LOG reset.")
+if __name__ == "__main__":
+    logger = set_logger(
+        PROJECT_NAME, reset=True, file_level="info", cmd_level="warn"
+    )
+    logger.info("LOG reset.")

### 2022-04-22 tools/processing.py

@@ -2,25 +2,44 @@
 # - * - coding: utf-8 - * -
 # author: Shuang Song time: 2020/1/14
 # Email: SongshGeo@Gmail.com
-# project: 
+# project:
 
 import os
+
+import dbfread  # 加载dbfread包才能读取文件
 import pandas as pd
-import numpy as np
-from matplotlib import pyplot as plt
-import csv
 
 PROVINCES = [
-    '青海', '青海省', 'Qinghai',
-    '四川', '四川省', 'Sichuan',
-    '甘肃', '甘肃省', 'Gansu',
-    '宁夏', '宁夏回族自治区', 'Ningxia',
-    '内蒙', '内蒙古', '内蒙古自治区', 'Neimeng',
-    '陕西', '陕西省', 'Shanxi', 
-    '山西', '山西省', 'Shaanxi',
-    '河南', '河南省', 'Henan',
-    '山东', '山东省', 'Shandong'
-    '河北', '河北省', 'Hebei'
+    "青海",
+    "青海省",
+    "Qinghai",
+    "四川",
+    "四川省",
+    "Sichuan",
+    "甘肃",
+    "甘肃省",
+    "Gansu",
+    "宁夏",
+    "宁夏回族自治区",
+    "Ningxia",
+    "内蒙",
+    "内蒙古",
+    "内蒙古自治区",
+    "Neimeng",
+    "陕西",
+    "陕西省",
+    "Shanxi",
+    "山西",
+    "山西省",
+    "Shaanxi",
+    "河南",
+    "河南省",
+    "Henan",
+    "山东",
+    "山东省",
+    "Shandong" "河北",
+    "河北省",
+    "Hebei",
 ]
 
 
@@ -39,31 +58,30 @@ def get_region_by_province_name(name):
     return: 区域（源区上中下游，或返回空值）
     """
     if name in PROVINCES[:6]:
-        return 'SR'
+        return "SR"
     elif name in PROVINCES[6:16]:
-        return 'UR'
+        return "UR"
     elif name in PROVINCES[16:22]:
-        return 'MR'
+        return "MR"
     elif name in PROVINCES[22:]:
-        return 'DR'
+        return "DR"
     else:
         return None
 
 
 # 将dbf文件读取入pandas.DataFrame
-def pd_read_dbf(io, usecols=False):
+def pd_read_dbf(io, use_cols=False):
     """从文件系统中读取dbf文件并写入DataFrame
     io: 文件路径，
[…]

### 2022-04-22 tools/statistic.py

@@ -2,13 +2,14 @@
 # - * - coding: utf-8 - * -
 # author: Shuang Song time: 2020/1/14
 # Email: SongshGeo@Gmail.com
-# project: 
+# project: WGRegimes_YRB_2020
 
-import os
-import pandas as pd
-import numpy as np
-from matplotlib import pyplot as plt
 import math
+import os
+
+import numpy as np
+import pandas as pd
+from matplotlib import pyplot as plt
 
 
 def line_fit(x, y):
@@ -21,8 +22,10 @@ def line_fit(x, y):
         syy += y[i] * y[i]
         sxy += x[i] * y[i]
     a = (sy * sx / N - sxy) / (sx * sx / N - sxx)
-    b = (sy - a * sx) / N
-    r = abs(sy * sx / N - sxy) / math.sqrt((sxx - sx * sx / N) * (syy - sy * sy / N))
+    # b = (sy - a * sx) / N
+    r = abs(sy * sx / N - sxy) / math.sqrt(
+        (sxx - sx * sx / N) * (syy - sy * sy / N)
+    )
     formula = r"$k = %10.2f; R^2 =%10.2f$" % (a, r)
     return formula
 
@@ -31,13 +34,13 @@ def compile_cols(data, col1, col2):
     # 需要对比的值为value_x和value_y
     # 新家的列名为value_final
     # 1.设置一个flag,值为value_y-value_x,为正代表y较大，负代表x较大
-    data['value_flag'] = data[col1] - data[col2]
+    data["value_flag"] = data[col1] - data[col2]
     # 2.分别取得y较大的部分和x较大的部分
-    df_test_bigger = data[data['value_flag'] >= 0].copy()
-    df_test_litter = data[data['value_flag'] < 0].copy()
+    df_test_bigger = data[data["value_flag"] >= 0].copy()
+    df_test_litter = data[data["value_flag"] < 0].copy()
     # 3.分别对final进行赋值
-    df_test_bigger['Value_Final'] = df_test_bigger[col1]
-    df_test_litter['Value_Final'] = df_test_litter[col2]
+    df_test_bigger["Value_Final"] = df_test_bigger[col1]
+    df_test_litter["Value_Final"] = df_test_litter[col2]
     # 4.使用concat函数将其聚合
     df_result = pd.concat([df_test_bigger, df_test_litter])
     return df_result
@@ -56,7 +59,11 @@ def huanbi_rate(data, use_col, new_col):
             rate = np.nan
             result.append(rate)
         else:
[…]

### 2022-04-22 tools/values.py

@@ -5,34 +5,51 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
+import matplotlib
 
 # 所有黄河流域的省份
 PROVINCES = [
-    '青海', '青海省', 'Qinghai',
-    '四川', '四川省', 'Sichuan',
-    '甘肃', '甘肃省', 'Gansu',
-    '宁夏', '宁夏回族自治区', 'Ningxia',
-    '内蒙', '内蒙古', '内蒙古自治区', 'Neimeng',
-    '陕西', '陕西省', 'Shanxi', 
-    '山西', '山西省', 'Shaanxi',
-    '河南', '河南省', 'Henan',
-    '山东', '山东省', 'Shandong'
-    '河北', '河北省', 'Hebei'
+    "青海",
+    "青海省",
+    "Qinghai",
+    "四川",
+    "四川省",
+    "Sichuan",
+    "甘肃",
+    "甘肃省",
+    "Gansu",
+    "宁夏",
+    "宁夏回族自治区",
+    "Ningxia",
+    "内蒙",
+    "内蒙古",
+    "内蒙古自治区",
+    "Neimeng",
+    "陕西",
+    "陕西省",
+    "Shanxi",
+    "山西",
+    "山西省",
+    "Shaanxi",
+    "河南",
+    "河南省",
+    "Henan",
+    "山东",
+    "山东省",
+    "Shandong" "河北",
+    "河北省",
+    "Hebei",
 ]
 
-REGIONS = ['SR', 'UR', 'MR', 'DR']  # 设置区域
-
+REGIONS = ["SR", "UR", "MR", "DR"]  # 设置区域
 
 # 所有GDP相关常量
-INDUSTRIES = ['第一', '第二', '第三']  # 三个产业
-INDUSTRIES_eng = ['Agriculture', 'Industry', 'Services']  # 三个产业对应的英文
+INDUSTRIES = ["第一", "第二", "第三"]  # 三个产业
+INDUSTRIES_eng = ["Agriculture", "Industry", "Services"]  # 三个产业对应的英文
 
+period_colors = ["#0889A6", "#F1801F", "#006C43"]
+region_colors = ["#0077b6", "#e07a5f", "#f2cc8f", "#81b29a"]
+index_colors = ["#CFA7D1", "#79D6F0", "#E25A53"]
 
-period_colors = ['#0889A6', '#F1801F', '#006C43']
[…]

### 2022-04-22 paper/main/01_introduction.tex
fix(introduction,-abstract,-discussion,-method): polish paper according to the refree-1 from GEC
mainly: methods change, texts polishing

BREAKING CHANGE:

@@
 
-In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation)
+In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation) %!
+UNDP year
 \cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
-First, the supply of water depends not only on weather (with worrying long-term trends in many regions, such as the loss of glaciers) but also on the demands of economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
+First, the supply of water depends not only on climate (with increasing scarcity and unsertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
 \cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
@@
 \cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
-Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive approach to identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability Figure~\ref{fig:framework}.
+Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive approach to identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
 
 As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details).
-The YRB has experienced some of the most intense water use and dramatic regime shifts of any large river basin in China, giving rise to long-standing challenges for its governance.
+With drastically anthropogenic intervention, the YRB experienced the most intense water challenges in China, leading to long-standing sustainability barriers.
 % 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters and the constant shifts in the river’s channel made it difficult for people to use its waters
+From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters, and the constant shifts of channels made it difficult for its governance
 \cite{wangReducedsedimenttransport2016,liDecadalwaterstorage2020}.
@@
 \cite{xiaDevelopmentWaterAllocation2012}.
-Today, given that it is still difficult to completely meet water demands and various trade-offs must be negotiated between regions and sectors, there is still a long way to go towards successful water governance
+Today, it is still impossible to completely cover water demands, balance trade-offs between ecosystem services, and lead to equities in different regions; -who gets water, when and how is still an open question for sustainable water governance
 \cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
@@
 		A framework for understanding the relationship between transitional water governance regimes and eventual transformation to a hydrosocial cycle.
-A key missing element in current knowledge is an ability to detect regime shifts using a simple and comprehensive index.
+We aim to detect regime shifts using a simple and comprehensive index.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。

### 2022-04-22 paper/main/02_methods.tex
fix(introduction,-abstract,-discussion,-method): polish paper according to the refree-1 from GEC
mainly: methods change, texts polishing

BREAKING CHANGE:

@@
-The aim of this analysis was to develop a transparent and easily replicable approach to identifying water governance regimes and regime shifts; thus, it is not intended to provide a comprehensive model of social-ecological water dynamics.
-We constructed the Integrated Water Governance Index (IWGI) based on three dimensions (supply, purpose, allocation, see Figure 1) selected a priori and identified the changes in periods of the index over time using change point detection.
-Each dimension is reflected by an independent indicator after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different time periods.
-The contribution to changes of IWGI index along with each main indicator were also decomposed and calculated separately for each regime period.
+This analysis aimed to develop a transparent and easily replicable approach to identifying water governance regimes and regime shifts; thus, it is not intended to provide a comprehensive model of social-ecological water dynamics.
+First, we constructed the Integrated Water Governance Index (IWGI) based on three dimensions (Supply, Purpose, and Allocation, see Figure 1).
+Then, we identify the changes in the index's periods over time using change point detection.
+An independent indicator reflects each dimension after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different periods.
+Finally, we decomposed the contribution of each indicator to changes in the IWGI at each regime.
 
@@
 
-		\item \textbf{Priority($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
+		\item \textbf{Purpose($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
 		\begin{equation}
@@
 	\begin{equation}
-		Transformation \propto P*A*S^{-1}
+		Transformation \propto S*P*A
 	\end{equation}
 
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
+	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, A or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
 	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
@@
 	\begin{equation}
-		Transformation \propto ln(I_S) + ln(I_P) - ln(I_A)
+		Transformation \propto ln(I_S) + ln(I_P) + ln(I_A)
 	\end{equation}
@@
 	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To describe allocations $I_C$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
-	Our indicator $I_C$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
+	To describe allocations $I_A$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
+	Our indicator $I_A$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
 	\begin{equation}
-		I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}
+		I_A = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}
 	\end{equation}
@@
 The non-parametric statistic is defined as:
+
+		Mathematically, when a sequence of random variables is divided into two segments represented by \mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
+To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:
+
 		\begin{equation}
-			K_t = max|U_{t, T}|
+			U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j), 1 \leqq t < T
 		\end{equation}
 
-		Where:
+		where:
 		\begin{equation}
-			U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j)
+			\operatorname{sgn}(\theta)= \begin{cases}1 & \text { if } \theta>0 \\ 0 & \text { if } \theta=0 \\ -1 & \text { if } \theta<0\end{cases}
 		\end{equation}
 
-		The change-point of the series is located at $K_T$, provided that the statistic is significant.
-We used 0.001 as the threshold p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
+		The most probable change point $\tau$ is found where its value satisfies $K_{\tau} = max|U_{t, T}|$ and the significance probability associated with value $K_{\tau}$ is approximately evaluated as:
+		\begin{equation}
+			p=2 \exp \left(\frac{-6 K_{\tau}^{2}}{T^{2}+T^{3}}\right)
+		\end{equation}
+		Given a certain significance level $\alpha$, if $p < \alpha$, we reject the null hypothesis and conclude that $x_{\tau}$ is a significant change point at level $\alpha$.
+
+		We used $\alpha = 0.001$ as the threshold level of p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
 		Since this method can only return one significant change point, we repeated it until all significant change points were detected.
@@
 		We decomposed the amount of variation in each index at different periods to quantify each influence's contribution to the index.
-Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$).
+Using the Integrated Water Governance Index (IWGI) as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_A$).
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
 		\begin{align}
-		\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
-		&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
-		&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
+		\Delta IWGI &= (I'_{P_{y_2}} + I'_{A_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{A_{y_1}} - I'_{S_{y_1}}) \\
+		&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{A_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
+		&= \Delta I'_P + \Delta I'_A + (-\Delta I'_S)
 		\end{align}
@@
 		% Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
-		% $$  Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x |\Delta I'_x|} $$
+		% \begin{equation}
+		% 	Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x \lvert \Delta I'_x \rvert}
+		% \end{equation}
 
 		% or just for contributions (in proportion) within a certain year $j$ to the regime:
-		% $$ Contribution_{x,j}\% = \frac{|I'_{x, j}|}{|\sum_x I'_{x, j}|} $$
+		% \begin{equation}
+		% 	Contribution_{x,j}\% = \frac{\lvert I'_{x, j} \rvert}{\lvert \sum_x I'_{x, j} \rvert}
+		% \end{equation}
 

### 2022-04-22 paper/main/04_discussion.tex
fix(introduction,-abstract,-discussion,-method): polish paper according to the refree-1 from GEC
mainly: methods change, texts polishing

BREAKING CHANGE:

@@
 \cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
-Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario
+Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario %! informal citation
 \cite{millenniumecosystemassessmentEcosystemshumanwellbeing2005}.
@@
 % 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
+Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %!
+Kitroeff citation wrong
 \cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
@@
 
-\subsection{Implications and future directions}
+\subsection{Implications and future directions} %! limitations
 \label{Outlook}
+
+%! How data obtained, how assumptions are made.
 

### 2022-04-22 paper/sup/supplementary_information.tex
initialize standard to NW
fix(introduction,-abstract,-discussion,-method): polish paper according to the refree-1 from GEC
mainly: methods change, texts polishing

BREAKING CHANGE:

--- 2021-03-04 tex/sup/supplementary_information.tex
@@
 \author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Graeme S. Cumming, Bojie Fu (complete author list)}
-\correspondingauthor{Bojie Fu.\\E-mail: fubj@bnu.edu.cn}
+\correspondingauthor{Bojie Fu.\\E-mail: bfu@rcees.ac.cn}
 
@@
 For the section Methods S3, we introduced how to harmonize different datasets with various spatial and temporal scales.
-Then, the indicators corresponding to the IWRU are introduced in the section Methods S4. 
+Then, the indicators corresponding to the IWGI are introduced in the section Methods S4.
 Finally, we proposed sensitivity analysis in the section Methods S5, to test the robustness of our results.}
@@
 Water resources use dataset was published by Zhou et al.
-\cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in perfects level.
+\cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in Prefectures level.
 This dataset was mainly extracted by 2nd National Water Resources Assessment Program launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details).
@@
 % 指数介绍
-\section*{Methods S4. Indicators of IWRU}
+\section*{Methods S4. Indicators of IWGI}
 % 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
-The Integrated Water Resources Utilization (IWRU) index of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
+The Integrated Water Governance Index (IWGI) of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
 % 为了对这些维度进行量化，我们发现或发明了三个与指示其变化趋势相对应的指标:SFV指数、非供应共享和配置熵指标。
@@
 
-\subsection*{Priority: Non-provisioning share}
+\subsection*{Purpose: Non-provisioning share}
     %* 从消耗水 到 利用水
@@
     % Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
-    Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate priority of water utility:
+    Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate purpose of water utility:
     $$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
@@
     %* 直接用水和非直接用水
-    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 priority 的变化。
+    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 purpose 的变化。
     In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as provisioning water.
@@
 But if industrial consumption is taken into account, China is exporting virtual water.
-However, as a river basin with high degree of water resource scarcity, the trade-off between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of priority with water.
+However, as a river basin with high degree of water resource scarcity, the trade-off between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of purpose with water.
 
@@
 
-Firstly, we performed three different normalization methods in construction of IWRU for breakpoint detection:
+Firstly, we performed three different normalization methods in construction of IWGI for breakpoint detection:
 
@@
 Where $X$ is a time series and $X_{mean}$, $X_{std}$, $X_{min}$, $X_{max}$ are mean, standard deviation, minimum, maximum of it.
-% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWRU，我们对IWRU的断点检测结果都相同。
-No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWRU breakpoints are the same.
+% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWGI，我们对IWGI的断点检测结果都相同。
+No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWGI breakpoints are the same.
 
@@
 % 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
-% 		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
+% 		\textbf{B,} changes of water utilization purpose, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
 % 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
 % 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
-% 		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
+% 		\textbf{E,} Main impact water uses to water utilization purpose, and their change contributions to non-provisioning water shares.
 % 		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
@@
     \midrule
-    1. Water use & Statistical & Perfects & 1965-2013 & 2nd National Water Resources Assessment Program \\
+    1. Water use & Statistical & Prefectures & 1965-2013 & 2nd National Water Resources Assessment Program \\
     2. GDP & Statistical & Province & 1949-2019 & Wind database \\
@@
 
-    \footnotesize{$^a$ If a policy was proposed by multiple legacies, we only choose the highest one to show.}
+    \footnotesize{$^a$ If a policy was proposed by multiple legacies, we only show the highest one.}
 \end{table}

### 2022-04-22 paper/main/02_methods.tex
fix(appendix,-discussion): texts fixed according to the refree-2 from GEC

@@
 	\begin{itemize}
+		%! Why ??? Explaination: why should development lead to balance among regions or meet the needs of different sectors.
 		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
@@
 		We used $\alpha = 0.001$ as the threshold level of p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
-		Since this method can only return one significant change point, we repeated it until all significant change points were detected.
+		Since this method can only return one significant change point, we divided the series into two at that point and analyzed seach series separately, until all significant change points were detected.
 
@@
 	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI, we need to calculate multiple indicators and sub-indicators.
+	In order to calculate IWGI from 1965 to 2013, we need to calculate multiple indicators and sub-indicators.
 All the datasets used are listed in the \textit{SI Appendix} table S1.

### 2022-04-22 paper/main/03_results.tex
fix(appendix,-discussion): texts fixed according to the refree-2 from GEC

@@
 		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in total irrigated area (orange line), and water uses in per unit of area (WU/A, green dot line, see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use for unit production (WU/GVA, red dot line) respectively (\textit{SI Appendix} Methods S2).
-		\textbf{C.} Completed time of each new reservoir and their surrounding region's water use percentages as a proportion of the basin's total water use (WU) at that time.
-Red circles denote hub reservoirs in the basin, which play a role in integrated basin water management.
+		\textbf{A.} Changes in total irrigated area (orange line), and in water use intensity ($WU/A$, water use divided by the area, the green dot line), see \textit{SI Appendix} Methods S2).
+		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line) (\textit{SI Appendix} Methods S2).
+		\textbf{C.} Completed time of each new reservoir and their located region's (source, upper, middle, or lower reaches) water use percentages as a proportion of the basin's total water use (WU) at that time.
+Red circles denote the reservoirs mainly for managing and regulating the whole basin.
 		The size of each circle indicates the magnitude of its water storage capacity.
@@
 The named reservoirs are significant for the entire basin, not only for regional development.
+		%! 不清楚D的这些圆圈代表啥
 		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).

### 2022-04-22 paper/sup/supplementary_information.tex
fix(appendix,-discussion): texts fixed according to the refree-2 from GEC

@@
     \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region.
-However, because of backward production methods, efficiency of irrigation are used to be very low.
+However, the efficiency of irrigation are used to be very low.
     \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk.
@@
 \begin{itemize}
-    \item \textbf{The Ethos of Conquering Nature (since 1958)} Conquering the natural movement, although the Yellow River basin was poor and backward at that time, a collective spirit of ``man can conquer nature'' was formed.
+    \item \textbf{The Ethos of Conquering Nature (since 1958)} Conquering the natural movement, although the Yellow River basin was poor at that time, a collective spirit of ``man can conquer nature'' was formed.
 In addition to the construction of large-scale water conservancy projects represented by the Yellow River ``The Hong Qi Channel'', dramatic changes such as the ``Great Leap Forward'' movement and ``Large-scale production'' movement were also formed in this transformation.
     \item \textbf{The Reform and Opening-up (since 1978).} Before the reform and opening up, the allocation of resources and production activities throughout China, including the Yellow River Basin, were led by the state.
-At this time, the market gradually began to dominate.
+At this time, the market gradually began to play a role.
     \item \textbf{The 87 Water Diversion Scheme (since 1987).} Before the water diversion Scheme, all local sectors had unlimited access to water resources.
@@
 for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
-	$$ B_{i, j} = \frac{WU_{inflexible}}{R_{i, avg}} $$
+	$$ B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}} $$
 	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
@@
 Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which provisioning water is often the key to support the production of agricultural products, while non-provisioning water is more involved in industrial and other social processes.
+%!
+extensive studies need citations.
     % For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade.
@@
         \textbf{B.} Population of urban or rural area in different regions.
-        \textbf{C.} Natural water yield in different regions.
+        \textbf{C.} Natural water resource in different regions.
         \textbf{D.} Total water use in different regions.
@@
     \caption{
-        Saving water irrigated area ratio in 2013 for each region. There were no saving water irrigated area in  the YRB in 1960s.
+        The ratio of irrigated area with saving-water equipments to the total irrigated area in 2013.
     }

### 2022-04-24 paper/main/01_introduction.tex
fix(appendix,-discussion): texts fixed according to the refree-2 from GEC
feat(introduction,-manuscript): change fig path correctly, add knowledge gap and defination of water governace
BREAKING CHANGE:

@@
 \cite{gleesonIlluminatingwatercycle2020}.
-It is essential, not only for earth system processes but also in supporting the economic development and continued wellbeing of human societies.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, moving rivers along a trajectory towards a hydrosocial water cycle in which social and power relations dominate the nature of hydrological cycles
+It is essential not only for earth system processes but also in supporting the economic development and continued well-being of human societies.
+Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, moving rivers dominated by a hybrid of social and natural tendencies
 \cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
-Facing this major transformation, many of the world’s big river basins (which are hot spots of civilization and economic growth) are urgently in need of new models of water governance for sustainability
+Facing this major transformation, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
 \cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.
-As an integral part of a proposed earth system governance framework, sustainable water governance requires a deep understanding of the complex relationships between people and water
+As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
 \cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.
 
-For water resources in populated areas, missing governance means missing sustainability
+Governance is essentially about ``who gets what, when and how''.
+Specifically, water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %!
+citation.
+For water resources in populated areas, missing governance means missing sustainability, and a first important step in understanding transitions toward successful water governance is identifying the different regimes.
 \cite{undpwatergovernancefacilityWaterGovernanceIssue}.
-A first important step in identifying transitions towards a hydrosocial water cycle is to identify the different regimes under which it occurs.
-According to the United Nations Development Programme (UNDP), three key dimensions of water use are decided by the water governance regime directly: ``How much water can be used?'' (supply), ``How can different services provided by water be balanced?'' (purpose), and ``How can water be allocated equally and efficiently?'' (allocation)
+Corresponding to ``who gets what, when and how'', the United Nations Development Programme (UNDP) suggests three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (supply), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
 \cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
-A regime is defined as a locally stable state of a system’s structure, function, and dominant controls
+As a locally stable state of a system, function, and dominant controls, habitual relationships between humans and water maintain regimes of water governance
 \cite{carpenterEarlyWarningsRegime2011}.
-Large and persistent changes in key system properties may lead to a loss of local stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
+However, large and persistent changes in key properties may lead to a loss of systematical stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
 \cite{rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
-Regime shifts are both consequences and signals of substantive changes in water governance, and may lead to new challenges to sustainability.
-
-In addition to being caused by changes in key environmental, economic, social and political variables, regime shifts in water governance can be triggered through changes in each of the three key dimensions of governance (supply, purpose, and allocation) %!
+Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts can trigger changes in the three key dimensions of water governance (supply, purpose, and allocation), with new challenges to sustainability %!
 UNDP year
 \cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
-First, the supply of water depends not only on climate (with increasing scarcity and unsertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
+First, the supply of water depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
 \cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
-Second, the purposes for which water is used are in need of balanced between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production or urban services)
+Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
 \cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
-Water governance can be viewed as the process of assigning weights to each of these different purposes and enforcing the resulting rules.
-Third, the allocation of water across the whole basin is influenced not only by regional environmental context but also by local socio-economic trends and regions’ comparative economic advantages, which can be altered by changing social and political drivers
+Third, the allocation of water across the whole basin is influenced not only by regionally socio-economic and environmental context but also by systematically regulating resources
 \cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
-Despite the obvious relevance of substantive changes in any of the three dimensions of water governance, the lack of a simple but comprehensive approach to identifying changes in water governance regimes makes it difficult to achieve water governance for sustainability (Figure~\ref{fig:framework}).
+Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.
+The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).
 
@@
 \cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
-However, water over-use has led to drying up of the Yellow River, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
+However, water over-use has led to depletions of the over-burdened river, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
 \cite{xiaDevelopmentWaterAllocation2012}.
@@
 \cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
-The YRB has been among the most rapidly-changing large river basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
-Identifying regime shifts in water governance within the YRB can thus provide crucial insights into the world’s rapidly-changing big river basins and the ways in which governance may respond to meeting challenges to their sustainability.
+The YRB has been among the most rapidly-changing large river basins worldwide, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
+Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.
 
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-We first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin scale (see Figure~\ref{fig:framework} and methods).
+Here, we first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
 % 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how the index can be used to analyse the complicated regimes of water governance and their main causes in a comprehensive but simple way.
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance and their leading causes in a comprehensive but straightforward way.
 % 最后总结出一般性框架
@@
 \begin{figure*}%[htbp]
+	%! I don't know that fig.1 adds much, the explanatory text to the figure is the key.
 	\centering
@@
 	\caption{
-		A framework for understanding the relationship between transitional water governance regimes and eventual transformation to a hydrosocial cycle.
-We aim to detect regime shifts using a simple and comprehensive index.
+		A framework for understanding the relationship between water governance regimes and transitions of a hydrosocial cycle. We aim to detect regime shifts using a simple and comprehensive index.
 		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see Methods for details).
+		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see \textbf{Methods} for details).
 Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
@@
 		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B:} governance changes are an emergent outcome of trends across the three dimensions.
-Water governance status changes along a trajectory towards a hydrosocial water cycle.
+		\textbf{B:} along a trajectory of hydrosocial water cycle, governance changes are related to the combination of trends across the three dimensions.
 When abrupt change occurs, it may indicate a regime shift in water governance

### 2022-04-24 paper/main/02_methods.tex
feat(results): now another way to calculate IWGI applied, results changed througout
S+P+A / 3 = IWGI, more directly and makes more sense

BREAKING CHANGE: refrees all asked about the method

@@
 
-		Mathematically, when a sequence of random variables is divided into two segments represented by \mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
+		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
 To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:

### 2022-04-24 paper/main/03_results.tex
feat(results): now another way to calculate IWGI applied, results changed througout
S+P+A / 3 = IWGI, more directly and makes more sense

BREAKING CHANGE: refrees all asked about the method

@@
 
-\begin{figure}[ht!]
+\begin{figure*}[ht!]
 	\centering
@@
 	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were respectively the main positive contributors to P1, P2 and P3.
+	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were the main positive contributors to P1, P2 and P3.
+	\textbf{C,} Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
+The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
+	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
+When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.
 	}
 	\label{fig:IWGI}
-\end{figure}
+\end{figure*}
 
 % 这一节主要展示IWGI的变化趋势和WUR的划分
-With two significant breakpoints, the changes in the IWGI are divided into three periods (Figure~\ref{fig:IWGI}A) with different slopes.
-The changes are contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
+Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three dimensions (Figure~\ref{fig:IWGI}A).
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI increased rapidly.
-Water supply made the most striking positive contribution (131\%), while purpose and allocation had a slight negative contribution (-11\% and -20\%).
+In the first period (P1, 1965-1978), the IWGI decreased rapidly.
+While the indicator of purpose and allocation contributed more to the IWGI, the remarkable downward trend correlates significantly to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
 % 第二阶段
-In the second period (P2, 1979-1994), the contributions of purpose and allocation became positive and the IWGI experienced a drop because steeply declining supply capacity played a larger negative role (dropping to -188\% lower than P1).
+In the second period (P2, 1979-2001), the increasing stress indicator significantly contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
 % 第三阶段
-In the third period (P3, 1995-2013), as positive contributions from purpose (75\%) and allocation (84\%) increased further and the negative contribution of water supply lessened (-59\%), positive growth of the IWGI returned.
+During the third period (P3, 1995-2013), while the stress indicator kept its most significant share in contributions, the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
 
 % 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-Each period has a unique most striking contributor to IWGI in positive. Overall features of the three dimensions in different periods are shown in Figure~\ref{fig:phases}.
+Overall features of the three dimensions in different periods are shown in Ternary, where each regime shift associates to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
 % 第一阶段到第二阶段
-Throughout P1, the water governance regime was dominated by increasing supply capacities.
+Throughout P1, the IWGI shifts paralleled with the left axis because the Purpose indicator was barely changed and others two changed in similar trends.
+Analogously, as the stress indicator unchanged during the P3, the IWGI shifts paralleled with the right axis while others two changed in opposite trends.
 % 第三阶段集中
-It then experienced a shift, slowing down in increasing supply during P2, with an accompanying reverse in the contributed proportion between purpose and allocation.
-Finally, the contribution of all three dimensions was similar in P3 (32.91\%, 31.87\% and 35.21\% for purpose, allocation and supply respectively), making the points cluster at the centre of the diagram.
+The regime then experienced a long distance shift during the P2, as three indicators changed their ratios of contribution drastically to IWGI, simultaneously.
 % 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a purpose-focused regime (P2: 1979-1993), and a many-sided governance regime (P3: 1994-2013).
+The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{main/phases.jpg}
-	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
+% \begin{figure}[!htbp]
+% 	\centering
+% 	\includegraphics[width=0.9\linewidth]{main/phases.jpg}
+% 	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
 The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
+% 	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
 When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
-	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
-	\label{fig:phases}
-\end{figure}
+% 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
+% 	\label{fig:phases}
+% \end{figure}
 
@@
 
-\begin{figure}[th!]
+\begin{figure*}[th!]
 	\centering
-	\includegraphics[width=0.9\linewidth]{main/causes.jpg}
+	\includegraphics[width=0.9\linewidth]{main/causes.pdf}
 	\caption{
@@
 	\label{fig:Causes}
-\end{figure}
+\end{figure*}
 
@@
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering P2, however, the expansion of irrigated area stalled and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
+Entering P2, however, the expansion of irrigated area slowed down and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
 
 % 水分利用效率由P2变化到P3。
-The efficiency of water use changed from P2 to P3.
-While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+From P2 to P3, the efficiency of water use changed obviously.
+Not only irrigated area kept its slowly expansion in P3 (Figure\ref{fig:Causes}A), industry and urban services also assumed stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
 However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
 S4), both experienced significant declines in water use for unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).
+As a result, the differences between sectors of water use were reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).
 
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and water governance policies played roles in all three regimes.
+Finally, environmental context, social transformation and policies played roles in all three regimes.
 % 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
-We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio), with a higher ratio representing a potential role for supply rather than regulation (Figure~\ref{fig:Causes}C).
+We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
 % 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1, when natural water resources were relatively abundant (\textit{SI Appendix} Fig.
-S5), and R/B ratios were significantly higher (Figure~\ref{fig:Causes}C, p<0.01).
+Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1 (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, p<0.01), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig.
+S5).
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-In P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by ``the 87 Water Allocation Scheme'', with little increase in total water storage capacity (\textit{SI Appendix} Fig.
+Since P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by significantly increased basinal policies (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, p<0.01 and \textit{SI Appendix} Fig.
 S6).
 % 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering P3, myriad national-level water governance policies were proposed under the guide of ``environmental regulation'' (Figure~\ref{fig:Causes}D), and the number of new reservoirs was even higher for facilitating and regulating objectives.
-Most of these were built in regions with lower R/B ratios (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig.
-S6).
+Entering P3, more national-level water governance policies were proposed under the guide of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
+Taken together, the regime shift from P1 to P2 in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-24 paper/main/04_discussion.tex
fix(appendix,-discussion): texts fixed according to the refree-2 from GEC
feat(results): now another way to calculate IWGI applied, results changed througout
S+P+A / 3 = IWGI, more directly and makes more sense

BREAKING CHANGE: refrees all asked about the method

@@
-\subsection{Water governance challenges along transition regimes}
+\subsection{Water governance challenges along with transition regimes}
 
@@
 		Transition schema of water governance during transformation towards a hydrosocial water cycle.
-Blue pathways are dominated by natural water cycle while red pathways are dominated by socio-economic feedbacks.
-There is a transformation towards the hydrosocial water cycle where red loop increases.
+The natural water cycle dominates blue pathways while socio-economic feedbacks dominate red pathways.
+Finally, there is a transformation towards the hydrosocial water cycle where red loop increases.
 		\textbf{A.
@@
 Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
+		%! The note to C. makes no sense! from the refree 2.
 		Thus, \textbf{C.
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB (Figure~\ref{fig:phases}): a massive supply regime (1965-1978), a purpose-focused regime (1979-1993) and a many-sided governance regime (1994-2013).
-Shifts between these regimes were caused by different environmental, economic, social or political drivers (Figure~\ref{fig:Causes}).
-% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
-It is important to note that each regime occurred gradually, with multifaceted causes, as the basin moves towards a hydrosocial water cycle.
-The challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
+Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013).
+Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers.
+The process echoes previous studies on how social systems can change water governance regimes by enhancing their adaptive capacity.
+However, the IWGI quantitatively identifies and reveals that conceptual pattern, thus characterizing the transition process of water governance in detail for the first time.
+It is important to note that each indicator or cause changed gradually, but emergence of regime shifts moves water governance along with the hydrosocial water cycle at a basin scale.
+As a result, the challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
 
@@
 \cite{konarExpandingScopeFoundation2019}.
+%! Discussion in water transfer.
 
+%! Discussion in which contries this method can be applied
 % 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
@@
 %! How data obtained, how assumptions are made.
-
 % IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
@@
 % 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
-It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability.
-%\cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
+It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability. %! 完全是陈词滥调
+%! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
 % 在一种制度下开发的模型和方法在另一种制度下不一定有用。

### 2022-04-26 paper/main/03_results.tex
docs(discussion-and-results): implications, limiations, and directions

@@
 % 第三阶段集中
-The regime then experienced a long distance shift during the P2, as three indicators changed their ratios of contribution drastically to IWGI, simultaneously.
+The regime then experienced a long distance shift during the P2, as three indicators simultaneously changed their ratios of contribution to IWGI.
 % 总结来说，三个稳态

### 2022-04-26 paper/main/04_discussion.tex
docs(discussion-and-results): implications, limiations, and directions

@@
-\subsection{Water governance challenges along with transition regimes}
+\subsection{Challenges along with transition of water governance regimes}
 
@@
 Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013).
-Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers.
-The process echoes previous studies on how social systems can change water governance regimes by enhancing their adaptive capacity.
-However, the IWGI quantitatively identifies and reveals that conceptual pattern, thus characterizing the transition process of water governance in detail for the first time.
-It is important to note that each indicator or cause changed gradually, but emergence of regime shifts moves water governance along with the hydrosocial water cycle at a basin scale.
-As a result, the challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).
+Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, then decide who gets water, when and how.
+The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
+However, the IWGI quantitatively identifies and reveals that conceptual pattern, thus characterizing the transition of water governance in detail for the first time.
+It is important to note that each indicator or cause changed gradually, but emerging regime shifts moves water governance along with the hydrosocial water cycle at a basin scale.
+As a result, the challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).
 
-% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
-During the massive supply regime (1965-1978), the basin economy was mainly dependent on the agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5); water governance thus tended to supply more resources for agriculture (e.g.
-by construction of reservoirs and channels).
-% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
-Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
+% 在水资源压力较低的大规模供应制度(长江流域1965-1978年)期间，水治理实践倾向于通过建设水库和渠道来增加服务用水(当时主要是供应目的——牲畜和农作物)。
+During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus practices tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by construction of reservoirs and channels.
+% 然而，正如“人类将征服自然”的流行口号所暗示的那样，水供应的增加很少考虑到人水关系不可逆转的变化，从而也急剧增加了水的需求，很少考虑到流域的保护。
+As the the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes of human-water relationship, thus also drastically increased water demand with few consideration in basinal conservation.
 \cite{zhouDecelerationChinahuman2020}.
-% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
-Since nearly 80\% of surface water was used (mainly for provisioning purposes), the Yellow River dried up during the second half of the regime (\textit{SI Appendix} Figure S7).
-% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
-Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
+% 在那十年里，灌溉农田和引水设施的迅速扩张，使负担过重的长江水利枢纽接近临界点，在这个临界点上，持续增加供应来满足无限的需求是不现实的
+The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimits of demand is unpractical
+% 结果，自1972年以来，超过80%的地表水使用量导致了河流的频繁枯竭，随之而来的是生态问题，如湿地的萎缩和生物多样性的下降。
+As a result, the over 80\% surface water use then led to depletions of the river frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity. 
+% 此外，由于处于上升阶段的工业经济也受到水资源压力的限制，现有的水治理模式严重导致了巨大的社会-生态危机和对可持续性的重大挑战
+In addition, as the industrial economy in the ascendant was also limited by the water stress, the existing modes of water governance led a huge social-ecological crisis and a significant challenge to sustainability rigorously
 \cite{wohlfartRiverBasinCourse2016}.
 
-% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
-The start of the purpose-focused regime (1978) coincided with Chinese ``reform and opening-up''.
-This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig.
-S8).
-% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
-In the face of ongoing environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) underwent a reorganization and received instructions from the Ministry of Water Resources (then called the Ministry of Water Resources and Electric Power) to resume and strengthen work on hydrology and basin management in the YRB
-\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
-% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
-As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
+The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after ``openning and reform''.
+% 正如理论预测的那样
+The results in the YRB keep in line with the suggestions from theorical analysis: continuous increases in water demand when the basinal total supply is stable can be accompanied by large changes in governance regime and the rapidly enhancement in overall social adaptive capacity.
+% 作为制度转变的先行者
+Being a pioneer in shifting governing institution, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfering plan and so on
 \cite{wangThirtyYearsYellow2018}.
+% 因此，1999年黄河的最后一次枯竭
+As a consequence, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnotes to the climax of this transformation in water governance.
 
-% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
-The next shift, to the many-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits
-\cite{liuWaterconservancyprojects2013}.
-% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
-Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
+Finally, it came into an adaptation-oriented regime (P3: 2002-2013), when drastically shifting in societies occurred with a stable water stress.
+Socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
 \cite{dalinBalancingwaterresource2015}.
-% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
-For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
-\cite{barnettSustainabilityTransferproject2015,yunpengWaterRightTransfer2010}.
-% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
-On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
-\cite{wangThirtyYearsYellow2018}.
+Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the widespread requirements of adjusting in the rigid quota shares from the previous regime can be an example.
 % 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
-Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
+Like this, much national-level water governing practices were proposed under the regime, because the absence of such policies with social dilemma of high quality development became new structural challenges for water governance
 \cite{konarExpandingScopeFoundation2019}.
-%! Discussion in water transfer.
 
-%! Discussion in which contries this method can be applied
 % 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
-In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
-% 随着越来越多的人为影响逐渐改变世界，对生态系统动力学从生物物理控制向社会和政治控制的转变可能在社会-生态系统中变得越来越普遍
-Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
+In general, shift between the governance regimes advances in parallel with the trajectory of hydrosocial cycle (Figure~\ref{fig:summary}A, B and C).
+Transition from biophysical control to social and institutional control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
 \cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
-Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario %! informal citation
-\cite{millenniumecosystemassessmentEcosystemshumanwellbeing2005}.
-% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
-The transition regimes identified here echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
+With intensive anthropogenic intervention, the YRB may be the most prominent example in this general transition of water governance -``improving supply, transforming governance, and enhancing adaptation'' %!
+citation.
+The transition regimes identified here also echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
 S9)
 \cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
-% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
+Our analysis suggests that the early phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
 Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
 \cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
-% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
 Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %!
@@
 \cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
-% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
-It is typical that resource challenges and structural challenges have occurred sequentially during the transition of water governance within the YRB.
-% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
-Our analysis thus suggests that the initial phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
-% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
-From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
+It is typical that resource challenges and structural challenges occurred sequentially during the transition of water governance within the YRB.
+From the perspective of the core dimensions emphasized by the UNDP for water governance, therefore, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
 
-% 随着河流流域在不同制度之间的过渡而发生的升级过程也带来了额外的挑战。在经济力量的影响下，水资源利用逐渐从一个地方性的问题转变为国家或国际的问题，大型河流流域成为生态系统服务、经济发展和人类福祉的重要来源。
-Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes.
-Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
-% 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
-For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi Dam of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time
-\cite{kongEnvironmentalimpactassessments2017}.
-% 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
-Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
-\cite{cummingScalemismatchessocialecological2006}.
-
-\subsection{Implications and future directions} %! limitations
+\subsection{Implications, limitations, and future directions}
 \label{Outlook}
 
-%! How data obtained, how assumptions are made.
-% IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
-The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
-% 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
-It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability. %! 完全是陈词滥调
+% Implications
+Water governance gradually changes from being a primarily local concern to becoming a national or international concern, because large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
+As the ubiquitous tele-coupling are rising additional challenges of water governance in the tighter connected world, where transition between regimes aligns with different human-water relationships. 
+Within the growing hydro-social cycle, the IWGI index captures the increasment of the adaptive capacity and sketches the transitional regimes of water governance, in a relatively straightforward but comprehensive way.
+It is important for scientists and decision makers to recognize the changing governance challenges, because models, institutions, engineerings, and approaches developed under one regime are not necessarily useful under a different regime
 %! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
-% 在一种制度下开发的模型和方法在另一种制度下不一定有用。
-Models and approaches developed under one regime are not necessarily useful under a different regime.
-% 就当今世界而言，与水有关的挑战仍是我们在实现可持续性方面取得进展的主要差距之一，而发展优先战略在许多地方仍是主导方针，可能不利于改善治理
+In the case of the YRB, an important institutions of water quota in the governance tranforming regime became rigid during the enhanced adaptation phase.
+On contrary, additional water from the ambitious cross-basins water diversion project, which originated in the phase of massive supply can play an even more crucial role in today's enhancing adaptation phase.
+Overall, applications of IWGI can induce a straightforward understanding of the water governance in transition of hydrosocial cycle, as descriptions from some previous conceptual frameworks suggested for all large-scale basins worldwide.
+
+%! limitations
+One of the main limitations of applying IWGI in abundant data availability for a long-term period of time. 
+For an example, we used the stress-flexibility-variability (SFV index) here, one of the most comprehensive index to our knowledge, as an indicator of the water stress dimension. 
+With other indicators, therefore, we obtained various datasets in the YRB: water use in different regions and sectors, streamflows in different reaches, reservoir capacity and completion time, with further more information in social, economic, and institutional for interpretation.
+It means still a gap between the comprehensively identifying and widespread application of IWGI.
+However, we assumed that all solutions of water governance are relative to the question of ``who gets water, when and how'', so water stress, purposes of water services, and patterns of water allocation are matters.
+We suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes.
+
+% direction
 For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
@@
 \cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
+% 我们的分析展示了这种路径的前方很可能是严峻的水治理挑战。
 % 总的来说，这种明显的治理失败可能有两个主要原因。
-Overall, there are probably two main reasons for this apparent failure of governance.
+% Overall, there are probably two main reasons for this apparent failure of governance.
 % 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
-First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
+% First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
 \cite{graftonparadoxirrigationefficiency2018}.
 % 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
-Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
+In the future, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
 \cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
 % 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
-From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage
+From these perspectives, we need more flexible and comprehensive strategies to address governance challenges because the core problems are dynamic and complex
 \cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.

### 2022-04-26 paper/main/01_introduction.tex
docs(introduction,-result,-discussion): grammarly check

@@
 
-As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details).
-With drastically anthropogenic intervention, the YRB experienced the most intense water challenges in China, leading to long-standing sustainability barriers.
-% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
-From about 550BC until half a century ago, flooding and the huge sediment loads of the Yellow River brought frequent human disasters, and the constant shifts of channels made it difficult for its governance
-\cite{wangReducedsedimenttransport2016,liDecadalwaterstorage2020}.
+As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details), the fifth-largest river in the world.
+With drastically anthropogenic intervention, the YRB experienced the most intense water governance challenges in China, leading to long-standing sustainability barriers.
 Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, we first use the three key dimensions (supply, purpose and allocation) of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
+Here, we first use the three key dimensions (supply, purpose and allocation) by corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
 % 使用案例研究

### 2022-04-26 paper/main/03_results.tex
docs(introduction,-result,-discussion): grammarly check

@@
 	\textbf{C,} Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
+	The red indicator line in this plot denotes a 1:1 contribution between purpose (P) and allocation (A).
 When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.
@@
 % 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-Overall features of the three dimensions in different periods are shown in Ternary, where each regime shift associates to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
+The ternary shows overall features of the three dimensions in different periods, where each regime shift is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
 % 第一阶段到第二阶段
-Throughout P1, the IWGI shifts paralleled with the left axis because the Purpose indicator was barely changed and others two changed in similar trends.
-Analogously, as the stress indicator unchanged during the P3, the IWGI shifts paralleled with the right axis while others two changed in opposite trends.
+Throughout P1, the IWGI shifts paralleled the left axis because the Purpose indicator barely changed, and the other two changed in similar trends.
+Analogously, as the stress indicator is unchanged during the P3, the IWGI shifts paralleled with the right side of the axis while the other two changed in opposite trends.
 % 第三阶段集中
-The regime then experienced a long distance shift during the P2, as three indicators simultaneously changed their ratios of contribution to IWGI.
+The regime then experienced a long-distance shift during the P2, as three indicators simultaneously changed their contribution ratios to IWGI.
 % 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).
-
-% \begin{figure}[!htbp]
-% 	\centering
-% 	\includegraphics[width=0.9\linewidth]{main/phases.jpg}
-% 	\caption{Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-The closer a point is to an angle of the outside triangle, the greater the proportion of the contribution of this dimension.
-% 	The red indicator line in this plot denotes a 1:1 contributions between purpose (P) and allocation (A).
-When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.}
-% 	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
-% 	\label{fig:phases}
-% \end{figure}
+The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).
 
@@
 		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in total irrigated area (orange line), and in water use intensity ($WU/A$, water use divided by the area, the green dot line), see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line), and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line) (\textit{SI Appendix} Methods S2).
+		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the area, the green dot line), see \textit{SI Appendix} Methods S2).
+		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line) (\textit{SI Appendix} Methods S2).
 		\textbf{C.} Completed time of each new reservoir and their located region's (source, upper, middle, or lower reaches) water use percentages as a proportion of the basin's total water use (WU) at that time.
@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-Some important reservoirs include: (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing flood water discharge and water supply.
+Some important reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which was constructed mainly for managing floodwater discharge and water supply.
 The named reservoirs are significant for the entire basin, not only for regional development.
@@
 % 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
-Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated area and the economic growth of industry and services were key to the change in purpose between P1 and P2.
+Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
@@
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering P2, however, the expansion of irrigated area slowed down and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to a $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
+Entering P2, however, the expansion of irrigated area slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
 
@@
 From P2 to P3, the efficiency of water use changed obviously.
-Not only irrigated area kept its slowly expansion in P3 (Figure\ref{fig:Causes}A), industry and urban services also assumed stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+Not only irrigated areas keep their slow expansion in P3 (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
 However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), both experienced significant declines in water use for unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use were reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).
+S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+As a result, the differences between sectors of water use reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).
 
@@
 % 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-Since P2, the number of new reservoirs decreased significantly and allocation of water was rigorously controlled by significantly increased basinal policies (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, p<0.01 and \textit{SI Appendix} Fig.
+Since P2, the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, p<0.01 and \textit{SI Appendix} Fig.
 S6).
 % 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-Entering P3, more national-level water governance policies were proposed under the guide of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
-Taken together, the regime shift from P1 to P2 in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.
+In P3, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
+The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-26 paper/main/04_discussion.tex
fix(format): format fix
docs(introduction,-result,-discussion): grammarly check

@@
-\subsection{Challenges along with transition of water governance regimes}
+\subsection{Challenges along with the transition}
 
@@
 		Transition schema of water governance during transformation towards a hydrosocial water cycle.
-The natural water cycle dominates blue pathways while socio-economic feedbacks dominate red pathways.
+The natural water cycle dominates blue pathways while socio-economic feedback dominate red pathways.
 Finally, there is a transformation towards the hydrosocial water cycle where red loop increases.
@@
 Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle.
-This is generally distinguished when water resource limits are reached.
+This is generally distinguished when it reaches water resource limits.
 The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
@@
 Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013).
-Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, then decide who gets water, when and how.
+Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, deciding who gets water, when and how.
 The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
-However, the IWGI quantitatively identifies and reveals that conceptual pattern, thus characterizing the transition of water governance in detail for the first time.
-It is important to note that each indicator or cause changed gradually, but emerging regime shifts moves water governance along with the hydrosocial water cycle at a basin scale.
-As a result, the challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).
+However, the IWGI quantitatively identifies and reveals that abstract pattern, thus characterizing the transition of water governance in detail for the first time.
+It is important to note that each indicator or cause changes gradually, but emerging regime shifts move water governance along with the hydrosocial water cycle at a basin scale.
+As a result, the water governance challenges were primarily economic and environmental at the beginning of the trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).
 
 % 在水资源压力较低的大规模供应制度(长江流域1965-1978年)期间，水治理实践倾向于通过建设水库和渠道来增加服务用水(当时主要是供应目的——牲畜和农作物)。
-During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus practices tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by construction of reservoirs and channels.
+During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
 % 然而，正如“人类将征服自然”的流行口号所暗示的那样，水供应的增加很少考虑到人水关系不可逆转的变化，从而也急剧增加了水的需求，很少考虑到流域的保护。
-As the the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes of human-water relationship, thus also drastically increased water demand with few consideration in basinal conservation.
+As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation.
 \cite{zhouDecelerationChinahuman2020}.
 % 在那十年里，灌溉农田和引水设施的迅速扩张，使负担过重的长江水利枢纽接近临界点，在这个临界点上，持续增加供应来满足无限的需求是不现实的
-The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimits of demand is unpractical
+The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical
 % 结果，自1972年以来，超过80%的地表水使用量导致了河流的频繁枯竭，随之而来的是生态问题，如湿地的萎缩和生物多样性的下降。
-As a result, the over 80\% surface water use then led to depletions of the river frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity. 
+As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity.
 % 此外，由于处于上升阶段的工业经济也受到水资源压力的限制，现有的水治理模式严重导致了巨大的社会-生态危机和对可持续性的重大挑战
-In addition, as the industrial economy in the ascendant was also limited by the water stress, the existing modes of water governance led a huge social-ecological crisis and a significant challenge to sustainability rigorously
+In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
 \cite{wohlfartRiverBasinCourse2016}.
 
-The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after ``openning and reform''.
+The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after ``opening and reform''.
 % 正如理论预测的那样
-The results in the YRB keep in line with the suggestions from theorical analysis: continuous increases in water demand when the basinal total supply is stable can be accompanied by large changes in governance regime and the rapidly enhancement in overall social adaptive capacity.
+The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity %!
+Citation.
 % 作为制度转变的先行者
-Being a pioneer in shifting governing institution, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfering plan and so on
+Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
 \cite{wangThirtyYearsYellow2018}.
 % 因此，1999年黄河的最后一次枯竭
-As a consequence, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnotes to the climax of this transformation in water governance.
+Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance.
 
-Finally, it came into an adaptation-oriented regime (P3: 2002-2013), when drastically shifting in societies occurred with a stable water stress.
-Socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
+Finally, it came into an adaptation-oriented regime (P3: 2002-2013), when drastically shifting in societies occurred with stable water stress.
+Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
 \cite{dalinBalancingwaterresource2015}.
-Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the widespread requirements of adjusting in the rigid quota shares from the previous regime can be an example.
+Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example.
 % 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
-Like this, much national-level water governing practices were proposed under the regime, because the absence of such policies with social dilemma of high quality development became new structural challenges for water governance
+Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
 \cite{konarExpandingScopeFoundation2019}.
@@
 % 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
-In general, shift between the governance regimes advances in parallel with the trajectory of hydrosocial cycle (Figure~\ref{fig:summary}A, B and C).
-Transition from biophysical control to social and institutional control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
+In general, the shift between the governance regimes advances in parallel with the trajectory of the hydrosocial cycle (Figure~\ref{fig:summary}A, B and C).
+The transition from biophysical control to social and institutional control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
 \cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
 With intensive anthropogenic intervention, the YRB may be the most prominent example in this general transition of water governance -``improving supply, transforming governance, and enhancing adaptation'' %!
-citation.
+Citation.
 The transition regimes identified here also echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
@@
 \cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
-Our analysis suggests that the early phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
-Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
+Our analysis suggests that the early phase of transition often leads to resource-focused challenges that result from economic and environmental change, while structural challenges dominate the later phases of governance in social and political aspects.
+Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
 \cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %!
+Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and maybe in urgent need of novel flexible, efficient sociopolitical governance structures %!
 Kitroeff citation wrong
 \cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
-It is typical that resource challenges and structural challenges occurred sequentially during the transition of water governance within the YRB.
-From the perspective of the core dimensions emphasized by the UNDP for water governance, therefore, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.
+Typically, resource and structural challenges occur sequentially during the transition of water governance within the YRB.
+From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins toward a hydrosocial water cycle.
 
@@
 % Implications
-Water governance gradually changes from being a primarily local concern to becoming a national or international concern, because large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
-As the ubiquitous tele-coupling are rising additional challenges of water governance in the tighter connected world, where transition between regimes aligns with different human-water relationships. 
-Within the growing hydro-social cycle, the IWGI index captures the increasment of the adaptive capacity and sketches the transitional regimes of water governance, in a relatively straightforward but comprehensive way.
-It is important for scientists and decision makers to recognize the changing governance challenges, because models, institutions, engineerings, and approaches developed under one regime are not necessarily useful under a different regime
+Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
+As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
+Within the growing hydro-social cycle, the IWGI index depicts the increase of the adaptive capacity and sketches the transitional water governance regimes in a relatively straightforward but comprehensive way.
+It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
 %! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
-In the case of the YRB, an important institutions of water quota in the governance tranforming regime became rigid during the enhanced adaptation phase.
-On contrary, additional water from the ambitious cross-basins water diversion project, which originated in the phase of massive supply can play an even more crucial role in today's enhancing adaptation phase.
-Overall, applications of IWGI can induce a straightforward understanding of the water governance in transition of hydrosocial cycle, as descriptions from some previous conceptual frameworks suggested for all large-scale basins worldwide.
+In the case of the YRB, an essential institution of water quota in the governance transforming regime became rigid during the enhanced adaptation phase.
+On the contrary, additional water from the ambitious cross-basins water diversion project, which originated in the phase of massive supply, can play an even more crucial role in today's enhancing adaptation phase.
+Overall, applications of IWGI can induce a straightforward understanding of the water governance in the transition of the hydrosocial cycle, as descriptions from some previous conceptual frameworks suggested for all large-scale basins worldwide.
 
 %! limitations
-One of the main limitations of applying IWGI in abundant data availability for a long-term period of time. 
-For an example, we used the stress-flexibility-variability (SFV index) here, one of the most comprehensive index to our knowledge, as an indicator of the water stress dimension. 
-With other indicators, therefore, we obtained various datasets in the YRB: water use in different regions and sectors, streamflows in different reaches, reservoir capacity and completion time, with further more information in social, economic, and institutional for interpretation.
+One of the main limitations of applying IWGI is abundant data availability for a long-term period.
+For example, we used the stress-flexibility-variability (SFV index) here, one of the most comprehensive indexes, as an indicator of the water stress dimension.
+With other indicators, therefore, we obtained various datasets in the YRB: water use in different regions and sectors, streamflows in different reaches, reservoir capacity and completion time, with furthermore information in social, economic, and institutional for interpretation.
 It means still a gap between the comprehensively identifying and widespread application of IWGI.
-However, we assumed that all solutions of water governance are relative to the question of ``who gets water, when and how'', so water stress, purposes of water services, and patterns of water allocation are matters.
+However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
 We suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes.
@@
 % direction
-For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
+For today's world, water-related challenges remain one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and maybe in opposition to improving governance
 \cite{xuAssessingprogresssustainable2020,liuAerosolweakenedsummermonsoons2017,greveGlobalassessmentwater2018}.
 % 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
-Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
+Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still approaching planetary boundaries where human-water systems may collapse
 \cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
@@
 % 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
-In the future, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
+In the future, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin-scale
 \cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
@@
 % 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
-A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
+A deeper understanding of governance that incorporates ideas of non-linear change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.

### 2022-04-26 paper/main/manuscript.tex
feat(introduction,-manuscript): change fig path correctly, add knowledge gap and defination of water governace
BREAKING CHANGE:
docs(manuscript): metadata pasted

@@
 
-\graphicspath{{/Users/songshgeo/Documents/VScode/water_governance_challenges/figures/}}
+\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
 \begin{document}
 
-\title[Article Title]{Article Title}
+\title[Article Title]{Identifying regime transitions for water governance at a basin scale}
 
@@
 
-\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}
+\abstract{In many large river basins, water governance for socio-economic development has led to a global transformation of water governance regimes from natural to social-ecological or ‘hydrosocial’ situations.
+Water governance decides who gets water, when, and how much.
+Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water.
+We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
+Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China), it describes how water governance shifts between three regimes (massive supply regime; purpose-focused regime; and many-sided governance regime, respectively) over half a century.
+Our application of the IWGI offers a way to link the shifts of water governance to environmental, economic social and political changes.
+As a potentially widespread transition schema for water governance regimes, the different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines on the coordinated governance of big river basins in general.}
 
-\keywords{keyword1, Keyword2, Keyword3, Keyword4}
+\keywords{
+    Regime shifts,
+    Water use,
+    Water governance,
+    Transformation,
+    Sustainability
+}
 

### 2022-04-26 paper/main/01_introduction.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

@@
 \label{Intro.}
-Water has been described as being ``at the centre of the planetary drama of the Anthropocene''
-\cite{gleesonIlluminatingwatercycle2020}.
-It is essential not only for earth system processes but also in supporting the economic development and continued well-being of human societies.
-Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, moving rivers dominated by a hybrid of social and natural tendencies
+Water, being ``at the centre of the planetary drama of the Anthropocene'' \cite{gleesonIlluminatingwatercycle2020}, is essential not only for earth system processes but also in supporting the economic development and human well-being.
+Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
 \cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
-Facing this major transformation, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
+Facing this transition, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
 \cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.
@@
 \cite{undpwatergovernancefacilityWaterGovernanceIssue}.
-Corresponding to ``who gets what, when and how'', the United Nations Development Programme (UNDP) suggests three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (supply), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
+Corresponding to ``who gets what, when and how'', the United Nations Development Programme (UNDP) suggests three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
 \cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
-As a locally stable state of a system, function, and dominant controls, habitual relationships between humans and water maintain regimes of water governance
+
+As a temporary stable state in structure, function, and dominant controls, a specific regime of water governance maintains by concreted intertwines within human-water systems (such as management, institutions, and exploitations)
 \cite{carpenterEarlyWarningsRegime2011}.
@@
 \cite{rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
-Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts can trigger changes in the three key dimensions of water governance (supply, purpose, and allocation), with new challenges to sustainability %!
+Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts align with changing three key dimensions of water governance (stress, purpose, and allocation), sometimes leading to new challenges in sustainability %!
 UNDP year
 \cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
-First, the supply of water depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
+First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
 \cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
@@
 \cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
-However, water over-use has led to depletions of the over-burdened river, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
+However, water over-use has led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
 \cite{xiaDevelopmentWaterAllocation2012}.
-Today, it is still impossible to completely cover water demands, balance trade-offs between ecosystem services, and lead to equities in different regions; -who gets water, when and how is still an open question for sustainable water governance
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is still an open question for sustainable water governance
 \cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
-The YRB has been among the most rapidly-changing large river basins worldwide, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors.
+However, confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, we first use the three key dimensions (supply, purpose and allocation) by corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
+Here, we use the three core dimensions (stress, purpose and allocation) and corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
 % 使用案例研究
@@
 % 最后总结出一般性框架
-Finally, we propose a general regime transition scheme as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
+Finally, we propose a general regime transition schema as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
 
 \begin{figure*}%[htbp]
+
 %! I don't know that fig.1 adds much, the explanatory text to the figure is the key.
 	\centering
-	\includegraphics[width=0.9\textwidth]{main/framework.jpg}
+	\includegraphics[width=0.9\textwidth]{main/framework.png}
 	\caption{
-		A framework for understanding the relationship between water governance regimes and transitions of a hydrosocial cycle. We aim to detect regime shifts using a simple and comprehensive index.
-		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
-		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see \textbf{Methods} for details).
-Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance.
-(2) ``purpose'' is weighted between consumptive services or non-consumptive uses.
-(3) ``allocation'' changes between balanced or lopsided.
-		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
-		\textbf{B:} along a trajectory of hydrosocial water cycle, governance changes are related to the combination of trends across the three dimensions.
-When abrupt change occurs, it may indicate a regime shift in water governance
-		\cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
+		A framework for identifying the water governance regimes and transitions of a hydrosocial cycle.
+		\textbf{A:} water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing: (1) ``stress'' of water shifts between scarcity and abundance; (2) ``purpose'' of water is weighted between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
+		\textbf{B:} along a transition of hydrosocial water cycle, water governance shifts in line with the three dimensions.
+By combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
+		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
 	}

### 2022-04-26 paper/main/02_methods.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

@@
 		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item \textbf{Supply($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
-However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
+		\item \textbf{Stress ($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
+However, since effective water governance may boost supply capacities to meet water demands through technical solutions in the process of development:
 		\begin{equation}
@@
 	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, A or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension.
+	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to stress, purpose, and allocation respectively) for each dimension.
 Then, the above equation was transformed into a natural logarithm to facilitate calculation:
@@
 
-	\subsubsection*{Indicator of supply}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityintensityglobal2019}.
+	\subsubsection*{Indicator of stress}
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a particular region $i$ \cite{qinFlexibilityintensityglobal2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
-For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
+For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
 	\begin{equation}

### 2022-04-26 paper/main/03_results.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

@@
 	\includegraphics[width=0.9\linewidth]{main/index.jpg}
-	\caption{Changes in the IWGI index.
-	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
-	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were the main positive contributors to P1, P2 and P3.
-	\textbf{C,} Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
-	The red indicator line in this plot denotes a 1:1 contribution between purpose (P) and allocation (A).
-When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.
+	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: 1965-1978, P2: 1979-2001, and P3: 2002-2013.
+	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
+	\textbf{B,} correlation of trends between the IWGI and the indicators.
+	\textbf{C,} across three indicators, changing components of the IWGI, whose directions shifts between different regimes.
 	}
@@
 In the first period (P1, 1965-1978), the IWGI decreased rapidly.
-While the indicator of purpose and allocation contributed more to the IWGI, the remarkable downward trend correlates significantly to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
+While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, spectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
 % 第二阶段
-In the second period (P2, 1979-2001), the increasing stress indicator significantly contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
+In the second period (P2, 1979-2001), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
 % 第三阶段
-During the third period (P3, 1995-2013), while the stress indicator kept its most significant share in contributions, the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
+During the third period (P3, 1995-2013), while the stress indicator kept its biggest share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
 
@@
 % 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).
+The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).
 
-\subsection{Causes of water governance regime shifts}
+\subsection{Causes of the regime shifts}
 \label{Res.2}
@@
 	\caption{
-		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
-		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the area, the green dot line), see \textit{SI Appendix} Methods S2).
-		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line) (\textit{SI Appendix} Methods S2).
-		\textbf{C.} Completed time of each new reservoir and their located region's (source, upper, middle, or lower reaches) water use percentages as a proportion of the basin's total water use (WU) at that time.
+		Causes of water governance regime shifts in the YRB: environmental change, economic growth and efficiency changes, social transformation, and governance policies.
+		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the area, the green dot line).
+		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line).
+		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time.
 Red circles denote the reservoirs mainly for managing and regulating the whole basin.
 		The size of each circle indicates the magnitude of its water storage capacity.
-Some important reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which was constructed mainly for managing floodwater discharge and water supply.
-The named reservoirs are significant for the entire basin, not only for regional development.
-		%! 不清楚D的这些圆圈代表啥
-		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2).
-In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Allocation Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
+Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing floodwater discharge and water regulation.
+These named reservoirs are significant for the whole basin rather than for local development.
+		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colors denote signed by different state institution, see \textit{SI Appendix} Table S2).
+The lightgray bars year-by-year show frequency of official documents related to the YRB at a basinal scale (see \textit{SI Appendix} Table S3).
 	}
@@
 % 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
-Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
+Underlying causes of changes in the IWGI associates to various factors, but different in dominates of the two regime shifts.
+The expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
+During the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
 S3).
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering P2, however, the expansion of irrigated area slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
+Entering the transformation governance regime (P2), however, the expansion of irrigated area slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
 
@@
 From P2 to P3, the efficiency of water use changed obviously.
-Not only irrigated areas keep their slow expansion in P3 (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
 However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
@@
 Finally, environmental context, social transformation and policies played roles in all three regimes.
-% 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
-% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1 (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, p<0.01), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig.
+Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, $p<0.01$), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig.
 S5).
-% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
-Since P2, the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, p<0.01 and \textit{SI Appendix} Fig.
+Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig.
 S6).
-% 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
-In P3, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
+In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
 The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-26 paper/main/04_discussion.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

@@
 	\caption{
-		Transition schema of water governance during transformation towards a hydrosocial water cycle.
-The natural water cycle dominates blue pathways while socio-economic feedback dominate red pathways.
-Finally, there is a transformation towards the hydrosocial water cycle where red loop increases.
+		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways while socio-economic feedback dominate red pathways.
 		\textbf{A.
-Early phase.} As socio-economic systems develop, industry and services gradually demand increasing amounts of water; at the same time, increasing social organization and technological capacity allow people to manage water resources more intensively, including intensive intervention in the natural water cycle.
+Early phase.} As socio-economic systems developing, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources for alleviating the water stress.
 		\textbf{B.
-Late phase} With further developed and economically efficient industries and services, trade-offs between provisioning-purpose and non-provisioning water use become prominent.
-Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
+Late phase} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; basin-wide socio-economic system requires to more organized water governance.
 		%! The note to C. makes no sense! from the refree 2.
 		Thus, \textbf{C.
-Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle.
-This is generally distinguished when it reaches water resource limits.
-The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
+the hydrosocial water cycle transition} correlates with the water governance regime shifts (in the YRB, they are identified as massive supply regime, transformation governance regime, and adaptation oriented regime).
+The transformation governance regime shift occurs following water deficit, with rapid growth of adaptive capacity.
 		\textbf{D.
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013).
+Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
 Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, deciding who gets water, when and how.
@@
 
-The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after ``opening and reform''.
+The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after the ``reform and opening-up''.
 % 正如理论预测的那样

### 2022-04-26 paper/main/manuscript.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

--- 2022-04-21 paper/main/manuscript.tex
@@
 
-\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}
+\abstract{
+    In many large river basins, transition of water governance regimes from natural to social-ecological or ‘hydrosocial’ situations profoundly changes who gets water, when, and how.
+Identifying changes of governance regimes is therefore critical to understanding the transition and guiding the efficient and sustainable use of water.
+We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
+Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China), it describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
+Our application of the IWGI offers a comprehensive and straightforward way to link the shifts of water governance to environmental, economic social and political factors.
+As a potentially widespread transition schema for water governance regimes, the different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines on the coordinated governance of big river basins in general.
+}
 
-\keywords{keyword1, Keyword2, Keyword3, Keyword4}
+\keywords{
+    Regime shifts,
+    Water governance,
+    Transformation,
+    Sustainability
+}
 

### 2022-04-26 paper/main/02_methods.tex
feat(method): update method

@@
-This analysis aimed to develop a transparent and easily replicable approach to identifying water governance regimes and regime shifts; thus, it is not intended to provide a comprehensive model of social-ecological water dynamics.
-First, we constructed the Integrated Water Governance Index (IWGI) based on three dimensions (Supply, Purpose, and Allocation, see Figure 1).
-Then, we identify the changes in the index's periods over time using change point detection.
-An independent indicator reflects each dimension after normalization, and water governance regimes were characterized by the combination of impacts along each dimension at different periods.
-Finally, we decomposed the contribution of each indicator to changes in the IWGI at each regime.
+This analysis aimed to develop a comprehensive and straightforward approach to identifying water governance regimes.
+First, we constructed the Integrated Water Governance Index (IWGI) based on three dimensions (Stress, Purpose, and Allocation, see Figure~\ref{fig:framework}).
+Then, we analyzed the changes in the IWGI from 1965 to 2013 by using change point detection methods.
+The normalized indicator for each dimension effects the IWGI by both changing trend and contributions.
 
@@
 
-Our Integrated Water Governance Index offers an accessible and operational way of measuring regime changes based on the transparent underlying assumptions that water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure 1 and SI 322 Appendix Methods S4 for details)
-\cite{abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020,steffenTrajectoriesEarthSystem2018}.
-
-	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
-	\begin{itemize}
-		%! Why ??? Explaination: why should development lead to balance among regions or meet the needs of different sectors.
-		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
-		\item \textbf{Stress ($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
-However, since effective water governance may boost supply capacities to meet water demands through technical solutions in the process of development:
-		\begin{equation}
-			Transformation \propto S^{-1}
-		\end{equation}
-
-		\item \textbf{Purpose($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
-		\begin{equation}
-			Transformation \propto P
-		\end{equation}
-
-		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
-		\item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
-		\begin{equation}
-			Transformation \propto A
-		\end{equation}
-
-	\end{itemize}
-
 	% 将三者合一起，即：
-	We combined these three dimensions into a single integrated index, keeping their positive or negative relationship with the transformation towards a hydrosocial water cycle:
+	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three core dimensions (Stress, Purpose, and Allocation) of water governance.
+Each dimension keeps two directions and we assumed the hydrosocial cycle aligns with one of them, respectively:
 	\begin{equation}
@@
 
-	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, A or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
-	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to stress, purpose, and allocation respectively) for each dimension.
+	To effectively quantify the dimensions, we selected an indicator ($I_x$, $x=S$, $P$ or $A$, corresponding to stress, purpose, and allocation respectively) for each dimension.
 Then, the above equation was transformed into a natural logarithm to facilitate calculation:
@@
 
-	Assuming they have equal weights, the Integrated Water Governance Index (IWGI) is:
+	Then, the Integrated Water Governance Index (IWGI) is average of the normalized indicators $I'_x$:
 	\begin{equation}
@@
 
-	where $I'_x$ is a normalization of log-transformed indicator $I_x$ for a certain dimension:
+	where:
 	\begin{equation}
-		I'_x = normalize(ln(I_x))
-	\end{equation}
-
-	\subsubsection*{Normalization}
-	We tested different normalization methods, and they made no difference in change points detection (see \textit{SI Appendix} Methods S5.
-Sensitivity analysis).
-We performed min-max normalization using the formulation below:
-	\begin{equation}
-		normalize(X) = (X - X_{min}) / (X_{max} - X_{min})
+		I'_x = (I_x - I_{x, min}) / (I_{x, max} - I_{x, min})
 	\end{equation}
@@
 	\begin{equation}
-		NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}}
-	\end{equation}
-
-	Where $i$ refers a certain region, or the whole basin, i.e:
-	\begin{equation}
-		I_P = NPS_{basin}
+		NPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
 	\end{equation}
@@
 	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
-	To describe allocations $I_A$, we designed an indicator based on information entropy, called Allocation Entropy Metric (AEM), AEM measures the degree of evenness of water allocation (see \textit{SI Appendix} Methods S4).
-	Our indicator $I_A$ was intended to reflect the idea that with the development of society, water resources allocation becomes more balanced among regions and generally meets the needs of different sectors, but different regions have a trend of division of labour among various sectors (with larger gaps):
+	To describe allocations $I_A$, we designed an indicator based on entropy, called Allocation Entropy Metric (AEM), which measures the degree of evenness in water allocation:
+
 	\begin{equation}
-		I_A = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}
+		I_A = CEM = \sum_{i=1}^N -log(p_{i}) * p_{i}
 	\end{equation}
 
-	where $AEM_{r}$ and $AEM_{s}$ are Allocation Entropy Metric in different regions and different sectors.
-$AEM_{rs}$ describes differences between sectors in a certain region relative to the whole basin (see \textit{SI Appendix} Methods S4).
+	where $p_{i}$ is the water proportion of region $i$ to the whole basin ($N$ regions in sum).
+The YRB is divided into 4 regions (i.e., $N = 4$) according to the natural and socio-economic backgrounds (see \textit{SI Appendix XX}).
 
@@
 
-	% 计算贡献度
-	\subsection{Contribution decomposition}
-		We decomposed the amount of variation in each index at different periods to quantify each influence's contribution to the index.
+	% % 计算贡献度
+	% \subsection{Contribution decomposition}
+	% 	We decomposed the amount of variation in each index at different periods to quantify each influence's contribution to the index.
 Using the Integrated Water Governance Index (IWGI) as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_A$).
 We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
-		\begin{align}
-		\Delta IWGI &= (I'_{P_{y_2}} + I'_{A_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{A_{y_1}} - I'_{S_{y_1}}) \\
-		&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{A_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
-		&= \Delta I'_P + \Delta I'_A + (-\Delta I'_S)
-		\end{align}
-		Then, the contribution of dimension $x$ to IWGI's changes can be referred to as:
-		\begin{equation}
-			Contribution_x = \frac{\Delta I'_x}{\lvert \Delta IWGI \rvert}
-		\end{equation}
+	% 	\begin{align}
+	% 	\Delta IWGI &= (I'_{P_{y_2}} + I'_{A_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{A_{y_1}} - I'_{S_{y_1}}) \\
+	% 	&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{A_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
+	% 	&= \Delta I'_P + \Delta I'_A + (-\Delta I'_S)
+	% 	\end{align}
+	% 	Then, the contribution of dimension $x$ to IWGI's changes can be referred to as:
+	% 	\begin{equation}
+	% 		Contribution_x = \frac{\Delta I'_x}{\lvert \Delta IWGI \rvert}
+	% 	\end{equation}
 

### 2022-04-26 paper/sup/supplementary_information.tex
feat(method): update method

@@
 \section*{Methods S4. Indicators of IWGI}
+
+Our Integrated Water Governance Index offers an accessible and operational way of measuring regime changes based on the transparent underlying assumptions that water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure 1 and SI 322 Appendix Methods S4 for details)
+\cite{abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020,steffenTrajectoriesEarthSystem2018}.
+
+% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
+\begin{itemize}
+    %! Why ??? Explaination: why should development lead to balance among regions or meet the needs of different sectors.
+    % - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
+    \item \textbf{Stress ($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals.
+However, since effective water governance may boost supply capacities to meet water demands through technical solutions in the process of development:
+    \begin{equation}
+        Transformation \propto S^{-1}
+    \end{equation}
+
+    \item \textbf{Purpose($P$)}: Transformation is usually accompanied by a change of purpose in water governance towards socio-economic services (usually towards non-provisioning purposes), because of higher returns:
+    \begin{equation}
+        Transformation \propto P
+    \end{equation}
+
+    % - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
+    \item \textbf{Allocation($A$)}: Transformation usually leads to more complicated structures in water allocation, as a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
+    \begin{equation}
+        Transformation \propto A
+    \end{equation}
+
+\end{itemize}
+
 % 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。

### 2022-04-27 paper/main/01_introduction.tex
fix(no-conclusion): add conclusion, check grammarly

@@
 \begin{figure*}%[htbp]
-
-%! I don't know that fig.1 adds much, the explanatory text to the figure is the key.
 	\centering
@@
 		A framework for identifying the water governance regimes and transitions of a hydrosocial cycle.
-		\textbf{A:} water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing: (1) ``stress'' of water shifts between scarcity and abundance; (2) ``purpose'' of water is weighted between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
-		\textbf{B:} along a transition of hydrosocial water cycle, water governance shifts in line with the three dimensions.
-By combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
+		\textbf{A:} water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing.
+(1) ``stress'' of water shifts between scarcity and abundance; (2) weighting ``purpose'' of water between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
+		\textbf{B:} along with a transition of hydrosocial water cycle, water governance shifts in line with the three dimensions.
+Combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
 		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.

### 2022-04-27 paper/main/02_methods.tex
fix(no-conclusion): add conclusion, check grammarly

@@
-This analysis aimed to develop a comprehensive and straightforward approach to identifying water governance regimes.
+To develop a comprehensive and straightforward approach to identifying water governance regimes.
 First, we constructed the Integrated Water Governance Index (IWGI) based on three dimensions (Stress, Purpose, and Allocation, see Figure~\ref{fig:framework}).
-Then, we analyzed the changes in the IWGI from 1965 to 2013 by using change point detection methods.
-The normalized indicator for each dimension effects the IWGI by both changing trend and contributions.
+Then, we analyzed the changes in the IWGI from 1965 to 2013 using change point detection methods.
+The normalized Indicator for each dimension affects the IWGI by changing trends and contributions.
 
@@
 	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three core dimensions (Stress, Purpose, and Allocation) of water governance.
-Each dimension keeps two directions and we assumed the hydrosocial cycle aligns with one of them, respectively:
+Each dimension keeps two directions, and we assumed the hydrosocial cycle aligns with one of them, respectively:
 	\begin{equation}
@@
 
-	To effectively quantify the dimensions, we selected an indicator ($I_x$, $x=S$, $P$ or $A$, corresponding to stress, purpose, and allocation respectively) for each dimension.
+	We selected an indicator ($I_x$, $x=S$, $P$ or $A$, corresponding to stress, purpose, and allocation, respectively) to quantify the dimensions effectively.
 Then, the above equation was transformed into a natural logarithm to facilitate calculation:
@@
 
-	Then, the Integrated Water Governance Index (IWGI) is average of the normalized indicators $I'_x$:
+	Then, the Integrated Water Governance Index (IWGI) is the average of the normalized indicators $I'_x$:
 	\begin{equation}
@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a particular region $i$ \cite{qinFlexibilityintensityglobal2019}.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the Indicator in a particular region $i$ \cite{qinFlexibilityintensityglobal2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
@@
 	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
+While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
 We calculated the NPS as:
@@
 
-		With no assumptions about the distribution of the data, the Pettitt (1979) approach of change-point detection is commonly applied to detect a single change-point in hydrological time series with continuous data
+		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
         \cite{pettittNonParametricApproachChangePoint1979}.
-		It tests $H0$: The variables follow one or more distributions that have the same location parameter (no change), against the alternative: a change point exists.
-The non-parametric statistic is defined as:
-
+		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
 		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
@@
 
-		We used $\alpha = 0.001$ as the threshold level of p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
-		Since this method can only return one significant change point, we divided the series into two at that point and analyzed seach series separately, until all significant change points were detected.
+		We used $\alpha = 0.001$ as the threshold level of the p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
+		Since this method can only return one significant change point, we divided the series into two at that point and analyzed each series separately until all significant change points were detected.
 

### 2022-04-27 paper/main/03_results.tex
fix(no-conclusion): add conclusion, check grammarly

@@
 In the first period (P1, 1965-1978), the IWGI decreased rapidly.
-While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, spectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
+While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
 % 第二阶段
@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing floodwater discharge and water regulation.
-These named reservoirs are significant for the whole basin rather than for local development.
-		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colors denote signed by different state institution, see \textit{SI Appendix} Table S2).
-The lightgray bars year-by-year show frequency of official documents related to the YRB at a basinal scale (see \textit{SI Appendix} Table S3).
+Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which was constructed mainly for managing floodwater discharge and water regulation.
+These named reservoirs are significant for the whole basin rather than local development.
+		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{SI Appendix} Table S2).
+The light grey bars year-by-year show the frequency of official documents related to the YRB at a basinal scale (see \textit{SI Appendix} Table S3).
 	}
@@
 % 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
-Underlying causes of changes in the IWGI associates to various factors, but different in dominates of the two regime shifts.
+The underlying causes of changes in the IWGI are associated with various factors but are different in the two regime shifts.
 The expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
@@
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering the transformation governance regime (P2), however, the expansion of irrigated area slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
+Entering the transformation governance regime (P2), however, the expansion of irrigated areas slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
 

### 2022-04-27 paper/main/04_discussion.tex
fix(no-conclusion): add conclusion, check grammarly

@@
 	\caption{
-		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways while socio-economic feedback dominate red pathways.
+		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red pathways.
 		\textbf{A.
-Early phase.} As socio-economic systems developing, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources for alleviating the water stress.
+Early phase.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate the water stress.
 		\textbf{B.
-Late phase} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; basin-wide socio-economic system requires to more organized water governance.
-		%! The note to C. makes no sense! from the refree 2.
+Late phase} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
 		Thus, \textbf{C.
-the hydrosocial water cycle transition} correlates with the water governance regime shifts (in the YRB, they are identified as massive supply regime, transformation governance regime, and adaptation oriented regime).
-The transformation governance regime shift occurs following water deficit, with rapid growth of adaptive capacity.
+the hydrosocial water cycle transition} correlates with the water governance regime shifts (in the YRB, they are massive supply regime, transformation governance regime, and adaptation oriented regime).
+The transformation governance regime shift occurs following the water deficit, with the rapid growth of adaptive capacity.
 		\textbf{D.

### 2022-04-27 paper/main/05_conclusion.tex
fix(no-conclusion): add conclusion, check grammarly

Three dimensions of water governance changes along with the hydrosocial cycle transition: water stress, services purpose, and water allocation, affecting ``who gets water, when and how''. By integrating them, we developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance. Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively). Our approach quantitatively identifies the genearl schema for water governance regimes in the YRB, in line with previous theoretical analysis with a representative transition process. Linking regime shifts to the underlying causes, the implementation of IWGI offers a comprehensive and straightforward way to interpret changes in intertwines of water governance, hydrosocial transition, and human-water relationships.

### 2022-04-27 paper/main/manuscript.tex
fix(no-conclusion): add conclusion, check grammarly

--- 2022-04-21 paper/main/manuscript.tex
@@
 
-\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}
+\abstract{
+    In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
+Therefore, identifying changes in governance regimes is critical to understanding the transition and guiding the efficient and sustainable use of water.
+We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
+Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
+Our application of the IWGI offers a comprehensive and straightforward way to link the shifts in water governance to environmental, economic, social and political factors.
+Moreover, as a potentially widespread transition schema for water governance regimes, the different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially helpful guidelines on the governance of big river basins in general.
+}
 
-\keywords{keyword1, Keyword2, Keyword3, Keyword4}
+\keywords{
+    Regime shifts,
+    Water governance,
+    Transformation,
+    Sustainability
+}
 
@@
 \section{Conclusion}\label{sec13}
-% \input{05_conclusion}
+\input{05_conclusion}
 

### 2022-04-28 paper/main/01_introduction.tex
fix(introducion,-conclusion,-meta): refactor introduction
according to ShuaiWang and XutongWu comments

@@
 
-Governance is essentially about ``who gets what, when and how''.
-Specifically, water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %!
-citation.
-For water resources in populated areas, missing governance means missing sustainability, and a first important step in understanding transitions toward successful water governance is identifying the different regimes.
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
+For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes.
 \cite{undpwatergovernancefacilityWaterGovernanceIssue}.
-Corresponding to ``who gets what, when and how'', the United Nations Development Programme (UNDP) suggests three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
+Regime of water governance maintains by concreted intertwines within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
+\cite{carpenterEarlyWarningsRegime2011,rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
+Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts sometimes leading to new challenges in water governance.
+The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).
 
-As a temporary stable state in structure, function, and dominant controls, a specific regime of water governance maintains by concreted intertwines within human-water systems (such as management, institutions, and exploitations)
-\cite{carpenterEarlyWarningsRegime2011}.
-However, large and persistent changes in key properties may lead to a loss of systematical stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
-\cite{rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
-Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts align with changing three key dimensions of water governance (stress, purpose, and allocation), sometimes leading to new challenges in sustainability %!
-UNDP year
-\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
+Governance is essentially about ``who gets what, when and how'', the United Nations Development Programme (UNDP) thus suggested three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
+\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. %! UNDP year
 First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
@@
 \cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
-Third, the allocation of water across the whole basin is influenced not only by regionally socio-economic and environmental context but also by systematically regulating resources
+Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
 \cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
 Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.
-The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).
 
-As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details), the fifth-largest river in the world.
-With drastically anthropogenic intervention, the YRB experienced the most intense water governance challenges in China, leading to long-standing sustainability barriers.
-Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
+The Yellow River Basin (YRB), fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
+Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled for thousands years of high sediment loads
 \cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
-However, water over-use has led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
+However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
 \cite{xiaDevelopmentWaterAllocation2012}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is still an open question for sustainable water governance
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is always an open question for sustainable development
 \cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
-However, confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
+Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

### 2022-04-28 paper/main/05_conclusion.tex
fix(introducion,-conclusion,-meta): refactor introduction
according to ShuaiWang and XutongWu comments

@@
-Three dimensions of water governance changes along with the hydrosocial cycle transition: water stress, services purpose, and water allocation, affecting ``who gets water, when and how''.
-By integrating them, we developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance.
+Three dimensions of water governance change along with the hydrosocial cycle transition: water stress, services purpose, and water allocation, affecting ``who gets water, when and how''.
+We developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance by integrating them.
 Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
-Our approach quantitatively identifies the genearl schema for water governance regimes in the YRB, in line with previous theoretical analysis with a representative transition process.
+Our approach quantitatively identifies the general schema for water governance regimes in the YRB, in line with previous theoretical analysis with a representative transition process.
 Linking regime shifts to the underlying causes, the implementation of IWGI offers a comprehensive and straightforward way to interpret changes in intertwines of water governance, hydrosocial transition, and human-water relationships.

### 2022-04-28 paper/main/manuscript.tex
fix(introducion,-conclusion,-meta): refactor introduction
according to ShuaiWang and XutongWu comments

@@
     In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
-Therefore, identifying changes in governance regimes is critical to understanding the transition and guiding the efficient and sustainable use of water.
-We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale.
-Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
-Our application of the IWGI offers a comprehensive and straightforward way to link the shifts in water governance to environmental, economic, social and political factors.
-Moreover, as a potentially widespread transition schema for water governance regimes, the different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially helpful guidelines on the governance of big river basins in general.
+    Identifying changes in governance regimes is critical to understanding the transition and guiding the efficient and sustainable use of water.
+    We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) to detect regime shifts in water governance at a basin scale.
+    Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century.
+(massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
+    In the YRB, the regime shifts' underlying causes are increasing water supply and demand through the construction of reservoirs and expansion of irrigated areas before the governance transformation, while are re-allocation and regulation after the transformation.
+    Our application of the IWGI offers a comprehensive and straightforward way to link the water governance regimes to the hydrosocial transition, following challenges in sustainability.
 }
@@
     Transformation,
+    Social-hydrology,
     Sustainability

### 2022-04-28 paper/main/01_introduction.tex
fix(result): shorter, focus, and explaination

@@
 % 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance and their leading causes in a comprehensive but straightforward way.
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance in a comprehensive but straightforward way.
+Following synthetic analyses of the changes in water demand, water supply, economic outcomes, and institutions, we interpret the leading causes of the regime shifts.
 % 最后总结出一般性框架

### 2022-04-28 paper/main/03_results.tex
fix(result): shorter, focus, and explaination

@@
 During the third period (P3, 1995-2013), while the stress indicator kept its biggest share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
-
-% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
-The ternary shows overall features of the three dimensions in different periods, where each regime shift is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
-% 第一阶段到第二阶段
-Throughout P1, the IWGI shifts paralleled the left axis because the Purpose indicator barely changed, and the other two changed in similar trends.
-Analogously, as the stress indicator is unchanged during the P3, the IWGI shifts paralleled with the right side of the axis while the other two changed in opposite trends.
-% 第三阶段集中
-The regime then experienced a long-distance shift during the P2, as three indicators simultaneously changed their contribution ratios to IWGI.
-% 总结来说，三个稳态
-The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).
+% Overall
+Taken together, the overall features of the three dimensions in different periods is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
+The results suggest three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).
 
@@
 
-% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
+% 进一步挖掘IWGI变化的根本原因，
 The underlying causes of changes in the IWGI are associated with various factors but are different in the two regime shifts.
-The expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
+% 灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
+Changing water demands and supply were critical to the shift between P1 and P2.
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-During the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig.
+As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the constructions of reservoirs (\textit{SI Appendix} Fig.
 S3).
@@
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Finally, environmental context, social transformation and policies played roles in all three regimes.
+Environmental context, social transformation and policies played roles in all three regimes.
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
@@
 S5).
-Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig.
+Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig.
 S6).

### 2022-04-28 paper/main/01_introduction.tex
docs(discussion): refactor and grammarly check

--- 2022-04-28 paper/main/01_introduction.tex
@@
 \cite{undpwatergovernancefacilityWaterGovernanceIssue}.
-Regime of water governance maintains by concreted intertwines within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
+Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
 \cite{carpenterEarlyWarningsRegime2011,rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
-Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts sometimes leading to new challenges in water governance.
+Therefore, regime shifts sometimes lead to new water governance challenges as both signals and consequences of substantive changes in human-water systems.
 The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).
 
-Governance is essentially about ``who gets what, when and how'', the United Nations Development Programme (UNDP) thus suggested three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
+Governance is essentially about ``who gets what, when and how''.
+The United Nations Development Programme (UNDP) thus suggested that three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How does water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
 \cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. %! UNDP year
@@
 
-The Yellow River Basin (YRB), fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
-Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled for thousands years of high sediment loads
+The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
+Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled by thousands of years of high sediment loads
 \cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
@@
 % 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance and their leading causes in a comprehensive but straightforward way.
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated water governance regimes in a comprehensive but straightforward way.
+Following synthetic analyses of the changes in water demand, supply, economic outcomes, and institutions, we interpret the leading causes of the regime shifts.
 % 最后总结出一般性框架
@@
 	\caption{
-		A framework for identifying the water governance regimes and transitions of a hydrosocial cycle.
-		\textbf{A:} water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing.
+		Identifying the water governance regimes in transitions of a hydrosocial cycle.
+		\textbf{A.} Water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing.
 (1) ``stress'' of water shifts between scarcity and abundance; (2) weighting ``purpose'' of water between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
-		\textbf{B:} along with a transition of hydrosocial water cycle, water governance shifts in line with the three dimensions.
+		\textbf{B.} Along with a transition in hydrosocial water cycle, water governance shifts in line with the three dimensions.
 Combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.

### 2022-04-28 paper/main/03_results.tex
docs(discussion): refactor and grammarly check

@@
 % 第三阶段
-During the third period (P3, 1995-2013), while the stress indicator kept its biggest share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
+During the third period (P3, 1995-2013), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
 % Overall
-Taken together, the overall features of the three dimensions in different periods is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
+Taken together, the overall features of the three dimensions in different periods are relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
 The results suggest three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).
@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the constructions of reservoirs (\textit{SI Appendix} Fig.
+As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{SI Appendix} Fig.
 S3).
@@
 S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).
+As a result, the differences between sectors of water use reduced while the total water stress remained stable during the adaptation oriented regime (\textit{SI Appendix} Fig. S3).
 
@@
 S6).
-In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
+In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
 The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-28 paper/main/04_discussion.tex
docs(discussion): refactor and grammarly check

@@
 
+% Implications
+Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
+As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
+The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition.
+It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
+%* \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
+
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
-Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, deciding who gets water, when and how.
-The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
-However, the IWGI quantitatively identifies and reveals that abstract pattern, thus characterizing the transition of water governance in detail for the first time.
-It is important to note that each indicator or cause changes gradually, but emerging regime shifts move water governance along with the hydrosocial water cycle at a basin scale.
-As a result, the water governance challenges were primarily economic and environmental at the beginning of the trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).
-
-% 在水资源压力较低的大规模供应制度(长江流域1965-1978年)期间，水治理实践倾向于通过建设水库和渠道来增加服务用水(当时主要是供应目的——牲畜和农作物)。
+In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
 During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
-% 然而，正如“人类将征服自然”的流行口号所暗示的那样，水供应的增加很少考虑到人水关系不可逆转的变化，从而也急剧增加了水的需求，很少考虑到流域的保护。
-As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation.
+As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation
 \cite{zhouDecelerationChinahuman2020}.
-% 在那十年里，灌溉农田和引水设施的迅速扩张，使负担过重的长江水利枢纽接近临界点，在这个临界点上，持续增加供应来满足无限的需求是不现实的
 The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical
-% 结果，自1972年以来，超过80%的地表水使用量导致了河流的频繁枯竭，随之而来的是生态问题，如湿地的萎缩和生物多样性的下降。
 As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity.
-% 此外，由于处于上升阶段的工业经济也受到水资源压力的限制，现有的水治理模式严重导致了巨大的社会-生态危机和对可持续性的重大挑战
 In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
@@
 
-Finally, it came into an adaptation-oriented regime (P3: 2002-2013), when drastically shifting in societies occurred with stable water stress.
+When it came to an adaptation-oriented regime (P3: 2002-2013), drastically shifting in societies adapted to the stable high water stress.
 Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
@@
 Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example.
-% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
 Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
@@
 
-% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
-In general, the shift between the governance regimes advances in parallel with the trajectory of the hydrosocial cycle (Figure~\ref{fig:summary}A, B and C).
-The transition from biophysical control to social and institutional control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
+% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
+In general, water governance of the YRB is among the most prominent example in the general transition of hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
+With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
+In the analogy at a global scale, the resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
+\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
+Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %* Kitroeff citation wrong
+\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
+Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
+
+%* limitations & direction
+One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
+However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
+We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically
+\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
+In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
 \cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
-With intensive anthropogenic intervention, the YRB may be the most prominent example in this general transition of water governance -``improving supply, transforming governance, and enhancing adaptation'' %!
-Citation.
-The transition regimes identified here also echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig.
-S9)
-\cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
-Our analysis suggests that the early phase of transition often leads to resource-focused challenges that result from economic and environmental change, while structural challenges dominate the later phases of governance in social and political aspects.
-Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
-\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and maybe in urgent need of novel flexible, efficient sociopolitical governance structures %!
-Kitroeff citation wrong
-\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
-Typically, resource and structural challenges occur sequentially during the transition of water governance within the YRB.
-From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins toward a hydrosocial water cycle.
-
-\subsection{Implications, limitations, and future directions}
-\label{Outlook}
-
-% Implications
-Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
-As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
-Within the growing hydro-social cycle, the IWGI index depicts the increase of the adaptive capacity and sketches the transitional water governance regimes in a relatively straightforward but comprehensive way.
-It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
-%! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
-In the case of the YRB, an essential institution of water quota in the governance transforming regime became rigid during the enhanced adaptation phase.
-On the contrary, additional water from the ambitious cross-basins water diversion project, which originated in the phase of massive supply, can play an even more crucial role in today's enhancing adaptation phase.
-Overall, applications of IWGI can induce a straightforward understanding of the water governance in the transition of the hydrosocial cycle, as descriptions from some previous conceptual frameworks suggested for all large-scale basins worldwide.
-
-%! limitations
-One of the main limitations of applying IWGI is abundant data availability for a long-term period.
-For example, we used the stress-flexibility-variability (SFV index) here, one of the most comprehensive indexes, as an indicator of the water stress dimension.
-With other indicators, therefore, we obtained various datasets in the YRB: water use in different regions and sectors, streamflows in different reaches, reservoir capacity and completion time, with furthermore information in social, economic, and institutional for interpretation.
-It means still a gap between the comprehensively identifying and widespread application of IWGI.
-However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
-We suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes.
-
-% direction
-For today's world, water-related challenges remain one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and maybe in opposition to improving governance
-\cite{xuAssessingprogresssustainable2020,liuAerosolweakenedsummermonsoons2017,greveGlobalassessmentwater2018}.
-% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
-Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still approaching planetary boundaries where human-water systems may collapse
+Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
 \cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
-% 我们的分析展示了这种路径的前方很可能是严峻的水治理挑战。
-% 总的来说，这种明显的治理失败可能有两个主要原因。
-% Overall, there are probably two main reasons for this apparent failure of governance.
-% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
-% First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
-\cite{graftonparadoxirrigationefficiency2018}.
-% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
-In the future, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin-scale
-\cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
-% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
-From these perspectives, we need more flexible and comprehensive strategies to address governance challenges because the core problems are dynamic and complex
-\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
-% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
-A deeper understanding of governance that incorporates ideas of non-linear change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
+A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.

### 2022-04-28 paper/main/01_introduction.tex
docs(introduction): openning sentence, compile authors info

@@
 \label{Intro.}
-Water, being ``at the centre of the planetary drama of the Anthropocene'' \cite{gleesonIlluminatingwatercycle2020}, is essential not only for earth system processes but also in supporting the economic development and human well-being.
+Water, being ``at the centre of the planetary drama of the Anthropocene'' \cite{gleesonIlluminatingwatercycle2020}, is essential not only for earth system processes but also in supporting development and human well-being.
+As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
+\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.
 Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
@@
 \cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.
-As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
-\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.
 
@@
 
-\begin{figure*}%[htbp]
+\begin{figure*}[!ht]
 	\centering

### 2022-04-28 paper/main/04_discussion.tex
docs(introduction): openning sentence, compile authors info

@@
 		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red pathways.
-		\textbf{A.
-Early phase.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate the water stress.
-		\textbf{B.
-Late phase} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
+		\textbf{A.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate the water stress.
+		\textbf{B.} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
 		Thus, \textbf{C.
@@
 The transformation governance regime shift occurs following the water deficit, with the rapid growth of adaptive capacity.
-		\textbf{D.
-Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
+		\textbf{D. Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges but social and policy challenges later.
 	}

### 2022-04-28 paper/main/manuscript.tex
docs(introduction): openning sentence, compile authors info

@@
 
-\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}
+\author[1,2]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
 
-\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
-\equalcont{These authors contributed equally to this work.}
+\author[1,2]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
+% \equalcont{These authors contributed equally to this work.}
 
-\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
-\equalcont{These authors contributed equally to this work.}
+\author[1,2]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
+% \equalcont{These authors contributed equally to this work.}
+\author[3]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
+\author[4]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
+\author*[1,2]{\fnm{Bojie} \sur{Fu}}\email{fubj@bnu.edu.cn}
 
-\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}
+\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\street{Xinjiekouwai Street}, \city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 
-\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}
+\affil[2]{\orgdiv{nstitute of Land Surface System and Sustainability}, \orgname{Beijing Normal University}, \orgaddress{\street{Xinjiekouwai Street}, \city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 
-\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}
+\affil[3]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
+
+\affil[4]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
 
@@
 
-\bibliographystyle{sn-basic}
+\bibliographystyle{sn-standardnature}
 \bibliography{mybib}% common bib file

### 2022-04-28 paper/main/01_introduction.tex
feat(references): update all references
BREAKING CHANGE:

@@
 \label{Intro.}
-Water, being ``at the centre of the planetary drama of the Anthropocene'' \cite{gleesonIlluminatingwatercycle2020}, is essential not only for earth system processes but also in supporting development and human well-being.
-As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
-\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.
+Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting the development and human well-being
+\cite{gleeson2020a,gleeson2020b}.
+As an integral part of earth system governance, water governance requires a deep understanding of changes in the complex relationships between humans and water
+\cite{ahlstrom2021,biermann2012,steffen2020}.
 Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
-\cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
+\cite{sivapalan2012,qin2014,abbott2019}.
 Facing this transition, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
-\cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.
+\cite{best2019,dibaldassarre2019}.
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
-For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes.
-\cite{undpwatergovernancefacilityWaterGovernanceIssue}.
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}.
+For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes \cite{kjellen2015, grafton2013}.
 Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
-\cite{carpenterEarlyWarningsRegime2011,rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
+\cite{falkenmark2021,bressers2013,loch2020}.
 Therefore, regime shifts sometimes lead to new water governance challenges as both signals and consequences of substantive changes in human-water systems.
@@
 
-Governance is essentially about ``who gets what, when and how''.
+Governance is essentially about ``who gets what, when and how''\cite{lasswell2018}.
 The United Nations Development Programme (UNDP) thus suggested that three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How does water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. %! UNDP year
+\cite{undpwatergovernancefacility2016}.
 First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
+\cite{qin2019,wada2014,huang2021}.
 Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
-\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
+\cite{liu2017,florke2018,jaeger2019}.
 Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
-\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
+\cite{schmandt2021,speed2013}.
 Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.
 
-The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
+The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability
+\cite{mostern2021}.
 Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled by thousands of years of high sediment loads
-\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
+\cite{wang2016e,song2020a}.
 However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
-\cite{xiaDevelopmentWaterAllocation2012}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is always an open question for sustainable development
-\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
-Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
+\cite{wang2019c}.
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how'' is always an open question for sustainable development
+\cite{wohlfart2016a}.
+Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide \cite{nickum2021}.
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

### 2022-04-28 paper/main/02_methods.tex
feat(references): update all references
BREAKING CHANGE:

@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the Indicator in a particular region $i$ \cite{qinFlexibilityintensityglobal2019}.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the Indicator in a particular region $i$ \cite{qin2019}.
 This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
@@
 		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
-        \cite{pettittNonParametricApproachChangePoint1979}.
+        \cite{pettitt1979}.
 		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.

### 2022-04-28 paper/main/04_discussion.tex
feat(references): update all references
BREAKING CHANGE:

@@
 % Implications
-Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
-As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
-The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition.
-It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
-%* \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
+Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being \cite{best2019, best2020}.
+As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships \cite{diaz2019}.
+The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
+It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime \cite{reyers2018}.
 
@@
 As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation
-\cite{zhouDecelerationChinahuman2020}.
-The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical
-As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity.
+\cite{zhou2020}.
+The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical \cite{loch2020}.
+As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity \cite{wang2019c}.
 In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
-\cite{wohlfartRiverBasinCourse2016}.
+\cite{wohlfart2016a}.
 
@@
 % 正如理论预测的那样
-The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity %!
-Citation.
+The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity \cite{loch2020}.
 % 作为制度转变的先行者
 Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
-\cite{wangThirtyYearsYellow2018}.
+\cite{wang2019a,long2020,nickum2021}.
 % 因此，1999年黄河的最后一次枯竭
-Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance.
+Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance \cite{wang2019a}.
 
@@
 Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
-\cite{dalinBalancingwaterresource2015}.
-Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example.
+\cite{dalin2015,song2022}.
+Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example \cite{wang2019a}.
 Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
-\cite{konarExpandingScopeFoundation2019}.
+\cite{konar2019}.
 
@@
 In general, water governance of the YRB is among the most prominent example in the general transition of hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
+With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
 In the analogy at a global scale, the resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
-\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
+\cite{allan2019,speed2013,liu2012a}.
 Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %* Kitroeff citation wrong
-\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
+\cite{unep-dhi2016,mirumachi2015}.
 Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
@@
 However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
-We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically
-\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
+We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
 In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
-\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
+\cite{cumming2018,cumming2014,jaeger2019}.
 Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
-\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
-A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
+\cite{gleeson2020, wang-erlandsson2022}.
+A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability
+\cite{falkenmark2019}.

### 2022-04-28 paper/main/manuscript.tex
feat(references): update all references
BREAKING CHANGE:

@@
 % \documentclass[default]{sn-jnl}% Default
-\documentclass[default,iicol]{sn-jnl}% Default with double column layout
+\documentclass[default,iicol,lineno]{sn-jnl}% Default with double column layout
 
@@
     In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
-    Identifying changes in governance regimes is critical to understanding the transition and guiding the efficient and sustainable use of water.
-    We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) to detect regime shifts in water governance at a basin scale.
-    Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century.
-(massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
-    In the YRB, the regime shifts' underlying causes are increasing water supply and demand through the construction of reservoirs and expansion of irrigated areas before the governance transformation, while are re-allocation and regulation after the transformation.
-    Our application of the IWGI offers a comprehensive and straightforward way to link the water governance regimes to the hydrosocial transition, following challenges in sustainability.
+    Identifying regime changes is critical to understanding the transition and guiding sustainability in water governance.
+    We combined three main dimensions -stress, purpose and allocation- to develop a quantitative Integrated Water Governance Index (IWGI) to detect water governance regimes at a basin scale.
+    Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between the massive supply regime, governance transformation regime, and adaptation oriented regime.
+    In the YRB, the regime shifts' underlying causes were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.
+    The IWGI offers a comprehensive and straightforward approach to linking the water governance regimes to the following challenges in sustainability, along with the hydrosocial transition.
 }

### 2022-04-28 paper/main/04_discussion.tex
fix(version,-abstract): new version 5.1.3, references updated, main text checked

@@
-\subsection{Challenges along with the transition}
-
 \begin{figure*}[htbp!]
@@
 % Implications
-Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being \cite{best2019, best2020}.
+Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being
+\cite{best2019,best2020}.
 As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships \cite{diaz2019}.
 The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
-It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime \cite{reyers2018}.
+It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime \cite{reyers2018}.
 
@@
 However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
-We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
+Therefore, we suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
 In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems

### 2022-04-28 paper/main/manuscript.tex
fix(version,-abstract): new version 5.1.3, references updated, main text checked

@@
     In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
-    Identifying regime changes is critical to understanding the transition and guiding sustainability in water governance.
+Therefore, identifying regime changes is critical to understanding the transition and guiding sustainability in water governance.
 We combined three main dimensions -stress, purpose and allocation- to develop a quantitative Integrated Water Governance Index (IWGI) to detect water governance regimes at a basin scale.
-    Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between the massive supply regime, governance transformation regime, and adaptation oriented regime.
+Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between massive supply, transformation governance, and adaptation-oriented regimes.
 In the YRB, the regime shifts' underlying causes were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.

### 2022-04-29 paper/main/02_methods.tex
feat(appendix): sort appendix
BREAKING CHANGE:

@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the Indicator in a particular region $i$ \cite{qin2019}.
-This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details).
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress \cite{qin2019}.
+This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the structure of water use on the evaluation of water scarcity.
+Based on the hydrological and economic context of YRB, four main regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{\ref{secA1}}).
 For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
@@
 
-	Where $SFV_i$ is the SFV-index for region $i$, and $i=1$ to $4$ refers SR, UR, MR, and DR (see \textit{SI Appendix} Methods S1 Definition of study area).
+	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \ref{secA2}.
 
@@
 	\end{equation}
+
+	In this study, we consider water for livestock, rural or urban domestic and water for agriculture as provisioning water. Others are non-provisioning water uses, such as energy water use.
 
@@
 
-	where $p_{i}$ is the water proportion of region $i$ to the whole basin ($N$ regions in sum).
-The YRB is divided into 4 regions (i.e., $N = 4$) according to the natural and socio-economic backgrounds (see \textit{SI Appendix XX}).
+	where $p_{i}$ is the water proportion of region $i$ to the whole basin ($N=4$ regions in sum).
+Based on the hydrological and economic context of YRB, four main regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{\ref{secA1}}).
 
 	\subsection{Change points detection}
-		% The method makes no assumptions about the distribution of the data and detects breakpoints based solely on the probability of the data coming from different distributions before and after the breakpoint.
-
 		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
@@
 
-		We used $\alpha = 0.001$ as the threshold level of the p-value (see \textit{SI Appendix} Methods S5 for Sensitivity analysis), meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
-		Since this method can only return one significant change point, we divided the series into two at that point and analyzed each series separately until all significant change points were detected.
+		%实际上这个阈值取0.001至0.1不会影响我们的结果，我们识别的断点是相当稳定的
+		We used $\alpha = 0.001$ as the threshold level of the p-value, meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
+We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
+Though two breakpoints were detected in the main text with $\alpha = 0.001$, in fact the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are fairly robust (see \textit{SI Appendix} Figure~\ref{fig:sensitivity}).
 

### 2022-04-29 paper/main/03_results.tex
feat(appendix): sort appendix
BREAKING CHANGE:

@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{SI Appendix} Fig.
-S3).
+As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{SI Appendix} Figure~\ref{fig:reservoirs}).
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering the transformation governance regime (P2), however, the expansion of irrigated areas slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).
-
+Entering the transformation governance regime (P2), however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes} A and B).
 % 水分利用效率由P2变化到P3。
-From P2 to P3, the efficiency of water use changed obviously.
+Then, the efficiency of water use changed obviously from P2 to P3.
 Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig.
-S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors of water use reduced while the total water stress remained stable during the adaptation oriented regime (\textit{SI Appendix} Fig. S3).
+However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Figure~\ref{fig:wci}), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the adaptation oriented regime (Figure~\ref{fig:IWGI}A).
 
@@
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, $p<0.01$), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig.
-S5).
-Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig.
-S6).
+Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, $p<0.01$, see Figure~\ref{fig:Causes}C), when natural water resources were also relatively abundant (\textit{SI Appendix} Figure~\ref{fig:water resources}).
+Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
 In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
-The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.
+Taken together, the regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-29 paper/main/04_discussion.tex
feat(appendix): sort appendix
BREAKING CHANGE:

@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
+In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013) (Figure~\ref{fig:IWGI}).
 During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
@@
 \cite{allan2019,speed2013,liu2012a}.
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %* Kitroeff citation wrong
+Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
 \cite{unep-dhi2016,mirumachi2015}.

### 2022-04-29 paper/main/manuscript.tex
feat(appendix): sort appendix
BREAKING CHANGE:

@@
 
-\section{Section title of first appendix}\label{secA1}
+\section{YRB Regions}\label{secA1}
+
+Since the socio-economic and natural conditions were both considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Figure~\ref{fig:YRB}).
+% 之前的研究也表明，当考虑流域的社会用水和自然条件时，这样的划分是有效的，因为区域之间具有很强的异质性(见图S1-C)。
+Previous studies have also shown that such a division is valid when both social water use and the natural conditions of the basin are considered, as the regions exhibit strong heterogeneity among themselves (see Fig.
+S1-C) \cite{wang2019c}:
+
+\begin{itemize}
+    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region. The most ecology function here is water yield, as sparsely populated and less economically developed.
+    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region.
+However, the efficiency of irrigation are used to be very low.
+    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk.
+To reverse this situation, the grain for green project changed the water utilization here strikingly.
+    \item \textbf{Lower Region (LR):} With dense population and the traditional agricultural trajectory, lower region used to be the largest water use region.
+However, as the industrial transformation going, proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
+\end{itemize}
+
+% 总体来看，黄河流域在经济布局、水资源分布、用水量分布、人口分布等方面存在明显的区域差异(图S2)。
+In general, there are obvious inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (Figure~\ref{fig:water resources}).
+% 在这些根本差异的基础上，社会发展和流域管理继续影响和重塑它们的变化，使黄河流域成为世界上联系最密切、变化最剧烈的大流域。
+On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin.
+
+% 补充图片1：研究区示意图
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.8\textwidth]{sup/s1_study_area.jpg}
+    % 黄河流域示意图
+    % A. 黄河流域示意图及研究区子区域的划分
+    % B. 黄河主河道的剖面图
+    % C. 典型景观
+    \caption{
+        The study area.
+        \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR: Source Region, UR: Upper Region, MR: Middle Region, DR: Downstream region).
+        \textbf{B.} Profile of main channel of the Yellow River. SR, UR, MR and DR are divided by main hydrological stations.
+        \textbf{C.} Typical landscapes in different regions in the YRB.
+    }
+    \label{fig:YRB}
+\end{figure*}
+
+% 补充图片4：天然水资源量
+\begin{figure*}[tb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{sup/sf_measured_runoff.pdf}
+    \caption{Water resources in different regions.
+        \textbf{A,} changing trend of measured runoff,
+        \textbf{B, C and D} average measured runoff within different periods.
+        \textbf{E, F and G} average total water consumptions within different periods.
+    }
+    \label{fig:water resources}
+\end{figure*}
+
+\section{SFV-index}
+By taking changes of water flexibility and variability into account, the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses \cite{qin2019}.
+
+To apply this method, we need to combine three metrics following:
+
+First for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume, in year $j$ and region $i$:
+\begin{equation}
+    A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
+\end{equation}
+
+Second for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.
+for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
+\begin{equation}
+    B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}}
+\end{equation}
+
+Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
+\begin{gather}
+C_i = C1_i * (1 - C2_i) \\
+C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} \\
+C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} \\
+C2_{i} = 1, \ if RC >= R_{i, avg}
+\end{gather}
+
+In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+
+Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate $SFV$ index after normalizing them:
+\begin{gather}
+    V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3}\\
+    a = \frac{1}{V_{max} - V_{min}};\\
+    b = \frac{1}{V_{min} - V_{max}} * V_{min}\\
+    SFV = a * V + b
+\end{gather}
+
+\begin{figure*}[tb!]
+	\centering
+	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
+	\caption{
+	    Ratio of irrigated areas with water-saving equipments.
+	}
+	\label{fig:wci}
+\end{figure*}
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[width=0.9\linewidth]{sup/reservoirs.pdf}
+	\caption{
+	    Reservoirs.
+	}
+	\label{fig:reservoirs}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.95\textwidth]{sup/sensitivity.pdf}
+    \caption{
+        Sensitivity analysis of the threshold of p-values.
+        \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
+        \textbf{B.} A typical result of two breakpoints.
+        \textbf{C.} A typical result of three breakpoints.
+    }
+    \label{fig:sensitivity}
+\end{figure*}
+
+\begin{table*}[!htbp]
+\begin{center}
+\begin{minipage}{\linewidth}
+\caption{Used datasets and their sources.}\label{datasets}%
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+Dataset & Type & Spatial scale & Time limit & Source \\
+\midrule
+1. Water use & Statistical & Prefectures & 1965-2013 & 2nd National Water Resources Assessment Program \\
+2. GDP & Statistical & Province & 1949-2019 & Wind database \\
+3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
+4. Reservoirs & Hydrological & Location & 1949-2015 & Wang et al. \cite{wang2019c} \\
+5. Measured runoff & Hydrological & Location & 1949-2019 & Measured data from YRCC \\
+6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommission2013} \\
+7. History of YRCC & Political & Documents & 1949-2002 & YRCC \cite{yellowriverarchives2004} \\
+\botrule
+\end{tabular}}
+% \footnotetext{Source: This is an example of table footnote.
+% This is an example of table footnote.}
+% \footnotetext[1]{Example for a first table footnote.
+% This is an example of table footnote.}
+% \footnotetext[2]{Example for a second table footnote.
+% This is an example of table footnote.}
+\end{minipage}
+\end{center}
+\end{table*}
+
+%% 表格
+\begin{table*}
+    \centering
+    \caption{Policies and regulations above YRB level which affected the whole basin in water utilization}
+    \begin{minipage}{\linewidth}
+    % 表格
+    \resizebox{\linewidth}{!}{
+    \begin{tabular}{lrr}
+    Name & Year & Agency \\
+    \midrule
+    1. Water Law of PRC & 1988 & National People's Congress of the PRC \\
+    2. Water Law of PRC -revised 1 & 2009 & National People's Congress of the PRC \\
+    3. Water Law of PRC -revised 2 & 2016 & National People's Congress of the PRC \\
+    4. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
+    5. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees -revised 1 & 2017 & State Council of the PRC \\
+    6. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
+    7. Yellow River water supply distribution scheme & 1987 & State Council of the PRC \\
+    8. Measures for the Administration of Water Drawing Permits & 2008 & Ministry of Water Resources of the PRC \\
+    9. Measures for the Administration of Water Drawing Permits -revised 1 & 2015 & Ministry of Water Resources of the PRC \\
+    10. Measures for the Administration of Water Drawing Permits -revised 2 & 2017 & Ministry of Water Resources of the PRC \\
+    11. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
+    12. Annual distribution of available water supply of the Yellow River and main stream water dispatching scheme & 1998 & Ministry of Water Resources of the PRC \\
+    13. The Yellow River water dispatching management measures & 1998 & Ministry of Water Resources \\
+    14. Measures for the Implementation of the Yellow River Water Rights Conversion Management & 2004 & Ministry of Water Resources \\
+    15. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
+    16. Measures for the implementation of the water drawing Permit system & 1993 \\ State Council of the PRC \\
+    17. Measures for the demonstration and management of water resources in construction projects & 2002 & Ministry of Water Resources of the PRC \\
+    18. Implementation Opinions on the Reform of Water Conservancy Project Management System & 2006 & State Council of the PRC \\
+    \bottomrule
+    \end{tabular}}
+
+    \footnotesize[1]{If a policy was proposed by multiple legacies, we only show the highest one.}
+    \label{policies}
+\end{minipage}
+\end{table*}
 

### 2022-04-29 paper/main/01_introduction.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

@@
 Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}.
-For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes \cite{kjellen2015, grafton2013}.
-Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
+For populated large river basins, missing governance means missing sustainability, and a first critical step in understanding the transitions with successful water governance is identifying the different regimes \cite{kjellen2015, grafton2013}.
+Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations) as a stable state in structures and functions
 \cite{falkenmark2021,bressers2013,loch2020}.

### 2022-04-29 paper/main/02_methods.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

@@
 
-	Then, the Integrated Water Governance Index (IWGI) is the average of the normalized indicators $I'_x$:
+	Then, the Integrated Water Governance Index (IWGI) is an average of the normalized indicators $I'_x$:
 	\begin{equation}
-		IWGI = I'_S + I'_P - I'_A
+		IWGI = (I'_S + I'_P + I'_A) / 3
 	\end{equation}
@@
 	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress \cite{qin2019}.
-This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the structure of water use on the evaluation of water scarcity.
-Based on the hydrological and economic context of YRB, four main regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{\ref{secA1}}).
+This metric considers management measures (such as the construction of reservoirs) and the impact of changes in the structure of water use on the evaluation of water scarcity.
+Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Appendix}\ref{secA1}).
 For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
@@
 
-	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \ref{secA2}.
+	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \textit{Appendix}\ref{secA2}.
 
@@
 	\subsubsection*{Indicator of allocations}
-	%$AEM$ 指标度量的是水资源配置“不均匀”的程度，类似于信息熵是对“混乱程度”的度量，即参与分配的各个单位之间，分配比例差距越大，则熵越小。
-	% 而我们的指标应反映随着社会发展，水资源配置在区域之间更加均衡（比例差距小）、整体满足不同用水部门的发展需求（比例差距减小）、但不同区域存在部门分工（比例差距增大）的趋势。
 	To describe allocations $I_A$, we designed an indicator based on entropy, called Allocation Entropy Metric (AEM), which measures the degree of evenness in water allocation:
@@
 
-	where $p_{i}$ is the water proportion of region $i$ to the whole basin ($N=4$ regions in sum).
-Based on the hydrological and economic context of YRB, four main regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{\ref{secA1}}).
+	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Appendix}\ref{secA1}).
 
@@
 		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
-		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
+		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}}$ and $x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
 To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:
@@
 We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
-Though two breakpoints were detected in the main text with $\alpha = 0.001$, in fact the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are fairly robust (see \textit{SI Appendix} Figure~\ref{fig:sensitivity}).
-
-	% % 计算贡献度
-	% \subsection{Contribution decomposition}
-	% 	We decomposed the amount of variation in each index at different periods to quantify each influence's contribution to the index.
-Using the Integrated Water Governance Index (IWGI) as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_A$).
-We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
-	% 	\begin{align}
-	% 	\Delta IWGI &= (I'_{P_{y_2}} + I'_{A_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{A_{y_1}} - I'_{S_{y_1}}) \\
-	% 	&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{A_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
-	% 	&= \Delta I'_P + \Delta I'_A + (-\Delta I'_S)
-	% 	\end{align}
-	% 	Then, the contribution of dimension $x$ to IWGI's changes can be referred to as:
-	% 	\begin{equation}
-	% 		Contribution_x = \frac{\Delta I'_x}{\lvert \Delta IWGI \rvert}
-	% 	\end{equation}
-
-		% Since $Contribution_x$ can be positive or negative, we used an absolute value to evaluate the contribution (in proportion) of a certain dimension in the all three dimensions to the changes:
-		% \begin{equation}
-		% 	Contribution_x\% = \frac{|\Delta I'_x|}{\sum_x \lvert \Delta I'_x \rvert}
-		% \end{equation}
-
-		% or just for contributions (in proportion) within a certain year $j$ to the regime:
-		% \begin{equation}
-		% 	Contribution_{x,j}\% = \frac{\lvert I'_{x, j} \rvert}{\lvert \sum_x I'_{x, j} \rvert}
-		% \end{equation}
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see \textit{Appendix} Figure~\ref{fig:sensitivity}).
 
@@
 	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI from 1965 to 2013, we need to calculate multiple indicators and sub-indicators.
-All the datasets used are listed in the \textit{SI Appendix} table S1.
-A detailed description of the data is provided in the supplementary materials \textit{SI Appendix} Methods S2.
+	In order to calculate IWGI in the YRB, all the datasets we need are listed in the \textit{SI Appendix} Table~\ref{tab:datasets} with a detailed description in \ref{secA3}.

### 2022-04-29 paper/main/03_results.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

@@
 	\caption{
-		Causes of water governance regime shifts in the YRB: environmental change, economic growth and efficiency changes, social transformation, and governance policies.
-		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the area, the green dot line).
+		Causes of water governance regime shifts in the YRB.
+		% environmental change, economic growth and efficiency changes, social transformation, and governance policies.
+		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the irrigated area, the green dot line).
 		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line).
@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which was constructed mainly for managing floodwater discharge and water regulation.
+		% Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing floodwater discharge and water regulation.
 These named reservoirs are significant for the whole basin rather than local development.
-		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{SI Appendix} Table S2).
-The light grey bars year-by-year show the frequency of official documents related to the YRB at a basinal scale (see \textit{SI Appendix} Table S3).
+		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Appendix} Table~\ref{tab:policies}).
+The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
 	}
@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{SI Appendix} Figure~\ref{fig:reservoirs}).
+As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Appendix} Figure~\ref{fig:reservoirs}).
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
@@
 Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Figure~\ref{fig:wci}), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
+Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
 As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the adaptation oriented regime (Figure~\ref{fig:IWGI}A).
@@
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, $p<0.01$, see Figure~\ref{fig:Causes}C), when natural water resources were also relatively abundant (\textit{SI Appendix} Figure~\ref{fig:water resources}).
+Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, $p<0.01$, see Figure~\ref{fig:Causes}C)).
 Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
 In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
-Taken together, the regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.
+The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-29 paper/main/04_discussion.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{main/transition.png}
+	\includegraphics[width=0.8\linewidth]{main/transition.png}
 	\caption{
@@
 \cite{allan2019,speed2013,liu2012a}.
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
+Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and maybe in urgent need of novel flexible, efficient sociopolitical governance structures
 \cite{unep-dhi2016,mirumachi2015}.
@@
 However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
-Therefore, we suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
+Therefore, we suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in holistically understanding the transition of governance regimes.
 In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems

### 2022-04-29 paper/main/manuscript.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

--- 2022-04-28 paper/main/manuscript.tex
@@
 %%\pacs[JEL Classification]{D8, H51}
-
 %%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
@@
 \input{03_results}
-
-%! \section{Equations}\label{sec4}
-
-% Equations in \LaTeX\ can either be inline or on-a-line by itself (``display equations''). For
-% inline equations use the \verb+$...$+ commands. E.g.: The equation
-% $H\psi = E \psi$ is written via the command \verb+$H \psi = E \psi$+.
-
-% For display equations (with auto generated equation numbers)
-% one can use the equation or align environments:
-% \begin{equation}
-% \|\tilde{X}(k)\|^2 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.\label{eq1}
-% \end{equation}
-% where,
-% \begin{align}
-% D_\mu &=  \partial_\mu - ig \frac{\lambda^a}{2} A^a_\mu \nonumber \\
-% F^a_{\mu\nu} &= \partial_\mu A^a_\nu - \partial_\nu A^a_\mu + g f^{abc} A^b_\mu A^a_\nu \label{eq2}
-% \end{align}
-% Notice the use of \verb+\nonumber+ in the align environment at the end
-% of each line, except the last, so as not to produce equation numbers on
-% lines where no equation numbers are required. The \verb+\label{}+ command
-% should only be used at the last line of an align environment where
-% \verb+\nonumber+ is not used.
-% \begin{equation}
-% Y_\infty = \left( \frac{m}{\textrm{GeV}} \right)^{-3}
-%     \left[ 1 + \frac{3 \ln(m/\textrm{GeV})}{15}
-%     + \frac{\ln(c_2/5)}{15} \right]
-% \end{equation}
-% The class file also supports the use of \verb+\mathbb{}+, \verb+\mathscr{}+ and
-% \verb+\mathcal{}+ commands. As such \verb+\mathbb{R}+, \verb+\mathscr{R}+
-% and \verb+\mathcal{R}+ produces $\mathbb{R}$, $\mathscr{R}$ and $\mathcal{R}$
-% respectively (refer Subsubsection~\ref{subsubsec2}).
-
-% \section{Tables}\label{sec5}
-
-% Tables can be inserted via the normal table and tabular environment. To put
-% footnotes inside tables you should use \verb+\footnotetext[]{...}+ tag.
-% The footnote appears just below the table itself (refer Tables~\ref{tab1} and \ref{tab2}).
-% For the corresponding footnotemark use \verb+\footnotemark[...]+
-
-% % \begin{table}[h]
-% % \begin{center}
-% % \begin{minipage}{174pt}
-% % \caption{Caption text}\label{tab1}%
-% % \begin{tabular}{@{}llll@{}}
-% % \toprule
-% % Column 1 & Column 2  & Column 3 & Column 4\\
-% % \midrule
-% % row 1    & data 1   & data 2  & data 3  \\
-% % row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
-% % row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
-% % \botrule
-% % \end{tabular}
-% % \footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
-% % \footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
-% % \footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
-% % \end{minipage}
-% % \end{center}
-% % \end{table}
-
-% % \noindent
-% % The input format for the above table is as follows:
-
-% % %%=============================================%%
-% % %% For presentation purpose, we have included  %%
-% % %% \bigskip command. please ignore this.       %%
-% % %%=============================================%%
-% % \bigskip
-% % \begin{verbatim}
-% % \begin{table}[<placement-specifier>]
-% % \begin{center}
-% % \begin{minipage}{<preferred-table-width>}
-% % \caption{<table-caption>}\label{<table-label>}%
-% % \begin{tabular}{@{}llll@{}}
-% % \toprule
-% % Column 1 & Column 2 & Column 3 & Column 4\\
-% % \midrule
-% % row 1 & data 1 & data 2	 & data 3 \\
-% % row 2 & data 4 & data 5\footnotemark[1] & data 6 \\
-% % row 3 & data 7 & data 8	 & data 9\footnotemark[2]\\
-% % \botrule
-% % \end{tabular}
-% % \footnotetext{Source: This is an example of table footnote.
-% % This is an example of table footnote.}
-% % \footnotetext[1]{Example for a first table footnote.
-% % This is an example of table footnote.}
-% % \footnotetext[2]{Example for a second table footnote.
-% % This is an example of table footnote.}
-% % \end{minipage}
-% % \end{center}
-% % \end{table}
-% % \end{verbatim}
-% % \bigskip
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-
-% \begin{table}[h]
-% \begin{center}
-% \begin{minipage}{\textwidth}
-% \caption{Example of a lengthy table which is set to full textwidth}\label{tab2}
-% \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
-% \toprule%
-% & \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Element 2\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
-% Project & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
-% \midrule
-% Element 3  & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$\\
-% Element 4  & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$\\
-% \botrule
-% \end{tabular*}
-% \footnotetext{Note: This is an example of table footnote.
-This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
-% \footnotetext[1]{Example for a first table footnote.}
-% \footnotetext[2]{Example for a second table footnote.}
-% \end{minipage}
-% \end{center}
-% \end{table}
-
-% In case of double column layout, tables which do not fit in single column width should be set to full text width.
-For this, you need to use \verb+\begin{table*}+ \verb+...+ \verb+\end{table*}+ instead of \verb+\begin{table}+ \verb+...+ \verb+\end{table}+ environment.
-Lengthy tables which do not fit in textwidth should be set as rotated table.
-For this, you need to use \verb+\begin{sidewaystable}+ \verb+...+ \verb+\end{sidewaystable}+ instead of \verb+\begin{table*}+ \verb+...+ \verb+\end{table*}+ environment.
-This environment puts tables rotated to single column width.
-For tables rotated to double column width, use \verb+\begin{sidewaystable*}+ \verb+...+ \verb+\end{sidewaystable*}+.
-
-% \begin{sidewaystable}
-% \sidewaystablefn%
-% \begin{center}
-% \begin{minipage}{\textheight}
-% \caption{Tables which are too long to fit, should be written using the ``sidewaystable'' environment as shown here}\label{tab3}
-% \begin{tabular*}{\textheight}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
-% \toprule%
-% & \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]}& \multicolumn{3}{@{}c@{}}{Element\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
-% Projectile & Energy	& $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
-% \midrule
-% Element 3 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
-% Element 4 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
-% Element 5 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
-% Element 6 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
-% \botrule
-% \end{tabular*}
-% \footnotetext{Note: This is an example of table footnote this is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
-% \footnotetext[1]{This is an example of table footnote.}
-% \end{minipage}
-% \end{center}
-% \end{sidewaystable}
-
-% \section{Figures}\label{sec6}
-
-% As per the \LaTeX\ standards you need to use eps images for \LaTeX\ compilation and \verb+pdf/jpg/png+ images for \verb+PDFLaTeX+ compilation.
-This is one of the major difference between \LaTeX\ and \verb+PDFLaTeX+.
-Each image should be from a single input .eps/vector image file.
-Avoid using subfigures.
-The command for inserting images for \LaTeX\ and \verb+PDFLaTeX+ can be generalized.
-The package used to insert images in \verb+LaTeX/PDFLaTeX+ is the graphicx package.
-Figures can be inserted via the normal figure environment as shown in the below example:
-
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-% \bigskip
-% \begin{verbatim}
-% \begin{figure}[<placement-specifier>]
-% \centering
-% \includegraphics{<eps-file>}
-% \caption{<figure-caption>}\label{<figure-label>}
-% \end{figure}
-% \end{verbatim}
-% \bigskip
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-
-% \begin{figure}[h]%
-% \centering
-% \includegraphics[width=0.9\textwidth]{fig.eps}
-% \caption{This is a widefig. This is an example of long caption this is an example of long caption  this is an example of long caption this is an example of long caption}\label{fig1}
-% \end{figure}
-
-% In case of double column layout, the above format puts figure captions/images to single column width.
-To get spanned images, we need to provide \verb+\begin{figure*}+ \verb+...+ \verb+\end{figure*}+.
-
-% For sample purpose, we have included the width of images in the optional argument of \verb+\includegraphics+ tag. Please ignore this.
-
-% \section{Algorithms, Program codes and Listings}\label{sec7}
-
-% Packages \verb+algorithm+, \verb+algorithmicx+ and \verb+algpseudocode+ are used for setting algorithms in \LaTeX\ using the format:
-
-% %%=============================================%%
-% %% For presentation purpose, we have included  %%
-% %% \bigskip command. please ignore this.       %%
-% %%=============================================%%
-% \bigskip
-% \begin{verbatim}
-% \begin{algorithm}
-% \caption{<alg-caption>}\label{<alg-label>}
-% \begin{algorithmic}[1]
-% . . .
-% \end{algorithmic}
-% \end{algorithm}
-% \end{verbatim}
-% \bigskip
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-
-% You may refer above listed package documentations for more details before setting \verb+algorithm+ environment.
-For program codes, the ``program'' package is required and the command to be used is \verb+\begin{program}+ \verb+...+ \verb+\end{program}+.
-A fast exponentiation procedure:
-
-% \begin{program}
-% \BEGIN \\ %
-%   \FOR i:=1 \TO 10 \STEP 1 \DO
-%      |expt|(2,i); \\ |newline|() \OD %
-% \rcomment{Comments will be set flush to the right margin}
-% \WHERE
-% \PROC |expt|(x,n) \BODY
-%           z:=1;
-%           \DO \IF n=0 \THEN \EXIT \FI;
-%              \DO \IF |odd|(n) \THEN \EXIT \FI;
-% \COMMENT{This is a comment statement};
-%                 n:=n/2; x:=x*x \OD;
-%              \{ n>0 \};
-%              n:=n-1; z:=z*x \OD;
-%           |print|(z) \ENDPROC
-% \END
-% \end{program}
-
-% \begin{algorithm}
-% \caption{Calculate $y = x^n$}\label{algo1}
-% \begin{algorithmic}[1]
-% \Require $n \geq 0 \vee x \neq 0$
-% \Ensure $y = x^n$
-% \State $y \Leftarrow 1$
-% \If{$n < 0$}\label{algln2}
-%         \State $X \Leftarrow 1 / x$
-%         \State $N \Leftarrow -n$
-% \Else
-%         \State $X \Leftarrow x$
-%         \State $N \Leftarrow n$
-% \EndIf
-% \While{$N \neq 0$}
-%         \If{$N$ is even}
-%             \State $X \Leftarrow X \times X$
-%             \State $N \Leftarrow N / 2$
-%         \Else[$N$ is odd]
-%             \State $y \Leftarrow y \times X$
-%             \State $N \Leftarrow N - 1$
-%         \EndIf
-% \EndWhile
-% \end{algorithmic}
-% \end{algorithm}
-% \bigskip
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-
-% Similarly, for \verb+listings+, use the \verb+listings+ package.
-\verb+\begin{lstlisting}+ \verb+...+ \verb+\end{lstlisting}+ is used to set environments similar to \verb+verbatim+ environment.
-Refer to the \verb+lstlisting+ package documentation for more details.
-
-% %%=============================================%%
-% %% For presentation purpose, we have included  %%
-% %% \bigskip command. please ignore this.       %%
-% %%=============================================%%
-% \bigskip
-% \begin{minipage}{\hsize}%
-% \lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}% Set your language (you can change the language for each code-block optionally)
-% %%% Start your code-block
-% \begin{lstlisting}
-% for i:=maxint to 0 do
-% begin
-% { do nothing }
-% end;
-% Write('Case insensitive ');
-% Write('Pascal keywords.');
-% \end{lstlisting}
-% \end{minipage}
-
-% \section{Cross referencing}\label{sec8}
-
-% Environments such as figure, table, equation and align can have a label
-% declared via the \verb+\label{#label}+ command. For figures and table
-% environments use the \verb+\label{}+ command inside or just
-% below the \verb+\caption{}+ command. You can then use the
-% \verb+\ref{#label}+ command to cross-reference them. As an example, consider
-% the label declared for Figure~\ref{fig1} which is
-% \verb+\label{fig1}+. To cross-reference it, use the command
-% \verb+Figure \ref{fig1}+, for which it comes up as
-% ``Figure~\ref{fig1}''.
-
-% To reference line numbers in an algorithm, consider the label declared for the line number 2 of Algorithm~\ref{algo1} is \verb+\label{algln2}+.
-To cross-reference it, use the command \verb+\ref{algln2}+ for which it comes up as line~\ref{algln2} of Algorithm~\ref{algo1}.
-
-% \subsection{Details on reference citations}\label{subsec7}
-
-% Standard \LaTeX\ permits only numerical citations.
-To support both numerical and author-year citations this template uses \verb+natbib+ \LaTeX\ package.
-For style guidance please refer to the template user manual.
-
-% Here is an example for \verb+\cite{...}+: \cite{bib1}.
-Another example for \verb+\citep{...}+: \citep{bib2}.
-For author-year citation mode, \verb+\cite{...}+ prints Jones et al.
-(1990) and \verb+\citep{...}+ prints (Jones et al., 1990).
-
-% All cited bib entries are printed at the end of this article: \cite{bib3}, \cite{bib4}, \cite{bib5}, \cite{bib6}, \cite{bib7}, \cite{bib8}, \cite{bib9}, \cite{bib10}, \cite{bib11} and \cite{bib12}.
-
-% \section{Examples for theorem like environments}\label{sec10}
-
-% For theorem like environments, we require \verb+amsthm+ package. There are three types of predefined theorem styles exists---\verb+thmstyleone+, \verb+thmstyletwo+ and \verb+thmstylethree+
-
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-% \bigskip
-% \begin{tabular}{|l|p{19pc}|}
-% \hline
-% \verb+thmstyleone+ & Numbered, theorem head in bold font and theorem text in italic style \\\hline
-% \verb+thmstyletwo+ & Numbered, theorem head in roman font and theorem text in italic style \\\hline
-% \verb+thmstylethree+ & Numbered, theorem head in bold font and theorem text in roman style \\\hline
-% \end{tabular}
-% \bigskip
-%%=============================================%%
-%% For presentation purpose, we have included  %%
-%% \bigskip command. please ignore this.       %%
-%%=============================================%%
-
-% For mathematics journals, theorem styles can be included as shown in the following examples:
-
-% \begin{theorem}[Theorem subhead]\label{thm1}
-% Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text.
-% Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text.
-% Example theorem text.
-% \end{theorem}
-
-% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.
-
-% \begin{proposition}
-% Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text.
-% Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text.
-% \end{proposition}
-
-% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.
-
-% \begin{example}
-% Phasellus adipiscing semper elit. Proin fermentum massa
-% ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-% at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.
-% \end{example}
-
-% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.
-
-% \begin{remark}
-% Phasellus adipiscing semper elit. Proin fermentum massa
-% ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-% at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.
-% \end{remark}
-
-% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.
-
-% \begin{definition}[Definition sub head]
-% Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-% \end{definition}
-
-% Additionally a predefined ``proof'' environment is available: \verb+\begin{proof}+ \verb+...+ \verb+\end{proof}+.
-This prints a ``Proof'' head in italic font style and the ``body text'' in roman font style with an open square at the end of each proof environment.
-
-% \begin{proof}
-% Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-% \end{proof}
-
-% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text. Sample body text.
-
-% \begin{proof}[Proof of Theorem~{\upshape\ref{thm1}}]
-% Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-% \end{proof}
-
-% \noindent
-% For a quote environment, use \verb+\begin{quote}...\end{quote}+
-% \begin{quote}
-% Quoted text example. Aliquam porttitor quam a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-% convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-% \end{quote}
-
-% Sample body text. Sample body text. Sample body text. Sample body text. Sample body text (refer Figure~\ref{fig1}). Sample body text. Sample body text. Sample body text (refer Table~\ref{tab3}).
-
-% Topical subheadings are allowed.
-Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.
-Authors are encouraged to include RIIDs where appropriate.
-
-% \textbf{Ethical approval declarations} (only required where applicable) Any article reporting experiment/s carried out on (i)~live vertebrate (or higher invertebrates), (ii)~humans or (iii)~human samples must include an unambiguous statement within the methods section that meets the following requirements:
-
-% \begin{enumerate}[1.]
-% \item Approval: a statement which confirms that all experimental protocols were approved by a named institutional and/or licensing committee.
-Please identify the approving body in the methods section
-
-% \item Accordance: a statement explicitly saying that the methods were carried out in accordance with the relevant guidelines and regulations
-
-% \item Informed consent (for experiments involving humans or human tissue samples): include a statement confirming that informed consent was obtained from all participants and/or their legal guardian/s
-% \end{enumerate}
-
-% If your manuscript includes potentially identifying patient/participant information, or if it describes human transplantation research, or if it reports results of a clinical trial then  additional information will be required.
-Please visit (\url{https://www.nature.com/nature-research/editorial-policies}) for Nature Portfolio journals, (\url{https://www.springer.com/gp/authors-editors/journal-author/journal-author-helpdesk/publishing-ethics/14214}) for Springer Nature journals, or (\url{https://www.biomedcentral.com/getpublished/editorial-policies\#ethics+and+consent}) for BMC.
 
@@
 \bmhead{Supplementary information}
-
-If your article has accompanying supplementary file/s please state so here.
-
-Authors reporting data from electrophoretic gels and blots should supply the full unprocessed scans for key as part of their Supplementary information.
-This may be requested by the editorial team/s if it is missing.
-
-Please refer to Journal-level guidance for any specific requirements.
+When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
+Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the \ref{secA1}.
+The formulation in detail for applying the SFV-index is available in the \ref{secA2}.
+We used multiple sources of datasets in this study, \textit{Appendix}~\ref{secA3} introduces where they came from and how we harmonise them for analysis.
 
@@
 
-Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.
-
-Please refer to Journal-level guidance for any specific requirements.
+Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
 
@@
 
-\section{Section title of first appendix}\label{secA1}
+\section{YRB Regions}\label{secA1}
+\input{../sup/01_yrb.tex}
 
-%%=============================================%%
-%% For submissions to Nature Portfolio Journals %%
-%% please use the heading ``Extended Data''.   %%
-%%=============================================%%
+\section{SFV-index}\label{secA2}
+\input{../sup/02_indicator.tex}
 
-%%=============================================================%%
-%% Sample for another appendix section			       %%
-%%=============================================================%%
+% \begin{figure}[tb!]
+% 	\centering
+% 	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
+% 	\caption{
+% 	    Ratio of irrigated areas with water-saving equipments.
+% 	}
+% 	\label{fig:wci}
+% \end{figure}
 
-%% \section{Example of another appendix section}\label{secA2}%
-%% Appendices may be used for helpful, supporting or essential material that would otherwise
-%% clutter, break up or be distracting to the text. Appendices can consist of sections, figures,
-%% tables and equations etc.
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
+	\caption{
+	    Numbers of new reservoirs in each year.
+	}
+	\label{fig:reservoirs}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{sup/sensitivity.pdf}
+    \caption{
+        Sensitivity analysis of the threshold of p-values.
+        \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
+        \textbf{B.} Threshold of p-values $\alpha=0.0005$.
+        \textbf{C.} Threshold of p-values $\alpha=0.05$.
+    }
+    \label{fig:sensitivity}
+\end{figure}
+
+\section{Datasets}\label{secA3}
+\input{../sup/03_datasets.tex}
 

### 2022-04-29 paper/sup/01_yrb.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

We divide the YRB into four regions to calculate the indicators considering both socio-economic and natural conditions. The division aligns with the customary schema from publications and the YRCC \cite{yellowriverconservancycommission2013,wang2019c,wang2016e}, so four important hydrological stations can distinguish the regions (see Figure~\ref{fig:YRB}).

\begin{itemize}
    \item \textbf{Source Region (SR):} Over 50\% of natural runoff originates from this region. The most ecological function here is water yield, as sparsely populated and less economically developed.
    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region. However, irrigation efficiency is relatively much lower than its lower reaches.
    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, a famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk. The ``grain for the green'' project changed the water utilization here strikingly to reverse this situation \cite{wu2020a}.
    \item \textbf{Lower Region (LR):} With a dense population and the traditional agricultural trajectory, the lower region used to be the largest water use region. However, as the industrial transformation going, the proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
\end{itemize}

% 补充图片1：研究区示意图
\begin{figure*}[hbtp!]
    \centering
    \includegraphics[width=0.6\textwidth]{sup/s1_study_area.jpg}
    \caption{
        The study area.
        \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR: Source Region, UR: Upper Region, MR: Middle Region, DR: Downstream region).
        \textbf{B.} Profile of the main channel of the Yellow River. The hydrological stations control the SR, UR, MR and DR.
        \textbf{C.} Typical landscapes in different regions in the YRB.
    }
    \label{fig:YRB}
\end{figure*}

% % 补充图片4：天然水资源量
% \begin{figure*}[tb]
%     \centering
%     \includegraphics[width=0.8\textwidth]{sup/sf_measured_runoff.pdf}
%     \caption{Water resources in different regions.
%         \textbf{A,} changing trend of measured runoff,
%         \textbf{B, C and D} average measured runoff within different periods.
%         \textbf{E, F and G} average total water consumptions within different periods.
%     }
%     \label{fig:water resources}
% \end{figure*}

### 2022-04-29 paper/sup/02_indicator.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

By taking water flexibility and variability into account, the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses \cite{qin2019}. To apply this method, we need to combine three metrics following:

First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Appendix}~\ref{secA1}):
\begin{equation}
    A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
\end{equation}

Second, for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e. for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
\begin{equation}
    B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}}
\end{equation}

Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
\begin{gather}
C_i = C1_i * (1 - C2_i) \\
C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} \\
C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} \\
C2_{i} = 1, \ if RC >= R_{i, avg}
\end{gather}

In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.

Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate the $SFV$ index after normalizing them:
\begin{gather}
    V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3}\\
    a = \frac{1}{V_{max} - V_{min}};\\
    b = \frac{1}{V_{min} - V_{max}} * V_{min}\\
    SFV = a * V + b
\end{gather}

### 2022-04-29 paper/sup/03_datasets.tex
docs(finish-appendix): full version, with finished appendix, well structured main text, all references, correct grammar
BREAKING CHANGE:

\subsection*{Descriptions}
This study used multiple types of data (see Table~\ref{tab:datasets}): statistical datasets, hydrological datasets, and political datasets.

\subsubsection*{Statistical datasets}
% We used GDP data; water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhou2020} and statistical yearbooks \url{http://www.yrcc.gov.cn/other/hhgb/}.
The water resources use dataset was published by Zhou et al. \cite{zhou2020}, which records water utilization in different sectors along with social-economic situations at the Prefectures level. 2nd National Water Resources Assessment Program mainly extracted this dataset launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details). Since then, the statistics from the survey using the same criteria have been supplemented and harmonized with the 2013 administrative divisions.

The data covers a total of subcategories of water use under four broad categories: agriculture (IRR), industry (IND), urban (URB) and rural (RUR) water use (see Zhou et al., for details \cite{zhou2020}).
% There is uncertainty at the county scale for each disaggregated water use sector, but because the corrected data has been for statistical information using the water balance method, the data are adequate for the regional scale used in this study.

\subsubsection*{Hydrological datasets}
The reservoir dataset was collected by Wang et al. \cite{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Figure~\ref{fig:reservoirs}). YRCC labelled the regulation-oriented reservoirs among them, see \url{http://www.yrcc.gov.cn/hhyl/sngc/}). In addition, annual runoff data derived from hydrological station measurements are the same as the datasets used in \cite{wang2019c} and \cite{wang2016e}.

\subsubsection*{Political datasets}
The policy dataset collects laws and policies listed in the book \cite{yellowriverconservancycommission2013}, which are related to the Yellow River basin promulgated and implemented by departments at (such as YRCC) and above (such as national institutions) at the Basin's level (Table~\ref{tab:policies}).
In addition, some are difficult to categorize; not a landmark, but numerous water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC; we collected them from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.

\subsection*{Methods S3. Harmonization}
Due to the wide sources of our data set and the different spatial scales, we need to harmonize them into a practical scale.
\begin{itemize}
    \item 1. Datasets at watersheds scales:
        We directly divided the annual hydrological data and measured runoff data according to their watersheds' corresponding hydrological stations (see Figure~\ref{fig:YRB} A and B).
    \item 2. Prefecture:
        We calculate the area of each prefecture to determine whether they belong to a region, with the threshold of $95\%$:

        \begin{equation}
            S_{ij} = MAX(S_ij / S_i)
        \end{equation}

        Where $i$ refers to a specific prefecture and $j$ refers to a region within YRB, i.e. SR, UR, MR, or DR. $S_i$ refers to the area of perfect $i$, and $S_{ij}$ refers intersecting area between perfect $i$ and region $j$.
        We define perfecture $i$ belongs to region $j$ if their intersecting area $S_{ij}$ over 95\% of $S_i$, i.e.:

        \begin{equation}
            MAX(S_{ij}) > 0.95 * S_i
        \end{equation}
    \item 3. Province:
        According to the major provinces contained in different regions, we determine which region the data of that province is merged into by referring to the traditional division practice:
    \begin{itemize}
        \item SR: Qinghai Gansu and Sichuan,
        \item UR: Ningxia and Inner Mongolia,
        \item MR: Shanxi and Shaanxi,
        \item DR: Shandong, Hebei and Henan.
    \end{itemize}
\end{itemize}

Finally, when we process the location data (i.e., the location data of the reservoirs), we judge the province it belongs to according to its location and then fit it to the regional scale.

\begin{table*}[!htbp]
    \begin{center}
    \small
    \begin{minipage}{\linewidth}
    \caption{Used datasets and their sources.}\label{tab:datasets}%
    \resizebox{\linewidth}{!}{
    \begin{tabular}{lrrrp{0.4\linewidth}}
    \toprule
    Dataset & Type & Spatial scale & Time scale & Source \\
    \midrule
    1. Administrative water use & Statistical & Prefectures & 1965-2013 & 2nd National Water Resources Assessment Program \cite{zhou2020}\\
    2. GDP & Statistical & Province & 1949-2019 & Wind database \\
    3. Streamflow withdrawals & Statistical & Watershed & 2003-2019 & Yearbooks \url{http://www.yrcc.gov.cn/other/hhgb/} \\
    4. Reservoirs & Hydrological & Location & 1949-2015 & Publication \cite{wang2019c} \\
    5. Measured runoff & Hydrological & Location & 1949-2019 & Measured data \cite{wang2019c,wang2016e} \\
    6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommission2013} \\
    7. History of YRCC & Political & Documents & 1949-2002 & YRCC \cite{yellowriverarchives2004} \\
    8. YRB Events & Political & Documents & 1949-2015 & YRCC: \url{http://www.yrcc.gov.cn/hhyl/hhjs/} \\
    \botrule
    \end{tabular}}
    \end{minipage}
    \end{center}
    \end{table*}

    %% 表格
\begin{table*}
    \centering
    \small
    \caption{Policies and regulations above YRB level which affected the whole basin in water utilization}\label{tab:policies}
    \begin{minipage}{\linewidth}
    \resizebox{\linewidth}{!}{
    \begin{tabular}{p{0.6\linewidth}rp{0.35\linewidth}}
        Name & Year & Agency \\
        \midrule
        1. Water Law of PRC & 1988 & National People's Congress of the PRC \\
        2. Water Law of PRC -revised 1 & 2009 & National People's Congress of the PRC \\
        3. Water Law of PRC -revised 2 & 2016 & National People's Congress of the PRC \\
        4. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
        5. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees -revised 1 & 2017 & State Council of the PRC \\
        6. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
        7. Yellow River water supply distribution scheme & 1987 & State Council of the PRC \\
        8. Measures for the Administration of Water Drawing Permits & 2008 & Ministry of Water Resources of the PRC \\
        9. Measures for the Administration of Water Drawing Permits -revised 1 & 2015 & Ministry of Water Resources of the PRC \\
        10. Measures for the Administration of Water Drawing Permits -revised 2 & 2017 & Ministry of Water Resources of the PRC \\
        11. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
        12. Annual distribution of available water supply of the Yellow River and mainstream water dispatching scheme & 1998 & Ministry of Water Resources of the PRC \\
        13. The Yellow River water dispatching management measures & 1998 & Ministry of Water Resources \\
        14. Measures for the Implementation of the Yellow River Water Rights Conversion Management & 2004 & Ministry of Water Resources \\
        15. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
        16. Measures for the implementation of the water drawing Permit system & 1993 \\ State Council of the PRC \\
        17. Measures for the demonstration and management of water resources in construction projects & 2002 & Ministry of Water Resources of the PRC \\
        18. Implementation Opinions on the Reform of Water Conservancy Project Management System & 2006 & State Council of the PRC \\
        \bottomrule
    \end{tabular}}

    \footnotesize[1]{If a policy was proposed by multiple legacies, we only show the highest one.}
    \end{minipage}
\end{table*}

### 2022-05-29 paper/main/01_introduction.tex
fix(paper-manuscript-(introduction,-discussion)): rectified according to Cumming's comments (email)
BREAKING CHANGE:

@@
 \label{Intro.}
-Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting the development and human well-being
+Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being
 \cite{gleeson2020a,gleeson2020b}.
-As an integral part of earth system governance, water governance requires a deep understanding of changes in the complex relationships between humans and water
+As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water
 \cite{ahlstrom2021,biermann2012,steffen2020}.
-Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers
 \cite{sivapalan2012,qin2014,abbott2019}.
-Facing this transition, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
+Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance
 \cite{best2019,dibaldassarre2019}.
@@
 Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}.
-For populated large river basins, missing governance means missing sustainability, and a first critical step in understanding the transitions with successful water governance is identifying the different regimes \cite{kjellen2015, grafton2013}.
-Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations) as a stable state in structures and functions
+For populated large river basins, missing governance means missing sustainability.
+A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
+Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
 \cite{falkenmark2021,bressers2013,loch2020}.
-Therefore, regime shifts sometimes lead to new water governance challenges as both signals and consequences of substantive changes in human-water systems.
-The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).
+Therefore, regime shifts sometimes lead to new water governance challenges; they are both causes and consequences of substantive changes in human-water systems.
 
-Governance is essentially about ``who gets what, when and how''\cite{lasswell2018}.
-The United Nations Development Programme (UNDP) thus suggested that three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How does water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
+The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes represents a challenge for efforts to enhance the sustainability of water resource use.
+Filling this gap, which is the aim of this paper, is important for the appropriate alignment of human and water systems (Figure~\ref{fig:framework}).
+Water governance is essentially about ``who gets water, when and how''\cite{lasswell2018}.
+The United Nations Development Programme (UNDP) has thus suggested that three key dimensions of water use are decided by water governance directly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
 \cite{undpwatergovernancefacility2016}.
@@
 \cite{liu2017,florke2018,jaeger2019}.
-Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
+Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematic regulation
 \cite{schmandt2021,speed2013}.
-Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.
+Although regime shifts in water governance are related to substantive changes in any of the three dimensions, considering them separately can lead to systematic failure.
 
-The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability
+The Yellow River Basin (YRB), which contains the fifth-largest river in the world, needs integrated water governance because of geological and human history
 \cite{mostern2021}.
-Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled by thousands of years of high sediment loads
+Since the 1960s, conservation measures and the construction of regulation reservoirs and levees have contained the issues troubled by thousands of years of high sediment loads
 \cite{wang2016e,song2020a}.
-However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
+Decreased streamflows and water over-use in more recent times led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
 \cite{wang2019c}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how'' is always an open question for sustainable development
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors; the question of ``who gets water, when and how?'' remains open for sustainable development
 \cite{wohlfart2016a}.
-Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide \cite{nickum2021}.
+Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide \cite{nickum2021}.
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.
@@
 % 最后总结出一般性框架
-Finally, we propose a general regime transition schema as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
+Finally, we propose a general regime transition schema that offers practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
 

### 2022-05-29 paper/main/03_results.tex
fix(paper-manuscript-(introduction,-discussion)): rectified according to Cumming's comments (email)
BREAKING CHANGE:

@@
 		Causes of water governance regime shifts in the YRB.
-		% environmental change, economic growth and efficiency changes, social transformation, and governance policies.
 		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the irrigated area, the green dot line).
@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-		% Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing floodwater discharge and water regulation.
-These named reservoirs are significant for the whole basin rather than local development.
 		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Appendix} Table~\ref{tab:policies}).
@@
 % 进一步挖掘IWGI变化的根本原因，
-The underlying causes of changes in the IWGI are associated with various factors but are different in the two regime shifts.
+The underlying causes of changes in the IWGI are different in the two regime shifts.
 % 灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
@@
 Then, the efficiency of water use changed obviously from P2 to P3.
-Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
+Not only did irrigated areas continue to expand slowly in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
 Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
@@
 Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, $p<0.01$, see Figure~\ref{fig:Causes}C)).
-Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
+Under the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
 In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).

### 2022-05-29 paper/main/04_discussion.tex
fix(paper-manuscript-(introduction,-discussion)): rectified according to Cumming's comments (email)
BREAKING CHANGE:

@@
 \cite{best2019,best2020}.
-As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships \cite{diaz2019}.
-The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
+As tele-coupling raises additional water governance challenges in an increasingly tightly-connected world, regime shifts in water governance align with different human-water relationships \cite{diaz2019}.
+The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
 It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime \cite{reyers2018}.
@@
 During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
-As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation
+As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation
 \cite{zhou2020}.
-The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical \cite{loch2020}.
-As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity \cite{wang2019c}.
-In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
+The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical \cite{loch2020}.
+Use of over 80\% of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity \cite{wang2019c}.
+In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis
 \cite{wohlfart2016a}.
 
-The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after the ``reform and opening-up''.
+The start of the governance transforming regime (P2: 1979-2001) coincided with rising competition for water use after the ``reform and opening-up''.
 % 正如理论预测的那样
-The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity \cite{loch2020}.
+The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity \cite{loch2020}.
 % 作为制度转变的先行者
-Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
+As a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime.
+These included, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme; and the creation of a preliminary cross-boundary water transfer plan
 \cite{wang2019a,long2020,nickum2021}.
 % 因此，1999年黄河的最后一次枯竭
-Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance \cite{wang2019a}.
+Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance \cite{wang2019a}.
 
-When it came to an adaptation-oriented regime (P3: 2002-2013), drastically shifting in societies adapted to the stable high water stress.
-Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
+The ensuing adaptation-oriented regime (P3: 2002-2013) involved a significant shift in society to adapt to stable high water stress.
+Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply
 \cite{dalin2015,song2022}.
-Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example \cite{wang2019a}.
-Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
+Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example \cite{wang2019a}.
+Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance
 \cite{konar2019}.
@@
 % 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
-In general, water governance of the YRB is among the most prominent example in the general transition of hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
-In the analogy at a global scale, the resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
+In general, water governance of the YRB is among the most prominent example in the general transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
+With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
+In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
 \cite{allan2019,speed2013,liu2012a}.
-Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and maybe in urgent need of novel flexible, efficient sociopolitical governance structures
+Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
 \cite{unep-dhi2016,mirumachi2015}.
@@
 %* limitations & direction
-One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
+One of the main limitations in the approach is the lack of long-term data worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI more widely.
 However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
-Therefore, we suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in holistically understanding the transition of governance regimes.
-In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
+Choices of indicators for different dimensions can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
+In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seems likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems
 \cite{cumming2018,cumming2014,jaeger2019}.
-Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
+Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional and planetary boundaries where human-water systems may collapse
 \cite{gleeson2020, wang-erlandsson2022}.

### 2022-05-29 paper/main/manuscript.tex
fix(paper-manuscript-(introduction,-discussion)): rectified according to Cumming's comments (email)
BREAKING CHANGE:

@@
 \abstract{
-    In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
-Therefore, identifying regime changes is critical to understanding the transition and guiding sustainability in water governance.
-We combined three main dimensions -stress, purpose and allocation- to develop a quantitative Integrated Water Governance Index (IWGI) to detect water governance regimes at a basin scale.
-Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between massive supply, transformation governance, and adaptation-oriented regimes.
-In the YRB, the regime shifts' underlying causes were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.
-The IWGI offers a comprehensive and straightforward approach to linking the water governance regimes to the following challenges in sustainability, along with the hydrosocial transition.
+    In most large river basins, water governance determine who gets water, when, and how.
+Shifts in water governance regimes from natural to social-ecological or ``hydrosocial'' carry profound implications for human wellbeing; identifying regime changes in water governance is critical to navigating social-ecological transitions and guiding sustainability.
+We characterised water governance along the three main dimensions - stress, purpose and allocation - to develop a quantitative Integrated Water Governance Index (IWGI) at a basin scale.
+Applying the IWGI to the rapidly-changing Yellow River Basin (YRB) in China clarifies shifts in water governance between massive supply, transformation governance, and adaptation-oriented regimes.
+In the YRB, the underlying causes of regime shifts were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.
+The IWGI offers a comprehensive and straightforward approach that links the water governance regimes to sustainability, providing useful insights into hydrosocial transitions.
 }

### 2022-05-30 paper/main/01_introduction.tex
fix: delete unnecessary files, move files to correct folder

@@
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}.
-For populated large river basins, missing governance means missing sustainability.
-A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
-Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
-\cite{falkenmark2021,bressers2013,loch2020}.
-Therefore, regime shifts sometimes lead to new water governance challenges; they are both causes and consequences of substantive changes in human-water systems.
-
-The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes represents a challenge for efforts to enhance the sustainability of water resource use.
-Filling this gap, which is the aim of this paper, is important for the appropriate alignment of human and water systems (Figure~\ref{fig:framework}).
-Water governance is essentially about ``who gets water, when and how''\cite{lasswell2018}.
-The United Nations Development Programme (UNDP) has thus suggested that three key dimensions of water use are decided by water governance directly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
+Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
 \cite{undpwatergovernancefacility2016}.
@@
 \cite{schmandt2021,speed2013}.
-Although regime shifts in water governance are related to substantive changes in any of the three dimensions, considering them separately can lead to systematic failure.
+Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.
 
-The Yellow River Basin (YRB), which contains the fifth-largest river in the world, needs integrated water governance because of geological and human history
-\cite{mostern2021}.
-Since the 1960s, conservation measures and the construction of regulation reservoirs and levees have contained the issues troubled by thousands of years of high sediment loads
+A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
+Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
+\cite{falkenmark2021,bressers2013,loch2020}.
+For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
+However, the lack of a comprehensive but straightforward approach to identifying changes in water governance regimes represents a challenge for efforts to enhance the sustainability of water resource use.
+Filling this gap, which is the aim of this paper, is essential for the appropriate alignment of human and water systems.
+
+The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history
+\cite{mostern2021,best2019}.
+Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads
 \cite{wang2016e,song2020a}.
-Decreased streamflows and water over-use in more recent times led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
+However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic
 \cite{wang2019c}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors; the question of ``who gets water, when and how?'' remains open for sustainable development
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors
 \cite{wohlfart2016a}.
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, we use the three core dimensions (stress, purpose and allocation) and corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
+Here, we depict the three aspects of water governance (stress, purpose and allocation) with corresponding indicators (see methods) and thus develop an Integrated Water Governance Index (IWGI) by equally weighting them, to indicate results from water governance (see Figure~\ref{fig:framework}~B).
 % 使用案例研究
-Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated water governance regimes in a comprehensive but straightforward way.
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how IWGI helps detect and describe complicated water governance regimes comprehensively but straightforwardly.
 Following synthetic analyses of the changes in water demand, supply, economic outcomes, and institutions, we interpret the leading causes of the regime shifts.
 % 最后总结出一般性框架
-Finally, we propose a general regime transition schema that offers practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
+Finally, we propose a general regime transition schema that offers a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
 
@@
 	\caption{
-		Identifying the water governance regimes in transitions of a hydrosocial cycle.
-		\textbf{A.} Water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing.
-(1) ``stress'' of water shifts between scarcity and abundance; (2) weighting ``purpose'' of water between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
-		\textbf{B.} Along with a transition in hydrosocial water cycle, water governance shifts in line with the three dimensions.
-Combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
+		Framework for identifying the water governance regimes in transitions of a hydrosocial cycle.
+Water stress (S), purpose of water services (P) and water allocation (A) are three aspects to be considered (\textbf{A.}).
+Along hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance, such as: construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2), water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
+		Therefore, the methonology is to combine three aspects' corresponding indicator, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
 		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.

### 2022-05-30 paper/main/02_methods.tex
fix: delete unnecessary files, move files to correct folder

@@
 To develop a comprehensive and straightforward approach to identifying water governance regimes.
-First, we constructed the Integrated Water Governance Index (IWGI) based on three dimensions (Stress, Purpose, and Allocation, see Figure~\ref{fig:framework}).
+First, we constructed the Integrated Water Governance Index (IWGI) based on three aspects (Stress, Purpose, and Allocation, see Figure~\ref{fig:framework}).
 Then, we analyzed the changes in the IWGI from 1965 to 2013 using change point detection methods.
@@
 	% 将三者合一起，即：
-	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three core dimensions (Stress, Purpose, and Allocation) of water governance.
+	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance.
 Each dimension keeps two directions, and we assumed the hydrosocial cycle aligns with one of them, respectively:
@@
 
-	We selected an indicator ($I_x$, $x=S$, $P$ or $A$, corresponding to stress, purpose, and allocation, respectively) to quantify the dimensions effectively.
+	We selected an indicator ($I_x$, $x=S$, $P$, or $A$, corresponding to stress, purpose, and allocation, respectively) to quantify the aspects effectively.
 Then, the above equation was transformed into a natural logarithm to facilitate calculation:
@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress \cite{qin2019}.
-This metric considers management measures (such as the construction of reservoirs) and the impact of changes in the structure of water use on the evaluation of water scarcity.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress \cite{qin2019}.
+This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
 Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Appendix}\ref{secA1}).
@@
 
-	In this study, we consider water for livestock, rural or urban domestic and water for agriculture as provisioning water. Others are non-provisioning water uses, such as energy water use.
+	In this study, we consider livestock water use, rural and urban domestic water use, and agricultural water use as provisioning water because they directly service for survival.
+Others are non-provisioning: services and industrial water use because they mainly service the economy.
 

### 2022-05-30 paper/main/03_results.tex
fix: delete unnecessary files, move files to correct folder

@@
 % 这一节主要展示IWGI的变化趋势和WUR的划分
-Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three dimensions (Figure~\ref{fig:IWGI}A).
+Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
 % 第一阶段
@@
 % 第三阶段
-During the third period (P3, 1995-2013), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
+During the third period (P3, 1995-2013), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
 % Overall
-Taken together, the overall features of the three dimensions in different periods are relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
-The results suggest three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).
+Taken together, the overall features of the three aspects in different periods are relative to a directional change in the combination of three aspects (Figure~\ref{fig:IWGI}C).
 
@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Appendix} Figure~\ref{fig:reservoirs}).
+As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Appendix} Figure~\ref{fig:reservoirs}).
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
-Entering the transformation governance regime (P2), however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes} A and B).
+Ensuing the P2, however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes}~A and B).
 % 水分利用效率由P2变化到P3。
 Then, the efficiency of water use changed obviously from P2 to P3.
-Not only did irrigated areas continue to expand slowly in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
-Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
-As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the adaptation oriented regime (Figure~\ref{fig:IWGI}A).
+Not only did irrigated areas continue to expand slowly during the P3 (Figure\ref{fig:Causes}~A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}~B).
+Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}~A and Figure~\ref{fig:Causes}~B).
+As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the P3 (Figure~\ref{fig:IWGI}A).
 
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Environmental context, social transformation and policies played roles in all three regimes.
+Environmental context, social transformation, and policies played roles in all three periods.
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
-Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, $p<0.01$, see Figure~\ref{fig:Causes}C)).
-Under the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
-In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
+Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
+Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
+During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
 The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-05-30 paper/main/04_discussion.tex
fix: delete unnecessary files, move files to correct folder

@@
 	\caption{
-		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red pathways.
-		\textbf{A.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate the water stress.
+		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
+		\textbf{A.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate water stress.
 		\textbf{B.} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
 		Thus, \textbf{C.
-the hydrosocial water cycle transition} correlates with the water governance regime shifts (in the YRB, they are massive supply regime, transformation governance regime, and adaptation oriented regime).
+the hydrosocial water cycle transition} correlates with the water governance regime shifts.
 The transformation governance regime shift occurs following the water deficit, with the rapid growth of adaptive capacity.
@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013) (Figure~\ref{fig:IWGI}).
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: 1965-1978), a governance transforming command (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013) (Figure~\ref{fig:IWGI}).
 During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
@@
 The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical \cite{loch2020}.
-Use of over 80\% of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity \cite{wang2019c}.
+Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity \cite{wang2019c}.
 In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis
@@
 % 作为制度转变的先行者
-As a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime.
-These included, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme; and the creation of a preliminary cross-boundary water transfer plan
+As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
+These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan
 \cite{wang2019a,long2020,nickum2021}.
@@
 
-The ensuing adaptation-oriented regime (P3: 2002-2013) involved a significant shift in society to adapt to stable high water stress.
+The ensuing adaptation-oriented regime (P3: 2002-2013) involved a significant societal shift in adapting to stable high water stress.
 Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply
@@
 % 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
-In general, water governance of the YRB is among the most prominent example in the general transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
+In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
+With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
 In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
@@
 One of the main limitations in the approach is the lack of long-term data worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI more widely.
-However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
-Choices of indicators for different dimensions can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
-In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seems likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems
+However, we propose that all water governance issues result in changing ``who gets water, when and how'', so monitoring water stress, purposes of water services, and water allocation patterns do help.
+Choices of indicators for different aspects can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
+In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems
 \cite{cumming2018,cumming2014,jaeger2019}.
-Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional and planetary boundaries where human-water systems may collapse
+Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional, and planetary boundaries where human-water systems may collapse
 \cite{gleeson2020, wang-erlandsson2022}.

### 2022-05-30 paper/main/05_conclusion.tex
docs(introduction): openning sentence, compile authors info
fix: delete unnecessary files, move files to correct folder

@@
-Three dimensions of water governance change along with the hydrosocial cycle transition: water stress, services purpose, and water allocation, affecting ``who gets water, when and how''.
+Focusing on ``who gets water, when and how'', three aspects of water governance change along with the hydrosocial cycle transition: water stress, water services purpose, and water allocation.
 We developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance by integrating them.
-Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
+Applying the IWGI to a rapidly-changing large river basin (the Yellow River Basin, China), we interpret how water governance shifts between three regimes over half a century.
 Our approach quantitatively identifies the general schema for water governance regimes in the YRB, in line with previous theoretical analysis with a representative transition process.

### 2022-05-30 paper/main/manuscript.tex
fix: delete unnecessary files, move files to correct folder

@@
 \newtheorem{definition}{Definition}%
-
+% \usepackage{tikz}
+% \newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
+%     circle (.5em) node {\makebox[1em][c]{\small #1}};}}
 \raggedbottom
@@
 
-\author[1,2]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
+\author[1]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
 
-\author[1,2]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
+\author[1]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
 % \equalcont{These authors contributed equally to this work.}
 
-\author[1,2]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
+\author[1]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
 % \equalcont{These authors contributed equally to this work.}
-\author[3]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
-\author[4]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
-\author*[1,2]{\fnm{Bojie} \sur{Fu}}\email{fubj@bnu.edu.cn}
+\author[2]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
+\author[3]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
+\author[4]{\fnm{Yue} \sur{Qin}}\email{qinyue@pku.edu.cn}
+\author[5]{\fnm{Xilin} \sur{Wu}}\email{wuxilin20@mails.ucas.ac.cn}
+\author*[1,5]{\fnm{Bojie} \sur{Fu}}\email{bfu@rcees.ac.cn}
 
 \affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\street{Xinjiekouwai Street}, \city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-
-\affil[2]{\orgdiv{nstitute of Land Surface System and Sustainability}, \orgname{Beijing Normal University}, \orgaddress{\street{Xinjiekouwai Street}, \city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 
@@
 
+\affil[5]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+
+\affil[6]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 %%==================================%%
@@
 Shifts in water governance regimes from natural to social-ecological or ``hydrosocial'' carry profound implications for human wellbeing; identifying regime changes in water governance is critical to navigating social-ecological transitions and guiding sustainability.
-We characterised water governance along the three main dimensions - stress, purpose and allocation - to develop a quantitative Integrated Water Governance Index (IWGI) at a basin scale.
+We characterised water governance along the three main aspects - stress, purpose and allocation - to develop a quantitative Integrated Water Governance Index (IWGI) at a basin scale.
 Applying the IWGI to the rapidly-changing Yellow River Basin (YRB) in China clarifies shifts in water governance between massive supply, transformation governance, and adaptation-oriented regimes.

### 2022-05-30 paper/sup/supplementary_information.tex
fix: delete unnecessary files, move files to correct folder

@@
 
-Our Integrated Water Governance Index offers an accessible and operational way of measuring regime changes based on the transparent underlying assumptions that water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three dimensions below (see Figure 1 and SI 322 Appendix Methods S4 for details)
+Our Integrated Water Governance Index offers an accessible and operational way of measuring regime changes based on the transparent underlying assumptions that water resources governance system is closely related to a transformation towards a hydrosocial water cycle in the three aspects below (see Figure 1 and SI 322 Appendix Methods S4 for details)
 \cite{abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020,steffenTrajectoriesEarthSystem2018}.
@@
 % 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
-The Integrated Water Governance Index (IWGI) of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
+The Integrated Water Governance Index (IWGI) of water resources utilization considers the three basic aspects of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
 % 为了对这些维度进行量化，我们发现或发明了三个与指示其变化趋势相对应的指标:SFV指数、非供应共享和配置熵指标。
-In order for these dimensions to be quantified, we used a total of three sub-indicators corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.
+In order for these aspects to be quantified, we used a total of three sub-indicators corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.
 
@@
 
-    $I_C$, an indicator to measure the configuration dimensions of water resources utilization, is composed of three parts:
+    $I_C$, an indicator to measure the allocation aspect of water resources utilization, is composed of three parts:
 
@@
 % 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWGI，我们对IWGI的断点检测结果都相同。
-No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWGI breakpoints are the same.
+No matter which of the above standardized methods we use in combining the indicators of the three aspects, and our detection results for IWGI breakpoints are the same.
 
@@
 % 	\centering
-% 	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
+% 	\includegraphics[width=\linewidth]{../../figures/main/aspects.pdf}
 % 	\caption{
-% 		Changes in different dimensions of water resources utilization regimes and their main contributors.
+% 		Changes in different aspects of water resources utilization regimes and their main contributors.
 % 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
@@
 % 		}
-% 	\label{fig:dimensions}
+% 	\label{fig:aspects}
 % \end{figure}

### 2022-05-31 paper/main/manuscript.tex
fix: fix author-affli number

@@
 
-\affil[3]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
+\affil[2]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
 
-\affil[4]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
+\affil[3]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
 
-\affil[5]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+\affil[4]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 
-\affil[6]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+\affil[5]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 %%==================================%%

### 2022-05-31 paper/main/manuscript.tex
fix: abstract grammar

@@
 \abstract{
-    In most large river basins, water governance determine who gets water, when, and how.
+    Water governance determines who gets water, when, and how in most large river basins.
 Shifts in water governance regimes from natural to social-ecological or ``hydrosocial'' carry profound implications for human wellbeing; identifying regime changes in water governance is critical to navigating social-ecological transitions and guiding sustainability.
-We characterised water governance along the three main aspects - stress, purpose and allocation - to develop a quantitative Integrated Water Governance Index (IWGI) at a basin scale.
+We characterized water governance along with the three main aspects - stress, purpose, and allocation - to develop a quantitative Integrated Water Governance Index (IWGI) at a basin scale.
 Applying the IWGI to the rapidly-changing Yellow River Basin (YRB) in China clarifies shifts in water governance between massive supply, transformation governance, and adaptation-oriented regimes.
-In the YRB, the underlying causes of regime shifts were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.
-The IWGI offers a comprehensive and straightforward approach that links the water governance regimes to sustainability, providing useful insights into hydrosocial transitions.
+In the YRB, the underlying causes of regime shifts were increasing water supply and demand before the governance transformation and re-allocation and regulation after the change.
+The IWGI offers a comprehensive and straightforward approach to linking water governance regimes to sustainability, providing valuable insights into hydrosocial transitions.
 }

### 2022-05-31 paper/letter/cover_letter.tex
fix(cover-letter): add cover letter text, fix figure1's caption

\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\moderncvstyle{classic}
\moderncvcolor{green} % Bullet point color

% Page margins
\usepackage[scale=0.8]{geometry} % Page margins

% Your Information, please revise
\name{Shuang}{Song}
\address{Haidian District, Beijing, China}{No.19, Xinjiekouwai St.}
\phone[mobile]{+86 185 0068 5922}
\email{songshgeo@mail.bnu.edu.cn}

\begin{document}

% Insert Olin Logo
\begin{minipage}[t]{\textwidth}
\includegraphics[width=0.40\textwidth]{bnu}
\end{minipage}

\recipient{Dear Editor in Chief,}{}
\opening{\vspace*{-2em}}
\closing{Sincerely,}{\vspace*{-2em}}
\enclosure[Enclosures]{Main manuscript, Appendix}
\makelettertitle

I am pleased to submit an original research article entitled ``Identifying regime transitions for water governance at a basin scale'' for consideration for publication in \textit{Nature Water} as an \textit{Analysis}.

Water governance determines ``who gets water, when, and how'' in most large river basins; missing governance means missing sustainability. However, the lack of a comprehensive but straightforward approach to identifying the changes in water governance presents a challenge for efforts to underpin it. Therefore, we choose indicators for the corresponding aspects (water stress, water services purpose, and water allocation) and combine them into an integrated water governance index (IWGI) to analyze long-term changes in a large river basin.

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.9\textwidth]{../../figures/main/framework.png}
% 	\caption{
% 		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI). Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}). Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance. For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
% 		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
% 	}
% 	\label{fig:framework}
% \end{figure}

Applying the IWGI to the rapidly-changing Yellow River Basin (YRB) in China clarifies shifts in water governance between massive supply, transformation governance, and adaptation-oriented regimes. After interpreting these regimes with underlying causes, we propose a potentially widespread transition schema in a human-dominated hydrosocial cycle.

Our analysis approach links river basin governance with transitions of hydrosocial water cycles and offers valuable sustainability guidelines for big river basins worldwide. Therefore, we believe that this manuscript is appropriate for publication by \textit{Nature Water} because it tightly echoes the aims \& scope of water governance.

This manuscript has not been published and is not under consideration for publication elsewhere, and all the authors have read and approved the manuscript. The manuscript includes the main body of text with $4176$ words and $4$ figures; the three-section appendix has $3$ supporting figures and $2$ supporting tables. We have no conflicts of interest to disclose. If you feel that the manuscript is appropriate for your journal, we suggest the following reviewers:

[list reviewers and contact info, if requested by the journal]

\vspace{0.5cm}

I appreciate your consideration!

\vspace{0.5cm}

Sincerely,

\textbf{Bojie Fu} (On behalf of the author team)

%\begin{minipage}[t]{\textwidth}
%	\includegraphics[height=1cm]{signature.jpeg}
%\end{minipage}

State Key Laboratory of Earth Surface Processes and Resource Ecology,

Faculty of Geographical Science,

Beijing Normal University,

Beijing 100875, China

Email: bfu@rcees.ac.cn

\end{document}

### 2022-05-31 paper/main/01_introduction.tex
fix(cover-letter): add cover letter text, fix figure1's caption

@@
 	\caption{
-		Framework for identifying the water governance regimes in transitions of a hydrosocial cycle.
-Water stress (S), purpose of water services (P) and water allocation (A) are three aspects to be considered (\textbf{A.}).
-Along hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance, such as: construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2), water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
-		Therefore, the methonology is to combine three aspects' corresponding indicator, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
-		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
+		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
+Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
+Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
+For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
+		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
 	}

### 2022-05-31 paper/letter/cover_letter.tex
docs: cover letter update refrees

@@
 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.9\textwidth]{../../figures/main/framework.png}
-% 	\caption{
-% 		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
-Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
-Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
-For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
-% 		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
-% 	}
-% 	\label{fig:framework}
-% \end{figure}
-
 Applying the IWGI to the rapidly-changing Yellow River Basin (YRB) in China clarifies shifts in water governance between massive supply, transformation governance, and adaptation-oriented regimes.
 After interpreting these regimes with underlying causes, we propose a potentially widespread transition schema in a human-dominated hydrosocial cycle.
-
 Our analysis approach links river basin governance with transitions of hydrosocial water cycles and offers valuable sustainability guidelines for big river basins worldwide.
@@
 The manuscript includes the main body of text with $4176$ words and $4$ figures; the three-section appendix has $3$ supporting figures and $2$ supporting tables.
-We have no conflicts of interest to disclose.
+Furthermore, we declare no conflicts of interest to disclose.
+
 If you feel that the manuscript is appropriate for your journal, we suggest the following reviewers:
 
-[list reviewers and contact info, if requested by the journal]
+\begin{itemize}
+\item Prof. Fuqiang Tian (Tsinghua University); Email: tianfq@tsinghua.edu.cn; Dr. Tian focuses on socio-hydrology and is familiar with the case basin in this study.
+\item Prof.
+Tom Gleeson (University of Victoria); Email: tgleeson@uvic.ca; Dr.
+Gleeson cares about the significant changes during the transformation toward a human-interrupted world, especially the hydrology system.
+\item Prof. Murugesu Sivapalan (University of Illinois, Urbana-Champaign); Email: sivapala@illinois.edu; Dr. Sivapalan focuses on socio-hydrology, linking water and human society with basin studies.
 
-\vspace{0.5cm}
+\vspace{0.3cm}
 
@@
 
-\vspace{0.5cm}
+\vspace{0.3cm}
 

### 2022-07-12 paper/main/manuscript.tex
fix: fix abstract
fix(mansucript.tex,-index_cause.ipynb): v-5.3.6: fix superscript and determine
Cumming suggests: first line should be determine, rather than determines
feat: compiled by 1.5 line-width, changed page edge

@@
 % \documentclass[default]{sn-jnl}% Default
-\documentclass[default,iicol,lineno]{sn-jnl}% Default with double column layout
+\documentclass[default, sn-standardnature]{sn-jnl}% Default with double column layout
 
@@
 
-\jyear{2021}%
+\jyear{2022}%
+\newgeometry{left=2cm, right=2cm}
+\linespread{1.5}
 
@@
 \abstract{
-    Water governance determines who gets water, when, and how in most large river basins.
+    Water governance determine ``who gets water, when, and how'' in most large river basins.
 Shifts in water governance regimes from natural to social-ecological or ``hydrosocial'' carry profound implications for human wellbeing; identifying regime changes in water governance is critical to navigating social-ecological transitions and guiding sustainability.

### 2022-07-12 paper/letter/cover_letter.tex
fix(cover-letter): fix the address into Fu's
feat: appendix separated version

@@
 % Your Information, please revise
-\name{Shuang}{Song}
+\name{Bojie}{Fu}
 \address{Haidian District, Beijing, China}{No.19, Xinjiekouwai St.}
-\phone[mobile]{+86 185 0068 5922}
-\email{songshgeo@mail.bnu.edu.cn}
+\phone[mobile]{+86 139 1062 3747}
+\email{bfu@rcees.ac.cn}
 
@@
 
-I am pleased to submit an original research article entitled ``Identifying regime transitions for water governance at a basin scale'' for consideration for publication in \textit{Nature Water} as an \textit{Analysis}.
+I am pleased to submit an original research article entitled ``Identifying regime transitions for water governance at a basin scale'' for consideration for publication in \textit{People and Nature} as a \textit{Research Article}.
 
@@
 Our analysis approach links river basin governance with transitions of hydrosocial water cycles and offers valuable sustainability guidelines for big river basins worldwide.
-Therefore, we believe that this manuscript is appropriate for publication by \textit{Nature Water} because it tightly echoes the aims \& scope of water governance.
+Therefore, we believe that this manuscript is appropriate for publication by \textit{People and Nature} because it tightly echoes the aims \& scope of water governance.
 

### 2022-07-12 paper/sup/supplementary_information.tex
feat: appendix separated version

--- 2022-04-22 paper/sup/supplementary_information.tex
@@
-\documentclass[9pt,twoside,lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
+\documentclass[default, sn-standardnature]{sn-jnl}% Default with double column layout
 
-\templatetype{pnassupportinginfo}
+%%%% Standard Packages
+%%<additional latex packages if required can be included here>
+%%%%
 
-\title{Identifying regime transitions for water governance at a basin scale}
-\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Graeme S. Cumming, Bojie Fu (complete author list)}
-\correspondingauthor{Bojie Fu.\\E-mail: bfu@rcees.ac.cn}
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published
+%%%%  by Springer Nature. The guidance has been prepared in partnership with
+%%%%  production teams to conform to Springer Nature technical requirements.
+%%%%  Editorial and presentation requirements differ among journal portfolios and
+%%%%  research disciplines. You may find sections in this template are irrelevant
+%%%%  to your work and are empowered to omit any such section if allowed by the
+%%%%  journal you intend to submit to. The submission guidelines and policies
+%%%%  of the journal take precedence. A detailed User Manual is available in the
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
 
+\jyear{2022}%
+\newgeometry{left=2cm, right=2cm}
+\linespread{1.5}
+
+%% as per the requirement new theorem styles can be included as shown below
+\theoremstyle{thmstyleone}%
+\newtheorem{theorem}{Theorem}%  meant for continuous numbers
+%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+\newtheorem{proposition}[theorem]{Proposition}%
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+\theoremstyle{thmstyletwo}%
+\newtheorem{example}{Example}%
+\newtheorem{remark}{Remark}%
+
+\theoremstyle{thmstylethree}%
+\newtheorem{definition}{Definition}%
+% \usepackage{tikz}
+% \newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
+%     circle (.5em) node {\makebox[1em][c]{\small #1}};}}
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
+%! path of figs
+
+\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
 \begin{document}
+
+\title{Supporting Materials of ``Identifying regime transitions for water governance at a basin scale''}
+
+%%=============================================================%%
+%% Prefix	-> \pfx{Dr}
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% NatureName	-> \tanm{Poet Laureate} -> Title after name
+%% Degrees	-> \dgr{MSc, PhD}
+%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
+%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author[1]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
+
+\author[1]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
+% \equalcont{These authors contributed equally to this work.}
+
+\author[1]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
+% \equalcont{These authors contributed equally to this work.}
+\author[2]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
+\author[3]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
+\author[4]{\fnm{Yue} \sur{Qin}}\email{qinyue@pku.edu.cn}
+\author[5]{\fnm{Xilin} \sur{Wu}}\email{wuxilin20@mails.ucas.ac.cn}
+\author*[1,5]{\fnm{Bojie} \sur{Fu}}\email{bfu@rcees.ac.cn}
+
+\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\street{Xinjiekouwai Street}, \city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+
+\affil[2]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
+
+\affil[3]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
+
+\affil[4]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+
+\affil[5]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+%%==================================%%
+%% sample for unstructured abstract %%
+%%==================================%%
 
@@
 
-%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
-\SItext{This supplementary document consists of 5 \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables.
-% 在方法S1部分，我们介绍了我们的研究区域——黄河流域及其区域划分。
-In the section Methods S1, we introduced our study area, the Yellow River Basin, and its subdivisions of regions.
-% 在Methods S2部分，我们给出了使用的数据集的详细描述和分析它们的不确定性。
-In the section Methods S2, we give a detailed description of used datasets and analysis their uncertainties.
-For the section Methods S3, we introduced how to harmonize different datasets with various spatial and temporal scales.
-Then, the indicators corresponding to the IWGI are introduced in the section Methods S4.
-Finally, we proposed sensitivity analysis in the section Methods S5, to test the robustness of our results.}
+%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text
 
-% \subsection*{Brief description of Supplementary Information contents: }
-% Type or paste text here. This should be additional explanatory text such as an extended technical description of results, full details of mathematical models, etc.
+\section{YRB Regions}\label{secA1}
+\input{01_yrb.tex}
 
-% tag 研究区定义
-\newpage
-\section*{Methods S1. Definition of study area}
+\section{SFV-index}\label{secA2}
+\input{02_indicator.tex}
 
-\subsection*{Region divisions of Yellow River Basin}
-% 研究区为黄河流域(YRB，图S1-A)，是中国水资源开发最强烈、管理体制变化最剧烈的区域。
-The study area is the Yellow River Basin (YRB, see Fig. S1-A), which had experienced the most intense water exploitation and the most dramatic shifts of management regime in China.
-% 根据黄河水利委员会(水利部下属的流域一级行政政府)的研究，黄河的上、中、下游可由河流特征来区分。
-According to the Yellow River Conservancy Commission (YRCC), an administrative government directly under the Ministry of Water Resources at the basin level, the upper, middle and lower reaches of the Yellow River can be distinguished by the physics characteristic of river.
-% 但也有一种方案认为上游仅指人为干扰少、蓄水量大的河源区。
-However, there is another scheme suggesting that the upstream only refers to river source areas with little human disturbance and high water retention capacity.
-% 无论如何，由于本研究同时考虑了社会经济条件和自然条件，我们将上述两种方案结合起来，将黄河流域划分为四个区域，并以三个重要的水文控制站加以区分(见图S1-B)。
-Since the socio-economic and natural conditions were both considered in this study, we integrated the two schemes above and divided the Yellow River Basin into four regions, which can be distinguished by three important hydrological control stations (see Fig.
-S1-B).
-% 之前的研究也表明，当考虑流域的社会用水和自然条件时，这样的划分是有效的，因为区域之间具有很强的异质性(见图S1-C)。
-Previous studies have also shown that such a division is valid when both social water use and the natural conditions of the basin are considered, as the regions exhibit strong heterogeneity among themselves (see Fig.
-S1-C) \cite{wangYellowRiverWater2019}:
-
-\begin{itemize}
-    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region. The most ecology function here is water yield, as sparsely populated and less economically developed.
-    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region.
-However, the efficiency of irrigation are used to be very low.
-    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk.
-To reverse this situation, the grain for green project changed the water utilization here strikingly.
-    \item \textbf{Lower Region (LR):} With dense population and the traditional agricultural trajectory, lower region used to be the largest water use region.
-However, as the industrial transformation going, proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
-\end{itemize}
-
-% 总体来看，黄河流域在经济布局、水资源分布、用水量分布、人口分布等方面存在明显的区域差异(图S2)。
-In general, there are obvious inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (see Fig.
-S2).
-% 在这些根本差异的基础上，社会发展和流域管理继续影响和重塑它们的变化，使黄河流域成为世界上联系最密切、变化最剧烈的大流域。
-On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin.
-% 特别是水资源对长江流域的社会发展做出了不可替代的贡献。
-Specially, Water resources make an irreplaceable contribution to the development of society in the YRB.
-% 因此，作为分析人水关系演变的个案研究，具有典型性。
-Thus, as a case study for analysing the evolution of the human-water relationship, the YRB possesses typicality.
-
-% Secondly, their relationships have noticeably changed over the study period. In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig. S3-B).
-
-% 举农业案例作为说明
-%For an example, the agriculture, which occupied over 60\% of water consumptions, whose relationship with regional economic development has weakened, and there have been significant changes in water consumption per unit and total water consumption (see Fig.
-S).
-
-\subsection*{Changes brought from human activities on the YRB}
-Humans are constantly modifying the water cycle processes in the watersheds as society develops.
-\begin{itemize}
-    % 首先，长江三角洲自古以来就受到人类活动的强烈干预，近60年来变化最为剧烈。近60年来，在人类活动的影响下，黄河地表径流、输沙和人类用水格局均经历了多次变迁
-    \item Firstly, the YRB has been subject to strong intervention by human activities since ancient times, while the last 60 years have seen the most dramatic changes.
-Under human influence, the Yellow River's surface runoff, sediment transport, and human water consumption patterns have all undergone multiple regime shifts in the last 60 years
-    \cite{wu2020,wangReducedsedimenttransport2016}.
-    % 第二，人类活动对长江流域的景观产生了重大影响，这不仅改变了自然水循环，也改变了社会水循环。例如，“退耕还林”工程使长江铁路中部地区的景观发生了重大变化。随着易受侵蚀地区森林的增加，该地区的水利用模式和中下游的地表径流模式已发生根本改变。
-    \item Secondly, landscapes in the YRB have significantly altered by human activities, which can both change the natural and the social water cycle.
-For an example, ``grain for green'' project has produced a significant change of landscapes in the Middle Region (MR) of the YRB.
-With the addition forest in an erosion-prone area, water use patterns in the area and surface runoff patterns in the middle and lower reaches have been radically altered
-    \cite{wu2020}.
-    \item Thirdly, a series of management practices have promoted in order to manage the YRB.
-Since the establishment of the Yellow River Water Conservancy Commission, the agency has continued to reform and expand, eventually forming a basin management agency with unified coordination, scheduling and regulatory functions \cite{yellowriverconservancycommissionYellowRiverBasin2013}.
-    As results, the Ministry of Water Resources, the YRCC and other relevant agencies have issued a series of policies to carry out comprehensive river basin management under the guidance of national laws (see \textit{SI Appendix} Table S2).
-\end{itemize}
-% Historic and recent river basin management practices have strong impacts on water utilization.
-
-\subsection*{Historical Social transformations within the YRB}
-
-We list four main water-governance-related social transformations in Fig 5D of the main text, here are explanations:
-
-\begin{itemize}
-    \item \textbf{The Ethos of Conquering Nature (since 1958)} Conquering the natural movement, although the Yellow River basin was poor at that time, a collective spirit of ``man can conquer nature'' was formed.
-In addition to the construction of large-scale water conservancy projects represented by the Yellow River ``The Hong Qi Channel'', dramatic changes such as the ``Great Leap Forward'' movement and ``Large-scale production'' movement were also formed in this transformation.
-    \item \textbf{The Reform and Opening-up (since 1978).} Before the reform and opening up, the allocation of resources and production activities throughout China, including the Yellow River Basin, were led by the state.
-At this time, the market gradually began to play a role.
-    \item \textbf{The 87 Water Diversion Scheme (since 1987).} Before the water diversion Scheme, all local sectors had unlimited access to water resources.
-However, after the water diversion scheme was proposed, the Yellow River Basin formed social rules to control water use indicators from top to bottom, from the province to the urban area to all departments.
-    % 自2003年新一届领导人上任以来，包括水治理在内的环境问题已成为中国地方官员的关键考核指标。
-    \item \textbf{Environmental Regulation (since 2003).} Environmental issues, including water governance, have become key indicators for local officials in China since a new leader took office in 2003 with an emphasis on environmental issues
-    \cite{heWateringEnvironmentalRegulation2020}.
-\end{itemize}
-
-% tag 数据集介绍
-\newpage
-\section*{Methods S2. Detailed information on datasets}
-
-Multiple types of dataset were used in this study (see Table S1).
-\subsection*{Statistical datasets}
-% 使用了GDP数据，年鉴数据，还有从第二次水资源调查提取的数据
-For statistics, we used GDP data, water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhouDecelerationChinaHuman2020} and statistical yearbook data of YRB \url{http://www.yrcc.gov.cn/other/hhgb/}.
-GDP data from the China Macro data in the Wind database, which firstly aggregated from annual reports of the provinces.
-Water resources use dataset was published by Zhou et al.
-\cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in Prefectures level.
-This dataset was mainly extracted by 2nd National Water Resources Assessment Program launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details).
-Since then, the statistics from the survey using the same criteria have been supplemented and harmonized to the 2013 administrative divisions.
-
-The data covers a total of subcategories of water use under four broad categories: agriculture (IRR), industry (IND), urban (URB) and rural (RUR) water uses (see Zhou et al., for details \cite{zhouDecelerationChinahuman2020}).
-There is uncertainty at the county scale for each disaggregated water use sector, but because the data are corrected for statistical information using the water balance method, the data are adequate for the regional scale used in this study.
-
-Finally, in order to make a simple distinction the proportion of surface water and groundwater uses, we calculate a basin-scale ratio between the two types of water use, by yearbook data.
-
-\subsection*{Hydrological datasets}
-Reservoirs data and a measured runoff data were used in this study.
-% 水库数据集由Wang et al. 收集，其中介绍了1949年以来黄河流域新建的主要水库。
-The reservoir dataset were collected by Wang et al. \cite{wangYellowRiverWater2019}, which introduced includes the major new reservoirs built in the Yellow River Basin since 1949.
-% 其中，我们认为枢纽水库更为重要，因为它们直接参与流域水资源管理(由YRCC定义，见\url{http://www.yrcc.gov.cn/hhyl/sngc/})。
-Of these, we consider the hub-reservoirs to be more important, as they are directly involved in water resources management in the basin (defined by YRCC, see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
-% 年径流数据来源于水文站的测量。
-Annual runoff data derived from hydrological station measurements.
-
-\subsection*{Political datasets}
-%对于政策数据集，我们选取了《黄河流域综合规划》中流域级部门（如黄河水利委员会）级以上（如国家部委）颁布施行的与黄河流域有关的法律政策。此外，我们还从《黄河水利委员会组织沿革》一书中获取的黄河水利委员会作为黄河流域级管理单位的组织沿革情况，以反映流域级管理举措的实施情况。
-For the policy data set, we list the laws and policies related to the Yellow River basin promulgated and implemented by departments at (such as YRCC) and above (such as national institutions) the Basin's level  \cite{yellowriverconservancycommissionYellowRiverBasin2013}.
-% In addition, we also obtain the organizational evolution of the Yellow River Water Conservancy Commission as a watershed management unit from the book Organizational Evolution of the Yellow River Water Conservancy Commission to reflect the implementation of watershed management measures \cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
-
-% tag 数据处理
-\newpage
-\section*{Methods S3. Harmonization of datasets}
-% 由于我们的数据集来源广泛，且具有不同的空间尺度，我们需要在区域尺度（SR，UR，MR和DR）上对数据进行调和，根据数据的空间尺度有不同的处理方式。
-Due to the wide sources of our data set and the different spatial scales, we need to reconcile the datasets into the regional scale (SR, UR, MR and DR).
-\begin{itemize}
-    \item 1. Datasets at watersheds scales:
-    % 由于流域的分区由水文分区决定，所以水文年报数据和实测径流量数据都能直接根据其对应的水文站直接划分。
-        Due to the fact that the subdivision of a basin is determined by hydrological subdivision, hydrological annual data and measured runoff data can be directly divided according to their corresponding hydrological stations (see Figure S1 A and B).
-    \item 2. Perfecture:
-    % 在市县尺度下，我们分别计算了市县在不同流域分区中所占的面积，选取其中最大的区域，如果该面积占该县面积的95%以上，则认为该市属于该区域，即：
-        At the scale of perfecture, we calculate the area of each perfecture belongs to different regions respectively and select the largest one.
-If this area accounts for more than 95\% of the area of the county, the city is considered to belong to this region, that is:
-        $$ S_{ij} = MAX(S_ij / S_i)$$
-        where $i$ refers a certain perfecture and $j$ refers a region within YRB, i.e.
-SR, UR, MR, or DR.
-$S_i$ refers the area of perfect $i$, and $S_{ij}$ refers intersecting area between perfect $i$ and region $j$.
-        We define perfecture $i$ belongs to region $j$ if their intersecting area $S_{ij}$ over 95\% of $S_i$, i.e.:
-        $$ MAX(S_{ij}) > 0.95 * S_i $$
-    \item 3. Province:
-    % 在省域尺度的数据（即不同行业的GDP数据）更多用以定性描述，且不与县域尺度数据进行横向比例，因此数据的精度不再重要。我们采用了粗略的处理。即，根据不同区域包含的主要省份，判断该省的数据被融合进哪个区域。参考传统划分惯例，我们进行的划分是：
-    Data at the provincial scale (i.e., GDP data of different industries) are more used for qualitative description, so it is not important and necessary for down-scaling.
-Thus, according to the major provinces contained in different regions, we determine which region the data of that province is merged into by referring to the traditional division practice:
-    \begin{itemize}
-        \item SR: Qinghai Gansu and Sichuan,
-        \item UR: Ningxia and Neimeng,
-        \item MR: Shanxi and Shaanxi,
-        \item DR: Shandong, Hebei and Henan.
-    \end{itemize}
-\end{itemize}
-
-% 最后，当我们处理位置点数据（如水库修建位置数据时），根据其所在位置判断其所属省份，再按照省尺度的区域归类方式进行处理。经过上述处理，所有的数据都能很好的在区域尺度得到协调。
-Finally, when we process the location data (i.e., the location data of reservoir), we judge the province it belongs to according to its location, and then process it as provincial scale.
-
-After the above processing, all the data can be well coordinated at the regional scale.
-
-\newpage
-% 指数介绍
-\section*{Methods S4. Indicators of IWGI}
-% 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
-The Integrated Water Governance Index (IWGI) of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
-% 为了对这些维度进行量化，我们发现或发明了三个与指示其变化趋势相对应的指标:SFV指数、非供应共享和配置熵指标。
-In order for these dimensions to be quantified, we used a total of three sub-indicators corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.
-
-\subsection*{Indicator of supply: SFV-index}
-	%* 提出了很多的指标度量水压力，如水资源压力指数，水资源xxx等
-	How much water can be supplied in a basin?
-    Various metrics, therefore, proposed for description of stresses on water supply (e.g. water scarcity, water stresses index, scarcity-flexibility-variability index)
-    \cite{qinFlexibilityintensityglobal2019,bestAnthropogenicstressesworld2019,florke2018}.
-    Among of them, by taking changes of water flexibility and variability into account,	the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in developing perspective, which considered a valid metric of temporal changes in water stresses \cite{qinFlexibilityintensityglobal2019}.
-
-	To apply this method, we need to combine three metrics following:
-
-	First for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume, in year $j$ and region $i$:
-	$$ A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}} $$
-	Second for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.
-for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
-	$$ B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}} $$
-	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
-	$$ C_i = C1_i * (1 - C2_i) $$
-	$$ C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} $$
-	$$ C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} $$
-	$$ C2_{i} = 1, \ if RC >= R_{i, avg} $$
-	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
-
-	Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate $SFV$ index after normalizing them:
-	$$ V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3} $$
-	$$ a = \frac{1}{V_{max} - V_{min}}; $$
-	$$ b = \frac{1}{V_{min} - V_{max}} * V_{min} $$
-	$$ SFV = a * V + b $$
-
-\subsection*{Purpose: Non-provisioning share}
-    %* 从消耗水 到 利用水
-    % xxx等人通过考虑消费品中的水消耗提出了虚拟水理论，发现水资源作为粮食与消耗产品的供给是水资源的主要用途，且能够随着贸易发生流动。但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类社会发生着从“消耗水”向“利用水”的倾斜。
-    How to use water resources?
-    % 这里是一段关于虚拟水的介绍
-    % There has been put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption provisions is the main use of water resources, and can flow with trade.
-However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related provisions and services.
-    % Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
-    Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate purpose of water utility:
-    $$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
-    Where $i$ refers a certain region, or the whole basin, i.e:
-	$I_P$ = $NPS_{basin}$
-    %* 直接用水和非直接用水
-    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 purpose 的变化。
-    In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as provisioning water.
-Correspondingly, non-provisioning water is often industrial water, mainly energy water.
-Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which provisioning water is often the key to support the production of agricultural products, while non-provisioning water is more involved in industrial and other social processes.
-%!
-extensive studies need citations.
-    % For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade.
-But if industrial consumption is taken into account, China is exporting virtual water.
-However, as a river basin with high degree of water resource scarcity, the trade-off between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of purpose with water.
-
-\subsection*{Allocation: Allocation Entropy Metric}
-    %* 哪里利用水资源？
-    Where to use water resources?
-    % 水资源的分配一直是难题，需要在上下游之间、不同用水部门之间进行权衡，但目前还缺少相关的指标进行量化。
-    % The allocation of water resources has always been a difficult problem, requiring trade-offs between upstream and downstream and even different water sectors.
-However, there is still a lack of comprehensive indicators to quantify.
-    % 这里我们设计了一个“分配熵指标”，能够把水资源分配的格局（倾向于平均分配还是更加侧重某一区域）简单直接的表达出来。
-    Here we designed a ``Allocation Entropy Metric (AEM)'', which can simply and directly express the configuration of water allocation (which tends to be more evenly distributed or more focused on a certain region and sector).
-    % 我们模仿了物理学中信息熵的思想，当信息（这里是水资源）的分配越趋于平均时，其熵在增加，当分配更倾向于某一区域时，该区域获得发展的确定性在增加，导致总体的熵减少。
-    We imitate the idea of information entropy in physics --When the distribution of information (here is water resource) is more equal, its entropy increases.
-    % 该指标将不同区域（SR, UR, MR, DR）和不同部门（农业、工业、服务业、人居）消耗的水资源 Water Use (WU) 视做观察的结果，计算完全平均分配水资源时候的水资源分配熵作为最大值，再计算实际水资源分配最大熵与实际熵的比值，以表示水资源分配的格局多大程度上偏离平均分配。
-    The AEM is a metrics for different regions (SR, UR, MR, DR) or different sectors (agriculture, industry, domestic and services) in allocation of Water Use (WU), calculated by:
-
-    $$ AEM = \sum_{i=1}^n -log(p_{i}) * p_{i} $$
-
-    Where $i$ represents the unit (a region or a sector) in configuration of water utilization, $p_i$ represents the proportion of water used by the units.
-    For different regions, when water resources are completely evenly used, (i.e. for any region $i$, $p_i = 1/n $), the maximum value of AEM is:
-
-    $$ AEM_{max} = \sum_{i=1}^n -log(p_{i}) * p_{i} = - log(\frac{1}{n}) $$
-
-    $I_C$, an indicator to measure the configuration dimensions of water resources utilization, is composed of three parts:
-
-    $$ I_C = \frac{AEM_{r}*AEM_{s}}{AEM_{rs}}$$
-
-    \begin{itemize}
-        \item Allocation between regions $AEM_r$:
-            $$ AEM_r = \sum_{i=1}^4 -log(p_{i}) * p_{i} $$
-            where $p_i$ is the proportion of region $i$ in water resource usage ($WU_i$), in the total water resource consumption in all regions ($i=1$ to $4$ represents SR, UR, MR, or, DR respectively), i.e.:
-            $$ p_i = \frac{WU_i}{\sum_{i=1}^4 WU_i} $$
-        \item Allocation between sectors $AEM_s$:
-            $$ AEM_s = \sum_{j=1}^3 -log(p_{j}) * p_{j} $$
-            where $p_j$ is the proportion of sector $j$ in water resources usage ($WU_j$), in the total water consumption in all sectors ($j=1$ to $3$ represents agriculture, industry and domestic \& services respectively), i.e.:
-            $$ p_j = \frac{WU_j}{\sum_{j=1}^3 WU_j} $$
-        \item Division of sectors' function between regions $AEM_{rs}$
-            $$ AEM_{rs} = \frac{1}{3} * \sum_{j=1}^3 \sum_{i=1}^4 -log(p_{ij} * p_{ij})$$
-            where $p_{ij}$ refers water use proportion of region $i$ in the sector $j$, in the total water consumptions of all regions in this sector, i.e.:
-            $$ p_{ij} = \frac{WU_ij}{\sum_{i=1}^4 WU_ij} $$
-    \end{itemize}
-
-    % 上述指标同时考虑了地区之间的分配和行业之间的分配，但随着流域发展，两者的趋势是有差异的。对于位于同一个国家内的流域，区域之间通过开采水资源获取发展的机会是相等的，实际的水资源使用更多取决于自身的经济实力，因此考虑不受实际经济制约的理想情况，四个区域之间的水资源应该被公平（平均）分配的（熵增）。但同时，由于地理差异和部门分工的广泛存在，不同的区域有其比较优势，是制约其理论上将水资源分配于哪个用水行业的关键因素，因此其特定区域的部门之间水资源分配在理想情况下将总体呈现差异增加（熵减）的趋势。同时，部门分工也将随着比较优势出现，让不同区域都相较于流域的平均水平有其各自的优势部门（相较于平均熵）。
-    % TODO 这里一定要想一下，怎么能给人讲的更明白
-    The indicator $I_C$ (Allocation of water utilization), therefore, not only take into account the distribution between different regions and industries, but also considers the complicated professional division with the development of society.
-
-\newpage
-\section*{Sensitive analysis}
-% 一个对断点检测方法普遍的批评是可以通过调整方法的使用来操纵结果，因此我们对断点识别的过程进行了敏感性分析，以证明我们的结果是鲁棒性的。
-A common criticism of breakpoint detection methods is that the results can be manipulated by adjusting the use of the methods, so we conducted a sensitivity analysis of the breakpoint recognition process to demonstrate that our results are robust.
-
-Firstly, we performed three different normalization methods in construction of IWGI for breakpoint detection:
-
-\begin{itemize}
-    \item Min-max normalization:
-        $$ normalized(X) = \frac{X - X_{min}}{X_{max} - X_{min}} $$
-    \item Mean-max normalization:
-        $$ normalized(X) = \frac{X - X_{mean}}{X_{max} - X_{min}} $$
-    \item Z-score normalization:
-        $$ normalized(X) = \frac{X-X_{mean}}{X_{std}} $$
-\end{itemize}
-
-Where $X$ is a time series and $X_{mean}$, $X_{std}$, $X_{min}$, $X_{max}$ are mean, standard deviation, minimum, maximum of it.
-% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWGI，我们对IWGI的断点检测结果都相同。
-No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWGI breakpoints are the same.
-
-Another place where there is room for manipulation is the choice of significance threshold (i.e.
-threshold of the p-value) in the Pettitt Change points detection method.
-Here, we test 1000 possible p-values between $10^{-6}$ and $0.01$, and most of the results give the same detection in breakpoints.
-It has not given another breakpoint before the threshold is near to $10^{-2}$ (see \textit{SI Appendix} Fig. S12: A).
-% 不仅如此，当三个断点被检测出时，之前的两个断点仍然存在，且新增加的断点带来阶段划分的趋势差异并不明显
-Not only that, when three breakpoints are detected, the previous two breakpoints still exist (1978 and 1994), and the trend difference of the new breakpoints is not obvious (see \textit{SI Appendix} Fig.
-S12: B and C).
-
-Taken together, the results of three periods in this study with the two breakpoints detected (1978 and 1994) are robust.
-
-% tag 附录图
-
-%%% Each figure should be on its own page
-% 补充图片1：研究区示意图
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{../../figures/sup/s1_study_area.jpg}
-    % 黄河流域示意图
-    % A. 黄河流域示意图及研究区子区域的划分
-    % B. 黄河主河道的剖面图
-    % C. 典型景观
-    \caption{
-        The study area.
-        \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR: Source Region, UR: Upper Region, MR: Middle Region, DR: Downstream region).
-        \textbf{B.} Profile of main channel of the Yellow River. SR, UR, MR and DR are divided by main hydrological stations.
-        \textbf{C.} Typical landscapes in different regions in the YRB.
-    }
-\end{figure}
-
-% 补充图片2：研究区分区特征
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{../../figures/sup/region_differences.jpg}
-    % 黄河流域各区域的基本社会-经济状况和水资源条件差异。
-    \caption{
-        Basic socio-economic status and water resource conditions of different regions in the YRB, the average from 1980 to 2000 shown.
-        \textbf{A.} Proportion of GDP in different industries (primary, secondary or tertiary industry) in different regions.
-        \textbf{B.} Population of urban or rural area in different regions.
-        \textbf{C.} Natural water resource in different regions.
-        \textbf{D.} Total water use in different regions.
-    }
-\end{figure}
-
-% 补充图片3：用水比例
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
-    \caption{
-        Total water use of different sectors.
-        IND: Industrial water use;
-        IRR: Irrigation water use;
-        URB: Urban water use;
-        RUR: Rural water use;
-    }
-\end{figure}
-
-% 补充图片7：节水措施
-\begin{figure}
-    % TODO 这里还要增加一个过去的比例做对比
-    \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/saving_water.jpg}
-    \caption{
-        The ratio of irrigated area with saving-water equipments to the total irrigated area in 2013.
-    }
-\end{figure}
-
-% 补充图片4：天然水资源量
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
-    \caption{Water resources in different regions.
-        \textbf{A,} changing trend of measured runoff,
-        \textbf{B, C and D} average measured runoff within different periods.
-        \textbf{E, F and G} average total water consumptions within different periods.
-    }
-\end{figure}
-
-% 补充图片5：水库数量和累积库容
-\begin{figure}
-    \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/reservoirs.pdf}
-    \caption{
-        Reservoirs and their storage.
-        \textbf{A,} number of new reservoirs in different periods.
-        \textbf{B,} total storage capacities in different regions.
-    }
-\end{figure}
-
-% \begin{figure}
+% \begin{figure}[tb!]
 % 	\centering
-% 	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
+% 	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
 % 	\caption{
-% 		Changes in different dimensions of water resources utilization regimes and their main contributors.
-% 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
-% 		\textbf{B,} changes of water utilization purpose, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
-% 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
-% 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
-% 		\textbf{E,} Main impact water uses to water utilization purpose, and their change contributions to non-provisioning water shares.
-% 		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
+% 	    Ratio of irrigated areas with water-saving equipments.
 % 	}
-% 	\label{fig:dimensions}
+% 	\label{fig:wci}
 % \end{figure}
 
-% 补充图片9：黄河断流
-\begin{figure}
+\begin{figure}[tb]
     \centering
-    \includegraphics[width=0.6\textwidth]{../../figures/sup/outages.pdf}
-    \caption{Runoff drying-up records. Size of the circles indicates length of drying up river segments.}
+    \includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
+    \caption{
+        Numbers of new reservoirs in each year.
+    }
+    \label{fig:reservoirs}
 \end{figure}
-
-% 补充图片8：
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{../../figures/sup/ternary.pdf}
-    \caption{Net contribution of agriculture, industry and services to GDP of the whole YRB in different years.}
-\end{figure}
-
-% % 补充图片10：管理政策
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\textwidth]{../../figures/sup/managements.pdf}
-%     \caption{Number of management practices in different periods, including policy and reservoirs.}
-% \end{figure}
-
-% 补充图片 11 全球案例
-\begin{figure}%[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
-	\caption{
-		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
-		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure.
-Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
-	}
-	\label{fig:traps}
-\end{figure}
-
-% % 补充图片4：水资源灵活性
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
-%     \caption{
-%         Flexibility and its change contributions of water utilization.
-%         \textbf{A,} Proportion of inflexible water uses.
-%         \textbf{B,} Change contributions of inflexible water uses.
-%     }
-% \end{figure}
 
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{../../figures/sup/sensitivity.pdf}
+    \includegraphics[width=\linewidth]{sup/sensitivity.pdf}
     \caption{
@@
         \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
-        \textbf{B.} A typical result of two breakpoints.
-        \textbf{C.} A typical result of three breakpoints.
+        \textbf{B.} Threshold of p-values $\alpha=0.0005$.
+        \textbf{C.} Threshold of p-values $\alpha=0.05$.
     }
+    \label{fig:sensitivity}
 \end{figure}
 
-%% 表格
-\begin{table}\centering
-    \caption{Used datasets and their sources.}
-
-    % 表格
-    \begin{tabular}{lrrrr}
-    Dataset & Type & Spatial scale & Time limit & Source \\
-    \midrule
-    1. Water use & Statistical & Prefectures & 1965-2013 & 2nd National Water Resources Assessment Program \\
-    2. GDP & Statistical & Province & 1949-2019 & Wind database \\
-    3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
-    4. Reservoirs & Hydrological & Location & 1949-2015 & Wang et al. \cite{wangYellowRiverWater2019} \\
-    5. Measured runoff & Hydrological & Location & 1949-2019 & Measured data from YRCC \\
-    6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommissionYellowRiverBasin2013} \\
-    7. History of YRCC & Political & Documents & 1949-2002 & YRCC \cite{ yellowriverarchivesOrganizationalHistoryYellow2004} \\
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-% TODO 这里要加一个黄委会沿革的简表
-
-%% 表格
-\begin{table}\centering
-    \caption{Policies and regulations above YRB level which affected the whole basin in water utilization $^a$}
-
-    % 表格
-    \begin{tabular}{lrr}
-    Name & Year & Agency \\
-    \midrule
-    1. Water Law of PRC & 1988 & National People's Congress of the PRC \\
-    2. Water Law of PRC -revised 1 & 2009 & National People's Congress of the PRC \\
-    3. Water Law of PRC -revised 2 & 2016 & National People's Congress of the PRC \\
-    4. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
-    5. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees -revised 1 & 2017 & State Council of the PRC \\
-    6. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
-    7. Yellow River water supply distribution scheme & 1987 & State Council of the PRC \\
-    8. Measures for the Administration of Water Drawing Permits & 2008 & Ministry of Water Resources of the PRC \\
-    9. Measures for the Administration of Water Drawing Permits -revised 1 & 2015 & Ministry of Water Resources of the PRC \\
-    10. Measures for the Administration of Water Drawing Permits -revised 2 & 2017 & Ministry of Water Resources of the PRC \\
-    11. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
-    12. Annual distribution of available water supply of the Yellow River and main stream water dispatching scheme & 1998 & Ministry of Water Resources of the PRC \\
-    13. The Yellow River water dispatching management measures & 1998 & Ministry of Water Resources \\
-    14. Measures for the Implementation of the Yellow River Water Rights Conversion Management & 2004 & Ministry of Water Resources \\
-    15. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
-    16. Measures for the implementation of the water drawing Permit system & 1993 \\ State Council of the PRC \\
-    17. Measures for the demonstration and management of water resources in construction projects & 2002 & Ministry of Water Resources of the PRC \\
-    18. Implementation Opinions on the Reform of Water Conservancy Project Management System & 2006 & State Council of the PRC \\
-
-    \bottomrule
-    \end{tabular}
-
-    \footnotesize{$^a$ If a policy was proposed by multiple legacies, we only show the highest one.}
-\end{table}
-
-%%% Add this line AFTER all your figures and tables
-\FloatBarrier
+\section{Datasets}\label{secA3}
+\input{03_datasets.tex}
 
@@
 
-\bibliography{pnas-sample}
+\bibliographystyle{sn-standardnature}
+\bibliography{mybib}% common bib file
 

### 2022-07-13 paper/letter/cover_letter.tex
fix: keyword change

@@
 Our analysis approach links river basin governance with transitions of hydrosocial water cycles and offers valuable sustainability guidelines for big river basins worldwide.
-Therefore, we believe that this manuscript is appropriate for publication by \textit{People and Nature} because it tightly echoes the aims \& scope of water governance.
+Therefore, we believe that this manuscript is appropriate for publication by \textit{People and Nature} because it tightly echoes the widespread reader interest in environmental governance.
 
@@
 \item Prof. Murugesu Sivapalan (University of Illinois, Urbana-Champaign); Email: sivapala@illinois.edu; Dr. Sivapalan focuses on socio-hydrology, linking water and human society with basin studies.
+\end{itemize}
 

### 2022-07-15 paper/letter/cover_letter.tex
fix(MS,-appendix,-letter): fix format mistakes according to Wu's comment

@@
 \begin{itemize}
-\item Prof. Fuqiang Tian (Tsinghua University); Email: tianfq@tsinghua.edu.cn; Dr. Tian focuses on socio-hydrology and is familiar with the case basin in this study.
-\item Prof.
-Tom Gleeson (University of Victoria); Email: tgleeson@uvic.ca; Dr.
+\item Fuqiang Tian (Tsinghua University); Email: tianfq@tsinghua.edu.cn; Dr. Tian focuses on socio-hydrology and is familiar with the case basin in this study.
+\item Tom Gleeson (University of Victoria); Email: tgleeson@uvic.ca; Dr.
 Gleeson cares about the significant changes during the transformation toward a human-interrupted world, especially the hydrology system.
-\item Prof. Murugesu Sivapalan (University of Illinois, Urbana-Champaign); Email: sivapala@illinois.edu; Dr. Sivapalan focuses on socio-hydrology, linking water and human society with basin studies.
+\item Murugesu Sivapalan (University of Illinois, Urbana-Champaign); Email: sivapala@illinois.edu; Dr. Sivapalan focuses on socio-hydrology, linking water and human society with basin studies.
+\item Olli Varis (Aalto University); Email: olli.varis@aalto.fi; Dr.
+Varis analyzed global water-based social-ecological vulnerability by integrated index, and he is also good at water resources research.
 \end{itemize}

### 2022-07-15 paper/main/manuscript.tex
feat: appendix separated version
fix: keyword change
fix(MS,-appendix,-letter): fix format mistakes according to Wu's comment

@@
 \linespread{1.5}
+\usepackage{lineno}
 
@@
 
-\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\street{Xinjiekouwai Street}, \city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
 
@@
 %%==================================%%
-
+\linenumbers
 \abstract{
@@
     Water governance,
-    Transformation,
+    Hydrosocial cycle,
     Social-hydrology,
@@
 
-\section*{Declarations}
+% \section*{Declarations}
 
@@
 
-\begin{itemize}
-\item Funding
-\item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
-\item Ethics approval
-\item Consent to participate
-\item Consent for publication
-\item Availability of data and materials
-\item Code availability
-\item Authors' contributions
-\end{itemize}
+% \begin{itemize}
+% \item Funding
+% \item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
+% \item Ethics approval
+% \item Consent to participate
+% \item Consent for publication
+% \item Availability of data and materials
+% \item Code availability
+% \item Authors' contributions
+% \end{itemize}
 
-\noindent
-If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.
+%%===========================================================================================%%
+%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
+%% system, please include the references within the manuscript file itself. You may do this  %%
+%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
+%% file, and delete the associated \verb+\bibliography+ commands.                            %%
+%%===========================================================================================%%
 
-%%===================================================%%
-%% For presentation purpose, we have included        %%
-%% \bigskip command. please ignore this.             %%
-%%===================================================%%
-\bigskip
-\begin{flushleft}%
-Editorial Policies for:
+\newpage
+\bibliographystyle{sn-standardnature}
+\bibliography{mybib}% common bib file
+%% if required, the content of .bbl file can be included here once bbl is generated
+%%\input sn-article.bbl
 
-\bigskip\noindent
-Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}
-
-\bigskip\noindent
-Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}
-
-\bigskip\noindent
-\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}
-
-\bigskip\noindent
-BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
-\end{flushleft}
+%% Default %%
+%%\input sn-sample-bib.tex%
 
@@
 
-%%===========================================================================================%%
-%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
-%% system, please include the references within the manuscript file itself. You may do this  %%
-%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
-%% file, and delete the associated \verb+\bibliography+ commands.                            %%
-%%===========================================================================================%%
-
-\bibliographystyle{sn-standardnature}
-\bibliography{mybib}% common bib file
-%% if required, the content of .bbl file can be included here once bbl is generated
-%%\input sn-article.bbl
-
-%% Default %%
-%%\input sn-sample-bib.tex%
-
 \end{document}

### 2022-11-04 paper/letter/cover_letter.tex
docs(manuscript): Submission WRR v-8.0.0

@@
 
-I am pleased to submit an original research article entitled ``Identifying regime transitions for water governance at a basin scale'' for consideration for publication in \textit{People and Nature} as a \textit{Research Article}.
+I am pleased to submit an original research article entitled ``Identifying regime transitions for water governance at a basin scale'' for consideration for publication in \textit{Water Resources Research} as a \textit{Research Article}.
 
@@
 Our analysis approach links river basin governance with transitions of hydrosocial water cycles and offers valuable sustainability guidelines for big river basins worldwide.
-Therefore, we believe that this manuscript is appropriate for publication by \textit{People and Nature} because it tightly echoes the widespread reader interest in environmental governance.
+Therefore, we believe that this manuscript is appropriate for publication by \textit{Water Resources Research} because it tightly echoes the widespread reader interest in water governance.
 

### 2022-11-04 paper/main/02_methods.tex
docs(manuscript): Submission WRR v-8.0.0

@@
 This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
-Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Appendix}\ref{secA1}).
+Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).
 For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
@@
 
-	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \textit{Appendix}\ref{secA2}.
+	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \textit{Supporting Information S2}.
 
@@
 
-	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Appendix}\ref{secA1}).
+	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
 
@@
 		\begin{equation}
-			U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j), 1 \leqq t < T
+			U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j), 1 \leq t < T
 		\end{equation}
@@
 We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
-Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see \textit{Appendix} Figure~\ref{fig:sensitivity}).
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see \\textit{Supporting Information} Figure~S3).
 
@@
 	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI in the YRB, all the datasets we need are listed in the \textit{SI Appendix} Table~\ref{tab:datasets} with a detailed description in \ref{secA3}.
+	In order to calculate IWGI in the YRB, all the datasets we need are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.

### 2022-11-04 paper/main/03_results.tex
docs(manuscript): Submission WRR v-8.0.0

@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Appendix} Table~\ref{tab:policies}).
+		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Appendix} Figure~\ref{fig:reservoirs}).
+As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2.
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
@@
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Figure~\ref{fig:reservoirs}).
+Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
 During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).

### 2022-11-04 paper/main/manuscript.tex
docs(manuscript): Submission WRR v-8.0.0

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                 %%
-%% Please do not use \input{...} to include other tex files.       %%
-%% Submit your LaTeX manuscript as one .tex document.              %%
-%%                                                                 %%
-%% All additional figures and files should be attached             %%
-%% separately and not embedded in the \TeX\ document itself.       %%
-%%                                                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
+%
+% This file includes commands and instructions
+% given in the order necessary to produce a final output that will
+% satisfy AGU requirements, including customized APA reference formatting.
+%
+% You may copy this file and give it your
+% article name, and enter your text.
+%
+% guidelines and troubleshooting are here:
 
-%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
+%% To submit your paper:
+\documentclass[draft]{agujournal2019}
+\usepackage{url} %this package should fix any errors with URLs in refs.
+\usepackage{lineno}
+\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage{soul}
+\usepackage{amsmath}
+\linenumbers
+%%%%%%%
+% As of 2018 we recommend use of the TrackChanges package to mark revisions.
+% The trackchanges package adds five new LaTeX commands:
+%
+%  \note[editor]{The note}
+%  \annote[editor]{Text to annotate}{The note}
+%  \add[editor]{Text to add}
+%  \remove[editor]{Text to remove}
+%  \change[editor]{Text to remove}{Text to add}
+%
+% complete documentation is here: http://trackchanges.sourceforge.net/
+%%%%%%%
 
-%%=======================================================%%
-%% to print line numbers in the margin use lineno option %%
-%%=======================================================%%
+\draftfalse
 
-%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+%% Enter journal name below.
+%% Choose from this list of Journals:
+%
+% JGR: Atmospheres
+% JGR: Biogeosciences
+% JGR: Earth Surface
+% JGR: Oceans
+% JGR: Planets
+% JGR: Solid Earth
+% JGR: Space Physics
+% Global Biogeochemical Cycles
+% Geophysical Research Letters
+% Paleoceanography and Paleoclimatology
+% Radio Science
+% Reviews of Geophysics
+% Tectonics
+% Space Weather
+% Water Resources Research
+% Geochemistry, Geophysics, Geosystems
+% Journal of Advances in Modeling Earth Systems (JAMES)
+% Earth's Future
+% Earth and Space Science
+% Geohealth
+%
+% ie, \journalname{Water Resources Research}
 
-%%======================================================%%
-%% to compile with pdflatex/xelatex use pdflatex option %%
-%%======================================================%%
+\journalname{Water Resources Research}
 
-%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-
-%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-% \documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
-%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
-%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
-%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
-%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
-% \documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
-% \documentclass[default]{sn-jnl}% Default
-\documentclass[default, sn-standardnature]{sn-jnl}% Default with double column layout
-
-%%%% Standard Packages
-%%<additional latex packages if required can be included here>
-%%%%
-
-%%%%%=============================================================================%%%%
-%%%%  Remarks: This template is provided to aid authors with the preparation
-%%%%  of original research articles intended for submission to journals published
-%%%%  by Springer Nature. The guidance has been prepared in partnership with
-%%%%  production teams to conform to Springer Nature technical requirements.
-%%%%  Editorial and presentation requirements differ among journal portfolios and
-%%%%  research disciplines. You may find sections in this template are irrelevant
-%%%%  to your work and are empowered to omit any such section if allowed by the
-%%%%  journal you intend to submit to. The submission guidelines and policies
-%%%%  of the journal take precedence. A detailed User Manual is available in the
-%%%%  template package for technical guidance.
-%%%%%=============================================================================%%%%
-
-\jyear{2022}%
-\newgeometry{left=2cm, right=2cm}
-\linespread{1.5}
-\usepackage{lineno}
-
-%% as per the requirement new theorem styles can be included as shown below
-\theoremstyle{thmstyleone}%
-\newtheorem{theorem}{Theorem}%  meant for continuous numbers
-%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
-%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-\newtheorem{proposition}[theorem]{Proposition}%
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
-
-\theoremstyle{thmstyletwo}%
-\newtheorem{example}{Example}%
-\newtheorem{remark}{Remark}%
-
-\theoremstyle{thmstylethree}%
-\newtheorem{definition}{Definition}%
-% \usepackage{tikz}
-% \newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
-%     circle (.5em) node {\makebox[1em][c]{\small #1}};}}
-\raggedbottom
-%%\unnumbered% uncomment this for unnumbered level heads
-%! path of figs
-
-\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
 \begin{document}
 
-\title[Article Title]{Identifying regime transitions for water governance at a basin scale}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%  TITLE
+%
+% (A title should be specific, informative, and brief. Use
+% abbreviations only if they are defined in the abstract. Titles that
+% start with general keywords then specific terms are optimized in
+% searches)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%=============================================================%%
-%% Prefix	-> \pfx{Dr}
-%% GivenName	-> \fnm{Joergen W.}
-%% Particle	-> \spfx{van der} -> surname prefix
-%% FamilyName	-> \sur{Ploeg}
-%% Suffix	-> \sfx{IV}
-%% NatureName	-> \tanm{Poet Laureate} -> Title after name
-%% Degrees	-> \dgr{MSc, PhD}
-%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
-%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
-%%=============================================================%%
+% Example: \title{This is a test title}
+\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
+\title{Identifying regime transitions for water governance at a basin scale}
 
-\author[1]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  AUTHORS AND AFFILIATIONS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\author[1]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
+% Authors are individuals who have significantly contributed to the
+% research and preparation of the article. Group authors are allowed, if
+% each author in the group is separately identified in an appendix.)
 
-\author[1]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
-\author[2]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
-\author[3]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
-\author[4]{\fnm{Yue} \sur{Qin}}\email{qinyue@pku.edu.cn}
-\author[5]{\fnm{Xilin} \sur{Wu}}\email{wuxilin20@mails.ucas.ac.cn}
-\author*[1,5]{\fnm{Bojie} \sur{Fu}}\email{bfu@rcees.ac.cn}
+% List authors by first name or initial followed by last name and
+% separated by commas. Use \affil{} to number affiliations, and
+% \thanks{} for author notes.
+% Additional author notes should be indicated with \thanks{} (for
+% example, for current addresses).
 
-\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
+% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
 
-\affil[2]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
+\authors{
+      Shuang Song\affil{1},
+      Shuai Wang\affil{1},
+      Xutong Wu\affil{1},
+      Yongping Wei\affil{2},
+      Graeme S. Cumming\affil{3},
+      Yue Qin\affil{4},
+      Xilin Wu\affil{5},
+      Bojie Fu\affil{1,5}
+}
 
-\affil[3]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
+\affiliation{1}{
+      State Key Laboratory of Earth Surface Processes and Resource Ecology,
+      Beijing Normal University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{2}{
+      School of Earth and Environmental Sciences,
+      The University of Queensland,
+      Brisbane, 4067, QLD, Australia.
+}
+\affiliation{3}{
+      ARC Centre of Excellence for Coral Reef Studies,
+      James Cook University,
+      Townsville, 4811, QLD, Australia.
+}
+\affiliation{4}{
+      College of Environmental Sciences and Engineering,
+      Peking University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{5}{
+      State Key Laboratory of Urban and Regional Ecology,
+      Research Center for Eco-Environmental Sciences,
+      Chinese Academy of Sciences,
+      Beijing, 100875, Beijing, China.
+}
+%(repeat as many times as is necessary)
 
-\affil[4]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+% Corresponding author mailing address and e-mail address:
 
-\affil[5]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-%%==================================%%
-%% sample for unstructured abstract %%
-%%==================================%%
-\linenumbers
-\abstract{
+% (include name and email addresses of the corresponding author.  More
+% than one corresponding author is allowed in this LaTeX file and for
+% publication; but only one corresponding author is allowed in our
+% editorial system.)
+
+% Example: \correspondingauthor{First and Last Name}{email@address.edu}
+
+\correspondingauthor{Shuai Wang}{shuaiwang@bnu.edu.cn}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% KEY POINTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%  List up to three key points (at least one is required)
+%  Key Points summarize the main points and conclusions of the article
+%  Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
+
+% Example:
+% \begin{keypoints}
+% \item	List up to three key points (at least one is required)
+% \item	Key Points summarize the main points and conclusions of the article
+% \item	Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
+% \end{keypoints}
+
+\begin{keypoints}
+\item We developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance.
+\item We interpret how water governance shifts within a rapidly-changing large river basin.
+\item We developed an approach to analyzing intertwines of water governance, hydrosocial transition, and human-water relationships.
+\end{keypoints}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  ABSTRACT and PLAIN LANGUAGE SUMMARY
+%
+% A good Abstract will begin with a short description of the problem
+% being addressed, briefly describe the new data or analyses, then
+% briefly states the main conclusion(s) and how they are supported and
+% uncertainties.
+
+% The Plain Language Summary should be written for a broad audience,
+% including journalists and the science-interested public, that will not have
+% a background in your field.
+%
+% A Plain Language Summary is required in GRL, JGR: Planets, JGR: Biogeosciences,
+% JGR: Oceans, G-Cubed, Reviews of Geophysics, and JAMES.
+% see http://sharingscience.agu.org/creating-plain-language-summary/)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% \begin{abstract} starts the second page
+
+\begin{abstract}
 Water governance determine ``who gets water, when, and how'' in most large river basins.
@@
 The IWGI offers a comprehensive and straightforward approach to linking water governance regimes to sustainability, providing valuable insights into hydrosocial transitions.
-}
+\end{abstract}
 
-\keywords{
-    Regime shifts,
-    Water governance,
-    Hydrosocial cycle,
-    Social-hydrology,
-    Sustainability
-}
+\section*{Plain Language Summary}
+% Enter your Plain Language Summary here or delete this section.
+% Here are instructions on writing a Plain Language Summary:
+% https://www.agu.org/Share-and-Advocate/Share/Community/Plain-language-summary
+Missing governance means missing sustainability.
+However, the lack of a comprehensive but straightforward approach to identifying the changes in water governance presents a challenge for efforts to underpin it.
+Therefore, we choose indicators for the corresponding aspects (water stress, water services purpose, and water allocation) and combine them into an integrated water governance index (IWGI) to analyze long-term changes in a large river basin.
 
-%%\pacs[JEL Classification]{D8, H51}
-%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  BODY TEXT
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\maketitle
-
+%%% Suggested section heads:
+% \section{Introduction}
+%
+% The main text should start with an introduction. Except for short
+% manuscripts (such as comments and replies), the text should be divided
+% into sections, each with its own heading.
 \section{Introduction}\label{sec1}
@@
 
+% Headings should be sentence fragments and do not begin with a
+% lowercase letter or number. Examples of good headings are:
+\section{Materials and Methods}\label{sec11}
+\input{02_methods}
+% \section{Materials and Methods}
+% Here is text on Materials and Methods.
+%
+% \subsection{A descriptive heading about methods}
+% More about Methods.
+%
+% \section{Data} (Or section title might be a descriptive heading about data)
+%
+% \section{Results} (Or section title might be a descriptive heading about the
+% results)
 \section{Results}\label{sec2}
 \input{03_results}
+
+% \section{Conclusions}
 
@@
 
-\section{Methods}\label{sec11}
-\input{02_methods}
+% \section{= enter section title =}
+%Text here ===>>>
 
-\backmatter
+%%
 
-\bmhead{Supplementary information}
-When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
-Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the \ref{secA1}.
-The formulation in detail for applying the SFV-index is available in the \ref{secA2}.
-We used multiple sources of datasets in this study, \textit{Appendix}~\ref{secA3} introduces where they came from and how we harmonise them for analysis.
+%  Numbered lines in equations:
+%  To add line numbers to lines in equations,
+%  \begin{linenomath*}
+%  \begin{equation}
+%  \end{equation}
+%  \end{linenomath*}
 
-\bmhead{Acknowledgments}
+%% Enter Figures and Tables near as possible to where they are first mentioned:
+%
+% DO NOT USE \psfrag or \subfigure commands.
+%
+% Figure captions go below the figure.
+% Acronyms used in figure captions will be spelled out in the final, published version.
 
+% Table titles go above tables;  other caption information
+%  should be placed in last line of the table, using
+% \multicolumn2l{$^a$ This is a table note.}
+% NOTE that there is no difference between table caption and table heading in the final, published version
+%
+%----------------
+% EXAMPLE FIGURES
+%
+% \begin{figure}
+% \includegraphics{example.png}
+% \caption{caption}
+% \end{figure}
+%
+% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
+% \begin{figure}
+% \noindent\includegraphics[width=\textwidth]{anothersample.png}
+%\caption{caption}
+%\label{pngfiguresample}
+%\end{figure}
+%
+%
+% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options.
+This is common when trying to add a PDF figure without pdflatex.
+% \begin{figure}
+% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.pdf}
+%\caption{caption}
+%\label{pdffiguresample}
+%\end{figure}
+%
+%
+% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
+%
+
+%
+% ---------------
+% EXAMPLE TABLE
+%
+% \begin{table}
+% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
+% \centering
+% \begin{tabular}{l c}
+% \hline
+%  Run  & Time (min)  \\
+% \hline
+%   $l1$  & 260   \\
+%   $l2$  & 300   \\
+%   $l3$  & 340   \\
+%   $h1$  & 270   \\
+%   $h2$  & 250   \\
+%   $h3$  & 380   \\
+%   $r1$  & 370   \\
+%   $r2$  & 390   \\
+% \hline
+% \multicolumn{2}{l}{$^{a}$Footnote text here.}
+% \end{tabular}
+% \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% SIDEWAYS FIGURES and TABLES
+% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
+%
+% \begin{sidewaysfigure}
+% \includegraphics[width=20pc]{figsamp}
+% \caption{caption here}
+% \label{newfig}
+% \end{sidewaysfigure}
+%
+%  \begin{sidewaystable}
+%  \caption{Caption here}
+% \label{tab:signif_gap_clos}
+%  \begin{tabular}{ccc}
+% one&two&three\\
+% four&five&six
+%  \end{tabular}
+%  \end{sidewaystable}
+
+%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
+%\begin{linenomath*}
+%\begin{equation}
+%y|{f} \sim g(m, \sigma),
+%\end{equation}
+%\end{linenomath*}
+
+%%% End of body of article
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional Appendices go here
+%
+% The \appendix command resets counters and redefines section heads
+%
+% After typing \appendix
+%
+%\section{Here Is Appendix Title}
+% will show
+% A: Here Is Appendix Title
+%
+%\appendix
+%\section{Here is a sample appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Optional Glossary, Notation or Acronym section goes here:
+%
+% Glossary is only allowed in Reviews of Geophysics
+%  \begin{glossary}
+%  \term{Term}
+%   Term Definition here
+%  \term{Term}
+%   Term Definition here
+%  \term{Term}
+%   Term Definition here
+%  \end{glossary}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Acronyms
+%% NOTE that acronyms in the final published version will be spelled out when used in figure captions.
+%   \begin{acronyms}
+%   \acro{Acronym}
+%   Definition here
+%   \acro{EMOS}
+%   Ensemble model output statistics
+%   \acro{ECMWF}
+%   Centre for Medium-Range Weather Forecasts
+%   \end{acronyms}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Notation
+%   \begin{notation}
+%   \notation{$a+b$} Notation Definition here
+%   \notation{$e=mc^2$}
+%   Equation in German-born physicist Albert Einstein's theory of special
+%  relativity that showed that the increased relativistic mass ($m$) of a
+%  body comes from the energy of motion of the body—that is, its kinetic
+%  energy ($E$)—divided by the speed of light squared ($c^2$).
+%   \end{notation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% DATA SECTION and ACKNOWLEDGMENTS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Open Research Section}
+All the used datasets and access source are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
+
+\acknowledgments
 Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% REFERENCES and BIBLIOGRAPHY
+%
+% \bibliography{<name of your .bib file>} don't specify the file extension
+% don't specify bibliographystyle
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% \section*{Declarations}
+\bibliography{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/paper/main/mybibtex.bib}
 
-% Some journals require declarations to be submitted in a standardised format.
-Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section.
-If yes, your manuscript must contain the following sections under the heading `Declarations':
-
-% \begin{itemize}
-% \item Funding
-% \item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
-% \item Ethics approval
-% \item Consent to participate
-% \item Consent for publication
-% \item Availability of data and materials
-% \item Code availability
-% \item Authors' contributions
-% \end{itemize}
-
-%%===========================================================================================%%
-%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
-%% system, please include the references within the manuscript file itself. You may do this  %%
-%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
-%% file, and delete the associated \verb+\bibliography+ commands.                            %%
-%%===========================================================================================%%
-
-\newpage
-\bibliographystyle{sn-standardnature}
-\bibliography{mybib}% common bib file
-%% if required, the content of .bbl file can be included here once bbl is generated
-%%\input sn-article.bbl
-
-%% Default %%
-%%\input sn-sample-bib.tex%
-
-\begin{appendices}
-
-\section{YRB Regions}\label{secA1}
-\input{../sup/01_yrb.tex}
-
-\section{SFV-index}\label{secA2}
-\input{../sup/02_indicator.tex}
-
-% \begin{figure}[tb!]
-% 	\centering
-% 	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
-% 	\caption{
-% 	    Ratio of irrigated areas with water-saving equipments.
-% 	}
-% 	\label{fig:wci}
-% \end{figure}
-
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
-    \caption{
-        Numbers of new reservoirs in each year.
-    }
-    \label{fig:reservoirs}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{sup/sensitivity.pdf}
-    \caption{
-        Sensitivity analysis of the threshold of p-values.
-        \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
-        \textbf{B.} Threshold of p-values $\alpha=0.0005$.
-        \textbf{C.} Threshold of p-values $\alpha=0.05$.
-    }
-    \label{fig:sensitivity}
-\end{figure}
-
-\section{Datasets}\label{secA3}
-\input{../sup/03_datasets.tex}
-
-\end{appendices}
+%Reference citation instructions and examples:
+%
+% Please use ONLY \cite and \citeA for reference citations.
+% \cite for parenthetical references
+% ...as shown in recent studies (Simpson et al., 2019)
+% \citeA for in-text citations
+% ...Simpson et al. (2019) have shown...
+%
+%
+%...as shown by \citeA{jskilby}.
+%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
+%...has been shown \cite{jskilbye}.
+%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
+%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
+%...has been shown by \cite <e.g.,>[and others]{lewin76}.
+%
+% apacite uses < > for prenotes and [ ] for postnotes
+% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
+%
 
 \end{document}
+
+More Information and Advice:
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  SECTION HEADS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Capitalize the first letter of each word (except for
+% prepositions, conjunctions, and articles that are
+% three or fewer letters).
+
+% AGU follows standard outline style; therefore, there cannot be a section 1 without
+% a section 2, or a section 2.3.1 without a section 2.3.2.
+% Please make sure your section numbers are balanced.
+% ---------------
+% Level 1 head
+%
+% Use the \section{} command to identify level 1 heads;
+% type the appropriate head wording between the curly
+% brackets, as shown below.
+%
+%An example:
+%\section{Level 1 Head: Introduction}
+%
+% ---------------
+% Level 2 head
+%
+% Use the \subsection{} command to identify level 2 heads.
+%An example:
+%\subsection{Level 2 Head}
+%
+% ---------------
+% Level 3 head
+%
+% Use the \subsubsection{} command to identify level 3 heads
+%An example:
+%\subsubsection{Level 3 Head}
+%
+%---------------
+% Level 4 head
+%
+% Use the \subsubsubsection{} command to identify level 3 heads
+% An example:
+%\subsubsubsection{Level 4 Head} An example.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  IN-TEXT LISTS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Do not use bulleted lists; enumerated lists are okay.
+% \begin{enumerate}
+% \item
+% \item
+% \item
+% \end{enumerate}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  EQUATIONS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Single-line equations are centered.
+% Equation arrays will appear left-aligned.
+
+Math coded inside display math mode \[ ...\]
+ will not be numbered, e.g.,:
+ \[ x^2=y^2 + z^2\]
+
+ Math coded inside \begin{equation} and \end{equation} will
+ be automatically numbered, e.g.,:
+ \begin{equation}
+ x^2=y^2 + z^2
+ \end{equation}
+
+% To create multiline equations, use the
+% \begin{eqnarray} and \end{eqnarray} environment
+% as demonstrated below.
+\begin{eqnarray}
+  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
+        && + (y - y_{0}) \sin \Theta  \nonumber \\
+  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
+        && + (y - y_{0}) \cos \Theta.
+\end{eqnarray}
+
+%If you don't want an equation number, use the star form:
+%\begin{eqnarray*}...\end{eqnarray*}
+
+% Break each line at a sign of operation
+% (+, -, etc.) if possible, with the sign of operation
+% on the new line.
+
+% Indent second and subsequent lines to align with
+% the first character following the equal sign on the
+% first line.
+
+% Use an \hspace{} command to insert horizontal space
+% into your equation if necessary. Place an appropriate
+% unit of measure between the curly braces, e.g.
+% \hspace{1in}; you may have to experiment to achieve
+% the correct amount of space.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  EQUATION NUMBERING: COUNTER
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% You may change equation numbering by resetting
+% the equation counter or by explicitly numbering
+% an equation.
+
+% To explicitly number an equation, type \eqnum{}
+% (with the desired number between the brackets)
+% after the \begin{equation} or \begin{eqnarray}
+% command.  The \eqnum{} command will affect only
+% the equation it appears with; LaTeX will number
+% any equations appearing later in the manuscript
+% according to the equation counter.
+%
+
+% If you have a multiline equation that needs only
+% one equation number, use a \nonumber command in
+% front of the double backslashes (\\) as shown in
+% the multiline equation above.
+
+% If you are using line numbers, remember to surround
+% equations with \begin{linenomath*}...\end{linenomath*}
+
+%  To add line numbers to lines in equations:
+%  \begin{linenomath*}
+%  \begin{equation}
+%  \end{equation}
+%  \end{linenomath*}

### 2022-11-04 paper/sup/02_indicator.tex
docs(manuscript): Submission WRR v-8.0.0

@@
 
-First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Appendix}~\ref{secA1}):
+First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \\textit{Supporting Information}~\ref{secA1}):
 \begin{equation}

### 2022-11-04 paper/sup/03_datasets.tex
feat: appendix separated version
docs(manuscript): Submission WRR v-8.0.0

@@
 
-\begin{table*}[!htbp]
+\begin{table}[!htbp]
+    \settablenum{S1}
     \begin{center}
-    \small
-    \begin{minipage}{\linewidth}
+    % \small
+    % \begin{minipage}{\linewidth}
     \caption{Used datasets and their sources.}\label{tab:datasets}%
-    \resizebox{\linewidth}{!}{
-    \begin{tabular}{lrrrp{0.4\linewidth}}
-    \toprule
+    % \resizebox{\linewidth}{!}{
+    \begin{tabular}{lrrrp{0.35\linewidth}}
+    \hline
     Dataset & Type & Spatial scale & Time scale & Source \\
-    \midrule
+    \hline
     1. Administrative water use & Statistical & Prefectures & 1965-2013 & 2nd National Water Resources Assessment Program \cite{zhou2020}\\
@@
     8. YRB Events & Political & Documents & 1949-2015 & YRCC: \url{http://www.yrcc.gov.cn/hhyl/hhjs/} \\
-    \botrule
-    \end{tabular}}
-    \end{minipage}
+    \hline
+    \end{tabular}
+    % }
+    % \end{minipage}
     \end{center}
-    \end{table*}
+    \end{table}
 
     %% 表格
-\begin{table*}
+\begin{table}[!h]
+    \settablenum{S2} %%Change number for each table
     \centering
-    \small
+    % \small
+    \renewcommand\arraystretch{1.2}
     \caption{Policies and regulations above YRB level which affected the whole basin in water utilization}\label{tab:policies}
-    \begin{minipage}{\linewidth}
-    \resizebox{\linewidth}{!}{
+    % \begin{minipage}{\linewidth}
+    % \resizebox{\linewidth}{!}{
     \begin{tabular}{p{0.6\linewidth}rp{0.35\linewidth}}
         Name & Year & Agency \\
-        \midrule
+        \hline
         1. Water Law of PRC & 1988 & National People's Congress of the PRC \\
@@
         18. Implementation Opinions on the Reform of Water Conservancy Project Management System & 2006 & State Council of the PRC \\
-        \bottomrule
-    \end{tabular}}
+        \hline
+    \end{tabular}
+    % }
 
-    \footnotesize[1]{If a policy was proposed by multiple legacies, we only show the highest one.}
-    \end{minipage}
-\end{table*}
+    \tablenotetext{1}{If a policy was proposed by multiple legacies, we only show the highest one.}
+    % \end{minipage}
+\end{table}

### 2022-11-04 paper/sup/supplementary_information.tex
docs(manuscript): Submission WRR v-8.0.0

@@
-\documentclass[default, sn-standardnature]{sn-jnl}% Default with double column layout
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
+% Modified December 2018
+%
+% This template includes commands and instructions
+% given in the order necessary to produce a final output that will
+% satisfy AGU requirements.
+%
+% FOR FIGURES, DO NOT USE \psfrag
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% IMPORTANT NOTE:
+%
+% SUPPORTING INFORMATION DOCUMENTATION IS NOT COPYEDITED BEFORE PUBLICATION.
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Step 1: Set the \documentclass
+%
+%
+% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
+% The draft option produces double spaced output.
+%
+% Choose the journal abbreviation for the journal you are
+% submitting to:
 
-%%%% Standard Packages
-%%<additional latex packages if required can be included here>
-%%%%
+% jgrga JOURNAL OF GEOPHYSICAL RESEARCH (use for all of them)
+% gbc   GLOBAL BIOCHEMICAL CYCLES
+% grl   GEOPHYSICAL RESEARCH LETTERS
+% pal   PALEOCEANOGRAPHY
+% ras   RADIO SCIENCE
+% rog   REVIEWS OF GEOPHYSICS
+% tec   TECTONICS
+% wrr   WATER RESOURCES RESEARCH
+% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
+% sw    SPACE WEATHER
+% ms    JAMES
+% ef    EARTH'S FUTURE
+%
+%
+%
+% (If you are submitting to a journal other than jgrga,
+% substitute the initials of the journal for "jgrga" below.)
 
-%%%%%=============================================================================%%%%
-%%%%  Remarks: This template is provided to aid authors with the preparation
-%%%%  of original research articles intended for submission to journals published
-%%%%  by Springer Nature. The guidance has been prepared in partnership with
-%%%%  production teams to conform to Springer Nature technical requirements.
-%%%%  Editorial and presentation requirements differ among journal portfolios and
-%%%%  research disciplines. You may find sections in this template are irrelevant
-%%%%  to your work and are empowered to omit any such section if allowed by the
-%%%%  journal you intend to submit to. The submission guidelines and policies
-%%%%  of the journal take precedence. A detailed User Manual is available in the
-%%%%  template package for technical guidance.
-%%%%%=============================================================================%%%%
+\documentclass[draft,wrr]{agutexSI2019}
+\usepackage{amsmath}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  SUPPORTING INFORMATION TEMPLATE
+%
+%% ------------------------------------------------------------------------ %%
+%
+%
+%Please use this template when formatting and submitting your Supporting Information.
 
-\jyear{2022}%
-\newgeometry{left=2cm, right=2cm}
-\linespread{1.5}
+%This template serves as both a “table of contents” for the supporting information for your article and as a summary of files.
+%
+%
+%OVERVIEW
+%
+%Please note that all supporting information will be peer reviewed with your manuscript. It will not be copyedited if the paper is accepted.
+%In general, the purpose of the supporting information is to enable authors to provide and archive auxiliary information such as data tables, method information, figures, video, or computer software, in digital formats so that other scientists can use it.
+%The key criteria are that the data:
+% 1. supplement the main scientific conclusions of the paper but are not essential to the conclusions (with the exception of
+%    including %data so the experiment can be reproducible);
+% 2. are likely to be usable or used by other scientists working in the field;
+% 3. are described with sufficient precision that other scientists can understand them, and
+% 4. are not exe files.
+%
+%USING THIS TEMPLATE
+%
+%***All references should be included in the reference list of the main paper so that they can be indexed, linked, and counted as citations.  The reference section does not count toward length limits.
+%
+%All Supporting text and figures should be included in this document.
+Insert supporting information content into each appropriate section of the template.
+To add additional captions, simply copy and paste each sample as needed.
 
-%% as per the requirement new theorem styles can be included as shown below
-\theoremstyle{thmstyleone}%
-\newtheorem{theorem}{Theorem}%  meant for continuous numbers
-%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
-%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-\newtheorem{proposition}[theorem]{Proposition}%
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+%Tables may be included, but can also be uploaded separately, especially if they are larger than 1 page, or if necessary for retaining table formatting.
+Data sets, large tables, movie files, and audio files should be uploaded separately.
+Include their captions in this document and list the file name with the caption.
+You will be prompted to upload these files on the Upload Files tab during the submission process, using file type “Supporting Information (SI)”
 
-\theoremstyle{thmstyletwo}%
-\newtheorem{example}{Example}%
-\newtheorem{remark}{Remark}%
+%IMPORTANT NOTE ON FIGURES AND TABLES
+% Placeholders for figures and tables appear after the \end{article} command, after references.
+% DO NOT USE \psfrag or \subfigure commands.
+%
+ \usepackage{graphicx}
+%
+%  Uncomment the following command to allow illustrations to print
+%   when using Draft:
+ \setkeys{Gin}{draft=false}
+%
+% You may need to use one of these options for graphicx depending on the driver program you are using.
+%
+% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
+% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
+% [oztex], [textures]
+%
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  ENTER PREAMBLE
+%
+%% ------------------------------------------------------------------------ %%
 
-\theoremstyle{thmstylethree}%
-\newtheorem{definition}{Definition}%
-% \usepackage{tikz}
-% \newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
-%     circle (.5em) node {\makebox[1em][c]{\small #1}};}}
-\raggedbottom
-%%\unnumbered% uncomment this for unnumbered level heads
-%! path of figs
+% Author names in capital letters:
+%\authorrunninghead{BALES ET AL.}
+
+% Shorter version of title entered in capital letters:
+%\titlerunninghead{SHORT TITLE}
+
+%Corresponding author mailing address and e-mail address:
+%\authoraddr{Corresponding author: A. B. Smith,
+%Department of Hydrology and Water Resources, University of
+%Arizona, Harshbarger Building 11, Tucson, AZ 85721, USA.
+%(a.b.smith@hwr.arizona.edu)}
+
+\begin{document}
+
+%% ------------------------------------------------------------------------ %%
+%
+%  TITLE
+%
+%% ------------------------------------------------------------------------ %%
+
+%\includegraphics{agu_pubart-white_reduced.eps}
 
 \graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
-\begin{document}
+\title{Supporting Information for ``Identifying regime transitions for water governance at a basin scale''}
+%
+% e.g., \title{Supporting Information for "Terrestrial ring current:
+% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
+%
+%DOI: 10.1002/%insert paper number here%
 
-\title{Supporting Materials of ``Identifying regime transitions for water governance at a basin scale''}
+%% ------------------------------------------------------------------------ %%
+%
+%  AUTHORS AND AFFILIATIONS
+%
+%% ------------------------------------------------------------------------ %%
 
-%%=============================================================%%
-%% Prefix	-> \pfx{Dr}
-%% GivenName	-> \fnm{Joergen W.}
-%% Particle	-> \spfx{van der} -> surname prefix
-%% FamilyName	-> \sur{Ploeg}
-%% Suffix	-> \sfx{IV}
-%% NatureName	-> \tanm{Poet Laureate} -> Title after name
-%% Degrees	-> \dgr{MSc, PhD}
-%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
-%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
-%%=============================================================%%
+% List authors by first name or initial followed by last name and
+% separated by commas. Use \affil{} to number affiliations, and
+% \thanks{} for author notes.
+% Additional author notes should be indicated with \thanks{} (for
+% example, for current addresses).
 
-\author[1]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
+% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
+% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
 
-\author[1]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
+\authors{
+      Shuang Song\affil{1},
+      Shuai Wang\affil{1},
+      Xutong Wu\affil{1},
+      yongping Wei\affil{2},
+      Graeme S. Cumming\affil{3},
+      Yue Qin\affil{4},
+      Xilin Wu\affil{5},
+      Bojie Fu\affil{1,5}
+}
 
-\author[1]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
-\author[2]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
-\author[3]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
-\author[4]{\fnm{Yue} \sur{Qin}}\email{qinyue@pku.edu.cn}
-\author[5]{\fnm{Xilin} \sur{Wu}}\email{wuxilin20@mails.ucas.ac.cn}
-\author*[1,5]{\fnm{Bojie} \sur{Fu}}\email{bfu@rcees.ac.cn}
+\affiliation{1}{
+      State Key Laboratory of Earth Surface Processes and Resource Ecology,
+      Beijing Normal University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{2}{
+      School of Earth and Environmental Sciences,
+      The University of Queensland,
+      Brisbane, 4067, QLD, Australia.
+}
+\affiliation{3}{
+      ARC Centre of Excellence for Coral Reef Studies,
+      James Cook University,
+      Townsville, 4811, QLD, Australia.
+}
+\affiliation{4}{
+      College of Environmental Sciences and Engineering,
+      Peking University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{5}{
+      State Key Laboratory of Urban and Regional Ecology,
+      Research Center for Eco-Environmental Sciences,
+      Chinese Academy of Sciences,
+      Beijing, 100875, Beijing, China.
+}
 
-\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+%% ------------------------------------------------------------------------ %%
+%
+%  BEGIN ARTICLE
+%
+%% ------------------------------------------------------------------------ %%
 
-\affil[2]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
+% The body of the article must start with a \begin{article} command
+%
+% \end{article} must follow the references section, before the figures
+%  and tables.
 
-\affil[3]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
+\begin{article}
 
-\affil[4]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
+%% ------------------------------------------------------------------------ %%
+%
+%  TEXT
+%
+%% ------------------------------------------------------------------------ %%
 
-\affil[5]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-%%==================================%%
-%% sample for unstructured abstract %%
-%%==================================%%
+\noindent\textbf{Contents of this file}
+%%%Remove or add items as needed%%%
+\begin{enumerate}
+\item Text S1 to S3
+\item Figures S1 to S3
+\item Tables S1 to S2
+%if Tables are larger than 1 page, upload as separate excel file
+\end{enumerate}
+% \noindent\textbf{Additional Supporting Information (Files uploaded separately)}
+% \begin{enumerate}
+% \item Captions for Datasets S1 to Sx
+% \item Captions for large Tables S1 to Sx (if larger than 1 page, upload as separate excel file)
+% \item Captions for Movies S1 to Sx
+% \item Captions for Audio S1 to Sx
+% \end{enumerate}
 
-%% Comment out or remove this line before generating final copy for submission; this will also remove the warning re: "Consecutive odd pages found".
-% \instructionspage
+\noindent\textbf{Introduction}
+%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
+% 1. a general overview of the kind of data files;
+% 2. information about when and how the data were collected or created;
+% 3. a general description of processing steps used;
+% 4. any known imperfections or anomalies in the data.
+When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
+Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the \ref{secA1}.
+The formulation in detail for applying the SFV-index is available in the \ref{secA2}.
+We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonise them for analysis.
+%\clearpage
 
-\maketitle
+%Delete all unused file types below. Copy/paste for multiples of each file type as needed.
 
-%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text
-
-\section{YRB Regions}\label{secA1}
+%Type or paste text here.
+This should be additional explanatory text, such as: extended descriptions of results, full details of models, extended lists of acknowledgements etc.
+It should not be additional discussion, analysis, interpretation or critique.
+It should not be an additional scientific experiment or paper.
+%
+%Repeat for any additional Supporting Text
+\noindent\textbf{YRB Regions}\label{secA1}
 \input{01_yrb.tex}
 
-\section{SFV-index}\label{secA2}
+\noindent\textbf{SFV-index}\label{secA2}
 \input{02_indicator.tex}
-
-% \begin{figure}[tb!]
-% 	\centering
-% 	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
-% 	\caption{
-% 	    Ratio of irrigated areas with water-saving equipments.
-% 	}
-% 	\label{fig:wci}
-% \end{figure}
 
@@
 
-\section{Datasets}\label{secA3}
+\noindent\textbf{Datasets}\label{secA3}
 \input{03_datasets.tex}
 
-% \dataset{dataset_one.txt}{Type or paste legend here.}
+%%Enter Data Set, Movie, and Audio captions here
+%%EXAMPLE CAPTIONS
 
-% \dataset{dataset_two.txt}{Type or paste legend here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}
+% \noindent\textbf{Data Set S1.} %Type or paste caption here.
+%upload your dataset(s) to AGU's journal submission site and select "Supporting Information (SI)" as the file type. Following naming %convention: ds01.
 
-\bibliographystyle{sn-standardnature}
-\bibliography{mybib}% common bib file
+%Repeat for any additional Supporting data sets
+
+% \noindent\textbf{Movie S1.} %Type or paste caption here.
+%upload your movie(s) to AGU's journal submission site and select, "Supporting Information %(SI)" as the file type. Following naming convention: ms01.
+
+%Repeat any additional Supporting movies
+
+% \noindent\textbf{Audio S1.} %Type or paste caption here.
+%upload your audio file(s) to AGU's journal submission site and select "Supporting Information %(SI)" as the file type. Following naming convention: auds01.
+
+%Repeat for any additional Supporting audio files
+
+%%% End of body of article:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Optional Notation section goes here
+%
+% Notation -- End each entry with a period.
+% \begin{notation}
+% Term & definition.\\
+% Second term & second definition.\\
+% \end{notation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% ------------------------------------------------------------------------ %%
+%%  REFERENCE LIST AND TEXT CITATIONS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+\bibliography{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/paper/main/mybibtex.bib}
+%
+% no need to specify bibliographystyle
+%
+% Note that ALL references in this supporting information file must also be referenced in the primary manuscript
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% if you get an error about newblock being undefined, uncomment this line:
+%\newcommand{\newblock}{}
+
+% \bibliography{ uncomment this line and enter the name of your bibtex file here }
+
+%Reference citation instructions and examples:
+%
+% Please use ONLY \cite and \citeA for reference citations.
+% \cite for parenthetical references
+% ...as shown in recent studies (Simpson et al., 2019)
+% \citeA for in-text citations
+% ...Simpson et al (2019) have shown...
+% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
+%
+%
+%...as shown by \citeA{jskilby}.
+%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
+%...has been shown \cite<e.g.,>{jskilbye}.
+%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
+%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
+%
+% apacite uses < > for prenotes, not [ ]
+% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
+%
+
+%% ------------------------------------------------------------------------ %%
+%
+%  END ARTICLE
+%
+%% ------------------------------------------------------------------------ %%
+\end{article}
+\clearpage
+
+% Copy/paste for multiples of each file type as needed.
+
+% enter figures and tables below here: %%%%%%%
+%
+%
+%
+%
+% EXAMPLE FIGURES
+% ---------------
+% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options.
+% \begin{figure}
+%\setfigurenum{S1} %%You can change number for each figure if you want, not required. "S" prepended automatically.
+% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.eps}
+%\caption{caption}
+%\label{epsfiguresample}
+%\end{figure}
+%
+%
+% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
+% \begin{figure}
+% \noindent\includegraphics[width=\textwidth]{anothersample.png}
+%\caption{caption}
+%\label{pngfiguresample}
+%\end{figure}
+%
+%
+%\begin{figure}
+%\noindent\includegraphics[width=\textwidth]{athirdsample.pdf}
+%\caption{A pdf test figure}
+%\label{pdffiguresample}
+%\end{figure}
+%
+% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
+%
+%
+% ---------------
+% EXAMPLE TABLE
+%
+%\begin{table}
+%\settablenum{S1} %%Change number for each table
+%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
+%\centering
+%\begin{tabular}{l c}
+%\hline
+% Run  & Time (min)  \\
+%\hline
+%  $l1$  & 260   \\
+%  $l2$  & 300   \\
+%  $l3$  & 340   \\
+%  $h1$  & 270   \\
+%  $h2$  & 250   \\
+%  $h3$  & 380   \\
+%  $r1$  & 370   \\
+%  $r2$  & 390   \\
+%\hline
+%\end{tabular}
+%\tablenotetext{a}{Footnote text here.}
+%\end{table}
+% ---------------
+%
+% EXAMPLE LARGE TABLE (UPLOADED SEPARATELY)
+%\begin{table}
+%\settablenum{S1} %%Change number for each table
+%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
+%\end{table}
 
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+More Information and Advice:
+
+%% ------------------------------------------------------------------------ %%
+%
+%  SECTION HEADS
+%
+%% ------------------------------------------------------------------------ %%
+
+% Capitalize the first letter of each word (except for
+% prepositions, conjunctions, and articles that are
+% three or fewer letters).
+
+% AGU follows standard outline style; therefore, there cannot be a section 1 without
+% a section 2, or a section 2.3.1 without a section 2.3.2.
+% Please make sure your section numbers are balanced.
+% ---------------
+% Level 1 head
+%
+% Use the \section{} command to identify level 1 heads;
+% type the appropriate head wording between the curly
+% brackets, as shown below.
+%
+%An example:
+%\section{Level 1 Head: Introduction}
+%
+% ---------------
+% Level 2 head
+%
+% Use the \subsection{} command to identify level 2 heads.
+%An example:
+%\subsection{Level 2 Head}
+%
+% ---------------
+% Level 3 head
+%
+% Use the \subsubsection{} command to identify level 3 heads
+%An example:
+%\subsubsection{Level 3 Head}
+%
+%---------------
+% Level 4 head
+%
+% Use the \subsubsubsection{} command to identify level 3 heads
+% An example:
+%\subsubsubsection{Level 4 Head} An example.
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  IN-TEXT LISTS
+%
+%% ------------------------------------------------------------------------ %%
+%
+% Do not use bulleted lists; enumerated lists are okay.
+% \begin{enumerate}
+% \item
+% \item
+% \item
+% \end{enumerate}
+%
+%% ------------------------------------------------------------------------ %%
+%
+%  EQUATIONS
+%
+%% ------------------------------------------------------------------------ %%
+
+% Single-line equations are centered.
+% Equation arrays will appear left-aligned.
+
+Math coded inside display math mode \[ ...\]
+ will not be numbered, e.g.,:
+ \[ x^2=y^2 + z^2\]
+
+ Math coded inside \begin{equation} and \end{equation} will
+ be automatically numbered, e.g.,:
+ \begin{equation}
+ x^2=y^2 + z^2
+ \end{equation}
+
+% IF YOU HAVE MULTI-LINE EQUATIONS, PLEASE
+% BREAK THE EQUATIONS INTO TWO OR MORE LINES
+% OF SINGLE COLUMN WIDTH (20 pc, 8.3 cm)
+% using double backslashes (\\).
+
+% To create multiline equations, use the
+% \begin{eqnarray} and \end{eqnarray} environment
+% as demonstrated below.
+\begin{eqnarray}
+  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
+        && + (y - y_{0}) \sin \Theta  \nonumber \\
+  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
+        && + (y - y_{0}) \cos \Theta.
+\end{eqnarray}
+
+%If you don't want an equation number, use the star form:
+%\begin{eqnarray*}...\end{eqnarray*}
+
+% Break each line at a sign of operation
+% (+, -, etc.) if possible, with the sign of operation
+% on the new line.
+
+% Indent second and subsequent lines to align with
+% the first character following the equal sign on the
+% first line.
+
+% Use an \hspace{} command to insert horizontal space
+% into your equation if necessary. Place an appropriate
+% unit of measure between the curly braces, e.g.
+% \hspace{1in}; you may have to experiment to achieve
+% the correct amount of space.
+
+%% ------------------------------------------------------------------------ %%
+%
+%  EQUATION NUMBERING: COUNTER
+%
+%% ------------------------------------------------------------------------ %%
+
+% You may change equation numbering by resetting
+% the equation counter or by explicitly numbering
+% an equation.
+
+% To explicitly number an equation, type \eqnum{}
+% (with the desired number between the brackets)
+% after the \begin{equation} or \begin{eqnarray}
+% command.  The \eqnum{} command will affect only
+% the equation it appears with; LaTeX will number
+% any equations appearing later in the manuscript
+% according to the equation counter.
+%
+
+% If you have a multiline equation that needs only
+% one equation number, use a \nonumber command in
+% front of the double backslashes (\\) as shown in
+% the multiline equation above.
+
+%% ------------------------------------------------------------------------ %%
+%
+%  SIDEWAYS FIGURE AND TABLE EXAMPLES
+%
+%% ------------------------------------------------------------------------ %%
+%
+% For tables and figures, add \usepackage{rotating} to the paper and add the rotating.sty file to the folder.
+% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
+%
+% \begin{sidewaysfigure}
+% \includegraphics[width=20pc]{samplefigure.eps}
+% \caption{caption here}
+% \label{label_here}
+% \end{sidewaysfigure}
+%
+%
+%
+% \begin{sidewaystable}
+% \caption{}
+% \begin{tabular}
+% Table layout here.
+% \end{tabular}
+% \end{sidewaystable}
+%
+%

### 2023-03-30 paper/letter/response_letter.tex
feat(paper): :memo: 准备返修论文

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{svg}
\usepackage{xr}
\usepackage{amsthm,cite,url,graphicx,booktabs,lipsum,color,bm,caption,subcaption,soul}
\usepackage{pifont,tikz,paralist,multirow,amssymb}
\usepackage{xifthen}
\usepackage{enumerate}
\usepackage{titlesec}
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
%\renewcommand{\thepoint}{C\,\thereviewer.\arabic{point}}

\renewcommand{\thepoint}{Comment\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses

\newenvironment{point1}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Associate Editor Comment~}} ---\ }
   {\par }

\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

% \newenvironment{point}

%    {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~\thepoint} } ---\ }
%    {\par }

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}   \bigskip \noindent
	{\textbf{Reviewer~Point~\thepoint} } ---~#1  }

\newenvironment{reply}
   {\medskip \noindent \color{blue} \begin{sf}\textbf{Reply}:\  }
   {\medskip \par \end{sf}}

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}

\myexternaldocument{main}
%\externaldocument[I-]{main}

\def\thesubsubsection{\arabic{subsubsection}}
\titleformat{\subsubsection}[runin]
{\normalfont\bfseries}
{\indent\thesubsubsection)}{0.5em}{}

\begin{document}
\section*{Notes on revision made to manuscript Paper $\#$ABC-2099-12-1234
}
\vspace{10pt}

The authors would like to thank the editor and reviewers for their constructive comments and suggestions that have helped improve the quality of this manuscript. The manuscript has undergone a thorough revision according to the editor and reviewers’ comments. Please see below our responses. For the reviewers’ convenience, we have highlighted significant changes in the revised manuscript in \textcolor{blue}{blue}.

% Let's start point-by-point with Reviewer 1

\section*{Response to the Associate Editor}
% General intro text goes here
\begin{point1}

    Dear Authors, thanks for the submission of the manuscript. We have asked two experts in the relevant fields to review the manuscript. Both reviewers overall find the merit in the manuscript however they also noted several major issues in the current manuscript. With my own reading, I fully agree with the reviewers and would like to highlight a few major issues:

    1. Overall the results and discussion are relatively shallow and I would encourage the authors to do deep dive into the results, e.g. change points, as also pointed out by both reviewers,

    2. I fully agree with Reviewer \#2 that more thorough review of existing and relevant indicators with IWGI, and

    3. I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer \#1. In addition, I find the data in supplementary materials is not accessible, which should be amended. The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously. Overall, based on the reviewers' recommendations, I would like to ask the authors to submit a suitably revised manuscript in due course.
\end{point1}

\begin{reply}
\input{response_v6/associate_editor.tex}

\end{reply}

\section*{Response to the reviewers}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection
% General intro text goes here

% Point one description

%%%%%%%%%%%%%%%%
\begin{point}
	In the new submission, the paper should be read and corrected by a native English speaker as there are several verbal and syntactic errors. Also, the references should be checked and provided correctly. \label{comment_11}
\end{point}

% Our reply
\begin{reply}
	Thank you so much for your constructive comments. We have thus scrutinized the manuscript and corrected the grammar errors and typos.  Also, we have also corrected the format errors in the references.
\end{reply}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection

%%%%%%%%%%%%%%%%
\begin{point}
\label{comment_21}a
\end{point}

\begin{reply}
 Thank you so much for your constructive comments.
\end{reply}

%%%%%%%%%%%%%%%%
\begin{point}
\label{comment_22}
\end{point}

\begin{reply}
 Thank you so much for your constructive comments.
\end{reply}
%%%%%%%%%%%%%%%%
\begin{point}

\end{point}

\begin{reply}
 Thank you so much for your constructive comments.
\end{reply}
%%%%%%%%%%%%%%%%
\begin{point}
\label{comment_31}
\end{point}

\begin{reply}
 Thank you so much for your constructive comments.
\end{reply}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection

%%%%%%%%%%%%%%%%
\begin{point}

\end{point}

\begin{reply}
 Thank you so much for your constructive comments.
\end{reply}

%\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv,mybibfile}
\end{document}

\begin{point}

\end{point}

\begin{reply}

\end{reply}

### 2023-03-30 paper/letter/response_v6/associate_editor.tex
feat(paper): :memo: 准备返修论文

Dear Associate Editor,

Thank you for your constructive comments and for providing us with the opportunity to address the concerns raised by both reviewers. We appreciate the valuable feedback, which has helped us identify areas for improvement in our manuscript. We have carefully considered each point and have made substantial revisions to address these issues. Please find our detailed responses to the highlighted concerns below.

Shallow results and discussion:
We acknowledge the need for a more in-depth analysis of our results. We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers. We have also provided more context and explanation for these changes in the manuscript, which can be found on pages 14-16 and 18-21.
Review of existing and relevant indicators with IWGI:
We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI. We have added a new section in the manuscript discussing these indicators, comparing and contrasting their strengths and weaknesses, and explaining how our approach fills the gaps in the current literature. This new section can be found on pages 5-7.
More recent data (beyond 2013):
We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis, extending our dataset up to 2021. The updated data, along with the revised results and discussion, can be found on pages 11-13 and 18-21.
Accessibility of supplementary materials:
We apologize for the inconvenience caused by the inaccessibility of the supplementary materials. We have rectified this issue by ensuring that all supplementary data and files are now accessible and properly linked within the manuscript. We have also provided a clear description of the data and methodology in the supplementary materials to facilitate reproducibility of our results.
We hope that these revisions address the concerns raised by both reviewers and the associate editor. We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community. We look forward to your further feedback and the possibility of our manuscript being accepted for publication.

Sincerely,

[Your Name]
[Your Affiliation]

### 2023-04-01 regimes_yrb/allocation.py
refactor(notebooks): :recycle: 将必要的结构重构到脚本

@@ -1,0 +1,94 @@
+#!/usr/bin/env python 3.11.0
+# -*-coding:utf-8 -*-
+# @Author  : Shuang (Twist) Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Website: https://cv.songshgeo.com/
+
+import numpy as np
+import pandas as pd
+
+from regimes_yrb.tools.statistic import ratio_contribution
+
+
+def calculate_yearly_indices(
+    region_consumption: pd.DataFrame, year: int
+) -> dict:
+    """
+    计算指定年份的水资源分配熵指数。
+
+    参数:
+    region_consumption (pd.DataFrame): 按年份和区域分组的用水量数据
+    year (int): 需要计算指数的年份
+
+    返回:
+    dict: 该年份的水资源分配熵指数数据，包含以下键值：
+          - "Regions": 区域间熵指数
+          - "Divisions": 部门间熵指数
+          - "Sectors": 总体熵指数
+          - "Ratio": 区域间与部门间熵指数之比
+    """
+    data = region_consumption.loc[year].replace(0.0, 0.0000000001)
+    region_p = data.sum(axis=1) / data.sum().sum()
+    region_entropy = np.sum(-region_p * np.log(region_p))
+
+    section_entropy = (
+        data.apply(lambda row: row / row.sum(), axis=0)
+        .apply(lambda row: row.apply(lambda p: -p * np.log(p)).sum(), axis=0)
+        .mean()
+    )
+    section_max_p = data.sum() / data.sum().sum()
+    section_max_entropy = section_max_p.apply(lambda p: -p * np.log(p)).sum()
+    # section_index = section_entropy / section_max_entropy
+
+    index_ratio = region_entropy / -np.log(1 / 4)
+
+    return {
+        "Regions": region_entropy,
+        "Divisions": section_entropy,
+        "Sectors": section_max_entropy,
+        "Ratio": index_ratio,
+    }
+
+
+def calculate_water_consumption_indices(city_yr: pd.DataFrame) -> pd.DataFrame:
+    """
+    计算每年各区域的总用水，并计算区域间、部门间以及总体的水资源分配熵指数。
+
+    参数:
+    city_yr (pd.DataFrame): 城市年度用水数据，包含以下列：
+                             - "Year": 年份
+                             - "Region": 区域
+                             - "IRR": 农业用水
+                             - "IND": 工业用水
+                             - "RUR": 农村生活用水
[…]

### 2023-04-01 regimes_yrb/index.py

@@ -1,0 +1,105 @@
+#!/usr/bin/env python 3.11.0
+# -*-coding:utf-8 -*-
+# @Author  : Shuang (Twist) Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Website: https://cv.songshgeo.com/
+
+import numpy as np
+import pandas as pd
+
+from regimes_yrb.tools.statistic import pettitt_change_points, zscore
+
+# 设置探索断点的显著性阈值
+p_shr = 0.0005
+
+# 第二种 Z-score 标准化方法，对断点无影响
+# def zscore(x):
+#     average = x.mean(numeric_only=True)
+#     stddev = x.std()
+#     return (x-average)/stddev
+
+
+# # 第三种 [-1, 1] 之间的标准化，也对断点无影响
+# def zscore(x):
+#     return (x-x.mean(numeric_only=True))/(x.max()-x.min())
+
+
+def integrated_water_governance_index(
+    scarcity: np.ndarray,
+    priority: np.ndarray,
+    allocation: np.ndarray,
+    norm: str = "log_zscore",
+) -> pd.DataFrame:
+    """计算综合水治理指数 Integrated Water Governance Index."""
+    # 计算 iwgi 指数
+    data = pd.DataFrame({"S": scarcity, "P": priority, "A": allocation})
+    if norm == "log_zscore":
+        norm_data = data.apply(np.log).apply(zscore)
+    else:
+        raise KeyError("'norm' must be 'log_zscore' or 'zscore'")
+    norm_data["IWGI"] = norm_data.sum(axis=1) / 3
+    return norm_data
+
+
+def calc_contribution(iwgi, threshold, span=5):
+    """计算每个阶段的贡献度"""
+    priority = iwgi["P"]
+    allocation = iwgi["A"]
+    scarcity = iwgi["S"]
+
+    dims = ["P", "A", "S"]  # 数据集字典的键
+    contribution = {index: [] for index in dims}  # 用于储存贡献率计算结果的字典
+    periods = []  # 用于储存时间段划分的空列表
+    changes = {}  # 储存每个时间段的变化
+
+    # 寻找断点
+    breakpoints = pettitt_change_points(iwgi["IWGI"], p_shr=threshold)
+    change_points = breakpoints.copy()
+    change_points.extend([iwgi.index.max(), iwgi.index.min()])  # 为断点增加头尾
[…]

### 2023-04-01 regimes_yrb/plot.py

@@ -1,0 +1,269 @@
+#!/usr/bin/env python 3.11.0
+# -*-coding:utf-8 -*-
+# @Author  : Shuang (Twist) Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Website: https://cv.songshgeo.com/
+
+import os
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+# 如果没有ternary包，就 uncommand 下面一行进行安装
+# pip install python-ternary
+import ternary
+from hydra import compose, initialize
+from matplotlib.gridspec import GridSpec
+from scipy import stats
+
+from regimes_yrb.tools.statistic import (
+    get_optimal_fit_linear,
+    plot_pittitt_change_points,
+    plot_ratio_contribution,
+    zscore,
+)
+
+# 加载项目层面的配置
+with initialize(version_base=None, config_path="../config"):
+    cfg = compose(config_name="config")
+os.chdir(cfg.root)
+
+plt.rcParams["xtick.direction"] = "in"
+plt.rcParams["ytick.direction"] = "out"
+
+COLORS = cfg.style.colors
+period_colors = COLORS.period
+region_colors = COLORS.region
+index_colors = COLORS.index
+
+index_colormap = matplotlib.colors.ListedColormap(index_colors, "indexed")
+total_water_use_color = COLORS.total_WU
+
+
+def plot_data(
+    data1, data2, change_points, ylabel1, ylabel2, denominator_label
+):
+    """绘制指标的以及它们的贡献"""
+    fig = plt.figure(figsize=(8, 3), constrained_layout=True)
+    gs = GridSpec(1, 2, figure=fig, width_ratios=[3, 4])
+    ax1 = fig.add_subplot(gs[0, 0])
+    ax2 = fig.add_subplot(gs[0, 1])
+
+    plot_pittitt_change_points(
+        data1, change_points=change_points, ax=ax1, colors=period_colors
+    )
+    plot_ratio_contribution(
+        data2,
+        ax=ax2,
+        colors=region_colors,
+        denominator_color=total_water_use_color,
+        denominator_label=denominator_label,
+    )
+
+    ax1.set_ylabel(ylabel1)
+    ax1.set_xlabel("Year")
+
+    ax2.set_xlabel("Different periods")
+    ax2.set_ylabel(ylabel2)
[…]

### 2023-04-01 regimes_yrb/priority.py

@@ -1,0 +1,92 @@
+#!/usr/bin/env python 3.11.0
+# -*-coding:utf-8 -*-
+# @Author  : Shuang (Twist) Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Website: https://cv.songshgeo.com/
+
+from typing import Iterable, LiteralString, TypeAlias
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+from .tools.statistic import (
+    plot_pittitt_change_points,
+    plot_ratio_contribution,
+    ratio_contribution,
+)
+
+Columns: TypeAlias = Iterable[LiteralString]
+
+
+def direct_ratio(
+    data: pd.DataFrame, direct: Columns, indirect: Columns
+) -> pd.DataFrame:
+    """计算直接用水比例"""
+    # 间接用水量
+    direct_wu = data.loc[:, direct]
+    # 总用水量
+    total_water_use = data.loc[:, [*direct, *indirect]].sum(
+        axis=1, numeric_only=True
+    )
+    # 整个流域的间接惠益用水占比
+    priority = direct_wu.sum(axis=1) / total_water_use
+    # 计算贡献
+    contributions = ratio_contribution(
+        numerator=direct_wu, denominator=total_water_use
+    )
+    return priority, contributions
+
+
+# def plot_priority(priority, contributions):
+#     # 绘图
+#     fig = plt.figure(figsize=(8, 3), constrained_layout=True)
+#     gs = GridSpec(1, 2, figure=fig, width_ratios=[3, 4])
+#     ax1 = fig.add_subplot(gs[0, 0])
+#     ax2 = fig.add_subplot(gs[0, 1])
+
+#     # 绘制图1
+#     plot_pittitt_change_points(
+#         priority, change_points=[1977, 1993], ax=ax1, colors=period_colors
+#     )
+
+#     # 绘制图2
+#     plot_ratio_contribution(
+#         contributions,
+#         ax=ax2,
+#         colors=region_colors,
+#         denominator_color=total_water_use_color,
+#         denominator_label="Total",
+#     )
+
+#     # 修饰图1
+#     ax1.set_ylabel("Indirect Proportion of Water Use, configuration")
+#     ax1.set_xlabel("Year")
+#     # ax1.set_yticks(np.arange(0.08, 0.21, 0.04))
[…]

### 2023-04-01 regimes_yrb/scarcity.py

@@ -1,0 +1,257 @@
+#!/usr/bin/env python 3.11.0
+# -*-coding:utf-8 -*-
+# @Author  : Shuang (Twist) Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Website: https://cv.songshgeo.com/
+
+from typing import Iterable, LiteralString, TypeAlias
+
+import numpy as np
+import pandas as pd
+from matplotlib import pyplot as plt
+
+Columns: TypeAlias = Iterable[LiteralString]
+
+SITE_COLS = {
+    "唐乃亥": "SR",  # 唐乃亥控制源区
+    "头道拐": "UR",  # 头道拐控制上游
+    "花园口": "MR",  # 花园口控制中游
+    "利津": "DR",  # 利津控制下游
+}
+
+regions = ["SR", "UR", "MR", "DR"]
+
+
+def measure_runoff(runoff, cite_cols):
+    """加载径流数据"""
+    # 加载径流和水库数据
+    measured_runoff = pd.read_csv(runoff, index_col="年份")
+    measured_runoff = measured_runoff.loc[:, cite_cols.keys()]
+    measured_runoff.rename(cite_cols, axis=1, inplace=True)
+    return measured_runoff
+
+
+def load_reservoirs_data(reservoirs):
+    """加载水库数据"""
+    # 水库库容数据
+    reservoirs_capacity = pd.read_csv(reservoirs, index_col=0)
+
+    # 水库库容累积相加数据
+    return reservoirs_capacity.cumsum()
+
+
+def calculate_index_a(
+    runoff: pd.DataFrame,
+    consumptions: pd.DataFrame,
+    total_col: str = "Total water use",
+) -> pd.DataFrame:
+    """
+    计算指数 A: 总耗水量 / 平均多年径流量
+
+    Args:
+        measured_runoff (pd.DataFrame): 指示流域径流量的 DataFrame。
+        consumptions (pd.DataFrame): 包含用水数据的 DataFrame。
+
+    Returns:
+        pd.DataFrame: 包含指数 A 的 DataFrame。
+    """
+    total_water_use = consumptions.pivot_table(
+        index="Year", columns="Region", aggfunc=np.sum, values=total_col
+    )
+    results = total_water_use.apply(
+        lambda row: row / runoff.mean(axis=0), axis=1
+    )
+    return results[["SR", "UR", "MR", "DR"]]
+
+
[…]

### 2023-04-01 regimes_yrb/tools/statistic.py

@@ -15,7 +15,7 @@ from matplotlib import pyplot as plt
 def line_fit(x, y):
     N = float(len(x))
     sx, sy, sxx, syy, sxy = 0, 0, 0, 0, 0
-    for i in range(0, int(N)):
+    for i in range(int(N)):
         sx += x[i]
         sy += y[i]
         sxx += x[i] * x[i]
@@ -26,8 +26,18 @@ def line_fit(x, y):
     r = abs(sy * sx / N - sxy) / math.sqrt(
         (sxx - sx * sx / N) * (syy - sy * sy / N)
     )
-    formula = r"$k = %10.2f; R^2 =%10.2f$" % (a, r)
-    return formula
+    return r"$k = %10.2f; R^2 =%10.2f$" % (a, r)
+
+
+def get_optimal_fit_linear(x_arr, y_arr):
+    from scipy import optimize
+
+    def linear(x, slope, intercept):
+        return slope * x + intercept
+
+    k, b = optimize.curve_fit(linear, x_arr, y_arr)[0]  # optimize
+    y_sim = linear(x_arr, k, b)  # simulated y
+    return y_sim, k, b
 
 
 def compile_cols(data, col1, col2):
@@ -41,9 +51,7 @@ def compile_cols(data, col1, col2):
     # 3.分别对final进行赋值
     df_test_bigger["Value_Final"] = df_test_bigger[col1]
     df_test_litter["Value_Final"] = df_test_litter[col2]
-    # 4.使用concat函数将其聚合
-    df_result = pd.concat([df_test_bigger, df_test_litter])
-    return df_result
+    return pd.concat([df_test_bigger, df_test_litter])
 
 
 def normalization(data):
@@ -54,30 +62,28 @@ def normalization(data):
 def huanbi_rate(data, use_col, new_col):
     data = data.reset_index()
     result = []
-    for i in range(0, len(data)):
+    for i in range(len(data)):
         if i == 0:
             rate = np.nan
-            result.append(rate)
         else:
             rate = format(
                 (data[use_col][i] - data[use_col][i - 1])
                 / data[use_col][i - 1],
                 ".2%",
             )
-            result.append(rate)
+        result.append(rate)
     data[new_col] = result
 
 
 def difference(data, use_col, new_col):
     data = data.reset_index()
     result = []
-    for i in range(0, len(data)):
+    for i in range(len(data)):
         if i == 0:
             rate = np.nan
[…]

### 2023-04-02 regimes_yrb/allocation.py
refactor(project): :recycle: 将三个指数拆开

@@ -8,12 +8,10 @@
 import numpy as np
 import pandas as pd
 
-from regimes_yrb.tools.statistic import ratio_contribution
+from regimes_yrb.tools.statistic import pettitt_changes, ratio_contribution
 
 
-def calculate_yearly_indices(
-    region_consumption: pd.DataFrame, year: int
-) -> dict:
+def calculate_yearly_indices(region_consumption: pd.DataFrame, year: int) -> dict:
     """
     计算指定年份的水资源分配熵指数。
 
@@ -73,9 +71,7 @@ def calculate_water_consumption_indices(city_yr: pd.DataFrame) -> pd.DataFrame:
     """
     wu_cols = ["IRR", "IND", "DOM"]
     city_yr["DOM"] = city_yr["RUR"] + city_yr["URB"]  # 人居耗水
-    region_consumption = city_yr.groupby(["Year", "Region"])[
-        wu_cols
-    ].sum()  # 每个区域的总耗水量
+    region_consumption = city_yr.groupby(["Year", "Region"])[wu_cols].sum()  # 每个区域的总耗水量
 
     results = {
         yr: calculate_yearly_indices(region_consumption, yr)
@@ -90,5 +86,6 @@ def entropy_and_contribution(data):
     entropy_contributions = ratio_contribution(
         numerator=index_result[["Sectors", "Regions"]],
         denominator=index_result["Divisions"],
+        breakpoints=pettitt_changes(index_result["Ratio"]),
     )
     return index_result["Ratio"], entropy_contributions

### 2023-04-02 regimes_yrb/index.py

@@ -7,22 +7,9 @@
 
 import numpy as np
 import pandas as pd
+from scipy import stats
 
-from regimes_yrb.tools.statistic import pettitt_change_points, zscore
-
-# 设置探索断点的显著性阈值
-p_shr = 0.0005
-
-# 第二种 Z-score 标准化方法，对断点无影响
-# def zscore(x):
-#     average = x.mean(numeric_only=True)
-#     stddev = x.std()
-#     return (x-average)/stddev
-
-
-# # 第三种 [-1, 1] 之间的标准化，也对断点无影响
-# def zscore(x):
-#     return (x-x.mean(numeric_only=True))/(x.max()-x.min())
+from regimes_yrb.tools.statistic import get_optimal_fit_linear, pettitt_changes, zscore
 
 
 def integrated_water_governance_index(
@@ -35,11 +22,18 @@ def integrated_water_governance_index(
     # 计算 iwgi 指数
     data = pd.DataFrame({"S": scarcity, "P": priority, "A": allocation})
     if norm == "log_zscore":
-        norm_data = data.apply(np.log).apply(zscore)
+        results = data.apply(np.log).apply(zscore)
     else:
         raise KeyError("'norm' must be 'log_zscore' or 'zscore'")
-    norm_data["IWGI"] = norm_data.sum(axis=1) / 3
-    return norm_data
+    results["IWGI"] = results.sum(axis=1) / 3
+    breakpoints = pettitt_changes(results["IWGI"])
+    results.loc[results.index < breakpoints[0], "stage"] = "P1"
+    results.loc[
+        (breakpoints[0] <= results.index) & (results.index < breakpoints[1]),
+        "stage",
+    ] = "P2"
+    results.loc[breakpoints[1] <= results.index, "stage"] = "P3"
+    return results
 
 
 def calc_contribution(iwgi, threshold, span=5):
@@ -54,7 +48,7 @@ def calc_contribution(iwgi, threshold, span=5):
     changes = {}  # 储存每个时间段的变化
 
     # 寻找断点
-    breakpoints = pettitt_change_points(iwgi["IWGI"], p_shr=threshold)
+    breakpoints = pettitt_changes(iwgi["IWGI"], p_shr=threshold)
     change_points = breakpoints.copy()
     change_points.extend([iwgi.index.max(), iwgi.index.min()])  # 为断点增加头尾
[…]

### 2023-04-02 regimes_yrb/plot.py

@@ -6,22 +6,21 @@
 # Website: https://cv.songshgeo.com/
 
 import os
+from typing import List, Optional
 
 import matplotlib
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
-
-# 如果没有ternary包，就 uncommand 下面一行进行安装
-# pip install python-ternary
-import ternary
+import ternary  # pip install python-ternary
 from hydra import compose, initialize
 from matplotlib.gridspec import GridSpec
 from scipy import stats
 
 from regimes_yrb.tools.statistic import (
     get_optimal_fit_linear,
-    plot_pittitt_change_points,
+    pettitt_changes,
+    plot_pettitt_change_points,
     plot_ratio_contribution,
     zscore,
 )
@@ -44,7 +43,12 @@ total_water_use_color = COLORS.total_WU
 
 
 def plot_data(
-    data1, data2, change_points, ylabel1, ylabel2, denominator_label
+    index,
+    contribution,
+    ylabel1: str = "Index_Y_label",
+    ylabel2: str = "Contribution_Y_label",
+    denominator_label: str = "Denominator",
+    change_points: Optional[List[int]] = None,
 ):
     """绘制指标的以及它们的贡献"""
     fig = plt.figure(figsize=(8, 3), constrained_layout=True)
@@ -52,11 +56,11 @@ def plot_data(
     ax1 = fig.add_subplot(gs[0, 0])
     ax2 = fig.add_subplot(gs[0, 1])
 
-    plot_pittitt_change_points(
-        data1, change_points=change_points, ax=ax1, colors=period_colors
+    plot_pettitt_change_points(
+        index, change_points=change_points, ax=ax1, colors=period_colors
     )
     plot_ratio_contribution(
-        data2,
+        contribution,
         ax=ax2,
         colors=region_colors,
         denominator_color=total_water_use_color,
@@ -70,7 +74,7 @@ def plot_data(
     ax2.set_ylabel(ylabel2)
     ax2.tick_params(axis="x", tickdir="in", bottom=False, labelrotation=0)
     ax2.axhline(0.0, lw=2, color="gray")
-    ax2.set_ylim(-0.08, 0.08)
+    # ax2.set_ylim(-0.08, 0.08)
     ax2.set_yticks(np.arange(-0.08, 0.081, 0.04))
     ax2.axvline(1.5, ls=":", color="gray", lw=1.5)
     ax2.axvline(0.5, ls=":", color="gray", lw=1.5)
[…]

### 2023-04-02 regimes_yrb/priority.py

@@ -7,86 +7,25 @@
 
 from typing import Iterable, LiteralString, TypeAlias
 
-import matplotlib.pyplot as plt
-import numpy as np
 import pandas as pd
 
-from .tools.statistic import (
-    plot_pittitt_change_points,
-    plot_ratio_contribution,
-    ratio_contribution,
-)
+from .tools.statistic import pettitt_changes, ratio_contribution
 
 Columns: TypeAlias = Iterable[LiteralString]
 
 
-def direct_ratio(
-    data: pd.DataFrame, direct: Columns, indirect: Columns
-) -> pd.DataFrame:
+def direct_ratio(data: pd.DataFrame, direct: Columns, indirect: Columns) -> pd.DataFrame:
     """计算直接用水比例"""
     # 间接用水量
     direct_wu = data.loc[:, direct]
     # 总用水量
-    total_water_use = data.loc[:, [*direct, *indirect]].sum(
-        axis=1, numeric_only=True
-    )
+    total_water_use = data.loc[:, [*direct, *indirect]].sum(axis=1, numeric_only=True)
     # 整个流域的间接惠益用水占比
     priority = direct_wu.sum(axis=1) / total_water_use
     # 计算贡献
     contributions = ratio_contribution(
-        numerator=direct_wu, denominator=total_water_use
+        numerator=direct_wu,
+        denominator=total_water_use,
+        breakpoints=pettitt_changes(priority),
     )
     return priority, contributions
-
-
-# def plot_priority(priority, contributions):
-#     # 绘图
-#     fig = plt.figure(figsize=(8, 3), constrained_layout=True)
-#     gs = GridSpec(1, 2, figure=fig, width_ratios=[3, 4])
-#     ax1 = fig.add_subplot(gs[0, 0])
-#     ax2 = fig.add_subplot(gs[0, 1])
-
-#     # 绘制图1
-#     plot_pittitt_change_points(
-#         priority, change_points=[1977, 1993], ax=ax1, colors=period_colors
-#     )
-
-#     # 绘制图2
-#     plot_ratio_contribution(
-#         contributions,
-#         ax=ax2,
-#         colors=region_colors,
-#         denominator_color=total_water_use_color,
-#         denominator_label="Total",
-#     )
-
-#     # 修饰图1
[…]

### 2023-04-02 regimes_yrb/tools/plot_support.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python 3.11.0
+# -*-coding:utf-8 -*-
+# @Author  : Shuang (Twist) Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Website: https://cv.songshgeo.com/
+
+
+# 使用图片的比例来定位
+def get_position_by_ratio(ax, x_ratio, y_ratio):
+    """
+    使用图片的比例来返回定位，从而更好的控制说明文字的位置
+    ax: 一个 matplotlib 的画图轴对象
+    x_ratio: 横坐标的比例位置
+    y_ratio: 纵坐标的比例位置
+    """
+    x_min, x_max = ax.get_xlim()
+    y_min, y_max = ax.get_ylim()
+    x = (x_max - x_min) * x_ratio + x_min
+    y = (y_max - y_min) * y_ratio + y_min
+    return x, y

### 2023-04-02 regimes_yrb/tools/statistic.py

@@ -5,7 +5,6 @@
 # project: WGRegimes_YRB_2020
 
 import math
-import os
 
 import numpy as np
 import pandas as pd
@@ -23,9 +22,7 @@ def line_fit(x, y):
         sxy += x[i] * y[i]
     a = (sy * sx / N - sxy) / (sx * sx / N - sxx)
     # b = (sy - a * sx) / N
-    r = abs(sy * sx / N - sxy) / math.sqrt(
-        (sxx - sx * sx / N) * (syy - sy * sy / N)
-    )
+    r = abs(sy * sx / N - sxy) / math.sqrt((sxx - sx * sx / N) * (syy - sy * sy / N))
     return r"$k = %10.2f; R^2 =%10.2f$" % (a, r)
 
 
@@ -67,8 +64,7 @@ def huanbi_rate(data, use_col, new_col):
             rate = np.nan
         else:
             rate = format(
-                (data[use_col][i] - data[use_col][i - 1])
-                / data[use_col][i - 1],
+                (data[use_col][i] - data[use_col][i - 1]) / data[use_col][i - 1],
                 ".2%",
             )
         result.append(rate)
@@ -88,7 +84,8 @@ def difference(data, use_col, new_col):
 
 
 # Pettitt 断点检测法
-def Pettitt_change_point_detection(inputdata, p_shr=0.05):
+def pettitt_change_point_detection(inputdata, p_shr=0.05):
+    """使用一次 Pettitt 断点检测"""
     index = inputdata.index
     inputdata = np.array(inputdata.values)
     n = inputdata.shape[0]
@@ -106,18 +103,17 @@ def Pettitt_change_point_detection(inputdata, p_shr=0.05):
 
 
 # 循环检测所有显著的断点
-def pettitt_change_points(inputdata, p_shr=0.001):
+def pettitt_changes(inputdata, p_shr=0.001):
+    """根据给定阈值进行循环，找到所有断点"""
     change_points = []
     detect_series = [inputdata]
     while detect_series:
         tmp_detect = []
         for series in detect_series:
-            K, Pettitt_result = Pettitt_change_point_detection(
-                series, p_shr=p_shr
-            )
-            if Pettitt_result["突变程度"] == "显著":
-                change_points.append(K)
-                tmp_detect.extend([series.loc[: K - 1], series.loc[K + 1 :]])
+            k, pettitt_result = pettitt_change_point_detection(series, p_shr=p_shr)
+            if pettitt_result["突变程度"] == "显著":
+                change_points.append(k)
[…]

### 2023-04-02 regimes_yrb/tools/statistic.py
feat(notebooks): :art: 绘制各个阶段的相关图

@@ -4,11 +4,13 @@
 # Email: SongshGeo@Gmail.com
 # project: WGRegimes_YRB_2020
 
+import itertools
 import math
 
 import numpy as np
 import pandas as pd
 from matplotlib import pyplot as plt
+from scipy.stats import pearsonr
 
 
 def line_fit(x, y):
@@ -337,3 +339,38 @@ def zscore(arr: np.ndarray) -> np.ndarray:
 def norm_zscore(arr: np.ndarray) -> np.ndarray:
     """先取对数，再最大-最小值归一化，所有数据映射到0-1之间"""
     return zscore(np.log(arr))
+
+
+def calc_correlation(
+    data: pd.DataFrame, columns: list = None, significance_level: float = 0.01
+) -> pd.DataFrame:
+    """
+    计算 DataFrame 中指定的 4 列之间两两的相关系数和显著性水平。
+
+    参数:
+        data (pd.DataFrame): 输入的 DataFrame。
+        columns (list): 列名列表，包含需要计算相关系数的 4 列。
+        significance_level (float): 显著性水平（0 到 1 之间的值，例如 0.05）。
+
+    返回:
+        dict: 关于相关系数和显著性的字典。
+    """
+
+    if columns is None:
+        columns = data.select_dtypes(include="number").columns.tolist()
+
+    correlations = {}
+
+    for col1, col2 in itertools.combinations(columns, 2):
+        corr, p_value = pearsonr(data[col1], data[col2])
+
+        is_significant = (
+            "Significant" if p_value < significance_level else "Not Significant"
+        )
+        correlations[f"{col1} vs {col2}"] = {
+            "correlation": corr,
+            "p_value": p_value,
+            "significance": is_significant,
+        }
+
+    return pd.DataFrame(correlations)

### 2023-04-02 regimes_yrb/scarcity.py
refactor(notebooks): :recycle: 重构SFV贡献度的分解

@@ -59,17 +59,13 @@ def calculate_index_a(
     total_water_use = consumptions.pivot_table(
         index="Year", columns="Region", aggfunc=np.sum, values=total_col
     )
-    results = total_water_use.apply(
-        lambda row: row / runoff.mean(axis=0), axis=1
-    )
+    results = total_water_use.apply(lambda row: row / runoff.mean(axis=0), axis=1)
     return results[["SR", "UR", "MR", "DR"]]
 
 
 def calculate_index_b(runoff, consumptions, inflexible_wu) -> pd.DataFrame:
     """计算指数 B: 总不灵活耗水量 / 平均多年径流量"""
-    consumptions["_inflexible_wu"] = consumptions.loc[:, inflexible_wu].sum(
-        axis=1
-    )
+    consumptions["_inflexible_wu"] = consumptions.loc[:, inflexible_wu].sum(axis=1)
     inflexible_water_use = consumptions.pivot_table(
         index="Year",
         columns="Region",
@@ -77,15 +73,11 @@ def calculate_index_b(runoff, consumptions, inflexible_wu) -> pd.DataFrame:
         values="_inflexible_wu",
     )
     del consumptions["_inflexible_wu"]
-    results = inflexible_water_use.apply(
-        lambda row: row / runoff.mean(axis=0), axis=1
-    )
+    results = inflexible_water_use.apply(lambda row: row / runoff.mean(axis=0), axis=1)
     return results[["SR", "UR", "MR", "DR"]]
 
 
-def calculate_index_c(
-    runoff: pd.DataFrame, reservoirs: pd.DataFrame
-) -> pd.DataFrame:
+def calculate_index_c(runoff: pd.DataFrame, reservoirs: pd.DataFrame) -> pd.DataFrame:
     """
     计算指数 C。
 
@@ -98,9 +90,7 @@ def calculate_index_c(
     """
     index_c1 = runoff.std() / runoff.mean()
     avg_runoff = runoff.mean(axis=0)
-    index_c2 = reservoirs.apply(lambda row: row / avg_runoff, axis=1).clip(
-        upper=1
-    )
+    index_c2 = reservoirs.apply(lambda row: row / avg_runoff, axis=1).clip(upper=1)
     return (1 - index_c2) * index_c1
 
 
@@ -151,107 +141,6 @@ def calc_sfv(runoff, consumptions, reservoirs, inflexible_wu):
[…]

### 2023-04-02 regimes_yrb/tools/statistic.py

@@ -6,6 +6,7 @@
 
 import itertools
 import math
+from typing import List, Optional
 
 import numpy as np
 import pandas as pd
@@ -374,3 +375,45 @@ def calc_correlation(
         }
 
     return pd.DataFrame(correlations)
+
+
+def calc_contribution_ratio(
+    data: pd.DataFrame,
+    columns: Optional[list] = None,
+    start_yr: Optional[int] = None,
+    end_yr: Optional[int] = None,
+) -> pd.DataFrame:
+    """
+    计算指定时间段内列对其均值变化的贡献比例。
+
+    参数:
+        data (pd.DataFrame): 输入的 DataFrame，索引为时间序列，包含 A、B 和 C 三列。
+        start_date (str): 时间段的开始日期，格式为 'YYYY-MM-DD'。
+        end_date (str): 时间段的结束日期，格式为 'YYYY-MM-DD'。
+
+    返回:
+        dict: A、B 和 C 三列在指定时间段内对 SUM 变化的贡献比例。
+    """
+    if columns is None:
+        columns = data.select_dtypes(include=["number"]).columns.to_list()
+    if start_yr is None:
+        start_yr = data.index.min()
+    if end_yr is None:
+        end_yr = data.index.max()
+
+    # 检查输入数据是否包含 A、B 和 C 列
+    if not all(col in data.columns for col in columns):
+        raise ValueError("Please ensure the input DataFrame contains columns.")
+
+    # 根据指定的时间范围筛选数据
+    data = data.loc[start_yr:end_yr]
+
+    # 计算 SUM 列的变化量
+    delta_sum = data[columns].mean(axis=1).diff().sum()
+
+    contribution_ratio = {}
+    # 计算 A、B 和 C 三列的变化量
+    for col in columns:
+        delta = data[col].diff().sum() / len(columns)
+        contribution_ratio[col] = delta / delta_sum
+    return pd.Series(contribution_ratio)

### 2023-05-07 paper/letter/response_letter/AR_to_RC/response_letter.tex
build(paper): :building_construction: 重新配置回复信模板

% chktex-file 10
\documentclass{article}
	\def\papertitle{Identifying regime transitions for water governance at a basin scale}
	\def\authors{Shuang Song, Shuai Wang}
	\def\journal{Water Resources Research}
	\def\doi{\#2022WR033819}
\input{../templates/AR_to_RC.tex}

\section{Associate Editor}

\subsection{General comments}
\RC{} Dear Authors, thanks for the submission of the manuscript. We have asked two experts in the relevant fields to review the manuscript. Both reviewers overall find the merit in the manuscript however they also noted several major issues in the current manuscript. With my own reading, I fully agree with the reviewers and would like to highlight a few major issues:

\AR{} Thank you for your constructive comments and for providing us with the opportunity to address the concerns raised by both reviewers. We appreciate the valuable feedback, which has helped us identify areas for improvement in our manuscript. We have carefully considered each point and have made substantial revisions to address these issues. Please find our detailed responses to the highlighted concerns below.

\subsection{Issue \#1}
\RC{} overall the results and discussion are relatively shallow and I would encourage the authors to do deep dive into the results, e.g.\ change points, as also pointed out by both reviewers,

\AR{} We acknowledge the need for a more in-depth analysis of our results. We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers. We have also provided more context and explanation for these changes in the manuscript, which can be found on pages 14\-16 and 18\-21.

\subsection{Issue \#2}
\RC{} I fully agree with Reviewer \#2 that more thorough review of existing and relevant indicators with IWGI,

\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI. We have added a new section in the manuscript discussing these indicators, comparing and contrasting their strengths and weaknesses, and explaining how our approach fills the gaps in the current literature. This new section can be found on pages 5\-7.

\subsection{Issue \#3}
\RC{} I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer 1. In addition, I find the data in supplementary materials is not accessible, which should be amended. The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously.

\RC*{} Overall, based on the reviewers' recommendations, I would like to ask the authors to submit a suitably revised manuscript in due course.

\AR{} We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis, extending our dataset up to 2021. The updated data, along with the revised results and discussion, can be found on pages 11-13 and 18-21.

\AR*{} We apologize for the inconvenience caused by the inaccessibility of the supplementary materials. We have rectified this issue by ensuring that all supplementary data and files are now accessible and properly linked within the manuscript. We have also provided a clear description of the data and methodology in the supplementary materials to facilitate reproducibility of our results.

\AR*{} We hope that these revisions address the concerns raised by both reviewers and the associate editor. We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community. We look forward to your further feedback and the possibility of our manuscript being accepted for publication.

\newpage
\section{Reviewer \#1}

\subsection{Overall comments}

\RC{} This study proposed an integrated index that incorporates water resources, water use, and water allocation to represent the water governance regime in the Yellow River basin. The authors showed an in-depth understanding of the water governance in this basin and made a great effort to represent the status of water governance straightforwardly with the integrated index. The figures were generally well-designed and presented clearly. But I feel the paper lacks details of the results which makes it difficult to understand the paper. Specific comments are listed below.

% 感谢您认可。
% 很抱歉缺少细节，可能会使您难以完全理解我们的研究。
% 为了回应您的担忧，我们已经修改了我们的稿件，并提供了更详细的结果解释。请在下面找到我们对您的具体评论的逐条回复。
\AR{} Thank you for your valuable feedback and for acknowledging our efforts in understanding the water governance in the Yellow River basin. We appreciate your comments regarding the clarity of the figures and our integrated index. Sorry about the lack of details in the results section may have made it difficult to fully comprehend our study. In response to your concerns, we have revised our manuscript and provided a more detailed explanation of the results. Please find our point-by-point response to your specific comments below.

\subsection{Major concern \#3}

% 气候变化在指数中没有明确的体现，这可能是本世纪黄河流量恢复的关键因素。气候变化将是未来该流域面临的巨大挑战。重大的气候变化可能影响流域的适应能力，因此需要不同的治理策略。
\RC{} Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。
% 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。
% 我们现在在讨论中涉及了这些话题。
\AR{} Ok, I changed this:

% 我们强调流域治理需要考虑这些因素，但我们可能很难穷尽优秀的流域治理策略需要考虑哪些因素。因此，IWGI至少让我们可以知道在诸多治理因素的共同影响下，流域的未来正在走向何方。
\AR*{}

\subsection{Specific comments \#4}
% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
\RC{} The results are summative. I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions. And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values. These details could help readers understand the reasonability of the results.

\end{document}

### 2023-05-07 paper/letter/response_letter/RC_to_MS/Einstein1905.tex
build(paper): :building_construction: 重新配置回复信模板

\documentclass{article}
	\def\papertitle{The Dark Side of Light}
	\def\authors{A. Einstein}
	\def\journal{Some Journal}
	\def\doi{12345}
\input{../templates/RC_to_MS.tex}

\section{General Comments}

\subsection{Major concern \#1}

\RC Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

\section{Specific Comments}

\subsection{Page 3 Lines 15-22}

\RC This is an awkward paragraph that I do not understand. Please elaborate.

\subsection{Page 4 Line 55}

\begin{quote}
The cat in the box is \hl{dead} by $5\sigma\pm\pi$.
\end{quote}

\RC I am convinced the cat is alive. Please double-check.

\end{document}

### 2023-05-07 paper/letter/response_letter/AR_to_RC/response_letter.tex
docs(paper): :memo: 增加审稿人意见

@@
 	\def\papertitle{Identifying regime transitions for water governance at a basin scale}
-	\def\authors{Shuang Song, Shuai Wang}
+	\def\authors{Shuang Song, Shuai Wang*, Xutong Wu, Yongping Wei, Graeme S. Cumming, Yue Qin, Xilin Wu, Bojie Fu}
 	\def\journal{Water Resources Research}
@@
 
-\subsection{Overall comments}
+\subsection*{Overall comments} % todo
 
@@
 
-\subsection{Major concern \#3}
+\subsection{Major concern \#1}
 
@@
 
-\subsection{Specific comments \#4}
+\subsection{Major concern \#2}
 % 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
@@
 
+\subsection{Major concern \#3}
+% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
+\RC{} The data used in this study seem to have different time periods, and most data are from before 2013.
+The hydrological regime and water governance in the Yellow River should have changed significantly in the recent decade.
+Therefore, incorporating the result from the recent decade would make this study more solid.
+
+\subsection{Major concern \#4}
+% 这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?
+\RC{} There might be interactions/interconnections among the three indicators. Did the authors examine the relations between the indicators?
+
+\subsection{Major concern \#5}
+% IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。
+\RC{} The IWGI includes reservoir storage information in the "stress" aspect.
+However, the water conveyance ability is not represented, which is also an important indicator of water governance/hydrosocial resilience.
+
+\subsection{Major concern \#6}
+% 我建议在标题中加上“黄河流域”。因为没有对IWGI的适用性和有效性进行测试或讨论。它能在其他盆地使用吗?使用索引的先决条件是什么?
+\RC{} I would suggest adding "Yellow River basin" in the title.
+Because the applicability and validity of the IWGI were not tested or discussed.
+Can it be used in other basins?
+What is the prerequisite for using the index?
+
+\subsection{Major concern \#7}
+% 最好在引言部分解释“水治理机制”的概念，然后解释使用综合指数IWGI代表水治理机制的必要性。
+\RC{} It would be better to explain the concept "water governance regime" in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.
+\subsection{Detailed issues}
+
+% 我没有在引用的文献中找到“用水的三个核心方面”。这三个方面是作者提出的吗?
+\RC{} Line 57-62: I did not find the "three core aspects of water use" in the cited reference. Were the three aspects put forward by the authors?
+
+\RC{} Line 92: missing information for the citation?
+
+\RC{} Line 94-95: the sentence is unclear.
+
+\RC{} Line 121: Repeated citation Qin et al. 2019.
+
+\RC{} Line 122: It would be better to introduce the calculation of SFV in the main text.
+
+\RC{} Equation (6): Why is the numerator WUpro not WUnon-pro? Please check the equation.
+
+\RC{} Equation (7): CEM => AEM?
+
+\RC{} Line 154: Please explain the source of irrigated area data.
+
+\RC{} Fig.2A, p<0.01 or p<0.001? (line 147 says that α=0.001 was used for the change-point detection).
+
+\RC{} Fig.2C: How were the directions determined?
+
+\RC{} Fig.3C: What do the dashed lines denote?
+
+\RC{} Line 187: what is "social transformation"?
+
+\RC{} Line 208: the IWGI was proposed in this study, here the citations of Loch's and Turton's studies are not appropriate.
+
+\RC{} Line 273: adapted => adopted?
+
+\RC{} Line 275: biophysical? Please check the sentence.
+
+\newpage
+\section{Reviewer \#2}
+
+\subsection*{Overall comments}
+% 作者提出了IWGI，并将其应用于黄河流域的水治理历史，分析了流域的制度变迁。该方法具有很强的合理性和适应性，案例分析的结果为理解中国的水治理提供了有益的见解。然而，讨论并没有充分利用案例研究分析的结果。讨论结果的内容应该更具有支持性和可靠性。此外，讨论的叙事分析非常有趣，但如果这项研究的原创性之一是识别变化点，那么就需要更多地讨论导致这些变化点的触发因素。请参考我下面的审稿意见并进行修改，以提高本文的价值。
+\RC{} The authors proposed the IWGI, applied the index to the history of water governance in the Yellow River basin, and analyzed the regime change in the basin.
+The methodology is very reasonable and adaptable, and the results of the case analysis provide useful insights for understanding water governance in China.
+However, the discussion does not fully exploit the results of the case study analysis.
+The discussion should be more supportive and solid in its content of the results.
+Also, the narrative analysis of the discussion is very interesting, but if one of the originalities of this study is the identification of change points, more discussion of the triggers that caused these change points is needed.
+Please refer to my review comments below and revise them to enhance the value of this paper.
+
+\AR{} Thanks!
+
+\subsection{Comment \#1}
+% 图1:很难理解B中每个数字的含义。也许是这个数字的大小有问题。
+\RC{} Figure 1: It is difficult to understand what each number in B means. Perhaps it may be a problem with the size of the figure.
+
+\subsection{Comment \#2}
+% 导言:与流域和水资源相关的指标有很多，其中一些指标具有与治理和政策相关的参数。为了突出你所制定的IWGI的新颖性，也许你可以加上对其他相关指标的审查。
+\RC{} Introduction: There are many indicators related to watersheds and water resources, some of which have parameters related to governance and policy.
+To highlight the novelty of the IWGI that you have developed, perhaps you could add a review of other relevant indicators.
+
+\subsection{Comment \#3}
+% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
+\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained. e.g. R or WU.
+
+\subsection{Comment \#4}
+% 第2.2节:您提到您将Pettitt(1979)方法应用于“水文时间序列”，但结果似乎适用于IWGI时间序列数据。请说明您将该方法应用于哪些数据。
+\RC{} Section 2.2: You mention that you apply the Pettitt (1979) approach to "hydrological time series", but the results appear to be for IWGI time series data.
+Please clarify to which data you applied the approach.
+
+\subsection{Comment \#5}
+% 图3:D中哪些类型的官方文件被统计以及如何统计?
+\RC{} Figure 3: What types of official documents in D are counted and how?
+
+\subsection{Comment \#6}
+% 讨论:每个政权的故事都令人印象深刻。然而，结果与图3的关系并不清楚。请通过更直接地引用结果和图3来加强你的论点。
+\RC{} Discussion: The stories of each regime are very impressive.
+However, the relation to the results and Figure 3 is not clear.
+Please strengthen your argument by citing the results and Figure 3 more directly.
+
+\subsection{Comment \#7}
+% 讨论:从您对变更点的分析中可以明显看出，每个制度中都存在变更点。但为什么会出现这些变化“点”呢?是什么导致或触发了它们?这是管理机构的变化还是象征性的政策变化?该制度期间的特征已被很好地描述，但请更多地考虑为什么变化点发生在特定的年份/时期。
+\RC{} Discussion: The existence of change points in each of the regimes is evident from your analysis of the change points.
+But why did these change "points" occur?
+What caused or triggered them?
+Was it a change in governing institutions or a symbolic policy change?
+The characteristics during that regime period are well described, but please give more thought to why the change points occurred in that particular year/period.
+
+\subsection{Comment \#8}
+% 图4:A中的蓝色圆形箭头和B中的红色圆形箭头是什么意思?它们似乎包含了您非常重要的言论，但它们并不清楚。此外，您需要更多地解释A和B中的每个箭头。
+\RC{} Figure 4: What do the blue circular arrows in A and the red circular arrows in B mean?
+They seem to contain your very important remarks, but they are unclear.
+Also, you need to explain more about each of the arrows in A and B.
+
+\subsection{Comment \#9}
+% 结论:对定量分析的结果进行了描述，但是Discussion中的叙事分析似乎没有得到充分的体现。建议对此添加几行。
+\RC{} Conclusion: The results of the quantitative analysis are described, but the narrative analysis in the Discussion does not seem to be fully reflected.
+It is recommended to add a few lines about it.
+
 \end{document}

### 2023-05-08 paper/letter/response_letter/AR_to_RC/response_letter.tex
build(paper): :seedling: 添加供后面diff比对的v8版本

@@
 \input{../templates/AR_to_RC.tex}
+
+\graphicspath{{/Users/songshgeo/Documents/VSCode/WGRegimes_YRB_2020/figures/}}
 
@@
 % 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。
+% 在新增加的图表中，我增加了天然水量的图表展示这种变化
 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。
 % 我们现在在讨论中涉及了这些话题。
-\AR{} Ok, I changed this:
+\AR{} Climate change indeed has a multitude of impacts, such as altering precipitation and evaporation rates.
+However, these effects are inherently captured within the Integrated Water Governance Index (IWGI) as they influence the available water resources.
+In the revised version of our paper, we have added new graphs to demonstrate the changes in natural water availability caused by climate change.
+For example, climate change may alter water scarcity levels and make it more difficult to effectively allocate water resources due to extreme climate events.
+Additionally, adapting to climate change could lead to societal transformations, prompting a reevaluation of governance strategies that increasingly focus on industrial and economic development (priority).
+We have now addressed these topics in our discussion, illustrating the various ways in which climate change influences the adaptive capacity of a basin and its subsequent governance requirements.
+
+\begin{quote}
+	Climate change may alter water scarcity levels and make it more difficult to effectively allocate water resources due to extreme climate events.
+\end{quote}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=\textwidth]{sup/sf_measured_runoff.jpg}
+	\caption{绘图测试}\label{fig:xfig0}
+\end{figure}
 

### 2023-05-08 paper/main/01_introduction.tex
fix(MS,-appendix,-letter): fix format mistakes according to Wu's comment
feat(paper): :memo: 增加对指数的综述

@@
 \cite{undpwatergovernancefacility2016}.
-First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
+% 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。
+Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
+From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
+However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
+A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used. % todo cite OECD
+From the water side, intuitive indexes can provide an embodiment of governance outcomes.
+Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
+As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
+These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
+Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
+
+An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
+First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress
 \cite{qin2019,wada2014,huang2021}.
-Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
+Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)
 \cite{liu2017,florke2018,jaeger2019}.
-Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematic regulation
+Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations
 \cite{schmandt2021,speed2013}.
@@
 Filling this gap, which is the aim of this paper, is essential for the appropriate alignment of human and water systems.
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=0.9\textwidth]{main/framework.png}
+	\caption{
+		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
+Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
+Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
+For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
+		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
+	}
+	\label{fig:framework}
+\end{figure*}
 
@@
 % 这里我们整合了三个方向，提出了描绘流域人水关系的指数
-Here, we depict the three aspects of water governance (stress, purpose and allocation) with corresponding indicators (see methods) and thus develop an Integrated Water Governance Index (IWGI) by equally weighting them, to indicate results from water governance (see Figure~\ref{fig:framework}~B).
+Here, we depict three aspects of water governance -stress, purpose and allocation with corresponding indicators (see methods) and thus develop an Integrated Water Governance Index (IWGI) by equally weighting them, to indicate results from water governance (see Figure~\ref{fig:framework}~B).
 % 使用案例研究
@@
 Finally, we propose a general regime transition schema that offers a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
-
-\begin{figure*}[!ht]
-	\centering
-	\includegraphics[width=0.9\textwidth]{main/framework.png}
-	\caption{
-		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
-Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
-Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
-For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
-		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
-	}
-	\label{fig:framework}
-\end{figure*}

### 2023-05-09 paper/main/manuscript.tex
fix(paper): :ambulance: 修改文件路径，新电脑能编译
refactor(paper): :recycle: 重构补充材料格式

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Example: \title{This is a test title}
-\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
-\title{Identifying regime transitions for water governance at a basin scale}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  AUTHORS AND AFFILIATIONS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Authors are individuals who have significantly contributed to the
-% research and preparation of the article. Group authors are allowed, if
-% each author in the group is separately identified in an appendix.)
-
-% List authors by first name or initial followed by last name and
-% separated by commas. Use \affil{} to number affiliations, and
-% \thanks{} for author notes.
-% Additional author notes should be indicated with \thanks{} (for
-% example, for current addresses).
-
-% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
-% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
-
-\authors{
-      Shuang Song\affil{1},
-      Shuai Wang\affil{1},
-      Xutong Wu\affil{1},
-      Yongping Wei\affil{2},
-      Graeme S. Cumming\affil{3},
-      Yue Qin\affil{4},
-      Xilin Wu\affil{5},
-      Bojie Fu\affil{1,5}
-}
-
-\affiliation{1}{
-      State Key Laboratory of Earth Surface Processes and Resource Ecology,
-      Beijing Normal University,
-      Beijing, 100875, Beijing, China.
-}
-\affiliation{2}{
-      School of Earth and Environmental Sciences,
-      The University of Queensland,
-      Brisbane, 4067, QLD, Australia.
-}
-\affiliation{3}{
-      ARC Centre of Excellence for Coral Reef Studies,
-      James Cook University,
-      Townsville, 4811, QLD, Australia.
-}
-\affiliation{4}{
-      College of Environmental Sciences and Engineering,
-      Peking University,
-      Beijing, 100875, Beijing, China.
-}
-\affiliation{5}{
-      State Key Laboratory of Urban and Regional Ecology,
-      Research Center for Eco-Environmental Sciences,
-      Chinese Academy of Sciences,
-      Beijing, 100875, Beijing, China.
-}
+\input{../metadata.tex}
 %(repeat as many times as is necessary)
@@
 
-\bibliography{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/paper/main/mybibtex.bib}
+\bibliography{../mybibtex.bib}
 

### 2023-05-09 paper/metadata.tex
refactor(paper): :recycle: 重构补充材料格式

--- 2022-07-15 paper/sup/supplementary_information.tex
@@
-\documentclass[default, sn-standardnature]{sn-jnl}% Default with double column layout
+%\includegraphics{agu_pubart-white_reduced.eps}
 
-%%%% Standard Packages
-%%<additional latex packages if required can be included here>
-%%%%
+\graphicspath{{/Users/songshgeo/Documents/VSCode/WGRegimes_YRB_2020/figures}}
+\title{Identifying regime transitions for water governance at a basin scale}
+%
+% e.g., \title{Supporting Information for "Terrestrial ring current:
+% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
+%
+%DOI: 10.1002/%insert paper number here%
 
-%%%%%=============================================================================%%%%
-%%%%  Remarks: This template is provided to aid authors with the preparation
-%%%%  of original research articles intended for submission to journals published
-%%%%  by Springer Nature. The guidance has been prepared in partnership with
-%%%%  production teams to conform to Springer Nature technical requirements.
-%%%%  Editorial and presentation requirements differ among journal portfolios and
-%%%%  research disciplines. You may find sections in this template are irrelevant
-%%%%  to your work and are empowered to omit any such section if allowed by the
-%%%%  journal you intend to submit to. The submission guidelines and policies
-%%%%  of the journal take precedence. A detailed User Manual is available in the
-%%%%  template package for technical guidance.
-%%%%%=============================================================================%%%%
+%% ------------------------------------------------------------------------ %%
+%
+%  AUTHORS AND AFFILIATIONS
+%
+%% ------------------------------------------------------------------------ %%
 
-\jyear{2022}%
-\newgeometry{left=2cm, right=2cm}
-\linespread{1.5}
+% List authors by first name or initial followed by last name and
+% separated by commas. Use \affil{} to number affiliations, and
+% \thanks{} for author notes.
+% Additional author notes should be indicated with \thanks{} (for
+% example, for current addresses).
 
-%% as per the requirement new theorem styles can be included as shown below
-\theoremstyle{thmstyleone}%
-\newtheorem{theorem}{Theorem}%  meant for continuous numbers
-%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
-%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-\newtheorem{proposition}[theorem]{Proposition}%
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
+% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
 
-\theoremstyle{thmstyletwo}%
-\newtheorem{example}{Example}%
-\newtheorem{remark}{Remark}%
+\authors{
+      Shuang Song\affil{1},
+      Shuai Wang\affil{1},
+      Xutong Wu\affil{1},
+      yongping Wei\affil{2},
+      Graeme S. Cumming\affil{3},
+      Yue Qin\affil{4},
+      Xilin Wu\affil{5},
+      Bojie Fu\affil{1,5}
+}
 
-\theoremstyle{thmstylethree}%
-\newtheorem{definition}{Definition}%
-% \usepackage{tikz}
-% \newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
-%     circle (.5em) node {\makebox[1em][c]{\small #1}};}}
-\raggedbottom
-%%\unnumbered% uncomment this for unnumbered level heads
-%! path of figs
-
-\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
-\begin{document}
-
-\title{Supporting Materials of ``Identifying regime transitions for water governance at a basin scale''}
-
-%%=============================================================%%
-%% Prefix	-> \pfx{Dr}
-%% GivenName	-> \fnm{Joergen W.}
-%% Particle	-> \spfx{van der} -> surname prefix
-%% FamilyName	-> \sur{Ploeg}
-%% Suffix	-> \sfx{IV}
-%% NatureName	-> \tanm{Poet Laureate} -> Title after name
-%% Degrees	-> \dgr{MSc, PhD}
-%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
-%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
-%%=============================================================%%
-
-\author[1]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
-
-\author[1]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
-
-\author[1]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
-\author[2]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
-\author[3]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
-\author[4]{\fnm{Yue} \sur{Qin}}\email{qinyue@pku.edu.cn}
-\author[5]{\fnm{Xilin} \sur{Wu}}\email{wuxilin20@mails.ucas.ac.cn}
-\author*[1,5]{\fnm{Bojie} \sur{Fu}}\email{bfu@rcees.ac.cn}
-
-\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-
-\affil[2]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
-
-\affil[3]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
-
-\affil[4]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-
-\affil[5]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-%%==================================%%
-%% sample for unstructured abstract %%
-%%==================================%%
-
-%% Comment out or remove this line before generating final copy for submission; this will also remove the warning re: "Consecutive odd pages found".
-% \instructionspage
-
-\maketitle
-
-%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text
-
-\section{YRB Regions}\label{secA1}
-\input{01_yrb.tex}
-
-\section{SFV-index}\label{secA2}
-\input{02_indicator.tex}
-
-% \begin{figure}[tb!]
-% 	\centering
-% 	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
-% 	\caption{
-% 	    Ratio of irrigated areas with water-saving equipments.
-% 	}
-% 	\label{fig:wci}
-% \end{figure}
-
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
-    \caption{
-        Numbers of new reservoirs in each year.
+\affiliation{1}{
+      State Key Laboratory of Earth Surface Processes and Resource Ecology,
+      Beijing Normal University,
+      Beijing, 100875, Beijing, China.
 }
-    \label{fig:reservoirs}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{sup/sensitivity.pdf}
-    \caption{
-        Sensitivity analysis of the threshold of p-values.
-        \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
-        \textbf{B.} Threshold of p-values $\alpha=0.0005$.
-        \textbf{C.} Threshold of p-values $\alpha=0.05$.
+\affiliation{2}{
+      School of Earth and Environmental Sciences,
+      The University of Queensland,
+      Brisbane, 4067, QLD, Australia.
 }
-    \label{fig:sensitivity}
-\end{figure}
-
-\section{Datasets}\label{secA3}
-\input{03_datasets.tex}
-
-% \dataset{dataset_one.txt}{Type or paste legend here.}
-
-% \dataset{dataset_two.txt}{Type or paste legend here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}
-
-\bibliographystyle{sn-standardnature}
-\bibliography{mybib}% common bib file
-
-\end{document}
+\affiliation{3}{
+      ARC Centre of Excellence for Coral Reef Studies,
+      James Cook University,
+      Townsville, 4811, QLD, Australia.
+}
+\affiliation{4}{
+      College of Environmental Sciences and Engineering,
+      Peking University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{5}{
+      State Key Laboratory of Urban and Regional Ecology,
+      Research Center for Eco-Environmental Sciences,
+      Chinese Academy of Sciences,
+      Beijing, 100875, Beijing, China.
+}

### 2023-05-09 paper/sup/01_yrb.tex
refactor(paper): :recycle: 重构补充材料格式

@@
 We divide the YRB into four regions to calculate the indicators considering both socio-economic and natural conditions.
-The division aligns with the customary schema from publications and the YRCC \cite{yellowriverconservancycommission2013,wang2019c,wang2016e}, so four important hydrological stations can distinguish the regions (see Figure~\ref{fig:YRB}).
+The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverconservancycommission2013,wang2019c,wang2016e}, so four important hydrological stations can distinguish the regions (see Figure~\ref{fig:YRB}).
 
@@
     \item \textbf{Middle Region (MR):} Crossing Loess Plateau, a famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk.
-The ``grain for the green'' project changed the water utilization here strikingly to reverse this situation \cite{wu2020a}.
+The ``grain for the green'' project changed the water utilization here strikingly to reverse this situation~\cite{wu2020a}.
     \item \textbf{Lower Region (LR):} With a dense population and the traditional agricultural trajectory, the lower region used to be the largest water use region.
@@
         \textbf{C.} Typical landscapes in different regions in the YRB.
-    }
-    \label{fig:YRB}
+    }\label{fig:YRB}
 \end{figure*}

### 2023-05-09 paper/sup/supplementary_information.tex
refactor(paper): :recycle: 重构补充材料格式

@@
 %   when using Draft:
- \setkeys{Gin}{draft=false}
+\setkeys{Gin}{draft=true}
 %
@@
 \begin{document}
+\noindent\textbf{\large{Supplementary Information for}}
 
-%% ------------------------------------------------------------------------ %%
-%
-%  TITLE
-%
-%% ------------------------------------------------------------------------ %%
-
-%\includegraphics{agu_pubart-white_reduced.eps}
-
-\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
-\title{Supporting Information for ``Identifying regime transitions for water governance at a basin scale''}
-%
-% e.g., \title{Supporting Information for "Terrestrial ring current:
-% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
-%
-%DOI: 10.1002/%insert paper number here%
-
-%% ------------------------------------------------------------------------ %%
-%
-%  AUTHORS AND AFFILIATIONS
-%
-%% ------------------------------------------------------------------------ %%
-
-% List authors by first name or initial followed by last name and
-% separated by commas. Use \affil{} to number affiliations, and
-% \thanks{} for author notes.
-% Additional author notes should be indicated with \thanks{} (for
-% example, for current addresses).
-
-% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
-% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
-
-\authors{
-      Shuang Song\affil{1},
-      Shuai Wang\affil{1},
-      Xutong Wu\affil{1},
-      yongping Wei\affil{2},
-      Graeme S. Cumming\affil{3},
-      Yue Qin\affil{4},
-      Xilin Wu\affil{5},
-      Bojie Fu\affil{1,5}
-}
-
-\affiliation{1}{
-      State Key Laboratory of Earth Surface Processes and Resource Ecology,
-      Beijing Normal University,
-      Beijing, 100875, Beijing, China.
-}
-\affiliation{2}{
-      School of Earth and Environmental Sciences,
-      The University of Queensland,
-      Brisbane, 4067, QLD, Australia.
-}
-\affiliation{3}{
-      ARC Centre of Excellence for Coral Reef Studies,
-      James Cook University,
-      Townsville, 4811, QLD, Australia.
-}
-\affiliation{4}{
-      College of Environmental Sciences and Engineering,
-      Peking University,
-      Beijing, 100875, Beijing, China.
-}
-\affiliation{5}{
-      State Key Laboratory of Urban and Regional Ecology,
-      Research Center for Eco-Environmental Sciences,
-      Chinese Academy of Sciences,
-      Beijing, 100875, Beijing, China.
-}
-
-%% ------------------------------------------------------------------------ %%
-%
-%  BEGIN ARTICLE
-%
-%% ------------------------------------------------------------------------ %%
-
-% The body of the article must start with a \begin{article} command
-%
-% \end{article} must follow the references section, before the figures
-%  and tables.
-
+\input{../metadata.tex}
 \begin{article}
-
-%% ------------------------------------------------------------------------ %%
-%
-%  TEXT
-%
-%% ------------------------------------------------------------------------ %%
 
@@
 \end{enumerate}
-% \noindent\textbf{Additional Supporting Information (Files uploaded separately)}
-% \begin{enumerate}
-% \item Captions for Datasets S1 to Sx
-% \item Captions for large Tables S1 to Sx (if larger than 1 page, upload as separate excel file)
-% \item Captions for Movies S1 to Sx
-% \item Captions for Audio S1 to Sx
-% \end{enumerate}
 
@@
 When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
-Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the \ref{secA1}.
-The formulation in detail for applying the SFV-index is available in the \ref{secA2}.
-We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonise them for analysis.
-%\clearpage
+Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.
+The formulation in detail for applying the SFV-index is available in the~\ref{secA2}.
+We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonies them for analysis.
 
-%Delete all unused file types below. Copy/paste for multiples of each file type as needed.
-
-%Type or paste text here.
-This should be additional explanatory text, such as: extended descriptions of results, full details of models, extended lists of acknowledgements etc.
-It should not be additional discussion, analysis, interpretation or critique.
-It should not be an additional scientific experiment or paper.
-%
-%Repeat for any additional Supporting Text
 \noindent\textbf{YRB Regions}\label{secA1}
@@
           Numbers of new reservoirs in each year.
-      }
-      \label{fig:reservoirs}
+      }\label{fig:reservoirs}
   \end{figure}
@@
           \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
-          \textbf{B.} Threshold of p-values $\alpha=0.0005$.
-          \textbf{C.} Threshold of p-values $\alpha=0.05$.
-      }
-      \label{fig:sensitivity}
+          \textbf{B.} Threshold of p-values \(\alpha=0.0005\).
+          \textbf{C.} Threshold of p-values \(\alpha=0.05\).
+      }\label{fig:sensitivity}
   \end{figure}
@@
 %
-\bibliography{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/paper/main/mybibtex.bib}
-%
-% no need to specify bibliographystyle
-%
-% Note that ALL references in this supporting information file must also be referenced in the primary manuscript
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% if you get an error about newblock being undefined, uncomment this line:
-%\newcommand{\newblock}{}
-
-% \bibliography{ uncomment this line and enter the name of your bibtex file here }
-
-%Reference citation instructions and examples:
-%
-% Please use ONLY \cite and \citeA for reference citations.
-% \cite for parenthetical references
-% ...as shown in recent studies (Simpson et al., 2019)
-% \citeA for in-text citations
-% ...Simpson et al (2019) have shown...
-% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
-%
-%
-%...as shown by \citeA{jskilby}.
-%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
-%...has been shown \cite<e.g.,>{jskilbye}.
-%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
-%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
-%
-% apacite uses < > for prenotes, not [ ]
-% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
-%
-
-%% ------------------------------------------------------------------------ %%
-%
-%  END ARTICLE
-%
-%% ------------------------------------------------------------------------ %%
+\bibliography{../mybibtex.bib}
 \end{article}
 \clearpage
-
-% Copy/paste for multiples of each file type as needed.
-
-% enter figures and tables below here: %%%%%%%
-%
-%
-%
-%
-% EXAMPLE FIGURES
-% ---------------
-% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options.
-% \begin{figure}
-%\setfigurenum{S1} %%You can change number for each figure if you want, not required. "S" prepended automatically.
-% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.eps}
-%\caption{caption}
-%\label{epsfiguresample}
-%\end{figure}
-%
-%
-% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
-% \begin{figure}
-% \noindent\includegraphics[width=\textwidth]{anothersample.png}
-%\caption{caption}
-%\label{pngfiguresample}
-%\end{figure}
-%
-%
-%\begin{figure}
-%\noindent\includegraphics[width=\textwidth]{athirdsample.pdf}
-%\caption{A pdf test figure}
-%\label{pdffiguresample}
-%\end{figure}
-%
-% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
-%
-%
-% ---------------
-% EXAMPLE TABLE
-%
-%\begin{table}
-%\settablenum{S1} %%Change number for each table
-%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
-%\centering
-%\begin{tabular}{l c}
-%\hline
-% Run  & Time (min)  \\
-%\hline
-%  $l1$  & 260   \\
-%  $l2$  & 300   \\
-%  $l3$  & 340   \\
-%  $h1$  & 270   \\
-%  $h2$  & 250   \\
-%  $h3$  & 380   \\
-%  $r1$  & 370   \\
-%  $r2$  & 390   \\
-%\hline
-%\end{tabular}
-%\tablenotetext{a}{Footnote text here.}
-%\end{table}
-% ---------------
-%
-% EXAMPLE LARGE TABLE (UPLOADED SEPARATELY)
-%\begin{table}
-%\settablenum{S1} %%Change number for each table
-%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
-%\end{table}
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-More Information and Advice:
-
-%% ------------------------------------------------------------------------ %%
-%
-%  SECTION HEADS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Capitalize the first letter of each word (except for
-% prepositions, conjunctions, and articles that are
-% three or fewer letters).
-
-% AGU follows standard outline style; therefore, there cannot be a section 1 without
-% a section 2, or a section 2.3.1 without a section 2.3.2.
-% Please make sure your section numbers are balanced.
-% ---------------
-% Level 1 head
-%
-% Use the \section{} command to identify level 1 heads;
-% type the appropriate head wording between the curly
-% brackets, as shown below.
-%
-%An example:
-%\section{Level 1 Head: Introduction}
-%
-% ---------------
-% Level 2 head
-%
-% Use the \subsection{} command to identify level 2 heads.
-%An example:
-%\subsection{Level 2 Head}
-%
-% ---------------
-% Level 3 head
-%
-% Use the \subsubsection{} command to identify level 3 heads
-%An example:
-%\subsubsection{Level 3 Head}
-%
-%---------------
-% Level 4 head
-%
-% Use the \subsubsubsection{} command to identify level 3 heads
-% An example:
-%\subsubsubsection{Level 4 Head} An example.
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  IN-TEXT LISTS
-%
-%% ------------------------------------------------------------------------ %%
-%
-% Do not use bulleted lists; enumerated lists are okay.
-% \begin{enumerate}
-% \item
-% \item
-% \item
-% \end{enumerate}
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATIONS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Single-line equations are centered.
-% Equation arrays will appear left-aligned.
-
-Math coded inside display math mode \[ ...\]
- will not be numbered, e.g.,:
- \[ x^2=y^2 + z^2\]
-
- Math coded inside \begin{equation} and \end{equation} will
- be automatically numbered, e.g.,:
- \begin{equation}
- x^2=y^2 + z^2
- \end{equation}
-
-% IF YOU HAVE MULTI-LINE EQUATIONS, PLEASE
-% BREAK THE EQUATIONS INTO TWO OR MORE LINES
-% OF SINGLE COLUMN WIDTH (20 pc, 8.3 cm)
-% using double backslashes (\\).
-
-% To create multiline equations, use the
-% \begin{eqnarray} and \end{eqnarray} environment
-% as demonstrated below.
-\begin{eqnarray}
-  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
-        && + (y - y_{0}) \sin \Theta  \nonumber \\
-  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
-        && + (y - y_{0}) \cos \Theta.
-\end{eqnarray}
-
-%If you don't want an equation number, use the star form:
-%\begin{eqnarray*}...\end{eqnarray*}
-
-% Break each line at a sign of operation
-% (+, -, etc.) if possible, with the sign of operation
-% on the new line.
-
-% Indent second and subsequent lines to align with
-% the first character following the equal sign on the
-% first line.
-
-% Use an \hspace{} command to insert horizontal space
-% into your equation if necessary. Place an appropriate
-% unit of measure between the curly braces, e.g.
-% \hspace{1in}; you may have to experiment to achieve
-% the correct amount of space.
-
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATION NUMBERING: COUNTER
-%
-%% ------------------------------------------------------------------------ %%
-
-% You may change equation numbering by resetting
-% the equation counter or by explicitly numbering
-% an equation.
-
-% To explicitly number an equation, type \eqnum{}
-% (with the desired number between the brackets)
-% after the \begin{equation} or \begin{eqnarray}
-% command.  The \eqnum{} command will affect only
-% the equation it appears with; LaTeX will number
-% any equations appearing later in the manuscript
-% according to the equation counter.
-%
-
-% If you have a multiline equation that needs only
-% one equation number, use a \nonumber command in
-% front of the double backslashes (\\) as shown in
-% the multiline equation above.
-
-%% ------------------------------------------------------------------------ %%
-%
-%  SIDEWAYS FIGURE AND TABLE EXAMPLES
-%
-%% ------------------------------------------------------------------------ %%
-%
-% For tables and figures, add \usepackage{rotating} to the paper and add the rotating.sty file to the folder.
-% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
-%
-% \begin{sidewaysfigure}
-% \includegraphics[width=20pc]{samplefigure.eps}
-% \caption{caption here}
-% \label{label_here}
-% \end{sidewaysfigure}
-%
-%
-%
-% \begin{sidewaystable}
-% \caption{}
-% \begin{tabular}
-% Table layout here.
-% \end{tabular}
-% \end{sidewaystable}
-%
-%

### 2023-05-09 paper/letter/response_letter/AR_to_RC/response_letter.tex
docs(paper): :memo: 准备好修改审稿人意见回复信

@@
 
+% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
+% 再方法中补充了指标的取值范围（三个子指标的变化范围都是0～1）。
+\AR{} Thanks for point it out! Now
+
+\AR*{} Figure SX to SX are three indicators changing trends with different regions' contribution.
+
+\AR*{} Ranges of three indicators and meaning of their values are further explained in the methodology section, now:
+
+\begin{quote}[page=1, sline=1]
+	Methods
+\end{quote}
+
 \subsection{Major concern \#3}
@@
 
+\AR{} Multiple-source dataset.
+
 \subsection{Major concern \#4}
@@
 \RC{} There might be interactions/interconnections among the three indicators. Did the authors examine the relations between the indicators?
+
+\AR{} Yes, we did examination for the interconnections between the three indicators. Sorry we didn't make the information accessible. Now, we added a table to describe them:
+
+\begin{quote}
+	Table
+\end{quote}
+
+\AR*{} Note that independent is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
+However, our
 
@@
 However, the water conveyance ability is not represented, which is also an important indicator of water governance/hydrosocial resilience.
+
+% 短期的输水能力是衡量水治理/水社会复原力的重要指标
+% 但年尺度上，变化不大
+\AR*{} Correct, conveyance is crucial to water governance/water society resilience, especially in the short term.
+However, the IWGI in this study focuses on annual time resolution.
+At this scale, conveyance has a less significant impact on water governance.
+From this point of view, we have two reasons that IWGI doesn't have to consider this in our study:
+
+% 我们检验过了年尺度的输水数据，基本变化不大
+
+% 水治理很复杂，考虑到越来越多的要素会增加其复杂度。Scarcity是本研究使用最复杂的指标，因为这是一个经过检验的，可以有效表征的指数。如果经过检验影响不大，没有必要增加复杂度。
 
@@
 
+% 感谢你的提议，我们增加了黄河流域
+
+% 关于IWGI的泛用性，实际上我们在讨论中讨论了这一点。我们也
+
+% 我们如今在方法部分提到了使用它的先决条件。
+
 \subsection{Major concern \#7}
@@
 \RC{} It would be better to explain the concept "water governance regime" in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.
+
+% 感谢你的建议，我们做了如下解释：
+\begin{quote}
+	``Water governance regime'' is \ldots
+\end{quote}
+
 \subsection{Detailed issues}

### 2023-05-09 paper/main/01_introduction.tex
style(paper): :lipstick: fix all chktex warns

@@
-\label{Intro.}
-Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being
-\cite{gleeson2020a,gleeson2020b}.
-As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water
-\cite{ahlstrom2021,biermann2012,steffen2020}.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers
-\cite{sivapalan2012,qin2014,abbott2019}.
-Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance
-\cite{best2019,dibaldassarre2019}.
+Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being~\cite{gleeson2020a,gleeson2020b}.
+As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014,abbott2019}.
+Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
-Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacility2016}.
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
+Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{undpwatergovernancefacility2016}.
 % 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。
@@
 An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
-First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress
-\cite{qin2019,wada2014,huang2021}.
-Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)
-\cite{liu2017,florke2018,jaeger2019}.
-Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations
-\cite{schmandt2021,speed2013}.
+First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress~\cite{qin2019,wada2014,huang2021}.
+Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)~\cite{liu2017,florke2018,jaeger2019}.
+Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations~\cite{schmandt2021,speed2013}.
 Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.
 
-A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
-Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
-\cite{falkenmark2021,bressers2013,loch2020}.
+A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
+Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020}.
 For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
@@
 		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
-	}
-	\label{fig:framework}
+	}\label{fig:framework}
 \end{figure*}
 
-The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history
-\cite{mostern2021,best2019}.
-Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads
-\cite{wang2016e,song2020a}.
-However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic
-\cite{wang2019c}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors
-\cite{wohlfart2016a}.
-Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide \cite{nickum2021}.
+The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019}.
+Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016e,song2020a}.
+However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic~\cite{wang2019c}.
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016a}.
+Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

### 2023-05-09 paper/main/02_methods.tex
style(paper): :lipstick: fix all chktex warns

@@
+% chktex-file 46
+
 To develop a comprehensive and straightforward approach to identifying water governance regimes.
@@
 	\begin{equation}
-		Transformation \propto ln(I_S) + ln(I_P) + ln(I_A)
+		Transformation \propto \ln(I_S) + \ln(I_P) + \ln(I_A)
 	\end{equation}
@@
 	\begin{equation}
-		I'_x = (I_x - I_{x, min}) / (I_{x, max} - I_{x, min})
+		I'_x = (I_x - I_{x, \min}) / (I_{x, \max} - I_{x, \min})
 	\end{equation}
@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress \cite{qin2019}.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress~\cite{qin2019}.
 This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
@@
 	\begin{equation}
-		I_A = CEM = \sum_{i=1}^N -log(p_{i}) * p_{i}
+		I_A = CEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
 	\end{equation}
@@
 	\subsection{Change points detection}
-		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
-        \cite{pettitt1979}.
+		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data~\cite{pettitt1979}.
 		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
@@
 
-		The most probable change point $\tau$ is found where its value satisfies $K_{\tau} = max|U_{t, T}|$ and the significance probability associated with value $K_{\tau}$ is approximately evaluated as:
+		The most probable change point $\tau$ is found where its value satisfies $K_{\tau} = \max|U_{t, T}|$ and the significance probability associated with value $K_{\tau}$ is approximately evaluated as:
 		\begin{equation}

### 2023-05-09 paper/main/03_results.tex
style(paper): :lipstick: fix all chktex warns

@@
-\subsection{Water governance regimes}
-\label{Res.1}
+% chktex-file 46
+\subsection{Water governance regimes}\label{Res.1}
 
@@
 	\includegraphics[width=0.9\linewidth]{main/index.jpg}
-	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: 1965-1978, P2: 1979-2001, and P3: 2002-2013.
+	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: $1965 \sim 1978$, P2: $1979 \sim 2001$, and P3: $2002 \sim 2013$.
 	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
@@
 	\textbf{C,} across three indicators, changing components of the IWGI, whose directions shifts between different regimes.
-	}
-	\label{fig:IWGI}
+	}\label{fig:IWGI}
 \end{figure*}
@@
 % 第一阶段
-In the first period (P1, 1965-1978), the IWGI decreased rapidly.
+In the first period (P1, $1965 \sim 1978$), the IWGI decreased rapidly.
 While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
 % 第二阶段
-In the second period (P2, 1979-2001), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
+In the second period (P2, $1979 \sim 2001$), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.\
 % 第三阶段
-During the third period (P3, 1995-2013), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
+During the third period (P3, $1995 \sim 2013$), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
 % Overall
@@
 
-\subsection{Causes of the regime shifts}
-\label{Res.2}
+\subsection{Causes of the regime shifts}\label{Res.2}
 
@@
 	\caption{
-		Causes of water governance regime shifts in the YRB.
+		Causes of water governance regime shifts in the YRB.\
 		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the irrigated area, the green dot line).
@@
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
-	}
-	\label{fig:Causes}
+	}\label{fig:Causes}
 \end{figure*}
@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2.
+As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2).
+% todo 检查图引用
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。

### 2023-05-09 paper/main/04_discussion.tex
fix(MS,-appendix,-letter): fix format mistakes according to Wu's comment
style(paper): :lipstick: fix all chktex warns

@@
+% Implications
+Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being~\cite{best2019,best2020}.
+As tele-coupling raises additional water governance challenges in an increasingly tightly-connected world, regime shifts in water governance align with different human-water relationships~\cite{diaz2019}.
+The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition~\cite{loch2020,turton1999}.
+It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime~\cite{reyers2018}.
+
+% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming command (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
+During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
+As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
+The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
+Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
+In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016a}.
+
+The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
+% 正如理论预测的那样
+The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
+% 作为制度转变的先行者
+As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
+These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019a,long2020,nickum2021}.
+% 因此，1999年黄河的最后一次枯竭
+Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019a}.
+
+The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
+Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
+Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019a}.
+Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.
+
+% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
+In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
+With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
+In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012a}.
+Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
+Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
+
 \begin{figure*}[htbp!]
@@
 		\textbf{D. Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges but social and policy challenges later.
-	}
-	\label{fig:summary}
+	}\label{fig:summary}
 \end{figure*}
-
-% Implications
-Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being
-\cite{best2019,best2020}.
-As tele-coupling raises additional water governance challenges in an increasingly tightly-connected world, regime shifts in water governance align with different human-water relationships \cite{diaz2019}.
-The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
-It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime \cite{reyers2018}.
-
-% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: 1965-1978), a governance transforming command (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013) (Figure~\ref{fig:IWGI}).
-During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
-As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation
-\cite{zhou2020}.
-The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical \cite{loch2020}.
-Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity \cite{wang2019c}.
-In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis
-\cite{wohlfart2016a}.
-
-The start of the governance transforming regime (P2: 1979-2001) coincided with rising competition for water use after the ``reform and opening-up''.
-% 正如理论预测的那样
-The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity \cite{loch2020}.
-% 作为制度转变的先行者
-As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan
-\cite{wang2019a,long2020,nickum2021}.
-% 因此，1999年黄河的最后一次枯竭
-Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance \cite{wang2019a}.
-
-The ensuing adaptation-oriented regime (P3: 2002-2013) involved a significant societal shift in adapting to stable high water stress.
-Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply
-\cite{dalin2015,song2022}.
-Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example \cite{wang2019a}.
-Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance
-\cite{konar2019}.
-
-% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
-In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
-In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
-\cite{allan2019,speed2013,liu2012a}.
-Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures
-\cite{unep-dhi2016,mirumachi2015}.
-Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
 
@@
 Choices of indicators for different aspects can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
-In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems
-\cite{cumming2018,cumming2014,jaeger2019}.
-Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional, and planetary boundaries where human-water systems may collapse
-\cite{gleeson2020, wang-erlandsson2022}.
-A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability
-\cite{falkenmark2019}.
+In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
+Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional, and planetary boundaries where human-water systems may collapse~\cite{gleeson2020, wang-erlandsson2022}.
+A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability~\cite{falkenmark2019}.

### 2023-05-09 paper/diff/v-8.0.0.tex
build(paper): :seedling: 添加供后面diff比对的v8版本
fix(paper): :ambulance: 修复diff版本没有flatten的错误

--- 2022-07-15 paper/main/manuscript.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                 %%
-%% Please do not use \input{...} to include other tex files.       %%
-%% Submit your LaTeX manuscript as one .tex document.              %%
-%%                                                                 %%
-%% All additional figures and files should be attached             %%
-%% separately and not embedded in the \TeX\ document itself.       %%
-%%                                                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[draft]{agujournal2019}
+\usepackage{url} \usepackage{lineno}
+\usepackage[inline]{trackchanges} \usepackage{soul}
+\usepackage{amsmath}
+\linenumbers
 
-%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
+\draftfalse
 
-%%=======================================================%%
-%% to print line numbers in the margin use lineno option %%
-%%=======================================================%%
+\journalname{Water Resources Research}
 
-%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-
-%%======================================================%%
-%% to compile with pdflatex/xelatex use pdflatex option %%
-%%======================================================%%
-
-%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-
-%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-% \documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
-%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
-%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
-%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
-%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
-% \documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
-% \documentclass[default]{sn-jnl}% Default
-\documentclass[default, sn-standardnature]{sn-jnl}% Default with double column layout
-
-%%%% Standard Packages
-%%<additional latex packages if required can be included here>
-%%%%
-
-%%%%%=============================================================================%%%%
-%%%%  Remarks: This template is provided to aid authors with the preparation
-%%%%  of original research articles intended for submission to journals published
-%%%%  by Springer Nature. The guidance has been prepared in partnership with
-%%%%  production teams to conform to Springer Nature technical requirements.
-%%%%  Editorial and presentation requirements differ among journal portfolios and
-%%%%  research disciplines. You may find sections in this template are irrelevant
-%%%%  to your work and are empowered to omit any such section if allowed by the
-%%%%  journal you intend to submit to. The submission guidelines and policies
-%%%%  of the journal take precedence. A detailed User Manual is available in the
-%%%%  template package for technical guidance.
-%%%%%=============================================================================%%%%
-
-\jyear{2022}%
-\newgeometry{left=2cm, right=2cm}
-\linespread{1.5}
-\usepackage{lineno}
-
-%% as per the requirement new theorem styles can be included as shown below
-\theoremstyle{thmstyleone}%
-\newtheorem{theorem}{Theorem}%  meant for continuous numbers
-%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
-%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-\newtheorem{proposition}[theorem]{Proposition}%
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
-
-\theoremstyle{thmstyletwo}%
-\newtheorem{example}{Example}%
-\newtheorem{remark}{Remark}%
-
-\theoremstyle{thmstylethree}%
-\newtheorem{definition}{Definition}%
-% \usepackage{tikz}
-% \newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
-%     circle (.5em) node {\makebox[1em][c]{\small #1}};}}
-\raggedbottom
-%%\unnumbered% uncomment this for unnumbered level heads
-%! path of figs
-
-\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
 \begin{document}
 
-\title[Article Title]{Identifying regime transitions for water governance at a basin scale}
+\graphicspath{{/Users/songshgeo/Documents/VSCode/WGRegimes_YRB_2020/figures}}
+\title{Identifying regime transitions for water governance at a basin scale}
 
-%%=============================================================%%
-%% Prefix	-> \pfx{Dr}
-%% GivenName	-> \fnm{Joergen W.}
-%% Particle	-> \spfx{van der} -> surname prefix
-%% FamilyName	-> \sur{Ploeg}
-%% Suffix	-> \sfx{IV}
-%% NatureName	-> \tanm{Poet Laureate} -> Title after name
-%% Degrees	-> \dgr{MSc, PhD}
-%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
-%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
-%%=============================================================%%
+\authors{
+      Shuang Song\affil{1},
+      Shuai Wang\affil{1},
+      Xutong Wu\affil{1},
+      yongping Wei\affil{2},
+      Graeme S. Cumming\affil{3},
+      Yue Qin\affil{4},
+      Xilin Wu\affil{5},
+      Bojie Fu\affil{1,5}
+}
 
-\author[1]{\fnm{Shuang} \sur{Song}}\email{songshgeo@mail.bnu.edu.cn}
+\affiliation{1}{
+      State Key Laboratory of Earth Surface Processes and Resource Ecology,
+      Beijing Normal University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{2}{
+      School of Earth and Environmental Sciences,
+      The University of Queensland,
+      Brisbane, 4067, QLD, Australia.
+}
+\affiliation{3}{
+      ARC Centre of Excellence for Coral Reef Studies,
+      James Cook University,
+      Townsville, 4811, QLD, Australia.
+}
+\affiliation{4}{
+      College of Environmental Sciences and Engineering,
+      Peking University,
+      Beijing, 100875, Beijing, China.
+}
+\affiliation{5}{
+      State Key Laboratory of Urban and Regional Ecology,
+      Research Center for Eco-Environmental Sciences,
+      Chinese Academy of Sciences,
+      Beijing, 100875, Beijing, China.
+}
 
-\author[1]{\fnm{Shuai} \sur{Wang}}\email{shuaiwang@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
+\correspondingauthor{Shuai Wang}{shuaiwang@bnu.edu.cn}
 
-\author[1]{\fnm{Xutong} \sur{Wu}}\email{wuxutong@bnu.edu.cn}
-% \equalcont{These authors contributed equally to this work.}
-\author[2]{\fnm{Yongping} \sur{Wei}}\email{yongping.wei@uq.edu.au}
-\author[3]{\fnm{Graeme S.} \sur{Cumming}}\email{graeme.cumming@jcu.edu.au}
-\author[4]{\fnm{Yue} \sur{Qin}}\email{qinyue@pku.edu.cn}
-\author[5]{\fnm{Xilin} \sur{Wu}}\email{wuxilin20@mails.ucas.ac.cn}
-\author*[1,5]{\fnm{Bojie} \sur{Fu}}\email{bfu@rcees.ac.cn}
+\begin{keypoints}
+\item We developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance.
+\item We interpret how water governance shifts within a rapidly-changing large river basin.
+\item We developed an approach to analyzing intertwines of water governance, hydrosocial transition, and human-water relationships.
+\end{keypoints}
 
-\affil*[1]{\orgdiv{State Key Laboratory of Earth Surface Processes and Resource Ecology}, \orgname{Beijing Normal University,}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-
-\affil[2]{\orgdiv{School of Earth and Environmental Sciences}, \orgname{The University of Queensland}, \orgaddress{\city{Brisbane}, \postcode{4067}, \state{QLD}, \country{Australia}}}
-
-\affil[3]{\orgdiv{ARC Centre of Excellence for Coral Reef Studies}, \orgname{James Cook University}, \orgaddress{\city{Townsville}, \postcode{4811}, \state{QLD}, \country{Australia}}}
-
-\affil[4]{\orgdiv{College of Environmental Sciences and Engineering} \orgname{Peking University}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-
-\affil[5]{\orgdiv{State Key Laboratory of Urban and Regional Ecology, Research Center for Eco-Environmental Sciences}, \orgname{Chinese Academy of Sciences}, \orgaddress{\city{Beijing}, \postcode{100875}, \state{Beijing}, \country{China}}}
-%%==================================%%
-%% sample for unstructured abstract %%
-%%==================================%%
-\linenumbers
-\abstract{
+\begin{abstract}
 Water governance determine ``who gets water, when, and how'' in most large river basins.
@@
 The IWGI offers a comprehensive and straightforward approach to linking water governance regimes to sustainability, providing valuable insights into hydrosocial transitions.
-}
+\end{abstract}
 
-\keywords{
-    Regime shifts,
-    Water governance,
-    Hydrosocial cycle,
-    Social-hydrology,
-    Sustainability
-}
-
-%%\pacs[JEL Classification]{D8, H51}
-%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
-
-\maketitle
+\section*{Plain Language Summary}
+Missing governance means missing sustainability.
+However, the lack of a comprehensive but straightforward approach to identifying the changes in water governance presents a challenge for efforts to underpin it.
+Therefore, we choose indicators for the corresponding aspects (water stress, water services purpose, and water allocation) and combine them into an integrated water governance index (IWGI) to analyze long-term changes in a large river basin.
 
 \section{Introduction}\label{sec1}
-\input{01_introduction}
+\label{Intro.}
+Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being
+\cite{gleeson2020a,gleeson2020b}.
+As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water
+\cite{ahlstrom2021,biermann2012,steffen2020}.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers
+\cite{sivapalan2012,qin2014,abbott2019}.
+Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance
+\cite{best2019,dibaldassarre2019}.
 
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
+Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
+\cite{undpwatergovernancefacility2016}.
+First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
+\cite{qin2019,wada2014,huang2021}.
+Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
+\cite{liu2017,florke2018,jaeger2019}.
+Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematic regulation
+\cite{schmandt2021,speed2013}.
+Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.
+
+A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
+Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
+\cite{falkenmark2021,bressers2013,loch2020}.
+For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
+However, the lack of a comprehensive but straightforward approach to identifying changes in water governance regimes represents a challenge for efforts to enhance the sustainability of water resource use.
+Filling this gap, which is the aim of this paper, is essential for the appropriate alignment of human and water systems.
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=0.9\textwidth]{main/framework.png}
+	\caption{
+		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
+Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
+Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
+For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
+		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
+	}
+	\label{fig:framework}
+\end{figure*}
+
+The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history
+\cite{mostern2021,best2019}.
+Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads
+\cite{wang2016e,song2020a}.
+However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic
+\cite{wang2019c}.
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors
+\cite{wohlfart2016a}.
+Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide \cite{nickum2021}.
+Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.
+
+Here, we depict the three aspects of water governance (stress, purpose and allocation) with corresponding indicators (see methods) and thus develop an Integrated Water Governance Index (IWGI) by equally weighting them, to indicate results from water governance (see Figure~\ref{fig:framework}~B).
+Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how IWGI helps detect and describe complicated water governance regimes comprehensively but straightforwardly.
+Following synthetic analyses of the changes in water demand, supply, economic outcomes, and institutions, we interpret the leading causes of the regime shifts.
+Finally, we propose a general regime transition schema that offers a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.
+
+\section{Materials and Methods}\label{sec11}
+
+To develop a comprehensive and straightforward approach to identifying water governance regimes.
+First, we constructed the Integrated Water Governance Index (IWGI) based on three aspects (Stress, Purpose, and Allocation, see Figure~\ref{fig:framework}).
+Then, we analyzed the changes in the IWGI from 1965 to 2013 using change point detection methods.
+The normalized Indicator for each dimension affects the IWGI by changing trends and contributions.
+
+\subsection{Integrated Water Governance Index (IWGI)}
+
+As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance.
+Each dimension keeps two directions, and we assumed the hydrosocial cycle aligns with one of them, respectively:
+	\begin{equation}
+		Transformation \propto S*P*A
+	\end{equation}
+
+	We selected an indicator ($I_x$, $x=S$, $P$, or $A$, corresponding to stress, purpose, and allocation, respectively) to quantify the aspects effectively.
+Then, the above equation was transformed into a natural logarithm to facilitate calculation:
+	\begin{equation}
+		Transformation \propto \ln(I_S) + \ln(I_P) + \ln(I_A)
+	\end{equation}
+
+	Then, the Integrated Water Governance Index (IWGI) is an average of the normalized indicators $I'_x$:
+	\begin{equation}
+		IWGI = (I'_S + I'_P + I'_A) / 3
+	\end{equation}
+
+	where:
+	\begin{equation}
+		I'_x = (I_x - I_{x, \min}) / (I_{x, \max} - I_{x, \min})
+	\end{equation}
+
+	\subsubsection*{Indicator of stress}
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress~\cite{qin2019}.
+This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
+Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).
+For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
+	\begin{equation}
+		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
+	\end{equation}
+
+	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \textit{Supporting Information S2}.
+
+	\subsubsection*{Indicator of purpose}
+	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
+While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
+We calculated the NPS as:
+	\begin{equation}
+		NPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
+	\end{equation}
+
+	In this study, we consider livestock water use, rural and urban domestic water use, and agricultural water use as provisioning water because they directly service for survival.
+Others are non-provisioning: services and industrial water use because they mainly service the economy.
+
+	\subsubsection*{Indicator of allocations}
+	To describe allocations $I_A$, we designed an indicator based on entropy, called Allocation Entropy Metric (AEM), which measures the degree of evenness in water allocation:
+
+	\begin{equation}
+		I_A = CEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
+	\end{equation}
+
+	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
+
+	\subsection{Change points detection}
+		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data~\cite{pettitt1979}.
+		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
+		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}}$ and $x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$.
+To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:
+
+		\begin{equation}
+			U_{t, T} = \sum_{i=1}^t\sum_{j=t+1}^T sgn(X_i - X_j), 1 \leq t < T
+		\end{equation}
+
+		where:
+		\begin{equation}
+			\operatorname{sgn}(\theta)= \begin{cases}1 & \text { if } \theta>0 \\ 0 & \text { if } \theta=0 \\ -1 & \text { if } \theta<0\end{cases}
+		\end{equation}
+
+		The most probable change point $\tau$ is found where its value satisfies $K_{\tau} = \max|U_{t, T}|$ and the significance probability associated with value $K_{\tau}$ is approximately evaluated as:
+		\begin{equation}
+			p=2 \exp \left(\frac{-6 K_{\tau}^{2}}{T^{2}+T^{3}}\right)
+		\end{equation}
+		Given a certain significance level $\alpha$, if $p < \alpha$, we reject the null hypothesis and conclude that $x_{\tau}$ is a significant change point at level $\alpha$.
+
+We used $\alpha = 0.001$ as the threshold level of the p-value, meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
+We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see \\textit{Supporting Information} Figure~S3).
+
+	\subsection{Datasets}
+In order to calculate IWGI in the YRB, all the datasets we need are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
  \section{Results}\label{sec2}
-\input{03_results}
+\subsection{Water governance regimes}\label{Res.1}
+
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[width=0.9\linewidth]{main/index.jpg}
+	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: $1965 \sim 1978$, P2: $1979 \sim 2001$, and P3: $2002 \sim 2013$.
+	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
+	\textbf{B,} correlation of trends between the IWGI and the indicators.
+	\textbf{C,} across three indicators, changing components of the IWGI, whose directions shifts between different regimes.
+	}\label{fig:IWGI}
+\end{figure*}
+
+Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
+In the first period (P1, $1965 \sim 1978$), the IWGI decreased rapidly.
+While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
+In the second period (P2, $1979 \sim 2001$), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.\
+During the third period (P3, $1995 \sim 2013$), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
+Taken together, the overall features of the three aspects in different periods are relative to a directional change in the combination of three aspects (Figure~\ref{fig:IWGI}C).
+
+\subsection{Causes of the regime shifts}\label{Res.2}
+
+\begin{figure*}[th!]
+	\centering
+	\includegraphics[width=0.9\linewidth]{main/causes.pdf}
+	\caption{
+		Causes of water governance regime shifts in the YRB.\
+		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the irrigated area, the green dot line).
+		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line).
+		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time.
+Red circles denote the reservoirs mainly for managing and regulating the whole basin.
+		The size of each circle indicates the magnitude of its water storage capacity.
+		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
+The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
+	}\label{fig:Causes}
+\end{figure*}
+
+The underlying causes of changes in the IWGI are different in the two regime shifts.
+Changing water demands and supply were critical to the shift between P1 and P2.
+As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2).
+Ensuing the P2, however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes}~A and B).
+Then, the efficiency of water use changed obviously from P2 to P3.
+Not only did irrigated areas continue to expand slowly during the P3 (Figure\ref{fig:Causes}~A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}~B).
+Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}~A and Figure~\ref{fig:Causes}~B).
+As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the P3 (Figure~\ref{fig:IWGI}A).
+
+Environmental context, social transformation, and policies played roles in all three periods.
+We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
+Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
+Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
+During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
+The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.
 
 \section{Discussion}\label{sec12}
-\input{04_discussion}
+
+Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being~\cite{best2019,best2020}.
+As tele-coupling raises additional water governance challenges in an increasingly tightly-connected world, regime shifts in water governance align with different human-water relationships~\cite{diaz2019}.
+The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition~\cite{loch2020,turton1999}.
+It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime~\cite{reyers2018}.
+
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming command (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
+During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
+As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
+The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
+Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
+In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016a}.
+
+The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
+The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
+As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
+These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019a,long2020,nickum2021}.
+Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019a}.
+
+The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
+Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
+Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019a}.
+Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.
+
+In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
+With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
+In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012a}.
+Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
+Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
+
+\begin{figure*}[htbp!]
+	\centering
+	\includegraphics[width=0.8\linewidth]{main/transition.png}
+	\caption{
+		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
+		\textbf{A.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate water stress.
+		\textbf{B.} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
+		Thus, \textbf{C.
+the hydrosocial water cycle transition} correlates with the water governance regime shifts.
+The transformation governance regime shift occurs following the water deficit, with the rapid growth of adaptive capacity.
+		\textbf{D. Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges but social and policy challenges later.
+	}\label{fig:summary}
+\end{figure*}
+
+One of the main limitations in the approach is the lack of long-term data worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI more widely.
+However, we propose that all water governance issues result in changing ``who gets water, when and how'', so monitoring water stress, purposes of water services, and water allocation patterns do help.
+Choices of indicators for different aspects can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
+In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
+Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional, and planetary boundaries where human-water systems may collapse~\cite{gleeson2020, wang-erlandsson2022}.
+A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability~\cite{falkenmark2019}.
 
 \section{Conclusion}\label{sec13}
-\input{05_conclusion}
+Focusing on ``who gets water, when and how'', three aspects of water governance change along with the hydrosocial cycle transition: water stress, water services purpose, and water allocation.
+We developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance by integrating them.
+Applying the IWGI to a rapidly-changing large river basin (the Yellow River Basin, China), we interpret how water governance shifts between three regimes over half a century.
+Our approach quantitatively identifies the general schema for water governance regimes in the YRB, in line with previous theoretical analysis with a representative transition process.
+Linking regime shifts to the underlying causes, the implementation of IWGI offers a comprehensive and straightforward way to interpret changes in intertwines of water governance, hydrosocial transition, and human-water relationships.
 
-\section{Methods}\label{sec11}
-\input{02_methods}
+\section*{Open Research Section}
+All the used datasets and access source are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
 
-\backmatter
-
-\bmhead{Supplementary information}
-When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
-Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the \ref{secA1}.
-The formulation in detail for applying the SFV-index is available in the \ref{secA2}.
-We used multiple sources of datasets in this study, \textit{Appendix}~\ref{secA3} introduces where they came from and how we harmonise them for analysis.
-
-\bmhead{Acknowledgments}
-
+\acknowledgments
 Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
 
-% \section*{Declarations}
-
-% Some journals require declarations to be submitted in a standardised format.
-Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section.
-If yes, your manuscript must contain the following sections under the heading `Declarations':
-
-% \begin{itemize}
-% \item Funding
-% \item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
-% \item Ethics approval
-% \item Consent to participate
-% \item Consent for publication
-% \item Availability of data and materials
-% \item Code availability
-% \item Authors' contributions
-% \end{itemize}
-
-%%===========================================================================================%%
-%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
-%% system, please include the references within the manuscript file itself. You may do this  %%
-%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
-%% file, and delete the associated \verb+\bibliography+ commands.                            %%
-%%===========================================================================================%%
-
-\newpage
-\bibliographystyle{sn-standardnature}
-\bibliography{mybib}% common bib file
-%% if required, the content of .bbl file can be included here once bbl is generated
-%%\input sn-article.bbl
-
-%% Default %%
-%%\input sn-sample-bib.tex%
-
-\begin{appendices}
-
-\section{YRB Regions}\label{secA1}
-\input{../sup/01_yrb.tex}
-
-\section{SFV-index}\label{secA2}
-\input{../sup/02_indicator.tex}
-
-% \begin{figure}[tb!]
-% 	\centering
-% 	\includegraphics[width=0.9\linewidth]{sup/S3_wci.pdf}
-% 	\caption{
-% 	    Ratio of irrigated areas with water-saving equipments.
-% 	}
-% 	\label{fig:wci}
-% \end{figure}
-
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
-    \caption{
-        Numbers of new reservoirs in each year.
-    }
-    \label{fig:reservoirs}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{sup/sensitivity.pdf}
-    \caption{
-        Sensitivity analysis of the threshold of p-values.
-        \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
-        \textbf{B.} Threshold of p-values $\alpha=0.0005$.
-        \textbf{C.} Threshold of p-values $\alpha=0.05$.
-    }
-    \label{fig:sensitivity}
-\end{figure}
-
-\section{Datasets}\label{secA3}
-\input{../sup/03_datasets.tex}
-
-\end{appendices}
+\bibliography{../mybibtex.bib}
 

### 2023-05-09 paper/diff/draft.tex
refactor(paper): :recycle: 将LaTeX工作流打通

--- 2023-05-09 paper/diff/v-8.0.0.tex
@@
 \section{Introduction}\label{sec1}
-\label{Intro.}
-Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being
-\cite{gleeson2020a,gleeson2020b}.
-As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water
-\cite{ahlstrom2021,biermann2012,steffen2020}.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers
-\cite{sivapalan2012,qin2014,abbott2019}.
-Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance
-\cite{best2019,dibaldassarre2019}.
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
-Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
-\cite{undpwatergovernancefacility2016}.
-First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
-\cite{qin2019,wada2014,huang2021}.
-Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
-\cite{liu2017,florke2018,jaeger2019}.
-Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematic regulation
-\cite{schmandt2021,speed2013}.
+Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being~\cite{gleeson2020a,gleeson2020b}.
+As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014,abbott2019}.
+Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.
+
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
+Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{undpwatergovernancefacility2016}.
+Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
+From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
+However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
+A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used.
+From the water side, intuitive indexes can provide an embodiment of governance outcomes.
+Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
+As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
+These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
+Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
+
+An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
+First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress~\cite{qin2019,wada2014,huang2021}.
+Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)~\cite{liu2017,florke2018,jaeger2019}.
+Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations~\cite{schmandt2021,speed2013}.
 Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.
 
-A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
-Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
-\cite{falkenmark2021,bressers2013,loch2020}.
+A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
+Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020}.
 For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
@@
 		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
-	}
-	\label{fig:framework}
+	}\label{fig:framework}
 \end{figure*}
 
-The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history
-\cite{mostern2021,best2019}.
-Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads
-\cite{wang2016e,song2020a}.
-However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic
-\cite{wang2019c}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors
-\cite{wohlfart2016a}.
-Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide \cite{nickum2021}.
+The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019}.
+Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016e,song2020a}.
+However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic~\cite{wang2019c}.
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016a}.
+Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.
 
-Here, we depict the three aspects of water governance (stress, purpose and allocation) with corresponding indicators (see methods) and thus develop an Integrated Water Governance Index (IWGI) by equally weighting them, to indicate results from water governance (see Figure~\ref{fig:framework}~B).
+Here, we depict three aspects of water governance -stress, purpose and allocation with corresponding indicators (see methods) and thus develop an Integrated Water Governance Index (IWGI) by equally weighting them, to indicate results from water governance (see Figure~\ref{fig:framework}~B).
 Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how IWGI helps detect and describe complicated water governance regimes comprehensively but straightforwardly.

### 2023-05-09 paper/sup/supplementary_information.tex
refactor(paper): :recycle: 将LaTeX工作流打通

@@
 
-\documentclass[draft,wrr]{agutexSI2019}
+\documentclass[draft,wrr]{../agutexSI2019}
 \usepackage{amsmath}
@@
 
+% 构成稀缺情况的指标（SFV指数）在研究时段（包括三个不同时期）内呈现出先降低、然后迅速增加、最后再次略微降低的变化趋势（图~\ref{ch4:fig:scarcity}~A），表明水资源压力先减少再迅速增加，后趋于稳定。
+% 源区、上游、中游、下游这四个不同的区域中（图~\ref{ch4:fig:scarcity}~B），源区对三个时段的SFV指标变化几乎没有贡献，下游也仅在治理转变时期和适应增强时期呈现微弱的负向贡献。
+% 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
+The index of scarcity (SFV index) in the study period (including three different periods) showed A change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
+In the four different regions (Figure~\ref{fig:scarcity}~B), the source region has almost no contribution to SFV index changes in the three periods, and the downstream region only has a weak negative contribution in the governance transition period and the adaptation enhancement period.
+The upper and middle reaches of the Yellow River had the greatest impact on the scarcity.
+The upper reaches made the greatest contribution to SFV change in the period of centralized water supply and governance change, while the middle reaches made the greatest contribution in the period of adaptation enhancement.
+
+% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:priority}~A）。
+% 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
+In terms of water use purpose, the proportion of supply water remained basically unchanged in the period of centralized water supply, but showed A rapid decline in the period of governance transformation and adaptation enhancement (Figure~\ref{fig:priority}~A).
+In the three periods, the change of irrigation water dominated the change of the proportion, while urban and rural water for human settlements and rural livestock had almost no influence on the change of the proportion (Figure~\ref{fig:allocation}~B).
+
+% 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
+The index change of distribution mode showed an obvious ``V-shaped'' trend, indicating that water resources in the source region, upper, middle and lower reaches of the Yellow River first gradually moved away from uniform distribution, and then gradually tended to average distribution after 2000 (Figure~\ref{fig:allocation}).
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\textwidth]{sup/priority.jpg}
+\caption{Changing trend of the indicator of priority}\label{fig:priority}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\textwidth]{sup/allocation.png}
+\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\textwidth]{sup/scarcity.png}
+\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
+\end{figure}
+
 \noindent\textbf{Datasets}\label{secA3}

### 2023-05-09 paper/main/02_methods.tex
refactor(paper): :recycle: 拆分到各个文件中

@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress~\cite{qin2019}.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed in~\citeA{qin2019} to evaluate water stress.
 	This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.

### 2023-05-09 paper/response_letter/source/editor.tex
refactor(paper): :recycle: 拆分到各个文件中

--- 2023-03-30 paper/letter/response_v6/associate_editor.tex
@@
-Dear Associate Editor,
+\subsection{General comments}
+\RC{} Dear Authors, thanks for the submission of the manuscript.
+We have asked two experts in the relevant fields to review the manuscript.
+Both reviewers overall find the merit in the manuscript however they also noted several major issues in the current manuscript.
+With my own reading, I fully agree with the reviewers and would like to highlight a few major issues:
 
-Thank you for your constructive comments and for providing us with the opportunity to address the concerns raised by both reviewers.
+\AR{} Thank you for your constructive comments and for providing us with the opportunity to address the concerns raised by both reviewers.
 We appreciate the valuable feedback, which has helped us identify areas for improvement in our manuscript.
@@
 
-Shallow results and discussion:
-We acknowledge the need for a more in-depth analysis of our results.
+\subsection{Issue \#1}
+\RC{} overall the results and discussion are relatively shallow and I would encourage the authors to do deep dive into the results, e.g.\ change points, as also pointed out by both reviewers,
+
+\AR{} We acknowledge the need for a more in-depth analysis of our results.
 We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers.
-We have also provided more context and explanation for these changes in the manuscript, which can be found on pages 14-16 and 18-21.
-Review of existing and relevant indicators with IWGI:
-We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.
+We have also provided more context and explanation for these changes in the manuscript, which can be found on pages 14\-16 and 18\-21.
+
+\subsection{Issue \#2}
+\RC{} I fully agree with Reviewer \#2 that more thorough review of existing and relevant indicators with IWGI,
+
+\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.
 We have added a new section in the manuscript discussing these indicators, comparing and contrasting their strengths and weaknesses, and explaining how our approach fills the gaps in the current literature.
-This new section can be found on pages 5-7.
-More recent data (beyond 2013):
-We appreciate the importance of using up-to-date data in our research.
+This new section can be found on pages 5\-7.
+
+\subsection{Issue \#3}
+\RC{} I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer 1.
+In addition, I find the data in supplementary materials is not accessible, which should be amended.
+The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously.
+
+\RC*{} Overall, based on the reviewers' recommendations, I would like to ask the authors to submit a suitably revised manuscript in due course.
+
+\AR{} We appreciate the importance of using up-to-date data in our research.
 We have now included more recent data in our analysis, extending our dataset up to 2021.
 The updated data, along with the revised results and discussion, can be found on pages 11-13 and 18-21.
-Accessibility of supplementary materials:
-We apologize for the inconvenience caused by the inaccessibility of the supplementary materials.
+
+\AR*{} We apologize for the inconvenience caused by the inaccessibility of the supplementary materials.
 We have rectified this issue by ensuring that all supplementary data and files are now accessible and properly linked within the manuscript.
 We have also provided a clear description of the data and methodology in the supplementary materials to facilitate reproducibility of our results.
-We hope that these revisions address the concerns raised by both reviewers and the associate editor.
+
+\AR*{} We hope that these revisions address the concerns raised by both reviewers and the associate editor.
 We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community.
 We look forward to your further feedback and the possibility of our manuscript being accepted for publication.
-
-Sincerely,
-
-[Your Name]
-[Your Affiliation]

### 2023-05-09 paper/response_letter/source/reviewer_2.tex
refactor(paper): :recycle: 拆分到各个文件中

\subsection*{Overall comments}
% 作者提出了IWGI，并将其应用于黄河流域的水治理历史，分析了流域的制度变迁。该方法具有很强的合理性和适应性，案例分析的结果为理解中国的水治理提供了有益的见解。然而，讨论并没有充分利用案例研究分析的结果。讨论结果的内容应该更具有支持性和可靠性。此外，讨论的叙事分析非常有趣，但如果这项研究的原创性之一是识别变化点，那么就需要更多地讨论导致这些变化点的触发因素。请参考我下面的审稿意见并进行修改，以提高本文的价值。
\RC{} The authors proposed the IWGI, applied the index to the history of water governance in the Yellow River basin, and analyzed the regime change in the basin. The methodology is very reasonable and adaptable, and the results of the case analysis provide useful insights for understanding water governance in China. However, the discussion does not fully exploit the results of the case study analysis. The discussion should be more supportive and solid in its content of the results. Also, the narrative analysis of the discussion is very interesting, but if one of the originalities of this study is the identification of change points, more discussion of the triggers that caused these change points is needed. Please refer to my review comments below and revise them to enhance the value of this paper.

\AR{} Thanks!

\subsection{Comment \#1}
% 图1:很难理解B中每个数字的含义。也许是这个数字的大小有问题。
\RC{} Figure 1: It is difficult to understand what each number in B means. Perhaps it may be a problem with the size of the figure.

\subsection{Comment \#2}
% 导言:与流域和水资源相关的指标有很多，其中一些指标具有与治理和政策相关的参数。为了突出你所制定的IWGI的新颖性，也许你可以加上对其他相关指标的审查。
\RC{} Introduction: There are many indicators related to watersheds and water resources, some of which have parameters related to governance and policy. To highlight the novelty of the IWGI that you have developed, perhaps you could add a review of other relevant indicators.

\subsection{Comment \#3}
% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained. e.g. R or WU.

\subsection{Comment \#4}
% 第2.2节:您提到您将Pettitt(1979)方法应用于“水文时间序列”，但结果似乎适用于IWGI时间序列数据。请说明您将该方法应用于哪些数据。
\RC{} Section 2.2: You mention that you apply the Pettitt (1979) approach to "hydrological time series", but the results appear to be for IWGI time series data. Please clarify to which data you applied the approach.

\subsection{Comment \#5}
% 图3:D中哪些类型的官方文件被统计以及如何统计?
\RC{} Figure 3: What types of official documents in D are counted and how?

\subsection{Comment \#6}
% 讨论:每个政权的故事都令人印象深刻。然而，结果与图3的关系并不清楚。请通过更直接地引用结果和图3来加强你的论点。
\RC{} Discussion: The stories of each regime are very impressive. However, the relation to the results and Figure 3 is not clear. Please strengthen your argument by citing the results and Figure 3 more directly.

\subsection{Comment \#7}
% 讨论:从您对变更点的分析中可以明显看出，每个制度中都存在变更点。但为什么会出现这些变化“点”呢?是什么导致或触发了它们?这是管理机构的变化还是象征性的政策变化?该制度期间的特征已被很好地描述，但请更多地考虑为什么变化点发生在特定的年份/时期。
\RC{} Discussion: The existence of change points in each of the regimes is evident from your analysis of the change points. But why did these change "points" occur? What caused or triggered them? Was it a change in governing institutions or a symbolic policy change? The characteristics during that regime period are well described, but please give more thought to why the change points occurred in that particular year/period.

\subsection{Comment \#8}
% 图4:A中的蓝色圆形箭头和B中的红色圆形箭头是什么意思?它们似乎包含了您非常重要的言论，但它们并不清楚。此外，您需要更多地解释A和B中的每个箭头。
\RC{} Figure 4: What do the blue circular arrows in A and the red circular arrows in B mean? They seem to contain your very important remarks, but they are unclear. Also, you need to explain more about each of the arrows in A and B.

\subsection{Comment \#9}
% 结论:对定量分析的结果进行了描述，但是Discussion中的叙事分析似乎没有得到充分的体现。建议对此添加几行。
\RC{} Conclusion: The results of the quantitative analysis are described, but the narrative analysis in the Discussion does not seem to be fully reflected. It is recommended to add a few lines about it.

\AR{} answer

### 2023-05-10 paper/diff/draft.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

@@
 As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019a,long2020,nickum2021}.
-Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019a}.
+These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
+Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.
 
@@
 Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
-Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019a}.
+Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
 Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

### 2023-05-10 paper/main/01_introduction.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

@@
 As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014,abbott2019}.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014a,abbott2019}.
 Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.

### 2023-05-10 paper/main/02_methods.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

@@
 	% 将三者合一起，即：
-	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance.
-Each dimension keeps two directions, and we assumed the hydrosocial cycle aligns with one of them, respectively:
+	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance:
 	\begin{equation}
@@
 	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in~\citeA{qin2019} to evaluate water stress.
-	This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
+	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
+	% 这个指数得到了许多应用，是就我们已知范围内考虑因素最为齐全的，反应水资源压力的指数。
+	The SFV-index, which has many applications, is the most comprehensive index of water stress we know. % todo citation
+
 	Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).

### 2023-05-10 paper/main/04_discussion.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

@@
 Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
-In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016a}.
+In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.
 
@@
 As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019a,long2020,nickum2021}.
+These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
 % 因此，1999年黄河的最后一次枯竭
-Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019a}.
+Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.
 
 The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
-Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
-Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019a}.
+% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
+Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
 Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.
@@
 With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
-In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012a}.
+In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
 Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
 Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
+
+Future's tightly intertwined socio-hydro interactions can lead water governance challenges even more complex and comprehensive, combining resources issues and structural barriers~\cite{huggins2022a}.
+For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
+Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (priority and allocation) which is being increasingly altered by current regime transitions.
+It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
 

### 2023-05-10 paper/main/04_discussion.tex
feat(paper): :sparkles: 回答审稿人1的意见4
正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。

这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?

@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming command (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
 During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.

### 2023-05-10 paper/response_letter/source/tab_corr.tex
feat(paper): :sparkles: 回答审稿人1的意见4
正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。

这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?

% Table generated by Excel2LaTeX from sheet '相关性情况'
\begin{table}[htbp]
    \centering
    \caption{The correlation of the Integrated Governance Index (IWGI) and its three sub-indicators (IS, IP, IA)}
      \begin{tabularx}{\textwidth}{XXXXXXX}
      \toprule
      Period & \multicolumn{1}{l}{IS vs IP} & \multicolumn{1}{l}{IS vs IA} & IP vs IA & \multicolumn{1}{l}{IP vs IWGI} & \multicolumn{1}{l}{IA vs IWGI} & \multicolumn{1}{l}{IS vs IWGI} \\
      \midrule
      P1 to P3 & \multicolumn{1}{l}{-0.75 *} & -0.29 & 0.36 & 0.37  & \multicolumn{1}{l}{0.75 *} & 0.14 \\
      P1    & -0.08 & -0.31 & 0.06 & 0.14  & 0.51  & 0.65 \\
      P2    & \multicolumn{1}{l}{-0.90 *} & \multicolumn{1}{l}{-0.87 *} & 0.77 * & -0.18 & -0.13 & 0.5 \\
      P3    & 0     & -0.38 & -0.86 * & -0.33 & 0.61  & 0 \\
      \bottomrule
      \end{tabularx}%
    \label{tab:corr}%
\end{table}%

### 2023-05-10 paper/sup/supplementary_information.tex
feat(paper): :sparkles: 回答审稿人1的意见4
正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。

这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?

@@
 \usepackage{amsmath}
+% For using tabularx
+\usepackage{tabularx}
+\usepackage{booktabs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), priority (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
+
+When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.
+On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI.
+However, the correlations of other combinations are not statistically significant overall.
+
+The correlations between time periods are very different with the overall trend above.
+There is no significant correlation between any indicator combinations in the massive supply regime (P1).
+In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
+The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3).
+However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).
+
+\input{../response_letter/source/tab_corr.tex}
+
 \noindent\textbf{Datasets}\label{secA3}

### 2023-05-10 paper/main/03_results.tex
feat(paper): :sparkles: 回答审稿人关于水库运输的问题
1. 运输是手段，2. 不增加复杂性，3. 讨论增加了一张图

IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。

@@
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
+Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
+% todo 检查图引用
+Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
 During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).

### 2023-05-11 paper/main/02_methods.tex
feat(paper): :sparkles: 回答审稿人关于指标应用的问题
1. 关于IWGI的泛用性, 2. 使用它的先决条件

Regarding the generality of IWGI, we actually discussed this in our discussion. I am very sorry that the previous discussion seems not clear enough, and we have clarified this point again in the revised manuscript

@@
 	\end{equation}
+
+	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
+	However, vary data sources can be used when estimating the specific indicator or cross different indicators, which makes IWGI a flexible framework for substituted indicators.
 

### 2023-05-11 paper/main/04_discussion.tex
feat(paper): :sparkles: 回答审稿人关于指标应用的问题
1. 关于IWGI的泛用性, 2. 使用它的先决条件

Regarding the generality of IWGI, we actually discussed this in our discussion. I am very sorry that the previous discussion seems not clear enough, and we have clarified this point again in the revised manuscript

@@
 %* limitations & direction
-One of the main limitations in the approach is the lack of long-term data worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI more widely.
-However, we propose that all water governance issues result in changing ``who gets water, when and how'', so monitoring water stress, purposes of water services, and water allocation patterns do help.
-Choices of indicators for different aspects can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
+One of the main limitations in the approach is the lack of multi-sources data in long-term period worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI widely.
+We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
+We suggest that choices of indicators for different aspects can be adapted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based priority indicator (IP) by complicated one.
+Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.
+As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:summary}).
+% TODO 补充材料新图
+Therefore, we suggest IWGI framework can be applied with adaptive indicators and flexible time series according to accessible datasets in future studies.
+
 In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.

### 2023-05-11 paper/main/01_introduction.tex
feat(paper): :sparkles: 应审稿人要求增加对定义和IWGI必要性的表述
1. water governance regime 定义 2. IWGI 的必要性

It would be better to explain the concept ``water governance regime'' in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.

@@
 
-A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
-Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020}.
+A critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
+Regimes of water governance, the general guidelines of practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
 For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)

### 2023-05-11 paper/sup/supplementary_information.tex
feat(paper): :sparkles: 回答审稿人关于水库运输的问题
1. 运输是手段，2. 不增加复杂性，3. 讨论增加了一张图

IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。
feat(paper): :sparkles: 根据审稿人意见增加子指标的图和说明
% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。 % 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。 % 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）

The results are summative. I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions. And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values. These

@@
 % 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
-The index of scarcity (SFV index) in the study period (including three different periods) showed A change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
-In the four different regions (Figure~\ref{fig:scarcity}~B), the source region has almost no contribution to SFV index changes in the three periods, and the downstream region only has a weak negative contribution in the governance transition period and the adaptation enhancement period.
-The upper and middle reaches of the Yellow River had the greatest impact on the scarcity.
-The upper reaches made the greatest contribution to SFV change in the period of centralized water supply and governance change, while the middle reaches made the greatest contribution in the period of adaptation enhancement.
+The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
+Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
+The upper and middle reaches (UR and MR) had the greatest impact on the IS changes.
+Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
 
@@
 % 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
-In terms of water use purpose, the proportion of supply water remained basically unchanged in the period of centralized water supply, but showed A rapid decline in the period of governance transformation and adaptation enhancement (Figure~\ref{fig:priority}~A).
-In the three periods, the change of irrigation water dominated the change of the proportion, while urban and rural water for human settlements and rural livestock had almost no influence on the change of the proportion (Figure~\ref{fig:allocation}~B).
+In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:priority}~A).
+Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
 
 % 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
-The index change of distribution mode showed an obvious ``V-shaped'' trend, indicating that water resources in the source region, upper, middle and lower reaches of the Yellow River first gradually moved away from uniform distribution, and then gradually tended to average distribution after 2000 (Figure~\ref{fig:allocation}).
+The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
 
@@
 \input{../response_letter/source/tab_corr.tex}
+
+\begin{figure}[htb]
+      \centering
+      \includegraphics[width=0.8\textwidth]{sup/conveyance.png}
+      \caption{Monthly conveyance flow differences of the reservoirs mainly for managing and regulating the whole basin and their variability}\label{fig:conveyance}
+\end{figure}
 

### 2023-05-11 regimes_yrb/allocation.py
feat(notebooks): :sparkles: 增补不同源数据并计算IWGI

@@ -49,7 +49,7 @@ def calculate_yearly_indices(region_consumption: pd.DataFrame, year: int) -> dic
     }
 
 
-def calc_regional_entropy(city_yr: pd.DataFrame) -> pd.DataFrame:
+def calc_regional_entropy(city_yr: pd.DataFrame, wu_cols: list = None) -> pd.DataFrame:
     """
     计算每年各区域的总用水，并计算区域间、部门间以及总体的水资源分配熵指数。
 
@@ -69,8 +69,9 @@ def calc_regional_entropy(city_yr: pd.DataFrame) -> pd.DataFrame:
                   - "Sectors": 总体熵指数
                   - "Ratio": 区域间与部门间熵指数之比
     """
-    wu_cols = ["IRR", "IND", "DOM"]
-    city_yr["DOM"] = city_yr["RUR"] + city_yr["URB"]  # 人居耗水
+    if wu_cols is None:
+        wu_cols = ["IRR", "IND", "DOM"]
+        city_yr["DOM"] = city_yr["RUR"] + city_yr["URB"]  # 人居耗水
     region_consumption = city_yr.groupby(["Year", "Region"])[wu_cols].sum()  # 每个区域的总耗水量
 
     results = {

### 2023-05-11 regimes_yrb/index.py

@@ -27,6 +27,9 @@ def integrated_water_governance_index(
         raise KeyError("'norm' must be 'log_zscore' or 'zscore'")
     results["IWGI"] = results.sum(axis=1) / 3
     breakpoints = pettitt_changes(results["IWGI"])
+    if len(breakpoints) == 0:
+        results["stage"] = "P1"
+        return results
     results.loc[results.index < breakpoints[0], "stage"] = "P1"
     results.loc[
         (breakpoints[0] <= results.index) & (results.index < breakpoints[1]),

### 2023-05-11 paper/main/01_introduction.tex
fix(paper): :pencil2: 修改 water governance 理解的引用错误
mariajacobson2013

Line 57\-62: I did not find the ``three core aspects of water use'' in the cited reference. Were the three aspects put forward by the authors?

@@
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
-Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{undpwatergovernancefacility2016}.
+Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018,allan2001}.
+Correspondingly, the United Nations Development Programme (UNDP) proposed that water governance can decide water use from three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (priority), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
 % 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。

### 2023-05-11 paper/main/01_introduction.tex
fix(paper): :pencil2: 修改参考文献缺失问题
Line 92: missing information for the citation?

@@
 The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019}.
-Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016e,song2020a}.
+Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.
 However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic~\cite{wang2019c}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016a}.
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016}.
 Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.

### 2023-05-11 paper/main/01_introduction.tex
fix(paper): :pencil2: 修改一处语意不明

@@
 Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.
-However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic~\cite{wang2019c}.
+However, new challenges such as decreased streamflows and water depletions occurred in more recent times, followed by different water governance practices like water use regulation and water transfer across basins~\cite{wang2019c}.
 Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016}.

### 2023-05-11 paper/main/02_methods.tex
feat(paper): :sparkles: 根据审稿人意见增加子指标的图和说明
% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。 % 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。 % 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）

The results are summative. I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions. And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values. These details could help readers understand the reasonability of the results.
refactor(paper): :memo: 将补充材料里的SFV计算挪到正文

@@
 Then, we analyzed the changes in the IWGI from 1965 to 2013 using change point detection methods.
-The normalized Indicator for each dimension affects the IWGI by changing trends and contributions.
+The normalized indicator for each dimension affects the IWGI by changing trends and contributions.
 
@@
 
-	where:
+	where $I'_x$ is calculated by Min-Max normalization of $I_x$ (thus ranges from zero to one):
 	\begin{equation}
@@
 
-	\subsubsection*{Indicator of stress}
+	\subsubsection{Indicator of stress (IS)}
 	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
@@
 
-	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \textit{Supporting Information S2}.
+	Where $SFV_i$ is the scarcity-flexibility-variability (SFV) index of region $i$.
+By taking water flexibility and variability into account, the SFV focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses~\cite{qin2019}.
+To apply this method, we need to combine three metrics following:
 
-	\subsubsection*{Indicator of purpose}
+	First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \\textit{Supporting Information}~\ref{secA1}):
+	\begin{equation}
+		A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
+	\end{equation}
+
+	Second, for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.\ for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
+	\begin{equation}
+		B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}}
+	\end{equation}
+
+	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
+	\begin{gather}
+	C_i = C1_i * (1 - C2_i) \\
+	C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} \\
+	C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} \\
+	C2_{i} = 1, \ if RC >= R_{i, avg}
+	\end{gather}
+
+	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+
+	Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate the $SFV$ index after normalizing them:
+	\begin{gather}
+		V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3}\\
+		a = \frac{1}{V_{\max} - V_{\min}};\\
+		b = \frac{1}{V_{\min} - V_{\max}} * V_{\min}\\
+		SFV = a * V + b
+	\end{gather}
+
+	\subsubsection{Indicator of purpose (IP)}
 	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
@@
 
-	\subsubsection*{Indicator of allocations}
+	\subsubsection{Indicator of allocations (IA)}
 	To describe allocations $I_A$, we designed an indicator based on entropy, called Allocation Entropy Metric (AEM), which measures the degree of evenness in water allocation:

### 2023-05-11 paper/main/02_methods.tex
fix(paper): :pencil2: 修改IP的公式名称
Equation (6): Why is the numerator WUpro not WUnon-pro? Please check the equation.

@@
 	\subsubsection{Indicator of purpose (IP)}
-	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
+	To quantify purpose $I_P$, we used provisioning purpose shares (PPS) of water use as an indicator.
 While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the NPS as:
+We calculated the PPS by:
 	\begin{equation}
-		NPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
+		PPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
 	\end{equation}

### 2023-05-11 paper/main/04_discussion.tex
fix(paper): :pencil2: 修改公式AEM和讨论的错别字
Equation (7): CEM => AEM?
Line 273: adapted => adopted?

@@
 We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
-We suggest that choices of indicators for different aspects can be adapted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based priority indicator (IP) by complicated one.
+We suggest that choices of indicators for different aspects can be adopted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based priority indicator (IP) by complicated one.
 Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.

### 2023-05-11 paper/main/03_results.tex
fix(paper): :pencil2: 根据审稿人意见修改一系列表述问题和错字问题

@@
 	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: $1965 \sim 1978$, P2: $1979 \sim 2001$, and P3: $2002 \sim 2013$.
-	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
+	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.001$) occurred in 1978 and 2001.
 	\textbf{B,} correlation of trends between the IWGI and the indicators.
@@
 		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time.
+Dashed lines denote average of these percentages in different regimes.
 Red circles denote the reservoirs mainly for managing and regulating the whole basin.
 		The size of each circle indicates the magnitude of its water storage capacity.
-		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
+		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
@@
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Environmental context, social transformation, and policies played roles in all three periods.
+Environmental context, social atmosphere, and policies played roles in all three periods.
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.

### 2023-05-11 paper/main/04_discussion.tex
fix(paper): :pencil2: 根据审稿人意见修改一系列表述问题和错字问题

@@
 As tele-coupling raises additional water governance challenges in an increasingly tightly-connected world, regime shifts in water governance align with different human-water relationships~\cite{diaz2019}.
-The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition~\cite{loch2020,turton1999}.
+The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle~\cite{loch2020,turton1999}, and the IWGI quantitatively identifies this transition.
 It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime~\cite{reyers2018}.
@@
 
-In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
+In today's world, regime shifts from natural to human-dominated seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
 Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional, and planetary boundaries where human-water systems may collapse~\cite{gleeson2020, wang-erlandsson2022}.

### 2023-05-12 paper/main/04_discussion.tex
docs(paper): :label: 更新了图3在讨论部分的引用

@@
 In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
-During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
-As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
-The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
+During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
+The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
 Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
@@
 
-The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
+The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
 % 正如理论预测的那样
@@
 As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
+These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
 % 因此，1999年黄河的最后一次枯竭
@@
 % 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
-Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
 Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.
do

@@
+\section{Reviewer \#2}\label{reviewer_2}
+
 \subsection*{Overall comments}
@@
 \RC{} Figure 1: It is difficult to understand what each number in B means. Perhaps it may be a problem with the size of the figure.
+
+\AR{} Thanks for the comment. We now improved the figure in the revised manuscript. % TODO 修改图1让它更清楚
 
@@
 
+\AR{} Thanks for the suggestion. We now append refers in discussion when figure 3 is supporting:
+
+\begin{quote}
+    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+\end{quote}
+
+\begin{quote}
+    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
+\end{quote}
+
+\begin{quote}
+    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
+\end{quote}
+
+\begin{quote}
+    As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
+These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes});
+\end{quote}
+
 \subsection{Comment \#7}
@@
 The characteristics during that regime period are well described, but please give more thought to why the change points occurred in that particular year/period.
+
+% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们认为总体来说是。这就像复杂系统中不是单独的一个，
+\AR{} A good comment.
 

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
feat(paper): :sparkles: 讨论审稿人提出的变化点问题

@@
 \RC{} Discussion: The existence of change points in each of the regimes is evident from your analysis of the change points.
-But why did these change "points" occur?
+But why did these change ``points'' occur?
 What caused or triggered them?
@@
 
-% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们认为总体来说是。这就像复杂系统中不是单独的一个，
-\AR{} A good comment.
+% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们总体认为制度转变还是一段时间内持续、积累的变化在特定的点产生了统计特征，很难将其总结成某种因素造成的变化。这也是为什么我们要把各种因素考虑在内，构造这样一个综合指数的原因，不是吗？
+\AR{} Thanks to such interesting comments, although the result changes at certain points statistically, we generally believe that the change of the system is still a result of the accumulation of water governance practices in period of time.
+Therefore, it is difficult to summarize it into a change caused by one factor.
+That's why we have to take all these factors into account and construct a composite index like this, right?
+
+% 我们认为这类似于复杂系统的涌现，许多数不胜数的治理措施在不断地提出与执行（正如图3C所示），每一个措施都会针对一个具体的问题，但流域整体将向何处发展取决于这些措施的合力。
+\AR*{} We think of this as analogous to the ``emergence'' of complex systems.
+Numerous practices being proposed and implemented (e.g., basin-scaled practices of the Yellow River as shown in Figure~3C).
+Each practice addresses a specific issue, but how the water governance feature changing overall depends on a combination of their outcomes.
+
+% 当然，并不是说完全无法在特定年份为Regime shift给出解释。在中国的治理模式里，``领会精神''是一个有趣的东西。通常，中央高层会释放一些信号，各级政府（包括部委和地方行政部门）如果按照这种``精神''执行了某种治理措施并取得不错的成果，便是一个非常好的政绩。这种治理模式便是我们在结果、图3、讨论中都提及``social atmosphere''（返修前的手稿我们称之为 social transformation）的原因，这种治理风气会引导治理措施。
+\AR*{} It is not to say that there is absolutely no explanation for Regime shift in a given year.
+In China's governance model, ``central spirit'' is interesting.
+Usually, the top level of the central government sends some signals.
+If governments at all levels (including ministries and local administrative departments) implement certain governance measures in accordance with this ``spirit'' and achieve good results, it will be a good governance.
+This feature is the reason why we mentioned the ``social atmosphere'' (the manuscript before the revision was called social transformation) in the results, Figure 3, and discussion -atmosphere can guide the governance practices.
+
+% 例如在上世纪1960s到1970s，中国在毛泽东领导下有着强烈的``征服自然''风气，这是非常出名的，这种风气能导致建立更多的水库大坝、增大供给。而改革开放带来的阶段二的需求增加、水竞争、效率提升。2000年后中国强调环境治理，等等。可以说我们识别的两次转变都和``social atmosphere''的变化不无关系。但我们很小心的避免了这种归因，因为这种治理转变，绝非单独自上而下的一句口号就能实现的，也有很多其它类似的``中央精神''未能得到有效贯彻执行。
+\AR*{} For instance, the ``reform and opening up'' led to increased water demand, water competition and efficiency in transformation regime.
+After 2000, China emphasized environmental issues \dots It can be said that the two changes we identified are partially related to the change of ``social atmosphere''.
+But we are very careful to avoid this simple attribution, because this change in governance can not be achieved by a top-down slogan alone, and there are many other similar ``central spirit'' has not been effectively implemented.
+
+\AR*{} Taken together, we believe regime shifts are ``emergence'' of the human-water system, but the significant and solid changing points of the YRB can be related to social atmosphere.
 

### 2023-05-12 paper/main/04_discussion.tex
feat(paper): :sparkles: 根据审稿人意见增加对讨论图的箭头说明

@@
 In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
+To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
+At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
+With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
 In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
@@
 		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
+		The large circular arrows indicate the social and hydrological processes that dominate in different stages.
+		Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
+		The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
+		The gray thick arrow represents weaker process, while the red arrow represents more significant one.
 		\textbf{A.} As socio-economic systems develop, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources to alleviate water stress.
-		\textbf{B.} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
+		\textbf{B.} With further growing socio-economic systems, trade-offs between provisioning-purpose and non-provisioning water use become prominent; a basin-wide socio-economic system requires more organized water governance.
 		Thus, \textbf{C.

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
feat(paper): :sparkles: 根据审稿人意见增加对讨论图的箭头说明

@@
 
+% 很抱歉之前的手稿造成了此困惑，我们现在在返修后的手稿中增加了以下内容，以便更清晰地说明
+\AR{} I'm sorry for the confusion caused by the previous manuscript. We have now added the following content to the caption of that figure in revised manuscript:
+
+\begin{quote}
+    Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
+    The large circular arrows indicate the social and hydrological processes that dominate in different stages.
+    Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
+    The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
+    The gray thick arrow represents weaker process, while the red arrow represents more significant one.
+\end{quote}
+
+\AR*{} In addition, other two sentences in discussion can make it clearer:
+
+\begin{quote}
+    To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
+    At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
+    With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
+\end{quote}
+
 \subsection{Comment \#9}

### 2023-05-12 paper/main/05_conclusion.tex
docs(paper): :memo: 根据审稿人意见，结论里提一些讨论的叙述

@@
+% 围绕“谁获得水、何时获得水、如何获得水”，水治理在水社会循环转型过程中发生了三个方面的变化:水压力、水服务目的和水分配。
+% 我们开发了一个综合水治理指数(IWGI)，通过整合它们来检测水治理的制度转变。将IWGI应用于一个快速变化的大流域(中国黄河流域)，我们解释了半个多世纪以来水治理如何在三种制度之间转变。
+% 我们的方法定量地确定了长江三角洲水治理制度的一般模式，与之前具有代表性的过渡过程的理论分析一致。
+% IWGI的实施将制度变迁与根本原因联系起来，为解释水治理、水社会转型和人水关系交织的变化提供了一种全面而直接的方法。
 Focusing on ``who gets water, when and how'', three aspects of water governance change along with the hydrosocial cycle transition: water stress, water services purpose, and water allocation.
@@
 Applying the IWGI to a rapidly-changing large river basin (the Yellow River Basin, China), we interpret how water governance shifts between three regimes over half a century.
+During the massive supply regime (P1: $1965 \sim 1978$), water governance tended to boost water supply by constructing reservoirs and channels in the YRB.\
+Then, the start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use and led to institutional changes like water-saving improvements, water quota policies, and cross-boundary water transfer plans.
+Last, adaptation-oriented regime (P3: $2002 \sim 2013$) with stable high water stress resulted in trade-offs and joint regulating between water-dependent regions and sectors.
 Our approach quantitatively identifies the general schema for water governance regimes in the YRB, in line with previous theoretical analysis with a representative transition process.

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 根据审稿人意见，结论里提一些讨论的叙述

@@
 
-\AR{} answer
+\AR{} Sure! Thanks for the valuable suggestion. We now added narrative analysis in the discussion to our conclusion:
+
+\begin{quote}
+    During the massive supply regime (P1: $1965 \sim 1978$), water governance tended to boost water supply by constructing reservoirs and channels in the YRB.\
+    Then, the start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use and led to institutional changes like water-saving improvements, water quota policies, and cross-boundary water transfer plans.
+    Last, adaptation-oriented regime (P3: $2002 \sim 2013$) with stable high water stress resulted in trade-offs and joint regulating between water-dependent regions and sectors.
+\end{quote}

### 2023-05-12 paper/main/02_methods.tex
fix(paper): :pencil2: 修改公式AEM和讨论的错别字
Equation (7): CEM => AEM?
Line 273: adapted => adopted?
docs(paper): :memo: 更新大事记的数据说明

@@
 	\begin{equation}
-		I_A = CEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
+		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
 	\end{equation}
@@
 	\subsection{Datasets}
+	% 本研究使用了多源数据，我们附上了一个数据表作为补充材料，并在补充文档中
 	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	In order to calculate IWGI in the YRB, all the datasets we need are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
+	Multiple sources of data were used in this study, and we have attached a summarized data table as supplementary material and their processing are detailed described in the supplementary documentation.

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 更新大事记的数据说明

@@
 % 第2.2节:您提到您将Pettitt(1979)方法应用于“水文时间序列”，但结果似乎适用于IWGI时间序列数据。请说明您将该方法应用于哪些数据。
-\RC{} Section 2.2: You mention that you apply the Pettitt (1979) approach to "hydrological time series", but the results appear to be for IWGI time series data.
+\RC{} Section 2.2: You mention that you apply the Pettitt (1979) approach to ``hydrological time series'', but the results appear to be for IWGI time series data.
 Please clarify to which data you applied the approach.
@@
 \RC{} Figure 3: What types of official documents in D are counted and how?
+
+% 抱歉之前的手稿中没有更加明确地进行说明，这份文件统计数据源来自黄河的流域管理部门-黄河水利委员会（YRCC），该部门会对黄河相关的“大事”进行记录并编纂发布。本研究仅根据这些“大事”的发生年份进行逐年统计记录数量。
+\AR{} Sorry for not being more explicit in the previous manuscript.
+The document comes from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river.
+This study only recorded the number of these ``events'' year by year according to the time they occurred.
+
+\AR*{} To make that more explicit, we modified the corresponding description in the Supplementary Materials:
+
+\begin{quote}
+    In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
+    The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river.
+This study only recorded the number of these ``events'' year by year according to the time they occurred.
+\end{quote}
 

### 2023-05-12 paper/sup/03_datasets.tex
docs(paper): :memo: 更新大事记的数据说明

@@
 The policy dataset collects laws and policies listed in the book \cite{yellowriverconservancycommission2013}, which are related to the Yellow River basin promulgated and implemented by departments at (such as YRCC) and above (such as national institutions) at the Basin's level (Table~\ref{tab:policies}).
-In addition, some are difficult to categorize; not a landmark, but numerous water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC; we collected them from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
+In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
+The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river.
+This study only recorded the number of these ``events'' year by year according to the time they occurred.
 

### 2023-05-12 paper/main/02_methods.tex
docs(paper): :memo: 更新Pettitt方法应用的数据描述

@@
 	\subsection{Change points detection}
-		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data~\cite{pettitt1979}.
+		We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
 		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.

### 2023-05-12 paper/main/02_methods.tex
docs(paper): :memo: 更新SFV的方法叙述，符号说明提前

@@
 By taking water flexibility and variability into account, the SFV focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses~\cite{qin2019}.
-To apply this method, we need to combine three metrics following:
+To apply this method, we need to combine three metrics: scarcity, flexibility and variability.
+	In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
 
@@
 	\end{gather}
-
-	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
 
@@
 
-	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
+	where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
 

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 更新Pettitt方法应用的数据描述
docs(paper): :memo: 更新SFV的方法叙述，符号说明提前

@@
 % 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
-\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained. e.g. R or WU.
+\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained.\ e.g. R or WU.\
+
+\AR{} Thanks for the comment. ``CEM'' should be ``AEM'' -the indicator we applied for IA.\ This has been revised in the new manuscript:
+
+\begin{quote}
+    \begin{equation}
+		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
+	\end{equation}
+\end{quote}
+
+\AR*{} Also, sorry about the misunderstanding term. We modified the sentence with ``water proportion'' to:
+
+\begin{quote}
+    where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
+\end{quote}
+
+% 很抱歉关于SFV计算的部分也造成了困惑。实际上我们提到了这些符号的意义，只不过是在所有公式之后。这的确会造成误解，因此在返修后的文章中我们将这段叙述放到了公式之前：
+\AR*{} Sorry that the part about SFV calculation also caused confusion.
+We actually mentioned the meaning of these symbols, but only after all the equations since they shared the same symbols.
+This indeed can be misleading, so in the revised article we put this statement before the formula:
+
+\begin{quote}
+    In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+\end{quote}
 
@@
 Please clarify to which data you applied the approach.
+
+\AR{} Thanks for pointing it out! Pettitt approach was applied to IWGI time series data. We now clarify that in the method section:
+
+\begin{quote}
+    We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
+\end{quote}
 

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 回答审稿人引言增加指标叙述

@@
 To highlight the novelty of the IWGI that you have developed, perhaps you could add a review of other relevant indicators.
+
+\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:  % TODO 检查引用
+
+\begin{quote}
+    Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
+    From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
+    However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
+    A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used.
+% todo cite OECD
+    From the water side, intuitive indexes can provide an embodiment of governance outcomes.
+    Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
+    As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
+    These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
+    Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
+\end{quote}
 

### 2023-05-12 paper/main/01_introduction.tex
fix(paper): :art: 修改图片1的大小
fix(project): :pencil2: priority -> purpose

@@
 Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018,allan2001}.
-Correspondingly, the United Nations Development Programme (UNDP) proposed that water governance can decide water use from three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (priority), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
+Correspondingly, the United Nations Development Programme (UNDP) proposed that water governance can decide water use from three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
 % 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。
@@
 \begin{figure*}[!ht]
-	\centering
-	\includegraphics[width=0.9\textwidth]{main/framework.png}
+	\centerline{
+		\includegraphics[width=1.2\linewidth]{main/framework.png}
+	}
 	\caption{

### 2023-05-12 paper/main/04_discussion.tex
fix(project): :pencil2: priority -> purpose

@@
 For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
-Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (priority and allocation) which is being increasingly altered by current regime transitions.
+Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (purpose and allocation) which is being increasingly altered by current regime transitions.
 It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
@@
 We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
-We suggest that choices of indicators for different aspects can be adopted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based priority indicator (IP) by complicated one.
+We suggest that choices of indicators for different aspects can be adopted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based purpose indicator (IP) by complicated one.
 Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.

### 2023-05-12 paper/sup/supplementary_information.tex
fix(project): :pencil2: priority -> purpose

@@
 
-% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:priority}~A）。
+% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:purpose}~A）。
 % 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
-In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:priority}~A).
+In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
 Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
@@
 \centering
-\includegraphics[width=\textwidth]{sup/priority.jpg}
-\caption{Changing trend of the indicator of priority}\label{fig:priority}
+\includegraphics[width=\textwidth]{sup/purpose.jpg}
+\caption{Changing trend of the indicator of purpose}\label{fig:purpose}
 \end{figure}
@@
 
-By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), priority (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
+By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
 

### 2023-05-12 paper/main/01_introduction.tex
refactor(paper): :art: 更新正文所有图件

@@
 	\centerline{
-		\includegraphics[width=1.2\linewidth]{main/framework.png}
+		\includegraphics[width=1.1\linewidth]{main/framework.png}
 	}
 	\caption{
-		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
-Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
-Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
-For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
-		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
+		\textbf{A.} Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
+Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered.
+		For example, reservoir construction (\ding{172} and \ding{173}) can relieve local water stress; The development of intensive irrigated agriculture (\ding{174}) and growth of energy industrial demand (\ding{175}) will change the purpose of water use; The water delivery system controls water allocation (\ding{176} and \ding{177}) within the basin system.
+		\textbf{B.} Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance.
 	}\label{fig:framework}

### 2023-05-12 paper/main/01_introduction.tex
docs(paper): :zap: 润色引言新增部分并补充参考文献

@@
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018,allan2001}.
-Correspondingly, the United Nations Development Programme (UNDP) proposed that water governance can decide water use from three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
+Water governance encompasses the political, social, economic, and administrative systems that regulate water use and management, dictating ``who gets water, when and how''~\cite{lasswell2018,allan2001}.
+In this context, the United Nations Development Programme (UNDP) suggests that water governance determines water usage across three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
 % 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。
-Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
-From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
-However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
-A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used. % todo cite OECD
-From the water side, intuitive indexes can provide an embodiment of governance outcomes.
-Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
-As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
-These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
-Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
+Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
+On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
+For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
+On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
+Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
+Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
+As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
 
-An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
-First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress~\cite{qin2019,wada2014,huang2021}.
-Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)~\cite{liu2017,florke2018,jaeger2019}.
-Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations~\cite{schmandt2021,speed2013}.
-Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.
+The impetus for developing this new index lies in the evolving practices of water governance driven by a blend of social and natural influences.
+Firstly, climate change impacts on current water yield, coupled with escalating demands from economic activities and the need for water storage development, intensify water stress~\cite{qin2019,wada2014,huang2021}.
+Secondly, the purpose of water in serving human well-being is witnessing a shift in trade-offs.
+The balance between provisioning uses (such as drinking water and food production) and non-provisioning uses (like energy production) is tilting, reflecting changes in societal needs and values~\cite{liu2017,florke2018,jaeger2019}.
+Thirdly, the allocation of water across a basin is not solely determined by regional socio-economic and environmental contexts but is also increasingly influenced by systematic regulations~\cite{schmandt2021,speed2013}.
+As we transition towards a human-dominated regime, these three interlinked aspects -stress, purpose, and allocation, are undergoing substantial changes.
+Assessing them separately could lead to systematic failures in water governance, highlighting the need for a more integrated approach in evaluating water governance practices.
 
 A critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
-Regimes of water governance, the general guidelines of practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
+Regimes of water governance, the general guidelines of governing practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
 For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)

### 2023-05-12 paper/diff/draft.tex
refactor(paper): :recycle: 生成LaTeXdiff 并搞清楚怎么弄

@@
-\documentclass[draft]{agujournal2019}
+\documentclass[draft]{../agujournal2019}
 \usepackage{url} \usepackage{lineno}
-\usepackage[inline]{trackchanges} \usepackage{soul}
+\usepackage[inline]{../trackchanges} \usepackage{soul}
 \usepackage{amsmath}
-\linenumbers
+\usepackage{pifont}  \linenumbers
 
@@
 \begin{document}
+\justify
 
 \graphicspath{{/Users/songshgeo/Documents/VSCode/WGRegimes_YRB_2020/figures}}
-\title{Identifying regime transitions for water governance at a basin scale}
+\title{Identifying regime transitions for water governance: Take the Yellow River Basin in China as case}
 
@@
 As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
-Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014,abbott2019}.
+Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014a,abbott2019}.
 Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.
 
-Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
-Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{undpwatergovernancefacility2016}.
-Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
-From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
-However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
-A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used.
-From the water side, intuitive indexes can provide an embodiment of governance outcomes.
-Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
-As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
-These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
-Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
+Water governance encompasses the political, social, economic, and administrative systems that regulate water use and management, dictating ``who gets water, when and how''~\cite{lasswell2018,allan2001}.
+In this context, the United Nations Development Programme (UNDP) suggests that water governance determines water usage across three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
+Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
+On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
+For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
+On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
+Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
+Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
+As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
 
-An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
-First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress~\cite{qin2019,wada2014,huang2021}.
-Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)~\cite{liu2017,florke2018,jaeger2019}.
-Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations~\cite{schmandt2021,speed2013}.
-Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.
+The impetus for developing this new index lies in the evolving practices of water governance driven by a blend of social and natural influences.
+Firstly, climate change impacts on current water yield, coupled with escalating demands from economic activities and the need for water storage development, intensify water stress~\cite{qin2019,wada2014,huang2021}.
+Secondly, the purpose of water in serving human well-being is witnessing a shift in trade-offs.
+The balance between provisioning uses (such as drinking water and food production) and non-provisioning uses (like energy production) is tilting, reflecting changes in societal needs and values~\cite{liu2017,florke2018,jaeger2019}.
+Thirdly, the allocation of water across a basin is not solely determined by regional socio-economic and environmental contexts but is also increasingly influenced by systematic regulations~\cite{schmandt2021,speed2013}.
+As we transition towards a human-dominated regime, these three interlinked aspects -stress, purpose, and allocation, are undergoing substantial changes.
+Assessing them separately could lead to systematic failures in water governance, highlighting the need for a more integrated approach in evaluating water governance practices.
 
-A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
-Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020}.
+A critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
+Regimes of water governance, the general guidelines of governing practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
 For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
@@
 \begin{figure*}[!ht]
-	\centering
-	\includegraphics[width=0.9\textwidth]{main/framework.png}
+	\centerline{
+		\includegraphics[width=1.1\linewidth]{main/framework.png}
+	}
 	\caption{
-		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
-Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}).
-Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance.
-For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
-		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
+		\textbf{A.} Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI).
+Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered.
+		For example, reservoir construction (\ding{172} and \ding{173}) can relieve local water stress; The development of intensive irrigated agriculture (\ding{174}) and growth of energy industrial demand (\ding{175}) will change the purpose of water use; The water delivery system controls water allocation (\ding{176} and \ding{177}) within the basin system.
+		\textbf{B.} Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance.
 	}\label{fig:framework}
@@
 The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019}.
-Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016e,song2020a}.
-However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic~\cite{wang2019c}.
-Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016a}.
+Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.
+However, new challenges such as decreased streamflows and water depletions occurred in more recent times, followed by different water governance practices like water use regulation and water transfer across basins~\cite{wang2019c}.
+Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016}.
 Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.
@@
 
-As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance.
-Each dimension keeps two directions, and we assumed the hydrosocial cycle aligns with one of them, respectively:
+As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance:
 	\begin{equation}
@@
 
-	\subsubsection*{Indicator of stress}
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress~\cite{qin2019}.
-This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
+	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
+	However, vary data sources can be used when estimating the specific indicator or cross different indicators, which makes IWGI a flexible framework for substituted indicators.
+
+	\subsubsection{Indicator of stress (IS)}
+	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
+	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
+The SFV-index, which has many applications, is the most comprehensive index of water stress we know.
+
 	Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).
@@
 
-	Where $SFV_i$ is the SFV-index for region $i$, and the detailed calculation of $SFV_i$ can be found in the \textit{Supporting Information S2}.
+	Where $SFV_i$ is the scarcity-flexibility-variability (SFV) index of region $i$.
+By taking water flexibility and variability into account, the SFV focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses~\cite{qin2019}.
+To apply this method, we need to combine three metrics: scarcity, flexibility and variability.
+	In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
 
-	\subsubsection*{Indicator of purpose}
-	To quantify purpose $I_P$, we used Non-Provisioning purpose Shares (NPS) of water use as an indicator.
+	First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \\textit{Supporting Information}~\ref{secA1}):
+	\begin{equation}
+		A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
+	\end{equation}
+
+	Second, for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.\ for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
+	\begin{equation}
+		B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}}
+	\end{equation}
+
+	Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
+	\begin{gather}
+	C_i = C1_i * (1 - C2_i) \\
+	C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} \\
+	C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} \\
+	C2_{i} = 1, \ if RC >= R_{i, avg}
+	\end{gather}
+
+	Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate the $SFV$ index after normalizing them:
+	\begin{gather}
+		V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3}\\
+		a = \frac{1}{V_{\max} - V_{\min}};\\
+		b = \frac{1}{V_{\min} - V_{\max}} * V_{\min}\\
+		SFV = a * V + b
+	\end{gather}
+
+	\subsubsection{Indicator of purpose (IP)}
+	To quantify purpose $I_P$, we used provisioning purpose shares (PPS) of water use as an indicator.
 While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the NPS as:
+We calculated the PPS by:
 	\begin{equation}
-		NPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
+		PPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
 	\end{equation}
@@
 	\begin{equation}
-		I_A = CEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
+		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
 	\end{equation}
 
-	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
+	where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
 
 	\subsection{Change points detection}
-		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data~\cite{pettitt1979}.
+		We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
 		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
@@
 	\subsection{Datasets}
-In order to calculate IWGI in the YRB, all the datasets we need are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
+Multiple sources of data were used in this study, and we have attached a summarized data table as supplementary material and their processing are detailed described in the supplementary documentation.
  \section{Results}\label{sec2}
@@
 		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time.
-Red circles denote the reservoirs mainly for managing and regulating the whole basin.
+Dashed lines denote average of these percentages in different regimes.
+Red circles (Major Reservoirs) denote the reservoirs mainly for managing and regulating the whole basin.
 		The size of each circle indicates the magnitude of its water storage capacity.
-		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
+		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
@@
 
-Environmental context, social transformation, and policies played roles in all three periods.
+Environmental context, social atmosphere, and policies played roles in all three periods.
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
+Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
+Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
 During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
@@
 As tele-coupling raises additional water governance challenges in an increasingly tightly-connected world, regime shifts in water governance align with different human-water relationships~\cite{diaz2019}.
-The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition~\cite{loch2020,turton1999}.
+The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle~\cite{loch2020,turton1999}, and the IWGI quantitatively identifies this transition.
 It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime~\cite{reyers2018}.
 
-In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming command (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
-During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
-As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
-The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
+During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
+The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
 Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
-In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016a}.
+In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.
 
-The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
+The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
 The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
 As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
+These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
 Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.
@@
 The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
-Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
 Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
@@
 In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
-In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012a}.
+To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
+At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
+With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
+In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
 Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
 Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.
+
+Future's tightly intertwined socio-hydro interactions can lead water governance challenges even more complex and comprehensive, combining resources issues and structural barriers~\cite{huggins2022a}.
+For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
+Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (purpose and allocation) which is being increasingly altered by current regime transitions.
+It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
 
@@
 
-One of the main limitations in the approach is the lack of long-term data worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI more widely.
-However, we propose that all water governance issues result in changing ``who gets water, when and how'', so monitoring water stress, purposes of water services, and water allocation patterns do help.
-Choices of indicators for different aspects can be adapted according to available datasets; the connections between underlying components remain crucial in holistically understanding transitions in governance regimes.
-In today's world, regime shifts from biophysical to hydrosocial control of water dynamics seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
+One of the main limitations in the approach is the lack of multi-sources data in long-term period worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI widely.
+We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
+We suggest that choices of indicators for different aspects can be adopted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based purpose indicator (IP) by complicated one.
+Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.
+As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:summary}).
+Therefore, we suggest IWGI framework can be applied with adaptive indicators and flexible time series according to accessible datasets in future studies.
+
+In today's world, regime shifts from natural to human-dominated seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
 Although river basins have shown improvements in water management technologies and water use efficiency, many are still approaching local, regional, and planetary boundaries where human-water systems may collapse~\cite{gleeson2020, wang-erlandsson2022}.

### 2023-05-13 paper/response_letter/source/reviewer_1.tex
fix(paper): :bug: 修改审稿意见返修的对应行号

% chktex-file 1
% chktex-file 46
\section{Reviewer \#1}\label{reviewer_1}

\subsection*{Overall comments} % todo

\RC{} This study proposed an integrated index that incorporates water resources, water use, and water allocation to represent the water governance regime in the Yellow River basin. The authors showed an in-depth understanding of the water governance in this basin and made a great effort to represent the status of water governance straightforwardly with the integrated index. The figures were generally well-designed and presented clearly. But I feel the paper lacks details of the results which makes it difficult to understand the paper. Specific comments are listed below.

% 感谢您认可。
% 很抱歉缺少细节，可能会使您难以完全理解我们的研究。
% 为了回应您的担忧，我们已经修改了我们的稿件，并提供了更详细的结果解释。请在下面找到我们对您的具体评论的逐条回复。
\AR{} Thank you for your valuable feedback and for acknowledging our efforts in understanding the water governance in the Yellow River basin. We appreciate your comments regarding the clarity of the figures and our integrated index. Sorry about the lack of details in the results section may have made it difficult to fully comprehend our study. In response to your concerns, we have revised our manuscript and provided a more detailed explanation of the results. Please find our point-by-point response to your specific comments below.

\subsection{Major concern \#1}

% 气候变化在指数中没有明确的体现，这可能是本世纪黄河流量恢复的关键因素。气候变化将是未来该流域面临的巨大挑战。重大的气候变化可能影响流域的适应能力，因此需要不同的治理策略。
\RC{} Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。
% 在新增加的图表中，我增加了天然水量的图表展示这种变化
% 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（purpose）。
% 我们现在在讨论中涉及了这些话题。
\AR{} Thanks for the comment that we lacked a discussion of climate change, which has a multitude of impacts e.g., on precipitation and evaporation.
However, these effects are inherently captured within the Integrated Water Governance Index (IWGI) because the available water resources are affected by climate change as consequences.
For clarity, we first modified our expression of SFV-index, which is the indicator highly related to climate change (both in water yield and its fluctuation):

\begin{quote}[page=3, sline=78, eline=82]
	The impetus for developing this new index lies in the evolving practices of water governance driven by a blend of social and natural influences.
	Firstly, climate change impacts on current water yield, coupled with escalating demands from economic activities and the need for water storage development, intensify water stress~\cite{qin2019,wada2014,huang2021}.
\end{quote}

\begin{quote}[page=5, sline=144, eline=149]
	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
	% 这个指数得到了许多应用，是就我们已知范围内考虑因素最为齐全的，反应水资源压力的指数。
	The SFV-index, which has many applications, is the most comprehensive index of water stress we know.
\end{quote}

\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of supplementary material to demonstrate the changes in runoff. Trend of natural runoff can also be inferred from the measured runoff (Figure~\ref{fig:runoff} from b to d) and water use (Figure~\ref{fig:runoff} from e to g). We quote this figure when discussing climate context, now:

\begin{quote}[page=10, sline=274, eline=277]
	% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
\end{quote}

\AR*{} Finally, we further discussed the challenges brought by climate changes in the discussion section:

% 我们强调流域治理需要考虑这些因素，但我们可能很难穷尽优秀的流域治理策略需要考虑哪些因素。因此，IWGI至少让我们可以知道在诸多治理因素的共同影响下，流域的未来正在走向何方。
\begin{quote}[page=11, sline=306, eline=316]
	Future's tightly intertwined socio-hydro interactions can lead water governance challenges even more complex and comprehensive, combining resources issues and structural barriers~\cite{huggins2022a}.
	For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
	Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (purpose and allocation) which is being increasingly altered by current regime transitions.
	It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
\end{quote}

\subsection{Major concern \#2}
% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
\RC{} The results are summative. I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions. And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values. These details could help readers understand the reasonability of the results.

% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。
% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
% 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）。
\AR{} Thank you for pointing this out, and we apologize for the confusion caused by the overly conclusive manuscript. In the revised manuscript, we have summarized the indicators by graphs with description in supplementary material:in the supplementary material.

% TODO 这里记得写一下是哪几个附图
\AR*{} Figure~\ref{fig:purpose} to Figure~\ref{fig:scarcity} are three indicators changing trends. We added them into supplementary materials with descriptions:

\begin{quote}[page=Supplementary Materials]
	The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
	Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
	The upper and middle reaches (UR and MR) had the greatest impact on the IS changes. Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.

	In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).

	The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
\end{quote}

\AR*{} In addition, ranges of three indicators and meaning of their values are further explained in the methodology section of main text, now:

\begin{quote}[page=5, sline=137, eline=138]
	where $I'_x$ is calculated by Min-Max normalization of $I_x$ (thus ranges from zero to one):
	\begin{equation}
		I'_x = (I_x - I_{x, \min}) / (I_{x, \max} - I_{x, \min})
	\end{equation}
\end{quote}

\subsection{Major concern \#3}
% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
\RC{} The data used in this study seem to have different time periods, and most data are from before 2013. The hydrological regime and water governance in the Yellow River should have changed significantly in the recent decade. Therefore, incorporating the result from the recent decade would make this study more solid.

% 感谢审稿人的宝贵建议，但出于以下原因，我们无法在新的手稿中将研究时段后延至今
\AR{} Thanks for the reviewer's valuable advice, but for the following reasons, we are unable to postpone the study period to date in the main text. Instead, we added robustness test by using different-source data in supplementary material.

% 首先，本研究结论希望展现黄河水治理演变过程，尤其是重点关注1978到2001年之间的治理转型过程。尽管许多数据能在近二十年间计算IWGI，但代价是忽略了更远的时间段。而正如我们在新手稿的方法部分所补充说明的，使用不同的数据源容易造成时间不连续的问题（通常它们的统计口径是不一样的）。
\AR*{} Firstly, the conclusion of this study aims to show the evolution process of water governance of the Yellow River, especially focusing on the governance transformation between 1978 and 2001. Although many dataset allow IWGI to be calculated over the last two decades, the cost is to ignore the more important past periods. In addition, it's difficult to assimilate the different data sources because datasets usually have different statistical approach when categorizing water use sectors. Now, we added an explanation in the methods section of the new manuscript:

\begin{quote}[page=5, sline=138, eline=140]
	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
\end{quote}

\AR*{} Secondly, as the reviewer noticed, we used multiple-source dataset to implement our approach, which means time periods of a coherent analysis is limited by the shortest data. To cover study period from 1960s to 2000s, water use data developed by \citeA{zhou2020} is the most good quality and widely used dataset. The shortage, however, is not enough to cover the period after 2013. We contacted the original author team, but only confirmed that latest dataset is still unavailable. As some of the source data used to produce this crucial dataset could not be easily supplemented, this was not an effort that could be supplemented in this study. Therefore, we decided to keep the analysis discontinued in 2013 in main texts:

\begin{quote}[page=11, sline=323, eline=325]
	Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.
\end{quote}

\AR*{} Last, we tried our best to strengthen robustness of this study despite the above limitations. We calculated IWGI by using another data source for the past two decades. Since our results suggest no significant regime change, we think it is robust that the YRB experienced two significant water governance regime changes.

\begin{quote}[page=11, sline=325, eline=327]
	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:recent}).  % TODO 补充材料新图
\end{quote}

\subsection{Major concern \#4}
% 这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?
\RC{} There might be interactions/interconnections among the three indicators. Did the authors examine the relations between the indicators?

\AR{} Yes, we did examination for the interconnections between the three indicators. Sorry we didn't make the information accessible. Now, we added a table to describe this in the supplementary material (Table~\ref{tab:corr}).

\input{source/tab_corr.tex}

\begin{quote}[page=Supplementary Materials]
	By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.

	When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.\
	On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI.\ However, the correlations of other combinations are not statistically significant overall.

	The correlations between time periods are very different with the overall trend above.
	There is no significant correlation between any indicator combinations in the massive supply regime (P1).
	In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
	The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3). However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).
\end{quote}

\AR*{} In addition, note that strictly independent of indicators is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
% 这是因为，如果两个子指标在某时期内相关性显著，可能说明两者在该时期同时受到某些治理驱动因素的共同作用，这是可能发生的。
This is because a significant correlation between two indicators in a given period may indicate that both were simultaneously affected by some governance drivers during that period, which is possible.
% 但同样，若两个指标始终都存在较强的关联，则可能说明稳态转换并不显著，IWGI同时考虑三者的意义也存疑。
Similarly, if there is always a strong correlation between the two indicators, it may indicate that the steady-state transformation is not significant, and the significance of IWGI considering the three indicators at the same time is doubtful.
% 然而，正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。
However, as we have shown in Table~\ref{tab:corr}, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.

\subsection{Major concern \#5}
% IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。
\RC{} The IWGI includes reservoir storage information in the ``stress'' aspect. However, the water conveyance ability is not represented, which is also an important indicator of water governance/hydrosocial resilience.

% 短期的输水能力是衡量水治理/水社会复原力的重要指标
% 但年尺度上，变化不大
\AR{} We agree that conveyance is crucial to water governance/water society resilience, especially in the short term. However, the IWGI in this study focuses on annual time resolution. At this scale, conveyance has a less significant impact on water governance. From this point of view, there are two reasons that IWGI doesn't have to consider this in our study:

% 输水是水治理的手段，我们更侧重于这种治理的结果。
\AR*{} Firstly, water conveyance is more like an approach of water governance, and we focus more on the outcomes -i.e., how water stress is relieved by conveyance; how it help provision to specific sectors with higher purpose; how convert water changes allocation of water resources \dots

% 水治理很复杂，考虑到越来越多的要素会增加其复杂度。Scarcity是本研究使用最复杂的指标，因为这是一个经过检验的，可以有效表征的指数。如果经过检验影响不大，没有必要增加复杂度。
\AR*{} Secondly, water governance is comprehensive, and taking into account more and more elements increases its complexity. SFV-index is the most complex index used in this study, because it is a tested index that can be effectively represented. If not necessary, we prefer not to include more complexity.

% 我们检验过了年尺度的输水数据，基本变化不大
\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in supplementary material. According to the Yellow River Water Conservancy Commission (YRCC, data source), these reservoirs are mainly for managing and regulating the whole basin. The result (Figure~\ref{fig:conveyance}) shows that variability increased in the later regimes, supporting our main results that regulation plays a more significant role since the governance transforming regime (P2). We also appropriately modified the description in main text:

\begin{quote}[page=8, sline=223, eline=225]
	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supplementary Materials Figure~S7).  % todo 检查图引用
\end{quote}

\subsection{Major concern \#6}
% 我建议在标题中加上“黄河流域”。因为没有对IWGI的适用性和有效性进行测试或讨论。它能在其他盆地使用吗?使用索引的先决条件是什么?
\RC{} I would suggest adding ``Yellow River basin'' in the title. Because the applicability and validity of the IWGI were not tested or discussed. Can it be used in other basins? What is the prerequisite for using the index?

% 感谢你的提议，我们现在在标题中增加了黄河流域，新的标题是：
\AR{} Thanks to your proposal, we have now added the Yellow River Basin to the title, and the new title is: \textbf{``Identifying regime transitions for water governance: Take the Yellow River Basin in China as case''}

% 关于IWGI的泛用性，实际上我们曾在讨论中讨论了这一点。
% 非常抱歉先前的讨论似乎不够明确，我们在修改后的论文中重新澄清了这点。
\AR*{} Regarding the generality of IWGI, we actually discussed this in our discussion. I am very sorry that the previous discussion seems not clear enough, and we have clarified this point again in the revised manuscript.

\begin{quote}[page=11, sline=317, eline=323]
	One of the main limitations in the approach is the lack of multi-sources data in long-term period worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI widely.
	We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
	We suggest that choices of indicators for different aspects can be adapted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based purpose indicator (IP) by complicated one.
\end{quote}

% 此外，我们如今在方法部分提到了使用它的先决条件，使用同样数据源保证单一子指标的时间序列连贯性，而不同子指标可以采用不同的数据源。
\AR*{} In addition, we have now mentioned in the methods section:

\begin{quote}[page=5, sline=138, eline=142]
	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
	However, vary data sources can be used when estimating the specific indicator or cross different indicators, which makes IWGI a flexible framework for substituted indicators.
\end{quote}

\subsection{Major concern \#7}
% 最好在引言部分解释“水治理机制”的概念，然后解释使用综合指数IWGI代表水治理机制的必要性。
\RC{} It would be better to explain the concept ``water governance regime'' in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.

% 感谢你的建议，我们在引言部分为“水治理机制”提供了一个简短但明确的解释：
\AR{} Thanks for your advice, we nor provide a short but clear explanation of the ``water governance regime'' in the introduction:

\begin{quote}[page=3, sline=93, eline=98]
	A critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
	Regimes of water governance, the general guidelines of governing practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
\end{quote}

% 我们还为这种指数的必要性做出了补充：
\AR*{} We also add to the argument for the need for such an index:

\begin{quote}[page=2, sline=66, eline=77]
	Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
	On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
	On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
	Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
	Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
	As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
\end{quote}

\subsection{Detailed issues}

% 我没有在引用的文献中找到“用水的三个核心方面”。这三个方面是作者提出的吗?
\RC{} Line 57$-$62: I did not find the ``three core aspects of water use'' in the cited reference. Were the three aspects put forward by the authors?

% 非常非常感谢您指出这个错误，由于我们弄混了 citation key，这是一个无意间产生的引用错误。
\AR Thank you very, very much for pointing out this error. It was an accidental reference error due to our mix-up of the citation key.

% 总体来说，这是一个引用，但不是逐字逐句的引用，而是基于我们对\citeA{mariajacobson2013}报告的理解。报告在背景部分提出水治理的三个方面，我们将其总结为 stress, purpose, and allocation. 而 what, when, how 的说法则直接来自于该文献，这也是较为广泛的一种对 water governance 如何影响用水的定义。
\AR*{} Overall, this is a quote, but not a word-for-word quote, based on our understanding of a report UNDP participated~\cite{mariajacobson2013}. In the background part of the report, three aspects of water governance are put forward, and we summarize them in as ``stress, purpose, and allocation''. On the other hand, the expression of ``what, when and how'' are directly derived from this literature, which is also a relatively extensive definition of how water governance affects water use~\cite{lasswell2018,allan2001,mariajacobson2013}. Hence, we modified the sentence to:

\begin{quote}[page=2, sline=56, eline=60]
	In this context, the United Nations Development Programme (UNDP) suggests that water governance determines water usage across three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
\end{quote}

\RC{} Line 92: missing information for the citation?

% 谢谢您指出！再次为我们的粗心感到抱歉
\AR{} Thank you for pointing out! Sorry again for our carelessness. Citations were added in the revised manuscript, now:

\begin{quote}[page=3, sline=108, eline=110]
	Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.
\end{quote}

\RC{} Line 94$-$95: the sentence is unclear.

\AR{} Sorry about that, we modified that sentence to:

\begin{quote}[page=3, sline=110, eline=113]
	However, new challenges such as decreased streamflows and water depletions occurred in more recent times, followed by different water governance practices like water use regulation and water transfer across basins~\cite{wang2019c}.
\end{quote}

\RC{} Line 121: Repeated citation Qin et al. 2019.

\AR{} Fixed now.

\RC{} Line 122: It would be better to introduce the calculation of SFV in the main text.

\AR{} That's a good suggestion. We now moved the calculation from supplementary material to the main text.

% 为什么分子W uppro不是W Unon-pro?请核对一下方程式。
\RC{} Equation (6): Why is the numerator WUpro not WUnon-pro? Please check the equation.

\AR{} Thanks for reminding. We used provisioning purpose share in our analysis at last. We forgot to change it's name in texts. We fixed this mistake and everything is coherent now:

\begin{quote}[page=6, sline=157]
	To quantify purpose $I_P$, we used provisioning purpose shares (PPS) of water use as an indicator. While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses. We calculated the PPS by:
	\begin{equation}
		PPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
	\end{equation}
\end{quote}

\RC{} Equation (7): CEM => AEM?\

\AR{} Yep, a typo. We fixed such a stupid mistake now.

\RC{} Line 154: Please explain the source of irrigated area data.

AR{} We cannot dive into every detail of the multi-source datasets in texts, and this dataset is openly published and accessible. Overall, the irrigated area data were obtained by statistical approach in this dataset.

\AR*{} We now attached a new supplementary material which includes descriptions and all sources of the datasets used in this study. If you want to know more about the data, please check the data source through the provided information.

\RC{} Fig.2A, p<0.01 or p<0.001? (line 147 says that α=0.001 was used for the change-point detection).

\AR{} We used $0.001$ for generating the figure at last (fixed the typo in Fig.2A now). Anyway, as we showed in supplementary material Figure~S3, no difference in results because the change points are robust. % TODO 检查一下鲁棒性的图表

\RC{} Fig.2C:\ How were the directions determined?

\AR{} We draw the directions for visual convenience. Smaller graph is not for quantitatively illustrating. The arrow of directions are determined by time: point from earlier data to later data locations.

\RC{} Fig.3C:\ What do the dashed lines denote?

\AR{} Sorry about missing necessary description and we now add a sentence in caption of the Fig.3C:\ ``Dashed lines denote average of these percentages in different regimes''.

\RC{} Line 187: what is ``social transformation''?

\AR{} Sorry about the confused expression. I changed the term into ``Social atmosphere'' now. Maybe this is a better phrase.

\RC{} Line 208: the IWGI was proposed in this study, here the citations of Loch's and Turton's studies are not appropriate.

\AR{} The citations should be put at the first half of the sentence, and we fixed this problem now:

\begin{quote}[page=9, sline=238, eline=240]
	The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle~\cite{loch2020,turton1999}, and the IWGI quantitatively identifies this transition.
\end{quote}

\RC{} Line 273: adapted => adopted?

\AR{} Yep, another typo. We fixed that now.

\RC{} Line 275: biophysical? Please check the sentence.

\AR{} For more clarity, we now changed the sentence to:

\begin{quote}[page=11, sline=330, eline=333]
	In today's world, regime shifts from natural to human-dominated seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
\end{quote}

### 2023-05-13 paper/response_letter/source/reviewer_2.tex
fix(paper): :art: 修改图片1的大小
fix(paper): :bug: 修改审稿意见返修的对应行号

--- 2023-05-12 paper/response_letter/source/reviewer_2.tex
@@
 
-\AR{} Thanks for the comment. We now improved the figure in the revised manuscript. % TODO 修改图1让它更清楚
+\AR{} Thanks for the comment. We now improved the figure size in the revised manuscript.
 
@@
 To highlight the novelty of the IWGI that you have developed, perhaps you could add a review of other relevant indicators.
+
+\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:
+
+\begin{quote}[page=2, sline=60, eline=77]
+    Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
+    On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
+    For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
+    On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
+    Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
+    Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
+    As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
+\end{quote}
 
@@
 
-\begin{quote}
-    \begin{equation}
-		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
-	\end{equation}
+\begin{quote}[page=6, sline=163, eline=164]
+    To describe allocations $I_A$, we designed an indicator based on entropy, called Allocation Entropy Metric (AEM), which measures the degree of evenness in water allocation:
+    \[I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}\]
 \end{quote}
@@
 
-\begin{quote}
+\begin{quote}[page=6, sline=165, eline=166]
     where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
@@
 
-\begin{quote}
+\begin{quote}[page=6, sline=154, eline=156]
     In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
@@
 
-\begin{quote}
+\begin{quote}[page=7, sline=168, eline=170]
     We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
@@
 
-\begin{quote}
+\begin{quote}[page=Supplementary Materials]
     In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
@@
 
-\begin{quote}
-    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+\begin{quote}[page=10, sline=247, eline=250]
+    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~3~B).
 \end{quote}
 
-\begin{quote}
-    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
+\begin{quote}[page=10, sline=253, eline=255]
+    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~3), where increasing supply to meet demand was impractical~\cite{loch2020}.
 \end{quote}
 
-\begin{quote}
-    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
+\begin{quote}[page=10, sline=260, eline=261]
+    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~3~C).
 \end{quote}
 
-\begin{quote}
+\begin{quote}[page=10, sline=264, eline=268]
     As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes});
+These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~3);
 \end{quote}
@@
 
-\begin{quote}
+\begin{quote}[page=Supplementary Materials]
     Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
@@
 
-\begin{quote}
-    To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
-    At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
-    With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
+\begin{quote}[page=10, sline=289, eline=296]
+    To support water use in early stage (Figure~4~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
+    At the later stage (Figure~4~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
+    With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~4)~\cite{singh2019,porcher2019}.
 \end{quote}
@@
 
-\begin{quote}
+\begin{quote}[page=13, sline=346, eline=353]
     During the massive supply regime (P1: $1965 \sim 1978$), water governance tended to boost water supply by constructing reservoirs and channels in the YRB.\

### 2023-05-15 paper/main/02_methods.tex
refactor(paper): :memo: 顺一遍正文和补充材料

@@
 We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
-Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see \\textit{Supporting Information} Figure~S3).
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see Figure~\ref{SIfig:sensitivity}).
 
 	\subsection{Datasets}
-	% 本研究使用了多源数据，我们附上了一个数据表作为补充材料，并在补充文档中
-	% 为了计算 IWGI ，我们需要计算多个指标及子指标，所有使用的数据集都在表中列出，数据的详细介绍可见补充材料。
-	Multiple sources of data were used in this study, and we have attached a summarized data table as supplementary material and their processing are detailed described in the supplementary documentation.
+
+	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
+	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Supplementary Materials Figure~\ref{SIfig:reservoirs}).
+	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
+	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supplementary Materials Section~\ref{SIsecA1}).
+	The water resources use dataset was from National Long-term Water Use Dataset of China (NLWUD) published by \citeA{zhou2020}, which includes water uses, water-consuming economic variables, and water use intensities by sectors the prefectures level.
+	We determined the prefectures belong to the YRB by filtering the NLWUD dataset with a threshold of $95\%$ intersected area.
+
+	For analyzing its causes of changing water, irrigated area, gross added values of industry and services, and water use intensities data were also from NLWUD dataset~\cite{zhou2020}.
+	Besides, two water governance policies datasets are used: laws data and ``big events'' documents dataset.
+	Data of laws were collected from~\citeA{yellowriverwaterconservancycommission2010}, which reviewed all important laws at the basin scale related to the Yellow River from the last century.
+	The original documents of ``big events'' related to the Yellow River come from the YRCC, the agency at the basin scale, which recorded and compiled these events (\url{http://www.yrcc.gov.cn/hhyl/hhjs/}).
+
+	% We summarized the multiple-source dataset in Table~\ref{tab:datasets}.

### 2023-05-15 paper/main/manuscript.tex
refactor(paper): :recycle: 将LaTeX工作流打通
style(paper): :lipstick: 修正bib index，两端对齐
refactor(paper): :art: 更新正文所有图件
refactor(paper): :memo: 顺一遍正文和补充材料

@@
 %% To submit your paper:
-\documentclass[draft]{agujournal2019}
+\documentclass[draft]{../agujournal2019}
 \usepackage{url} %this package should fix any errors with URLs in refs.
 \usepackage{lineno}
-\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage[inline]{../trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
 \usepackage{soul}
 \usepackage{amsmath}
+\usepackage{pifont}  % 输入带圈数字，参考https://blog.csdn.net/tsingke/article/details/105961016
+\usepackage{xr-hyper}
+% 参考其它文件的标签 https://texfaq.org/FAQ-extref
+\externaldocument[SI]{../sup/supplementary_information}
 \linenumbers
@@
 \begin{document}
-
+\justify
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{keypoints}
-\item We developed an Integrated Water Governance Index (IWGI) to detect regime shifts in water governance.
-\item We interpret how water governance shifts within a rapidly-changing large river basin.
-\item We developed an approach to analyzing intertwines of water governance, hydrosocial transition, and human-water relationships.
+\item An Integrated Water Governance Index (IWGI) was devised to identify regime shifts in water governance practices.
+\item The study interprets the transformation of water governance within a rapidly evolving large river basin -the Yellow River Basin.
+\item A novel approach was developed to analyze the complex interconnections between water governance, hydrosocial transition, and human-water relationships.
 \end{keypoints}

### 2023-05-15 paper/sup/01_yrb.tex
refactor(paper): :memo: 顺一遍正文和补充材料

@@
-We divide the YRB into four regions to calculate the indicators considering both socio-economic and natural conditions.
-The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverconservancycommission2013,wang2019c,wang2016e}, so four important hydrological stations can distinguish the regions (see Figure~\ref{fig:YRB}).
+When calculating the indicators of IS and IA in this study (the SFV-index and the allocation entropy metric), we need consider data at a regional scale.
+The YRB can be divided into four regions to calculate the indicators considering both socio-economic and natural conditions.
+The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverwaterconservancycommission2010,wang2019c}.
 
@@
 
+Based on the above vary characteristics, we applied the division of the YRB:\ source region (SR), upper region (UR), middle region (MR), and lower region (LR).
+Four important hydrological stations can distinguish the regions (see Figure~\ref{fig:YRB}).
+
 % 补充图片1：研究区示意图
-\begin{figure*}[hbtp!]
+\begin{figure*}[!hbtp]
     \centering
@@
         The study area.
-        \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR: Source Region, UR: Upper Region, MR: Middle Region, DR: Downstream region).
-        \textbf{B.} Profile of the main channel of the Yellow River. The hydrological stations control the SR, UR, MR and DR.
-        \textbf{C.} Typical landscapes in different regions in the YRB.
+        \textbf{A.} Diagram of the YRB and the subdivision of the basin (SR:\ Source Region, UR:\ Upper Region, MR:\ Middle Region, DR:\ Downstream region).
+        \textbf{B.} Profile of the main channel of the Yellow River. The hydrological stations control the SR, UR, MR and DR.\
+        \textbf{C.} Typical landscapes in different regions in the YRB.\
     }\label{fig:YRB}

### 2023-05-15 paper/sup/02_indicator.tex
refactor(paper): :memo: 顺一遍正文和补充材料

--- 2022-04-29 paper/sup/02_indicator.tex
@@
-By taking water flexibility and variability into account, the scarcity-flexibility-variability (SFV) index focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses \cite{qin2019}.
-To apply this method, we need to combine three metrics following:
+% 构成稀缺情况的指标（SFV指数）在研究时段（包括三个不同时期）内呈现出先降低、然后迅速增加、最后再次略微降低的变化趋势（图~\ref{ch4:fig:scarcity}~A），表明水资源压力先减少再迅速增加，后趋于稳定。
+% 源区、上游、中游、下游这四个不同的区域中（图~\ref{ch4:fig:scarcity}~B），源区对三个时段的SFV指标变化几乎没有贡献，下游也仅在治理转变时期和适应增强时期呈现微弱的负向贡献。
+% 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
+The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
+Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
+The upper and middle reaches (UR and MR) had the greatest impact on the IS changes.
+Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
 
-First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Appendix}~\ref{secA1}):
-\begin{equation}
-    A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
-\end{equation}
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=\textwidth]{sup/priority.jpg}
+    \caption{Changing trend of the indicator of purpose}\label{fig:purpose}
+\end{figure}
 
-Second, for flexibility, $B_{i, j}$ is the inflexible water use $WU_{inflexible}$ (i.e.
-for thermal power plants or humans and livestock) as a proportion of average multi-year runoff, in year $i$ and region $j$:
-\begin{equation}
-    B_{i, j} = \frac{WU_{i, j, inflexible}}{R_{i, avg}}
-\end{equation}
+% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:purpose}~A）。
+% 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
+In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
+Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
 
-Finally for variability, the capacity of the reservoir and the positive effects of storage on natural runoff fluctuations are also considered.
-\begin{gather}
-C_i = C1_i * (1 - C2_i) \\
-C1_{i, j} = \frac{R_{i, std}}{R_{i, avg}} \\
-C2_{i} = \frac{RC_{i}}{R_{i, avg}}, \ if RC < R_{i, avg} \\
-C2_{i} = 1, \ if RC >= R_{i, avg}
-\end{gather}
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{sup/allocation.png}
+    \caption{Changing trend of the indicator of allocation}\label{fig:allocation}
+\end{figure}
 
-In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
+% 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
+The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
 
-Finally, assuming three metrics (scarcity, flexibility and variability) have the same weights, we can calculate the $SFV$ index after normalizing them:
-\begin{gather}
-    V = \frac{A_{normalize} + B_{normalize} + C_{normalize}}{3}\\
-    a = \frac{1}{V_{max} - V_{min}};\\
-    b = \frac{1}{V_{min} - V_{max}} * V_{min}\\
-    SFV = a * V + b
-\end{gather}
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=\textwidth]{sup/scarcity.png}
+    \caption{
+        \textbf{Left} Changing trend of the indicator of stress (IS).
+        \textbf{Right} contributions of different region to the IS's changes.
+    }\label{fig:scarcity}
+\end{figure}

### 2023-05-15 paper/sup/03_correlation.tex
refactor(paper): :memo: 顺一遍正文和补充材料

--- 2023-05-13 paper/response_letter/source/reviewer_1.tex
@@
-% chktex-file 1
 % chktex-file 46
-\section{Reviewer \#1}\label{reviewer_1}
 
-\subsection*{Overall comments} % todo
-
-\RC{} This study proposed an integrated index that incorporates water resources, water use, and water allocation to represent the water governance regime in the Yellow River basin.
-The authors showed an in-depth understanding of the water governance in this basin and made a great effort to represent the status of water governance straightforwardly with the integrated index.
-The figures were generally well-designed and presented clearly.
-But I feel the paper lacks details of the results which makes it difficult to understand the paper.
-Specific comments are listed below.
-
-% 感谢您认可。
-% 很抱歉缺少细节，可能会使您难以完全理解我们的研究。
-% 为了回应您的担忧，我们已经修改了我们的稿件，并提供了更详细的结果解释。请在下面找到我们对您的具体评论的逐条回复。
-\AR{} Thank you for your valuable feedback and for acknowledging our efforts in understanding the water governance in the Yellow River basin.
-We appreciate your comments regarding the clarity of the figures and our integrated index.
-Sorry about the lack of details in the results section may have made it difficult to fully comprehend our study.
-In response to your concerns, we have revised our manuscript and provided a more detailed explanation of the results.
-Please find our point-by-point response to your specific comments below.
-
-\subsection{Major concern \#1}
-
-% 气候变化在指数中没有明确的体现，这可能是本世纪黄河流量恢复的关键因素。气候变化将是未来该流域面临的巨大挑战。重大的气候变化可能影响流域的适应能力，因此需要不同的治理策略。
-\RC{} Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century.
-Climate change would be a great challenge in the basin in the future.
-Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.
-
-% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。
-% 在新增加的图表中，我增加了天然水量的图表展示这种变化
-% 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（purpose）。
-% 我们现在在讨论中涉及了这些话题。
-\AR{} Thanks for the comment that we lacked a discussion of climate change, which has a multitude of impacts e.g., on precipitation and evaporation.
-However, these effects are inherently captured within the Integrated Water Governance Index (IWGI) because the available water resources are affected by climate change as consequences.
-For clarity, we first modified our expression of SFV-index, which is the indicator highly related to climate change (both in water yield and its fluctuation):
-
-\begin{quote}[page=3, sline=78, eline=82]
-	The impetus for developing this new index lies in the evolving practices of water governance driven by a blend of social and natural influences.
-	Firstly, climate change impacts on current water yield, coupled with escalating demands from economic activities and the need for water storage development, intensify water stress~\cite{qin2019,wada2014,huang2021}.
-\end{quote}
-
-\begin{quote}[page=5, sline=144, eline=149]
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
-	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
-	% 这个指数得到了许多应用，是就我们已知范围内考虑因素最为齐全的，反应水资源压力的指数。
-	The SFV-index, which has many applications, is the most comprehensive index of water stress we know.
-\end{quote}
-
-\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of supplementary material to demonstrate the changes in runoff.
-Trend of natural runoff can also be inferred from the measured runoff (Figure~\ref{fig:runoff} from b to d) and water use (Figure~\ref{fig:runoff} from e to g).
-We quote this figure when discussing climate context, now:
-
-\begin{quote}[page=10, sline=274, eline=277]
-	% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
-	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
-\end{quote}
-
-\AR*{} Finally, we further discussed the challenges brought by climate changes in the discussion section:
-
-% 我们强调流域治理需要考虑这些因素，但我们可能很难穷尽优秀的流域治理策略需要考虑哪些因素。因此，IWGI至少让我们可以知道在诸多治理因素的共同影响下，流域的未来正在走向何方。
-\begin{quote}[page=11, sline=306, eline=316]
-	Future's tightly intertwined socio-hydro interactions can lead water governance challenges even more complex and comprehensive, combining resources issues and structural barriers~\cite{huggins2022a}.
-	For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
-	Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (purpose and allocation) which is being increasingly altered by current regime transitions.
-	It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
-\end{quote}
-
-\subsection{Major concern \#2}
-% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
-\RC{} The results are summative.
-I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions.
-And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values.
-These details could help readers understand the reasonability of the results.
-
-% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。
-% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
-% 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）。
-\AR{} Thank you for pointing this out, and we apologize for the confusion caused by the overly conclusive manuscript.
-In the revised manuscript, we have summarized the indicators by graphs with description in supplementary material:in the supplementary material.
-
-% TODO 这里记得写一下是哪几个附图
-\AR*{} Figure~\ref{fig:purpose} to Figure~\ref{fig:scarcity} are three indicators changing trends. We added them into supplementary materials with descriptions:
-
-\begin{quote}[page=Supplementary Materials]
-	The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
-	Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
-	The upper and middle reaches (UR and MR) had the greatest impact on the IS changes.
-Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
-
-	In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
-	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
-
-	The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
-\end{quote}
-
-\AR*{} In addition, ranges of three indicators and meaning of their values are further explained in the methodology section of main text, now:
-
-\begin{quote}[page=5, sline=137, eline=138]
-	where $I'_x$ is calculated by Min-Max normalization of $I_x$ (thus ranges from zero to one):
-	\begin{equation}
-		I'_x = (I_x - I_{x, \min}) / (I_{x, \max} - I_{x, \min})
-	\end{equation}
-\end{quote}
-
-\subsection{Major concern \#3}
-% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
-\RC{} The data used in this study seem to have different time periods, and most data are from before 2013.
-The hydrological regime and water governance in the Yellow River should have changed significantly in the recent decade.
-Therefore, incorporating the result from the recent decade would make this study more solid.
-
-% 感谢审稿人的宝贵建议，但出于以下原因，我们无法在新的手稿中将研究时段后延至今
-\AR{} Thanks for the reviewer's valuable advice, but for the following reasons, we are unable to postpone the study period to date in the main text.
-Instead, we added robustness test by using different-source data in supplementary material.
-
-% 首先，本研究结论希望展现黄河水治理演变过程，尤其是重点关注1978到2001年之间的治理转型过程。尽管许多数据能在近二十年间计算IWGI，但代价是忽略了更远的时间段。而正如我们在新手稿的方法部分所补充说明的，使用不同的数据源容易造成时间不连续的问题（通常它们的统计口径是不一样的）。
-\AR*{} Firstly, the conclusion of this study aims to show the evolution process of water governance of the Yellow River, especially focusing on the governance transformation between 1978 and 2001.
-Although many dataset allow IWGI to be calculated over the last two decades, the cost is to ignore the more important past periods.
-In addition, it's difficult to assimilate the different data sources because datasets usually have different statistical approach when categorizing water use sectors.
-Now, we added an explanation in the methods section of the new manuscript:
-
-\begin{quote}[page=5, sline=138, eline=140]
-	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
-\end{quote}
-
-\AR*{} Secondly, as the reviewer noticed, we used multiple-source dataset to implement our approach, which means time periods of a coherent analysis is limited by the shortest data.
-To cover study period from 1960s to 2000s, water use data developed by \citeA{zhou2020} is the most good quality and widely used dataset.
-The shortage, however, is not enough to cover the period after 2013.
-We contacted the original author team, but only confirmed that latest dataset is still unavailable.
-As some of the source data used to produce this crucial dataset could not be easily supplemented, this was not an effort that could be supplemented in this study.
-Therefore, we decided to keep the analysis discontinued in 2013 in main texts:
-
-\begin{quote}[page=11, sline=323, eline=325]
-	Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.
-\end{quote}
-
-\AR*{} Last, we tried our best to strengthen robustness of this study despite the above limitations.
-We calculated IWGI by using another data source for the past two decades.
-Since our results suggest no significant regime change, we think it is robust that the YRB experienced two significant water governance regime changes.
-
-\begin{quote}[page=11, sline=325, eline=327]
-	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:recent}).
-% TODO 补充材料新图
-\end{quote}
-
-\subsection{Major concern \#4}
-% 这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?
-\RC{} There might be interactions/interconnections among the three indicators. Did the authors examine the relations between the indicators?
-
-\AR{} Yes, we did examination for the interconnections between the three indicators.
-Sorry we didn't make the information accessible.
-Now, we added a table to describe this in the supplementary material (Table~\ref{tab:corr}).
-
-\input{source/tab_corr.tex}
-
-\begin{quote}[page=Supplementary Materials]
 By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
@@
 However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).
-\end{quote}
 
-\AR*{} In addition, note that strictly independent of indicators is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
-% 这是因为，如果两个子指标在某时期内相关性显著，可能说明两者在该时期同时受到某些治理驱动因素的共同作用，这是可能发生的。
-This is because a significant correlation between two indicators in a given period may indicate that both were simultaneously affected by some governance drivers during that period, which is possible.
-% 但同样，若两个指标始终都存在较强的关联，则可能说明稳态转换并不显著，IWGI同时考虑三者的意义也存疑。
-Similarly, if there is always a strong correlation between the two indicators, it may indicate that the steady-state transformation is not significant, and the significance of IWGI considering the three indicators at the same time is doubtful.
-% 然而，正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。
-However, as we have shown in Table~\ref{tab:corr}, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.
-
-\subsection{Major concern \#5}
-% IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。
-\RC{} The IWGI includes reservoir storage information in the ``stress'' aspect.
-However, the water conveyance ability is not represented, which is also an important indicator of water governance/hydrosocial resilience.
-
-% 短期的输水能力是衡量水治理/水社会复原力的重要指标
-% 但年尺度上，变化不大
-\AR{} We agree that conveyance is crucial to water governance/water society resilience, especially in the short term.
-However, the IWGI in this study focuses on annual time resolution.
-At this scale, conveyance has a less significant impact on water governance.
-From this point of view, there are two reasons that IWGI doesn't have to consider this in our study:
-
-% 输水是水治理的手段，我们更侧重于这种治理的结果。
-\AR*{} Firstly, water conveyance is more like an approach of water governance, and we focus more on the outcomes -i.e., how water stress is relieved by conveyance; how it help provision to specific sectors with higher purpose; how convert water changes allocation of water resources \dots
-
-% 水治理很复杂，考虑到越来越多的要素会增加其复杂度。Scarcity是本研究使用最复杂的指标，因为这是一个经过检验的，可以有效表征的指数。如果经过检验影响不大，没有必要增加复杂度。
-\AR*{} Secondly, water governance is comprehensive, and taking into account more and more elements increases its complexity.
-SFV-index is the most complex index used in this study, because it is a tested index that can be effectively represented.
-If not necessary, we prefer not to include more complexity.
-
-% 我们检验过了年尺度的输水数据，基本变化不大
-\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in supplementary material.
-According to the Yellow River Water Conservancy Commission (YRCC, data source), these reservoirs are mainly for managing and regulating the whole basin.
-The result (Figure~\ref{fig:conveyance}) shows that variability increased in the later regimes, supporting our main results that regulation plays a more significant role since the governance transforming regime (P2).
-We also appropriately modified the description in main text:
-
-\begin{quote}[page=8, sline=223, eline=225]
-	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
-% todo 检查图引用
-\end{quote}
-
-\subsection{Major concern \#6}
-% 我建议在标题中加上“黄河流域”。因为没有对IWGI的适用性和有效性进行测试或讨论。它能在其他盆地使用吗?使用索引的先决条件是什么?
-\RC{} I would suggest adding ``Yellow River basin'' in the title.
-Because the applicability and validity of the IWGI were not tested or discussed.
-Can it be used in other basins?
-What is the prerequisite for using the index?
-
-% 感谢你的提议，我们现在在标题中增加了黄河流域，新的标题是：
-\AR{} Thanks to your proposal, we have now added the Yellow River Basin to the title, and the new title is: \textbf{``Identifying regime transitions for water governance: Take the Yellow River Basin in China as case''}
-
-% 关于IWGI的泛用性，实际上我们曾在讨论中讨论了这一点。
-% 非常抱歉先前的讨论似乎不够明确，我们在修改后的论文中重新澄清了这点。
-\AR*{} Regarding the generality of IWGI, we actually discussed this in our discussion.
-I am very sorry that the previous discussion seems not clear enough, and we have clarified this point again in the revised manuscript.
-
-\begin{quote}[page=11, sline=317, eline=323]
-	One of the main limitations in the approach is the lack of multi-sources data in long-term period worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI widely.
-	We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
-	We suggest that choices of indicators for different aspects can be adapted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based purpose indicator (IP) by complicated one.
-\end{quote}
-
-% 此外，我们如今在方法部分提到了使用它的先决条件，使用同样数据源保证单一子指标的时间序列连贯性，而不同子指标可以采用不同的数据源。
-\AR*{} In addition, we have now mentioned in the methods section:
-
-\begin{quote}[page=5, sline=138, eline=142]
-	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
-	However, vary data sources can be used when estimating the specific indicator or cross different indicators, which makes IWGI a flexible framework for substituted indicators.
-\end{quote}
-
-\subsection{Major concern \#7}
-% 最好在引言部分解释“水治理机制”的概念，然后解释使用综合指数IWGI代表水治理机制的必要性。
-\RC{} It would be better to explain the concept ``water governance regime'' in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.
-
-% 感谢你的建议，我们在引言部分为“水治理机制”提供了一个简短但明确的解释：
-\AR{} Thanks for your advice, we nor provide a short but clear explanation of the ``water governance regime'' in the introduction:
-
-\begin{quote}[page=3, sline=93, eline=98]
-	A critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
-	Regimes of water governance, the general guidelines of governing practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
-\end{quote}
-
-% 我们还为这种指数的必要性做出了补充：
-\AR*{} We also add to the argument for the need for such an index:
-
-\begin{quote}[page=2, sline=66, eline=77]
-	Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
-	On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
-	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
-	On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
-	Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
-	Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
-	As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
-\end{quote}
-
-\subsection{Detailed issues}
-
-% 我没有在引用的文献中找到“用水的三个核心方面”。这三个方面是作者提出的吗?
-\RC{} Line 57$-$62: I did not find the ``three core aspects of water use'' in the cited reference. Were the three aspects put forward by the authors?
-
-% 非常非常感谢您指出这个错误，由于我们弄混了 citation key，这是一个无意间产生的引用错误。
-\AR Thank you very, very much for pointing out this error. It was an accidental reference error due to our mix-up of the citation key.
-
-% 总体来说，这是一个引用，但不是逐字逐句的引用，而是基于我们对\citeA{mariajacobson2013}报告的理解。报告在背景部分提出水治理的三个方面，我们将其总结为 stress, purpose, and allocation. 而 what, when, how 的说法则直接来自于该文献，这也是较为广泛的一种对 water governance 如何影响用水的定义。
-\AR*{} Overall, this is a quote, but not a word-for-word quote, based on our understanding of a report UNDP participated~\cite{mariajacobson2013}.
-In the background part of the report, three aspects of water governance are put forward, and we summarize them in as ``stress, purpose, and allocation''.
-On the other hand, the expression of ``what, when and how'' are directly derived from this literature, which is also a relatively extensive definition of how water governance affects water use~\cite{lasswell2018,allan2001,mariajacobson2013}.
-Hence, we modified the sentence to:
-
-\begin{quote}[page=2, sline=56, eline=60]
-	In this context, the United Nations Development Programme (UNDP) suggests that water governance determines water usage across three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
-\end{quote}
-
-\RC{} Line 92: missing information for the citation?
-
-% 谢谢您指出！再次为我们的粗心感到抱歉
-\AR{} Thank you for pointing out! Sorry again for our carelessness. Citations were added in the revised manuscript, now:
-
-\begin{quote}[page=3, sline=108, eline=110]
-	Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.
-\end{quote}
-
-\RC{} Line 94$-$95: the sentence is unclear.
-
-\AR{} Sorry about that, we modified that sentence to:
-
-\begin{quote}[page=3, sline=110, eline=113]
-	However, new challenges such as decreased streamflows and water depletions occurred in more recent times, followed by different water governance practices like water use regulation and water transfer across basins~\cite{wang2019c}.
-\end{quote}
-
-\RC{} Line 121: Repeated citation Qin et al. 2019.
-
-\AR{} Fixed now.
-
-\RC{} Line 122: It would be better to introduce the calculation of SFV in the main text.
-
-\AR{} That's a good suggestion. We now moved the calculation from supplementary material to the main text.
-
-% 为什么分子W uppro不是W Unon-pro?请核对一下方程式。
-\RC{} Equation (6): Why is the numerator WUpro not WUnon-pro? Please check the equation.
-
-\AR{} Thanks for reminding. We used provisioning purpose share in our analysis at last. We forgot to change it's name in texts. We fixed this mistake and everything is coherent now:
-
-\begin{quote}[page=6, sline=157]
-	To quantify purpose $I_P$, we used provisioning purpose shares (PPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the PPS by:
-	\begin{equation}
-		PPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
-	\end{equation}
-\end{quote}
-
-\RC{} Equation (7): CEM => AEM?\
-
-\AR{} Yep, a typo. We fixed such a stupid mistake now.
-
-\RC{} Line 154: Please explain the source of irrigated area data.
-
-AR{} We cannot dive into every detail of the multi-source datasets in texts, and this dataset is openly published and accessible.
-Overall, the irrigated area data were obtained by statistical approach in this dataset.
-
-\AR*{} We now attached a new supplementary material which includes descriptions and all sources of the datasets used in this study.
-If you want to know more about the data, please check the data source through the provided information.
-
-\RC{} Fig.2A, p<0.01 or p<0.001? (line 147 says that α=0.001 was used for the change-point detection).
-
-\AR{} We used $0.001$ for generating the figure at last (fixed the typo in Fig.2A now).
-Anyway, as we showed in supplementary material Figure~S3, no difference in results because the change points are robust.
-% TODO 检查一下鲁棒性的图表
-
-\RC{} Fig.2C:\ How were the directions determined?
-
-\AR{} We draw the directions for visual convenience.
-Smaller graph is not for quantitatively illustrating.
-The arrow of directions are determined by time: point from earlier data to later data locations.
-
-\RC{} Fig.3C:\ What do the dashed lines denote?
-
-\AR{} Sorry about missing necessary description and we now add a sentence in caption of the Fig.3C:\ ``Dashed lines denote average of these percentages in different regimes''.
-
-\RC{} Line 187: what is ``social transformation''?
-
-\AR{} Sorry about the confused expression. I changed the term into ``Social atmosphere'' now. Maybe this is a better phrase.
-
-\RC{} Line 208: the IWGI was proposed in this study, here the citations of Loch's and Turton's studies are not appropriate.
-
-\AR{} The citations should be put at the first half of the sentence, and we fixed this problem now:
-
-\begin{quote}[page=9, sline=238, eline=240]
-	The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle~\cite{loch2020,turton1999}, and the IWGI quantitatively identifies this transition.
-\end{quote}
-
-\RC{} Line 273: adapted => adopted?
-
-\AR{} Yep, another typo. We fixed that now.
-
-\RC{} Line 275: biophysical? Please check the sentence.
-
-\AR{} For more clarity, we now changed the sentence to:
-
-\begin{quote}[page=11, sline=330, eline=333]
-	In today's world, regime shifts from natural to human-dominated seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
-\end{quote}
+\input{tab_corr.tex}

### 2023-05-15 paper/sup/03_datasets.tex
refactor(paper): :memo: 顺一遍正文和补充材料

--- 2022-11-04 paper/sup/03_datasets.tex
@@
+% chktex-file 46
 \subsection*{Descriptions}
@@
 
-\subsubsection*{Statistical datasets}
-% We used GDP data; water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhou2020} and statistical yearbooks \url{http://www.yrcc.gov.cn/other/hhgb/}.
-The water resources use dataset was published by Zhou et al.
-\cite{zhou2020}, which records water utilization in different sectors along with social-economic situations at the Prefectures level.
-2nd National Water Resources Assessment Program mainly extracted this dataset launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details).
-Since then, the statistics from the survey using the same criteria have been supplemented and harmonized with the 2013 administrative divisions.
-
-The data covers a total of subcategories of water use under four broad categories: agriculture (IRR), industry (IND), urban (URB) and rural (RUR) water use (see Zhou et al., for details \cite{zhou2020}).
-% There is uncertainty at the county scale for each disaggregated water use sector, but because the corrected data has been for statistical information using the water balance method, the data are adequate for the regional scale used in this study.
-
-\subsubsection*{Hydrological datasets}
-The reservoir dataset was collected by Wang et al.
-\cite{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Figure~\ref{fig:reservoirs}).
-YRCC labelled the regulation-oriented reservoirs among them, see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
-In addition, annual runoff data derived from hydrological station measurements are the same as the datasets used in \cite{wang2019c} and \cite{wang2016e}.
-
-\subsubsection*{Political datasets}
-The policy dataset collects laws and policies listed in the book \cite{yellowriverconservancycommission2013}, which are related to the Yellow River basin promulgated and implemented by departments at (such as YRCC) and above (such as national institutions) at the Basin's level (Table~\ref{tab:policies}).
-In addition, some are difficult to categorize; not a landmark, but numerous water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC; we collected them from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
-
-\subsection*{Methods S3. Harmonization}
+\subsection*{Data Harmonization}
 Due to the wide sources of our data set and the different spatial scales, we need to harmonize them into a practical scale.
@@
         \begin{equation}
-            S_{ij} = MAX(S_ij / S_i)
+            S_{ij} = MAX(S_{ij} / S_i)
         \end{equation}
@@
 
-Finally, when we process the location data (i.e., the location data of the reservoirs), we judge the province it belongs to according to its location and then fit it to the regional scale.
+% Finally, when we process the location data (i.e., the location data of the reservoirs), we judge the province it belongs to according to its location and then fit it to the regional scale.
 

### 2023-05-15 paper/sup/04_robustness.tex
refactor(paper): :memo: 顺一遍正文和补充材料

--- 2023-05-12 paper/sup/supplementary_information.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
-% Modified December 2018
-%
-% This template includes commands and instructions
-% given in the order necessary to produce a final output that will
-% satisfy AGU requirements.
-%
-% FOR FIGURES, DO NOT USE \psfrag
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% IMPORTANT NOTE:
-%
-% SUPPORTING INFORMATION DOCUMENTATION IS NOT COPYEDITED BEFORE PUBLICATION.
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Step 1: Set the \documentclass
-%
-%
-% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
-% The draft option produces double spaced output.
-%
-% Choose the journal abbreviation for the journal you are
-% submitting to:
-
-% jgrga JOURNAL OF GEOPHYSICAL RESEARCH (use for all of them)
-% gbc   GLOBAL BIOCHEMICAL CYCLES
-% grl   GEOPHYSICAL RESEARCH LETTERS
-% pal   PALEOCEANOGRAPHY
-% ras   RADIO SCIENCE
-% rog   REVIEWS OF GEOPHYSICS
-% tec   TECTONICS
-% wrr   WATER RESOURCES RESEARCH
-% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
-% sw    SPACE WEATHER
-% ms    JAMES
-% ef    EARTH'S FUTURE
-%
-%
-%
-% (If you are submitting to a journal other than jgrga,
-% substitute the initials of the journal for "jgrga" below.)
-
-\documentclass[draft,wrr]{../agutexSI2019}
-\usepackage{amsmath}
-% For using tabularx
-\usepackage{tabularx}
-\usepackage{booktabs}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  SUPPORTING INFORMATION TEMPLATE
-%
-%% ------------------------------------------------------------------------ %%
-%
-%
-%Please use this template when formatting and submitting your Supporting Information.
-
-%This template serves as both a “table of contents” for the supporting information for your article and as a summary of files.
-%
-%
-%OVERVIEW
-%
-%Please note that all supporting information will be peer reviewed with your manuscript. It will not be copyedited if the paper is accepted.
-%In general, the purpose of the supporting information is to enable authors to provide and archive auxiliary information such as data tables, method information, figures, video, or computer software, in digital formats so that other scientists can use it.
-%The key criteria are that the data:
-% 1. supplement the main scientific conclusions of the paper but are not essential to the conclusions (with the exception of
-%    including %data so the experiment can be reproducible);
-% 2. are likely to be usable or used by other scientists working in the field;
-% 3. are described with sufficient precision that other scientists can understand them, and
-% 4. are not exe files.
-%
-%USING THIS TEMPLATE
-%
-%***All references should be included in the reference list of the main paper so that they can be indexed, linked, and counted as citations.  The reference section does not count toward length limits.
-%
-%All Supporting text and figures should be included in this document.
-Insert supporting information content into each appropriate section of the template.
-To add additional captions, simply copy and paste each sample as needed.
-
-%Tables may be included, but can also be uploaded separately, especially if they are larger than 1 page, or if necessary for retaining table formatting.
-Data sets, large tables, movie files, and audio files should be uploaded separately.
-Include their captions in this document and list the file name with the caption.
-You will be prompted to upload these files on the Upload Files tab during the submission process, using file type “Supporting Information (SI)”
-
-%IMPORTANT NOTE ON FIGURES AND TABLES
-% Placeholders for figures and tables appear after the \end{article} command, after references.
-% DO NOT USE \psfrag or \subfigure commands.
-%
- \usepackage{graphicx}
-%
-%  Uncomment the following command to allow illustrations to print
-%   when using Draft:
-\setkeys{Gin}{draft=true}
-%
-% You may need to use one of these options for graphicx depending on the driver program you are using.
-%
-% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
-% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
-% [oztex], [textures]
-%
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  ENTER PREAMBLE
-%
-%% ------------------------------------------------------------------------ %%
-
-% Author names in capital letters:
-%\authorrunninghead{BALES ET AL.}
-
-% Shorter version of title entered in capital letters:
-%\titlerunninghead{SHORT TITLE}
-
-%Corresponding author mailing address and e-mail address:
-%\authoraddr{Corresponding author: A. B. Smith,
-%Department of Hydrology and Water Resources, University of
-%Arizona, Harshbarger Building 11, Tucson, AZ 85721, USA.
-%(a.b.smith@hwr.arizona.edu)}
-
-\begin{document}
-\noindent\textbf{\large{Supplementary Information for}}
-
-\input{../metadata.tex}
-\begin{article}
-
-\noindent\textbf{Contents of this file}
-%%%Remove or add items as needed%%%
-\begin{enumerate}
-\item Text S1 to S3
-\item Figures S1 to S3
-\item Tables S1 to S2
-%if Tables are larger than 1 page, upload as separate excel file
-\end{enumerate}
-
-\noindent\textbf{Introduction}
-%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
-% 1. a general overview of the kind of data files;
-% 2. information about when and how the data were collected or created;
-% 3. a general description of processing steps used;
-% 4. any known imperfections or anomalies in the data.
-When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
-Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.
-The formulation in detail for applying the SFV-index is available in the~\ref{secA2}.
-We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonies them for analysis.
-
-\noindent\textbf{YRB Regions}\label{secA1}
-\input{01_yrb.tex}
-
-\noindent\textbf{SFV-index}\label{secA2}
-\input{02_indicator.tex}
+% 为了增强本研究的鲁棒性，我们在不同的显著性水平下检验了突变点的识别结果，发现在0.0005到0.05的置信度水平下，都只能识别出本研究发现的两个突变点（1978与2001）。
+In order to enhance the robustness of this study, we tested the identification results of mutation points at different significance levels.
+Our results that only two mutation points (1978 and 2001) could be identified at the confidence level of $0.0005$ to $0.05$ (Figure~\ref{fig:sensitivity}).
+% 此外，我们讨论了在指标中没有体现的水库流量变化，在所有水库（图 x）中，我们分析了10个先后建成的枢纽水库，发现水库在 governance transforming regime 之后开始增强其调度的水平
+In addition, we analyzed the changes of reservoir flow that are not reflected in the IWGI.\ Among all the reservoirs (Figure~\ref{fig:reservoirs}), we focused on $9$ major reservoirs built successively and find that the reservoirs began to enhance their variability after the governance transforming regime, suggesting a higher level of regulating (Figure~\ref{fig:conveyance}).
 
@@
 
-% 构成稀缺情况的指标（SFV指数）在研究时段（包括三个不同时期）内呈现出先降低、然后迅速增加、最后再次略微降低的变化趋势（图~\ref{ch4:fig:scarcity}~A），表明水资源压力先减少再迅速增加，后趋于稳定。
-% 源区、上游、中游、下游这四个不同的区域中（图~\ref{ch4:fig:scarcity}~B），源区对三个时段的SFV指标变化几乎没有贡献，下游也仅在治理转变时期和适应增强时期呈现微弱的负向贡献。
-% 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
-The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
-Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
-The upper and middle reaches (UR and MR) had the greatest impact on the IS changes.
-Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
-
-% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:purpose}~A）。
-% 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
-In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
-Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
-
-% 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
-The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{sup/purpose.jpg}
-\caption{Changing trend of the indicator of purpose}\label{fig:purpose}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{sup/allocation.png}
-\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{sup/scarcity.png}
-\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
-\end{figure}
-
-By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
-
-When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.
-On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI.
-However, the correlations of other combinations are not statistically significant overall.
-
-The correlations between time periods are very different with the overall trend above.
-There is no significant correlation between any indicator combinations in the massive supply regime (P1).
-In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
-The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3).
-However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).
-
-\input{../response_letter/source/tab_corr.tex}
-
 \begin{figure}[htb]
@@
 \end{figure}
-
-\noindent\textbf{Datasets}\label{secA3}
-\input{03_datasets.tex}
-
-%%Enter Data Set, Movie, and Audio captions here
-%%EXAMPLE CAPTIONS
-
-% \noindent\textbf{Data Set S1.} %Type or paste caption here.
-%upload your dataset(s) to AGU's journal submission site and select "Supporting Information (SI)" as the file type. Following naming %convention: ds01.
-
-%Repeat for any additional Supporting data sets
-
-% \noindent\textbf{Movie S1.} %Type or paste caption here.
-%upload your movie(s) to AGU's journal submission site and select, "Supporting Information %(SI)" as the file type. Following naming convention: ms01.
-
-%Repeat any additional Supporting movies
-
-% \noindent\textbf{Audio S1.} %Type or paste caption here.
-%upload your audio file(s) to AGU's journal submission site and select "Supporting Information %(SI)" as the file type. Following naming convention: auds01.
-
-%Repeat for any additional Supporting audio files
-
-%%% End of body of article:
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Optional Notation section goes here
-%
-% Notation -- End each entry with a period.
-% \begin{notation}
-% Term & definition.\\
-% Second term & second definition.\\
-% \end{notation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% ------------------------------------------------------------------------ %%
-%%  REFERENCE LIST AND TEXT CITATIONS
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\bibliography{../mybibtex.bib}
-\end{article}
-\clearpage
-\end{document}

### 2023-05-15 paper/sup/supplementary_information.tex
fix(paper): :bug: 修改审稿意见返修的对应行号
refactor(paper): :memo: 顺一遍正文和补充材料

--- 2023-05-10 paper/sup/supplementary_information.tex
@@
 \item Text S1 to S3
-\item Figures S1 to S3
-\item Tables S1 to S2
+\item Figures S1 to Figure~\ref{fig:conveyance}
 %if Tables are larger than 1 page, upload as separate excel file
@@
 % 4. any known imperfections or anomalies in the data.
-When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale.
-Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.
-The formulation in detail for applying the SFV-index is available in the~\ref{secA2}.
-We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonies them for analysis.
+Section~\ref{secA1} provides a brief introduction to four regions (Source Region, Upper Region, Middle Region, and Lower Region -SR, UR, MR, and LR) of the YRB.\
+Section~\ref{secA2} detailed explains the changing trend of three indicators.
+Section~\ref{secA3} describes the correlations between the three indicators and
+Section~\ref{secA4} provides some sensitivity analysis for testing robustness.
+
+% Based on vary characteristics, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.
 
@@
 
-\noindent\textbf{SFV-index}\label{secA2}
+\noindent\textbf{Trend of Indicators}\label{secA2}
 \input{02_indicator.tex}
 
-\begin{figure}[tb]
-\centering
-\includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
-\caption{
-      Numbers of new reservoirs in each year.
-}\label{fig:reservoirs}
-\end{figure}
+\noindent\textbf{Correlation of Indicators}\label{secA3}
+\input{03_correlation.tex}
 
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{sup/sensitivity.pdf}
-\caption{
-      Sensitivity analysis of the threshold of p-values.
-      \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
-      \textbf{B.} Threshold of p-values \(\alpha=0.0005\).
-      \textbf{C.} Threshold of p-values \(\alpha=0.05\).
-}\label{fig:sensitivity}
-\end{figure}
+\noindent\textbf{Robustness}\label{secA4}
+\input{04_robustness.tex}
 
-% 构成稀缺情况的指标（SFV指数）在研究时段（包括三个不同时期）内呈现出先降低、然后迅速增加、最后再次略微降低的变化趋势（图~\ref{ch4:fig:scarcity}~A），表明水资源压力先减少再迅速增加，后趋于稳定。
-% 源区、上游、中游、下游这四个不同的区域中（图~\ref{ch4:fig:scarcity}~B），源区对三个时段的SFV指标变化几乎没有贡献，下游也仅在治理转变时期和适应增强时期呈现微弱的负向贡献。
-% 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
-The index of scarcity (SFV index) in the study period (including three different periods) showed A change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
-In the four different regions (Figure~\ref{fig:scarcity}~B), the source region has almost no contribution to SFV index changes in the three periods, and the downstream region only has a weak negative contribution in the governance transition period and the adaptation enhancement period.
-The upper and middle reaches of the Yellow River had the greatest impact on the scarcity.
-The upper reaches made the greatest contribution to SFV change in the period of centralized water supply and governance change, while the middle reaches made the greatest contribution in the period of adaptation enhancement.
-
-% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:priority}~A）。
-% 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
-In terms of water use purpose, the proportion of supply water remained basically unchanged in the period of centralized water supply, but showed A rapid decline in the period of governance transformation and adaptation enhancement (Figure~\ref{fig:priority}~A).
-In the three periods, the change of irrigation water dominated the change of the proportion, while urban and rural water for human settlements and rural livestock had almost no influence on the change of the proportion (Figure~\ref{fig:allocation}~B).
-
-% 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
-The index change of distribution mode showed an obvious ``V-shaped'' trend, indicating that water resources in the source region, upper, middle and lower reaches of the Yellow River first gradually moved away from uniform distribution, and then gradually tended to average distribution after 2000 (Figure~\ref{fig:allocation}).
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{sup/priority.jpg}
-\caption{Changing trend of the indicator of priority}\label{fig:priority}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{sup/allocation.png}
-\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{sup/scarcity.png}
-\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
-\end{figure}
-
-By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), priority (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
-
-When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.
-On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI.
-However, the correlations of other combinations are not statistically significant overall.
-
-The correlations between time periods are very different with the overall trend above.
-There is no significant correlation between any indicator combinations in the massive supply regime (P1).
-In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
-The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3).
-However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).
-
-\input{../response_letter/source/tab_corr.tex}
-
-\noindent\textbf{Datasets}\label{secA3}
-\input{03_datasets.tex}
+% \noindent\textbf{Datasets}\label{secA3}
+% \input{03_datasets.tex}
 

### 2023-05-15 paper/diff/draft.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
-For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
+For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2022a}.
 On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
@@
 	\subsection{Datasets}
-Multiple sources of data were used in this study, and we have attached a summarized data table as supplementary material and their processing are detailed described in the supplementary documentation.
+Multiple sources of data were used in this study, and we have attached a summarized data table as Supporting Information and their processing are detailed described in the supplementary documentation.
  \section{Results}\label{sec2}
@@
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
+Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S7).
 Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
@@
 The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
-Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
 Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.

### 2023-05-15 paper/main/02_methods.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 
-	Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).
+	Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information Section~S1}).
 	For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
@@
 
-	First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \\textit{Supporting Information}~\ref{secA1}):
+	First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Supporting Information Section S1}):
 	\begin{equation}
@@
 We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
-Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see Figure~\ref{SIfig:sensitivity}).
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see Figure~S6).
 
-	\subsection{Datasets}
+	\subsection{Datasets}\label{sec:datasets}
 
 	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
-	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Supplementary Materials Figure~\ref{SIfig:reservoirs}).
+	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Accessible with reasonable request).
 	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
-	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supplementary Materials Section~\ref{SIsecA1}).
+	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supporting Informations Section~S1).
 	The water resources use dataset was from National Long-term Water Use Dataset of China (NLWUD) published by \citeA{zhou2020}, which includes water uses, water-consuming economic variables, and water use intensities by sectors the prefectures level.
@@
 
-	% We summarized the multiple-source dataset in Table~\ref{tab:datasets}.
+	We calculated the IWGI from 2001 to 2017 (the latest) in the Supporting Information Section S4 for robustness test with another water use dataset from Yellow River Water Resources Bulletin (\url{http://www.yrcc.gov.cn/zwzc/gzgb/gb/szygb/}).

### 2023-05-15 paper/main/03_results.tex
refactor(paper): :art: 更新正文所有图件
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 Dashed lines denote average of these percentages in different regimes.
-Red circles denote the reservoirs mainly for managing and regulating the whole basin.
+Red circles (Major Reservoirs) denote the reservoirs mainly for managing and regulating the whole basin.
 		The size of each circle indicates the magnitude of its water storage capacity.
-		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
+		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state agencies).
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
@@
 % P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
-As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2).
-% todo 检查图引用
+As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs.
 % 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
@@
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
+Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S7).
 % todo 检查图引用
-Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
+Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$).
 During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).

### 2023-05-15 paper/main/04_discussion.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 % 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
-Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
 Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.

### 2023-05-15 paper/main/manuscript.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 \usepackage{pifont}  % 输入带圈数字，参考https://blog.csdn.net/tsingke/article/details/105961016
-\usepackage{xr-hyper}
-% 参考其它文件的标签 https://texfaq.org/FAQ-extref
-\externaldocument[SI]{../sup/supplementary_information}
+% \usepackage{xr}
+% \usepackage{xr-hyper}
+% % 参考其它文件的标签 https://texfaq.org/FAQ-extref
+% \externaldocument[SI]{../sup/supplementary_information}
 \linenumbers
@@
 \section*{Open Research Section}
-All the used datasets and access source are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
+All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
+% The National Long-term Water Use Dataset of China (NLWUD) dataset within the Yellow River Basin uploaded.
 
@@
 
-%Reference citation instructions and examples:
-%
-% Please use ONLY \cite and \citeA for reference citations.
-% \cite for parenthetical references
-% ...as shown in recent studies (Simpson et al., 2019)
-% \citeA for in-text citations
-% ...Simpson et al. (2019) have shown...
-%
-%
-%...as shown by \citeA{jskilby}.
-%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
-%...has been shown \cite{jskilbye}.
-%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
-%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
-%...has been shown by \cite <e.g.,>[and others]{lewin76}.
-%
-% apacite uses < > for prenotes and [ ] for postnotes
-% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
-%
-
 \end{document}
-
-More Information and Advice:
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  SECTION HEADS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Capitalize the first letter of each word (except for
-% prepositions, conjunctions, and articles that are
-% three or fewer letters).
-
-% AGU follows standard outline style; therefore, there cannot be a section 1 without
-% a section 2, or a section 2.3.1 without a section 2.3.2.
-% Please make sure your section numbers are balanced.
-% ---------------
-% Level 1 head
-%
-% Use the \section{} command to identify level 1 heads;
-% type the appropriate head wording between the curly
-% brackets, as shown below.
-%
-%An example:
-%\section{Level 1 Head: Introduction}
-%
-% ---------------
-% Level 2 head
-%
-% Use the \subsection{} command to identify level 2 heads.
-%An example:
-%\subsection{Level 2 Head}
-%
-% ---------------
-% Level 3 head
-%
-% Use the \subsubsection{} command to identify level 3 heads
-%An example:
-%\subsubsection{Level 3 Head}
-%
-%---------------
-% Level 4 head
-%
-% Use the \subsubsubsection{} command to identify level 3 heads
-% An example:
-%\subsubsubsection{Level 4 Head} An example.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  IN-TEXT LISTS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Do not use bulleted lists; enumerated lists are okay.
-% \begin{enumerate}
-% \item
-% \item
-% \item
-% \end{enumerate}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  EQUATIONS
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Single-line equations are centered.
-% Equation arrays will appear left-aligned.
-
-Math coded inside display math mode \[ ...\]
- will not be numbered, e.g.,:
- \[ x^2=y^2 + z^2\]
-
- Math coded inside \begin{equation} and \end{equation} will
- be automatically numbered, e.g.,:
- \begin{equation}
- x^2=y^2 + z^2
- \end{equation}
-
-% To create multiline equations, use the
-% \begin{eqnarray} and \end{eqnarray} environment
-% as demonstrated below.
-\begin{eqnarray}
-  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
-        && + (y - y_{0}) \sin \Theta  \nonumber \\
-  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
-        && + (y - y_{0}) \cos \Theta.
-\end{eqnarray}
-
-%If you don't want an equation number, use the star form:
-%\begin{eqnarray*}...\end{eqnarray*}
-
-% Break each line at a sign of operation
-% (+, -, etc.) if possible, with the sign of operation
-% on the new line.
-
-% Indent second and subsequent lines to align with
-% the first character following the equal sign on the
-% first line.
-
-% Use an \hspace{} command to insert horizontal space
-% into your equation if necessary. Place an appropriate
-% unit of measure between the curly braces, e.g.
-% \hspace{1in}; you may have to experiment to achieve
-% the correct amount of space.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  EQUATION NUMBERING: COUNTER
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% You may change equation numbering by resetting
-% the equation counter or by explicitly numbering
-% an equation.
-
-% To explicitly number an equation, type \eqnum{}
-% (with the desired number between the brackets)
-% after the \begin{equation} or \begin{eqnarray}
-% command.  The \eqnum{} command will affect only
-% the equation it appears with; LaTeX will number
-% any equations appearing later in the manuscript
-% according to the equation counter.
-%
-
-% If you have a multiline equation that needs only
-% one equation number, use a \nonumber command in
-% front of the double backslashes (\\) as shown in
-% the multiline equation above.
-
-% If you are using line numbers, remember to surround
-% equations with \begin{linenomath*}...\end{linenomath*}
-
-%  To add line numbers to lines in equations:
-%  \begin{linenomath*}
-%  \begin{equation}
-%  \end{equation}
-%  \end{linenomath*}

### 2023-05-15 paper/response_letter/source/editor.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.
fi

@@
+\section{Associate Editor}\label{editor}
+
 \subsection{General comments}
@@
 
-\AR{} We acknowledge the need for a more in-depth analysis of our results.
+\AR{} We acknowledge the need for a more in-depth analysis of our previous results.
 We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers.
-We have also provided more context and explanation for these changes in the manuscript, which can be found on pages 14\-16 and 18\-21.
+We have also provided more context, explanation, and robustness analysis in the Supporting Informations (Section S2 to Section S4).
 
@@
 
-\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.
-We have added a new section in the manuscript discussing these indicators, comparing and contrasting their strengths and weaknesses, and explaining how our approach fills the gaps in the current literature.
-This new section can be found on pages 5\-7.
+\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.\ We have added a new paragraph in the introduction discussing the existed indexes, comparing and contrasting their strengths and weaknesses, and explaining innovation of IWGI.\
 
@@
 \RC{} I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer 1.
-In addition, I find the data in supplementary materials is not accessible, which should be amended.
+In addition, I find the data in Supporting Informations is not accessible, which should be amended.
 The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously.
@@
 
-\AR{} We appreciate the importance of using up-to-date data in our research.
-We have now included more recent data in our analysis, extending our dataset up to 2021.
-The updated data, along with the revised results and discussion, can be found on pages 11-13 and 18-21.
+\AR{} We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis.
 
-\AR*{} We apologize for the inconvenience caused by the inaccessibility of the supplementary materials.
-We have rectified this issue by ensuring that all supplementary data and files are now accessible and properly linked within the manuscript.
-We have also provided a clear description of the data and methodology in the supplementary materials to facilitate reproducibility of our results.
+\AR*{} We apologize for the inconvenience caused by the inaccessibility of the dataset.
+We have rectified this issue by refined our data description.
+Now, all the used datasets and their links are detailed described in the method section.
 

### 2023-05-15 paper/response_letter/source/reviewer_1.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 
-\subsection*{Overall comments} % todo
+\subsection*{Overall comments}
 
@@
 
-\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of supplementary material to demonstrate the changes in runoff.
+\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of Supporting Information to demonstrate the changes in runoff.
 Trend of natural runoff can also be inferred from the measured runoff (Figure~\ref{fig:runoff} from b to d) and water use (Figure~\ref{fig:runoff} from e to g).
@@
 
+\begin{figure}[!ht]
+	\centering
+	\renewcommand{\thefigure}{S2}
+	\includegraphics[width=\textwidth]{sup/sf_measured_runoff.jpg}
+	\caption{
+		\textbf{a.} Measured runoff of different regions in the Yellow River Basin from 1965 to 2013.
+		\textbf{b.} Measured runoff of different regions under different water governance regimes.
+		\textbf{c.} Natural river runoff of different regions under different water governance regimes.
+	}\label{fig:runoff}
+\end{figure}
+
 \begin{quote}[page=10, sline=274, eline=277]
 	% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
-	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
 \end{quote}
@@
 \AR{} Thank you for pointing this out, and we apologize for the confusion caused by the overly conclusive manuscript.
-In the revised manuscript, we have summarized the indicators by graphs with description in supplementary material:in the supplementary material.
+In the revised manuscript, we have summarized the indicators by graphs with description in Supporting Information:in the Supporting Information.
 
-% TODO 这里记得写一下是哪几个附图
-\AR*{} Figure~\ref{fig:purpose} to Figure~\ref{fig:scarcity} are three indicators changing trends. We added them into supplementary materials with descriptions:
+\AR*{} Figure~S3, Figure~S4, and Figure~S5 are three indicators changing trends. We added them into Supporting Informations with descriptions:
 
-\begin{quote}[page=Supplementary Materials]
+\begin{figure}[!htb]
+	\centering
+	\renewcommand{\thefigure}{S5}
+	\includegraphics[width=\textwidth]{sup/scarcity.png}
+	\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
+\end{figure}
+
+\begin{quote}[page=Supporting Informations]
 	The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
@@
 Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
+\end{quote}
 
+\begin{figure}[!htb]
+	\centering
+	\renewcommand{\thefigure}{S3}
+	\includegraphics[width=\textwidth]{sup/priority.jpg}
+	\caption{Changing trend of the indicator of purpose}\label{fig:purpose}
+\end{figure}
+
+\begin{quote}[page=Supporting Informations]
 	In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
-	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
+	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:purpose}).
+\end{quote}
 
+\begin{figure}[!htb]
+	\centering
+	\renewcommand{\thefigure}{S4}
+	\includegraphics[width=0.7\textwidth]{sup/allocation.png}
+	\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
+\end{figure}
+
+\begin{quote}[page=Supporting Informations]
 	The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
@@
 \AR{} Thanks for the reviewer's valuable advice, but for the following reasons, we are unable to postpone the study period to date in the main text.
-Instead, we added robustness test by using different-source data in supplementary material.
+Instead, we added robustness test by using different-source data in Supporting Information.
 
@@
 
+\begin{figure}[!htb]
+	\centering
+	\renewcommand{\thefigure}{S9}
+	\includegraphics[width=0.8\textwidth]{sup/robustness.png}
+	\caption{Recent years' IWGI changes}\label{fig:recent}
+\end{figure}
+
 \begin{quote}[page=11, sline=325, eline=327]
-	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:recent}).
-% TODO 补充材料新图
+	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (Supporting Informations~S9).
 \end{quote}
@@
 Sorry we didn't make the information accessible.
-Now, we added a table to describe this in the supplementary material (Table~\ref{tab:corr}).
+Now, we added a table to describe this in the Supporting Information (Table~S1).
 
-\input{source/tab_corr.tex}
+\input{../sup/tab_corr.tex}
 
-\begin{quote}[page=Supplementary Materials]
+\begin{quote}[page=Supporting Informations]
 	By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
@@
 % 然而，正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。
-However, as we have shown in Table~\ref{tab:corr}, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.
+However, as we have shown in Table~S1, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.
 
@@
 % 我们检验过了年尺度的输水数据，基本变化不大
-\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in supplementary material.
+\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in Supporting Information.
 According to the Yellow River Water Conservancy Commission (YRCC, data source), these reservoirs are mainly for managing and regulating the whole basin.
@@
 
+\begin{figure}[!htb]
+	\centering
+	\renewcommand{\thefigure}{S8}
+	\includegraphics[width=0.8\textwidth]{sup/conveyance.png}
+	\caption{Monthly conveyance flow differences of the reservoirs mainly for managing and regulating the whole basin and their variability}\label{fig:conveyance}
+\end{figure}
+
 \begin{quote}[page=8, sline=223, eline=225]
-	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
-% todo 检查图引用
+	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supporting Informations Figure~\ref{fig:conveyance}).
 \end{quote}
@@
 	On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
-	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
+	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2022a}.
 	On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
@@
 
-\AR{} That's a good suggestion. We now moved the calculation from supplementary material to the main text.
+\AR{} That's a good suggestion. We now moved the calculation from Supporting Information to the main text.
 
@@
 
-\AR*{} We now attached a new supplementary material which includes descriptions and all sources of the datasets used in this study.
+\AR*{} We now attached a new Supporting Information which includes descriptions and all sources of the datasets used in this study.
 If you want to know more about the data, please check the data source through the provided information.
@@
 \AR{} We used $0.001$ for generating the figure at last (fixed the typo in Fig.2A now).
-Anyway, as we showed in supplementary material Figure~S3, no difference in results because the change points are robust.
-% TODO 检查一下鲁棒性的图表
+Anyway, as we showed in Supporting Information Figure~S7, no difference in results because the change points are robust.
 

### 2023-05-15 paper/response_letter/source/reviewer_2.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 
-\AR{} Thanks!
+\AR{} We appreciate your acknowledgement of the reasonable and adaptable methodology used in this study, as well as the useful insights provided by the case analysis.
+We agree that the discussion could be more supportive and solid in its content of the results and we will work to revise the manuscript accordingly.
+Please find our point-by-point response to your specific comments below.
 
@@
     On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
-    For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
+    For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2022a}.
     On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
@@
 
-\AR*{} To make that more explicit, we modified the corresponding description in the Supplementary Materials:
+\AR*{} To make that more explicit, we modified the corresponding description in the Supporting Informations:
 
-\begin{quote}[page=Supplementary Materials]
+\begin{quote}[page=Supporting Informations]
     In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
@@
 
-\begin{quote}[page=Supplementary Materials]
+\begin{quote}[page=Supporting Informations]
     Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.

### 2023-05-15 paper/sup/01_yrb.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 The YRB can be divided into four regions to calculate the indicators considering both socio-economic and natural conditions.
-The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverwaterconservancycommission2010,wang2019c}.
+The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverwaterconservancycommission2010,wang2019c}, hydrological characteristics are described in Figure~\ref{fig:runoff}.
 
@@
 
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=\textwidth]{sup/sf_measured_runoff.jpg}
+	\caption{
+		\textbf{a.} Measured runoff of different regions in the Yellow River Basin from 1965 to 2013.
+		\textbf{b.} Measured runoff of different regions under different water governance regimes.
+		\textbf{c.} Natural river runoff of different regions under different water governance regimes.
+	}\label{fig:runoff}
+\end{figure}
+
 % % 补充图片4：天然水资源量

### 2023-05-15 paper/sup/02_indicator.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
     \includegraphics[width=\textwidth]{sup/priority.jpg}
-    \caption{Changing trend of the indicator of purpose}\label{fig:purpose}
+    \caption{
+        \textbf{left} Changing trend of the indicator of purpose (IP)
+        \textbf{right} contributions of different water use sectors to the IS's changes.
+    }\label{fig:purpose}
 \end{figure}
@@
     \includegraphics[width=0.8\textwidth]{sup/allocation.png}
-    \caption{Changing trend of the indicator of allocation}\label{fig:allocation}
+    \caption{Changing trend of the indicator of allocation (IA)}\label{fig:allocation}
 \end{figure}

### 2023-05-15 paper/sup/04_robustness.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@
 In addition, we analyzed the changes of reservoir flow that are not reflected in the IWGI.\ Among all the reservoirs (Figure~\ref{fig:reservoirs}), we focused on $9$ major reservoirs built successively and find that the reservoirs began to enhance their variability after the governance transforming regime, suggesting a higher level of regulating (Figure~\ref{fig:conveyance}).
+
+Last, we tried our best to strengthen the period of this study despite the limitations of time span of the multiple-source dataset.
+We calculated the IWGI from 2003 to 2017 by using data from Yellow River Water Resources Bulletin to extend the study period.
+Since our results suggest no significant regime change (Figure~\ref{fig:recent}), we think it is robust that the YRB experienced two significant water governance regime changes in 1978 and 2001, without further changing since 21th century.
 
@@
 \end{figure}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{sup/robustness.png}
+	\caption{Recent years' IWGI changes calculated by data from Yellow River Water Resources Bulletin. No significant changing point exists}\label{fig:recent}
+\end{figure}

### 2023-05-15 paper/letter/cover_letter_r1.tex
docs(paper): :memo: 更新cover letter和给编辑的回复信

\documentclass[11pt,a4paper,roman]{moderncv}

\graphicspath{{../../../figs/}}
\linespread{1.5}
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\moderncvstyle{classic}
\moderncvcolor{blue} % Bullet point color

% Page margins
\usepackage[scale=0.85]{geometry} % Page margins

% Your Information, please revise
\name{Shuai}{Wang}
\address{Haidian District, Beijing, China}{No.19, Xinjiekouwai St.}
\phone[mobile]{+86 182 1009 3639}
\email{shuaiwang@bnu.edu.cn}

\begin{document}

% Insert Olin Logo
\begin{minipage}[t]{\textwidth}
\includegraphics[width=0.40\textwidth]{bnu}
\end{minipage}

\recipient{Dear Editor in chief,}{}
\opening{\vspace*{-2em}}
\closing{Sincerely,}{\vspace*{-2em}}
\enclosure[Enclosures]{Main manuscript, Appendix}
\makelettertitle
% https://pythonjishu.com/qggkmtfnuj
% 调整两端对齐
\justify

Thank you for the opportunity to revise our manuscript titled ``Identifying regime transitions for water governance at a basin scale'' We appreciate the constructive feedback provided by the reviewers and believe that our revised manuscript more effectively addresses their concerns.

% 很抱歉我们花了这么长时间来返修，但正如您看到的，我们在新的版本中补充了很多内容和图表，努力回应审稿人和编辑的一切关切。我们也花时间试着联系了数据的作者团队。在得知正文中数据短时间内无法增补到最新年份后，我们使用其它数据源再次计算了IWGI，从而努力增强结果的鲁棒性。
I'm sorry it took us so long to go back, but as you can see, we've added a lot of content and graphics to the new version in an effort to respond to all the concerns of reviewers and editors. We also took the time to try to contact the team that authored the data. After learning that the data in the text could not be updated to the latest year for a short time, we supplement analysis using other data sources in an effort to enhance the robustness of the results.
In response to the reviewers' feedback, we also restructured the introduction and discussion sections to provide a more supportive and solid content of the results.

We believe that these revisions have significantly improved the quality and value of our manuscript, and we hope that you will find it suitable for publication in Water Resources Research. We are confident that our study makes a valuable contribution to the understanding of water governance in China and beyond.

The revised manuscript includes the main body of text with $4423$ words and $4$ figures; the supporting information with $4$ sections has $9$ supporting figures and $1$ supporting tables. Furthermore, we declare no conflicts of interest to disclose.

\vspace{0.3cm}

Thanks for your time. We appreciate your consideration!

\vspace{0.3cm}

Sincerely,

\textbf{Shuai Wang} (On behalf of the author team)

%\begin{minipage}[t]{\textwidth}
%	\includegraphics[height=1cm]{signature.jpeg}
%\end{minipage}

State Key Laboratory of Earth Surface Processes and Resource Ecology,

Faculty of Geographical Science,

Beijing Normal University,

Beijing 100875, China

Email: bfu@rcees.ac.cn

\end{document}

### 2023-05-15 paper/main/02_methods.tex
docs(paper): :memo: 更新cover letter和给编辑的回复信

@@
 
-	We calculated the IWGI from 2001 to 2017 (the latest) in the Supporting Information Section S4 for robustness test with another water use dataset from Yellow River Water Resources Bulletin (\url{http://www.yrcc.gov.cn/zwzc/gzgb/gb/szygb/}).
+	Finally, we calculated the IWGI from 2001 to 2017 (the latest) in the Supporting Information Section S4 for robustness test with another water use dataset from Yellow River Water Resources Bulletin (\url{http://www.yrcc.gov.cn/zwzc/gzgb/gb/szygb/}).

### 2023-05-15 paper/main/04_discussion.tex
docs(paper): :memo: 更新cover letter和给编辑的回复信

@@
 % 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
-Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~S2 and Figure~S3).
 Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.

### 2023-05-15 paper/response_letter/source/editor.tex
docs(paper): :memo: 更新cover letter和给编辑的回复信

@@
-\section{Associate Editor}\label{editor}
+% chktex-file 46
+\section*{Associate Editor}\label{editor}
 
@@
 We have also provided more context, explanation, and robustness analysis in the Supporting Informations (Section S2 to Section S4).
+There is a detailed explanation for this issue in the Response~\ref{sec:1-2} to the reviewer \#1 and the Response~\ref{sec:2-7} to the reviewer \#2.
 
@@
 
-\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.\ We have added a new paragraph in the introduction discussing the existed indexes, comparing and contrasting their strengths and weaknesses, and explaining innovation of IWGI.\
+\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.\ We have added a new paragraph in the introduction discussing the existed indexes, comparing and contrasting their strengths and weaknesses, and explaining innovation of IWGI.\ There is a detailed explanation for this issue in the Response~\ref{sec:2-2} to the reviewer \#2.
 
@@
 
-\AR{} We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis.
+\AR{} We appreciate the importance of using up-to-date data in our research.
+We have now included an analysis with more recent data in our supporting information.
+You can find a detailed explanation for this issue in the Response~\ref{sec:1-3} to the reviewer \#1.
 
@@
 We have rectified this issue by refined our data description.
-Now, all the used datasets and their links are detailed described in the method section.
+Now, all the used datasets and their links are detailed described in the method section:
 
-\AR*{} We hope that these revisions address the concerns raised by both reviewers and the associate editor.
+\begin{quote}
+	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
+	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Accessible with reasonable request).
+	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
+	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supporting Informations Section~S1).
+	The water resources use dataset was from National Long-term Water Use Dataset of China (NLWUD) published by \citeA{zhou2020}, which includes water uses, water-consuming economic variables, and water use intensities by sectors the prefectures level.
+	We determined the prefectures belong to the YRB by filtering the NLWUD dataset with a threshold of $95\%$ intersected area.
+
+	For analyzing its causes of changing water, irrigated area, gross added values of industry and services, and water use intensities data were also from NLWUD dataset~\cite{zhou2020}.
+	Besides, two water governance policies datasets are used: laws data and ``big events'' documents dataset.
+	Data of laws were collected from~\citeA{yellowriverwaterconservancycommission2010}, which reviewed all important laws at the basin scale related to the Yellow River from the last century.
+	The original documents of ``big events'' related to the Yellow River come from the YRCC, the agency at the basin scale, which recorded and compiled these events (\url{http://www.yrcc.gov.cn/hhyl/hhjs/}).
+
+	Finally, we calculated the IWGI from 2001 to 2017 (the latest) in the Supporting Information Section S4 for robustness test with another water use dataset from Yellow River Water Resources Bulletin (\url{http://www.yrcc.gov.cn/zwzc/gzgb/gb/szygb/}).
+\end{quote}
+
+\AR*{} We hope that these revisions address the concerns raised by both reviewers.
 We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community.

### 2023-05-15 paper/diff/v-8.2.0.tex
fix(paper): :memo: keypoint 超字数

--- 2023-05-15 paper/diff/draft.tex
@@
 \graphicspath{{/Users/songshgeo/Documents/VSCode/WGRegimes_YRB_2020/figures}}
-\title{Identifying regime transitions for water governance: Take the Yellow River Basin in China as case}
+\title{Identifying regime transitions for water governance at the Yellow River Basin, China}
 
@@
 We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
-Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see \\textit{Supporting Information} Figure~S3).
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see Figure~S6).
 
-	\subsection{Datasets}
-Multiple sources of data were used in this study, and we have attached a summarized data table as Supporting Information and their processing are detailed described in the supplementary documentation.
+	\subsection{Datasets}\label{sec:datasets}
+
+	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
+	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Accessible with reasonable request).
+	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
+	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supporting Informations Section~S1).
+	The water resources use dataset was from National Long-term Water Use Dataset of China (NLWUD) published by \citeA{zhou2020}, which includes water uses, water-consuming economic variables, and water use intensities by sectors the prefectures level.
+	We determined the prefectures belong to the YRB by filtering the NLWUD dataset with a threshold of $95\%$ intersected area.
+
+	For analyzing its causes of changing water, irrigated area, gross added values of industry and services, and water use intensities data were also from NLWUD dataset~\cite{zhou2020}.
+	Besides, two water governance policies datasets are used: laws data and ``big events'' documents dataset.
+	Data of laws were collected from~\citeA{yellowriverwaterconservancycommission2010}, which reviewed all important laws at the basin scale related to the Yellow River from the last century.
+	The original documents of ``big events'' related to the Yellow River come from the YRCC, the agency at the basin scale, which recorded and compiled these events (\url{http://www.yrcc.gov.cn/hhyl/hhjs/}).
+
+	Finally, we calculated the IWGI from 2001 to 2017 (the latest) in the Supporting Information Section S4 for robustness test with another water use dataset from Yellow River Water Resources Bulletin (\url{http://www.yrcc.gov.cn/zwzc/gzgb/gb/szygb/}).
  \section{Results}\label{sec2}
@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2).
+		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state agencies).
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
@@
 Changing water demands and supply were critical to the shift between P1 and P2.
-As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2).
+As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs.
 Ensuing the P2, however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes}~A and B).
@@
 Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S7).
-Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
+Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$).
 During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
@@
 The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
-Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
+Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~S2 and Figure~S3).
 Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
@@
 \section*{Open Research Section}
-All the used datasets and access source are listed in the \textit{SI Appendix} Table~S1 with a detailed description in \textit{Supporting Information S3}.
+All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
 

### 2023-05-15 paper/main/manuscript.tex
fix(paper): :memo: keypoint 超字数

@@
       \item The study interprets the transformation of water governance within a rapidly evolving large river basin -the Yellow River Basin.
-\item A novel approach was developed to analyze the complex interconnections between water governance, hydrosocial transition, and human-water relationships.
+      \item A novel approach was developed to analyze interconnections between water governance, hydrosocial transition, and human-water relationships.
 \end{keypoints}

### 2023-05-22 paper/diff/v-8.2.1.tex
fix(paper): :memo: 调整并更新数据开源表述

--- 2023-05-15 paper/diff/v-8.2.0.tex
@@
 	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
-	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Accessible with reasonable request).
+	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1956.
 	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
@@
 \section*{Open Research Section}
-All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
+Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.
 
@@
 
-\bibliography{../mybibtex.bib}
+\bibliography{../v-8.2.1.bib}
 

### 2023-05-22 paper/main/manuscript.tex
fix(paper): :memo: 调整并更新数据开源表述

@@
 \section*{Open Research Section}
-All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
-% The National Long-term Water Use Dataset of China (NLWUD) dataset within the Yellow River Basin uploaded.
+Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.
 

### 2023-05-31 paper/diff/v-8.2.2.tex
docs(paper): :memo: 更新开放数据声明

--- 2023-05-22 paper/diff/v-8.2.1.tex
@@
 \section*{Open Research Section}
-Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.
+Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955500}~\cite{shuang_song_2023_7955500}.
 
@@
 
-\bibliography{../v-8.2.1.bib}
+\bibliography{../mybibtex.bib}
 

### 2023-05-31 paper/diff/v-8.2.3.tex
docs(paper): :memo: 更新开放数据声明

--- 2023-05-22 paper/diff/v-8.2.1.tex
@@
 \section*{Open Research Section}
-Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.
+All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events are available under CC-BY 4.0 license~\cite{shuang_song_2023_7955500}.
+Figures were made with Matplotlib version 3.7.1~\cite{Hunter:2007} and python-ternary version 1.0.8~\cite{pythonternary}.
+These open sourced softwares are available under the Matplotlib license at \url{https://github.com/matplotlib/matplotlib} and the MIT license at \url{https://github.com/marcharper/python-ternary}, separately.
 
@@
 
-\bibliography{../v-8.2.1.bib}
+\bibliography{
+../mybibtex.bib,
+../others.bib
+}
 

### 2023-05-31 paper/main/manuscript.tex
docs(paper): :memo: 更新开放数据声明

--- 2023-05-15 paper/main/manuscript.tex
@@
 \section*{Open Research Section}
-All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
-% The National Long-term Water Use Dataset of China (NLWUD) dataset within the Yellow River Basin uploaded.
+All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events are available under CC-BY 4.0 license~\cite{shuang_song_2023_7955500}.
+Figures were made with Matplotlib version 3.7.1~\cite{Hunter:2007} and python-ternary version 1.0.8~\cite{pythonternary}.
+These open sourced softwares are available under the Matplotlib license at \url{https://github.com/matplotlib/matplotlib} and the MIT license at \url{https://github.com/marcharper/python-ternary}, separately.
 
@@
 
-\bibliography{../mybibtex.bib}
+\bibliography{
+../mybibtex.bib,
+../others.bib
+}
 

### 2023-10-06 paper/response_letter/source/editor.tex
docs(paper): :memo: prepare revise the paper

--- 2023-05-15 paper/response_letter/source/editor.tex
@@
-\section{Associate Editor}\label{editor}
+% chktex-file 46
+\section*{Associate Editor}\label{editor}
 
-\subsection{General comments}
-\RC{} Dear Authors, thanks for the submission of the manuscript.
-We have asked two experts in the relevant fields to review the manuscript.
-Both reviewers overall find the merit in the manuscript however they also noted several major issues in the current manuscript.
-With my own reading, I fully agree with the reviewers and would like to highlight a few major issues:
+\subsection{Remarks to Author}
+\RC{} Dear Authors, thank you for the carful revisions.
+Our original referees have re-evaluated the revised manuscripts.
+While they are satisfied with most of the revisions, they find that some of their earlier comments were not fully addressed.
+
+\RC{} As Reviewer \#1 pointed out, there needs to be more carful evaluation of the method with water stress calculation, which would affect part of the outcome.
+
+\AR{}
+
+\RC{} Reviewer \#2 provided a set of very useful comments to further improve the clarity of the manuscript.
+Reviewer \#2 also pointed out that the link in the SI is not accessible so please carefully check.
+We won't be able to pursue publication without warranting all the supporting information and data access.
+I would like to encourage the authors to address all the comments and re-submit a suitably revised manuscript in due course.
 
@@
 
-\subsection{Issue \#1}
-\RC{} overall the results and discussion are relatively shallow and I would encourage the authors to do deep dive into the results, e.g.\ change points, as also pointed out by both reviewers,
-
-\AR{} We acknowledge the need for a more in-depth analysis of our previous results.
-We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers.
-We have also provided more context, explanation, and robustness analysis in the Supporting Informations (Section S2 to Section S4).
-
-\subsection{Issue \#2}
-\RC{} I fully agree with Reviewer \#2 that more thorough review of existing and relevant indicators with IWGI,
-
-\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.\ We have added a new paragraph in the introduction discussing the existed indexes, comparing and contrasting their strengths and weaknesses, and explaining innovation of IWGI.\
-
-\subsection{Issue \#3}
-\RC{} I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer 1.
-In addition, I find the data in Supporting Informations is not accessible, which should be amended.
-The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously.
-
-\RC*{} Overall, based on the reviewers' recommendations, I would like to ask the authors to submit a suitably revised manuscript in due course.
-
-\AR{} We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis.
-
-\AR*{} We apologize for the inconvenience caused by the inaccessibility of the dataset.
-We have rectified this issue by refined our data description.
-Now, all the used datasets and their links are detailed described in the method section.
-
-\AR*{} We hope that these revisions address the concerns raised by both reviewers and the associate editor.
+\AR*{} We hope that these revisions address the concerns raised by both reviewers.
 We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community.

### 2023-10-06 paper/response_letter/source/reviewer_1.tex
docs(paper): :memo: 更新cover letter和给编辑的回复信
docs(paper): :memo: prepare revise the paper

--- 2023-05-13 paper/response_letter/source/reviewer_1.tex
@@
 
-\subsection*{Overall comments} % todo
+Reviewer \#1 Evaluations:
+Recommendation (Required): Return to author for minor revisions
+Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.
+Supported: Mostly yes, but some further information and/or data are needed.
+Referencing: Yes
+Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.
+Data: Yes
+Accurate Key Points: Yes
 
-\RC{} This study proposed an integrated index that incorporates water resources, water use, and water allocation to represent the water governance regime in the Yellow River basin.
-The authors showed an in-depth understanding of the water governance in this basin and made a great effort to represent the status of water governance straightforwardly with the integrated index.
-The figures were generally well-designed and presented clearly.
-But I feel the paper lacks details of the results which makes it difficult to understand the paper.
-Specific comments are listed below.
+\subsection*{Overall comments}
 
-% 感谢您认可。
-% 很抱歉缺少细节，可能会使您难以完全理解我们的研究。
-% 为了回应您的担忧，我们已经修改了我们的稿件，并提供了更详细的结果解释。请在下面找到我们对您的具体评论的逐条回复。
-\AR{} Thank you for your valuable feedback and for acknowledging our efforts in understanding the water governance in the Yellow River basin.
-We appreciate your comments regarding the clarity of the figures and our integrated index.
-Sorry about the lack of details in the results section may have made it difficult to fully comprehend our study.
-In response to your concerns, we have revised our manuscript and provided a more detailed explanation of the results.
-Please find our point-by-point response to your specific comments below.
+Reviewer \#1 (Formal Review for Authors (shown to authors)):
 
-\subsection{Major concern \#1}
+The study on water governance stages relies heavily on the integrated index IWGI at the basin scale, which offers significant advantages for decision-making support.
+Nonetheless, in large basins, the index may obscure crucial details and spatial heterogeneity.
+For instance, averaging the water stress of areas with and without water stress could lead to a misleading "no water stress" result.
+To improve the discussion on water governance transition, I recommend the authors link the three periods to well-known phenomena or policies, such as the occurrence of zero-flow in the Yellow River.
+Additionally, the current separation of periods using the Pettitt method for change point detection could be improved or compared to other methods, considering its sensitivity to time series changes.
 
-% 气候变化在指数中没有明确的体现，这可能是本世纪黄河流量恢复的关键因素。气候变化将是未来该流域面临的巨大挑战。重大的气候变化可能影响流域的适应能力，因此需要不同的治理策略。
-\RC{} Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century.
-Climate change would be a great challenge in the basin in the future.
-Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.
+\subsection*{Specific comments}
 
-% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。
-% 在新增加的图表中，我增加了天然水量的图表展示这种变化
-% 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（purpose）。
-% 我们现在在讨论中涉及了这些话题。
-\AR{} Thanks for the comment that we lacked a discussion of climate change, which has a multitude of impacts e.g., on precipitation and evaporation.
-However, these effects are inherently captured within the Integrated Water Governance Index (IWGI) because the available water resources are affected by climate change as consequences.
-For clarity, we first modified our expression of SFV-index, which is the indicator highly related to climate change (both in water yield and its fluctuation):
+Equation (5): Would adopting an area-weighted average be more appropriate in Equation (5)?
+This change could offer a more accurate representation of the data, especially when considering the variations in water stress across different areas within the basin.
 
-\begin{quote}[page=3, sline=78, eline=82]
-	The impetus for developing this new index lies in the evolving practices of water governance driven by a blend of social and natural influences.
-	Firstly, climate change impacts on current water yield, coupled with escalating demands from economic activities and the need for water storage development, intensify water stress~\cite{qin2019,wada2014,huang2021}.
-\end{quote}
+Page 5: I guess WUi,j reflects water use (or water withdrawal) rather than water consumption.
 
-\begin{quote}[page=5, sline=144, eline=149]
-	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
-	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
-	% 这个指数得到了许多应用，是就我们已知范围内考虑因素最为齐全的，反应水资源压力的指数。
-	The SFV-index, which has many applications, is the most comprehensive index of water stress we know.
-\end{quote}
+Page 10, Line 265-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
+Furthermore, since 2000, zero-flow has not reappeared, which could be accounted for in the analysis.
 
-\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of supplementary material to demonstrate the changes in runoff.
-Trend of natural runoff can also be inferred from the measured runoff (Figure~\ref{fig:runoff} from b to d) and water use (Figure~\ref{fig:runoff} from e to g).
-We quote this figure when discussing climate context, now:
+Page 11, Line 308: Could you elaborate on "manage natural water processes"?
 
-\begin{quote}[page=10, sline=274, eline=277]
-	% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
-	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
-\end{quote}
+Page 11, Line 313-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
 
-\AR*{} Finally, we further discussed the challenges brought by climate changes in the discussion section:
-
-% 我们强调流域治理需要考虑这些因素，但我们可能很难穷尽优秀的流域治理策略需要考虑哪些因素。因此，IWGI至少让我们可以知道在诸多治理因素的共同影响下，流域的未来正在走向何方。
-\begin{quote}[page=11, sline=306, eline=316]
-	Future's tightly intertwined socio-hydro interactions can lead water governance challenges even more complex and comprehensive, combining resources issues and structural barriers~\cite{huggins2022a}.
-	For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
-	Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (purpose and allocation) which is being increasingly altered by current regime transitions.
-	It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
-\end{quote}
-
-\subsection{Major concern \#2}
-% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
-\RC{} The results are summative.
-I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions.
-And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values.
-These details could help readers understand the reasonability of the results.
-
-% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。
-% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
-% 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）。
-\AR{} Thank you for pointing this out, and we apologize for the confusion caused by the overly conclusive manuscript.
-In the revised manuscript, we have summarized the indicators by graphs with description in supplementary material:in the supplementary material.
-
-% TODO 这里记得写一下是哪几个附图
-\AR*{} Figure~\ref{fig:purpose} to Figure~\ref{fig:scarcity} are three indicators changing trends. We added them into supplementary materials with descriptions:
-
-\begin{quote}[page=Supplementary Materials]
-	The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
-	Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
-	The upper and middle reaches (UR and MR) had the greatest impact on the IS changes.
-Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
-
-	In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
-	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).
-
-	The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
-\end{quote}
-
-\AR*{} In addition, ranges of three indicators and meaning of their values are further explained in the methodology section of main text, now:
-
-\begin{quote}[page=5, sline=137, eline=138]
-	where $I'_x$ is calculated by Min-Max normalization of $I_x$ (thus ranges from zero to one):
-	\begin{equation}
-		I'_x = (I_x - I_{x, \min}) / (I_{x, \max} - I_{x, \min})
-	\end{equation}
-\end{quote}
-
-\subsection{Major concern \#3}
-% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
-\RC{} The data used in this study seem to have different time periods, and most data are from before 2013.
-The hydrological regime and water governance in the Yellow River should have changed significantly in the recent decade.
-Therefore, incorporating the result from the recent decade would make this study more solid.
-
-% 感谢审稿人的宝贵建议，但出于以下原因，我们无法在新的手稿中将研究时段后延至今
-\AR{} Thanks for the reviewer's valuable advice, but for the following reasons, we are unable to postpone the study period to date in the main text.
-Instead, we added robustness test by using different-source data in supplementary material.
-
-% 首先，本研究结论希望展现黄河水治理演变过程，尤其是重点关注1978到2001年之间的治理转型过程。尽管许多数据能在近二十年间计算IWGI，但代价是忽略了更远的时间段。而正如我们在新手稿的方法部分所补充说明的，使用不同的数据源容易造成时间不连续的问题（通常它们的统计口径是不一样的）。
-\AR*{} Firstly, the conclusion of this study aims to show the evolution process of water governance of the Yellow River, especially focusing on the governance transformation between 1978 and 2001.
-Although many dataset allow IWGI to be calculated over the last two decades, the cost is to ignore the more important past periods.
-In addition, it's difficult to assimilate the different data sources because datasets usually have different statistical approach when categorizing water use sectors.
-Now, we added an explanation in the methods section of the new manuscript:
-
-\begin{quote}[page=5, sline=138, eline=140]
-	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
-\end{quote}
-
-\AR*{} Secondly, as the reviewer noticed, we used multiple-source dataset to implement our approach, which means time periods of a coherent analysis is limited by the shortest data.
-To cover study period from 1960s to 2000s, water use data developed by \citeA{zhou2020} is the most good quality and widely used dataset.
-The shortage, however, is not enough to cover the period after 2013.
-We contacted the original author team, but only confirmed that latest dataset is still unavailable.
-As some of the source data used to produce this crucial dataset could not be easily supplemented, this was not an effort that could be supplemented in this study.
-Therefore, we decided to keep the analysis discontinued in 2013 in main texts:
-
-\begin{quote}[page=11, sline=323, eline=325]
-	Another limitation is the lack of latest datasets which is coherent with the historical datasets, so our analysis had to discontinued in 2013 despite potential shifts existing.
-\end{quote}
-
-\AR*{} Last, we tried our best to strengthen robustness of this study despite the above limitations.
-We calculated IWGI by using another data source for the past two decades.
-Since our results suggest no significant regime change, we think it is robust that the YRB experienced two significant water governance regime changes.
-
-\begin{quote}[page=11, sline=325, eline=327]
-	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:recent}).
-% TODO 补充材料新图
-\end{quote}
-
-\subsection{Major concern \#4}
-% 这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?
-\RC{} There might be interactions/interconnections among the three indicators. Did the authors examine the relations between the indicators?
-
-\AR{} Yes, we did examination for the interconnections between the three indicators.
-Sorry we didn't make the information accessible.
-Now, we added a table to describe this in the supplementary material (Table~\ref{tab:corr}).
-
-\input{source/tab_corr.tex}
-
-\begin{quote}[page=Supplementary Materials]
-	By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.
-
-	When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.\
-	On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI.\ However, the correlations of other combinations are not statistically significant overall.
-
-	The correlations between time periods are very different with the overall trend above.
-	There is no significant correlation between any indicator combinations in the massive supply regime (P1).
-	In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
-	The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3).
-However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).
-\end{quote}
-
-\AR*{} In addition, note that strictly independent of indicators is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
-% 这是因为，如果两个子指标在某时期内相关性显著，可能说明两者在该时期同时受到某些治理驱动因素的共同作用，这是可能发生的。
-This is because a significant correlation between two indicators in a given period may indicate that both were simultaneously affected by some governance drivers during that period, which is possible.
-% 但同样，若两个指标始终都存在较强的关联，则可能说明稳态转换并不显著，IWGI同时考虑三者的意义也存疑。
-Similarly, if there is always a strong correlation between the two indicators, it may indicate that the steady-state transformation is not significant, and the significance of IWGI considering the three indicators at the same time is doubtful.
-% 然而，正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。
-However, as we have shown in Table~\ref{tab:corr}, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.
-
-\subsection{Major concern \#5}
-% IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。
-\RC{} The IWGI includes reservoir storage information in the ``stress'' aspect.
-However, the water conveyance ability is not represented, which is also an important indicator of water governance/hydrosocial resilience.
-
-% 短期的输水能力是衡量水治理/水社会复原力的重要指标
-% 但年尺度上，变化不大
-\AR{} We agree that conveyance is crucial to water governance/water society resilience, especially in the short term.
-However, the IWGI in this study focuses on annual time resolution.
-At this scale, conveyance has a less significant impact on water governance.
-From this point of view, there are two reasons that IWGI doesn't have to consider this in our study:
-
-% 输水是水治理的手段，我们更侧重于这种治理的结果。
-\AR*{} Firstly, water conveyance is more like an approach of water governance, and we focus more on the outcomes -i.e., how water stress is relieved by conveyance; how it help provision to specific sectors with higher purpose; how convert water changes allocation of water resources \dots
-
-% 水治理很复杂，考虑到越来越多的要素会增加其复杂度。Scarcity是本研究使用最复杂的指标，因为这是一个经过检验的，可以有效表征的指数。如果经过检验影响不大，没有必要增加复杂度。
-\AR*{} Secondly, water governance is comprehensive, and taking into account more and more elements increases its complexity.
-SFV-index is the most complex index used in this study, because it is a tested index that can be effectively represented.
-If not necessary, we prefer not to include more complexity.
-
-% 我们检验过了年尺度的输水数据，基本变化不大
-\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in supplementary material.
-According to the Yellow River Water Conservancy Commission (YRCC, data source), these reservoirs are mainly for managing and regulating the whole basin.
-The result (Figure~\ref{fig:conveyance}) shows that variability increased in the later regimes, supporting our main results that regulation plays a more significant role since the governance transforming regime (P2).
-We also appropriately modified the description in main text:
-
-\begin{quote}[page=8, sline=223, eline=225]
-	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supplementary Materials Figure~S7).
-% todo 检查图引用
-\end{quote}
-
-\subsection{Major concern \#6}
-% 我建议在标题中加上“黄河流域”。因为没有对IWGI的适用性和有效性进行测试或讨论。它能在其他盆地使用吗?使用索引的先决条件是什么?
-\RC{} I would suggest adding ``Yellow River basin'' in the title.
-Because the applicability and validity of the IWGI were not tested or discussed.
-Can it be used in other basins?
-What is the prerequisite for using the index?
-
-% 感谢你的提议，我们现在在标题中增加了黄河流域，新的标题是：
-\AR{} Thanks to your proposal, we have now added the Yellow River Basin to the title, and the new title is: \textbf{``Identifying regime transitions for water governance: Take the Yellow River Basin in China as case''}
-
-% 关于IWGI的泛用性，实际上我们曾在讨论中讨论了这一点。
-% 非常抱歉先前的讨论似乎不够明确，我们在修改后的论文中重新澄清了这点。
-\AR*{} Regarding the generality of IWGI, we actually discussed this in our discussion.
-I am very sorry that the previous discussion seems not clear enough, and we have clarified this point again in the revised manuscript.
-
-\begin{quote}[page=11, sline=317, eline=323]
-	One of the main limitations in the approach is the lack of multi-sources data in long-term period worldwide, which means there is still a gap between comprehensively identifying and applying the IWGI widely.
-	We propose that all water governance issues, however, can change ``who gets water, when and how'' so monitoring such an integrated index is essential, even use simpler indicators.
-	We suggest that choices of indicators for different aspects can be adapted according to available datasets -e.g., replace the SFV-index (IA) with simpler scarcity index or proportion-based purpose indicator (IP) by complicated one.
-\end{quote}
-
-% 此外，我们如今在方法部分提到了使用它的先决条件，使用同样数据源保证单一子指标的时间序列连贯性，而不同子指标可以采用不同的数据源。
-\AR*{} In addition, we have now mentioned in the methods section:
-
-\begin{quote}[page=5, sline=138, eline=142]
-	Since the IWGI essentially comprises by three aspects' indicator with same weights, its prerequisite is to keep the same data source for each indicator throughout time, to ensure time series continuity.
-	However, vary data sources can be used when estimating the specific indicator or cross different indicators, which makes IWGI a flexible framework for substituted indicators.
-\end{quote}
-
-\subsection{Major concern \#7}
-% 最好在引言部分解释“水治理机制”的概念，然后解释使用综合指数IWGI代表水治理机制的必要性。
-\RC{} It would be better to explain the concept ``water governance regime'' in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.
-
-% 感谢你的建议，我们在引言部分为“水治理机制”提供了一个简短但明确的解释：
-\AR{} Thanks for your advice, we nor provide a short but clear explanation of the ``water governance regime'' in the introduction:
-
-\begin{quote}[page=3, sline=93, eline=98]
-	A critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
-	Regimes of water governance, the general guidelines of governing practices, arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020,pahl-wostl2007}.
-\end{quote}
-
-% 我们还为这种指数的必要性做出了补充：
-\AR*{} We also add to the argument for the need for such an index:
-
-\begin{quote}[page=2, sline=66, eline=77]
-	Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
-	On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
-	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
-	On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
-	Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
-	Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
-	As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
-\end{quote}
-
-\subsection{Detailed issues}
-
-% 我没有在引用的文献中找到“用水的三个核心方面”。这三个方面是作者提出的吗?
-\RC{} Line 57$-$62: I did not find the ``three core aspects of water use'' in the cited reference. Were the three aspects put forward by the authors?
-
-% 非常非常感谢您指出这个错误，由于我们弄混了 citation key，这是一个无意间产生的引用错误。
-\AR Thank you very, very much for pointing out this error. It was an accidental reference error due to our mix-up of the citation key.
-
-% 总体来说，这是一个引用，但不是逐字逐句的引用，而是基于我们对\citeA{mariajacobson2013}报告的理解。报告在背景部分提出水治理的三个方面，我们将其总结为 stress, purpose, and allocation. 而 what, when, how 的说法则直接来自于该文献，这也是较为广泛的一种对 water governance 如何影响用水的定义。
-\AR*{} Overall, this is a quote, but not a word-for-word quote, based on our understanding of a report UNDP participated~\cite{mariajacobson2013}.
-In the background part of the report, three aspects of water governance are put forward, and we summarize them in as ``stress, purpose, and allocation''.
-On the other hand, the expression of ``what, when and how'' are directly derived from this literature, which is also a relatively extensive definition of how water governance affects water use~\cite{lasswell2018,allan2001,mariajacobson2013}.
-Hence, we modified the sentence to:
-
-\begin{quote}[page=2, sline=56, eline=60]
-	In this context, the United Nations Development Programme (UNDP) suggests that water governance determines water usage across three core aspects: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{mariajacobson2013}.
-\end{quote}
-
-\RC{} Line 92: missing information for the citation?
-
-% 谢谢您指出！再次为我们的粗心感到抱歉
-\AR{} Thank you for pointing out! Sorry again for our carelessness. Citations were added in the revised manuscript, now:
-
-\begin{quote}[page=3, sline=108, eline=110]
-	Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.
-\end{quote}
-
-\RC{} Line 94$-$95: the sentence is unclear.
-
-\AR{} Sorry about that, we modified that sentence to:
-
-\begin{quote}[page=3, sline=110, eline=113]
-	However, new challenges such as decreased streamflows and water depletions occurred in more recent times, followed by different water governance practices like water use regulation and water transfer across basins~\cite{wang2019c}.
-\end{quote}
-
-\RC{} Line 121: Repeated citation Qin et al. 2019.
-
-\AR{} Fixed now.
-
-\RC{} Line 122: It would be better to introduce the calculation of SFV in the main text.
-
-\AR{} That's a good suggestion. We now moved the calculation from supplementary material to the main text.
-
-% 为什么分子W uppro不是W Unon-pro?请核对一下方程式。
-\RC{} Equation (6): Why is the numerator WUpro not WUnon-pro? Please check the equation.
-
-\AR{} Thanks for reminding. We used provisioning purpose share in our analysis at last. We forgot to change it's name in texts. We fixed this mistake and everything is coherent now:
-
-\begin{quote}[page=6, sline=157]
-	To quantify purpose $I_P$, we used provisioning purpose shares (PPS) of water use as an indicator.
-While provisioning purpose water use ($WU_{pro}$) includes domestic, irrigated, and livestock water uses, non-provisioning purpose water use ($WU_{non-pro}$) includes industrial and urban services water uses.
-We calculated the PPS by:
-	\begin{equation}
-		PPS = \frac{WU_{pro}}{WU_{pro} + WU_{non-pro}}
-	\end{equation}
-\end{quote}
-
-\RC{} Equation (7): CEM => AEM?\
-
-\AR{} Yep, a typo. We fixed such a stupid mistake now.
-
-\RC{} Line 154: Please explain the source of irrigated area data.
-
-AR{} We cannot dive into every detail of the multi-source datasets in texts, and this dataset is openly published and accessible.
-Overall, the irrigated area data were obtained by statistical approach in this dataset.
-
-\AR*{} We now attached a new supplementary material which includes descriptions and all sources of the datasets used in this study.
-If you want to know more about the data, please check the data source through the provided information.
-
-\RC{} Fig.2A, p<0.01 or p<0.001? (line 147 says that α=0.001 was used for the change-point detection).
-
-\AR{} We used $0.001$ for generating the figure at last (fixed the typo in Fig.2A now).
-Anyway, as we showed in supplementary material Figure~S3, no difference in results because the change points are robust.
-% TODO 检查一下鲁棒性的图表
-
-\RC{} Fig.2C:\ How were the directions determined?
-
-\AR{} We draw the directions for visual convenience.
-Smaller graph is not for quantitatively illustrating.
-The arrow of directions are determined by time: point from earlier data to later data locations.
-
-\RC{} Fig.3C:\ What do the dashed lines denote?
-
-\AR{} Sorry about missing necessary description and we now add a sentence in caption of the Fig.3C:\ ``Dashed lines denote average of these percentages in different regimes''.
-
-\RC{} Line 187: what is ``social transformation''?
-
-\AR{} Sorry about the confused expression. I changed the term into ``Social atmosphere'' now. Maybe this is a better phrase.
-
-\RC{} Line 208: the IWGI was proposed in this study, here the citations of Loch's and Turton's studies are not appropriate.
-
-\AR{} The citations should be put at the first half of the sentence, and we fixed this problem now:
-
-\begin{quote}[page=9, sline=238, eline=240]
-	The process echoes how societies have been proposed to change governance practices by enhancing their adaptive capacity in the hydrosocial cycle~\cite{loch2020,turton1999}, and the IWGI quantitatively identifies this transition.
-\end{quote}
-
-\RC{} Line 273: adapted => adopted?
-
-\AR{} Yep, another typo. We fixed that now.
-
-\RC{} Line 275: biophysical? Please check the sentence.
-
-\AR{} For more clarity, we now changed the sentence to:
-
-\begin{quote}[page=11, sline=330, eline=333]
-	In today's world, regime shifts from natural to human-dominated seem likely to become increasingly widespread; comprehensive strategies to address governance challenges will have to become the core of complex human-water systems~\cite{cumming2018,cumming2014,jaeger2019}.
-\end{quote}
+Page 11, Line 314-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.

### 2023-10-06 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 更新cover letter和给编辑的回复信
docs(paper): :memo: prepare revise the paper

--- 2023-05-12 paper/response_letter/source/reviewer_2.tex
@@
 
-\subsection*{Overall comments}
-% 作者提出了IWGI，并将其应用于黄河流域的水治理历史，分析了流域的制度变迁。该方法具有很强的合理性和适应性，案例分析的结果为理解中国的水治理提供了有益的见解。然而，讨论并没有充分利用案例研究分析的结果。讨论结果的内容应该更具有支持性和可靠性。此外，讨论的叙事分析非常有趣，但如果这项研究的原创性之一是识别变化点，那么就需要更多地讨论导致这些变化点的触发因素。请参考我下面的审稿意见并进行修改，以提高本文的价值。
-\RC{} The authors proposed the IWGI, applied the index to the history of water governance in the Yellow River basin, and analyzed the regime change in the basin.
-The methodology is very reasonable and adaptable, and the results of the case analysis provide useful insights for understanding water governance in China.
-However, the discussion does not fully exploit the results of the case study analysis.
-The discussion should be more supportive and solid in its content of the results.
-Also, the narrative analysis of the discussion is very interesting, but if one of the originalities of this study is the identification of change points, more discussion of the triggers that caused these change points is needed.
-Please refer to my review comments below and revise them to enhance the value of this paper.
+Recommendation (Required): Return to author for minor revisions
+Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.
+Supported: Yes
+Referencing: Yes
+Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.
+Data: Yes
+Accurate Key Points: Yes
 
-\AR{} Thanks!
+\subsection*{General comments}
 
-\subsection{Comment \#1}
-% 图1:很难理解B中每个数字的含义。也许是这个数字的大小有问题。
-\RC{} Figure 1: It is difficult to understand what each number in B means. Perhaps it may be a problem with the size of the figure.
+Thank you for sharing your revised manuscript.
+The revised manuscript was very carefully constructed.
+This revision solved most of my questions, but there were some incomplete and vague parts in the response to "2.7.
+Comment \#7".
 
-\AR{} Thanks for the comment. We now improved the figure in the revised manuscript. % TODO 修改图1让它更清楚
+I agree that the change of the system is still a result of the accumulation of water governance practices in period.
+However, it was clear from your results and discussion that these system changes are dictated by specific factors (historical events): e.g.
+the Chinese slogan "human will conquer nature," rapid expansion of irrigated farmland and water diversion facilities so on, in the P1.
+I suggest that you organize them in a table that shows those factors (historical events) that are causing the "emergence" of each complex system.
+(Figure 4 is too conceptual for the historical phenomenon you were describing.) I believe that this will make the characteristics of each regime clearer.
 
-\subsection{Comment \#2}
-% 导言:与流域和水资源相关的指标有很多，其中一些指标具有与治理和政策相关的参数。为了突出你所制定的IWGI的新颖性，也许你可以加上对其他相关指标的审查。
-\RC{} Introduction: There are many indicators related to watersheds and water resources, some of which have parameters related to governance and policy.
-To highlight the novelty of the IWGI that you have developed, perhaps you could add a review of other relevant indicators.
+The "social atmosphere" is an interesting term, but very vague.
+First of all, please define what it is (I have never heard of such a term in previous studies in my field).
+At the very least, you should discuss what "social atmosphere" is in the Discussion.
+Furthermore, I really wonder how your research and the proposed index can be practically contribute to understanding "the successes and failures of water governanceis" created by the "social atmosphere".
+Perhaps this "social atmosphere" is the most troubling and important factor to understand in water governance regime.
 
-\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:  % TODO 检查引用
+\subsection*{Minor comment}
 
-\begin{quote}
-    Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
-    From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
-    However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
-    A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used.
-% todo cite OECD
-    From the water side, intuitive indexes can provide an embodiment of governance outcomes.
-    Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
-    As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
-    These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
-    Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.
-\end{quote}
-
-\subsection{Comment \#3}
-% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
-\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained.\ e.g. R or WU.\
-
-\AR{} Thanks for the comment. ``CEM'' should be ``AEM'' -the indicator we applied for IA.\ This has been revised in the new manuscript:
-
-\begin{quote}
-    \begin{equation}
-		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
-	\end{equation}
-\end{quote}
-
-\AR*{} Also, sorry about the misunderstanding term. We modified the sentence with ``water proportion'' to:
-
-\begin{quote}
-    where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
-\end{quote}
-
-% 很抱歉关于SFV计算的部分也造成了困惑。实际上我们提到了这些符号的意义，只不过是在所有公式之后。这的确会造成误解，因此在返修后的文章中我们将这段叙述放到了公式之前：
-\AR*{} Sorry that the part about SFV calculation also caused confusion.
-We actually mentioned the meaning of these symbols, but only after all the equations since they shared the same symbols.
-This indeed can be misleading, so in the revised article we put this statement before the formula:
-
-\begin{quote}
-    In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
-\end{quote}
-
-\subsection{Comment \#4}
-% 第2.2节:您提到您将Pettitt(1979)方法应用于“水文时间序列”，但结果似乎适用于IWGI时间序列数据。请说明您将该方法应用于哪些数据。
-\RC{} Section 2.2: You mention that you apply the Pettitt (1979) approach to ``hydrological time series'', but the results appear to be for IWGI time series data.
-Please clarify to which data you applied the approach.
-
-\AR{} Thanks for pointing it out! Pettitt approach was applied to IWGI time series data. We now clarify that in the method section:
-
-\begin{quote}
-    We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
-\end{quote}
-
-\subsection{Comment \#5}
-% 图3:D中哪些类型的官方文件被统计以及如何统计?
-\RC{} Figure 3: What types of official documents in D are counted and how?
-
-% 抱歉之前的手稿中没有更加明确地进行说明，这份文件统计数据源来自黄河的流域管理部门-黄河水利委员会（YRCC），该部门会对黄河相关的“大事”进行记录并编纂发布。本研究仅根据这些“大事”的发生年份进行逐年统计记录数量。
-\AR{} Sorry for not being more explicit in the previous manuscript.
-The document comes from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river.
-This study only recorded the number of these ``events'' year by year according to the time they occurred.
-
-\AR*{} To make that more explicit, we modified the corresponding description in the Supplementary Materials:
-
-\begin{quote}
-    In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
-    The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river.
-This study only recorded the number of these ``events'' year by year according to the time they occurred.
-\end{quote}
-
-\subsection{Comment \#6}
-% 讨论:每个政权的故事都令人印象深刻。然而，结果与图3的关系并不清楚。请通过更直接地引用结果和图3来加强你的论点。
-\RC{} Discussion: The stories of each regime are very impressive.
-However, the relation to the results and Figure 3 is not clear.
-Please strengthen your argument by citing the results and Figure 3 more directly.
-
-\AR{} Thanks for the suggestion. We now append refers in discussion when figure 3 is supporting:
-
-\begin{quote}
-    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
-\end{quote}
-
-\begin{quote}
-    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
-\end{quote}
-
-\begin{quote}
-    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
-\end{quote}
-
-\begin{quote}
-    As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime.
-These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes});
-\end{quote}
-
-\subsection{Comment \#7}
-% 讨论:从您对变更点的分析中可以明显看出，每个制度中都存在变更点。但为什么会出现这些变化“点”呢?是什么导致或触发了它们?这是管理机构的变化还是象征性的政策变化?该制度期间的特征已被很好地描述，但请更多地考虑为什么变化点发生在特定的年份/时期。
-\RC{} Discussion: The existence of change points in each of the regimes is evident from your analysis of the change points.
-But why did these change ``points'' occur?
-What caused or triggered them?
-Was it a change in governing institutions or a symbolic policy change?
-The characteristics during that regime period are well described, but please give more thought to why the change points occurred in that particular year/period.
-
-% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们总体认为制度转变还是一段时间内持续、积累的变化在特定的点产生了统计特征，很难将其总结成某种因素造成的变化。这也是为什么我们要把各种因素考虑在内，构造这样一个综合指数的原因，不是吗？
-\AR{} Thanks to such interesting comments, although the result changes at certain points statistically, we generally believe that the change of the system is still a result of the accumulation of water governance practices in period of time.
-Therefore, it is difficult to summarize it into a change caused by one factor.
-That's why we have to take all these factors into account and construct a composite index like this, right?
-
-% 我们认为这类似于复杂系统的涌现，许多数不胜数的治理措施在不断地提出与执行（正如图3C所示），每一个措施都会针对一个具体的问题，但流域整体将向何处发展取决于这些措施的合力。
-\AR*{} We think of this as analogous to the ``emergence'' of complex systems.
-Numerous practices being proposed and implemented (e.g., basin-scaled practices of the Yellow River as shown in Figure~3C).
-Each practice addresses a specific issue, but how the water governance feature changing overall depends on a combination of their outcomes.
-
-% 当然，并不是说完全无法在特定年份为Regime shift给出解释。在中国的治理模式里，``领会精神''是一个有趣的东西。通常，中央高层会释放一些信号，各级政府（包括部委和地方行政部门）如果按照这种``精神''执行了某种治理措施并取得不错的成果，便是一个非常好的政绩。这种治理模式便是我们在结果、图3、讨论中都提及``social atmosphere''（返修前的手稿我们称之为 social transformation）的原因，这种治理风气会引导治理措施。
-\AR*{} It is not to say that there is absolutely no explanation for Regime shift in a given year.
-In China's governance model, ``central spirit'' is interesting.
-Usually, the top level of the central government sends some signals.
-If governments at all levels (including ministries and local administrative departments) implement certain governance measures in accordance with this ``spirit'' and achieve good results, it will be a good governance.
-This feature is the reason why we mentioned the ``social atmosphere'' (the manuscript before the revision was called social transformation) in the results, Figure 3, and discussion -atmosphere can guide the governance practices.
-
-% 例如在上世纪1960s到1970s，中国在毛泽东领导下有着强烈的``征服自然''风气，这是非常出名的，这种风气能导致建立更多的水库大坝、增大供给。而改革开放带来的阶段二的需求增加、水竞争、效率提升。2000年后中国强调环境治理，等等。可以说我们识别的两次转变都和``social atmosphere''的变化不无关系。但我们很小心的避免了这种归因，因为这种治理转变，绝非单独自上而下的一句口号就能实现的，也有很多其它类似的``中央精神''未能得到有效贯彻执行。
-\AR*{} For instance, the ``reform and opening up'' led to increased water demand, water competition and efficiency in transformation regime.
-After 2000, China emphasized environmental issues \dots It can be said that the two changes we identified are partially related to the change of ``social atmosphere''.
-But we are very careful to avoid this simple attribution, because this change in governance can not be achieved by a top-down slogan alone, and there are many other similar ``central spirit'' has not been effectively implemented.
-
-\AR*{} Taken together, we believe regime shifts are ``emergence'' of the human-water system, but the significant and solid changing points of the YRB can be related to social atmosphere.
-
-\subsection{Comment \#8}
-% 图4:A中的蓝色圆形箭头和B中的红色圆形箭头是什么意思?它们似乎包含了您非常重要的言论，但它们并不清楚。此外，您需要更多地解释A和B中的每个箭头。
-\RC{} Figure 4: What do the blue circular arrows in A and the red circular arrows in B mean?
-They seem to contain your very important remarks, but they are unclear.
-Also, you need to explain more about each of the arrows in A and B.
-
-% 很抱歉之前的手稿造成了此困惑，我们现在在返修后的手稿中增加了以下内容，以便更清晰地说明
-\AR{} I'm sorry for the confusion caused by the previous manuscript. We have now added the following content to the caption of that figure in revised manuscript:
-
-\begin{quote}
-    Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
-    The large circular arrows indicate the social and hydrological processes that dominate in different stages.
-    Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
-    The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
-    The gray thick arrow represents weaker process, while the red arrow represents more significant one.
-\end{quote}
-
-\AR*{} In addition, other two sentences in discussion can make it clearer:
-
-\begin{quote}
-    To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
-    At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
-    With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
-\end{quote}
-
-\subsection{Comment \#9}
-% 结论:对定量分析的结果进行了描述，但是Discussion中的叙事分析似乎没有得到充分的体现。建议对此添加几行。
-\RC{} Conclusion: The results of the quantitative analysis are described, but the narrative analysis in the Discussion does not seem to be fully reflected.
-It is recommended to add a few lines about it.
-
-\AR{} Sure! Thanks for the valuable suggestion. We now added narrative analysis in the discussion to our conclusion:
-
-\begin{quote}
-    During the massive supply regime (P1: $1965 \sim 1978$), water governance tended to boost water supply by constructing reservoirs and channels in the YRB.\
-    Then, the start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use and led to institutional changes like water-saving improvements, water quota policies, and cross-boundary water transfer plans.
-    Last, adaptation-oriented regime (P3: $2002 \sim 2013$) with stable high water stress resulted in trade-offs and joint regulating between water-dependent regions and sectors.
-\end{quote}
+I couldn't access the link http://www.yrcc.gov.cn/hhyl/hhjs/ in the Supporting Informations. Please confirm it.

### 2023-10-06 paper/response_letter/source/reviewer_1.tex
feat(notebooks): :sparkles: check other change points detection techs

@@
 
-The study on water governance stages relies heavily on the integrated index IWGI at the basin scale, which offers significant advantages for decision-making support.
+\RC{} The study on water governance stages relies heavily on the integrated index IWGI at the basin scale, which offers significant advantages for decision-making support.
 Nonetheless, in large basins, the index may obscure crucial details and spatial heterogeneity.
@@
 To improve the discussion on water governance transition, I recommend the authors link the three periods to well-known phenomena or policies, such as the occurrence of zero-flow in the Yellow River.
-Additionally, the current separation of periods using the Pettitt method for change point detection could be improved or compared to other methods, considering its sensitivity to time series changes.
+
+\AR{} We sincerely appreciate your constructive feedback and acknowledgment of our work.
+We concur that the IWGI index is designed to provide an overall understanding of the basin, and in this process, some spatial heterogeneity may indeed be overlooked.
+
+\AR*{} We would like to clarify that our intention in averaging water stress across the basin is not to obscure specific areas of concern but to provide a comprehensive view that can strongly support decision-making.
+We recognize that in a large basin like the Yellow River, disparities in water stress exist.
+However, these disparities, where one area might experience high water stress while another experiences low, can influence water allocation and management strategies, thus are crucial to capture at a macro level.
+
+\RC{} Additionally, the current separation of periods using the Pettitt method for change point detection could be improved or compared to other methods, considering its sensitivity to time series changes.
+
+\AR{} Regarding the separation of periods using the Pettitt method for change point detection, we have taken your feedback into account.
+To address this, we have incorporated results from other change point detection techniques to demonstrate the robustness of our stage delineations, particularly in the context of the Yellow River basin.
+The updated results indicate a consistent pattern, reaffirming the credibility of our initial findings:
+
+\begin{quote}
+	The results from the Pettitt method are robust to the inclusion of other change point detection techniques.
+\end{quote}
 

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
feat(paper): :memo: writing updated docs for the different change points detection methods

@@
 Nonetheless, in large basins, the index may obscure crucial details and spatial heterogeneity.
-For instance, averaging the water stress of areas with and without water stress could lead to a misleading "no water stress" result.
+For instance, averaging the water stress of areas with and without water stress could lead to a misleading ``no water stress'' result.
 To improve the discussion on water governance transition, I recommend the authors link the three periods to well-known phenomena or policies, such as the occurrence of zero-flow in the Yellow River.
@@
 To address this, we have incorporated results from other change point detection techniques to demonstrate the robustness of our stage delineations, particularly in the context of the Yellow River basin.
-The updated results indicate a consistent pattern, reaffirming the credibility of our initial findings:
+The updated results indicate a consistent pattern, reaffirming the credibility of our initial findings.
+
+Specifically, we employed the Generalized ESD Test, Dynamic Programming, Binary Segmentation, and Bottom-Up Segmentation methods to identify the change points in our index.
+The Generalized ESD Test, which does not require the pre-specification of the number of change points, identified three significant points: 1975, 1978, and 2000.
+On the other hand, Dynamic Programming, Binary Segmentation, and Bottom-Up Segmentation, which require the pre-specification of the number of change points, consistently pointed to 1975 and 2000.
+
+We observed that the first change point identified by the Generalized ESD Test is close to 1975 and 1978.
+After careful consideration, we opted for 1978 as the first change point to ensure that the total number of years across the three identified periods is more balanced.
+This decision aligns with our objective to provide a more comprehensive and equitable analysis of the different time frames, thereby enhancing the robustness and reliability of our findings.
 
 \begin{quote}
-	The results from the Pettitt method are robust to the inclusion of other change point detection techniques.
+	We have also employed a series of popular breakpoint detection methods to validate the results obtained through the Pettitt test.
+The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table S2.
+A consensus was observed among all methods regarding the identification of the second breakpoint, which consistently emerged around the year 2000.
+There was a minor variation of three years in the identification of the first breakpoint, pinpointed either in 1975 or 1978.
+
+	% 我们综合考虑每个时间段的年份数量后，选择了较为居中的、识别出1977年作为第一个断点的 Pettitt 方法。但可以看得出，本研究所依赖的断点识别结果，对于算法选择的鲁棒性也足够强。
+	After a thorough evaluation, we opted for the Pettitt method, which identified 1977 as the first breakpoint.
+This decision was influenced by our intent to ensure a balanced distribution of the number of years across each identified period.
+The consistency in the identification of breakpoints, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the breakpoint detection algorithm.
+This robustness reinforces the credibility and reliability of our analyses and conclusions, reflecting the methodological rigor embedded in our study.
 \end{quote}
+
+We believe that the consistency in the change points identified by different methods, despite their varied approaches and assumptions, underscores the robustness of our period delineations.
+We have included these additional analyses in the revised manuscript to offer a more comprehensive view and address any concerns regarding the sensitivity of our results to the change point detection method employed.
+
+We hope this clarification and the additional analyses sufficiently address your concern, and we are open to further discussions to enhance the quality of our work.
 
@@
 
-Page 10, Line 265-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
+Page 10, Line 265\-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
 Furthermore, since 2000, zero-flow has not reappeared, which could be accounted for in the analysis.
 
-Page 11, Line 308: Could you elaborate on "manage natural water processes"?
+Page 11, Line 308: Could you elaborate on ``manage natural water processes''?
 
-Page 11, Line 313-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
+Page 11, Line 313\-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
 
-Page 11, Line 314-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.
+Page 11, Line 314\-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.

### 2023-10-07 paper/sup/04_robustness.tex
feat(paper): :memo: writing updated docs for the different change points detection methods

@@
 Our results that only two mutation points (1978 and 2001) could be identified at the confidence level of $0.0005$ to $0.05$ (Figure~\ref{fig:sensitivity}).
+
+% 我们同样使用一些流行的断点识别方法检验了Pettitt的断点识别结果。它们的名称、结果、参考论文可以在表中找到。所有的结果在第二个断点的识别上几乎是一致的（2000年），而第一个断点也仅有3年的差异（1975年与1978年）。
+We have also employed a series of popular breakpoint detection methods to validate the results obtained through the Pettitt test.
+The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~\ref{table:breakpoint-detection-methods}.
+A consensus was observed among all methods regarding the identification of the second breakpoint, which consistently emerged around the year 2000.
+There was a minor variation of three years in the identification of the first breakpoint, pinpointed either in 1975 or 1978.
+
+% 我们综合考虑每个时间段的年份数量后，选择了较为居中的、识别出1977年作为第一个断点的 Pettitt 方法。但可以看得出，本研究所依赖的断点识别结果，对于算法选择的鲁棒性也足够强。
+After a thorough evaluation, we opted for the Pettitt method, which identified 1977 as the first breakpoint.
+This decision was influenced by our intent to ensure a balanced distribution of the number of years across each identified period.
+The consistency in the identification of breakpoints, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the breakpoint detection algorithm.
+This robustness reinforces the credibility and reliability of our analyses and conclusions, reflecting the methodological rigor embedded in our study.
+
+\input{tab_robustness.tex}
+
 % 此外，我们讨论了在指标中没有体现的水库流量变化，在所有水库（图 x）中，我们分析了10个先后建成的枢纽水库，发现水库在 governance transforming regime 之后开始增强其调度的水平

### 2023-10-07 paper/sup/tab_robustness.tex
feat(paper): :memo: writing updated docs for the different change points detection methods

\begin{table}[h!]
    \centering
    \begin{tabularx}{\textwidth}{llll}
        \toprule
        \textbf{Method} & \textbf{Breakpoints} & \textbf{Parameters$^*$} & \textbf{Reference} \\
        \midrule
        Generalized ESD Test & 1975, 1978, 2001 & No & \cite{matteson2014} \\
        Pettitt Method & 1977, 2000 & No & \cite{pettitt1979} \\
        Pelt & 1975, 2000 & $pen=0.05$ & \cite{killick2012} \\
        Binary Segmentation & 1975, 2000 & $bkp=2$ & \cite{bai1997} \\
        Bottom-Up Segmentation & 1975, 2000 & $bkp=2$ & \cite{keogh2001} \\
        \bottomrule
    \end{tabularx}
    \footnotesize{$pen$: Penalty coefficient; $bkp$: Number of breakpoints. $No$: Non-parametric test.}
    \caption{Comparison of different breakpoints detection methods}\label{table:breakpoint-detection-methods}
\end{table}

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
docs(paper): :memo: response the comment of weighted average

@@
 
-We believe that the consistency in the change points identified by different methods, despite their varied approaches and assumptions, underscores the robustness of our period delineations.
+\AR*{} We believe that the consistency in the change points identified by different methods, despite their varied approaches and assumptions, underscores the robustness of our period delineations.
 We have included these additional analyses in the revised manuscript to offer a more comprehensive view and address any concerns regarding the sensitivity of our results to the change point detection method employed.
 
-We hope this clarification and the additional analyses sufficiently address your concern, and we are open to further discussions to enhance the quality of our work.
+\AR*{} We hope this clarification and the additional analyses sufficiently address your concern, and we are open to further discussions to enhance the quality of our work.
 
@@
 
-Equation (5): Would adopting an area-weighted average be more appropriate in Equation (5)?
+\RC{} Equation (5): Would adopting an area-weighted average be more appropriate in Equation (5)?
 This change could offer a more accurate representation of the data, especially when considering the variations in water stress across different areas within the basin.
 
-Page 5: I guess WUi,j reflects water use (or water withdrawal) rather than water consumption.
+\AR{} We are grateful for your insightful suggestion regarding the incorporation of area-weighted averages in Equation (5).
+In our current study, we have adhered strictly to the algorithm proposed by Qin et al., which does not employ any weighting scheme.
+Our objective is to maintain consistency and avoid introducing additional complexities that could potentially lead to confusion in the interpretation of our results.
 
-Page 10, Line 265\-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
+\AR*{} However, we acknowledge the potential benefits of incorporating a weighting factor to account for the variations in water stress across different areas within the basin.
+In future studies, considering weights such as population or other socio-economic indicators might indeed be more appropriate.
+The underlying rationale would be that areas with higher populations facing water stress indicate a more severe shortage of water resources.
+
+\AR*{} This could represent a significant enhancement to the SFV index, offering a more nuanced and comprehensive representation of water stress at the basin scale.
+We are genuinely appreciative of your suggestion and are considering integrating this improvement in our subsequent works focusing on the refinement of the SFV index.
+
+\RC{} Page 5: I guess WUi,j reflects water use (or water withdrawal) rather than water consumption.
+
+\RC{} Page 10, Line 265\-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
 Furthermore, since 2000, zero-flow has not reappeared, which could be accounted for in the analysis.
 
-Page 11, Line 308: Could you elaborate on ``manage natural water processes''?
+\RC{} Page 11, Line 308: Could you elaborate on ``manage natural water processes''?
 
-Page 11, Line 313\-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
+\RC{} Page 11, Line 313\-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
 
-Page 11, Line 314\-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.
+\RC{} Page 11, Line 314\-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.

### 2023-10-07 paper/main/02_methods.tex
fix(paper): :pencil2: water consumption -> water use

@@
 
-	First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Supporting Information Section S1}):
+	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Supporting Information Section S1}):
 	\begin{equation}

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
fix(paper): :pencil2: water consumption -> water use

@@
 
+% 我们非常感谢你方对细节的关注和对我方术语的更正。我们已经复习了有问题的部分，并修改了术语，以确保我们的陈述准确和清晰。
+\AR{} We greatly appreciate your attention to detail and the correction you provided regarding our terminology.
+We have reviewed the section in question and have amended the terminology to ensure precision and clarity in our presentation:
+
+\begin{quote}
+	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ \dots
+\end{quote}
+
 \RC{} Page 10, Line 265\-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.

### 2023-10-07 paper/main/04_discussion.tex
docs(paper): :pencil2: delete the expression of lower stress in P1

@@
 In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
-During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+During the massive supply regime ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
 As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
docs(paper): :pencil2: delete the expression of lower stress in P1

@@
 
+% 1. 首先感谢指出这个表述问题，这确实造成了误解。
+% 2. 其次，第一阶段确实出现了断流，但正如下图所展示的，断流的天数和长度都还偏小。第一阶段确实相对来说已经是压力比较小的，但增大的太过迅速。
+% 3. 正如我们在新增的不同断点识别方法所诊断出的第一阶段结束在 1975-1978之间，而第一次出现断流的时间是1973年。就我们研究的时间尺度来说，已经是比较接近的识别了。但数据限制，没有办法非常完全准确到第一阶段没有断流。
+% 4. 总的来说，第一阶段相对其他时期压力并不算大，但压力增速极大，导致第一阶段末出现断流现象。我们已经删除了容易歧义的表述。
+\AR{} We extend our sincere gratitude for highlighting the inconsistency in our description.
+We acknowledge that our previous phrasing may have led to misunderstandings.
+We have taken the liberty to revise our manuscript, eliminating ambiguous phrases to ensure clarity and accuracy in paper.
+
+\AR*{} We recognize that zero-flow events occurred during the first stage.
+However, both the duration and frequency of these events were relatively minor (worst in 1990s).
+While the water stress was indeed lower during this period, the rapid increase in stress levels was a significant concern.
+
+\AR*{} With the introduction of additional breakpoint detection methods in our revised manuscript, we observed that the first stage ends between 1975 and 1978, aligning closely with the onset of zero-flow events in 1973.
+Given the temporal scale of our study and the limitations inherent in the available data, this alignment is reasonably accurate.
+
+\AR*{} In summation, while the water stress during the first stage was not as pronounced as in subsequent periods, the accelerated rate of increase in stress levels culminated in zero-flow events towards the end of this stage.
+
 \RC{} Page 11, Line 308: Could you elaborate on ``manage natural water processes''?

### 2023-10-07 paper/main/04_discussion.tex
fix(paper): :pencil2: natural water processes -> natural water cycle

@@
 In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
+To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water cycle in order to maintain the provisioning (larger) and non-provisioning water (less).
 At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.

### 2023-10-07 paper/main/04_discussion.tex
docs(paper): :memo: update discussion according to R1's suggestion

@@
 With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
-In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
-Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
+% 在黄河流域具体来说，其表现为国家的宣传口号从战胜自然和保护环境变成了人水和谐，但仍不得不用行政手段处理用水争端
+The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
+It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
 Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
fix(paper): :pencil2: natural water processes -> natural water cycle
docs(paper): :memo: update discussion according to R1's suggestion

@@
 
+\AR{} Thank you for bringing to our attention the ambiguity associated with the term ``natural water processes''.
+To enhance clarity and precision, we have revised this phrase to ``natural water cycle'' in our updated manuscript.
+
 \RC{} Page 11, Line 313\-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
 
+\AR{} We have incorporated the specific examples you suggested into the revised manuscript to provide a clearer illustration of the water governance transition in the Yellow River basin.
+We are grateful for your insightful recommendation.
+
+\begin{quote}
+	% 以黄河流域所面临的挑战为例，国家叙事从经济征服自然、消除污染到强调人水和谐的转变，增加了行政措施在解决与水有关的纠纷中的重要性。
+	The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
+\end{quote}
+
 \RC{} Page 11, Line 314\-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.
+
+\AR{} We have reviewed and carefully considered your feedback.
+We have removed the statements that were not strongly correlated with the core content of our study.
+After then, we linked the YRB's example by the interpretation:
+
+\begin{quote}
+	% 它再次表明，高度控制和开发的流域(特别是跨界河流)必须解决结构性挑战，例如水争端或缺乏公平，并且可能迫切需要新的灵活、有效的社会政治治理结构。
+	It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures.
+\end{quote}

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
docs(paper): :art: format of response letters

@@
 
-Reviewer \#1 Evaluations:
-Recommendation (Required): Return to author for minor revisions
-Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.
-Supported: Mostly yes, but some further information and/or data are needed.
-Referencing: Yes
-Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.
-Data: Yes
-Accurate Key Points: Yes
+\subsection*{Reviewer \#1 Evaluations:}
+
+\begin{itemize}
+	\item Recommendation (Required): Return to author for minor revisions
+	\item Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.
+	\item Supported: Mostly yes, but some further information and/or data are needed.
+	\item Referencing: Yes
+	\item Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.
+	\item Data: Yes
+	\item Accurate Key Points: Yes
+\end{itemize}
 

### 2023-10-07 paper/response_letter/source/reviewer_2.tex
docs(paper): :art: format of response letters

@@
 
-Recommendation (Required): Return to author for minor revisions
-Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.
-Supported: Yes
-Referencing: Yes
-Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.
-Data: Yes
-Accurate Key Points: Yes
+\subsection*{Reviewer \#2 Evaluations:}
+
+\begin{itemize}
+    \item Recommendation (Required): Return to author for minor revisions
+    \item Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.
+    \item Supported: Yes
+    \item Referencing: Yes
+    \item Quality: Yes, it is well-written, logically organized, and the figures and tables are appropriate.
+    \item Data: Yes
+    \item Accurate Key Points: Yes
+\end{itemize}
 
@@
 
-Thank you for sharing your revised manuscript.
+\RC{} Thank you for sharing your revised manuscript.
 The revised manuscript was very carefully constructed.
-This revision solved most of my questions, but there were some incomplete and vague parts in the response to "2.7.
-Comment \#7".
+This revision solved most of my questions, but there were some incomplete and vague parts in the response to ``2.7.
+Comment \#7''.
 
-I agree that the change of the system is still a result of the accumulation of water governance practices in period.
-However, it was clear from your results and discussion that these system changes are dictated by specific factors (historical events): e.g.
-the Chinese slogan "human will conquer nature," rapid expansion of irrigated farmland and water diversion facilities so on, in the P1.
-I suggest that you organize them in a table that shows those factors (historical events) that are causing the "emergence" of each complex system.
+\RC*{} I agree that the change of the system is still a result of the accumulation of water governance practices in period.
+However, it was clear from your results and discussion that these system changes are dictated by specific factors (historical events): e.g., the Chinese slogan ``human will conquer nature'', rapid expansion of irrigated farmland and water diversion facilities so on, in the P1.
+I suggest that you organize them in a table that shows those factors (historical events) that are causing the ``emergence'' of each complex system.
 (Figure 4 is too conceptual for the historical phenomenon you were describing.) I believe that this will make the characteristics of each regime clearer.
 
-The "social atmosphere" is an interesting term, but very vague.
+\RC{} The ``social atmosphere'' is an interesting term, but very vague.
 First of all, please define what it is (I have never heard of such a term in previous studies in my field).
-At the very least, you should discuss what "social atmosphere" is in the Discussion.
-Furthermore, I really wonder how your research and the proposed index can be practically contribute to understanding "the successes and failures of water governanceis" created by the "social atmosphere".
-Perhaps this "social atmosphere" is the most troubling and important factor to understand in water governance regime.
+At the very least, you should discuss what ``social atmosphere'' is in the Discussion.
+Furthermore, I really wonder how your research and the proposed index can be practically contribute to understanding ``the successes and failures of water governanceis'' created by the ``social atmosphere''.
+Perhaps this ``social atmosphere'' is the most troubling and important factor to understand in water governance regime.
 
@@
 
-I couldn't access the link http://www.yrcc.gov.cn/hhyl/hhjs/ in the Supporting Informations. Please confirm it.
+\RC{} I couldn't access the link http://www.yrcc.gov.cn/hhyl/hhjs/ in the Supporting Informations. Please confirm it.

### 2023-10-08 paper/main/01_introduction.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

@@
 Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016}.
-Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.
+Governance challenges induced by environmental
+, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.
 Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

### 2023-10-08 paper/main/03_results.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

@@
 		The size of each circle indicates the magnitude of its water storage capacity.
-		\textbf{D.} Social atmosphere (red triangles) and national-level governance policies (the circles, different colours denote signed by different state agencies).
+		\textbf{D.} Social atmosphere$^*$ (red triangles) and national-level governance policies (the circles, different colours denote signed by different state agencies).
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
+		\footnotesize{$^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.}
 	}\label{fig:Causes}
@@
 % 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
-Environmental context, social atmosphere, and policies played roles in all three periods.
+Environmental and social contexts, governance policies played roles in all three periods.
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S7).
-% todo 检查图引用
+Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S8).
 Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$).

### 2023-10-08 paper/main/04_discussion.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

@@
 % 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
-In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
-During the massive supply regime ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI} and Table~\ref{tab:regimes}).
+These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres in China (Table~\ref{tab:regimes}).
+The social atmospheres refers to the sociocultural context in which people live or in which something happens, underlying the direction of practices of water governance during a regime, despite lack of strict causality evidence.
+
+During the massive supply regime ($1965 \sim 1978$ in the YRB), water governance tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
 As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
@@
 In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.
+
+\input{tab_regimes.tex}
 

### 2023-10-08 paper/main/tab_regimes.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
    \centering
    \caption{Brief summary of regime transitions for water governance at the Yellow River Basin}
      \begin{tabularx}{\textwidth}{p{0.15\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.5\textwidth}}
      \toprule
      Time  & Closet social atmosphere$^*$ & Regime & Main trait \\
      \midrule
      $1965-1978$ & 1960s: Conquering nature & massive supply regime & boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels \\
      $1979-2001$ & 1978: reform and opening-up & governance transforming regime & triggered institutional changes for rapid enhancement of overall social adaptive capacity to severe water stresses \\
      $2002-2013$ & 2002: Environmental regulating & adaptation-oriented regime & adapting to stable high water stress with trade-offs between water-dependent regions and sectors \\
      \bottomrule
      \end{tabularx}\label{tab:regimes}%

      \footnotesize
      $^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
  \end{table}%

### 2023-10-08 paper/response_letter/source/reviewer_1.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

@@
 
-\RC{} Page 10, Line 265\-266: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
+\RC{} Page 10, Line $265-266$: It is crucial to rectify the statement claiming lower water stress during Period 1 (P1) as it contradicts the occurrence of zero-flow in the river five times between 1972 and 1978, with an average duration of 13 days per occurrence.
 Furthermore, since 2000, zero-flow has not reappeared, which could be accounted for in the analysis.
@@
 
-\RC{} Page 11, Line 313\-314: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
+\RC{} Page 11, Line $313-314$: For better comprehension, consider listing some of the environmental, economic, social, and policy challenges faced during the various water governance stages.
 
@@
 
-\RC{} Page 11, Line 314\-317: Please clarify the purpose of this sentence to ensure its relevance to the discussion.
+\RC{} Page 11, Line $314-317$: Please clarify the purpose of this sentence to ensure its relevance to the discussion.
 

### 2023-10-08 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

@@
 
+\AR{} Thank you for raising an intriguing point of discussion on the concept of ``social atmosphere''.
+We have taken your feedback into account and provided a definition in the revised manuscript to elucidate this term:
+
+\begin{quote}
+    Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
+\end{quote}
+
+\AR*{} We maintain a cautious stance regarding the assertion that changes in the ``social atmosphere'' directly lead to shifts in stable states, as our findings do not establish a causal relationship between the two.
+Nevertheless, as depicted in the newly added Table~1, prompted by your suggestion, a temporal co-occurrence between the two is observable.
+We discussed it more in the revised manuscript:
+
+\begin{quote}
+    These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres (Table~1).
+    The social atmospheres refers to the sociocultural context in which people live or in which something happens, underlying the direction of practices of water governance during a regime, despite lack of strict causality evidence.
+\end{quote}
+
+\AR*{} The evolution of the ``social atmosphere'' could potentially be a consequence of changes in human-water relations or a catalyst for such transformations.
+We appreciate your perspective that this shift might represent a breakthrough in addressing complex challenges in future studies.
+We have enriched our discussion with additional insights to reflect on this complex interplay.
+However, for the scope of this current study, the evidence at our disposal does not permit an extensive exploration centered on this aspect.
+It's interesting to delve deeper into this intricate relationship in our future work, backed by comprehensive data and analyses.
+
 \subsection*{Minor comment}
@@
 \RC{} I couldn't access the link http://www.yrcc.gov.cn/hhyl/hhjs/ in the Supporting Informations. Please confirm it.
+
+\AR{} Sorry to hear that.
+However, we double-checked that this link is still accessible.
+It's a page from the official website of Yellow River Conservancy Commission (YRCC).
+We also uploaded the dataset ``big\_events.csv'' of the web page is made by using the web crawler in the open-sourced Zenodo repo.

### 2023-10-08 paper/sup/tab_robustness.tex
docs(paper): :memo: reviewer #2 social atmosphere related changes

@@
         Generalized ESD Test & 1975, 1978, 2001 & No & \cite{matteson2014} \\
-        Pettitt Method & 1977, 2000 & No & \cite{pettitt1979} \\
+        Pettitt Method & 1978, 2001 & No & \cite{pettitt1979} \\
         Pelt & 1975, 2000 & $pen=0.05$ & \cite{killick2012} \\

### 2023-10-08 paper/response_letter/source/reviewer_1.tex
fix(paper): :memo: adding reform reason
according Shuai Wang's suggestion, adding a new reason for the method choice.

@@
 \begin{quote}
-	We have also employed a series of popular breakpoint detection methods to validate the results obtained through the Pettitt test.
-The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table S2.
-A consensus was observed among all methods regarding the identification of the second breakpoint, which consistently emerged around the year 2000.
-There was a minor variation of three years in the identification of the first breakpoint, pinpointed either in 1975 or 1978.
+	% 我们同样使用一些流行的断点识别方法检验了Pettitt的断点识别结果。它们的名称、结果、参考论文可以在表中找到。所有的结果在第二个断点的识别上几乎是一致的（2000年），而第一个断点也仅有3年的差异（1975年与1978年）。
+	We have also employed a series of popular change point detection methods to validate the results obtained through the Pettitt test.
+The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~\ref{table:breakpoint-detection-methods}.
+A consensus was observed among all methods regarding the identification of the second change point, which consistently emerged around the year 2000.
+There was a minor variation of three years in the identification of the first change point, pinpointed either in 1975 or 1978.
 
 	% 我们综合考虑每个时间段的年份数量后，选择了较为居中的、识别出1977年作为第一个断点的 Pettitt 方法。但可以看得出，本研究所依赖的断点识别结果，对于算法选择的鲁棒性也足够强。
-	After a thorough evaluation, we opted for the Pettitt method, which identified 1977 as the first breakpoint.
-This decision was influenced by our intent to ensure a balanced distribution of the number of years across each identified period.
-The consistency in the identification of breakpoints, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the breakpoint detection algorithm.
+	After a thorough evaluation, we opted for the Pettitt method, which identified 1978 as the first change point.
+This decision was based on two intents: (1) to ensure a balanced distribution of the number of years across each identified period (2) to stress the big change of China governance: ``reform and opening-up''.
+The consistency in the identification of breakpoints, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the change point detection algorithm.
 This robustness reinforces the credibility and reliability of our analyses and conclusions, reflecting the methodological rigor embedded in our study.

### 2023-10-08 paper/sup/04_robustness.tex
fix(paper): :memo: adding reform reason
according Shuai Wang's suggestion, adding a new reason for the method choice.

--- 2023-05-15 paper/sup/04_robustness.tex
@@
 Our results that only two mutation points (1978 and 2001) could be identified at the confidence level of $0.0005$ to $0.05$ (Figure~\ref{fig:sensitivity}).
+
+% 我们同样使用一些流行的断点识别方法检验了Pettitt的断点识别结果。它们的名称、结果、参考论文可以在表中找到。所有的结果在第二个断点的识别上几乎是一致的（2000年），而第一个断点也仅有3年的差异（1975年与1978年）。
+We have also employed a series of popular change point detection methods to validate the results obtained through the Pettitt test.
+The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~\ref{table:breakpoint-detection-methods}.
+A consensus was observed among all methods regarding the identification of the second change point, which consistently emerged around the year 2000.
+There was a minor variation of three years in the identification of the first change point, pinpointed either in 1975 or 1978.
+
+% 我们综合考虑每个时间段的年份数量后，选择了较为居中的、识别出1977年作为第一个断点的 Pettitt 方法。但可以看得出，本研究所依赖的断点识别结果，对于算法选择的鲁棒性也足够强。
+After a thorough evaluation, we opted for the Pettitt method, which identified 1978 as the first change point.
+This decision was based on two intents: (1) to ensure a balanced distribution of the number of years across each identified period (2) to stress the big change of China governance: ``reform and opening-up''.
+The consistency in the identification of breakpoints, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the change point detection algorithm.
+This robustness reinforces the credibility and reliability of our analyses and conclusions, reflecting the methodological rigor embedded in our study.
+
+\input{tab_robustness.tex}
+
 % 此外，我们讨论了在指标中没有体现的水库流量变化，在所有水库（图 x）中，我们分析了10个先后建成的枢纽水库，发现水库在 governance transforming regime 之后开始增强其调度的水平

### 2023-10-10 paper/diff/manuscript_v-8.3.0.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

--- 2023-05-31 paper/diff/v-8.2.3.tex
@@
 \usepackage{amsmath}
+\usepackage{tabularx}
+\usepackage{booktabs}
 \usepackage{pifont}  \linenumbers
@@
 
-Environmental context, social atmosphere, and policies played roles in all three periods.
+Environmental and social contexts, governance policies played roles in all three periods.
 We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
 Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
-Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S7).
+Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supporting Informations Figure~S8).
 Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$).
@@
 
-In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
-During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
+In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI} and Table~\ref{tab:regimes}).
+These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres in China (Table~\ref{tab:regimes}).
+The social atmospheres refers to the sociocultural context in which people live or in which something happens, underlying the direction of practices of water governance during a regime, despite lack of strict causality evidence.
+
+During the massive supply regime ($1965 \sim 1978$ in the YRB), water governance tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
 As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
@@
 
+\begin{table}[htbp]
+    \centering
+    \caption{Brief summary of regime transitions for water governance at the Yellow River Basin}
+      \begin{tabularx}{\textwidth}{p{0.15\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.5\textwidth}}
+      \toprule
+      Time  & Closet social atmosphere$^*$ & Regime & Main trait \\
+      \midrule
+      $1965-1978$ & 1960s: Conquering nature & massive supply regime & boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels \\
+      $1979-2001$ & 1978: reform and opening-up & governance transforming regime & triggered institutional changes for rapid enhancement of overall social adaptive capacity to severe water stresses \\
+      $2002-2013$ & 2002: Environmental regulating & adaptation-oriented regime & adapting to stable high water stress with trade-offs between water-dependent regions and sectors \\
+      \bottomrule
+      \end{tabularx}\label{tab:regimes}
+
+      \footnotesize
+      $^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
+  \end{table}
 The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
@@
 In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
-To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
+To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water cycle in order to maintain the provisioning (larger) and non-provisioning water (less).
 At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
 With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
-In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
-Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
+The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
+It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
 Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

### 2023-10-10 paper/letter/cover_letter_r2.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

--- 2023-05-15 paper/letter/cover_letter_r1.tex
@@
 
-Thank you for the opportunity to revise our manuscript titled ``Identifying regime transitions for water governance at a basin scale'' We appreciate the constructive feedback provided by the reviewers and believe that our revised manuscript more effectively addresses their concerns.
+% 我们写信是为了提交我们的手稿的修订版，题为“确定中国黄河流域水治理的政权过渡”，供您和审稿人考虑。我们非常感谢审稿人提供的建设性意见，这些意见有助于提高我们工作的质量和清晰度。
+We are writing to submit the revised version of our manuscript titled ``Identifying regime transitions for water governance at the Yellow River Basin, China'' for your and the reviewers’ consideration.
+We are grateful for the constructive feedback provided by the reviewers, which has been instrumental in enhancing the quality and clarity of our work.
 
-% 很抱歉我们花了这么长时间来返修，但正如您看到的，我们在新的版本中补充了很多内容和图表，努力回应审稿人和编辑的一切关切。我们也花时间试着联系了数据的作者团队。在得知正文中数据短时间内无法增补到最新年份后，我们使用其它数据源再次计算了IWGI，从而努力增强结果的鲁棒性。
-I'm sorry it took us so long to go back, but as you can see, we've added a lot of content and graphics to the new version in an effort to respond to all the concerns of reviewers and editors.
-We also took the time to try to contact the team that authored the data.
-After learning that the data in the text could not be updated to the latest year for a short time, we supplement analysis using other data sources in an effort to enhance the robustness of the results.
-In response to the reviewers' feedback, we also restructured the introduction and discussion sections to provide a more supportive and solid content of the results.
+One of the significant revisions in our manuscript involves the robustness check for the identified breakpoints in our study.
+Furthermore, we have addressed all the specific comments and suggestions raised by the reviewers meticulously.
+We introduced a new table and expanded the discussion to provide more comprehensive insights.
+These clarifications and modifications made in response to both reviewers’ inputs, have significantly enriched the content and narrative of our manuscript.
 
-We believe that these revisions have significantly improved the quality and value of our manuscript, and we hope that you will find it suitable for publication in Water Resources Research.
-We are confident that our study makes a valuable contribution to the understanding of water governance in China and beyond.
+We believe that these revisions have addressed the reviewers’ concerns effectively and hope that the enhancements made will meet their expectations and standards of quality for publication in \textit{Water Resources Research}.
 
-The revised manuscript includes the main body of text with $4423$ words and $4$ figures; the supporting information with $4$ sections has $9$ supporting figures and $1$ supporting tables.
+The revised manuscript includes the main body of text with $4423$ words and $4$ figures with $1$ table; the supporting information with $4$ sections has $9$ supporting figures and $2$ supporting tables.
 Furthermore, we declare no conflicts of interest to disclose.
@@
 
-Email: bfu@rcees.ac.cn
+Email: shuaiwang@bnu.edu.cn
 

### 2023-10-10 paper/response_letter/source/editor.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

@@
 \subsection{Remarks to Author}
+
 \RC{} Dear Authors, thank you for the carful revisions.
@@
 
+\AR{} Thank you for your constructive comments and for providing us with the opportunity to address the concerns raised by both reviewers.
+We appreciate the valuable feedback, which has helped us identify areas for improvement in our manuscript.
+We have carefully considered each point and have made substantial revisions to address these issues.
+Please find our detailed responses to the highlighted concerns below.
+
 \RC{} As Reviewer \#1 pointed out, there needs to be more carful evaluation of the method with water stress calculation, which would affect part of the outcome.
 
-\AR{}
+\AR{} Thanks for the suggestion.
+We have employed various change points detection methods, demonstrating that our results are robust and consistent.
+The inclusion of these additional methods underscores the validity of our initial findings and strengthens the overall credibility of our research.
 
@@
 
-\AR{} Thank you for your constructive comments and for providing us with the opportunity to address the concerns raised by both reviewers.
-We appreciate the valuable feedback, which has helped us identify areas for improvement in our manuscript.
-We have carefully considered each point and have made substantial revisions to address these issues.
-Please find our detailed responses to the highlighted concerns below.
+\AR{} Thanks for the comments. We now improved the clarity of discussion with a new table, and double-checked accessibility of the link.
 

### 2023-10-10 paper/response_letter/source/reviewer_1.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

@@
 
-\begin{quote}
+\begin{quote}[page=Supporting Informations]
 	% 我们同样使用一些流行的断点识别方法检验了Pettitt的断点识别结果。它们的名称、结果、参考论文可以在表中找到。所有的结果在第二个断点的识别上几乎是一致的（2000年），而第一个断点也仅有3年的差异（1975年与1978年）。
@@
 
-\begin{quote}
+\begin{quote}[page=5, sline=158, eline=160]
 	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ \dots
@@
 
-\begin{quote}
+\begin{quote}[page=11, sline=320, eline=323]
 	% 以黄河流域所面临的挑战为例，国家叙事从经济征服自然、消除污染到强调人水和谐的转变，增加了行政措施在解决与水有关的纠纷中的重要性。
@@
 
-\begin{quote}
+\begin{quote}[page=11, sline=323, eline=326]
 	% 它再次表明，高度控制和开发的流域(特别是跨界河流)必须解决结构性挑战，例如水争端或缺乏公平，并且可能迫切需要新的灵活、有效的社会政治治理结构。

### 2023-10-10 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: response letter finished
give Shuai Wang for some feedback

@@
 
-\begin{quote}
+\begin{quote}[page=footnotes from Figure~3 and Table~1]
     Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
@@
 
-\begin{quote}
+\begin{quote}[page=10, sline=265, eline=269]
     These regime shifts, as comprehensive outcomes of complex human-water interactions, are coincidentally well presented by several well-known and dominated social atmospheres (Table~1).

### 2023-10-10 paper/main/02_methods.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
 	% 这个指数得到了许多应用，是就我们已知范围内考虑因素最为齐全的，反应水资源压力的指数。
-	The SFV-index, which has many applications, is the most comprehensive index of water stress we know. % todo citation
+	The SFV-index, which has many applications, is the most comprehensive index of water stress we know~\cite{qin2019}.
 
@@
 We divided the series into two at that point and analyzed each series separately until all significant change points were detected.
-Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see Figure~S6).
+Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the change points we identified are robust (see Figure~S6).
 

### 2023-10-10 paper/main/03_results.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
 % 这一节主要展示IWGI的变化趋势和WUR的划分
-Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
+Two significant change points divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
 % 第一阶段
@@
 The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
-		\footnotesize{$^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.}
+		\footnotesize{$^*$ Here, ``social atmosphere'' refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.}
 	}\label{fig:Causes}

### 2023-10-10 paper/main/tab_regimes.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
       \footnotesize
-      $^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
+      $^*$ Here, social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
   \end{table}%

### 2023-10-10 paper/response_letter/source/reviewer_1.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
 	We have also employed a series of popular change point detection methods to validate the results obtained through the Pettitt test.
-The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~\ref{table:breakpoint-detection-methods}.
+The names of these methods, their respective results, and the references to the pertinent literature can be found in the accompanying table~S2.
 A consensus was observed among all methods regarding the identification of the second change point, which consistently emerged around the year 2000.
@@
 This decision was based on two intents: (1) to ensure a balanced distribution of the number of years across each identified period (2) to stress the big change of China governance: ``reform and opening-up''.
-The consistency in the identification of breakpoints, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the change point detection algorithm.
+The consistency in the identification of change points, especially the second one, across different methods underscores the robustness of our findings, attesting to their insensitivity to the choice of the change point detection algorithm.
 This robustness reinforces the credibility and reliability of our analyses and conclusions, reflecting the methodological rigor embedded in our study.

### 2023-10-10 paper/response_letter/source/reviewer_2.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
 \begin{quote}[page=footnotes from Figure~3 and Table~1]
-    Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
+    Here, social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
 \end{quote}
@@
 \AR*{} We maintain a cautious stance regarding the assertion that changes in the ``social atmosphere'' directly lead to shifts in stable states, as our findings do not establish a causal relationship between the two.
-Nevertheless, as depicted in the newly added Table~1, prompted by your suggestion, a temporal co-occurrence between the two is observable.
-We discussed it more in the revised manuscript:
+Nevertheless, as depicted in the newly added Table~1,
+
+\input{../main/tab_regimes.tex}
+
+\AR*{} prompted by your suggestion, a temporal co-occurrence between the two is observable. We discussed it more in the revised manuscript:
 

### 2023-10-10 paper/sup/04_robustness.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
           Sensitivity analysis of the threshold of p-values.
-          \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
+          \textbf{A.} number of change points in different p-values, the scheme with two-points are the dominant situation.
           \textbf{B.} Threshold of p-values \(\alpha=0.0005\).

### 2023-10-10 paper/sup/tab_robustness.tex
fix(paper): :bug: fixing paper response letter problems
based on Shuai Wang's comment

@@
         \toprule
-        \textbf{Method} & \textbf{Breakpoints} & \textbf{Parameters$^*$} & \textbf{Reference} \\
+        \textbf{Method} & \textbf{Change points} & \textbf{Parameters$^*$} & \textbf{Reference} \\
         \midrule
@@
     \end{tabularx}
-    \footnotesize{$pen$: Penalty coefficient; $bkp$: Number of breakpoints. $No$: Non-parametric test.}
-    \caption{Comparison of different breakpoints detection methods}\label{table:breakpoint-detection-methods}
+    \footnotesize{$pen$: Penalty coefficient; $bkp$: Pre-set number of change points. $No$: This method is a non-parametric test.}
+    \caption{Comparison of different change points detection methods}\label{table:breakpoint-detection-methods}
 \end{table}

### 2023-10-10 paper/out/manuscript_v-8.3.1.tex
docs(paper): :memo: v-8.3.1
submission version to WRR - RR

--- 2023-10-10 paper/diff/manuscript_v-8.3.0.tex
@@
 	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
-The SFV-index, which has many applications, is the most comprehensive index of water stress we know.
+The SFV-index, which has many applications, is the most comprehensive index of water stress we know~\cite{qin2019}.
 
@@
 
-Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
+Two significant change points divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
 In the first period (P1, $1965 \sim 1978$), the IWGI decreased rapidly.
@@
       \footnotesize
-      $^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
+      $^*$ Here, social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
   \end{table}

### 2023-10-13 paper/main/01_introduction.tex
fix(paper): :bug: fixing SI references not appeared in manuscript

@@
 
-The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019}.
+The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019,wu2020a}.
 Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016a,song2020}.

### 2023-10-13 paper/out/manuscript_v-8.3.2.tex
fix(paper): :bug: fixing SI references not appeared in manuscript

--- 2023-10-10 paper/out/manuscript_v-8.3.1.tex
@@
 
+For robustness, we tried different change points detection methodologies~\cite{matteson2014,killick2012,bai1997,keogh2001} and the results are close (see \textit{Supporting Information~S4} and Table~S2).
 		We used $\alpha = 0.001$ as the threshold level of the p-value, meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$.
